### 2015-04-20 analysis/e5_analysis.Rmd
e5 data + first analysis half

PSYCH 130 - EXPERIMENT 4 ANALYSIS
=================================

Preliminaries.

```{r}
rm(list=ls())
source("analysis/useful_dplyr.R")
library("rjson")
```

Read in files and consolidate to the same directory.

```{r}
files <- dir("production-results/e5/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}
```

Exclude non-compliant participants and non-English speakers.

```{r}
compliant <- d.raw %>% 
  filter(grepl("training", scale)) %>%
  group_by(workerid) %>%
  summarise(compliant = judgment[scale == "training1"] == 5 & 
              judgment[scale == "training2"] == 1)

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         domain != "training1", 
         domain != "training2", 
         compliant == TRUE)
```

Main Analysis
-------------

First look at means broken down by epistemic condition.

```{r}
ms <- d %>%
  group_by(knowledge) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment))

pdf("plots/e4.pdf",width=4)
qplot(x = knowledge, y = judgment, fill=knowledge, 
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih),
                 position = position_dodge(width=.9)) + 
  ylab("Does the inference follow? 1=yes, 0=no")
dev.off()
```

Next break down by domain condition.

```{r}
ms <- d %>%
  group_by(domain, knowledge) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            n = n())

# pdf("plots/e3_level.pdf")
qplot(x = domain, y = judgment, 
      fill = knowledge,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih),
                 position = position_dodge(width=.9)) + 
  ylab("Does the inference follow? 1=yes, 0=no")
# dev.off()
```

Statistics

```{r}

summary(glmer(judgment ~ knowledge + (1 | workerid) + 
                (knowledge | domain), 
              data = d,
              family = "binomial"))

summary(glmer(judgment ~ knowledge + (1 | workerid) + 
                (1 | domain), 
              data = d,
              family = "binomial"))

```

### 2015-04-20 analysis/e5_analysis.Rmd
e5 analysis

@@
 
-Exclude non-compliant participants and non-English speakers.
+Holding off on exclusions - everyone put English, and training 2 was confusing.
 
 ```{r}
-compliant <- d.raw %>% 
-  filter(grepl("training", scale)) %>%
-  group_by(workerid) %>%
-  summarise(compliant = judgment[scale == "training1"] == 5 & 
-              judgment[scale == "training2"] == 1)
-
-d <- d.raw %>% 
-  left_join(compliant) %>%
-  filter(grepl(pattern = "english", 
-               language, ignore.case = TRUE), 
-         domain != "training1", 
-         domain != "training2", 
-         compliant == TRUE)
+# compliant <- d.raw %>% 
+#   filter(grepl("training", scale)) %>%
+#   group_by(workerid) %>%
+#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
+#               judgment[scale == "training1" & degree == "low"] < 3)
+#   
+# d <- d.raw %>% 
+#   left_join(compliant) %>%
+#   filter(grepl(pattern = "english", 
+#                language, ignore.case = TRUE), 
+#          domain != "training1", 
+#          domain != "training2", 
+#          compliant == TRUE)
+d <- d.raw %>% filter(scale != "training1")
 ```
@@
 ms <- d %>%
-  group_by(knowledge) %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
   summarise(cil = ci.low(judgment), 
@@
 
-pdf("plots/e4.pdf",width=4)
-qplot(x = knowledge, y = judgment, fill=knowledge, 
-      geom = "bar", stat = "identity", 
+qplot(x = stars, y = judgment, col = degree,
+      geom = "line", stat = "identity", 
       position = "dodge", 
@@
   geom_linerange(aes(ymin = judgment - cil, 
-                     ymax = judgment + cih),
-                 position = position_dodge(width=.9)) + 
-  ylab("Does the inference follow? 1=yes, 0=no")
-dev.off()
+                     ymax = judgment + cih)) + 
+  facet_wrap(~scale)
 ```
-
-Next break down by domain condition.
-
-```{r}
-ms <- d %>%
-  group_by(domain, knowledge) %>%
-  summarise(cil = ci.low(judgment), 
-            cih = ci.high(judgment), 
-            judgment = mean(judgment), 
-            n = n())
-
-# pdf("plots/e3_level.pdf")
-qplot(x = domain, y = judgment, 
-      fill = knowledge,
-      geom = "bar", stat = "identity", 
-      position = "dodge", 
-      data = ms) + 
-  geom_linerange(aes(ymin = judgment - cil, 
-                     ymax = judgment + cih),
-                 position = position_dodge(width=.9)) + 
-  ylab("Does the inference follow? 1=yes, 0=no")
-# dev.off()
-```
-
-Statistics
-
-```{r}
-
-summary(glmer(judgment ~ knowledge + (1 | workerid) + 
-                (knowledge | domain), 
-              data = d,
-              family = "binomial"))
-
-summary(glmer(judgment ~ knowledge + (1 | workerid) + 
-                (1 | domain), 
-              data = d,
-              family = "binomial"))
-
-```

### 2015-04-22 implicatures_e6.js
Fixed warning message prompt when subject has not selected a rating. Fixed progress bar.

@@ -130,7 +130,6 @@ var experiment = {
     data: {
 		scale: [],
 		degree: [],
-		manipulation_level: [],
 		judgment: [],
 		language: [],
 		expt_aim: [],
@@ -148,15 +147,27 @@ var experiment = {
     //Log response
     log_response: function() {
 		var response_logged = false;
-		
+
 		var judgment = $(".rating-stars").attr("style");
 		judgment = parseInt(judgment.replace(/[^\d.]/g, ''));
-		judgment /= 20;
-		experiment.data.judgment.push(judgment);
-		console.log(judgment);
-
-		nextButton.blur();
-		experiment.next();
+		console.log("judgment: ", judgment);
+		if (judgment == 0) {
+			//Else respondent didn't make a response
+		    $("#testMessage").html('<font color="red">' + 
+					   'Please make a response!' + 
+					   '</font>');
+		    judgment = $(".rating-stars").attr("style");
+		    judgment = parseInt(judgment.replace(/[^\d.]/g, ''));
+		} else {
+			judgment /= 20;
+			experiment.data.judgment.push(judgment);
+		//console.log(judgment);
+			nextButton.blur();
+			experiment.next();
+		}
+		//judgment = $(".rating-stars").attr("style");
+		//judgment = parseInt(judgment.replace(/[^\d.]/g, ''));
+		
 	},
     
     //Run every trial
@@ -172,7 +183,7 @@ var experiment = {
 		    //Clear the test message and adjust progress bar
 		    $("#testMessage").html('');  
 		    $("#prog").attr("style","width:" +
-				    String(100 * (1 - scales.length/totalTrials)) + "%");
+				    String(100 * (1 - trials.length/TOTAL_TRIALS)) + "%");
 		    
 
 		    //Trial params ---------------------------->
@@ -205,22 +216,13 @@ var experiment = {
 		    $("#rating-stars").on("click", 
 			    	function(event) {
 						$("#rating-stars").fadeOut(100).fadeIn(100);
-				// event.stopImmediatePropagation();
-				// $('.rating-stars').unbind();
-				//Set attribute once clicked
 						var selection = $("#rating-stars").val();
-				// selection = Math.floor(parseInt(selection.replace(/[^\d.]/g, '')) / 10);
-				// console.log("selection", selection);
-				// $(".rating-stars").attr({"style":"width: " + selection.toString() + "%"});
-
-				//document.getElementsByClassName("rating-stars").hoverEnabled = false;
 			});
[…]

### 2015-04-22 implicatures_e5.js
fixed swapped scalars 'liked' and 'loved'

@@ -47,8 +47,8 @@ var sents = {
 		    low:  "thought the food deserved a <b>low</b> rating?"
 		},
 		liked_loved: {		   
-		    hi:  "<b>liked</b> the food?",
-		    low:  "<b>loved</b> the food?"
+		    hi:  "<b>loved</b> the food?",
+		    low:  "<b>liked</b> the food?"
 		},
 		good_excellent: {
 			hi:  "thought the food was <b>excellent</b>?",

### 2015-04-22 implicatures_e6.js
cleaned up some commenting - no more fade-in fade-out code. Seems in good working condition

@@ -82,24 +82,24 @@ function shuffle (a) {
 var sents = {
     scale: {
 		training1: {
-		    hi:  "thought the restaurant deserved a <b>high</b> rating.",
-		    low:  "thought the restaurant deserved a <b>low</b> rating"
+		    hi:  "thought the food deserved a <b>high</b> rating.",
+		    low:  "thought the food deserved a <b>low</b> rating"
 		},
 		liked_loved: {		   
-		    hi:  "<b>loved</b> the restaurant.",
-		    low:  "<b>liked</b> the restaurant."
+		    hi:  "<b>loved</b> the food.",
+		    low:  "<b>liked</b> the food."
 		},
 		good_excellent: {
-			hi:  "thought the restaurant was <b>excellent</b>.",
-		    low:  "thought the restaurant was <b>good</b>."
+			hi:  "thought the food was <b>excellent</b>.",
+		    low:  "thought the food was <b>good</b>."
 		},
 		palatable_delicious: {
-			hi:  "thought the restaurant was <b>delicious</b>.",
-		    low:  "thought the restaurant was <b>palatable</b>."
+			hi:  "thought the food was <b>delicious</b>.",
+		    low:  "thought the food was <b>palatable</b>."
 		},
 		memorabe_unforgettable: {
-			hi:  "thought the restaurant was <b>unforgettable</b>.",
-		    low:  "thought the restaurant was <b>memorable</b>."
+			hi:  "thought the food was <b>unforgettable</b>.",
+		    low:  "thought the food was <b>memorable</b>."
 		},
 		some_all: {
 			hi: "enjoyed <b>all</b> of the food.",
@@ -150,7 +150,7 @@ var experiment = {
 
 		var judgment = $(".rating-stars").attr("style");
 		judgment = parseInt(judgment.replace(/[^\d.]/g, ''));
-		console.log("judgment: ", judgment);
+		//console.log("judgment: ", judgment); for debuggging
 		if (judgment == 0) {
 			//Else respondent didn't make a response
 		    $("#testMessage").html('<font color="red">' + 
@@ -159,15 +159,12 @@ var experiment = {
 		    judgment = $(".rating-stars").attr("style");
 		    judgment = parseInt(judgment.replace(/[^\d.]/g, ''));
 		} else {
+			//Log judgment
 			judgment /= 20;
 			experiment.data.judgment.push(judgment);
-		//console.log(judgment);
 			nextButton.blur();
 			experiment.next();
 		}
-		//judgment = $(".rating-stars").attr("style");
[…]

### 2015-04-23 implicatures_e6.js
Centered questions, added line spacing, changed spelling of memorable

@@ -97,7 +97,7 @@ var sents = {
 			hi:  "thought the food was <b>delicious</b>.",
 		    low:  "thought the food was <b>palatable</b>."
 		},
-		memorabe_unforgettable: {
+		memorable_unforgettable: {
 			hi:  "thought the food was <b>unforgettable</b>.",
 		    low:  "thought the food was <b>memorable</b>."
 		},

### 2015-04-24 implicatures_e6.js
some formatting and commenting

@@ -38,47 +38,6 @@ function shuffle (a) {
 	return o;
 }
 
-
-//sent_materials = doSentSubs(scale, type, degree);
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-// function doSentSubs (group_type, scale, degree) {
-// 	//TODO: work with this function
-
-//     //inference = sents["scales"][scale]["sent_inference"];
-//     //question = sents["scales"][scale]["sent_question"];
-//     //manipulation = sents["domains"][domain][manip];
-//     //manipulation = sents["scales"][scale]["sent_manipulation"];
-
-//     main_sent = sents["group_type"][group_type]["sent_question"];
-//     target = sents["scale"][group_type][scale][degree];
-
-//     // SP = sents["domains"][domain]["SP"]; //Plural
-//     // SS = sents["domains"][domain]["SS"]; //Singular
-//     // P1 = sents["domains"][domain]["P1"]; //Predicate 1
-//     // P2 = sents["domains"][domain]["P2"]; //Predicate 2
-//     // V1 = sents["domains"][domain]["V1"]; //Past
-//     // V2 = sents["domains"][domain]["V2"]; //Present
-
-//     //inference = inference.replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
-
-
-//     //question = question.replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
-//     main_sent = main_sent.replace("ADJ", target).replace("VP", target);
-
-//     return main_sent;
-// }
-
-//Replace speaker name in manipulation
-// function doSpeakerSub(speaker, manip) {
-// 	manip = manip.replace("SPEAKER", speaker);
-// 	return manip;
-// }
-//############################## Helper functions ##############################	
-
-//3.24.25
-//1. Change "scale" to "type"
-//2. Change "domain" to "scale"
 var sents = {
     scale: {
 		training1: {
@@ -116,11 +75,9 @@ for(var i = TOTAL_TRIALS; i > 0; --i) {
 }
 var scales = Object.keys(sents.scale);
 var scale_degrees = ["hi", "low"];
-//var totalTrials = trials.length;
+var totalTrials = scales.length; //One trial for each domain
 //Trial condition params initializations ------------------->
 
-
-var totalTrials = scales.length; //One trial for each domain
[…]

### 2015-04-24 implicatures_e6.js
commit before merge

@@ -56,7 +56,7 @@ var sents = {
 			hi:  "thought the food was <b>delicious</b>.",
 		    low:  "thought the food was <b>palatable</b>."
 		},
-		memorabe_unforgettable: {
+		memorable_unforgettable: {
 			hi:  "thought the food was <b>unforgettable</b>.",
 		    low:  "thought the food was <b>memorable</b>."
 		},

### 2015-04-24 implicatures_e6.js
test commit

@@ -1,4 +1,4 @@
-//############################## Helper functions ##############################
+//############################## Helper functions #############################
 // Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
 function showSlide(id) {
 	// Hide all slides

### 2015-04-24 analysis/e5_analysis.Rmd
e5 analysis

@@
 
+pdf("plots/e5.pdf", width=8, height = 5)
 qplot(x = stars, y = judgment, col = degree,
@@
   facet_wrap(~scale)
+dev.off()
 ```

### 2015-04-29 analysis/e5_analysis_BP.Rmd
Analysis with ben tweaks

--- 2015-04-20 analysis/e5_analysis.Rmd
@@
 rm(list=ls())
-source("analysis/useful_dplyr.R")
+p = file.path("~/Desktop/Projects/scalar_implicature/")
+source(paste0(p,"analysis/useful_dplyr.R"))
 library("rjson")
@@
 ```{r}
-files <- dir("production-results/e5/", pattern = "*.json")
+files <- dir(paste0(p,"production-results/e5/"), pattern = "*.json")
 d.raw <- data.frame()
-
+f = "3X3OR7WPZZ0BL54CDY6ARQ6UXHB8L1.json"
 for (f in files) {
-  jf <- paste("production-results/e5/",f,sep="")
+  jf <- paste(p,"production-results/e5/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
 
+pdf(paste0(p,"plots/e5.pdf"), width=8, height = 5)
 qplot(x = stars, y = judgment, col = degree,
@@
   facet_wrap(~scale)
+dev.off()
 ```
+
+barplot
+
+```{r}
+qplot(stars, judgment, facets = degree ~ scale, 
+      geom="bar", stat = "identity",
+      binwidth = 1, data=ms)
+```

### 2015-04-30 implicatures_e7.js
Functionality for prior study working. Some funky solutions because of my jquery incompetence.

@@ -38,6 +38,74 @@ function shuffle (a) {
 	return o;
 }
 
+// substitution function - do we want to save all these factors to a data object?
+//Pass a trial object in to be populated?
+function doSentSubs (base_sent, x, y)
+{
+    var name = x;
+    var c = context[x][y];
+    var gender = context[x]["pro"];
+    /*SP = sents["domains"][domain]["SP"]; //Plural
+    SS = sents["domains"][domain]["SS"]; //Singular
+    P1 = sents["domains"][domain]["P1"]; //Predicate 1
+    P2 = sents["domains"][domain]["P2"]; //Predicate 2
+    V1 = sents["domains"][domain]["V1"]; //Past
+    V2 = sents["domains"][domain]["V2"]; //Present*/
+    sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender);
+    //sent = sent.replace("Q",Q).replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
+    return sent;
+}
+
+function get_context (name, pro) {
+	return context[name][pro];
+}
+
+var base_sent = "PERSON went out to a restaurant SETTING. Without knowing anything about the food, \
+how many stars do you think GEN gave?";
+
+var context = {
+	Bob: {
+		c1: "with his friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "he"
+	},
+	John: {
+		c1: "with his friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "he"
+	},
+	Chris: {
+		c1: "with his friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "he"
+	},
+	Lisa: {
+		c1: "with her friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "she"
+	},
+	Jenny: {
+		c1: "with her friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "she"
+	},
+	Alice: {
+		c1: "with her friend",
+		c2: "alone",
+		c3: "for a birthday",
+		pro: "she"
+	}
+};
+
+var names = Object.keys(context);
+names = shuffle(names);
+var settings = ["c1", "c2", "c3"];
+/*
 var sents = {
     scale: {
 		training1: {
@@ -66,17 +134,18 @@ var sents = {
 		}
     },
 };
+*/
+var TOTAL_TRIALS = 6;
[…]

### 2015-05-01 implicatures_e7.js
minor code formatting and language tweaks - should be good to deploy.

@@ -45,14 +45,7 @@ function doSentSubs (base_sent, x, y)
     var name = x;
     var c = context[x][y];
     var gender = context[x]["pro"];
-    /*SP = sents["domains"][domain]["SP"]; //Plural
-    SS = sents["domains"][domain]["SS"]; //Singular
-    P1 = sents["domains"][domain]["P1"]; //Predicate 1
-    P2 = sents["domains"][domain]["P2"]; //Predicate 2
-    V1 = sents["domains"][domain]["V1"]; //Past
-    V2 = sents["domains"][domain]["V2"]; //Present*/
     sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender);
-    //sent = sent.replace("Q",Q).replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
     return sent;
 }
 
@@ -67,85 +60,47 @@ var context = {
 	Bob: {
 		c1: "with his friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "he"
 	},
 	John: {
 		c1: "with his friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "he"
 	},
 	Chris: {
 		c1: "with his friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "he"
 	},
 	Lisa: {
 		c1: "with her friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "she"
 	},
 	Jenny: {
 		c1: "with her friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "she"
 	},
 	Alice: {
 		c1: "with her friend",
 		c2: "alone",
-		c3: "for a birthday",
+		c3: "for a birthday party",
 		pro: "she"
 	}
 };
 
+//Basic trial data--------------------->
 var names = Object.keys(context);
 names = shuffle(names);
 var settings = ["c1", "c2", "c3"];
-/*
-var sents = {
-    scale: {
-		training1: {
-		    hi:  "thought the food deserved a <b>high</b> rating.",
-		    low:  "thought the food deserved a <b>low</b> rating"
-		},
-		liked_loved: {		   
[…]

### 2015-05-01 analysis/e5_analysis.Rmd
e6 plus models
revised contexts

@@
             cih = ci.high(judgment), 
-            judgment = mean(judgment))
+            judgment = mean(judgment), 
+            p = (judgment - 1)/4)
 
@@
 ```
+
+barplot
+
+```{r}
+qplot(stars, judgment, facets = degree ~ scale, 
+      geom="bar", stat = "identity",
+      binwidth = 1, data=ms)
+```
+
+difference scores
+
+```{r}
+ms.delta <- ms %>% 
+  select(-cil, -cih) %>%
+  spread(degree, judgment) %>%
+  mutate(delta = ifelse(scale != "liked_loved", hi - low, low - hi))
+
+pdf("plots/e5_delta.pdf", width = 8, height = 3)
+qplot(stars, delta, facets = . ~ scale, geom = "line",
+      data = ms.delta) + 
+  geom_hline(yintercept = 0, lty=2)
+dev.off()
+```

### 2015-05-01 implicatures_e7.js

@@ -45,7 +45,7 @@ function doSentSubs (base_sent, x, y)
     var name = x;
     var c = context[x][y];
     var gender = context[x]["pro"];
-    sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender);
+    sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender).replace("GEN", gender);
     return sent;
 }
 
@@ -53,44 +53,62 @@ function get_context (name, pro) {
 	return context[name][pro];
 }
 
-var base_sent = "PERSON went out to a restaurant SETTING. Without knowing anything about the food, \
-how many stars do you think GEN gave?";
+var base_sent = "<b>PERSON went out to a restaurant SETTING.</b> <br><br>Without knowing anything about the food GEN ate, \
+how many stars do you think GEN gave the restaurant?";
 
 var context = {
 	Bob: {
-		c1: "with his friend",
+		c1: "with a friend",
 		c2: "alone",
-		c3: "for a birthday party",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with his co-workers",
+	        c6: "with his parents",
 		pro: "he"
 	},
 	John: {
-		c1: "with his friend",
+		c1: "with a friend",
 		c2: "alone",
-		c3: "for a birthday party",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with his co-workers",
+	        c6: "with his parents",
 		pro: "he"
 	},
 	Chris: {
-		c1: "with his friend",
+		c1: "with a friend",
 		c2: "alone",
-		c3: "for a birthday party",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with his co-workers",
+	        c6: "with his parents",
 		pro: "he"
 	},
 	Lisa: {
-		c1: "with her friend",
+		c1: "with a friend",
 		c2: "alone",
-		c3: "for a birthday party",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with her co-workers",
+	        c6: "with her parents",
 		pro: "she"
 	},
 	Jenny: {
-		c1: "with her friend",
+		c1: "with a friend",
 		c2: "alone",
-		c3: "for a birthday party",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with her co-workers",
+	        c6: "with her parents",
 		pro: "she"
 	},
 	Alice: {
[…]

### 2015-05-07 models/Model_Playspace.Rmd
Adding preliminary models using e5 data as informativity scores. Currently implemented wtih <some, all> but shouldn't be hard to generalize to other scalars

---
title: "Scalar_M1"
author: "BPeloquin"
date: "April 23, 2015"
output: html_document
---

```{r}
p = file.path("~/Desktop/Projects/scalar_implicature/")
source(paste0(p,"analysis/useful_dplyr.R"))
library("rjson")

#############   NOTES   #################
# <none, some, all> condition: the model correctly produces implicature.
# However "all"" condition is predicted to be compabitible with a 4 rating.
# This appears to be driven by several factors
# 1) High priors over 4
# 2) Fairly high compabitibiliy with All and four stars from e5
#
#
#########################################

#Basic form of the model
##############################################################################################
##########  p.Lp(r | u) ~ [p.S(u | r) * p.L(r)] / SIGMA_over_alts(p.S('u|r)*p.L(r)) ##########
##############################################################################################

r = seq(from=1, to=5) #Ratings
raw.priors = c(0.003, 0.053, 0.403, 0.387, 0.150) #Measured priors
unif.priors = rep(.2, times=5) #Uniform priors

#Informatitivy data from e5
none.prob = c(1, 0, 0, 0, 0)
some.prob = c(.16, .36, .68, .83, .83)
all.prob = c(.01, .11, .35, .68, .98)

scale.info = c(none.prob, some.prob, all.prob)
scale.matrix = matrix(data = scale.info, nrow = 5, ncol = 3)
scale = c("none", "some", "all")
colnames(scale.matrix) = c(scale)

#Informatitivy data from e5 normalized
n.none.prob = none.prob / sum(none.prob)
n.some.prob = some.prob / sum(some.prob)
n.all.prob = all.prob / sum(all.prob)
n.scale.info = c(n.none.prob, n.some.prob, n.all.prob)
n.scale.matrix = matrix(data = n.scale.info, nrow = 5, ncol = 3)
colnames(n.scale.matrix) = c(scale)
alpha = 4;

#cost function in length of chars
u.cost = function(u) {
  return(nchar(u))
}

##############################################################################################
##########                            MODEL IMPLEMENTATION                          ##########
##############################################################################################
#Key------------------------>
#u = utterance [string]
#alts = alternative utterances
#r = rating index [1-5]
#d.info = informativity judgements
#Key------------------------>

#speaker likelihood helper 
speaker.lhd = function(utt, info) {
  exp(alpha*(log(info) - 3)) #Rething cost??? 
}
#speaker likelihood normalized
speaker.prob = function(utt, rating, s.matrix) {
  num = speaker.lhd(utt, s.matrix[rating, utt])
  norm = 0
  for (i in 1:length(scale) ) {
    current.u = scale[i] #current utterance
    norm = norm + speaker.lhd(current.u, s.matrix[rating, current.u])
  }
  return(num / norm)
}

#non-normalized posterior------------------------------>
nn.post = function(utt, rating, s.matrix, priors) {
  return(speaker.prob(utt, rating, s.matrix) * priors[rating])
}

#normalized posterior---------------------------------->
norm.post = function(utt, rating, s.matrix, priors) {
  nn = nn.post(utt, rating, s.matrix, priors)
  norm = 0
  for (i in 1:5) {
    norm = norm + nn.post(utt, i, s.matrix, priors)
  }
  return(nn / norm)
}
speaker.prob = function(utt, rating, s.matrix)
##############################################################################################
##########                              DATA / PLOTS                                ##########
##############################################################################################
#priors
qplot(c(1:5), raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Priors over ratings")

#SOME ---------------------------------------------->
d.some.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, unif.priors)})
d.some.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("some", i, scale.matrix, raw.priors)})
qplot(c(1:5), d.some.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="Some Posteriors")

#ALL ------------------------------------------------>
d.all.raw.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, scale.matrix, raw.priors)})
d.all.unif.priors = sapply(1:5, FUN=function(i){
  norm.post("all", i, n.scale.matrix, unif.priors)})
qplot(c(1:5), d.all.raw.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Raw priors")
qplot(c(1:5), d.all.unif.priors,
      geom="bar", stat = "identity",
      binwidth = 1, main="All Posteriors, Uniform priors")
```

### 2015-05-08 models/Model_Playspace.Rmd
model update

@@
 
+Preliminaries.
+
 ```{r}
-p = file.path("~/Desktop/Projects/scalar_implicature/")
+rm(list=ls())
+p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
 source(paste0(p,"analysis/useful_dplyr.R"))
-library("rjson")
+library(rjson)
+```
 
-#############   NOTES   #################
-# <none, some, all> condition: the model correctly produces implicature.
-# However "all"" condition is predicted to be compabitible with a 4 rating.
-# This appears to be driven by several factors
-# 1) High priors over 4
-# 2) Fairly high compabitibiliy with All and four stars from e5
-#
-#
-#########################################
+## Notes
+* <none, some, all> condition: the model correctly produces implicature.
+* However "all"" condition is predicted to be compabitible with a 4 rating.
+* This appears to be driven by several factors
+  * 1) High priors over 4
+  * 2) Fairly high compabitibiliy with All and four stars from e5
 
-#Basic form of the model
-##############################################################################################
-##########  p.Lp(r | u) ~ [p.S(u | r) * p.L(r)] / SIGMA_over_alts(p.S('u|r)*p.L(r)) ##########
-##############################################################################################
+## Basic form of the model
 
+$$ p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$
+
+```{r}
 r = seq(from=1, to=5) #Ratings
@@
 }
+```
 
-##############################################################################################
-##########                            MODEL IMPLEMENTATION                          ##########
-##############################################################################################
-#Key------------------------>
-#u = utterance [string]
-#alts = alternative utterances
-#r = rating index [1-5]
-#d.info = informativity judgements
-#Key------------------------>
+## MODEL IMPLEMENTATION
+
+Key:
+* u = utterance [string]
+* alts = alternative utterances
+* r = rating index [1-5]
+* d.info = informativity judgements
+
+```{r}
 
@@
 }
-speaker.prob = function(utt, rating, s.matrix)
-##############################################################################################
-##########                              DATA / PLOTS                                ##########
-##############################################################################################
-#priors
+
+```
+
+## DATA / PLOTS
+
+Priors
+```{r}
 qplot(c(1:5), raw.priors,
@@
       binwidth = 1, main="Priors over ratings")
+```
 
-#SOME ---------------------------------------------->
+SOME
+```{r}
 d.some.unif.priors = sapply(1:5, FUN=function(i){
@@
   norm.post("some", i, scale.matrix, raw.priors)})
+
 qplot(c(1:5), d.some.raw.priors,
@@
       binwidth = 1, main="Some Posteriors")
+```
 
-#ALL ------------------------------------------------>
+ALL
+```{r}
 d.all.raw.priors = sapply(1:5, FUN=function(i){
@@
   norm.post("all", i, n.scale.matrix, unif.priors)})
+
 qplot(c(1:5), d.all.raw.priors,
@@
       binwidth = 1, main="All Posteriors, Raw priors")
-qplot(c(1:5), d.all.unif.priors,
-      geom="bar", stat = "identity",
-      binwidth = 1, main="All Posteriors, Uniform priors")
 ```

### 2015-05-08 models/Model_Playspace.Rmd
model revs

@@
 
+Read Data 
+---------
+
 ```{r}
-r = seq(from=1, to=5) #Ratings
-raw.priors = c(0.003, 0.053, 0.403, 0.387, 0.150) #Measured priors
-unif.priors = rep(.2, times=5) #Uniform priors
+priors = read.csv("models/prior.csv")
+speaker = read.csv("models/speaker.csv")
+listener = read.csv("models/listener.csv")
+# none.prob = c(1, 0, 0, 0, 0)
+# some.prob = c(.16, .36, .68, .83, .83)
+# all.prob = c(.01, .11, .35, .68, .98)
 
-#Informatitivy data from e5
-none.prob = c(1, 0, 0, 0, 0)
-some.prob = c(.16, .36, .68, .83, .83)
-all.prob = c(.01, .11, .35, .68, .98)
-
-scale.info = c(none.prob, some.prob, all.prob)
-scale.matrix = matrix(data = scale.info, nrow = 5, ncol = 3)
-scale = c("none", "some", "all")
-colnames(scale.matrix) = c(scale)
-
-#Informatitivy data from e5 normalized
-n.none.prob = none.prob / sum(none.prob)
-n.some.prob = some.prob / sum(some.prob)
-n.all.prob = all.prob / sum(all.prob)
-n.scale.info = c(n.none.prob, n.some.prob, n.all.prob)
-n.scale.matrix = matrix(data = n.scale.info, nrow = 5, ncol = 3)
-colnames(n.scale.matrix) = c(scale)
-alpha = 4;
-
-#cost function in length of chars
-u.cost = function(u) {
-  return(nchar(u))
-}
 ```
@@
 ```{r}
+#cost function in length of chars
+u.cost = function(u) {
+  return(nchar(u))
+}
 
 #speaker likelihood helper 
-speaker.lhd = function(utt, info) {
+speaker.lhd = function(utt, info, alpha) {
   exp(alpha*(log(info) - 3)) #Rething cost??? 
 }
+
 #speaker likelihood normalized
-speaker.prob = function(utt, rating, s.matrix) {
-  num = speaker.lhd(utt, s.matrix[rating, utt])
+speaker.prob = function(utt, rating, s.matrix, alpha, scale) {
+  num = speaker.lhd(utt, s.matrix[rating, utt], alpha)
   norm = 0
@@
     current.u = scale[i] #current utterance
-    norm = norm + speaker.lhd(current.u, s.matrix[rating, current.u])
+    norm = norm + speaker.lhd(current.u, s.matrix[rating, current.u], alpha)
   }
@@
 
-#non-normalized posterior------------------------------>
-nn.post = function(utt, rating, s.matrix, priors) {
-  return(speaker.prob(utt, rating, s.matrix) * priors[rating])
+#non-normalized posterior
+nn.post = function(utt, rating, s.matrix, priors, alpha, scale) {
+  return(speaker.prob(utt, rating, s.matrix, alpha, scale) * priors[rating])
 }
 
-#normalized posterior---------------------------------->
-norm.post = function(utt, rating, s.matrix, priors) {
-  nn = nn.post(utt, rating, s.matrix, priors)
+#normalized posterior
+norm.post = function(utt, rating, s.matrix, priors, 
+                     alpha = 1, scale = c("low","hi")) {
+  nn = nn.post(utt, rating, s.matrix, priors, alpha, scale)
   norm = 0
   for (i in 1:5) {
-    norm = norm + nn.post(utt, i, s.matrix, priors)
+    norm = norm + nn.post(utt, i, s.matrix, priors, alpha, scale)
   }
@@
 }
+
+```
+
+model wrapper functions:
+
+```{r}
+run.rsa <- function(d) {
+
+  scale.matrix <- d %>% 
+    select(stars, degree, speaker.p, prior.p) %>% 
+    spread(degree, speaker.p) %>% 
+    mutate(hi = hi / sum(hi), 
+           low = low / sum(low)) %>%
+    as.matrix
+
+  preds <- expand.grid(stars = 1:5, 
+              degree = c("low","hi")) %>%
+    rowwise %>%
+    mutate(listener.pred =  norm.post(scale, stars, 
+                                      s.matrix = scale.matrix[,c("low","hi")], 
+                                      prior = scale.matrix[,"prior.p"]))
+
+  return(preds)
+} 
+```
+
+RUN MODEL
+--------
+
+Run model on actual data
+
+```{r}
+data <- left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale) %>%
+  do(model.preds = run.rsa(.))
 

### 2015-05-11 models/Model_Playspace.Rmd
Minor tweaks to working dir call and priors plot. Need to fix RUN MODEL section

@@
 rm(list=ls())
-p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
-source(paste0(p,"analysis/useful_dplyr.R"))
+#p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
+source("analysis/useful_dplyr.R")
 library(rjson)
@@
 ```{r}
-qplot(c(1:5), raw.priors,
+qplot(c(1:5), priors$prior.p,
       geom="bar", stat = "identity",

### 2015-05-15 models/Model_Playspace.Rmd
practice commit branch
tinkering with data pipeline - need to fix equally-sized data frames error

@@
 rm(list=ls())
-#p = file.path("~/Projects/Scalar Implicature/scalar_implicature/")
 source("analysis/useful_dplyr.R")
@@
 listener = read.csv("models/listener.csv")
-# none.prob = c(1, 0, 0, 0, 0)
-# some.prob = c(.16, .36, .68, .83, .83)
-# all.prob = c(.01, .11, .35, .68, .98)
-
 ```
@@
 #speaker likelihood helper 
-speaker.lhd = function(utt, info, alpha) {
-  exp(alpha*(log(info) - 3)) #Rething cost??? 
+#speaker.lhd = function(utt, info, alpha) {
+#  exp(alpha*(log(info) - 3)) #Rething cost??? 
+#}
+speaker.lhd = function(d) {
+  exp(4*(log(d) - 3)) #Rethink alpha and costs?
 }
@@
 #speaker likelihood normalized
-speaker.prob = function(utt, rating, s.matrix, alpha, scale) {
-  num = speaker.lhd(utt, s.matrix[rating, utt], alpha)
+speaker.prob = function(rating, degree, m) {
+  num = speaker.lhd(m[rating, degree])
   norm = 0
-  for (i in 1:length(scale) ) {
-    current.u = scale[i] #current utterance
-    norm = norm + speaker.lhd(current.u, s.matrix[rating, current.u], alpha)
+  for ( i in 1:2 ) {
+    norm = norm + speaker.lhd(m[rating, i])
   }
@@
 #non-normalized posterior
-nn.post = function(utt, rating, s.matrix, priors, alpha, scale) {
-  return(speaker.prob(utt, rating, s.matrix, alpha, scale) * priors[rating])
+nn.post = function(rating, degree, m) {
+  return(speaker.prob(rating, degree, m) * priors[rating, "prior.p"])
 }
@@
 #normalized posterior
-norm.post = function(utt, rating, s.matrix, priors, 
-                     alpha = 1, scale = c("low","hi")) {
-  nn = nn.post(utt, rating, s.matrix, priors, alpha, scale)
+norm.post = function(rating, degree, m) {
+  nn = nn.post(rating, degree, m)
   norm = 0
   for (i in 1:5) {
-    norm = norm + nn.post(utt, i, s.matrix, priors, alpha, scale)
+    norm = norm + nn.post(i, degree, m)
   }
@@
 }  
-
 ```
@@
 run.rsa <- function(d) {
+  #BP------->
+  #Get current matrix
+  get.m = function(s, m) {
+    m2 <- filter(m, scale == s) %>%
+      spread(degree, speaker.p) %>%
+      mutate(hi = hi / sum(hi), 
+                  low = low / sum(low)) %>%
+      select(hi, low)
+    return(m2)
+  }
 
-  scale.matrix <- d %>% 
+  scale.matrix <- data %>% 
+    select(stars, degree, speaker.p, prior.p) %>%
+    mutate(listener.pred = norm.post(stars, degree, get.m(scale, .)))
+
+  return scale.matrx$
+ #BP------->
+
+  #Old Mike code------>
+  scale.matrix <- data %>% 
     select(stars, degree, speaker.p, prior.p) %>% 
@@
               degree = c("low","hi")) %>%
-    rowwise %>%
-    mutate(listener.pred =  norm.post(scale, stars, 
-                                      s.matrix = scale.matrix[,c("low","hi")], 
-                                      prior = scale.matrix[,"prior.p"]))
 
+    scale.matrix %>% 
+    mutate(listener.pred = norm.post(stars, degree, get.m(scale, scale.matrix)))
   return(preds)

### 2015-05-15 models/Model_Playspace.Rmd
commented out line
currently can't pass external d.f to mutate function. need work around

@@
 
+  m = d.m
+  s = "liked_loved"
+  get.m(s, d.m)
+
+  d.m <- data %>% 
+    select(stars, degree, speaker.p, prior.p)
+
   scale.matrix <- data %>% 
     select(stars, degree, speaker.p, prior.p) %>% 
-    mutate(listener.pred = norm.post(stars, degree, get.m(scale, .)))
+    rowwise() %>%
+    mutate(listener.pred = norm.post(stars, degree, get.m(scale, d.m)))
 
-  return scale.matrx$
+  #return scale.matrx$
  #BP------->

### 2015-05-15 models/Model_Playspace.Rmd
model revision

--- 2015-05-15 models/Model_Playspace.Rmd
@@
 #cost function in length of chars
-u.cost = function(u) {
-  return(nchar(u))
-}
+# u.cost = function(u) {
+#   return(nchar(u))
+# }
 
 #speaker likelihood helper 
-#speaker.lhd = function(utt, info, alpha) {
-#  exp(alpha*(log(info) - 3)) #Rething cost??? 
-#}
-speaker.lhd = function(d) {
-  exp(4*(log(d) - 3)) #Rethink alpha and costs?
+speaker.lhd = function(d, alpha, cost = 0) {
+  exp(alpha*(log(d) - cost)) #Rethink alpha and costs?
 }
@@
 #speaker likelihood normalized
-speaker.prob = function(rating, degree, m) {
-  num = speaker.lhd(m[rating, degree])
+speaker.prob = function(rating, degree, m, alpha) {
+  num = speaker.lhd(m[rating, degree], alpha)
   norm = 0
-  for ( i in 1:2 ) {
-    norm = norm + speaker.lhd(m[rating, i])
+  for (i in 1:ncol(m)) {
+    norm = norm + speaker.lhd(m[rating, i], alpha)
   }
@@
 #non-normalized posterior
-nn.post = function(rating, degree, m) {
-  return(speaker.prob(rating, degree, m) * priors[rating, "prior.p"])
+nn.post = function(rating, degree, m, alpha, useprior) {
+
+  if (useprior) {
+    prior <- priors[rating, "prior.p"]
+  } else {
+    prior = .2 
+  }
+
+  speaker.prob(rating, degree, m, alpha) * prior
 }
@@
 #normalized posterior
-norm.post = function(rating, degree, m) {
-  nn = nn.post(rating, degree, m)
+norm.post = function(rating, degree, m, alpha, useprior) {
+  nn = nn.post(rating, degree, m, alpha, useprior)
   norm = 0
   for (i in 1:5) {
-    norm = norm + nn.post(i, degree, m)
+    norm = norm + nn.post(i, degree, m, alpha, useprior)
   }
@@
 ```{r}
-run.rsa <- function(d) {
-  #BP------->
-  #Get current matrix
-  get.m = function(s, m) {
-    m2 <- filter(m, scale == s) %>%
+run.rsa <- function(d, alpha = 1, useprior = TRUE, usenone = FALSE) {
+
+  mat <- d %>%
+    select(stars, degree, speaker.p) %>%
     spread(degree, speaker.p) %>%
@@
     select(hi, low)
-    return(m2)
+
+  if (usenone) {
+    mat$none <- c(1, 0, 0, 0, 0)
   }
 
-  scale.matrix <- data %>% 
-    select(stars, degree, speaker.p, prior.p) %>%
-    mutate(listener.pred = norm.post(stars, degree, get.m(scale, .)))
+  d$pred <- round(as.numeric(mapply(norm.post, 
+                                    d$stars, 
+                                    d$degree, 
+                                    MoreArgs = list(m = mat, 
+                                                    alpha = alpha, 
+                                                    useprior = useprior))), 
+                  digits=4)
 
-  return scale.matrx$
- #BP------->
-
-  #Old Mike code------>
-  scale.matrix <- data %>% 
-    select(stars, degree, speaker.p, prior.p) %>% 
-    spread(degree, speaker.p) %>% 
-    mutate(hi = hi / sum(hi), 
-           low = low / sum(low)) %>%
-    as.matrix
-
-  preds <- expand.grid(stars = 1:5, 
-              degree = c("low","hi")) %>%
-
-    scale.matrix %>% 
-    mutate(listener.pred = norm.post(stars, degree, get.m(scale, scale.matrix)))
-  return(preds)
+  return(d)
 } 
@@
   mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
-  group_by(scale) %>%
-  do(model.preds = run.rsa(.))
+  group_by(scale)
+```
 
+run it.
+
+```{r}
+md <- data %>%
+  do(run.rsa(., alpha = 1, useprior = FALSE, usenone = TRUE))
+
+qplot(stars, listener.p, col=degree, 
+      data = md) + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 2)
 ```

### 2015-05-16 models/Model_Playspace.Rmd
more alternatives'
minor tweaks to model formatting

@@
     prior <- priors[rating, "prior.p"]
-  } else {
+  } else { #unif prior
     prior = .2 
@@
   if (usenone) {
-    mat$none <- c(1, 0, 0, 0, 0)
+    mat$none <- c(.8, .2, 0, 0, 0)
+    mat$bad <- c(.25, .5, .25, 0, 0)
+
   }
 
-  d$pred <- round(as.numeric(mapply(norm.post, 
-                                    d$stars, 
-                                    d$degree, 
+  d$pred <- round(as.numeric(mapply(norm.post, d$stars, d$degree, 
                                     MoreArgs = list(m = mat, 
@@
 md <- data %>%
-  do(run.rsa(., alpha = 1, useprior = FALSE, usenone = TRUE))
+  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))
 
 qplot(stars, listener.p, col=degree, 
-      data = md) + 
+      data = md, main="Model vs Human judgments") + 
   facet_wrap(~scale) + 

### 2015-05-20 models/Model_Playspace.Rmd
quick look at tuning alpha - find best.alpha by data with highest correlation with human judgemets

@@
 md <- data %>%
-  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))
+  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
 
@@
   geom_line(aes(y = pred), lty = 2)
+
+#Which alpha has tightest correlation with human judgements
+alphas = seq(from=1, to=25)
+cors = sapply(alphas, FUN=function(n) {
+  md <- data %>%
+    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))
+  cor(md$pred, md$listener.p)
+})
+qplot(alphas, cors)
+best.alpha = which(cors == max(cors))
 ```

### 2015-05-21 analysis/e5_analysis.Rmd
model revs
different take on informativity metric from e5. Looking at % in top agreement (4 or 5 on likert)

@@
 ```{r}
+n = length(unique(d$workerid))
+
 ms <- d %>%
@@
             p = (judgment - 1)/4)
+write.csv(ms, "models/e5.csv", row.names=FALSE)
 
+# Different take on speaker.p
+ma <- d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
+  summarise(speaker.p = mean( ifelse( (judgment >= 4), 1, 0)))
+write.csv(ma, "models/e5a.csv", row.names=FALSE)
+
+#Original lexical semantics plot
 pdf("plots/e5.pdf", width=8, height = 5)
@@
 dev.off()
+
+#New lexical semantics plot
+qplot(x = stars, y = speaker.p, col = degree,
+      geom = "line", stat = "identity", 
+      position = "dodge", 
+      data = ma) + facet_wrap(~scale)
 ```
@@
       binwidth = 1, data=ms)
+
+qplot(stars, p, facets = degree ~ scale, 
+      geom="bar", stat = "identity",
+      binwidth = 1, data=ma)
 ```

### 2015-05-21 models/Model_Playspace.Rmd
different take on informativity metric from e5. Looking at % in top agreement (4 or 5 on likert)

--- 2015-05-16 models/Model_Playspace.Rmd
@@
 
-$$ p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$
+$$p_{L_p} (r \mid u) \propto \frac{p_S(u | r) p_{L_0}(r)}{\sum_{u' \in alts}{p_S(u' \mid r) p_{L_0}(r)}}$$
 
@@
 priors = read.csv("models/prior.csv")
+# Possible transformations
+#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
+priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
+
 speaker = read.csv("models/speaker.csv")
+speaker.alt = read.csv("models/e5a.csv")
 listener = read.csv("models/listener.csv")
@@
     mat$bad <- c(.25, .5, .25, 0, 0)
-
   }
@@
 
-run it.
+## RUN MODEL
 
 ```{r}
+# Which alpha has tightest correlation with human judgements
+alphas = seq(from=1, to=20)
+fit = sapply(alphas, FUN=function(n) {
   md <- data %>%
-  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))
+    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))
 
+  mean((md$pred - md$listener.p)^2)
+})
+qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
+best.alpha = which(fit == min(fit))
+best.alpha
+
+# RUN MODEL
+md <- data %>%
+  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
+```
+
+## DATA / PLOTS ------------>
+
+```{r}
+# Facets all scales, Model vs Human judgements
 qplot(stars, listener.p, col=degree, 
@@
   geom_line(aes(y = pred), lty = 2)
+
+ggplot(md, aes(x=listener.p, y=pred)) +
+    geom_point(aes(colour = stars)) +
+    geom_smooth(method=lm) + ggtitle("Model pred vs Human judgment")
+cor(md$pred, md$listener.p)
 ```
-
-## DATA / PLOTS
 
@@
 ```
-
-SOME
-```{r}
-d.some.unif.priors = sapply(1:5, FUN=function(i){
-  norm.post("some", i, scale.matrix, unif.priors)})
-d.some.raw.priors = sapply(1:5, FUN=function(i){
-  norm.post("some", i, scale.matrix, raw.priors)})
-
-qplot(c(1:5), d.some.raw.priors,
-      geom="bar", stat = "identity",
-      binwidth = 1, main="Some Posteriors")
-```
-
-ALL
-```{r}
-d.all.raw.priors = sapply(1:5, FUN=function(i){
-  norm.post("all", i, scale.matrix, raw.priors)})
-d.all.unif.priors = sapply(1:5, FUN=function(i){
-  norm.post("all", i, n.scale.matrix, unif.priors)})
-
-qplot(c(1:5), d.all.raw.priors,
-      geom="bar", stat = "identity",
-      binwidth = 1, main="All Posteriors, Raw priors")
-```

### 2015-05-22 models/Model_Playspace.Rmd
Possible transformations for priors, MSE for alpha, additional plotting. Some code re-arranged ordering of data-load and model run.
Messing around with addition of negative valence, adjusting valence, scalar sd and mean - need to figure out why knitr isn't working

@@
 rm(list=ls())
+setwd("~/Desktop/Projects/scalar_implicature/")
 source("analysis/useful_dplyr.R")
@@
 
-Read Data 
+Read Data ---->
 ---------
@@
 priors = read.csv("models/prior.csv")
-# Possible transformations
-#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
-priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
-
+# Possible transformations --->
+priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
+#priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
+#priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))
 speaker = read.csv("models/speaker.csv")
-speaker.alt = read.csv("models/e5a.csv")
+#speaker.alt = read.csv("models/e5a.csv")
 listener = read.csv("models/listener.csv")
@@
   }
-
   speaker.prob(rating, degree, m, alpha) * prior
@@
   if (usenone) {
-    mat$none <- c(.8, .2, 0, 0, 0)
-    mat$bad <- c(.25, .5, .25, 0, 0)
+    mat$none <- c(.9, .1, 0, 0, 0)
+    mat$neg_valence <- c(.2, .5, .2, .1, 0)
   }
@@
   md <- data %>%
-    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))
+    do(run.rsa(., alpha = n, useprior = TRUE, usenone = TRUE))
 
   mean((md$pred - md$listener.p)^2)
+  #cor(md$pred, md$listener.p)
 })
@@
 md <- data %>%
-  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
+  do(run.rsa(., alpha = best.alpha, useprior = TRUE, usenone = TRUE))
 ```
@@
 qplot(stars, listener.p, col=degree, 
-      data = md, main="Model vs Human judgments") + 
+      data=md, main="Model vs Human judgments",
+      ylab="Posterior judgments p(r|u)") + 
   facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 2)
+  geom_line(aes(y = pred), lty = 4)
 
@@
 
+Speaker informativity measures
+```{r}
+# Scalar judgment scores by rating
+qplot(x = stars, y = speaker.judgment, col = degree, ymax = 5,
+      geom = "line", stat = "identity", 
+      position = "dodge", 
+      data = speaker, main= "Scalar + Rating compabililty") + 
+  geom_linerange(aes(ymin = speaker.judgment - speaker.cil, 
+                     ymax = speaker.judgment + speaker.cih)) + 
+  facet_wrap(~scale)
+
+# Scalar compatibility (information ratings)
+qplot(x = stars, y = speaker.p, col = degree, ymax = 1,
+      geom = c("point", "smooth"), stat = "identity", 
+      position = "dodge", 
+      data = speaker, main= "Scalar Compaibility distr") + 
+  facet_wrap(~scale)
+```
+
+Pragmatic Listener Judgments
+```{r}
+qplot(x=stars, y=listener.p, col=degree, ymax=1,
+      geom=c("point", "smooth"), stat = "identity",
+      ylab="Compatibility", position="dodge", 
+      data=listener, main="Pragmatic listener judgements") + 
+  facet_wrap(~scale)
+```
+
+Model judgments
+```{r}
+qplot(x = stars, y = pred, col = degree, ymax = 1, ylab="Posterior judgments",
+      geom = c("point", "smooth"), stat = "identity", 
+      position = "dodge", 
+      data = md, main= "Scalar + Rating compabililty") + 
+  facet_wrap(~scale)
+```
+
 Priors
@@
       binwidth = 1, main="Priors over ratings")
+
+shapiro.test(priors$prior.p)
+ks.test(priors$prior.p, "pnorm", mean=mean(priors$prior.p), sd=sd(priors$prior.p))
 ```
+
+```{r}
+#Some properties of our scales
+scales = levels(d$scale)[1:5]
+scales.info = sapply(scales, FUN=function(s) {
+    curr <- data %>%
+      filter(scale == s, degree == "hi") %>%
+      select(speaker.p)
+    return( c(sd(as.numeric(unlist(curr[,2]))),
+              mean(as.numeric(unlist(curr[,2])))))
+})
+row.names(scales.info) = c("sd", "mean")
+scales.info <- t(scales.info)
+```

### 2015-05-28 models/Model_Playspace.Rmd
Committing preliminary integration with Yelp data

@@
 priors = read.csv("models/prior.csv")
+
+# Yelp priors
+priors$prior.p = c(0.09020902, 0.10561056, 0.16281628, 0.30463046, 0.33673367)
 # Possible transformations --->
@@
 speaker = read.csv("models/speaker.csv")
-#speaker.alt = read.csv("models/e5a.csv")
+#speaker = read.csv("models/e5a.csv")
+speaker = read.csv("models/yelp1.csv")
 listener = read.csv("models/listener.csv")
@@
 }
+
+# speaker.prob = function(rating, degree, m, alpha) {
+#   p = m[rating, degree] / sum(m[rating, ])
+#   
+#   return(p)
+# }
 
@@
     mat$none <- c(.9, .1, 0, 0, 0)
-    mat$neg_valence <- c(.2, .5, .2, .1, 0)
+    mat$bad <- c(.5, .9, .4, .1, 0)
   }
@@
   md <- data %>%
-    do(run.rsa(., alpha = n, useprior = TRUE, usenone = TRUE))
+    do(run.rsa(., alpha = n, useprior = FALSE, usenone = TRUE))
 
-  mean((md$pred - md$listener.p)^2)
-  #cor(md$pred, md$listener.p)
+  #mean((md$pred - md$listener.p)^2)
+  cor(md$pred, md$listener.p)
 })
 qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
-best.alpha = which(fit == min(fit))
+best.alpha = which(fit == max(fit))
 best.alpha
@@
 md <- data %>%
-  do(run.rsa(., alpha = best.alpha, useprior = TRUE, usenone = TRUE))
+  do(run.rsa(., alpha = best.alpha, useprior = FALSE, usenone = TRUE))
 ```
@@
       data = speaker, main= "Scalar + Rating compabililty") + 
-  geom_linerange(aes(ymin = speaker.judgment - speaker.cil, 
-                     ymax = speaker.judgment + speaker.cih)) + 
+  #geom_linerange(aes(ymin = speaker.judgment - speaker.cil, 
+  #                   ymax = speaker.judgment + speaker.cih)) + 
   facet_wrap(~scale)

### 2015-07-20 analysis/e5_analysis.Rmd
analysis tweaks

@@
 }
+
+# Number of participants
+length(unique(d.raw$workerid))
 ```
@@
 
-# Different take on speaker.p
+#### Different take on speaker.p ###
 ma <- d %>%
@@
   group_by(scale, degree, stars) %>%
-  summarise(speaker.p = mean( ifelse( (judgment >= 4), 1, 0)))
+  summarise(speaker.p = sum( ifelse( (judgment >= 4), 1, 0)))
+  #summarise(speaker.p = sum( ifelse( (judgment == 5), stars, 0)))
 write.csv(ma, "models/e5a.csv", row.names=FALSE)
+
+table(ma$stars, ma$judgment, ma$degree) / sum(table(ma$stars, ma$judgment))
+mn <- filter(ma, scale == "good_excellent", degree=="hi")
+nt = table(mn$star, mn$judgment)
+nt = nt / sum(nt)
+
+mz <- filter(mz, scale == "good_excellent", degree=="low")
+nz = table(mz$star, mz$judgment)
+
+t = nz - nt
+
+t = matrix(table(d$judgment, d$degree), ncol=2, nrow = 5)
+p = t[,1] - t[,2]
+qplot(c(1, 2, 3, 4, 5), ma$speaker.p)
 

### 2015-07-20 implicatures_e7.js
updated e7 js

@@ -53,7 +53,7 @@ function get_context (name, pro) {
 	return context[name][pro];
 }
 
-var base_sent = "<b>PERSON went out to a restaurant SETTING.</b> <br><br>Without knowing anything about the food GEN ate, \
+var base_sent = "<b>PERSON went out to a restaurant SETTING.</b> <br><br>Without knowing anything about the food GEN ate,<br>\
 how many stars do you think GEN gave the restaurant?";
 
 var context = {

### 2015-07-20 models/Model_Playspace.Rmd
fiddling with model

--- 2015-05-22 models/Model_Playspace.Rmd
@@
 ```{r}
-priors = read.csv("models/prior.csv")
+# Priors ---------------->
+emp.priors = read.csv("models/prior.csv")
+yelp.priors = read.csv("models/yelp1_priors.csv")
+priors = yelp.priors
 # Possible transformations --->
-priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
+#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
 #priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
 #priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))
+
+# Speaker informativity ------------------------->
 speaker = read.csv("models/speaker.csv")
-#speaker.alt = read.csv("models/e5a.csv")
+speaker = read.csv("models/speaker_normed.csv") # for printing out semantic distr's
+speaker = read.csv("models/yelp1.csv")
+#speaker = read.csv("models/e5a.csv")
+
+# Listener judgments ---------------------------->
 listener = read.csv("models/listener.csv")
@@
 ```{r}
-#cost function in length of chars
+# cost 
+# ----
 # u.cost = function(u) {
@@
 
-#speaker likelihood helper 
+# speaker likelihood helper 
+# ------------------------
 speaker.lhd = function(d, alpha, cost = 0) {
@@
 
-#speaker likelihood normalized
+# speaker likelihood normalized
+# -----------------------------
 speaker.prob = function(rating, degree, m, alpha) {
@@
 
-#non-normalized posterior
+# non-normalized posterior 
+# ------------------------
 nn.post = function(rating, degree, m, alpha, useprior) {
@@
 
-#normalized posterior
+# normalized posterior
+# --------------------
 norm.post = function(rating, degree, m, alpha, useprior) {
@@
 ```{r}
+# Run rsa model
+# --------------------
 run.rsa <- function(d, alpha = 1, useprior = TRUE, usenone = FALSE) {
@@
 ```{r}
+# data
+# ----
 data <- left_join(speaker, listener) %>%
-  left_join(priors) %>%
+  left_join(emp.priors) %>%
   rowwise %>%
@@
 ```{r}
+# Tuning alpha, experimenting with params
+# ---------------------------------------
+
 # Which alpha has tightest correlation with human judgements
@@
   md <- data %>%
-    do(run.rsa(., alpha = n, useprior = TRUE, usenone = TRUE))
+    do(run.rsa(., alpha = n, useprior = T, usenone = TRUE))
 
-  mean((md$pred - md$listener.p)^2)
-  #cor(md$pred, md$listener.p)
+  #return(mean((md$pred - md$listener.p)^2))
+  return(cor(md$pred, md$listener.p))
 })
-qplot(alphas, fit, main="MSE for alpha values", ylab="MSE")
-best.alpha = which(fit == min(fit))
+qplot(alphas, fit, main="Cor for alpha values", ylab="MSE")
+best.alpha = which(fit == max(fit))
 best.alpha
@@
 # RUN MODEL
+# ---------
 md <- data %>%
-  do(run.rsa(., alpha = best.alpha, useprior = TRUE, usenone = TRUE))
+  do(run.rsa(., alpha = best.alpha, useprior = T, usenone = TRUE))
 ```
@@
 qplot(stars, listener.p, col=degree, 
-      data=md, main="Model vs Human judgments",
-      ylab="Posterior judgments p(r|u)") + 
+      data=md, main="Model vs Human judgments\nSemantics measured empirically",
+      ylab="Posteriors p(r|u)") + 
   facet_wrap(~scale) + 
@@
 
-ggplot(md, aes(x=listener.p, y=pred)) +
+ggplot(md, aes(x=pred, y=listener.p)) +
     geom_point(aes(colour = stars)) +
-    geom_smooth(method=lm) + ggtitle("Model pred vs Human judgment")
+    geom_smooth(method=lm) +
+  ggtitle("Model performance\nCorpus based") +
+  labs(x = "model prediction", y="human judgments")
 cor(md$pred, md$listener.p)
+
+# Individual scales ---------->
+# Scalar compatibility (information ratings) - individual plot
+current_scale = subset(md, scale=="good_excellent",
+                    select=c(stars, scale, speaker.p, listener.p, degree, pred))
+levels(current_scale$degree) = c("excellent", "good")
+qplot(stars, listener.p, col=degree, 
+      data=current_scale, main="Model vs Human judgments\nCorpus based",
+      ylab="p(stars|scalar_term)") +
+geom_line(aes(y = pred), lty = 4)
+
 ```
@@
 
-# Scalar compatibility (information ratings)
-qplot(x = stars, y = speaker.p, col = degree, ymax = 1,
+# Scalar compatibility (information ratings) - facet plot
+qplot(x = stars, y = speaker.normed, col = degree, ymax = 1,
       geom = c("point", "smooth"), stat = "identity", 
-      position = "dodge", 
-      data = speaker, main= "Scalar Compaibility distr") + 
+      position = "dodge", ylab="P(r|u)",
+      data = speaker, main= "Scalar compatibility\nCorpus based") + 
   facet_wrap(~scale)
+
+# Scalar compatibility (information ratings) - individual plot
+current_scale = subset(speaker, scale=="good_excellent",
+                    select=c(stars, scale, speaker.p, degree))
+
+levels(current_scale$degree) = c("excellent", "good")
+qplot(x = stars, y = speaker.p, col = degree, ymax = .75,
+      geom = c("point", "smooth"), stat = "identity", 
+      position = "dodge", ylab="p(stars|scalar_term)",
+      data = current_scale,
+      main= "Literal listener semantics\nCorpus data")
 ```
@@
   facet_wrap(~scale)
+
+# Individual scales ---------->
+current_scale = subset(listener, scale=="good_excellent",
+                    select=c(stars, scale, listener.p, degree, pred))
+levels(current_scale$degree) = c("excellent", "good")
+qplot(stars, listener.p, col=degree, xmin=0,
+      geom = c("point", "smooth"), stat = "identity", 
+      data=current_scale, main="Pragmatic listener",
+      ylab="p(stars|scalar_term)")
 ```
@@
 ```{r}
-qplot(c(1:5), priors$prior.p,
+qplot(c(1:5), yelp.priors$prior.p,
       geom="bar", stat = "identity",
-      binwidth = 1, main="Priors over ratings")
+      binwidth = 1, xlab="stars", ylab="p(stars)",
+      main="Priors\nCorpus based")
 
-shapiro.test(priors$prior.p)
-ks.test(priors$prior.p, "pnorm", mean=mean(priors$prior.p), sd=sd(priors$prior.p))
+shapiro.test(emp.priors$prior.p)
+ks.test(emp.priors$prior.p, "pnorm",
+        mean=mean(emp.priors$prior.p), sd=sd(emp.priors$prior.p))
 ```

### 2015-07-22 analysis/e5_analysis.Rmd
trying to break down literal listener semantics - just getting started

@@
 ```{r}
+
 rm(list=ls())
+#setwd("~/Desktop/Projects/scalar_implicature/")
 source("analysis/useful_dplyr.R")
@@
 ```
+
+# Histograms of agreement bins
+```{r}
+raw.scales <- d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars)
+
+raw.scales = raw.scales[
+  order(raw.scales[,2], raw.scales[,3], raw.scales[,4]),]
+raw.scales %>% gather()
+
+barplot(raw.scales[which(
+  raw.scales[,"scale"] == "good_excellent"
+  & raw.scales[,"degree"] == "low"
+  & raw.scales[,"stars"] == 1), ]$judgment)
+
+?gather
+library(dplyr)
+# From http://stackoverflow.com/questions/1181060
+stocks <- data.frame(
+  time = as.Date('2009-01-01') + 0:9,
+  X = rnorm(10, 0, 1),
+  Y = rnorm(10, 0, 2),
+  Z = rnorm(10, 0, 4)
+)
+?spread
+gather(stocks, stock, price, -time)
+stocksm <- stocks %>% gather(stock, price, -time)
+stocksm %>% spread(stock, price)
+
+# for reference -------->
+ms <- d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
+  summarise(cil = ci.low(judgment), 
+            cih = ci.high(judgment), 
+            judgment = mean(judgment), 
+            p = (judgment - 1)/4)
+# for reference -------->
+```
+
+# Gaussian Analysis 7-21-15
+```{r}
+# Just having a look using hard coded mean and var from e5a data
+# Note: e5a data looks at counts of likert ratings over 4 on aggreableness
+all.x = seq(1, 5, length=100)
+all.y = dnorm(x, mean=4.537037037, sd=sqrt(0.285665295))  
+plot(all.x,all.y, type="l", lwd=1, ylim = c(0, 1), col="blue")
+
+some.x = seq(1, 5, length=100)
+some.y = dnorm(x, mean=4.020522388, sd=sqrt(0.786892264))
+plot(some.x,some.y, type="l", lwd=1)
+
+lines(some.x, some.y, col="red")
+```

### 2015-07-24 analysis/e5_analysis2.Rmd
Literal listener semantics anaysis #2: Looking at matching between likert ratings and stars shown, visualized a couple ways. Looks like there is a good deal of matching, especially at extremes. Rolling together [1,2], 3, [4,5] seeing similar results as with means. Can we approximate gaussians with mean and variance for agreements here?

---
output: pdf_document
---
PSYCH 130 - EXPERIMENT 4 ANALYSIS
=================================

Preliminaries.

```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
```

Read in files and consolidate to the same directory.

```{r}
files <- dir("production-results/e5/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e5/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answer$scale,
                   degree = jd$answer$degree,
                   stars = jd$answer$manipulation_level,
                   judgment = as.numeric(jd$answer$judgment),
                   language = jd$answer$language)
  d.raw <- bind_rows(d.raw, id)
}

# Number of participants
length(unique(d.raw$workerid))
```

Holding off on exclusions - everyone put English, and training 2 was confusing. 
```{r}
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
d <- d.raw %>% filter(scale != "training1")
```

Main Analysis
-------------
```{r}
names(d)
dim(d)
# removing language - main data.frame()
d$stars = as.numeric(as.character(d$stars))/20
dt = d[, -6]
scalars = c("some_all", "liked_loved", "palatable_delicious",
            "good_excellent", "memorable_unforgettable")
dgrs = c("low", "hi")
```

Histogram Plots for our scalars
```{r}
scalar.agreements = function(scalar_pair, degree) {
  pair = dt[which(dt$scale == scalar_pair), ]
  scalar = pair[which(pair$degree == degree), ]
  scalar = spread(scalar, stars, judgment)
  # plots
  par(mfrow = c(2,3))
  wrd = unlist(strsplit(scalar_pair, "_"))
  wrd = ifelse(degree == "low", wrd[1], wrd[2])
  likert.plots(scalar, wrd)
}
likert.plots = function(scalar, wrd) {
  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
           xlab="Agree", ylab="Counts")
}
for (i in scalars) {
  for (j in dgrs) {
    scalar.agreements(i, j)
  }
}
```

Matching in data
```{r}
match = dt$stars == dt$judgment
par(mfrow=c(1,1))
barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
dm = data.frame(dt, match)

# Matches by stars
table(select(dm, stars, match))

# Matches by stars & degrees
table(select(dm, stars, match, degree))
table(select(dm, stars, match, degree))
```

Rolling 1,2 4,5
```{r}
ds = d[, -6] %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))

compatibility = function(scalar_pair, degree) {
  dr = ds[which(ds$scale == scalar_pair & ds$degree == degree),] %>%
    select(stars, speaker.hi)
  return(dr$speaker.hi / sum(dr$speaker.hi))
}
plot.pairs = function(scalar_pair) {
  plot(compatibility(scalar_pair, "hi"), type="b", col="red",
       main=toString(scalar_pair), ylab="% Agree Norm", xlab="Stars",
       xlim = c(1,5), ylim = c(0,1))
  lines(compatibility(scalar_pair, "low"), type="b", col="blue")  
}
compatibility("good_excellent", "hi")
par(mfrow=c(1,1))
plot.pairs("good_excellent")
par(mfrow=c(2,3))
for (i in 1:length(scalars)) {
  plot.pairs(scalars[i])  
}
```

### 2015-07-24 implicatures_e8.js
new literal listener exp with binary choice. DV changed to [reasonability] of scalar use in context

@@ -1,0 +1,216 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+var sents = {
+    scale: {
+		training1: {
+			//because training trial hi and low are the same
+		    hi:  "thought the food deserved a <b>high</b> rating?",
+		    low:  "thought the food deserved a <b>low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi:  "<b>loved</b> the food?",
+		    low:  "<b>liked</b> the food?"
+		},
+		good_excellent: {
+			hi:  "thought the food was <b>excellent</b>?",
+		    low:  "thought the food was <b>good</b>?"
+		},
+		palatable_delicious: {
+			hi:  "thought the food was <b>delicious</b>?",
+		    low:  "thought the food was <b>palatable</b>?"
+		},
+	memorable_unforgettable: {
+			hi:  "thought the food was <b>unforgettable</b>?",
+		    low:  "thought the food was <b>memorable</b>?"
+		},
+		some_all: {
[…]

### 2015-07-30 implicatures_e8.js
Added age and gender data collection functionality

@@ -102,6 +102,8 @@ var experiment = {
 		language: [],
 		expt_aim: [],
 		expt_gen: [],
+		age: [],
+		gender:[]
     },
     
     //End the experiment
@@ -144,7 +146,7 @@ var experiment = {
     
     //Run every trial
     next: function() {
-    	//If no trials are left go to debreifing
+    	//If no trials are left go to debriefing
 		if (!trials.length) {
 			return experiment.debriefing();
 		}
@@ -200,16 +202,28 @@ var experiment = {
 		}
     },
 
-    //Show debrief
+    // Show debrief
     debriefing: function() {
-		showSlide("debriefing");
+    	showSlide("debriefing");
+		// Get age
+    	var select_age = '';
+    	for (i = 18; i <= 100; i++) {
+    		select_age += '<option val=' + i + '>' + i + '</option>';
+    	}
+    	$('#age').html(select_age);    	
     },
 
     //###:-------------Log debrief data-------------:###
     submit_comments: function() {
-		experiment.data.language.push(document.getElementById("homelang").value);
-		experiment.data.expt_aim.push(document.getElementById("expthoughts").value);
-		experiment.data.expt_gen.push(document.getElementById("expcomments").value);
+		experiment.data.language.push(document.getElementById("homelang").value);		// language
+		experiment.data.expt_aim.push(document.getElementById("expthoughts").value);	// thoughts
+		experiment.data.expt_gen.push(document.getElementById("expcomments").value);	// comments
+		experiment.data.age.push(document.getElementById("age").value);					// age
+		if (document.getElementById("Male").checked) {
+    		experiment.data.gender.push(document.getElementById("Male").value);			// gender
+    	} else {
+    		experiment.data.gender.push(document.getElementById("Female").value);
+    	}
 		experiment.end();
     }
     //###:-------------Log debrief data-------------:###

### 2015-07-30 analysis/e5_analysis2.Rmd
looking at literal listener semantics - matching between likert and star-rating, rolling together <4, 5> to approx binary

@@
 }
+scalar.agreements("liked_loved", "hi")
+
 ```

### 2015-07-30 implicatures_e8.js
changed DV wording to do you think

@@ -188,7 +188,7 @@ var experiment = {
 		    //Display Trials -------------------------->
 			$(".rating-stars").attr("style","width: " +
 							    manipulation_level + "%");
-		    $("#sent_question").html("Is it reasonable to assume that the person "+
+		    $("#sent_question").html("Do you think the person "+
 					     sent_materials);
 		    //Display Trials -------------------------->
 

### 2015-09-17 analysis/e8_analysis.Rmd
general update after exp 8 run

---
title: "e8_analysis"
author: "BPeloquin"
date: "August 6, 2015"
output: html_document
---

Prelims
-------
```{r}
rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library("rjson")
```

Read in data
------------
```{r}
files <- dir("production-results/e8/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e8/", f, sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId,
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}
```

Initial data clean
------------------
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")

ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment)) 
# write to csv for model
write.csv(ms, "models/e8.csv", row.names=FALSE)
```

Literal Listener semantics plot - averages
```{r}
pdf("plots/e8_L0.pdf", width=8, height = 5)
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", main = "Average", data = ms) + 
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale)
dev.off()
```

Literal Listener semantics plot - counts
```{r}
qplot(x = stars, y = cnt.judgment,
      geom = "bar", fill = factor(degree), stat = "identity", 
      position = "dodge", main = "counts", data = ms) +
  facet_wrap(~scale)
```

Looking at mean and var
```{r}

weighted.avg = function(scalar, degree) {
  return( sum(
    ms[which(ms$scale == scalar & ms$degree == degree), ]$speaker.p *
      ms[which(ms$scale == scalar & ms$degree == degree), ]$stars) / 5)   
}
weighted.avg("some_all", "low")

normals = matrix(ncol = 4, nrow = 5)
colnames(overall.cnts) = dgrs
for (i in 1:length(scalars)) {
  normals[i, 1] = 
    mean(ms[which(ms$scale == scalars[i] & ms$degree == "low"),]$cnt.judgment)
  normals[i, 2] = 
    mean(ms[which(ms$scale == scalars[i] & ms$degree == "hi"),]$cnt.judgment)
  normals[i, 3] = 
    var(ms[which(ms$scale == scalars[i] & ms$degree == "low"),]$cnt.judgment)
  normals[i, 4] = 
    var(ms[which(ms$scale == scalars[i] & ms$degree == "hi"),]$cnt.judgment)
}
colnames(normals) = c("mean hi", )
```

Looking at counts
```{r}
scalars = c("some_all",
            "liked_loved",
            "palatable_delicious",
            "good_excellent",
            "memorable_unforgettable")
dgrs = c("low", "hi")
overall.cnts = matrix(ncol = 2, nrow = 5)
colnames(overall.cnts) = dgrs
for (i in 1:length(scalars)) {
  overall.cnts[i, 1] = 
    sum(ms[which(ms$scale == scalars[i] & ms$degree == "low"),]$cnt.judgment)
  overall.cnts[i, 2] = 
    sum(ms[which(ms$scale == scalars[i] & ms$degree == "hi"),]$cnt.judgment)
}
overall.cnts = data.frame(overall.cnts)
overall.cnts$scalar = scalars

# for plotting
dc = overall.cnts %>%
  gather(degree, cnt, -scalar)
dc

qplot(scalars, y=cnt,
      geom="bar", stat="identity",
      data=dc) +
  facet_wrap(~degree)
qplot(scalars, y=hi,
      geom="bar", stat="identity", main="low", ylim=c(0, 150),
      data=data.frame(overall.cnts))

```

### 2015-09-17 models/RSA_Model2.Rmd
general update after exp 8 run

---
title: "RSA_model2"
author: "BPeloquin"
date: "August 6, 2015"
output: html_document
---

Set-up
------

```{r}
rm(list=ls())

library(knitr)
library(rjson)

opts_chunk$set(cache=TRUE)

source("analysis/useful_dplyr.R")
```

Data
----
```{r}
speaker = read.csv("models/e8.csv")
listener = read.csv("models/listener.csv")
# priors
# ------
unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empirical = read.csv("models/prior.csv")
yelp = read.csv("models/yelp1_priors.csv")
priors = unif
# combine speaker / listener
data <- left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
head(data)
```

Model
-----
```{r}
# speaker informativity
# ---------------------
speaker.lhd = function(d, alpha, cost = 0) {
  exp(alpha*(log(d) - cost))
}
# speaker likelihood
# ------------------
speaker.prob = function(rating, degree, m, alpha) {
  numerator = speaker.lhd(m[rating, degree], alpha)
  norm = 0
  for (i in 1:ncol(m)) {
    norm = norm + speaker.lhd(m[rating, i], alpha)
  }
  return(numerator / norm)
}
# non-normalized posterior
# -----------------------
nn.post = function(rating, degree, m, alpha, useprior) {
  prior <- priors[rating, "prior.p"]
  speaker.prob(rating, degree, m, alpha) * prior
}
# normalized posterior
# --------------------
norm.post = function(rating, degree, m, alpha, useprior) {
  nn = nn.post(rating, degree, m, alpha, useprior)
  norm = 0
  for (i in 1:5) {
    # summation over all scale mates
    norm = norm + nn.post(i, degree, m, alpha, useprior)
  }
  return(nn / norm)
}  
```

Run Model
----------
```{r}
# Run rsa model
# --------------------
run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {

  mat <- d %>%
    select(stars, degree, speaker.p) %>%
    spread(degree, speaker.p) %>%
    mutate(hi = hi / sum(hi), 
           low = low / sum(low)) %>%
    select(hi, low)

  if (usenone) {
    mat$none <- c(0.8, 0.2, 0, 0, 0)
    #mat$bad <- c(.5, .9, .4, .1, 0)
  }

  d$pred <- round(as.numeric(mapply(norm.post, d$stars, d$degree, 
                                    MoreArgs = list(m = mat, 
                                                    alpha = alpha, 
                                                    useprior = useprior))), 
                  digits=4)

  return(d)
} 
```

Run model
---------
```{r}
md <- data %>%
  do(run.rsa(., alpha = 5, useprior = T, usenone = T))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md, main="Model vs Human judgments\nSemantics measured empirically",
      ylab="Posteriors p( rating | word )") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

ggplot(md, aes(x=pred, y=listener.p)) +
    geom_point(aes(colour = stars)) +
    geom_smooth(method=lm) +
  ggtitle("Model performance\nCorpus based") +
  labs(x = "model prediction", y="human judgments")
cor(md$pred, md$listener.p)

# scalar level cor
specific.cor = function(scalar) {
  return (cor(md[which(md$scale==scalar), ]$pred,
              md[which(md$scale==scalar), ]$listener.p))
}
qplot(unique(md$scale), y = sapply(unique(md$scale), specific.cor),
    aes(group=1), geom="bar", stat="identity")
```

Tuning
-------
```{r}
# alpha
alphas = seq(from=1, to=10)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = F, usenone = T))

  return(mean((md$pred - md$listener.p)^2))
  #return(cor(md$pred, md$listener.p))
})
qplot(alphas, fit, main="Cor for alpha values", ylab="MSE")
best.alpha = which(fit == min(fit))
best.alpha
```

### 2015-09-18 implicatures_e9.js
preliminary commit for alternatives elicitation exp. Built out basic forms, need to capture data in .js. Based off Van Tiel Scalar Diversity Exp. 3

@@ -1,0 +1,240 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+
+
+
+
+
+
+var sents = {
+    scale: {
+		training1: {
+			//because training trial hi and low are the same
+		    hi:  "thought the food deserved a <b>high</b> rating.",
+		    low:  "thought the food deserved a <b>low</b> rating."
+		},
+		liked_loved: {		   
+		    hi:  "<b>loved</b> the food.",
+		    low:  "<b>liked</b> the food."
+		},
+		good_excellent: {
+			hi:  "thought the food was <b>excellent</b>.",
+		    low:  "thought the food was <b>good</b>."
+		},
+		palatable_delicious: {
+			hi:  "thought the food was <b>delicious</b>.",
+		    low:  "thought the food was <b>palatable</b>."
+		},
+	memorable_unforgettable: {
+			hi:  "thought the food was <b>unforgettable</b>.",
+		    low:  "thought the food was <b>memorable</b>."
+		},
+		some_all: {
[…]

### 2015-09-18 implicatures_e9.js
Commit before changing the structure of the sents{} data object

@@ -48,7 +48,6 @@ function shuffle (a) {
 var sents = {
     scale: {
 		training1: {
-			//because training trial hi and low are the same
 		    hi:  "thought the food deserved a <b>high</b> rating.",
 		    low:  "thought the food deserved a <b>low</b> rating."
 		},

### 2015-09-19 implicatures_e9.js
correctly getting form data, but need to fix trials - make sure we don't get repeats and fix order of training

@@ -43,33 +43,43 @@ function shuffle (a) {
 
 
 
-
-
 var sents = {
     scale: {
 		training1: {
-		    hi:  "thought the food deserved a <b>high</b> rating.",
-		    low:  "thought the food deserved a <b>low</b> rating."
+		    hi:  "<b>high</b>",
+		    low:  "<b>low</b>",
+		    before: " thought the food deserved a ",
+		    after: " rating."
 		},
 		liked_loved: {		   
-		    hi:  "<b>loved</b> the food.",
-		    low:  "<b>liked</b> the food."
+		    hi:  "<b>loved</b>",
+		    low:  "<b>liked</b>",
+		    before: " ",
+		    after: " the food."
 		},
 		good_excellent: {
-			hi:  "thought the food was <b>excellent</b>.",
-		    low:  "thought the food was <b>good</b>."
+			hi:  "<b>excellent</b>",
+		    low:  "<b>good</b>",
+		    before: " thought the food was ",
+		    after: "."
 		},
 		palatable_delicious: {
-			hi:  "thought the food was <b>delicious</b>.",
-		    low:  "thought the food was <b>palatable</b>."
+			hi:  "<b>delicious</b>",
+		    low:  "<b>palatable</b>",
+		    before: " thought the food was ",
+		    after: "."
 		},
-	memorable_unforgettable: {
-			hi:  "thought the food was <b>unforgettable</b>.",
-		    low:  "thought the food was <b>memorable</b>."
+		memorable_unforgettable: {
+			hi:  "<b>unforgettable</b>",
+		    low:  "<b>memorable</b>",
+		    before: " thought the food was ",
+		    after: "."
 		},
 		some_all: {
-			hi: "enjoyed <b>all</b> of the food they ate.",
-			low: "enjoyed <b>some</b> of the food they ate."
+			hi: "<b>all</b>",
+			low: "<b>some</b>",
+			before: "enjoyed ",
+		    after: " of the food they ate."
 		}
     },
 };
@@ -101,7 +111,9 @@ var experiment = {
 		scale: [],
 		degree: [],
 		manipulation_level: [],
-		judgment: [],
+		alt1: [],
+		alt2: [],
+		alt3: [],
 		language: [],
 		expt_aim: [],
 		expt_gen: [],
@@ -117,28 +129,25 @@ var experiment = {
 		}, 1500);
     },
 
+    reset_form: function() {
+    	document.getElementById("alt1").value = "";
+		document.getElementById("alt2").value = "";
[…]

### 2015-09-19 implicatures_e9.js
fixed repeated trials - now correctly only displaying the trials we're interested in

@@ -84,21 +84,17 @@ var sents = {
     },
 };
 
-
 //Trial condition params initializations ------------------->
-var TOTAL_TRIALS = 10;
+var TOTAL_TRIALS = 8;
+var TRAINING_ROUNDS = 2;
 var trials = [];
 for(var i = 0; i < TOTAL_TRIALS; i++) {
 	trials.push(i);
 }
-trials = shuffle(trials); 								// randomize trials
-var scales = Object.keys(sents.scale);
+trials = shuffle(trials); 						// randomize trials
+var scales = Object.keys(sents.scale);			// array of target scales
+scales.shift(); 								// remove 'training1' trial from scales array
 var scale_degrees = ["hi", "low"];
-
-//var manipulation = ["20", "40", "60", "80", "100"];
-//var totalTrials = trials.length;
-//Trial condition params initializations ------------------->
-
 
 
 // Show the instructions slide -- this is what we want subjects to see first.
@@ -172,11 +168,21 @@ var experiment = {
 		    $("#prog").attr("style","width:" +
 				    String(100 * ((TOTAL_TRIALS - trials.length)/TOTAL_TRIALS)) + "%");
 		    
-		    
-		    current_trial = Math.floor(trials.shift() / 2);
-		    current_scale = scales[current_trial];
-		    degree = scale_degrees[current_trial % 2];
 
+		    if (TRAINING_ROUNDS == 2) {
+		     	current_scale = "training1";
+		     	degree = "hi";
+		     	TRAINING_ROUNDS--;
+		    } else if (TRAINING_ROUNDS == 1) {
+		    	current_scale = "training1";
+		     	degree = "low";
+		     	TRAINING_ROUNDS--;
+		    } else {
+
+			    current_trial = trials.shift();
+			    current_scale = scales[Math.floor(current_trial / 2)];
+			    degree = scale_degrees[current_trial % 2];	
+		    }
 			sent_materials = sents.scale[current_scale]["before"] + 
 							 sents.scale[current_scale][degree] +
 							 sents.scale[current_scale]["after"];

### 2015-09-20 implicatures_e9.js
included some target word formatting into .js file

@@ -46,38 +46,38 @@ function shuffle (a) {
 var sents = {
     scale: {
 		training1: {
-		    hi:  "<b>high</b>",
-		    low:  "<b>low</b>",
+		    hi:  "<font color=\"blue\"><b>high</b></font>",
+		    low:  "<font color=\"blue\"><b>low</b></font>",
 		    before: " thought the food deserved a ",
 		    after: " rating."
 		},
 		liked_loved: {		   
-		    hi:  "<b>loved</b>",
-		    low:  "<b>liked</b>",
+		    hi:  "<font color=\"blue\"><b>loved</b></font>",
+		    low:  "<font color=\"blue\"><b>liked</b></font>",
 		    before: " ",
 		    after: " the food."
 		},
 		good_excellent: {
-			hi:  "<b>excellent</b>",
-		    low:  "<b>good</b>",
+			hi:  "<font color=\"blue\"><b>excellent</b></font>",
+		    low:  "<font color=\"blue\"><b>good</b></font>",
 		    before: " thought the food was ",
 		    after: "."
 		},
 		palatable_delicious: {
-			hi:  "<b>delicious</b>",
-		    low:  "<b>palatable</b>",
+			hi:  "<font color=\"blue\"><b>delicious</b></font>",
+		    low:  "<font color=\"blue\"><b>palatable</b></font>",
 		    before: " thought the food was ",
 		    after: "."
 		},
 		memorable_unforgettable: {
-			hi:  "<b>unforgettable</b>",
-		    low:  "<b>memorable</b>",
+			hi:  "<font color=\"blue\"><b>unforgettable</b></font>",
+		    low:  "<font color=\"blue\"><b>memorable</b></font>",
 		    before: " thought the food was ",
 		    after: "."
 		},
 		some_all: {
-			hi: "<b>all</b>",
-			low: "<b>some</b>",
+			hi: "<font color=\"blue\"><b>all</b></font>",
+			low: "<font color=\"blue\"><b>some</b></font>",
 			before: "enjoyed ",
 		    after: " of the food they ate."
 		}
@@ -216,10 +216,11 @@ var experiment = {
 		    //Display Trials -------------------------->
 			//$(".rating-stars").attr("style","width: " +
 			//				    manipulation_level + "%");
-		    $("#sent_question").html("In a recent restaurant review someone said "+
-					     sent_materials);
+		    $("#sent_question").html("\"In a recent restaurant review someone said they "+
+					     sent_materials + "\"");
[…]

### 2015-09-21 models/RSA_Model2.Rmd
minor formatting change

@@
 nn.post = function(rating, degree, m, alpha, useprior) {
-  prior <- priors[rating, "prior.p"]
+  prior = priors[rating, "prior.p"]
   speaker.prob(rating, degree, m, alpha) * prior
@@
 md <- data %>%
-  do(run.rsa(., alpha = 5, useprior = T, usenone = T))
+  do(run.rsa(., alpha = 1, useprior = T, usenone = T))
 ```

### 2015-09-21 analysis/e8_analysis.Rmd
added norming section - do we take care of this in RSA??? Next step to plot the literal semantics

@@
       data=data.frame(overall.cnts))
+```
 
+```{r}
+# working with vector
+normed.counts = NA
+s = scalars[1]
+d = dgrs[2]
+
+for (s in scalars) {
+  cnts = data.frame()
+  for (d in dgrs) {
+    cnts$scale = rep(s, 5)
+    cnts$dgrs = rep(d, 5)
+    cnts = ms[ms$scale == s & ms$degree == d, "cnt.judgment"] + 1       # Laplace smooth
+    cnts = cnts / sum(cnts)
+  }
+  new.sems = c(new.sems, cnts)
+}
+as.vector(unlist(new.sems))
+ms
+
+# init.df
+# ------
+# initialze a new nrows * ncols data.frame()
+init.df = function(ncols, nrows, names = NA) {
+  new.df = data.frame(matrix(ncol = ncols, nrow = nrows))
+  colnames(new.df) = names
+  return(new.df)
+}
+
+# working wit df()
+new.sems = data.frame(scale=character(),
+                      degree=character(),
+                      stars=numeric(),
+                      cnt.judgment=numeric())
+for (s in scalars) {
+  cnts = init.df(4, 5, names=c("scale", "degree", "stars", "cnt.judgment"))
+  for (d in dgrs) {
+    cnts$scale = rep(s, 5)
+    cnts$degree = rep(d, 5)
+    cnts$stars = seq(1, 5)
+    cnts$cnt.judgment = ms[ms$scale == s & ms$degree == d, ]$cnt.judgment + 1 # Laplace smooth
+    cnts$cnt.judgment = cnts$cnt.judgment / sum(cnts$cnt.judgment)
+    new.sems = rbind(new.sems, cnts)
+  }
+}
+# for merging with ms df()
+new.sems = rbind(new.sems, data.frame(scale=rep("training1", 5),
+                           degree=c(rep("hi",5), rep("low",5)),
+                           cnt.judgment=rep(NA,10)))
+ma = merge(ms, new.sems, by=c("scale", "degree", "stars"))
 ```

### 2015-10-03 analysis/alts_analysis.py
preliminary data organization - returns .json object with all alternatives for each scalar. no data clearning.

@@ -1,0 +1,75 @@
+import os
+import json
+
+
+# read in data
+# ------------
+path = "production-results/e9/"
+files = os.listdir(path)
+
+# data org
+# --------
+scalars = {"memorable_unforgettable":	{"hi": "unforgettable", "low": "memorable"},
+		   "liked_loved": 			  	{"hi": "loved", "low": "liked" },
+		   "some_all": 					{"hi": "all", "low": "some" },
+		   "palatable_delicious": 		{"hi": "delicious", "low": "palatable" },
+		   "good_excellent": 			{"hi": "excellent", "low": "good" },
+		   "training1": 				{"hi": "high", "low": "low"}}
+
+scalar_data = { "liked":[],
+				"loved":[],
+				"memorable":[],
+				"unforgettable":[],
+				"liked":[],
+				"loved":[],
+				"good":[],
+				"excellent":[],
+				"palatable":[],
+				"delicious":[],
+				"some":[],
+				"all":[],
+				"high":[],
+				"low":[] }
+
+# read in for each respondent
+# ---------------------------
+for f in files:
+	with open(path + f) as data_file:    
+		data = json.load(data_file)
+
+		scales = data['answers']['data']['scale']    	# get scale
+		degree = data['answers']['data']['degree']		# get degree
+		alt1 = data['answers']['data']['alt1']			# alternative 1
+		alt2 = data['answers']['data']['alt2']			# alternative 2
+		alt3 = data['answers']['data']['alt3']  		# alternative 3
+		
+		# if True:
+		# 	print("----------------------------------------")
+		# 	print f
+		# 	print("scales: %s" % scales)
+		# 	print("degree: %s" % degree)
+		# 	print("alt1: %s" % alt1)
+		# 	print("alt2: %s" % alt2)
+		# 	print("alt3: %s" % alt3)
+		# 	print("----------------------------------------")
+
+		for i in range(len(scales)):
+			scale = scales[i]
+			d = degree[i]
+			a1 = alt1[i]
+			a2 = alt2[i]
+			a3 = alt3[i]
+
+			scalar_data[scalars[scale][d]].extend((a1, a2, a3))
+
+# print scalar_data
+# print scalar_data["liked"]
+# print len(scalar_data["liked"])
+# print scalar_data["some"]
+# print len(scalar_data["some"])
+
+# Output to .json to for R
+# ------------------------
+with open('alts.json', 'w') as fp:
+    json.dump(scalar_data, fp)
+

### 2015-10-03 analysis/e9_altsAnalysis.Rmd
preliminary analylsis of alternatives in R. Using table to derive counts. Think of a better way to do this.

---
title: "e9_altsAnalysis"
author: "BPeloquin"
date: "October 2, 2015"
output: html_document
---

```{r}
#library(rjson)
rm(list = ls())
library(jsonlite)
setwd("~/Desktop/Projects/scalar_implicature/")
```

```{r}
d0 = fromJSON(file="alts.json")
names(d0)
scalar_data = c()
for (scalar in names(d0)) {
  for(word in d[[scalar]]) {
    scalar = c(scalar, word)
    print(scalar)
  }
  scalar_data = rbind(scalar_data, scalar)
}
scalar_data
```

```{r}
d1 = fromJSON("alts.json", simplifyDataFrame=T)
d1 = as.data.frame(d1)
# conver to lower case
sapply(seq(1, ncol(d1)), FUN=function(i) {
  d1[,i] = tolower(d1[,i])
})

sort(table(d1$all))
sort(table(d1$some))
sort(table(d1$unforgettable))
sort(table(d1$memorable))
sort(table(d1$excellent))
sort(table(d1$good))
sort(table(d1$loved))
sort(table(d1$liked))
sort(table(d1$delicious))
sort(table(d1$palatable))

```

### 2015-10-06 alts_analysis.py
data cleaning and output. infrastructure for manual data cleaning.

@@ -1,0 +1,179 @@
+import os
+import json
+import collections
+import copy
+from nltk import metrics
+
+path = "production-results/e9/"
+
+# fill this in with functionality we want to run
+toDo = "read_data edit_data output_editedData"
+
+#################################################################################
+#################################################################################
+# Helpers
+# -------
+def convertLower(lst):
+	"""
+	convert each item in lst to lower case
+	"""
+	lower_list = [x.strip().lower() for x in lst]
+	return lower_list
+
+def combineIncorrectSpellings(input_list, dist, cached): 
+	"""
+	Given input lst of alternatives and dist (numeric) calculate edit distance.
+	If edit distance is greater than 0 and less than 'dist' manually update data
+	"""
+	
+	lst = copy.deepcopy(input_list)
+	n = len(lst)
+	# All pairwise comparisons
+	for i in range(n - 1):
+		for j in range(i, n):
+			print("i: %s, j: %s" % (i, j))
+			edit_distance = metrics.distance.edit_distance(lst[i], lst[j])	# store edit distance
+
+			if ((edit_distance > 0 and edit_distance < dist) or\
+				(abs(len(lst[i]) - len(lst[j])) == 1) and lst[i][0] == lst[j][0]):	# single representation
+				combine_strings = str(lst[i]+'_'+lst[j])
+
+				# first check cache for existing values
+				if combine_strings in cached.keys():
+					if (cached[combine_strings] == "do-not-change"):
+						print("***Don't change pair: %s" % combine_strings)
+						continue
+					else:
+						print("cache[%s] =  %s" % (combine_strings, cached[combine_strings]))
+						lst[i] = cached[combine_strings]
+						lst[j] = cached[combine_strings]
+						continue
+				else:
+					print("--------------------------------------------------")
+					print("Editing... %s and %s" % (lst[i], lst[j]))
+					make_edit = raw_input("Make an edit here? ('y'/'n'): ")
+
+				# go into manual edit
+				if make_edit == 'y':
+					print("--------------------------")
+					print("*%s*,*%s*" % (lst[i], lst[j]))
+					print("--------------------------")
+					change = raw_input("'left word' is correct press 1; " +\
+						"'right word' is correct press 2; " + \
+						"Type correct spelling (or 0 for not a match): ")
+
+					if change == '1':
+						lst[j] = lst[i]
+						cached.update({combine_strings : lst[i]})
+						print("stored in cache")
+
+					elif change == '2':
[…]

### 2015-10-06 analysis/e9_altsAnalysis.Rmd
alts analysis in R, just reading in data and superficial look at alt sets

@@
 ```{r}
+rm(list = ls())
 #library(rjson)
-rm(list = ls())
 library(jsonlite)
+fp = "~/Desktop/Projects/scalar_implicature/analysis/"
 setwd("~/Desktop/Projects/scalar_implicature/")
@@
 
+**Analysis of alternative gathering experiment**
+
+Data cleaning in alts_analysis.py
+
+Explore
+--------
 ```{r}
-d0 = fromJSON(file="alts.json")
-names(d0)
-scalar_data = c()
-for (scalar in names(d0)) {
-  for(word in d[[scalar]]) {
-    scalar = c(scalar, word)
-    print(scalar)
-  }
-  scalar_data = rbind(scalar_data, scalar)
-}
-scalar_data
-```
+d1 = fromJSON("analysis/edited_alts.json", simplifyDataFrame=T)
+d1 = as.data.frame(d1)
 
-```{r}
-d1 = fromJSON("alts.json", simplifyDataFrame=T)
-d1 = as.data.frame(d1)
-# conver to lower case
-sapply(seq(1, ncol(d1)), FUN=function(i) {
-  d1[,i] = tolower(d1[,i])
-})
+length(sort(table(d1$all)))
+length(sort(table(d1$some)))
 
-sort(table(d1$all))
-sort(table(d1$some))
-sort(table(d1$unforgettable))
-sort(table(d1$memorable))
-sort(table(d1$excellent))
-sort(table(d1$good))
-sort(table(d1$loved))
-sort(table(d1$liked))
-sort(table(d1$delicious))
-sort(table(d1$palatable))
+length(sort(table(d1$unforgettable)))
+length(sort(table(d1$memorable)))
+
+length(sort(table(d1$excellent)))
+length(sort(table(d1$good)))
+
+length(sort(table(d1$loved)))
+length(sort(table(d1$liked)))
+
+length(sort(table(d1$delicious)))
+length(sort(table(d1$palatable)))
 

### 2015-10-07 analysis/e9_altsAnalysis.Rmd
Mike changes to working withe alts data - using tidyr and a dataframe

@@
 d1 = fromJSON("analysis/edited_alts.json", simplifyDataFrame=T)
-d1 = as.data.frame(d1)
+d1 = as.data.frame(d1, stringsAsFactors = FALSE)
+```
 
+```{r}
+library(tidyr)
+library(dplyr)
+d <- d1 %>% 
+  select(-high, -low) %>%
+  gather(base, alt, 
+         palatable, liked, good, loved, some, all, 
+         delicious, excellent, memorable, unforgettable) %>%
+  mutate(base = as.character(base)) %>%
+  rowwise %>%
+  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
+                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
+                               ifelse(base == "liked" | base == "loved", "liked_loved",
+                                      ifelse(base == "good" | base == "excellent", 
+                                             "good_excellent", "memorable_unforgettable"))))) %>%
+  group_by(scale, alt) %>%
+  summarise(n = n()) %>%
+  filter(n >= 10)
+```
+
+```{r}
+sort(table(d1$all))
+sort(table(d1$some))
 length(sort(table(d1$all)))
@@
 
+mem_un <- sort(table(c(as.character(d1$unforgettable), 
+             as.character(d1$memorable))))
+mem_un[mem_un > 4]
+
+some_all <- sort(table(c(as.character(d1$some), 
+             as.character(d1$all))))
+some_all[some_all > 4]
+
+ex_good <- sort(table(c(as.character(d1$excellent), 
+             as.character(d1$good))))
+ex_good[ex_good > 4]
+
+sort(table(d1$unforgettable))
+sort(table(d1$memorable))
 length(sort(table(d1$unforgettable)))
@@
 
+sort(table(d1$excellent))
+sort(table(d1$good))
 length(sort(table(d1$excellent)))
@@
 
+sort(table(d1$loved))
+sort(table(d1$liked))
 length(sort(table(d1$loved)))
@@
 
+sort(table(d1$delicious))
+sort(table(d1$palatable))
 length(sort(table(d1$delicious)))

### 2015-10-13 implicatures_e10.js
Initial copies of binary var literal listener study (e8)

@@ -1,0 +1,230 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+var sents = {
+    scale: {
+		training1: {
+			//because training trial hi and low are the same
+		    hi:  "thought the food deserved a <b>high</b> rating?",
+		    low:  "thought the food deserved a <b>low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi:  "<b>loved</b> the food?",
+		    low:  "<b>liked</b> the food?"
+		},
+		good_excellent: {
+			hi:  "thought the food was <b>excellent</b>?",
+		    low:  "thought the food was <b>good</b>?"
+		},
+		palatable_delicious: {
+			hi:  "thought the food was <b>delicious</b>?",
+		    low:  "thought the food was <b>palatable</b>?"
+		},
+	memorable_unforgettable: {
+			hi:  "thought the food was <b>unforgettable</b>?",
+		    low:  "thought the food was <b>memorable</b>?"
+		},
+		some_all: {
[…]

### 2015-10-13 implicatures_e10.js
first modification to e8 experiment code. Looks like things are working after first run through

@@ -42,46 +42,52 @@ function shuffle (a) {
 var sents = {
     scale: {
 		training1: {
-			//because training trial hi and low are the same
-		    hi:  "thought the food deserved a <b>high</b> rating?",
-		    low:  "thought the food deserved a <b>low</b> rating?"
+		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating?",
+		    low1:  "thought the food deserved a <b>low</b> rating?",
+		    //low2:  "thought the food deserved a <b>very low</b> rating?"
 		},
 		liked_loved: {		   
-		    hi:  "<b>loved</b> the food?",
-		    low:  "<b>liked</b> the food?"
+		    hi1:  "<b>loved</b> the food?",
+		    hi2:  "<b>liked</b> the food?",
+		    low1:  "<b>disliked</b> the food?",
+		    low2:  "<b>hated</b> the food?",
 		},
 		good_excellent: {
-			hi:  "thought the food was <b>excellent</b>?",
-		    low:  "thought the food was <b>good</b>?"
+			hi1:  "thought the food was <b>excellent</b>?",
+		    hi2:  "thought the food was <b>good</b>?",
+		    low1:  "thought the food was <b>bad</b>?",
+		    low2:  "thought the food was <b>terrible</b>?"
 		},
 		palatable_delicious: {
-			hi:  "thought the food was <b>delicious</b>?",
-		    low:  "thought the food was <b>palatable</b>?"
+			hi1:  "thought the food was <b>delicious</b>?",
+		    hi2:  "thought the food was <b>palatable</b>?",
+		    low1:  "thought the food was <b>gross</b>?",
+		    low2:  "thought the food was <b>disgusting</b>?"
 		},
 	memorable_unforgettable: {
-			hi:  "thought the food was <b>unforgettable</b>?",
-		    low:  "thought the food was <b>memorable</b>?"
+			hi1:  "thought the food was <b>unforgettable</b>?",
+		    hi2:  "thought the food was <b>memorable</b>?",
+		    low1:  "thought the food was <b>bland</b>?",
+		    low2:  "thought the food was <b>forgettable</b>?"
 		},
 		some_all: {
-			hi: "enjoyed <b>all</b> of the food they ate?",
-			low: "enjoyed <b>some</b> of the food they ate?"
+			hi1: "enjoyed <b>all</b> of the food they ate?",
+			hi2: "enjoyed <b>most</b> of the food they ate?",
[…]

### 2015-10-13 implicatures_e11.js
cp of e6 pragmatic listner with full alternative scales (same as e10 -> alts taken from e9)

@@ -1,0 +1,212 @@
+//############################## Helper functions #############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+var sents = {
+    scale: {
+		training1: {
+		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating?",
+		    low1:  "thought the food deserved a <b>low</b> rating?",
+		    //low2:  "thought the food deserved a <b>very low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi1:  "<b>loved</b> the food?",
+		    hi2:  "<b>liked</b> the food?",
+		    low1:  "<b>disliked</b> the food?",
+		    low2:  "<b>hated</b> the food?",
+		},
+		good_excellent: {
+			hi1:  "thought the food was <b>excellent</b>?",
+		    hi2:  "thought the food was <b>good</b>?",
+		    low1:  "thought the food was <b>bad</b>?",
+		    low2:  "thought the food was <b>terrible</b>?"
+		},
+		palatable_delicious: {
[…]

### 2015-10-13 implicatures_e11.js
fixed training trial bug, appears to be working smoothly

@@ -42,39 +42,39 @@ var sents = {
     scale: {
 		training1: {
 		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
-		    hi2:  "thought the food deserved a <b>high</b> rating?",
-		    low1:  "thought the food deserved a <b>low</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating.",
+		    low1:  "thought the food deserved a <b>low</b> rating.",
 		    //low2:  "thought the food deserved a <b>very low</b> rating?"
 		},
 		liked_loved: {		   
-		    hi1:  "<b>loved</b> the food?",
-		    hi2:  "<b>liked</b> the food?",
-		    low1:  "<b>disliked</b> the food?",
-		    low2:  "<b>hated</b> the food?",
+		    hi1:  "<b>loved</b> the food.",
+		    hi2:  "<b>liked</b> the food.",
+		    low1:  "<b>disliked</b> the food.",
+		    low2:  "<b>hated</b> the food.",
 		},
 		good_excellent: {
-			hi1:  "thought the food was <b>excellent</b>?",
-		    hi2:  "thought the food was <b>good</b>?",
-		    low1:  "thought the food was <b>bad</b>?",
-		    low2:  "thought the food was <b>terrible</b>?"
+			hi1:  "thought the food was <b>excellent</b>.",
+		    hi2:  "thought the food was <b>good</b>.",
+		    low1:  "thought the food was <b>bad</b>.",
+		    low2:  "thought the food was <b>terrible</b>."
 		},
 		palatable_delicious: {
-			hi1:  "thought the food was <b>delicious</b>?",
-		    hi2:  "thought the food was <b>palatable</b>?",
-		    low1:  "thought the food was <b>gross</b>?",
-		    low2:  "thought the food was <b>disgusting</b>?"
+			hi1:  "thought the food was <b>delicious</b>.",
+		    hi2:  "thought the food was <b>palatable</b>.",
+		    low1:  "thought the food was <b>gross</b>.",
+		    low2:  "thought the food was <b>disgusting</b>."
 		},
 	memorable_unforgettable: {
-			hi1:  "thought the food was <b>unforgettable</b>?",
-		    hi2:  "thought the food was <b>memorable</b>?",
-		    low1:  "thought the food was <b>bland</b>?",
-		    low2:  "thought the food was <b>forgettable</b>?"
+			hi1:  "thought the food was <b>unforgettable</b>.",
+		    hi2:  "thought the food was <b>memorable</b>.",
[…]

### 2015-10-13 analysis/e9_altsAnalysis.Rmd
organize data into top ten alterntives by scalar pairs

--- 2015-10-06 analysis/e9_altsAnalysis.Rmd
@@
 
-Data cleaning in alts_analysis.py
+Note: Data cleaning in alts_analysis.py
 
@@
 d1 = fromJSON("analysis/edited_alts.json", simplifyDataFrame=T)
-d1 = as.data.frame(d1)
+d1 = as.data.frame(d1, stringsAsFactors = FALSE)
+```
 
-length(sort(table(d1$all)))
-length(sort(table(d1$some)))
+```{r}
+library(tidyr)
+library(dplyr)
+d <- d1 %>% 
+  select(-high, -low) %>%
+  gather(base, alt, 
+         palatable, liked, good, loved, some, all, 
+         delicious, excellent, memorable, unforgettable) %>%
+  mutate(base = as.character(base)) %>%
+  rowwise %>%
+  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
+                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
+                               ifelse(base == "liked" | base == "loved", "liked_loved",
+                                      ifelse(base == "good" | base == "excellent", 
+                                             "good_excellent", "memorable_unforgettable"))))) %>%
+  group_by(scale, alt) %>%
+  summarise(n = n())
 
-length(sort(table(d1$unforgettable)))
-length(sort(table(d1$memorable)))
+d.topTen = d %>%
+  filter(n >= 10)
+```
 
-length(sort(table(d1$excellent)))
-length(sort(table(d1$good)))
-
-length(sort(table(d1$loved)))
-length(sort(table(d1$liked)))
-
-length(sort(table(d1$delicious)))
-length(sort(table(d1$palatable)))
-
+**Output to text file for reference:**
+```{r}
+d.topTen =  d.topTen[order(d.topTen$scale, -d.topTen$n),]
+write.table(d.topTen, "analysis/top_alts_output.txt")
 ```

### 2015-10-13 implicatures_e10.js
Checking data collection, appears to be working

@@ -192,8 +192,6 @@ var experiment = {
 		    	manipulation_level = manipulation[current_trial % 5];
 		    }
 			sent_materials = sents.scale[current_scale][degree];
-			console.log("current_scale", current_scale)
-			console.log("degree", degree)
 		    //Trial params ---------------------------->
 
 

### 2015-10-15 implicatures_e10.js
minor change, don't actually know what it was...

@@ -44,7 +44,7 @@ var sents = {
 		training1: {
 		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
 		    hi2:  "thought the food deserved a <b>high</b> rating?",
-		    low1:  "thought the food deserved a <b>low</b> rating?",
+		    low1:  "thought the food deserved a <b>low</b> rating?"
 		    //low2:  "thought the food deserved a <b>very low</b> rating?"
 		},
 		liked_loved: {		   

### 2015-10-16 analysis/e10_analysis.Rmd
e10 analysis using e8 framework

---
output: pdf_document
---
PSYCH 130 - EXPERIMENT 4 ANALYSIS
=================================

Workspace
---------
```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
```

Data prep
---------
```{r}
files <- dir("production-results/e10/", pattern = "*.json")
#files <- dir("sandbox-results/", pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste("production-results/e10/",f,sep="")
  #jf <- paste("sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language)
  d.raw <- bind_rows(d.raw, id)
}

# Number of participants
length(unique(d.raw$workerid))
```

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
d <- d.raw %>% filter(scale != "training1")
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
```

Main analysis below
-------------------
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")

ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment)) 
# write to csv for model
#write.csv(ms, "models/e10.csv", row.names=FALSE)
```

Histogram Plots for our scalars
-------------------------------
```{r}
scalar.agreements = function(scalar_pair, degree) {
  pair = dt[which(dt$scale == scalar_pair), ]
  scalar = pair[which(pair$degree == degree), ]
  scalar = spread(scalar, stars, judgment)
  # plots
  par(mfrow = c(2,3))
  wrd = unlist(strsplit(scalar_pair, "_"))
  wrd = ifelse(degree == "low", wrd[1], wrd[2])
  likert.plots(scalar, wrd)
}
likert.plots = function(scalar, wrd) {
  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
           xlab="Agree", ylab="Counts")
}

# plotting all scalars --> for pdf print out, not working
for (i in scalars) {
  for (j in dgrs) {
    scalar.agreements(i, j)
  }
}

# call to plot single scalar
scalar.agreements("palatable_delicious", "hi")

lm.overall = lm(judgment~stars + degree + scale, data=dt)
summary(lm.fit)
cor(dt$judgment, dt$stars)

# Overall matching
par(mfrow=c(1,1))
plot(jitter(dt$stars), jitter(dt$judgment),
     main = "Matching between stars and judgments", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt), col="green")

# Low and High matching
low.obs = which(dt$degree == "low")
hi.obs = -low.obs
par(mfrow=c(1,2))
plot(jitter(dt[low.obs, ]$stars), jitter(dt[low.obs, ]$judgment),
     main = "Low Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[low.obs,]), col="red")

plot(jitter(dt[hi.obs, ]$stars), jitter(dt[hi.obs, ]$judgment),
     main = "High Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[hi.obs,]), col="blue")
```

Matching in data
----------------
```{r}
match = dt$stars == dt$judgment
par(mfrow=c(1,1))
barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
dm = data.frame(dt, match)

# Matches by stars
table(select(dm, stars, match))

# Matches by stars & degrees
table(select(dm, stars, match, degree))
table(select(dm, stars, match, degree))
```

# Rolling [1,2] [4,5]
---------------------
```{r}
ds = d[, -6] %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))

compatibility = function(scalar_pair, degree) {
  dr = ds[which(ds$scale == scalar_pair & ds$degree == degree),] %>%
    select(stars, speaker.hi)
  return(dr$speaker.hi / sum(dr$speaker.hi))
}
plot.pairs = function(scalar_pair) {
  plot(compatibility(scalar_pair, "hi"), type="b", col="red",
       main=toString(scalar_pair), ylab="% Agree Norm", xlab="Stars",
       xlim = c(1,5), ylim = c(0,1))
  lines(compatibility(scalar_pair, "low"), type="b", col="blue")  
}
compatibility("good_excellent", "hi")
par(mfrow=c(1,1))
plot.pairs("good_excellent")
par(mfrow=c(2,3))
for (i in 1:length(scalars)) {
  plot.pairs(scalars[i])  
}
```

### 2015-10-17 analysis/e10_analysis.Rmd
e10 basic analysis with plots

@@
 ---
-PSYCH 130 - EXPERIMENT 4 ANALYSIS
-=================================
 
-Workspace
----------
 ```{r}
@@
 library("rjson")
+
+# commentary on weird RMarkdown bug
+# https://github.com/hadley/xml2/issues/34
 ```
@@
 files <- dir("production-results/e10/", pattern = "*.json")
-#files <- dir("sandbox-results/", pattern = "*.json")
 d.raw <- data.frame()
@@
   jf <- paste("production-results/e10/",f,sep="")
-  #jf <- paste("sandbox-results/",f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))
@@
 -------------------
+
+Let's remove training runs
 ```{r}
@@
 d = d.raw %>% filter(scale != "training1")
+```
 
+Populate a new df
+```{r}
 ms <- d %>%
@@
             speaker.p = mean(judgment)) 
-# write to csv for model
-#write.csv(ms, "models/e10.csv", row.names=FALSE)
 ```
 
-Histogram Plots for our scalars
--------------------------------
+Plot our literal listener semantic (counts data)
 ```{r}
-scalar.agreements = function(scalar_pair, degree) {
-  pair = dt[which(dt$scale == scalar_pair), ]
-  scalar = pair[which(pair$degree == degree), ]
-  scalar = spread(scalar, stars, judgment)
-  # plots
-  par(mfrow = c(2,3))
-  wrd = unlist(strsplit(scalar_pair, "_"))
-  wrd = ifelse(degree == "low", wrd[1], wrd[2])
-  likert.plots(scalar, wrd)
-}
-likert.plots = function(scalar, wrd) {
-  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
-           xlab="Agree", ylab="Counts")
-  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
-           xlab="Agree", ylab="Counts")
-  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
-           xlab="Agree", ylab="Counts")
-  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
-           xlab="Agree", ylab="Counts")
-  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
-           xlab="Agree", ylab="Counts")
-}
+pdf("plots/e10_L0Counts.pdf", width=8, height = 5)
+qplot(x = stars, y = cnt.judgment, col = degree,
+      geom = "line", stat = "identity", 
+      position = "dodge", 
+      data = ms) + 
+  geom_linerange(aes(ymin = cnt.judgment - cil, 
+                     ymax = cnt.judgment + cih)) + 
+  facet_wrap(~scale) +
+  ggtitle("Literal listener counts")
+dev.off()
 
-# plotting all scalars --> for pdf print out, not working
-for (i in scalars) {
-  for (j in dgrs) {
-    scalar.agreements(i, j)
-  }
-}
-
-# call to plot single scalar
-scalar.agreements("palatable_delicious", "hi")
-
-lm.overall = lm(judgment~stars + degree + scale, data=dt)
-summary(lm.fit)
-cor(dt$judgment, dt$stars)
-
-# Overall matching
-par(mfrow=c(1,1))
-plot(jitter(dt$stars), jitter(dt$judgment),
-     main = "Matching between stars and judgments", xlab = "Judgment", ylab = "Stars")
-abline(lm(judgment~stars, data=dt), col="green")
-
-# Low and High matching
-low.obs = which(dt$degree == "low")
-hi.obs = -low.obs
-par(mfrow=c(1,2))
-plot(jitter(dt[low.obs, ]$stars), jitter(dt[low.obs, ]$judgment),
-     main = "Low Degree", xlab = "Judgment", ylab = "Stars")
-abline(lm(judgment~stars, data=dt[low.obs,]), col="red")
-
-plot(jitter(dt[hi.obs, ]$stars), jitter(dt[hi.obs, ]$judgment),
-     main = "High Degree", xlab = "Judgment", ylab = "Stars")
-abline(lm(judgment~stars, data=dt[hi.obs,]), col="blue")
+pdf("plots/e10_L0Percent.pdf", width=8, height = 5)
+qplot(x = stars, y = speaker.p, col = degree,
+      geom = "line", stat = "identity", 
+      position = "dodge", 
+      data = ms) + 
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih)) + 
+  facet_wrap(~scale) +
+  ggtitle("Literal listener percent 'yes'")
+dev.off()
 ```
 
-Matching in data
-----------------
 ```{r}
-match = dt$stars == dt$judgment
-par(mfrow=c(1,1))
-barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
-dm = data.frame(dt, match)
+# prop.calc = function(scalar, degree, stars, df) {
+#   total = sum(df[(df$scale == scalar) & (df$degree == degree), "cnt.judgment"])
+#   prop = df[(df$scale == scalar) & (df$degree == degree) & (df$stars = stars), "cnt.judgment"]
+#   return(prop / total)
+# }
+# scales = rep("some_all", 5)
+# stars = seq(1:5)
+# degree = rep("hi1", 5)
+# cnt.judgment = c(0, 0, 0, 2, 28)
+# 
+# df = data.frame(scales, stars, degree, cnt.judgment)
+# prop.calc("some_all", "hi1", 1, df)
+# 
+# ms$judgment.prop = ms$judgment
+# # write to csv for model
+# #write.csv(ms, "models/e10.csv", row.names=FALSE)
 
-# Matches by stars
-table(select(dm, stars, match))
-
-# Matches by stars & degrees
-table(select(dm, stars, match, degree))
-table(select(dm, stars, match, degree))
 ```
-
-# Rolling [1,2] [4,5]
----------------------
-```{r}
-ds = d[, -6] %>%
-  group_by(scale, degree, stars) %>%
-  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
-            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
-            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))
-
-compatibility = function(scalar_pair, degree) {
-  dr = ds[which(ds$scale == scalar_pair & ds$degree == degree),] %>%
-    select(stars, speaker.hi)
-  return(dr$speaker.hi / sum(dr$speaker.hi))
-}
-plot.pairs = function(scalar_pair) {
-  plot(compatibility(scalar_pair, "hi"), type="b", col="red",
-       main=toString(scalar_pair), ylab="% Agree Norm", xlab="Stars",
-       xlim = c(1,5), ylim = c(0,1))
-  lines(compatibility(scalar_pair, "low"), type="b", col="blue")  
-}
-compatibility("good_excellent", "hi")
-par(mfrow=c(1,1))
-plot.pairs("good_excellent")
-par(mfrow=c(2,3))
-for (i in 1:length(scalars)) {
-  plot.pairs(scalars[i])  
-}
-```

### 2015-10-17 analysis/e11_analysis.Rmd
adding copy of e10 analysis for e11

--- 2015-10-17 analysis/e10_analysis.Rmd
@@
 
+Experiment e11 - Pragmatic Listener experiment with alternatives
 ```{r}
@@
 ```{r}
-files <- dir("production-results/e10/", pattern = "*.json")
+
+# make sure to set directory path to 'production-results/e11/'
+results_path = "sandbox-results/e11/"
+files <- dir(results_path, pattern = "*.json")
 d.raw <- data.frame()
@@
 for (f in files) {
-  jf <- paste("production-results/e10/",f,sep="")
+  jf <- paste(results_path,f,sep="")
   jd <- fromJSON(paste(readLines(jf), collapse=""))

### 2015-10-17 alts_analysis.py
test - just adding alts_analysis

@@ -7,7 +7,7 @@ from nltk import metrics
 path = "production-results/e9/"
 
 # fill this in with functionality we want to run
-toDo = "read_data edit_data output_editedData"
+toDo = "read_data edit_data"
 
 #################################################################################
 #################################################################################
@@ -166,7 +166,7 @@ if "output_editedData" in toDo:
 	print "edited data output..."
 
 	with open('analysis/edited_alts.json', 'w') as fp:
-		json.dump(scalar_data, fp)
+		json.dump(data_edited, fp)
 
 #################################################################################
 #################################################################################

### 2015-10-17 analysis/e11_analysis.Rmd
basic plot for prag listener judgments - need to implement output to .csv for RSA model

@@
 library("rjson")
-
 # commentary on weird RMarkdown bug
@@
 # make sure to set directory path to 'production-results/e11/'
-results_path = "sandbox-results/e11/"
+results_path = "production-results/e11/"
 files <- dir(results_path, pattern = "*.json")
@@
   id <- data.frame(workerid = jd$WorkerId, 
-                   scale = jd$answers$data$scale,
-                   degree = jd$answers$data$degree,
-                   stars = jd$answers$data$manipulation_level,
-                   judgment = as.numeric(jd$answers$data$judgment),
-                   language = jd$answers$data$language)
+                   scale = jd$answer$data$scale,
+                   degree = jd$answer$data$degree,
+                   stars = as.numeric(jd$answer$data$judgment),
+                   language = jd$answer$data$language,
+                   gender = jd$answers$data$gender,
+                   age = jd$answers$data$age)
   d.raw <- bind_rows(d.raw, id)
@@
 ```{r}
-d.raw = d.raw[c(-1, -2), ]       # remove first two rows
-d = d.raw %>% filter(scale != "training1")
+#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
+#d = d.raw %>% filter(scale != "training1")
 ```
@@
 ```{r}
-ms <- d %>%
-  mutate(stars = as.numeric(as.character(stars))/20) %>%
-  group_by(scale, degree, stars) %>%
-  summarise(cil = ci.low(judgment), 
-            cih = ci.high(judgment), 
-            cnt.judgment = sum(judgment),
-            speaker.p = mean(judgment)) 
+density <- d %>%
+  group_by(degree, scale) %>%
+  mutate(n = n()) %>%
+  group_by(degree, scale, stars) %>%
+  summarise(prop = n() / n[1])
 ```
 
-Plot our literal listener semantic (counts data)
+Plot our pragmatic listener judgments
 ```{r}
-pdf("plots/e10_L0Counts.pdf", width=8, height = 5)
-qplot(x = stars, y = cnt.judgment, col = degree,
-      geom = "line", stat = "identity", 
-      position = "dodge", 
-      data = ms) + 
-  geom_linerange(aes(ymin = cnt.judgment - cil, 
-                     ymax = cnt.judgment + cih)) + 
-  facet_wrap(~scale) +
-  ggtitle("Literal listener counts")
-dev.off()
-
-pdf("plots/e10_L0Percent.pdf", width=8, height = 5)
-qplot(x = stars, y = speaker.p, col = degree,
-      geom = "line", stat = "identity", 
-      position = "dodge", 
-      data = ms) + 
-  geom_linerange(aes(ymin = speaker.p - cil, 
-                     ymax = speaker.p + cih)) + 
-  facet_wrap(~scale) +
-  ggtitle("Literal listener percent 'yes'")
+write.csv(density, "models/e11.csv", row.names=FALSE)
+pdf("plots/e11.pdf", width = 8, height = 4)
+qplot(stars, prop, facets = degree ~ scale, 
+      geom="bar", stat = "identity",
+      binwidth = 1, data=density)
 dev.off()

### 2015-10-20 analysis/e11_analysis.Rmd
checking for compliance of training trials - appears we had 100% compliance on e11

@@
 ```{r}
-
 rm(list=ls())
@@
 library("rjson")
+library(ggplot2)
 # commentary on weird RMarkdown bug
@@
 ```{r}
+# Make sure people answered training trials correctly
+compliant <- d.raw %>% 
+   filter(grepl("training", scale)) %>%
+   group_by(workerid) %>%
+   summarise(compliant = stars[scale == "training1" & degree == "hi2"] > 3 & 
+               stars[scale == "training1" & degree == "low1"] < 3)
+
+d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1", 
+         scale != "training2", 
+         compliant == TRUE)
+
+# remove training runs
 d <- d.raw %>% filter(scale != "training1")
-# compliant <- d.raw %>% 
-#   filter(grepl("training", scale)) %>%
-#   group_by(workerid) %>%
-#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
-#               judgment[scale == "training1" & degree == "low"] < 3)
-#   
-# d <- d.raw %>% 
-#   left_join(compliant) %>%
-#   filter(grepl(pattern = "english", 
-#                language, ignore.case = TRUE), 
-#          domain != "training1", 
-#          domain != "training2", 
-#          compliant == TRUE)
+head(d)
 ```
@@
 -------------------
-
-Let's remove training runs
-```{r}
-#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
-#d = d.raw %>% filter(scale != "training1")
-```
 
@@
   group_by(degree, scale, stars) %>%
-  summarise(prop = n() / n[1])
+  summarise(listener.p = n() / n[1])
 ```
@@
 write.csv(density, "models/e11.csv", row.names=FALSE)
+```
+
+```{r}
 pdf("plots/e11.pdf", width = 8, height = 4)
-qplot(stars, prop, facets = degree ~ scale, 
+qplot(stars, listener.p, facets = degree ~ scale, 
       geom="bar", stat = "identity",
@@
 ```
-
-```{r}
-# prop.calc = function(scalar, degree, stars, df) {
-#   total = sum(df[(df$scale == scalar) & (df$degree == degree), "cnt.judgment"])
-#   prop = df[(df$scale == scalar) & (df$degree == degree) & (df$stars = stars), "cnt.judgment"]
-#   return(prop / total)
-# }
-# scales = rep("some_all", 5)
-# stars = seq(1:5)
-# degree = rep("hi1", 5)
-# cnt.judgment = c(0, 0, 0, 2, 28)
-# 
-# df = data.frame(scales, stars, degree, cnt.judgment)
-# prop.calc("some_all", "hi1", 1, df)
-# 
-# ms$judgment.prop = ms$judgment
-# # write to csv for model
-# #write.csv(ms, "models/e10.csv", row.names=FALSE)
-
-```

### 2015-10-20 models/RSA_Model2.Rmd
update for running with e8 l0 listener and e6 prag listener :

@@
 library(rjson)
+library(dplyr)
+library(tidyr)
 
 opts_chunk$set(cache=TRUE)
-
+setwd("~/Desktop/Projects/scalar_implicature/")
 source("analysis/useful_dplyr.R")
@@
   if (usenone) {
-    mat$none <- c(0.8, 0.2, 0, 0, 0)
+    mat$none <- c(1, 0, 0, 0, 0)
+    #mat$meh <- c(0.0, 0.2, 0.6, 0.2, 0)
     #mat$bad <- c(.5, .9, .4, .1, 0)
@@
 ```{r}
+alpha = 1
 md <- data %>%
-  do(run.rsa(., alpha = 1, useprior = T, usenone = T))
+  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
 ```
@@
 qplot(stars, listener.p, col=degree, 
-      data=md, main="Model vs Human judgments\nSemantics measured empirically",
+      data=md,
+      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
+                 alpha),
       ylab="Posteriors p( rating | word )") + 

### 2015-10-26 models/RSA_Model2.Rmd
adjustments for Symsys 290 preso 10.26.15

@@
 ```{r}
-alpha = 1
+alpha = 4
 md <- data %>%
@@
                  alpha),
-      ylab="Posteriors p( rating | word )") + 
+      ylab="Posterior p(rating | word)") + 
   facet_wrap(~scale) + 
@@
     geom_smooth(method=lm) +
-  ggtitle("Model performance\nCorpus based") +
+  ggtitle("Model performance: Baseline") +
   labs(x = "model prediction", y="human judgments")
-cor(md$pred, md$listener.p)
-
+cor(md$pred, md$listener.p)^2
+cor.test(md$pred, md$listener.p)
 # scalar level cor
@@
 ```
+
+For Presentation to Symsys290 10.26.15
+```{r}
+qplot(stars, listener.p, col=degree, 
+      data=md[md$scale=="some_all",],
+      main=paste("Model vs Human judgments\nalpha=",
+                 alpha),
+      ylab="Posterior p(m | u)") +
+  geom_line(aes(y = pred), lty = 4)
+```

### 2015-10-28 models/RSA_Model2.Rmd
minor tweaks for symsys preso 10.26.15

@@
 ```{r}
-alpha = 4
+alpha = 5
 md <- data %>%
-  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
+  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
 ```
@@
   md <- data %>%
-    do(run.rsa(., alpha = n, useprior = F, usenone = T))
+    do(run.rsa(., alpha = n, useprior = F, usenone = F))
 

### 2015-10-30 experiments/implicatures_e10.js
moving all .html and .js in experiments directory

@@ -1,0 +1,240 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+var sents = {
+    scale: {
+		training1: {
+		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating?",
+		    low1:  "thought the food deserved a <b>low</b> rating?"
+		    //low2:  "thought the food deserved a <b>very low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi1:  "<b>loved</b> the food?",
+		    hi2:  "<b>liked</b> the food?",
+		    low1:  "<b>disliked</b> the food?",
+		    low2:  "<b>hated</b> the food?",
+		},
+		good_excellent: {
+			hi1:  "thought the food was <b>excellent</b>?",
+		    hi2:  "thought the food was <b>good</b>?",
+		    low1:  "thought the food was <b>bad</b>?",
+		    low2:  "thought the food was <b>terrible</b>?"
+		},
[…]

### 2015-10-30 experiments/implicatures_e11.js

@@ -1,0 +1,228 @@
+//############################## Helper functions #############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+var sents = {
+    scale: {
+		training1: {
+		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating.",
+		    low1:  "thought the food deserved a <b>low</b> rating.",
+		    //low2:  "thought the food deserved a <b>very low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi1:  "<b>loved</b> the food.",
+		    hi2:  "<b>liked</b> the food.",
+		    low1:  "<b>disliked</b> the food.",
+		    low2:  "<b>hated</b> the food.",
+		},
+		good_excellent: {
+			hi1:  "thought the food was <b>excellent</b>.",
+		    hi2:  "thought the food was <b>good</b>.",
+		    low1:  "thought the food was <b>bad</b>.",
+		    low2:  "thought the food was <b>terrible</b>."
+		},
+		palatable_delicious: {
[…]

### 2015-10-30 experiments/implicatures_e2.js

@@ -1,0 +1,325 @@
+// ############################## Helper functions ##############################
+
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+  // Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) 
+{ 
+    var o = [];
+    
+    for (var i=0; i < a.length; i++) {
+	o[i] = a[i];
+    }
+    
+    for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+    return o;
+}
+
+// substitution function - do we want to save all these factors to a data object?
+//Pass a trial object in to be populated?
+function doSentSubs (sents, scale, domain)
+{
+
+    inference = sents["scales"][scale]["sent_inference"];
+    question = sents["scales"][scale]["sent_question"];
+
+    SP = sents["domains"][domain]["SP"]; //Plural
+    SS = sents["domains"][domain]["SS"]; //Singular
+    P1 = sents["domains"][domain]["P1"]; //Predicate 1
+    P2 = sents["domains"][domain]["P2"]; //Predicate 2
+    V1 = sents["domains"][domain]["V1"]; //Past
+    V2 = sents["domains"][domain]["V2"]; //Present
+
+    inference = inference.replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
+
[…]

### 2015-10-30 experiments/implicatures_e3.js

@@ -1,0 +1,361 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+// substitution function - do we want to save all these factors to a data object?
+//Pass a trial object in to be populated?
+function doSentSubs (sents, scale, domain) {
+	//TODO: work with this function
+
+    inference = sents["scales"][scale]["sent_inference"];
+    question = sents["scales"][scale]["sent_question"];
+    //manipulation = sents["domains"][domain][manip];
+    //manipulation = sents["scales"][scale]["sent_manipulation"];
+
+    SP = sents["domains"][domain]["SP"]; //Plural
+    SS = sents["domains"][domain]["SS"]; //Singular
+    P1 = sents["domains"][domain]["P1"]; //Predicate 1
+    P2 = sents["domains"][domain]["P2"]; //Predicate 2
+    V1 = sents["domains"][domain]["V1"]; //Past
+    V2 = sents["domains"][domain]["V2"]; //Present
+
[…]

### 2015-10-30 experiments/implicatures_e4.js

@@ -1,0 +1,310 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+// substitution function - do we want to save all these factors to a data object?
+//Pass a trial object in to be populated?
+function doSentSubs (sents, scale, domain) {
+	//TODO: work with this function
+
+    inference = sents["scales"][scale]["sent_inference"];
+    question = sents["scales"][scale]["sent_question"];
+    //manipulation = sents["domains"][domain][manip];
+    //manipulation = sents["scales"][scale]["sent_manipulation"];
+
+    SP = sents["domains"][domain]["SP"]; //Plural
+    SS = sents["domains"][domain]["SS"]; //Singular
+    P1 = sents["domains"][domain]["P1"]; //Predicate 1
+    P2 = sents["domains"][domain]["P2"]; //Predicate 2
+    V1 = sents["domains"][domain]["V1"]; //Past
+    V2 = sents["domains"][domain]["V2"]; //Present
+
[…]

### 2015-10-30 experiments/implicatures_e5.js

@@ -1,0 +1,216 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+var sents = {
+    scale: {
+		training1: {
+			//because training trial hi and low are the same
+		    hi:  "thought the food deserved a <b>high</b> rating?",
+		    low:  "thought the food deserved a <b>low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi:  "<b>loved</b> the food?",
+		    low:  "<b>liked</b> the food?"
+		},
+		good_excellent: {
+			hi:  "thought the food was <b>excellent</b>?",
+		    low:  "thought the food was <b>good</b>?"
+		},
+		palatable_delicious: {
+			hi:  "thought the food was <b>delicious</b>?",
+		    low:  "thought the food was <b>palatable</b>?"
+		},
+	memorable_unforgettable: {
+			hi:  "thought the food was <b>unforgettable</b>?",
+		    low:  "thought the food was <b>memorable</b>?"
+		},
+		some_all: {
[…]

### 2015-10-30 experiments/implicatures_e6.js

@@ -1,0 +1,200 @@
+//############################## Helper functions #############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+var sents = {
+    scale: {
+		training1: {
+		    hi:  "thought the food deserved a <b>high</b> rating.",
+		    low:  "thought the food deserved a <b>low</b> rating"
+		},
+		liked_loved: {		   
+		    hi:  "<b>loved</b> the food.",
+		    low:  "<b>liked</b> the food."
+		},
+		good_excellent: {
+			hi:  "thought the food was <b>excellent</b>.",
+		    low:  "thought the food was <b>good</b>."
+		},
+		palatable_delicious: {
+			hi:  "thought the food was <b>delicious</b>.",
+		    low:  "thought the food was <b>palatable</b>."
+		},
+		memorable_unforgettable: {
+			hi:  "thought the food was <b>unforgettable</b>.",
+		    low:  "thought the food was <b>memorable</b>."
+		},
+		some_all: {
[…]

### 2015-10-30 experiments/implicatures_e7.js

@@ -1,0 +1,231 @@
+//############################## Helper functions #############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+
+// substitution function - do we want to save all these factors to a data object?
+//Pass a trial object in to be populated?
+function doSentSubs (base_sent, x, y)
+{
+    var name = x;
+    var c = context[x][y];
+    var gender = context[x]["pro"];
+    sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender).replace("GEN", gender);
+    return sent;
+}
+
+function get_context (name, pro) {
+	return context[name][pro];
+}
+
+var base_sent = "<b>PERSON went out to a restaurant SETTING.</b> <br><br>Without knowing anything about the food GEN ate,<br>\
+how many stars do you think GEN gave the restaurant?";
+
+var context = {
+	Bob: {
+		c1: "with a friend",
+		c2: "alone",
+	        c3: "for a birthday party",
+	        c4: "on a date",
+	        c5: "with his co-workers",
[…]

### 2015-10-30 experiments/implicatures_e9.js

@@ -1,0 +1,266 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+
+
+
+
+var sents = {
+    scale: {
+		training1: {
+		    hi:  "<font color=\"blue\"><b>high</b></font>",
+		    low:  "<font color=\"blue\"><b>low</b></font>",
+		    before: " thought the food deserved a ",
+		    after: " rating."
+		},
+		liked_loved: {		   
+		    hi:  "<font color=\"blue\"><b>loved</b></font>",
+		    low:  "<font color=\"blue\"><b>liked</b></font>",
+		    before: " ",
+		    after: " the food."
+		},
+		good_excellent: {
+			hi:  "<font color=\"blue\"><b>excellent</b></font>",
+		    low:  "<font color=\"blue\"><b>good</b></font>",
+		    before: " thought the food was ",
+		    after: "."
+		},
+		palatable_delicious: {
+			hi:  "<font color=\"blue\"><b>delicious</b></font>",
[…]

### 2015-10-30 analysis/e10_analysis.Rmd
getting rid of delted files

@@
 
-Holding off on exclusions (but exclusion code here)
+Exclusions (but exclusion code here)
 ---------------------------------------------------
 ```{r}
+compliant <- d.raw %>% 
+  filter(grepl("training", scale)) %>%
+  group_by(workerid) %>%
+  summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
+              (judgment[scale == "training1" & degree == "low1"] == 1))
+
+num_uncompliant = sum(compliant$compliant == FALSE)
+num_uncompliant
+
+d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1",  
+         compliant == TRUE)
 d <- d.raw %>% filter(scale != "training1")
-# compliant <- d.raw %>% 
-#   filter(grepl("training", scale)) %>%
-#   group_by(workerid) %>%
-#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
-#               judgment[scale == "training1" & degree == "low"] < 3)
-#   
-# d <- d.raw %>% 
-#   left_join(compliant) %>%
-#   filter(grepl(pattern = "english", 
-#                language, ignore.case = TRUE), 
-#          domain != "training1", 
-#          domain != "training2", 
-#          compliant == TRUE)
+
+# new sample after filtering compliant and English
+length(unique(d$workerid))
+head(d)
 ```
@@
             speaker.p = mean(judgment)) 
+```
+
+Write to csv
+```{r}
+write.csv(ms, "models/e10.csv", row.names=FALSE)
 ```

### 2015-10-30 analysis/e5_analysis2.Rmd
getting rid of delted files

--- 2015-07-24 analysis/e5_analysis2.Rmd
@@
 
-Preliminaries.
-
+Workspace
+---------
 ```{r}
@@
 
-Read in files and consolidate to the same directory.
-
+Data prep
+---------
 ```{r}
@@
 
-Holding off on exclusions - everyone put English, and training 2 was confusing. 
+Holding off on exclusions (but exclusion code here)
+---------------------------------------------------
 ```{r}
+d <- d.raw %>% filter(scale != "training1")
 # compliant <- d.raw %>% 
@@
 #          compliant == TRUE)
-d <- d.raw %>% filter(scale != "training1")
 ```
 
-Main Analysis
--------------
+Main analysis below
+-------------------
 ```{r}
@@
 Histogram Plots for our scalars
+-------------------------------
 ```{r}
@@
 }
+
+# plotting all scalars --> for pdf print out, not working
 for (i in scalars) {
@@
 }
+
+# call to plot single scalar
+scalar.agreements("palatable_delicious", "hi")
+
+lm.overall = lm(judgment~stars + degree + scale, data=dt)
+summary(lm.fit)
+cor(dt$judgment, dt$stars)
+
+# Overall matching
+par(mfrow=c(1,1))
+plot(jitter(dt$stars), jitter(dt$judgment),
+     main = "Matching between stars and judgments", xlab = "Judgment", ylab = "Stars")
+abline(lm(judgment~stars, data=dt), col="green")
+
+# Low and High matching
+low.obs = which(dt$degree == "low")
+hi.obs = -low.obs
+par(mfrow=c(1,2))
+plot(jitter(dt[low.obs, ]$stars), jitter(dt[low.obs, ]$judgment),
+     main = "Low Degree", xlab = "Judgment", ylab = "Stars")
+abline(lm(judgment~stars, data=dt[low.obs,]), col="red")
+
+plot(jitter(dt[hi.obs, ]$stars), jitter(dt[hi.obs, ]$judgment),
+     main = "High Degree", xlab = "Judgment", ylab = "Stars")
+abline(lm(judgment~stars, data=dt[hi.obs,]), col="blue")
 ```
@@
 Matching in data
+----------------
 ```{r}
@@
 
-Rolling 1,2 4,5
+# Rolling [1,2] [4,5]
+---------------------
 ```{r}

### 2015-10-30 analysis/e9_altsAnalysis.Rmd
getting rid of delted files

@@
 
-**Output to text file for reference:**
+**Output top ten to text file for reference:**
 ```{r}

### 2015-10-30 models/Model_Playspace.Rmd
getting rid of delted files

@@
 yelp.priors = read.csv("models/yelp1_priors.csv")
-priors = yelp.priors
+priors = data.frame(stars=seq(1,5), prior.p=rep(0.2,5))
 # Possible transformations --->
@@
 # Speaker informativity ------------------------->
-speaker = read.csv("models/speaker.csv")
-speaker = read.csv("models/speaker_normed.csv") # for printing out semantic distr's
-speaker = read.csv("models/yelp1.csv")
+speaker = read.csv("models/e8.csv")
+#speaker = read.csv("models/speaker_normed.csv") # for printing out semantic distr's
+#speaker = read.csv("models/yelp1.csv")
 #speaker = read.csv("models/e5a.csv")
@@
 nn.post = function(rating, degree, m, alpha, useprior) {
-
   if (useprior) {
@@
   group_by(scale)
+tail(data)
 ```
@@
   md <- data %>%
-    do(run.rsa(., alpha = n, useprior = T, usenone = TRUE))
+    do.call(run.rsa(., alpha = n, useprior = T, usenone = TRUE))
 
@@
 md <- data %>%
-  do(run.rsa(., alpha = best.alpha, useprior = T, usenone = TRUE))
+  do(run.rsa(., alpha = 1, useprior = T, usenone = F))
 ```

### 2015-10-30 models/RSA_Model2.Rmd
getting rid of delted files

@@
 
+library(ggplot2)
 library(knitr)
@@
 
-opts_chunk$set(cache=TRUE)
-setwd("~/Desktop/Projects/scalar_implicature/")
-source("analysis/useful_dplyr.R")
+#setwd("~/Desktop/Projects/scalar_implicature/")
+#source("analysis/useful_dplyr.R")
 ```
@@
 ```{r}
-speaker = read.csv("models/e8.csv")
-listener = read.csv("models/listener.csv")
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/e8.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/listener.csv")
 # priors
@@
 unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
-empirical = read.csv("models/prior.csv")
-yelp = read.csv("models/yelp1_priors.csv")
+empirical = read.csv("~/Desktop/Projects/scalar_implicature//models/prior.csv")
+yelp = read.csv("~/Desktop/Projects/scalar_implicature//models/yelp1_priors.csv")
 priors = unif

### 2015-10-30 analysis/alts_analysis.py

@@ -1,75 +1,0 @@
-import os
-import json
-
-
-# read in data
-# ------------
-path = "production-results/e9/"
-files = os.listdir(path)
-
-# data org
-# --------
-scalars = {"memorable_unforgettable":	{"hi": "unforgettable", "low": "memorable"},
-		   "liked_loved": 			  	{"hi": "loved", "low": "liked" },
-		   "some_all": 					{"hi": "all", "low": "some" },
-		   "palatable_delicious": 		{"hi": "delicious", "low": "palatable" },
-		   "good_excellent": 			{"hi": "excellent", "low": "good" },
-		   "training1": 				{"hi": "high", "low": "low"}}
-
-scalar_data = { "liked":[],
-				"loved":[],
-				"memorable":[],
-				"unforgettable":[],
-				"liked":[],
-				"loved":[],
-				"good":[],
-				"excellent":[],
-				"palatable":[],
-				"delicious":[],
-				"some":[],
-				"all":[],
-				"high":[],
-				"low":[] }
-
-# read in for each respondent
-# ---------------------------
-for f in files:
-	with open(path + f) as data_file:    
-		data = json.load(data_file)
-
-		scales = data['answers']['data']['scale']    	# get scale
-		degree = data['answers']['data']['degree']		# get degree
-		alt1 = data['answers']['data']['alt1']			# alternative 1
-		alt2 = data['answers']['data']['alt2']			# alternative 2
-		alt3 = data['answers']['data']['alt3']  		# alternative 3
-		
-		# if True:
-		# 	print("----------------------------------------")
-		# 	print f
-		# 	print("scales: %s" % scales)
-		# 	print("degree: %s" % degree)
-		# 	print("alt1: %s" % alt1)
-		# 	print("alt2: %s" % alt2)
-		# 	print("alt3: %s" % alt3)
-		# 	print("----------------------------------------")
-
-		for i in range(len(scales)):
-			scale = scales[i]
-			d = degree[i]
-			a1 = alt1[i]
-			a2 = alt2[i]
-			a3 = alt3[i]
-
-			scalar_data[scalars[scale][d]].extend((a1, a2, a3))
-
-# print scalar_data
-# print scalar_data["liked"]
-# print len(scalar_data["liked"])
-# print scalar_data["some"]
-# print len(scalar_data["some"])
-
-# Output to .json to for R
-# ------------------------
-with open('alts.json', 'w') as fp:
-    json.dump(scalar_data, fp)
-

### 2015-10-30 implicatures_e1.js

@@ -1,313 +1,0 @@
-// ############################## Helper functions ##############################
-
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) 
-{ 
-    var o = [];
-    
-    for (var i=0; i < a.length; i++) {
-	o[i] = a[i];
-    }
-    
-    for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-    return o;
-}
-
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-function doSentSubs (sents, scale, domain, order)
-{
-    sent = sents["scales"][scale]["base"];
-    Q = sents["scales"][scale]["Q"][order];
-    SP = sents["domains"][domain]["SP"]; //Plural
-    SS = sents["domains"][domain]["SS"]; //Singular
-    P1 = sents["domains"][domain]["P1"]; //Predicate 1
-    P2 = sents["domains"][domain]["P2"]; //Predicate 2
-    V1 = sents["domains"][domain]["V1"]; //Past
-    V2 = sents["domains"][domain]["V2"]; //Present
-
[…]

### 2015-10-30 implicatures_e10.js

@@ -1,240 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-//############################## Helper functions ##############################	
-
-var sents = {
-    scale: {
-		training1: {
-		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
-		    hi2:  "thought the food deserved a <b>high</b> rating?",
-		    low1:  "thought the food deserved a <b>low</b> rating?"
-		    //low2:  "thought the food deserved a <b>very low</b> rating?"
-		},
-		liked_loved: {		   
-		    hi1:  "<b>loved</b> the food?",
-		    hi2:  "<b>liked</b> the food?",
-		    low1:  "<b>disliked</b> the food?",
-		    low2:  "<b>hated</b> the food?",
-		},
-		good_excellent: {
-			hi1:  "thought the food was <b>excellent</b>?",
-		    hi2:  "thought the food was <b>good</b>?",
-		    low1:  "thought the food was <b>bad</b>?",
-		    low2:  "thought the food was <b>terrible</b>?"
-		},
[…]

### 2015-10-30 implicatures_e11.js

@@ -1,228 +1,0 @@
-//############################## Helper functions #############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-
-var sents = {
-    scale: {
-		training1: {
-		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
-		    hi2:  "thought the food deserved a <b>high</b> rating.",
-		    low1:  "thought the food deserved a <b>low</b> rating.",
-		    //low2:  "thought the food deserved a <b>very low</b> rating?"
-		},
-		liked_loved: {		   
-		    hi1:  "<b>loved</b> the food.",
-		    hi2:  "<b>liked</b> the food.",
-		    low1:  "<b>disliked</b> the food.",
-		    low2:  "<b>hated</b> the food.",
-		},
-		good_excellent: {
-			hi1:  "thought the food was <b>excellent</b>.",
-		    hi2:  "thought the food was <b>good</b>.",
-		    low1:  "thought the food was <b>bad</b>.",
-		    low2:  "thought the food was <b>terrible</b>."
-		},
-		palatable_delicious: {
[…]

### 2015-10-30 implicatures_e2.js

@@ -1,325 +1,0 @@
-// ############################## Helper functions ##############################
-
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-  // Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) 
-{ 
-    var o = [];
-    
-    for (var i=0; i < a.length; i++) {
-	o[i] = a[i];
-    }
-    
-    for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-    return o;
-}
-
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-function doSentSubs (sents, scale, domain)
-{
-
-    inference = sents["scales"][scale]["sent_inference"];
-    question = sents["scales"][scale]["sent_question"];
-
-    SP = sents["domains"][domain]["SP"]; //Plural
-    SS = sents["domains"][domain]["SS"]; //Singular
-    P1 = sents["domains"][domain]["P1"]; //Predicate 1
-    P2 = sents["domains"][domain]["P2"]; //Predicate 2
-    V1 = sents["domains"][domain]["V1"]; //Past
-    V2 = sents["domains"][domain]["V2"]; //Present
-
-    inference = inference.replace("SP",SP).replace("SS",SS).replace("P1",P1).replace("P2",P2).replace("V1",V1).replace("V2",V2);
-
[…]

### 2015-10-30 implicatures_e3.js

@@ -1,361 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-function doSentSubs (sents, scale, domain) {
-	//TODO: work with this function
-
-    inference = sents["scales"][scale]["sent_inference"];
-    question = sents["scales"][scale]["sent_question"];
-    //manipulation = sents["domains"][domain][manip];
-    //manipulation = sents["scales"][scale]["sent_manipulation"];
-
-    SP = sents["domains"][domain]["SP"]; //Plural
-    SS = sents["domains"][domain]["SS"]; //Singular
-    P1 = sents["domains"][domain]["P1"]; //Predicate 1
-    P2 = sents["domains"][domain]["P2"]; //Predicate 2
-    V1 = sents["domains"][domain]["V1"]; //Past
-    V2 = sents["domains"][domain]["V2"]; //Present
-
[…]

### 2015-10-30 implicatures_e4.js

@@ -1,310 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-function doSentSubs (sents, scale, domain) {
-	//TODO: work with this function
-
-    inference = sents["scales"][scale]["sent_inference"];
-    question = sents["scales"][scale]["sent_question"];
-    //manipulation = sents["domains"][domain][manip];
-    //manipulation = sents["scales"][scale]["sent_manipulation"];
-
-    SP = sents["domains"][domain]["SP"]; //Plural
-    SS = sents["domains"][domain]["SS"]; //Singular
-    P1 = sents["domains"][domain]["P1"]; //Predicate 1
-    P2 = sents["domains"][domain]["P2"]; //Predicate 2
-    V1 = sents["domains"][domain]["V1"]; //Past
-    V2 = sents["domains"][domain]["V2"]; //Present
-
[…]

### 2015-10-30 implicatures_e5.js

@@ -1,216 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-//############################## Helper functions ##############################	
-
-var sents = {
-    scale: {
-		training1: {
-			//because training trial hi and low are the same
-		    hi:  "thought the food deserved a <b>high</b> rating?",
-		    low:  "thought the food deserved a <b>low</b> rating?"
-		},
-		liked_loved: {		   
-		    hi:  "<b>loved</b> the food?",
-		    low:  "<b>liked</b> the food?"
-		},
-		good_excellent: {
-			hi:  "thought the food was <b>excellent</b>?",
-		    low:  "thought the food was <b>good</b>?"
-		},
-		palatable_delicious: {
-			hi:  "thought the food was <b>delicious</b>?",
-		    low:  "thought the food was <b>palatable</b>?"
-		},
-	memorable_unforgettable: {
-			hi:  "thought the food was <b>unforgettable</b>?",
-		    low:  "thought the food was <b>memorable</b>?"
-		},
-		some_all: {
[…]

### 2015-10-30 implicatures_e6.js

@@ -1,200 +1,0 @@
-//############################## Helper functions #############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-
-var sents = {
-    scale: {
-		training1: {
-		    hi:  "thought the food deserved a <b>high</b> rating.",
-		    low:  "thought the food deserved a <b>low</b> rating"
-		},
-		liked_loved: {		   
-		    hi:  "<b>loved</b> the food.",
-		    low:  "<b>liked</b> the food."
-		},
-		good_excellent: {
-			hi:  "thought the food was <b>excellent</b>.",
-		    low:  "thought the food was <b>good</b>."
-		},
-		palatable_delicious: {
-			hi:  "thought the food was <b>delicious</b>.",
-		    low:  "thought the food was <b>palatable</b>."
-		},
-		memorable_unforgettable: {
-			hi:  "thought the food was <b>unforgettable</b>.",
-		    low:  "thought the food was <b>memorable</b>."
-		},
-		some_all: {
[…]

### 2015-10-30 implicatures_e7.js

@@ -1,231 +1,0 @@
-//############################## Helper functions #############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-
-// substitution function - do we want to save all these factors to a data object?
-//Pass a trial object in to be populated?
-function doSentSubs (base_sent, x, y)
-{
-    var name = x;
-    var c = context[x][y];
-    var gender = context[x]["pro"];
-    sent = base_sent.replace("PERSON", name).replace("SETTING", c).replace("GEN", gender).replace("GEN", gender);
-    return sent;
-}
-
-function get_context (name, pro) {
-	return context[name][pro];
-}
-
-var base_sent = "<b>PERSON went out to a restaurant SETTING.</b> <br><br>Without knowing anything about the food GEN ate,<br>\
-how many stars do you think GEN gave the restaurant?";
-
-var context = {
-	Bob: {
-		c1: "with a friend",
-		c2: "alone",
-	        c3: "for a birthday party",
-	        c4: "on a date",
-	        c5: "with his co-workers",
[…]

### 2015-10-30 implicatures_e8.js

@@ -1,230 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-//############################## Helper functions ##############################	
-
-var sents = {
-    scale: {
-		training1: {
-			//because training trial hi and low are the same
-		    hi:  "thought the food deserved a <b>high</b> rating?",
-		    low:  "thought the food deserved a <b>low</b> rating?"
-		},
-		liked_loved: {		   
-		    hi:  "<b>loved</b> the food?",
-		    low:  "<b>liked</b> the food?"
-		},
-		good_excellent: {
-			hi:  "thought the food was <b>excellent</b>?",
-		    low:  "thought the food was <b>good</b>?"
-		},
-		palatable_delicious: {
-			hi:  "thought the food was <b>delicious</b>?",
-		    low:  "thought the food was <b>palatable</b>?"
-		},
-	memorable_unforgettable: {
-			hi:  "thought the food was <b>unforgettable</b>?",
-		    low:  "thought the food was <b>memorable</b>?"
-		},
-		some_all: {
[…]

### 2015-10-30 implicatures_e9.js

@@ -1,266 +1,0 @@
-//############################## Helper functions ##############################
-// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
-function showSlide(id) {
-	// Hide all slides
-	$(".slide").hide();
-	// Show just the slide we want to show
-	$("#"+id).show();
-}
-
-// Get random integers.
-// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
-function random(a,b) {
-	if (typeof b == "undefined") {
-		a = a || 2;
-		return Math.floor(Math.random()*a);
-	} else {
-		return Math.floor(Math.random()*(b-a+1)) + a;
-	}
-}
-
-// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
-Array.prototype.random = function() {
-  return this[random(this.length)];
-}
-
-// shuffle function - from stackoverflow?
-// shuffle ordering of argument array -- are we missing a parenthesis?
-function shuffle (a) { 
-	var o = [];
-
-	for (var i=0; i < a.length; i++) {
-		o[i] = a[i];
-	}
-
-	for (var j, x, i = o.length;
-	 i;
-	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
-	return o;
-}
-//############################## Helper functions ##############################	
-
-
-
-
-
-var sents = {
-    scale: {
-		training1: {
-		    hi:  "<font color=\"blue\"><b>high</b></font>",
-		    low:  "<font color=\"blue\"><b>low</b></font>",
-		    before: " thought the food deserved a ",
-		    after: " rating."
-		},
-		liked_loved: {		   
-		    hi:  "<font color=\"blue\"><b>loved</b></font>",
-		    low:  "<font color=\"blue\"><b>liked</b></font>",
-		    before: " ",
-		    after: " the food."
-		},
-		good_excellent: {
-			hi:  "<font color=\"blue\"><b>excellent</b></font>",
-		    low:  "<font color=\"blue\"><b>good</b></font>",
-		    before: " thought the food was ",
-		    after: "."
-		},
-		palatable_delicious: {
-			hi:  "<font color=\"blue\"><b>delicious</b></font>",
[…]

### 2015-10-30 alts_analysis.py
moved Yelp analysis and alts_analysis into analysis dir

@@ -1,179 +1,0 @@
-import os
-import json
-import collections
-import copy
-from nltk import metrics
-
-path = "production-results/e9/"
-
-# fill this in with functionality we want to run
-toDo = "read_data edit_data"
-
-#################################################################################
-#################################################################################
-# Helpers
-# -------
-def convertLower(lst):
-	"""
-	convert each item in lst to lower case
-	"""
-	lower_list = [x.strip().lower() for x in lst]
-	return lower_list
-
-def combineIncorrectSpellings(input_list, dist, cached): 
-	"""
-	Given input lst of alternatives and dist (numeric) calculate edit distance.
-	If edit distance is greater than 0 and less than 'dist' manually update data
-	"""
-	
-	lst = copy.deepcopy(input_list)
-	n = len(lst)
-	# All pairwise comparisons
-	for i in range(n - 1):
-		for j in range(i, n):
-			print("i: %s, j: %s" % (i, j))
-			edit_distance = metrics.distance.edit_distance(lst[i], lst[j])	# store edit distance
-
-			if ((edit_distance > 0 and edit_distance < dist) or\
-				(abs(len(lst[i]) - len(lst[j])) == 1) and lst[i][0] == lst[j][0]):	# single representation
-				combine_strings = str(lst[i]+'_'+lst[j])
-
-				# first check cache for existing values
-				if combine_strings in cached.keys():
-					if (cached[combine_strings] == "do-not-change"):
-						print("***Don't change pair: %s" % combine_strings)
-						continue
-					else:
-						print("cache[%s] =  %s" % (combine_strings, cached[combine_strings]))
-						lst[i] = cached[combine_strings]
-						lst[j] = cached[combine_strings]
-						continue
-				else:
-					print("--------------------------------------------------")
-					print("Editing... %s and %s" % (lst[i], lst[j]))
-					make_edit = raw_input("Make an edit here? ('y'/'n'): ")
-
-				# go into manual edit
-				if make_edit == 'y':
-					print("--------------------------")
-					print("*%s*,*%s*" % (lst[i], lst[j]))
-					print("--------------------------")
-					change = raw_input("'left word' is correct press 1; " +\
-						"'right word' is correct press 2; " + \
-						"Type correct spelling (or 0 for not a match): ")
-
-					if change == '1':
-						lst[j] = lst[i]
-						cached.update({combine_strings : lst[i]})
-						print("stored in cache")
-
-					elif change == '2':
-						lst[i] = lst[j]
[…]

### 2015-10-30 models/RSA+AmbiguousSemantics.Rmd
Initial framework for writeup

---
title: "RSA + Scalar implicature / TBD"
author: "BPeloquin/MFrank"
date: "October 29, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---

# Pragmatics / Implicature intro

## Rational Speech-act theory

## Extending RSA to scalar implicature

# Experimental investigations / Star-rating paradigm

## Literal listener studies

### Description

### Results

## Pragmatic listener studies

### Description

### Results

# Formalizing Grice / RSA / Bayesian model

## Current model description

## Implementation

# Connecting experiments and model

## Baseline performance

## Miniumum alternatives incorporation

## Eliciting alternatives Exp

### Description

### Results

## Full model (alternatives) performance

#Conclusions

### 2015-11-02 analysis/exp_data_clean.Rmd
starting single documnet for all data output from experimental studies (mostly interested in literal listener e8,e10 and prag listener e6,e11 studies

---
title: "data_cleaning"
author: "BPeloquin"
date: "November 1, 2015"
output: html_document
---

Data cleaning code for Literal listener and Pragmatic listener experiments
```{r}
rm(list = ls())
setwd("~/Desktop/Projects/scalar_implicature/")
library(dplyr)
library(rjson)
```

Literal listener studies
```{r}
data_path = "production-results/"
current_exp = "e6"

# getTurkData
# -----------
# @file_path:   file path to results dir (i.e. "production-results/")
# @ exp_num:    data for specific experiment we're looking at (i.e. "e6")
readTurkData = function(file_path, exp_num) {
  complete_path = paste(file_path, exp_num, "/", sep="")
  files = dir(complete_path, pattern = "*.json")
  d.raw = data.frame()

  for (f in files) {
    jf = paste(complete_path,f,sep="")
    jd = fromJSON(paste(readLines(jf), collapse=""))
    id = data.frame(
      workerid = jd$WorkerId, 
      scale = jd$answer$scale,
      degree = jd$answer$degree,
      stars = as.numeric(jd$answer$judgment),
      language = jd$answer$language)
    d.raw = bind_rows(d.raw, id)
  }
  return(d.raw)
}
d.raw = readTurkData(data_path, current_exp)
head(d.raw)
```

### 2015-11-03 analysis/exp_data_clean.Rmd
centralized data cleaning/formatting and output for literal listener studies

@@
 setwd("~/Desktop/Projects/scalar_implicature/")
-library(dplyr)
+source("analysis/useful_dplyr.R")
 library(rjson)
@@
 
-Literal listener studies
+# Literal Listener study e8 output
+
+## Read in data
 ```{r}
-data_path = "production-results/"
-current_exp = "e6"
-
-# getTurkData
-# -----------
-# @file_path:   file path to results dir (i.e. "production-results/")
-# @ exp_num:    data for specific experiment we're looking at (i.e. "e6")
-readTurkData = function(file_path, exp_num) {
-  complete_path = paste(file_path, exp_num, "/", sep="")
-  files = dir(complete_path, pattern = "*.json")
+# Grab raw data from .json
+# ------------------------
+files = dir("production-results/e8/", pattern = "*.json")
 d.raw = data.frame()
@@
 for (f in files) {
-    jf = paste(complete_path,f,sep="")
+  jf = paste("production-results/e8/", f, sep="")
   jd = fromJSON(paste(readLines(jf), collapse=""))
-    id = data.frame(
-      workerid = jd$WorkerId, 
-      scale = jd$answer$scale,
-      degree = jd$answer$degree,
-      stars = as.numeric(jd$answer$judgment),
-      language = jd$answer$language)
+  id = data.frame(workerid = jd$WorkerId,
+                   scale = jd$answers$data$scale,
+                   degree = jd$answers$data$degree,
+                   stars = jd$answers$data$manipulation_level,
+                   judgment = as.numeric(jd$answers$data$judgment),
+                   language = jd$answers$data$language)
   d.raw = bind_rows(d.raw, id)
 }
-  return(d.raw)
+```
+
+## Compliance checks
+
+I'm holding off on compliance for e8. We made it a bit easier in e10 (both were agreement) and I think we're missing a large portion of the sample unncessarily.
+
+1. training1:high  -> presented 5 stars asked if the person thought the food deserved a `high` rating
+
+2. training:low    -> presented 4 stars, asked if the person thought the food deserved a `low` rating
+```{r}
+# Sample size pre compliance check
+n.pre.compliance = length(unique(d.raw$workerid))
+# Check for compliance
+compliant <- d.raw %>% 
+  filter(grepl("training1", scale)) %>%
+  group_by(workerid) %>%
+  summarise(compliant = judgment[scale == "training1" & degree == "hi"] == 1 & 
+              judgment[scale == "training1" & degree == "low"] == 0)
+
+# Sample size post compliance check
+n.post.compliance = sum(compliant$compliant)
+
+if (FALSE) { # Enforce compliance check for training 1
+  d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1", 
+         compliant == TRUE)
+} else { # Only enforce language check
+  d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1")
 }
-d.raw = readTurkData(data_path, current_exp)
-head(d.raw)
+
+# Current sample
+n.post.compliance = length(unique(d$workerid)); n.post.compliance
 ```
+
+## Cleaning / formatting - output
+```{r}
+# Preliminary data cleaning
+# -------------------------
+ms = d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
+  summarise(cil = ci.low(judgment), 
+            cih = ci.high(judgment), 
+            cnt.judgment = sum(judgment),
+            speaker.p = mean(judgment))
+
+# Output to CSV
+# --------------
+# write.csv(ms, "models/L0_e8.csv", row.names=FALSE)
+```
+
+# Literal Listener study e10 output
+```{r}
+files <- dir("production-results/e10/", pattern = "*.json")
+d.raw <- data.frame()
+
+for (f in files) {
+  jf <- paste("production-results/e10/",f,sep="")
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- data.frame(workerid = jd$WorkerId, 
+                   scale = jd$answers$data$scale,
+                   degree = jd$answers$data$degree,
+                   stars = jd$answers$data$manipulation_level,
+                   judgment = as.numeric(jd$answers$data$judgment),
+                   language = jd$answers$data$language)
+  d.raw = bind_rows(d.raw, id)
+}
+```
+
+## Compliance checks - Enforce compliance in e10. This check seemed more reasonable:
+
+1. training1:high  -> presented 5 stars asked if the person thought the food deserved a `high` rating
+
+2. training:low    -> presented 1 star, asked if the person thought the food deserved a `low` rating
+```{r}
+# Sample size pre compliance check
+n.pre.compliance = length(unique(d.raw$workerid)); n.pre.compliance
+
+compliant <- d.raw %>% 
+  filter(grepl("training", scale)) %>%
+  group_by(workerid) %>%
+  summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
+              (judgment[scale == "training1" & degree == "low1"] == 1))
+
+num_uncompliant = sum(compliant$compliant == FALSE); num_uncompliant
+
+d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1",  
+         compliant == TRUE)
+
+# Sample size post compliance check
+n.post.compliance = sum(compliant$compliant); n.post.compliance
+```
+
+## Cleaning / formatting - output
+```{r}
+# Preliminary data cleaning
+# -------------------------
+ms = d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
+  summarise(cil = ci.low(judgment), 
+            cih = ci.high(judgment), 
+            cnt.judgment = sum(judgment),
+            speaker.p = mean(judgment))
+
+# Output to CSV
+# --------------
+# write.csv(ms, "models/L0_e10.csv", row.names=FALSE)
+```

### 2015-11-03 analysis/exp_data_clean.Rmd
Data cleaning for pragmatic listener experiments

@@
 date: "November 1, 2015"
-output: html_document
+output:
+  html_document:
+    highlight: pygments
+    theme: flatly
+    toc: yes
 ---
@@
 Data cleaning code for Literal listener and Pragmatic listener experiments
-```{r}
+```{r load_data, results="hide", message=FALSE, warning=FALSE}
 rm(list = ls())
-setwd("~/Desktop/Projects/scalar_implicature/")
-source("analysis/useful_dplyr.R")
+setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/analysis")
+source("useful_dplyr.R")
 library(rjson)
@@
 ## Read in data
-```{r}
+```{r read_data, message=FALSE, warning=FALSE}
 # Grab raw data from .json
 # ------------------------
-files = dir("production-results/e8/", pattern = "*.json")
+results_path = "../production-results/e8/"
+files = dir(results_path, pattern = "*.json")
 d.raw = data.frame()
@@
 for (f in files) {
-  jf = paste("production-results/e8/", f, sep="")
+  jf = paste(results_path, f, sep="")
   jd = fromJSON(paste(readLines(jf), collapse=""))
@@
 }
+
+str(d.raw)
+head(d.raw)
 ```
@@
 
+# If set to TRUE then enroce compliance for e8 (n reduced to 16)
 if (FALSE) { # Enforce compliance check for training 1
@@
 
+str(ms)
+head(ms)
 # Output to CSV
 # --------------
-# write.csv(ms, "models/L0_e8.csv", row.names=FALSE)
+# write.csv(ms, "../models/L0_e8.csv", row.names=FALSE)
 ```
@@
 # Literal Listener study e10 output
-```{r}
-files <- dir("production-results/e10/", pattern = "*.json")
+
+## Read in data
+```{r read_data2, message=FALSE, warning=FALSE}
+results_path = "../production-results/e10/"
+files <- dir(results_path, pattern = "*.json")
 d.raw <- data.frame()
@@
 for (f in files) {
-  jf <- paste("production-results/e10/",f,sep="")
-  jd <- fromJSON(paste(readLines(jf), collapse=""))
-  id <- data.frame(workerid = jd$WorkerId, 
+  jf = paste(results_path,f,sep="")
+  jd = fromJSON(paste(readLines(jf), collapse=""))
+  id = data.frame(workerid = jd$WorkerId, 
                    scale = jd$answers$data$scale,
@@
 }
+
+str(d.raw)
+head(d.raw)
 ```
 
-## Compliance checks - Enforce compliance in e10. This check seemed more reasonable:
+## Compliance checks
 
-1. training1:high  -> presented 5 stars asked if the person thought the food deserved a `high` rating
+Enforce compliance in e10. This check seemed more reasonable:
 
-2. training:low    -> presented 1 star, asked if the person thought the food deserved a `low` rating
+1. training1:high2  -> presented 5 stars asked if the person thought the food deserved a `high(est)` rating
+
+2. training:low1    -> presented 1 star, asked if the person thought the food deserved a `low(est)` rating
 ```{r}
@@
             speaker.p = mean(judgment)) 
+str(ms)
+head(ms)
+# Output to CSV
+# --------------
+# write.csv(ms, "../models/L0_e10.csv", row.names=FALSE)
+```
+
+# Pragmatic Listener study e6 output
+
+## Read in data
+```{r read_data3, message=FALSE, warning=FALSE}
+results_path = "../production-results/e6/"
+files = dir(results_path, pattern = "*.json")
+d.raw = data.frame()
+
+for (f in files) {
+  jf = paste(results_path,f,sep="")
+  jd = fromJSON(paste(readLines(jf), collapse=""))
+  id = data.frame(workerid = jd$WorkerId, 
+                   scale = jd$answer$scale,
+                   degree = jd$answer$degree,
+                   judgment = as.numeric(jd$answer$judgment),
+                   language = jd$answer$language)
+  d.raw = bind_rows(d.raw, id)
+}
+```
+
+## Compliance checks
+
+Enforce compliance in e6.
+
+1. training1:high  ->
+
+2. training:low    -> 
+```{r}
+# Sample size pre compliance check
+n.pre.compliance = length(unique(d.raw$workerid)); n.pre.compliance
+
+compliant = d.raw %>% 
+  filter(grepl("training", scale)) %>%
+  group_by(workerid) %>%
+  summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
+              judgment[scale == "training1" & degree == "low"] < 3)
+
+d = d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1", 
+         compliant == TRUE)
+
+# Sample size post compliance check
+n.post.compliance = length(unique(d$workerid)); n.post.compliance
+```
+
+## Cleaning / formatting - output
+```{r}
+# Preliminary data cleaning
+# -------------------------
+ms <- d %>%
+  group_by(degree, scale) %>%
+  mutate(n = n()) %>%
+  group_by(degree, scale, judgment) %>%
+  summarise(prop = n() / n[1])
+str(ms)
+head(ms)
 
@@
 # --------------
-# write.csv(ms, "models/L0_e10.csv", row.names=FALSE)
+# write.csv(ms, "../models/L1_e6.csv", row.names=FALSE)
 ```
+
+# Pragmatic Listener study e11 output
+
+## Read in data
+```{r read_data4, message=FALSE, warning=FALSE}
+results_path = "../production-results/e11/"
+files = dir(results_path, pattern = "*.json")
+d.raw = data.frame()
+
+for (f in files) {
+  jf = paste(results_path,f,sep="")
+  jd = fromJSON(paste(readLines(jf), collapse=""))
+  id = data.frame(workerid = jd$WorkerId, 
+                   scale = jd$answer$data$scale,
+                   degree = jd$answer$data$degree,
+                   judgment = as.numeric(jd$answer$data$judgment),
+                   language = jd$answer$data$language)
+  d.raw = bind_rows(d.raw, id)
+}
+```
+
+## Compliance checks
+
+Enforce compliance in e11.
+
+1. training1:high  -> present "Someone said the food derved a `high` rating". Respondent must choose > 3 stars
+
+2. training:low    -> present "Someone said the food deserved a `low` rating". Respondnet must choose < 3 stars
+```{r}
+# Sample size pre compliance check
+n.pre.compliance = length(unique(d.raw$workerid)); n.pre.compliance
+
+compliant <- d.raw %>% 
+   filter(grepl("training", scale)) %>%
+   group_by(workerid) %>%
+   summarise(compliant = judgment[scale == "training1" & degree == "hi2"] > 3 & 
+               judgment[scale == "training1" & degree == "low1"] < 3)
+
+d <- d.raw %>% 
+  left_join(compliant) %>%
+  filter(grepl(pattern = "english", 
+               language, ignore.case = TRUE), 
+         scale != "training1", 
+         compliant == TRUE)
+
+# Sample size post compliance check
+n.post.compliance = length(unique(d$workerid)); n.post.compliance
+```
+
+## Cleaning / formatting - output
+```{r}
+# Preliminary data cleaning
+# -------------------------
+ms <- d %>%
+  group_by(degree, scale) %>%
+  mutate(n = n()) %>%
+  group_by(degree, scale, judgment) %>%
+  summarise(prop = n() / n[1])
+# Output to CSV
+# --------------
+# write.csv(ms, "../models/L1_e11.csv", row.names=FALSE)
+```

### 2015-11-03 models/RSA+AmbiguousSemantics.Rmd
spelling
populating basic L0 studies information

@@
 ---
+```{r load_data, results="hide", message=FALSE, warning=FALSE}
+rm(list = ls())
+setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
+source("../analysis/useful_dplyr.R")
+library(rjson)
+library(ggplot2)
+```
 
-# Pragmatics / Implicature intro
+# Pragmatics / implicature introduction
 
@@
 
-# Experimental investigations / Star-rating paradigm
+# Experimental investigations / star rating paradigm
 
 ## Literal listener studies
+
+## Can we elicit literal listener semantics for scalar items?
+
+Using the paradigm described in the `star rating paridigm` setting we attempted to elicit literal listener semantics.
+```{r}
+l0.listener = read.csv("model_data/L0_e8.csv")
+str(l0.listener)
+head(l0.listener)
+```
+Data from each literal listener study:
+
+`scale`: The scale we're currently investigating (i.e. `good_excellent`).
+
+`degree`: Valence of the current scalar item (i.e. in the scale `good_excellent` the scalar item `good` has degree `low` and `excellent` has degree `hi`).
+
+`stars`: Number of stars the subject was presented
+
+`cih` and `cil`: lower and upper 95% confidence intervals on the probability average number of positive judgments
+
+`cnt.judgment`: Count of positive responses (`yes`) signalling compatibility between a scalar item and a star rating.
+
+`speaker.p`: Estimated probability of a speaker believing a given scalar items is compatible with a presented star rating.
+
+### Literal Listener study - two scalar items
+
+We can approximate the idea of `literal listener` semantics as a distribution over star ratings.
+```{r}
+qplot(x = stars, y = speaker.p, col = degree,
+      geom = "line", stat = "identity", position = "dodge",
+      main = "Scalar compatibility with star ratings \n Experiment L0_e8",
+      ylab = "P(Word | Rating)",
+      data = l0.listener) +
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih)) + 
+  facet_wrap(~scale)
+```
+
+### Literal Listener study - Full scale from empirically derived alternatives
+```{r}
+l0.listener2 = read.csv("model_data/L0_e10.csv")
+str(l0.listener2)
+head(l0.listener2)
+```
+
+`literal listener` semantics with full distribution over ratings.
+```{r}
+qplot(x = stars, y = speaker.p, col = degree,
+      geom = "line", stat = "identity", position = "dodge", 
+      main = "Scalar compatibility with star ratings \n Experiment L0_e10",
+      ylab = "P(Word | Rating)",
+      data = l0.listener2) + 
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih)) + 
+  facet_wrap(~scale)
+```
+
+Have the distributions changed between studies (for the shared items)?
+```{r}
+subset.l2 = which((l0.listener2[, "scale"] != "some_all" &
+        (l0.listener2[, "degree"] == "hi2" | l0.listener2[, "degree"] == "hi1")) |
+       (l0.listener2[, "scale"] == "some_all" &
+          (l0.listener2[, "degree"] == "hi2" | l0.listener2[, "degree"] == "low1")))
+
+l0.listener2.match = l0.listener2[subset.l2,]
+l0.listener2.match$degree = ifelse(l0.listener2.match$degree == "hi2", "hi", "low")
+
+qplot(x = stars, y = speaker.p, col = degree,
+      geom = "line", stat = "identity", position = "dodge", 
+      main = "Scalar compatibility with star ratings \n Experiment L0_e10",
+      ylab = "P(Word | Rating)",
+      data = l0.listener2.match) + 
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih)) + 
+  facet_wrap(~scale)
+```
 
@@
 
-## Baseline performance
+## Baseline model performance
 
-## Miniumum alternatives incorporation
+## Miniumum alternatives model
 
-## Eliciting alternatives Exp
+## Eliciting alternatives experiment
 

### 2015-11-06 models/RSA+AmbiguousSemantics.Rmd
plot for literal listener semantics comparison between e1 and e2

@@
 library(ggplot2)
+library(MASS)
 ```
@@
 
-Using the paradigm described in the `star rating paridigm` setting we attempted to elicit literal listener semantics.
+Using the paradigm described in the `star rating paridigm` setting we attempted to elicit literal listener semantics. Let's read in the data and get acquanted.
 ```{r}
@@
 We can approximate the idea of `literal listener` semantics as a distribution over star ratings.
-```{r}
+```{r message=FALSE, warning=FALSE}
 qplot(x = stars, y = speaker.p, col = degree,
@@
 `literal listener` semantics with full distribution over ratings.
-```{r}
+```{r message=FALSE, warning=FALSE}
 qplot(x = stars, y = speaker.p, col = degree,
@@
 
-Have the distributions changed between studies (for the shared items)?
-```{r}
+We might be concerned that `literal listener` semantic distributions between experiments one (partial scale) and two (full scale) are different.
+Given our experimental design in which respondents are exposed to all scalar items (target scalars  and alternatives) the presence of alternatives might influence responses.
+If this is the case we'd expect to see significant differences in our estimates of the literal listener semantic distributions between experiments.
+
+Let's plot the scalar semantics for matched items between the two studies.
+```{r message=FALSE, warning=FALSE}
+# subset of full (alts exp) that match first literal listener exp
 subset.l2 = which((l0.listener2[, "scale"] != "some_all" &
@@
        (l0.listener2[, "scale"] == "some_all" &
-          (l0.listener2[, "degree"] == "hi2" | l0.listener2[, "degree"] == "low1")))
+          (l0.listener2[, "degree"] == "hi1" | l0.listener2[, "degree"] == "low1")))
 
 l0.listener2.match = l0.listener2[subset.l2,]
-l0.listener2.match$degree = ifelse(l0.listener2.match$degree == "hi2", "hi", "low")
+l0.listener2.match$degree = ifelse(l0.listener2.match$degree == "hi1", "hi", "low")
+l0.listener2.match$exp = "full"
+l0.listener$exp = "partial"
+match.scalars = rbind(l0.listener2.match, l0.listener)
 
-qplot(x = stars, y = speaker.p, col = degree,
+qplot(x = stars, y = speaker.p, colour = exp,
       geom = "line", stat = "identity", position = "dodge", 
-      main = "Scalar compatibility with star ratings \n Experiment L0_e10",
+      main = "Literal listener semantics estimates \nfor matched items",
       ylab = "P(Word | Rating)",
-      data = l0.listener2.match) + 
+      data = match.scalars) + 
   geom_linerange(aes(ymin = speaker.p - cil, 
                      ymax = speaker.p + cih)) + 
-  facet_wrap(~scale)
+  facet_wrap(~scale+degree)
+```
+
+Formal test of distributional differences:
+```{r}
+match.scalars$n.exp = ifelse(match.scalars$exp == "partial", 0, 1)
+summary(glm(n.exp ~ scale + degree + stars + speaker.p, data=match.scalars))
+head(match.scalars)
+
 ```
@@
 ### Results
+
+## How to find alternatives?
+
+Under the Gricean framework, scalar implicature occurs because of the presence of salient alternatives.
+That is, we would not enrich `some` to `some, but not all` if `all` was not somehow also present.
+This goes back to the suggested mechanism of inference - if a listener assumes a speaker is being cooperative...
+FILL THIS IN.
+
+Let's return to the scalar items `some` and `all`. Levinson (1983) proposes (http://web.stanford.edu/class/linguist236/implicature/materials/ling236-handout-04-23-scalars.pdf)...
+
+Building off a framework used by van Tiel (2014) we presented participants with a target scalar item and asked a free-response question (limited to one word): "If the person had felt differently what is another word they could have used?".
+
+which implicature arises (in this framework). If a listener assumes a speaker is cooperative and obeying the maxims
+
+## Description
 

### 2015-11-06 models/RSA+AmbiguousSemantics.Rmd
multiple plots for alts analysis - at least it's working with multiplot, but don't know how useful

@@
 library(MASS)
+library(jsonlite)
+library(tidyr)
 ```
@@
 which implicature arises (in this framework). If a listener assumes a speaker is cooperative and obeying the maxims 
+```{r multiplot(), results="hide", message=FALSE, warning=FALSE}
+multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+
+  numPlots = length(plots)
+
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                    ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+
+ if (numPlots==1) {
+    print(plots[[1]])
+
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+```
+
+```{r, fig.width=16, fig.height=30}
+# Code from e9_altsAnalysis.Rmd
+d1 = fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T)
+d1 = as.data.frame(d1, stringsAsFactors = FALSE)
+
+d <- d1 %>% 
+  gather(base, alt, 
+         palatable, liked, good, loved, some, all, 
+         delicious, excellent, memorable, unforgettable) %>%
+  mutate(base = as.character(base)) %>%
+  rowwise %>%
+  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
+                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
+                               ifelse(base == "liked" | base == "loved", "liked_loved",
+                                      ifelse(base == "good" | base == "excellent", 
+                                             "good_excellent", "memorable_unforgettable"))))) %>%
+  group_by(scale, alt) %>%
+  summarise(n = n())
+
+# Plot findings of salient alternatives for each scale
+# -------------------------------------------------------
+scales = unique(d$scale)
+p1 = ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") + ylim(0, 50) +
+  ggtitle(paste("Salient alternatives for ", scales[1])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p2 = ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[2])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p3 = ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[3])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p4 = ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[4])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p5 = ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[5])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+multiplot(p1, p2, p3, p4, p5, cols=1)
+```
 

### 2015-11-06 models/RSA+AmbiguousSemantics.Rmd
First steps in prag listener section - image formatting? Incorp images into literal listener sections?

@@
 
-We can approximate the idea of `literal listener` semantics as a distribution over star ratings.
+We can approximate `literal listener` semantics as a distribution over star ratings.
 ```{r message=FALSE, warning=FALSE}
@@
 which implicature arises (in this framework). If a listener assumes a speaker is cooperative and obeying the maxims 
-```{r multiplot(), results="hide", message=FALSE, warning=FALSE}
+```{r multiplot(), echo=FALSE}
 multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {
@@
 
-```{r, fig.width=16, fig.height=30}
+```{r, fig.width=16, fig.height=30, warning=FALSE}
 # Code from e9_altsAnalysis.Rmd
@@
 p1 = ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
-  geom_bar(stat="identity") + ylim(0, 50) +
+  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
   ggtitle(paste("Salient alternatives for ", scales[1])) +
@@
 p2 = ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
-  geom_bar(stat="identity") +
+  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
   ggtitle(paste("Salient alternatives for ", scales[2])) +
@@
 p3 = ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
-  geom_bar(stat="identity") +
+  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
   ggtitle(paste("Salient alternatives for ", scales[3])) +
@@
 p4 = ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
-  geom_bar(stat="identity") +
+  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
   ggtitle(paste("Salient alternatives for ", scales[4])) +
@@
 p5 = ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
-  geom_bar(stat="identity") +
+  geom_bar(stat="identity") + ylim(0, 50) + labs(x = "alternative", y = "counts") +
   ggtitle(paste("Salient alternatives for ", scales[5])) +
@@
 ```
+Clearly some interesting differences between scalar sets.
+In particular, responses for scales such as `some_all` and `liked_loved` appear to have more clearly defined set of alternatives with high responses for alternatives such as `none` (XX responses) or `most`.
+Conversely, scales such as `memorable_unforgettable` and `palatable_delicious` have a much longer tail of possible alternatives, with less cleary defined top competitors.
+
+Explanation / Investigation of these differences?
 
@@
 ## Pragmatic listener studies
+
+Our `Literal Listener` experimental design involves presenting participants with a star rating and asking for a judgment on the compatibility of a target scalar term with that rating using a binary (yes/no) dependent variable.
+While these distributions differ from what we might have proposed from a purely logical interpretation of literal listener semantics (i.e.
+`some` entails "at least one" and is uniformily compatible across all star ratings >= 1) we do capture the intuition that `some` has some compatibility across all ratings >= 1, but that this compatibility is graded across star ratings, not uniform.
+
+Can we also capture pragmatic enrichment in this current paradigm?
+Rational Speech-act theory frames language understanding as a special case of social cognition (Goodman & Stuhmuller, 2013) in which a listener must reason about a speaker who must reason about a listener (with an eventual grounding out of the recursion).
+In order to capture this iterated reasoning process we'll need to extend our paradigm so that participants must consider *what someone else might have meant by an utterance*.
+This is equivalent to capturing the posterior quantity we're interesed in:
+
+$$p(meaning | utterance)$$
+
+With a slight modification to our current paradigm, we can get estimates of this posterior distribution.
+Instead of presenting participants with a star rating and target scalar item and ask for a compatbility judgment, we ask participants to reason about the possible meaning of a given scalar term given a speaker utterance.
+Meaning is again quantified through star ratings.
+
+<center>
+<img src="RSA+AmbiguousSemantics_Images/e11_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
+</center>
+```{r}
+#![alt text](RSA+AmbiguousSemantics_Images/e11_example.png)
+```
 

### 2015-11-10 models/RSA+AmbiguousSemantics.Rmd
updated writeup

@@
 ## Literal listener studies
+<center>
+<img src="RSA+AmbiguousSemantics_Images/literal_listener_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
+</center>
 
@@
 
-`scale`: The scale we're currently investigating (i.e. `good_excellent`).
+`scale`: The scale we're currently investigating (i.e. "good_excellent").
 
@@
 <center>
-<img src="RSA+AmbiguousSemantics_Images/e11_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
+<img src="RSA+AmbiguousSemantics_Images/prag_listener_example.png" alt="Pragmatic Listener example" style="width: 500px;" align="middle" border="2"/>
 </center>
-```{r}
-#![alt text](RSA+AmbiguousSemantics_Images/e11_example.png)
-```
 

### 2015-11-14 models/Model_Comparison.Rmd
Model comparison doc - for working through code. Currently copied over from RSA_model2. Had to debug naming issue in exp_data_clean to run run.rsa()

--- 2015-10-30 models/RSA_Model2.Rmd
@@
 ```{r}
-speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/e8.csv")
-listener = read.csv("~/Desktop/Projects/scalar_implicature/models/listener.csv")
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
 # priors
@@
 unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
-empirical = read.csv("~/Desktop/Projects/scalar_implicature//models/prior.csv")
-yelp = read.csv("~/Desktop/Projects/scalar_implicature//models/yelp1_priors.csv")
 priors = unif
-# combine speaker / listener
+```
+
+Combine data
+```{r}
+# Combine speaker / listener
 data <- left_join(speaker, listener) %>%
@@
 run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {
-
+  #d$row = seq(1, nrow(d))
   mat <- d %>%
@@
 ```{r}
-alpha = 5
+alpha = 0
 md <- data %>%

### 2015-11-14 analysis/exp_data_clean.Rmd
fixed col naming --> had changed from 'stars' to 'judgment', but that is problemnatic for work in run.rsa which groups by 'stars'

@@
 library(rjson)
+library(jsonlite)
+library(tidyr)
+library(dplyr)
 ```
@@
                    degree = jd$answer$degree,
-                   judgment = as.numeric(jd$answer$judgment),
+                   stars = as.numeric(jd$answer$judgment),
                    language = jd$answer$language)
@@
   group_by(workerid) %>%
-  summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
-              judgment[scale == "training1" & degree == "low"] < 3)
+  summarise(compliant = stars[scale == "training1" & degree == "hi"] > 3 & 
+              stars[scale == "training1" & degree == "low"] < 3)
 
@@
   mutate(n = n()) %>%
-  group_by(degree, scale, judgment) %>%
-  summarise(prop = n() / n[1])
+  group_by(degree, scale, stars) %>%
+  summarise(listener.p = n() / n[1])
 str(ms)
@@
 # --------------
-# write.csv(ms, "../models/L1_e6.csv", row.names=FALSE)
+#write.csv(ms, "../models/L1_e6.csv", row.names=FALSE)
 ```
@@
                    degree = jd$answer$data$degree,
-                   judgment = as.numeric(jd$answer$data$judgment),
+                   stars = as.numeric(jd$answer$data$judgment),
                    language = jd$answer$data$language)
@@
    group_by(workerid) %>%
-   summarise(compliant = judgment[scale == "training1" & degree == "hi2"] > 3 & 
-               judgment[scale == "training1" & degree == "low1"] < 3)
+   summarise(compliant = stars[scale == "training1" & degree == "hi2"] > 3 & 
+               stars[scale == "training1" & degree == "low1"] < 3)
 
@@
   mutate(n = n()) %>%
-  group_by(degree, scale, judgment) %>%
-  summarise(prop = n() / n[1])
+  group_by(degree, scale, stars) %>%
+  summarise(listener.p = n() / n[1])
 # Output to CSV
 # --------------
-# write.csv(ms, "../models/L1_e11.csv", row.names=FALSE)
+#write.csv(ms, "../models/L1_e11.csv", row.names=FALSE)
 ```
+
+```{r}
+multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
+  library(grid)
+
+  # Make a list from the ... arguments and plotlist
+  plots <- c(list(...), plotlist)
+
+  numPlots = length(plots)
+
+  # If layout is NULL, then use 'cols' to determine layout
+  if (is.null(layout)) {
+    # Make the panel
+    # ncol: Number of columns of plots
+    # nrow: Number of rows needed, calculated from # of cols
+    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
+                    ncol = cols, nrow = ceiling(numPlots/cols))
+  }
+
+ if (numPlots==1) {
+    print(plots[[1]])
+
+  } else {
+    # Set up the page
+    grid.newpage()
+    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
+
+    # Make each plot, in the correct location
+    for (i in 1:numPlots) {
+      # Get the i,j matrix positions of the regions that contain this subplot
+      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
+
+      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
+                                      layout.pos.col = matchidx$col))
+    }
+  }
+}
+```
+
+# Empirically derived alternatives
+```{r}
+# Code from e9_altsAnalysis.Rmd
+d1 = fromJSON("edited_alts.json", simplifyDataFrame=T)
+d1 = as.data.frame(d1, stringsAsFactors = FALSE)
+
+d <- d1 %>% 
+  gather(base, alt, 
+         palatable, liked, good, loved, some, all, 
+         delicious, excellent, memorable, unforgettable) %>%
+  mutate(base = as.character(base)) %>%
+  rowwise %>%
+  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
+                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
+                               ifelse(base == "liked" | base == "loved", "liked_loved",
+                                      ifelse(base == "good" | base == "excellent", 
+                                             "good_excellent", "memorable_unforgettable"))))) %>%
+  group_by(scale, alt) %>%
+  summarise(n = n())
+
+# Plot findings of salient alternatives for each scale
+# -------------------------------------------------------
+scales = unique(d$scale)
+p1 = ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") + ylim(0, 50) +
+  ggtitle(paste("Salient alternatives for ", scales[1])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p2 = ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[2])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p3 = ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[3])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p4 = ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[4])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+p5 = ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
+  geom_bar(stat="identity") +
+  ggtitle(paste("Salient alternatives for ", scales[5])) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+#multiplot(p1, p2, p3, p4, p5, cols=1)
+```

### 2015-11-19 analysis/exp_data_clean.Rmd
updated file path in exp_data_clean.Rmd for e6 and e11 for correct column labeling

@@
 
-# If set to TRUE then enroce compliance for e8 (n reduced to 16)
+# If set to TRUE then enforce compliance for e8 (n reduced to 16)
 if (FALSE) { # Enforce compliance check for training 1
@@
 # --------------
-#write.csv(ms, "../models/L1_e6.csv", row.names=FALSE)
+# write.csv(ms, "../models/model_data/L1_e6.csv", row.names=FALSE)
 ```
@@
 # --------------
-#write.csv(ms, "../models/L1_e11.csv", row.names=FALSE)
+write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
 ```

### 2015-11-19 models/Model_Comparison.Rmd
minor tweak
initial comparison code for entailment models

@@
 
-Data
-----
-```{r}
-speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
-listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
-# priors
-# ------
-unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
-priors = unif
-```
+# RSA functionality
 
-Combine data
-```{r}
-# Combine speaker / listener
-data <- left_join(speaker, listener) %>%
-  left_join(priors) %>%
-  rowwise %>%
-  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
-  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
-  group_by(scale)
-head(data)
-```
-
-Model
------
+Generic posterior computation
 ```{r}
@@
 
-Run Model
-----------
+# Run functionality
 ```{r}
-# Run rsa model
-# --------------------
-run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {
-  #d$row = seq(1, nrow(d))
+# run.partial()
+# ------------
+# Run RSA with model1 (entailment) and model2 (entailment + generic)
+run.partial <- function(d, alpha = 1, useprior = F, usenone = F) {
   mat <- d %>%
@@
     mat$none <- c(1, 0, 0, 0, 0)
-    #mat$meh <- c(0.0, 0.2, 0.6, 0.2, 0)
-    #mat$bad <- c(.5, .9, .4, .1, 0)
   }
@@
 }
+
+# run.full()
+# ------------
+# Run RSA with model3 (full) with alternatives
+run.full <- function(d, alpha = 1, useprior = F, usenone = F) {
+  mat <- d %>%
+    select(stars, degree, speaker.p) %>%
+    spread(degree, speaker.p) %>%
+    mutate(hi1 = hi1 / sum(hi1),
+           hi2 = hi2 / sum(hi2),
+           low1 = low1 / sum(low1),
+           low2 = low2 / sum(low2)) %>%
+    select(hi1, hi2, low1, low2)
+
+  if (usenone) {
+    mat$none <- c(1, 0, 0, 0, 0)
+  }
+
+  d$pred <- round(as.numeric(mapply(norm.post, d$stars, d$degree, 
+                                    MoreArgs = list(m = mat, 
+                                                    alpha = alpha, 
+                                                    useprior = useprior))), 
+                  digits=4)
+
+  return(d)
+}
+
+# tune.alhpa()
+# ------------
+# d        --> data
+# alphas   --> range of alphas to test
+# type     --> full or partial model
+# useprior --> use uniform prior
+# usenone  --> use gener None
+tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F) {
+  # Tune best alphas
+  fit = sapply(alphas, FUN=function(n) {
+    if (type == "partial") {
+      md <- d %>%
+        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
+    } else {
+      md <- d %>%
+        do(run.full(., alpha = n, useprior = F, usenone = F))
+    }
+    # MSE
+    return(mean((md$pred - md$listener.p)^2))
+  })  
+  # get lowest MSE
+  best.alpha = which(fit == min(fit))
+  return(best.alpha)
+}
 ```
 
-Run model
----------
+# Model Comparisons
+
+## Data for Entailment models
 ```{r}
-alpha = 0
-md <- data %>%
-  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
+# Save performance output
+performance.output = data.frame(model=rep(NA, 6), cor=rep(NA, 6))
+
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+# Uniform priors
+priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
+# Combine speaker / listener
+data = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
+
+```
+
+## Data for full model
+```{r}
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+```
+
+## Run comparisons
+```{r}
+# Model 1 - Entailment, no alpha tuning
+# -------------------------------------
+m1.noFit = data %>%
+  do(run.partial(., alpha = 1, useprior = T, usenone = F))
+performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))
+
+# Model 1 - Entailment, alpha tuning
+# ----------------------------------
+best.alpha = tune.alpha(data)
+m1.fit = data %>%
+  do(run.partial(., alpha = best.alpha))
+performance.output[2, ] = c("M1_Fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))
+
+# Model 2 - Entailment, generic "None", no alpha tuning
+# -----------------------------------------------------
+m2.noFit = data %>%
+  do(run.partial(., alpha = 1, usenone = T))
+performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))
+
+# Model 2 - Entailment, generic "None", alpha tuning
+# ----------------------------------
+best.alpha = tune.alpha(data, usenone = T)
+m2.fit = data %>%
+  do(run.partial(., alpha = best.alpha, usenone = T))
+performance.output[4, ] = c("M2_Fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
 ```
@@
 # alpha
+tune.alpha = function(d, alphas = seq(from=1, to=10)) {
+  fit = sapply(alphas, FUN=function(n) {
+    md <- d %>%
+      do(run.rsa(., alpha = n, useprior = F, usenone = F))
+    return(mean((md$pred - md$listener.p)^2))
+    #return(cor(md$pred, md$listener.p))
+  })  
+  best.alpha = which(fit == min(fit))
+  return(best.alpha)
+}
+
 alphas = seq(from=1, to=10)
@@
     do(run.rsa(., alpha = n, useprior = F, usenone = F))
-
   return(mean((md$pred - md$listener.p)^2))

### 2015-11-19 models/Model_Comparison.Rmd
initial runs for fitted and unfitted alphas for full model - need to restrict to just comparison set of scalar terms (from e6, e8)

@@
 library(tidyr)
-
 #setwd("~/Desktop/Projects/scalar_implicature/")
@@
 # Combine speaker / listener
-data = left_join(speaker, listener) %>%
+data.partial = left_join(speaker, listener) %>%
   left_join(priors) %>%
@@
   group_by(scale)
-
 ```
@@
 listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+data.full = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
 ```
@@
 # -------------------------------------
-m1.noFit = data %>%
+m1.noFit = data.partial %>%
   do(run.partial(., alpha = 1, useprior = T, usenone = F))
@@
 # ----------------------------------
-best.alpha = tune.alpha(data)
-m1.fit = data %>%
+best.alpha = tune.alpha(data.partial)
+m1.fit = data.partial %>%
   do(run.partial(., alpha = best.alpha))
@@
 # -----------------------------------------------------
-m2.noFit = data %>%
+m2.noFit = data.partial %>%
   do(run.partial(., alpha = 1, usenone = T))
@@
 # ----------------------------------
-best.alpha = tune.alpha(data, usenone = T)
-m2.fit = data %>%
+best.alpha = tune.alpha(data.partial, usenone = T)
+m2.fit = data.partial %>%
   do(run.partial(., alpha = best.alpha, usenone = T))
 performance.output[4, ] = c("M2_Fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
+
+# Scalar matches between Full and partial
+
+# Model 3 - Full, no alpha tuning
+# ----------------------------------
+m3.noFit = data.full %>%
+  do(run.full(., alpha = 1))
+performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit$listener.p, m3.noFit$pred)^2, 5))
+
+# Model 3 - Full, alpha tuning
+# ----------------------------------
+best.alpha = tune.alpha(data.full, type = "full")
+m3.fit = data.full %>%
+  do(run.full(., alpha = best.alpha))
+performance.output[6, ] = c("M3_Fit", round(cor(m3.fit$listener.p, m3.fit$pred)^2, 5))
 ```
@@
 ```{r}
+alpha = best.alpha
 qplot(stars, listener.p, col=degree, 
-      data=md,
+      data=m3.fit,
       main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",

### 2015-11-20 models/Model_Comparison.Rmd
All model comparison populated with matched target items between e6 and e11. Still need to run tests for e10 on e6...

--- 2015-11-14 models/Model_Comparison.Rmd
@@
 ---
-title: "RSA_model2"
+title: "Model Comparisons"
 author: "BPeloquin"
-date: "August 6, 2015"
-output: html_document
+output:
+  html_document:
+    highlight: pygments
+    theme: flatly
+    toc: yes
+    toc_depth: 2
 ---
@@
 
-Data
-----
-```{r}
-speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
-listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
-# priors
-# ------
-unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
-priors = unif
-```
-
-Combine data
-```{r}
-# Combine speaker / listener
-data <- left_join(speaker, listener) %>%
-  left_join(priors) %>%
-  rowwise %>%
-  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
-  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
-  group_by(scale)
-head(data)
-```
-
-Model
------
+# RSA functionality
 ```{r}
@@
 
-Run Model
-----------
+# Run model functionality
 ```{r}
-# Run rsa model
-# --------------------
-run.rsa <- function(d, alpha = 1, useprior = F, usenone = F) {
-  #d$row = seq(1, nrow(d))
+# run.partial()
+# ------------
+# Run RSA with model1 (entailment) and model2 (entailment + generic)
+run.partial <- function(d, alpha = 1, useprior = F, usenone = F) {
   mat <- d %>%
@@
 }
+
+# run.full()
+# ------------
+# Run RSA with model3 (full) with alternatives
+run.full <- function(d, alpha = 1, useprior = F, usenone = F) {
+  mat <- d %>%
+    select(stars, degree, speaker.p) %>%
+    spread(degree, speaker.p) %>%
+    mutate(hi1 = hi1 / sum(hi1),
+           hi2 = hi2 / sum(hi2),
+           low1 = low1 / sum(low1),
+           low2 = low2 / sum(low2)) %>%
+    select(hi1, hi2, low1, low2)
+
+  if (usenone) {
+    mat$none <- c(1, 0, 0, 0, 0)
+  }
+
+  d$pred <- round(as.numeric(mapply(norm.post, d$stars, d$degree, 
+                                    MoreArgs = list(m = mat, 
+                                                    alpha = alpha, 
+                                                    useprior = useprior))), 
+                  digits=4)
+
+  return(d)
+}
+
 ```
 
-Run model
----------
+## Tune hyperparams
 ```{r}
-alpha = 0
-md <- data %>%
-  do(run.rsa(., alpha = alpha, useprior = T, usenone = F))
+# tune.alhpa()
+# ------------
+# d        --> data
+# alphas   --> range of alphas to test
+# type     --> full or partial model
+# useprior --> use uniform prior
+# usenone  --> use gener None
+tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F) {
+  # Tune best alphas
+  fit = sapply(alphas, FUN=function(n) {
+    if (type == "partial") {
+      md <- d %>%
+        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
+    } else {
+      md <- d %>%
+        do(run.full(., alpha = n, useprior = F, usenone = F))
+    }
+    # MSE
+    return(mean((md$pred - md$listener.p)^2))
+  })  
+  # get lowest MSE
+  best.alpha = which(fit == min(fit))
+  return(best.alpha)
+}
+```
+
+# Model Comparisons
+
+## Data for Entailment models
+```{r}
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+# Uniform priors
+priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
+# Combine speaker / listener
+data.partial = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
+```
+
+## Data for full model
+```{r}
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
+listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+data.full = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
+```
+
+## Match items between studies (full and partial)
+```{r}
+matched.items = which((data.full[, "scale"] != "some_all" &
+        (data.full[, "degree"] == "hi2" | data.full[, "degree"] == "hi1")) |
+       (data.full[, "scale"] == "some_all" &
+          (data.full[, "degree"] == "hi1" | data.full[, "degree"] == "low1")))
+```
+
+## Run comparisons
+```{r}
+# Save performance output
+performance.output = data.frame(model=rep(NA, 6), r2=rep(NA, 6))
+
+# Model 1 - Entailment, no alpha tuning
+# -------------------------------------
+m1.noFit = data.partial %>%
+  do(run.partial(., alpha = 1, useprior = T, usenone = F))
+performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))
+
+# Model 1 - Entailment, alpha tuning
+# ----------------------------------
+best.alpha = tune.alpha(data.partial)
+m1.fit = data.partial %>%
+  do(run.partial(., alpha = best.alpha))
+performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))
+
+# Model 2 - Entailment, generic "None", no alpha tuning
+# -----------------------------------------------------
+m2.noFit = data.partial %>%
+  do(run.partial(., alpha = 1, usenone = T))
+performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))
+
+# Model 2 - Entailment, generic "None", alpha tuning
+# --------------------------------------------------
+best.alpha = tune.alpha(data.partial, usenone = T)
+m2.fit = data.partial %>%
+  do(run.partial(., alpha = best.alpha, usenone = T))
+performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
+
+# Model 3 - Full, no alpha tuning
+# -------------------------------
+m3.noFit = data.full %>%
+  do(run.full(., alpha = 1))
+m3.noFit.matched = m3.noFit[matched.items, ]
+performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$listener.p, m3.noFit.matched$pred)^2, 5))
+
+# Model 3 - Full, alpha tuning
+# ----------------------------
+best.alpha = tune.alpha(data.full, type = "full")
+m3.fit = data.full %>%
+  do(run.full(., alpha = best.alpha))
+m3.fit.matched = m3.fit[matched.items, ]
+performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$listener.p, m3.fit.matched$pred)^2, 5))
 ```
@@
 ```{r}
-qplot(stars, listener.p, col=degree, 
-      data=md,
-      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
-                 alpha),
+performance.output
+performance.output$model = factor(performance.output$model, levels=c(
+  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit"
+))
+performance.output$r2 = as.numeric(performance.output$r2)
+qplot(data=performance.output, x=model, y=performance.output$r2,
+      geom="bar", stat="identity",
+      main = "Model performance", ylab="r^2", xlab="model") +
+  geom_text(aes(label = round(r2, 3), y = r2 + 0.02), size = 3) +
+  scale_y_continuous(limits=c(0, 1))
+
+m1.noFit.G = qplot(stars, listener.p, col=degree, 
+      data=m1.noFit,
+      main="M1, no fit",
       ylab="Posterior p(rating | word)") + 
@@
   geom_line(aes(y = pred), lty = 4)
+m1.noFit.G
 
-ggplot(md, aes(x=pred, y=listener.p)) +
-    geom_point(aes(colour = stars)) +
-    geom_smooth(method=lm) +
-  ggtitle("Model performance: Baseline") +
-  labs(x = "model prediction", y="human judgments")
-cor(md$pred, md$listener.p)^2
-cor.test(md$pred, md$listener.p)
-# scalar level cor
-specific.cor = function(scalar) {
-  return (cor(md[which(md$scale==scalar), ]$pred,
-              md[which(md$scale==scalar), ]$listener.p))
-}
-qplot(unique(md$scale), y = sapply(unique(md$scale), specific.cor),
-    aes(group=1), geom="bar", stat="identity")
+m1.fit.G = qplot(stars, listener.p, col=degree, 
+      data=m1.fit,
+      main="M1, no fit",
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m1.fit.G
+
+m2.noFit.G = qplot(stars, listener.p, col=degree, 
+      data=m2.noFit,
+      main="M2, no fit",
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m2.noFit.G
+
+m2.fit.G = qplot(stars, listener.p, col=degree, 
+      data=m2.fit,
+      main="M2, no fit",
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m2.fit.G
+
+m3.matched.noFit.G = qplot(stars, listener.p, col=degree, 
+      data=m3.noFit.matched,
+      main="M3, no fit",
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m3.matched.noFit.G
+
+m3.matched.fit.G = qplot(stars, listener.p, col=degree, 
+      data=m3.fit.matched,
+      main="M3, no fit",
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m3.matched.fit.G
 ```
-
-Tuning
--------
-```{r}
-# alpha
-alphas = seq(from=1, to=10)
-fit = sapply(alphas, FUN=function(n) {
-  md <- data %>%
-    do(run.rsa(., alpha = n, useprior = F, usenone = F))
-
-  return(mean((md$pred - md$listener.p)^2))
-  #return(cor(md$pred, md$listener.p))
-})
-qplot(alphas, fit, main="Cor for alpha values", ylab="MSE")
-best.alpha = which(fit == min(fit))
-best.alpha
-```
-
-For Presentation to Symsys290 10.26.15
-```{r}
-qplot(stars, listener.p, col=degree, 
-      data=md[md$scale=="some_all",],
-      main=paste("Model vs Human judgments\nalpha=",
-                 alpha),
-      ylab="Posterior p(m | u)") +
-  geom_line(aes(y = pred), lty = 4)
-```

### 2015-11-20 models/Model_Comparison.Rmd
all model comparisons included - each testing against e6 pragmatics. One issue is that m3 tuning occurs with e11 prags - we will likely need to adjust run.rsa to accomodate this.

@@
 
-Set-up
-------
-
-```{r}
+```{r include=FALSE}
 rm(list=ls())
@@
 library(tidyr)
-#setwd("~/Desktop/Projects/scalar_implicature/")
-#source("analysis/useful_dplyr.R")
 ```
@@
 # Run RSA with model1 (entailment) and model2 (entailment + generic)
-run.partial <- function(d, alpha = 1, useprior = F, usenone = F) {
-  mat <- d %>%
+run.partial = function(d, alpha = 1, useprior = F, usenone = F) {
+  mat = d %>%
     select(stars, degree, speaker.p) %>%
@@
   if (usenone) {
-    mat$none <- c(1, 0, 0, 0, 0)
+    mat$none = c(1, 0, 0, 0, 0)
   }
 
-  d$pred <- round(as.numeric(mapply(norm.post, d$stars, d$degree, 
+  d$pred = round(as.numeric(mapply(norm.post, d$stars, d$degree, 
                                     MoreArgs = list(m = mat, 
@@
 # Run RSA with model3 (full) with alternatives
-run.full <- function(d, alpha = 1, useprior = F, usenone = F) {
-  mat <- d %>%
+run.full = function(d, alpha = 1, useprior = F, usenone = F) {
+  mat = d %>%
     select(stars, degree, speaker.p) %>%
@@
 } 
-
 ```
@@
 
-## Data for Entailment models
-```{r}
+## Data for entailment models
+```{r entailment_models_data, message=FALSE, warning=FALSE}
 speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
@@
 ## Data for full model
-```{r}
+```{r full_model_data, message=FALSE, warning=FALSE}
 speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
@@
 ## Run comparisons
-```{r}
+```{r run_comparisons, message=FALSE}
 # Save performance output
 performance.output = data.frame(model=rep(NA, 6), r2=rep(NA, 6))
+alphas = rep(NA, 6)
 
@@
 # -------------------------------------
+alphas[1] = 1
 m1.noFit = data.partial %>%
-  do(run.partial(., alpha = 1, useprior = T, usenone = F))
+  do(run.partial(., alpha = alphas[1], useprior = T, usenone = F))
 performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))
@@
 # ----------------------------------
-best.alpha = tune.alpha(data.partial)
+alphas[2] = tune.alpha(data.partial)
 m1.fit = data.partial %>%
-  do(run.partial(., alpha = best.alpha))
+  do(run.partial(., alpha = alphas[2]))
 performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))
@@
 # -----------------------------------------------------
+alphas[3] = 1
 m2.noFit = data.partial %>%
-  do(run.partial(., alpha = 1, usenone = T))
+  do(run.partial(., alpha = alphas[3], usenone = T))
 performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))
@@
 # --------------------------------------------------
-best.alpha = tune.alpha(data.partial, usenone = T)
+alphas[4] = tune.alpha(data.partial, usenone = T)
 m2.fit = data.partial %>%
-  do(run.partial(., alpha = best.alpha, usenone = T))
+  do(run.partial(., alpha = alphas[4], usenone = T))
 performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
@@
 # -------------------------------
+alphas[5] = 1
 m3.noFit = data.full %>%
-  do(run.full(., alpha = 1))
+  do(run.full(., alpha = alphas[5]))
 m3.noFit.matched = m3.noFit[matched.items, ]
-performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$listener.p, m3.noFit.matched$pred)^2, 5))
+m3.noFit.matched$degree = ifelse(m3.noFit.matched$degree == "hi1", "hi", "low")
+m3.noFit.matched = cbind(m3.noFit.matched, data.partial$listener.p)
+# Check that everything lines up between partial and full
+all(m3.noFit.matched$scale == data.partial$scale & m3.noFit.matched$degree == data.partial$degree)
+colnames(m3.noFit.matched)[length(colnames(m3.noFit.matched))] = "e6.listener.p"
+performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)^2, 5))
 
@@
 # ----------------------------
-best.alpha = tune.alpha(data.full, type = "full")
+alphas[6] = tune.alpha(data.full, type = "full")
 m3.fit = data.full %>%
-  do(run.full(., alpha = best.alpha))
+  do(run.full(., alpha = alphas[6]))
 m3.fit.matched = m3.fit[matched.items, ]
-performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$listener.p, m3.fit.matched$pred)^2, 5))
+m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
+m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
+# Check that everything lines up between partial and full
+all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
+colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
+performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)^2, 5))
 ```
 
-Visualize
----------
-```{r}
+# Plots
+
+Overall model performance: $r^2$
+```{r overall_perf}
 performance.output
@@
   scale_y_continuous(limits=c(0, 1))
+```
 
+## Individual model performance
+```{r individual_plots}
 m1.noFit.G = qplot(stars, listener.p, col=degree, 
       data=m1.noFit,
-      main="M1, no fit",
+      main=paste("M1, no fit\nalpha: ", alphas[1]),
       ylab="Posterior p(rating | word)") + 
@@
       data=m1.fit,
-      main="M1, no fit",
+      main=paste("M1, fit\nalpha: ", alphas[2]),
       ylab="Posterior p(rating | word)") + 
@@
       data=m2.noFit,
-      main="M2, no fit",
+      main=paste("M2, no fit\nalpha: ", alphas[3]),
       ylab="Posterior p(rating | word)") + 
@@
       data=m2.fit,
-      main="M2, no fit",
+      main=paste("M2, fit\nalpha: ", alphas[4]),
       ylab="Posterior p(rating | word)") + 
@@
 
-m3.matched.noFit.G = qplot(stars, listener.p, col=degree, 
+m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
       data=m3.noFit.matched,
-      main="M3, no fit",
+      main=paste("M3, no fit\nalpha: ", alphas[5]),
       ylab="Posterior p(rating | word)") + 
@@
 
-m3.matched.fit.G = qplot(stars, listener.p, col=degree, 
+m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
       data=m3.fit.matched,
-      main="M3, no fit",
+      main=paste("M3, fit\nalpha: ", alphas[6]),
       ylab="Posterior p(rating | word)") + 
@@
 m3.matched.fit.G
+
+m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
+  geom_point(aes(colour = scale)) +
+  geom_smooth(method=lm) +
+  ggtitle("Model performance: M3 fit") +
+  labs(x = "human judgments", y="model prediction")
+
+m3.matched.fit.CorPlot
 ```
+
+# Other exploration
+```{r}
+bad.predictions = m3.fit.matched$pred > 0 &
+                  m3.fit.matched$e6.listener.p == 0 &
+                  (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
+```

### 2015-11-20 models/Model_Comparison.Rmd
updated description for plots

@@
 Overall model performance: $r^2$
+
+Here we're plotting $r^2$ values for each model - comparing model predictions with e6 pragmatic listener judgments.
+Note we use literal listener values from e8 in M1 and M2 and literal listener values from e10 for M3.
+Also note that we've tuned the M3 model using e11 literal listener pragmatics (ideally we'd use e6).
+This requires an adjustment to the tune.alpha() (or run.full()) function.
+
 ```{r overall_perf}

### 2015-11-20 models/Model_Comparison.Rmd
initial alpha tuning for e10 literal listener semantics with e6 pragmatic judgments

@@
 # usenone  --> use gener None
-tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F) {
+tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F, compare.data=NULL) {
   # Tune best alphas
@@
     if (type == "partial") {
-      md <- d %>%
+      md = d %>%
         do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
     } else {
-      md <- d %>%
+      md = d %>%
         do(run.full(., alpha = n, useprior = F, usenone = F))
     }
+    # Fit to e6 data
+    if (!is.null(compare.data)) {
+      matched.items = which((md[, "scale"] != "some_all" &
+                               (md[, "degree"] == "hi2" | md[, "degree"] == "hi1")) |
+                              (md[, "scale"] == "some_all" &
+                                 (md[, "degree"] == "hi1" | md[, "degree"] == "low1")))
+      md = md[matched.items, ]
+      md$degree = ifelse(md$degree == "hi1", "hi", "low")
+      stopifnot("listener.p" %in% colnames(compare.data))
+      md$listener.p = compare.data$listener.p
+    }
+
     # MSE
@@
 # ----------------------------
-alphas[6] = tune.alpha(data.full, type = "full")
+alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial)
 m3.fit = data.full %>%

### 2015-11-20 models/Model_Comparison.Rmd
added by star and by scale correlation plots

@@
 
+# Full model fitted - color scale
 m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
@@
   labs(x = "human judgments", y="model prediction")
+m3.matched.fit.CorPlot
 
+# Full model fitted - color stars
+m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
+  geom_point(aes(colour = stars)) +
+  geom_smooth(method=lm) +
+  ggtitle("Model performance: M3 fit") +
+  labs(x = "human judgments", y="model prediction")
 m3.matched.fit.CorPlot

### 2015-11-20 models/Model_Comparison.Rmd
better description and results table

@@
 library(tidyr)
+library(gridExtra)
 ```
@@
 
-Overall model performance: $r^2$
-
-Here we're plotting $r^2$ values for each model - comparing model predictions with e6 pragmatic listener judgments.
-Note we use literal listener values from e8 in M1 and M2 and literal listener values from e10 for M3.
-Also note that we've tuned the M3 model using e11 literal listener pragmatics (ideally we'd use e6).
-This requires an adjustment to the tune.alpha() (or run.full()) function.
-
+Overall model performance: $r^2$.
+M1 and M2 use literal listener values from exp8.
+M2 includes a generic "None" defined in terms of stars (1: 1.0, 2:0.0, 3:0.0, 4:0.0, 5:0.0).
+M3 uses the full set of literal listener alternatives from exp10, however r^2 values and tuning reflects comparisons to exp6 pragmatic listener judgments (not exp11).
 ```{r overall_perf}
-performance.output
 performance.output$model = factor(performance.output$model, levels=c(
@@
 ))
+# Populate extra model info
 performance.output$r2 = as.numeric(performance.output$r2)
+performance.output$alphas = alphas
+performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2))
+grid.table(performance.output)
+
 qplot(data=performance.output, x=model, y=performance.output$r2,

### 2015-11-26 models/Model_Comparison.Rmd
not normalizing scales before calling RSA

@@
 # ---------------------
-speaker.lhd = function(d, alpha, cost = 0) {
+speaker.inf = function(d, alpha, cost = 0) {
   exp(alpha*(log(d) - cost))
@@
 # ------------------
-speaker.prob = function(rating, degree, m, alpha) {
-  numerator = speaker.lhd(m[rating, degree], alpha)
-  norm = 0
-  for (i in 1:ncol(m)) {
-    norm = norm + speaker.lhd(m[rating, i], alpha)
-  }
-  return(numerator / norm)
+speaker.lhd = function(rating, degree, m, alpha) {
+  numerator = speaker.inf(m[rating, degree], alpha)
+  normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
+  return(numerator / normalize)
 }
@@
   prior = priors[rating, "prior.p"]
-  speaker.prob(rating, degree, m, alpha) * prior
+  return(speaker.lhd(rating, degree, m, alpha) * prior)
 }
@@
   nn = nn.post(rating, degree, m, alpha, useprior)
-  norm = 0
-  for (i in 1:5) {
-    # summation over all scale mates
-    norm = norm + nn.post(i, degree, m, alpha, useprior)
-  }
-  return(nn / norm)
+  normalize = sum(unlist(sapply(seq(1, 5), function(i){nn.post(i, degree, m, alpha, useprior)})))
+  return(nn / normalize)
 }
@@
     spread(degree, speaker.p) %>%
-    mutate(hi = hi / sum(hi), 
-           low = low / sum(low)) %>%
+#     mutate(hi = hi / sum(hi), 
+#            low = low / sum(low)) %>%
     select(hi, low)
@@
     spread(degree, speaker.p) %>%
-    mutate(hi1 = hi1 / sum(hi1),
-           hi2 = hi2 / sum(hi2),
-           low1 = low1 / sum(low1),
-           low2 = low2 / sum(low2)) %>%
+#     mutate(hi1 = hi1 / sum(hi1),
+#            hi2 = hi2 / sum(hi2),
+#            low1 = low1 / sum(low1),
+#            low2 = low2 / sum(low2)) %>%
     select(hi1, hi2, low1, low2)
@@
 # Save performance output
-performance.output = data.frame(model=rep(NA, 6), r2=rep(NA, 6))
+performance.output = data.frame(model=rep(NA, 6), cor=rep(NA, 6))
 alphas = rep(NA, 6)
@@
   do(run.partial(., alpha = alphas[1], useprior = T, usenone = F))
-performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred)^2, 5))
+performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
 
@@
   do(run.partial(., alpha = alphas[2]))
-performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred)^2, 5))
+performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred), 5))
 
@@
   do(run.partial(., alpha = alphas[3], usenone = T))
-performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred)^2, 5))
+performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred), 5))
 
@@
   do(run.partial(., alpha = alphas[4], usenone = T))
-performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred)^2, 5))
+performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred), 5))
 
@@
 colnames(m3.noFit.matched)[length(colnames(m3.noFit.matched))] = "e6.listener.p"
-performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)^2, 5))
+performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred), 5))
 
@@
 colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
-performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)^2, 5))
+performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
 ```
@@
 # Populate extra model info
-performance.output$r2 = as.numeric(performance.output$r2)
+performance.output$cor = as.numeric(performance.output$cor)
 performance.output$alphas = alphas
@@
 
-qplot(data=performance.output, x=model, y=performance.output$r2,
+qplot(data=performance.output, x=model, y=performance.output$cor,
       geom="bar", stat="identity",
       main = "Model performance", ylab="r^2", xlab="model") +
-  geom_text(aes(label = round(r2, 3), y = r2 + 0.02), size = 3) +
+  geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
   scale_y_continuous(limits=c(0, 1))

### 2015-11-26 analysis/exp_data_clean.Rmd
added total to e11 prag listener - need to figure out how to add CI's. Why is this hard?

@@
   group_by(degree, scale, stars) %>%
-  summarise(listener.p = n() / n[1])
+  summarise(listener.p = n() / n[1],
+            total = sum(stars == stars))
+
 # Output to CSV
 # --------------
-write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
+#write.csv(ms, "../models/model_data/L1_e11.csv", row.names=FALSE)
 ```

### 2015-11-26 models/Model_Comparison.Rmd
model comparisons with normalization adjustments and subjective alts from e10a.csv

@@
 # Run RSA with model1 (entailment) and model2 (entailment + generic)
-run.partial = function(d, alpha = 1, useprior = F, usenone = F) {
+run.partial = function(d, alpha = 1, useprior = F, usenone = F, normalize=F) {
+  if (normalize) {
     mat = d %>%
@@
       spread(degree, speaker.p) %>%
-#     mutate(hi = hi / sum(hi), 
-#            low = low / sum(low)) %>%
+      mutate(hi = hi / sum(hi),
+             low = low / sum(low)) %>%
       select(hi, low)
+  } else {
+    mat = d %>%
+      select(stars, degree, speaker.p) %>%
+      spread(degree, speaker.p) %>%
+      select(hi, low)
+  }
 
@@
 # Run RSA with model3 (full) with alternatives
-run.full = function(d, alpha = 1, useprior = F, usenone = F) {
+run.full = function(d, alpha=1, useprior=F, usenone=F, addMid=F, normalize=F) {
+  if (addMid) {
+    if (normalize) {
       mat = d %>%
@@
         spread(degree, speaker.p) %>%
-#     mutate(hi1 = hi1 / sum(hi1),
-#            hi2 = hi2 / sum(hi2),
-#            low1 = low1 / sum(low1),
-#            low2 = low2 / sum(low2)) %>%
+        mutate(hi1 = hi1 / sum(hi1),
+               hi2 = hi2 / sum(hi2),
+               mid = mid / sum(mid),
+               low1 = low1 / sum(low1),
+               low2 = low2 / sum(low2)) %>%
+        select(hi1, hi2, mid, low1, low2)    
+    } else {
+      mat = d %>%
+        select(stars, degree, speaker.p) %>%
+        spread(degree, speaker.p) %>%
+        select(hi1, hi2, mid, low1, low2)    
+    }
+  } else {
+    if (normalize) {
+      mat = d %>%
+        select(stars, degree, speaker.p) %>%
+        spread(degree, speaker.p) %>%
+        mutate(hi1 = hi1 / sum(hi1),
+               hi2 = hi2 / sum(hi2),
+               low1 = low1 / sum(low1),
+               low2 = low2 / sum(low2)) %>%
         select(hi1, hi2, low1, low2)
+    } else {
+      mat = d %>%
+        select(stars, degree, speaker.p) %>%
+        spread(degree, speaker.p) %>%
+        select(hi1, hi2, low1, low2)
+    }
+  }
 
@@
 # usenone  --> use gener None
-tune.alpha = function(d, alphas = seq(from=1, to=10), type="partial", useprior = T, usenone=F, compare.data=NULL) {
+tune.alpha = function(d, alphas = seq(from=1, to=10),
+                      type="partial", useprior = T,
+                      usenone=F, compare.data=NULL, addMid = F, normalize=F) {
   # Tune best alphas
@@
       md = d %>%
-        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone))
+        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone, normalize=normalize))
     } else {
       md = d %>%
-        do(run.full(., alpha = n, useprior = F, usenone = F))
+        do(run.full(., alpha = n, useprior = useprior, usenone = usenone, addMid=addMid, normalize=normalize))
     }
@@
   group_by(scale)
+
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10a.csv")
+data.full.extras = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
 ```
@@
           (data.full[, "degree"] == "hi1" | data.full[, "degree"] == "low1")))
+matched.items.extras = which((data.full.extras[, "scale"] != "some_all" &
+        (data.full.extras[, "degree"] == "hi2" | data.full.extras[, "degree"] == "hi1")) |
+       (data.full.extras[, "scale"] == "some_all" &
+          (data.full.extras[, "degree"] == "hi1" | data.full.extras[, "degree"] == "low1")))
 ```
@@
 # Save performance output
-performance.output = data.frame(model=rep(NA, 6), cor=rep(NA, 6))
-alphas = rep(NA, 6)
+performance.output = data.frame(model=rep(NA, 8), cor=rep(NA, 8))
+alphas = rep(NA, 8)
 
@@
 m3.noFit = data.full %>%
-  do(run.full(., alpha = alphas[5]))
+  do(run.full(., alpha = alphas[5], addMid=F, normalize=F))
 m3.noFit.matched = m3.noFit[matched.items, ]
@@
 # ----------------------------
-alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial)
+alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
 m3.fit = data.full %>%
@@
 performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
+
+# Model 4 - Full, no alpha tuning
+# -------------------------------
+alphas[7] = 1
+m4.noFit = data.full.extras %>%
+  do(run.full(., alpha = alphas[7], addMid=T))
+m4.noFit.matched = m4.noFit[matched.items.extras, ]
+# Need to fix this to dealt with 'mid'
+m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
+m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
+# Check that everything lines up between partial and full
+all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
+colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
+# store corr
+performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
+
+# Model 4 - Full, alpha tuning, added 'mid'
+# ----------------------------
+alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
+m4.fit = data.full.extras %>%
+  do(run.full(., alpha = alphas[8], addMid=T))
+m4.fit.matched = m4.fit[matched.items.extras, ]
+m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
+m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
+# Check that everything lines up between partial and full
+all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
+colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
+# store corr
+performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
 ```
@@
 performance.output$model = factor(performance.output$model, levels=c(
-  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit"
+  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
 ))
@@
 performance.output$alphas = alphas
-performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2))
+performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
 grid.table(performance.output)
@@
 m3.matched.noFit.G
+cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
 
@@
 m3.matched.fit.G
+cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
 
@@
 m3.matched.fit.CorPlot
+
+m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.noFit.matched,
+      main=paste("M4, no fit\nalpha: ", alphas[7]),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m4.matched.noFit.G
+
+m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.fit.matched,
+      main=paste("M4, fit\nalpha: ", alphas[8]),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+m4.matched.fit.G
 ```

### 2015-11-28 models/Model_Comparison.Rmd
Minor tweaks - prelim tests between unnormalized and normalized

@@
 # Run RSA with model1 (entailment) and model2 (entailment + generic)
-run.partial = function(d, alpha = 1, useprior = F, usenone = F, normalize=F) {
+run.partial = function(d, alpha=1, useprior=F, usenone=F, normalize=F) {
   if (normalize) {
@@
       md = d %>%
-        do(run.partial(., alpha = n, useprior = useprior, usenone = usenone, normalize=normalize))
+        do(run.partial(., alpha=n, useprior=useprior, usenone=usenone, normalize=normalize))
     } else {
       md = d %>%
-        do(run.full(., alpha = n, useprior = useprior, usenone = usenone, addMid=addMid, normalize=normalize))
+        do(run.full(., alpha=n, useprior=useprior, usenone=usenone, addMid=addMid, normalize=normalize))
     }
@@
 
-## Data for entailment models
+### Data for entailment models
 ```{r entailment_models_data, message=FALSE, warning=FALSE}
@@
 
-## Data for full model
+### Data for full model - no alternatives
 ```{r full_model_data, message=FALSE, warning=FALSE}
@@
   group_by(scale)
+```
 
+### Data for full model - alternatives
+```{r}
 speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10a.csv")
@@
 # Save performance output
-performance.output = data.frame(model=rep(NA, 8), cor=rep(NA, 8))
+performance.output = data.frame(model=rep(NA, 8), norm.cor=rep(NA, 8))
 alphas = rep(NA, 8)
 
-# Model 1 - Entailment, no alpha tuning
-# -------------------------------------
+# Model 1 - Entailment only model
+# --------------------------------
+# a)
+# Normalized = T
+# alpha tune = F
 alphas[1] = 1
-m1.noFit = data.partial %>%
-  do(run.partial(., alpha = alphas[1], useprior = T, usenone = F))
+m1.a = data.partial %>%
+  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
+performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
+# b)
+# Normalized = F
+# alpha tune = F
+alphas[1] = 1
+m1.b = data.partial %>%
+  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
 performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
@@
 # ----------------------------------
-alphas[2] = tune.alpha(data.partial)
+alphas[2] = tune.alpha(data.partial, normalize=F)
 m1.fit = data.partial %>%
@@
 m4.noFit = data.full.extras %>%
-  do(run.full(., alpha = alphas[7], addMid=T))
+  do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
 m4.noFit.matched = m4.noFit[matched.items.extras, ]

### 2015-11-28 models/Model_Comparison.Rmd
Full testing for normalized vs unnormalized, need to clean-up old code?

@@
 # Save performance output
-performance.output = data.frame(model=rep(NA, 8), norm.cor=rep(NA, 8))
-alphas = rep(NA, 8)
+performance.output = data.frame(model=rep(NA, 16),
+                                cor=rep(NA, 16),
+                                normalized=rep(NA, 16))
+alphas = rep(NA, 16)
 
-# Model 1 - Entailment only model
+# Model 1 - Entailment only models
 # --------------------------------
-# a)
+# 1.a)
+# Entailment only
 # Normalized = T
-# alpha tune = F
+# alpha tuning = F
 alphas[1] = 1
 m1.a = data.partial %>%
-  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
-performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
-# b)
+  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
+# Store output
+performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5), T)
+# Store plot
+m1.a.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m1.a,
+      main=paste("m1.a\nalpha: ", alphas[1], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 1.b)
+# Entailment only
 # Normalized = F
 # alpha tune = F
-alphas[1] = 1
+alphas[2] = 1
 m1.b = data.partial %>%
   do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
-performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
+# Store output
+performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5), F)
+# Store plot
+m1.b.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m1.b,
+      main=paste("m1.b\nalpha: ", alphas[2], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
 
-# Model 1 - Entailment, alpha tuning
-# ----------------------------------
-alphas[2] = tune.alpha(data.partial, normalize=F)
-m1.fit = data.partial %>%
-  do(run.partial(., alpha = alphas[2]))
-performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred), 5))
+# 1.c)
+# Entailment only
+# Normalized = T
+# alpha tune = T
+alphas[3] = tune.alpha(data.partial, normalize=T)
+m1.c = data.partial %>%
+  do(run.partial(., alpha = alphas[3], useprior=T, usenone=F, normalize=T))
+# Store output
+performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5), normalized=T)
+# Store plot
+m1.c.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m1.c,
+      main=paste("m1.c\nalpha: ", alphas[3], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
 
-# Model 2 - Entailment, generic "None", no alpha tuning
-# -----------------------------------------------------
-alphas[3] = 1
-m2.noFit = data.partial %>%
-  do(run.partial(., alpha = alphas[3], usenone = T))
-performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred), 5))
+# 1.d)
+# Entailment only
+# Normalized = F
+# alpha tune = T
+alphas[4] = tune.alpha(data.partial, normalize=F)
+m1.d = data.partial %>%
+  do(run.partial(., alpha = alphas[4], useprior=T, usenone=F, normalize=F))
+# Store output
+performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5), normalized=F)
+# Store plot
+m1.d.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m1.d,
+      main=paste("m1.d\nalpha: ", alphas[4], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
 
-# Model 2 - Entailment, generic "None", alpha tuning
-# --------------------------------------------------
-alphas[4] = tune.alpha(data.partial, usenone = T)
-m2.fit = data.partial %>%
-  do(run.partial(., alpha = alphas[4], usenone = T))
-performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred), 5))
+# Model 2 - Entailment + generic none
+# --------------------------------
+# 2.a)
+# Entailment + generic None
+# Normalized = T
+# alpha tuning = F
+alphas[5] = 1
+m2.a = data.partial %>%
+  do(run.partial(., alpha = alphas[5], useprior=T, usenone=T, normalize=T))
+# Store output
+performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5), T)
+# Store plot
+m2.a.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m2.a,
+      main=paste("m2.a\nalpha: ", alphas[5], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
 
-# Model 3 - Full, no alpha tuning
-# -------------------------------
-alphas[5] = 1
-m3.noFit = data.full %>%
-  do(run.full(., alpha = alphas[5], addMid=F, normalize=F))
-m3.noFit.matched = m3.noFit[matched.items, ]
-m3.noFit.matched$degree = ifelse(m3.noFit.matched$degree == "hi1", "hi", "low")
-m3.noFit.matched = cbind(m3.noFit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m3.noFit.matched$scale == data.partial$scale & m3.noFit.matched$degree == data.partial$degree)
-colnames(m3.noFit.matched)[length(colnames(m3.noFit.matched))] = "e6.listener.p"
-performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred), 5))
+# 2.b)
+# Entailment + generic None
+# Normalized = F
+# alpha tune = F
+alphas[6] = 1
+m2.b = data.partial %>%
+  do(run.partial(., alpha = alphas[1], useprior=T, usenone=T, normalize=F))
+# Store output
+performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5), F)
+# Store plot
+m2.b.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m2.b,
+      main=paste("m2.b\nalpha: ", alphas[6], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 2.c)
+# Entailment + generic None
+# Normalized = T
+# alpha tune = T
+alphas[7] = tune.alpha(data.partial, normalize=T)
+m2.c = data.partial %>%
+  do(run.partial(., alpha = alphas[7], useprior=T, usenone=T, normalize=T))
+# Store output
+performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5), normalized=T)
+# Store plot
+m2.c.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m2.c,
+      main=paste("m2.c\nalpha: ", alphas[3], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 2.d)
+# Entailment + generic None
+# Normalized = F
+# alpha tune = T
+alphas[8] = tune.alpha(data.partial, normalize=F)
+m2.d = data.partial %>%
+  do(run.partial(., alpha = alphas[8], useprior=T, usenone=T, normalize=F))
+# Store output
+performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5), normalized=F)
+# Store plot
+m2.d.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m2.d,
+      main=paste("m2.d\nalpha: ", alphas[8], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# Model 3 - Empirical alternatives
+# --------------------------------
+# 3.a)
+# Emp alts
+# Normalized = T
+# alpha tuning = F
+alphas[9] = 1
+m3.a = data.full %>%
+  do(run.full(., alpha = alphas[9], addMid=F, normalize=T))
+# Match with e6 w/ checks
+m3.a.matched = m3.a[matched.items, ]
+m3.a.matched$degree = ifelse(m3.a.matched$degree == "hi1", "hi", "low")
+m3.a.matched = cbind(m3.a.matched, data.partial$listener.p)
+all(m3.a.matched$scale == data.partial$scale & m3.a.matched$degree == data.partial$degree)
+colnames(m3.a.matched)[length(colnames(m3.a.matched))] = "e6.listener.p"
+# Store output
+performance.output[9, ] = c("m3.a", round(cor(m3.a.matched$e6.listener.p, m3.a.matched$pred), 5), T)
+# Store plot
+m3.a.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m3.a.matched,
+      main=paste("m3.a\nalpha: ", alphas[9], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 3.b)
+# Emp alts
+# Entailment + generic None
+# Normalized = F
+# alpha tune = F
+alphas[10] = 1
+m3.b = data.full %>%
+  do(run.full(., alpha = alphas[10], addMid=F, normalize=F))
+# Match with e6 w/ checks
+m3.b.matched = m3.b[matched.items, ]
+m3.b.matched$degree = ifelse(m3.b.matched$degree == "hi1", "hi", "low")
+m3.b.matched = cbind(m3.b.matched, data.partial$listener.p)
+all(m3.b.matched$scale == data.partial$scale & m3.b.matched$degree == data.partial$degree)
+colnames(m3.b.matched)[length(colnames(m3.b.matched))] = "e6.listener.p"
+# Store output
+performance.output[10, ] = c("m3.b", round(cor(m3.b.matched$e6.listener.p, m3.b.matched$pred), 5), F)
+# Store plot
+m3.b.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m3.b.matched,
+      main=paste("m3.b\nalpha: ", alphas[10], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 3.c)
+# Emp alts
+# Normalized = T
+# alpha tune = T
+alphas[11] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=T)
+m3.c = data.full %>%
+  do(run.full(., alpha = alphas[11], addMid=F, normalize=T))
+# Match with e6 w/ checks
+m3.c.matched = m3.c[matched.items, ]
+m3.c.matched$degree = ifelse(m3.c.matched$degree == "hi1", "hi", "low")
+m3.c.matched = cbind(m3.c.matched, data.partial$listener.p)
+all(m3.c.matched$scale == data.partial$scale & m3.c.matched$degree == data.partial$degree)
+colnames(m3.c.matched)[length(colnames(m3.c.matched))] = "e6.listener.p"
+# Store output
+performance.output[11, ] = c("m3.c", round(cor(m3.c.matched$e6.listener.p, m3.c.matched$pred), 5), T)
+# Store plot
+m3.c.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m3.c.matched,
+      main=paste("m3.c\nalpha: ", alphas[11], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 3.d)
+# Emp alts
+# Normalized = F
+# alpha tune = T
+alphas[12] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
+m3.d = data.full %>%
+  do(run.full(., alpha = alphas[12], addMid=F, normalize=F))
+# Match with e6 w/ checks
+m3.d.matched = m3.d[matched.items, ]
+m3.d.matched$degree = ifelse(m3.d.matched$degree == "hi1", "hi", "low")
+m3.d.matched = cbind(m3.d.matched, data.partial$listener.p)
+all(m3.d.matched$scale == data.partial$scale & m3.d.matched$degree == data.partial$degree)
+colnames(m3.d.matched)[length(colnames(m3.d.matched))] = "e6.listener.p"
+# Store output
+performance.output[12, ] = c("m3.d", round(cor(m3.d.matched$e6.listener.p, m3.d.matched$pred), 5), F)
+# Store plot
+m3.d.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m3.d.matched,
+      main=paste("m3.d\nalpha: ", alphas[12], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# Model 4 - Empirical alternatives + extras
+# -----------------------------------------
+# 4.a)
+# Emp alts + extras
+# Normalized = T
+# alpha tuning = F
+alphas[13] = 1
+m4.a = data.full.extras %>%
+  do(run.full(., alpha = alphas[13], addMid=T, normalize=T))
+# Match with e6 w/ checks
+m4.a.matched = m4.a[matched.items.extras, ]
+m4.a.matched$degree = ifelse(m4.a.matched$degree == "hi1", "hi", "low")
+m4.a.matched = cbind(m4.a.matched, data.partial$listener.p)
+all(m4.a.matched$scale == data.partial$scale & m4.a.matched$degree == data.partial$degree)
+colnames(m4.a.matched)[length(colnames(m4.a.matched))] = "e6.listener.p"
+# Store output
+performance.output[13, ] = c("m4.a", round(cor(m4.a.matched$e6.listener.p, m4.a.matched$pred), 5), T)
+# Store plot
+m4.a.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.a.matched,
+      main=paste("m4.a\nalpha: ", alphas[13], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 4.b)
+# Emp alts + extras
+# Normalized = F
+# alpha tune = F
+alphas[14] = 1
+m4.b = data.full.extras %>%
+  do(run.full(., alpha = alphas[14], addMid=T, normalize=F))
+# Match with e6 w/ checks
+m4.b.matched = m4.b[matched.items.extras, ]
+m4.b.matched$degree = ifelse(m4.b.matched$degree == "hi1", "hi", "low")
+m4.b.matched = cbind(m4.b.matched, data.partial$listener.p)
+all(m4.b.matched$scale == data.partial$scale & m4.b.matched$degree == data.partial$degree)
+colnames(m4.b.matched)[length(colnames(m4.b.matched))] = "e6.listener.p"
+# Store output
+performance.output[14, ] = c("m4.b", round(cor(m4.b.matched$e6.listener.p, m4.b.matched$pred), 5), F)
+# Store plot
+m4.b.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.b.matched,
+      main=paste("m4.b\nalpha: ", alphas[14], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 4.c)
+# Emp alts + extras
+# Normalized = T
+# alpha tune = T
+alphas[15] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=T)
+m4.c = data.full.extras %>%
+  do(run.full(., alpha = alphas[15], addMid=T, normalize=T))
+# Match with e6 w/ checks
+m4.c.matched = m4.c[matched.items.extras, ]
+m4.c.matched$degree = ifelse(m4.c.matched$degree == "hi1", "hi", "low")
+m4.c.matched = cbind(m4.c.matched, data.partial$listener.p)
+all(m4.c.matched$scale == data.partial$scale & m4.c.matched$degree == data.partial$degree)
+colnames(m4.c.matched)[length(colnames(m4.c.matched))] = "e6.listener.p"
+# Store output
+performance.output[15, ] = c("m4.c", round(cor(m4.c.matched$e6.listener.p, m4.c.matched$pred), 5), T)
+# Store plot
+m4.c.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.c.matched,
+      main=paste("m4.c\nalpha: ", alphas[15], "\nNormalized = ", T),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 4.d)
+# Emp alts + extras
+# Normalized = F
+# alpha tune = T
+alphas[16] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=F)
+m4.d = data.full.extras %>%
+  do(run.full(., alpha = alphas[16], addMid=T, normalize=F))
+# Match with e6 w/ checks
+m4.d.matched = m4.d[matched.items.extras, ]
+m4.d.matched$degree = ifelse(m4.d.matched$degree == "hi1", "hi", "low")
+m4.d.matched = cbind(m4.d.matched, data.partial$listener.p)
+all(m4.d.matched$scale == data.partial$scale & m4.d.matched$degree == data.partial$degree)
+colnames(m4.d.matched)[length(colnames(m4.d.matched))] = "e6.listener.p"
+# Store output
+performance.output[16, ] = c("m4.d", round(cor(m4.d.matched$e6.listener.p, m4.d.matched$pred), 5), F)
+# Store plot
+m4.d.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m4.d.matched,
+      main=paste("m4.d\nalpha: ", alphas[16], "\nNormalized = ", F),
+      ylab="Posterior p(rating | word)") + 
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
+# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
+# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
+# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
 

### 2015-11-28 models/Model_Comparison.Rmd
tweaks to performance storage

@@
 }
+
+# Uniform priors
+unif.priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
+emp.priors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
+priors = unif.priors
 ```
@@
 listener = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
-# Uniform priors
-priors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
 # Combine speaker / listener
@@
 # Store plot
-m1.a.plot = qplot(stars, e6.listener.p, col=degree, 
+m1.a.plot = qplot(stars, listener.p, col=degree, 
       data=m1.a,
@@
 # Store plot
-m1.b.plot = qplot(stars, e6.listener.p, col=degree, 
+m1.b.plot = qplot(stars, listener.p, col=degree, 
       data=m1.b,
@@
 # Store plot
-m1.c.plot = qplot(stars, e6.listener.p, col=degree, 
+m1.c.plot = qplot(stars, listener.p, col=degree, 
       data=m1.c,
@@
 # Store plot
-m1.d.plot = qplot(stars, e6.listener.p, col=degree, 
+m1.d.plot = qplot(stars, listener.p, col=degree, 
       data=m1.d,
@@
 # Store plot
-m2.a.plot = qplot(stars, e6.listener.p, col=degree, 
+m2.a.plot = qplot(stars, listener.p, col=degree, 
       data=m2.a,
@@
 m2.b = data.partial %>%
-  do(run.partial(., alpha = alphas[1], useprior=T, usenone=T, normalize=F))
+  do(run.partial(., alpha = alphas[6], useprior=T, usenone=T, normalize=F))
 # Store output
@@
 # Store plot
-m2.b.plot = qplot(stars, e6.listener.p, col=degree, 
+m2.b.plot = qplot(stars, listener.p, col=degree, 
       data=m2.b,
@@
 # Store plot
-m2.c.plot = qplot(stars, e6.listener.p, col=degree, 
+m2.c.plot = qplot(stars, listener.p, col=degree, 
       data=m2.c,
-      main=paste("m2.c\nalpha: ", alphas[3], "\nNormalized = ", T),
+      main=paste("m2.c\nalpha: ", alphas[7], "\nNormalized = ", T),
       ylab="Posterior p(rating | word)") + 
@@
 # Store plot
-m2.d.plot = qplot(stars, e6.listener.p, col=degree, 
+m2.d.plot = qplot(stars, listener.p, col=degree, 
       data=m2.d,
@@
 # ----------------------------
-alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
-m3.fit = data.full %>%
-  do(run.full(., alpha = alphas[6]))
-m3.fit.matched = m3.fit[matched.items, ]
-m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
-m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
-colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
-performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
-
-# Model 4 - Full, no alpha tuning
-# -------------------------------
-alphas[7] = 1
-m4.noFit = data.full.extras %>%
-  do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
-m4.noFit.matched = m4.noFit[matched.items.extras, ]
-# Need to fix this to dealt with 'mid'
-m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
-m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
-colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
-# store corr
-performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
-
-# Model 4 - Full, alpha tuning, added 'mid'
-# ----------------------------
-alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
-m4.fit = data.full.extras %>%
-  do(run.full(., alpha = alphas[8], addMid=T))
-m4.fit.matched = m4.fit[matched.items.extras, ]
-m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
-m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
-colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
-# store corr
-performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
+# alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
+# m3.fit = data.full %>%
+#   do(run.full(., alpha = alphas[6]))
+# m3.fit.matched = m3.fit[matched.items, ]
+# m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
+# m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
+# # Check that everything lines up between partial and full
+# all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
+# colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
+# performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
+# 
+# # Model 4 - Full, no alpha tuning
+# # -------------------------------
+# alphas[7] = 1
+# m4.noFit = data.full.extras %>%
+#   do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
+# m4.noFit.matched = m4.noFit[matched.items.extras, ]
+# # Need to fix this to dealt with 'mid'
+# m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
+# m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
+# # Check that everything lines up between partial and full
+# all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
+# colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
+# # store corr
+# performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
+# 
+# # Model 4 - Full, alpha tuning, added 'mid'
+# # ----------------------------
+# alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
+# m4.fit = data.full.extras %>%
+#   do(run.full(., alpha = alphas[8], addMid=T))
+# m4.fit.matched = m4.fit[matched.items.extras, ]
+# m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
+# m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
+# # Check that everything lines up between partial and full
+# all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
+# colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
+# # store corr
+# performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
 ```
@@
 ```{r overall_perf}
-performance.output$model = factor(performance.output$model, levels=c(
-  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
-))
-# Populate extra model info
-performance.output$cor = as.numeric(performance.output$cor)
-performance.output$alphas = alphas
-performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
+performance.output = cbind(performance.output, alphas)
 grid.table(performance.output)
 
-qplot(data=performance.output, x=model, y=performance.output$cor,
-      geom="bar", stat="identity",
-      main = "Model performance", ylab="r^2", xlab="model") +
-  geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
-  scale_y_continuous(limits=c(0, 1))
+m1.a.plot
+m1.b.plot
+m1.c.plot
+m1.d.plot
+
+m2.a.plot
+m2.b.plot
+m2.c.plot
+m2.d.plot
+
+m3.a.plot
+m3.b.plot
+m3.c.plot
+m3.d.plot
+
+m4.a.plot
+m4.b.plot
+m4.c.plot
+m4.d.plot
+# performance.output$model = factor(performance.output$model, levels=c(
+#   "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
+# ))
+# # Populate extra model info
+# performance.output$cor = as.numeric(performance.output$cor)
+# performance.output$alphas = alphas
+# performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
+# grid.table(performance.output)
+# 
+# qplot(data=performance.output, x=model, y=performance.output$cor,
+#       geom="bar", stat="identity",
+#       main = "Model performance", ylab="r^2", xlab="model") +
+#   geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
+#   scale_y_continuous(limits=c(0, 1))
 ```
@@
 ```{r individual_plots}
-m1.noFit.G = qplot(stars, listener.p, col=degree, 
-      data=m1.noFit,
-      main=paste("M1, no fit\nalpha: ", alphas[1]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m1.noFit.G
-
-m1.fit.G = qplot(stars, listener.p, col=degree, 
-      data=m1.fit,
-      main=paste("M1, fit\nalpha: ", alphas[2]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m1.fit.G
-
-m2.noFit.G = qplot(stars, listener.p, col=degree, 
-      data=m2.noFit,
-      main=paste("M2, no fit\nalpha: ", alphas[3]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m2.noFit.G
-
-m2.fit.G = qplot(stars, listener.p, col=degree, 
-      data=m2.fit,
-      main=paste("M2, fit\nalpha: ", alphas[4]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m2.fit.G
-
-m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.noFit.matched,
-      main=paste("M3, no fit\nalpha: ", alphas[5]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m3.matched.noFit.G
-cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
-
-m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.fit.matched,
-      main=paste("M3, fit\nalpha: ", alphas[6]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m3.matched.fit.G
-cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
-
-# Full model fitted - color scale
-m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-  geom_point(aes(colour = scale)) +
-  geom_smooth(method=lm) +
-  ggtitle("Model performance: M3 fit") +
-  labs(x = "human judgments", y="model prediction")
-m3.matched.fit.CorPlot
-
-# Full model fitted - color stars
-m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-  geom_point(aes(colour = stars)) +
-  geom_smooth(method=lm) +
-  ggtitle("Model performance: M3 fit") +
-  labs(x = "human judgments", y="model prediction")
-m3.matched.fit.CorPlot
-
-m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m4.noFit.matched,
-      main=paste("M4, no fit\nalpha: ", alphas[7]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m4.matched.noFit.G
-
-m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m4.fit.matched,
-      main=paste("M4, fit\nalpha: ", alphas[8]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m4.matched.fit.G
+# m1.noFit.G = qplot(stars, listener.p, col=degree, 
+#       data=m1.noFit,
+#       main=paste("M1, no fit\nalpha: ", alphas[1]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# # m1.noFit.G
+# 
+# m1.fit.G = qplot(stars, listener.p, col=degree, 
+#       data=m1.fit,
+#       main=paste("M1, fit\nalpha: ", alphas[2]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m1.fit.G
+# 
+# m2.noFit.G = qplot(stars, listener.p, col=degree, 
+#       data=m2.noFit,
+#       main=paste("M2, no fit\nalpha: ", alphas[3]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m2.noFit.G
+# 
+# m2.fit.G = qplot(stars, listener.p, col=degree, 
+#       data=m2.fit,
+#       main=paste("M2, fit\nalpha: ", alphas[4]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m2.fit.G
+# 
+# m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
+#       data=m3.noFit.matched,
+#       main=paste("M3, no fit\nalpha: ", alphas[5]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m3.matched.noFit.G
+# cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
+# 
+# m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
+#       data=m3.fit.matched,
+#       main=paste("M3, fit\nalpha: ", alphas[6]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m3.matched.fit.G
+# cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
+# 
+# # Full model fitted - color scale
+# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
+#   geom_point(aes(colour = scale)) +
+#   geom_smooth(method=lm) +
+#   ggtitle("Model performance: M3 fit") +
+#   labs(x = "human judgments", y="model prediction")
+# m3.matched.fit.CorPlot
+# 
+# # Full model fitted - color stars
+# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
+#   geom_point(aes(colour = stars)) +
+#   geom_smooth(method=lm) +
+#   ggtitle("Model performance: M3 fit") +
+#   labs(x = "human judgments", y="model prediction")
+# m3.matched.fit.CorPlot
+# 
+# m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
+#       data=m4.noFit.matched,
+#       main=paste("M4, no fit\nalpha: ", alphas[7]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m4.matched.noFit.G
+# 
+# m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
+#       data=m4.fit.matched,
+#       main=paste("M4, fit\nalpha: ", alphas[8]),
+#       ylab="Posterior p(rating | word)") + 
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = pred), lty = 4)
+# m4.matched.fit.G
 ```
@@
 ```{r}
-bad.predictions = m3.fit.matched$pred > 0 &
-                  m3.fit.matched$e6.listener.p == 0 &
-                  (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
+# bad.predictions = m3.fit.matched$pred > 0 &
+#                   m3.fit.matched$e6.listener.p == 0 &
+#                   (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
 ```

### 2015-11-28 models/Model_additionalAlts.Rmd
subjective alts for specific scalars. basic functionality used for liked_loved, good_excellent, some_all

--- 2015-11-28 models/Model_Comparison.Rmd
@@
 ---
-title: "Model Comparisons"
+title: "Model_additionalAlts"
 author: "BPeloquin"
-output:
-  html_document:
-    highlight: pygments
-    theme: flatly
-    toc: yes
-    toc_depth: 2
+date: "November 25, 2015"
+output: html_document
 ---
-
 ```{r include=FALSE}
@@
 
-## Run comparisons
-```{r run_comparisons, message=FALSE}
-# Save performance output
-performance.output = data.frame(model=rep(NA, 8), norm.cor=rep(NA, 8))
-alphas = rep(NA, 8)
+Focus on `good_excellent`:
+```{r}
+focus_alts = function(target, combos, normalize=F) {
+  if (is.null(combos)) {
+    combos = data.frame(c(0, 0, 1, 0, 0),
+                        c(0, 0.05, 0.9, 0.05, 0),
+                        c(0, 0.1, 0.8, 0.1, 0),
+                        c(0, 0.2, 0.6, 0.2, 0),
+                        c(0, 0.25, 0.5, 0.25, 0))  
+  }
+  colnames(combos) = LETTERS[1:length(colnames(combos))]
+  cors = c()
+  for (i in 1:ncol(combos)) {
+    ge.subset = data.full.extras[data.full.extras$scale == target, ]
+    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
+    target.scalars = c("hi1", "hi2")
+    # Run model)
+    m1 = ge.subset %>%
+      do(run.full(., alpha = 8, addMid = T, normalize=normalize))
+    if (target == "some_all") {
+      target.scalars = c("hi1", "low1")
+      m1 = m1[m1$degree %in% target.scalars, ]  
+    } else {
+      m1 = m1[m1$degree %in% target.scalars, ]  
+    }
+    cors[i] = cor(m1$pred, m1$listener.p)  
+  }
+  cors
 
-# Model 1 - Entailment only model
-# --------------------------------
-# a)
-# Normalized = T
-# alpha tune = F
-alphas[1] = 1
-m1.a = data.partial %>%
-  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
-performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
-# b)
-# Normalized = F
-# alpha tune = F
-alphas[1] = 1
-m1.b = data.partial %>%
-  do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=F))
-performance.output[1, ] = c("M1_noFit", round(cor(m1.noFit$listener.p, m1.noFit$pred), 5))
+  i = which(cors == max(cors))
+  # combos[i]
+  ge.subset = data.full.extras[data.full.extras$scale == target, ]
+    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
+  m1 = ge.subset %>%
+    do(run.full(., alpha = 8, addMid = T))
 
-# Model 1 - Entailment, alpha tuning
-# ----------------------------------
-alphas[2] = tune.alpha(data.partial, normalize=F)
-m1.fit = data.partial %>%
-  do(run.partial(., alpha = alphas[2]))
-performance.output[2, ] = c("M1_fit", round(cor(m1.fit$listener.p, m1.fit$pred), 5))
+  qplot(stars, listener.p, col=degree, 
+        data=m1,
+        ylab="Posterior p(rating | word)") + 
+    geom_line(aes(y = pred), lty = 4)
+  return(combos[i])
+}
 
-# Model 2 - Entailment, generic "None", no alpha tuning
-# -----------------------------------------------------
-alphas[3] = 1
-m2.noFit = data.partial %>%
-  do(run.partial(., alpha = alphas[3], usenone = T))
-performance.output[3, ] = c("M2_noFit", round(cor(m2.noFit$listener.p, m2.noFit$pred), 5))
-
-# Model 2 - Entailment, generic "None", alpha tuning
-# --------------------------------------------------
-alphas[4] = tune.alpha(data.partial, usenone = T)
-m2.fit = data.partial %>%
-  do(run.partial(., alpha = alphas[4], usenone = T))
-performance.output[4, ] = c("M2_fit", round(cor(m2.fit$listener.p, m2.fit$pred), 5))
-
-# Model 3 - Full, no alpha tuning
-# -------------------------------
-alphas[5] = 1
-m3.noFit = data.full %>%
-  do(run.full(., alpha = alphas[5], addMid=F, normalize=F))
-m3.noFit.matched = m3.noFit[matched.items, ]
-m3.noFit.matched$degree = ifelse(m3.noFit.matched$degree == "hi1", "hi", "low")
-m3.noFit.matched = cbind(m3.noFit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m3.noFit.matched$scale == data.partial$scale & m3.noFit.matched$degree == data.partial$degree)
-colnames(m3.noFit.matched)[length(colnames(m3.noFit.matched))] = "e6.listener.p"
-performance.output[5, ] = c("M3_noFit", round(cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred), 5))
-
-# Model 3 - Full, alpha tuning
-# ----------------------------
-alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
-m3.fit = data.full %>%
-  do(run.full(., alpha = alphas[6]))
-m3.fit.matched = m3.fit[matched.items, ]
-m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
-m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
-colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
-performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
-
-# Model 4 - Full, no alpha tuning
-# -------------------------------
-alphas[7] = 1
-m4.noFit = data.full.extras %>%
-  do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
-m4.noFit.matched = m4.noFit[matched.items.extras, ]
-# Need to fix this to dealt with 'mid'
-m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
-m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
-colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
-# store corr
-performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
-
-# Model 4 - Full, alpha tuning, added 'mid'
-# ----------------------------
-alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
-m4.fit = data.full.extras %>%
-  do(run.full(., alpha = alphas[8], addMid=T))
-m4.fit.matched = m4.fit[matched.items.extras, ]
-m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
-m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
-# Check that everything lines up between partial and full
-all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
-colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
-# store corr
-performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
+focus_alts("good_excellent", combos=NULL)
+focus_alts("liked_loved", combos=NULL)
+combos = data.frame(c(0, 1, 0, 0, 0),
+                    c(0.05, 0.9, 0.05, 0, 0),
+                    c(0.1, 0.8, 0.1, 0, 0),
+                    c(0.2, 0.6, 0.2, 0, 0),
+                    c(0.25, 0.5, 0.25, 0, 0))
+focus_alts("some_all", combos=combos)
 ```
 
-# Plots
+Focus on `some_all`:
+```{r}
+ge.subset = data.full[data.full$scale == "some_all", ]
+ge.subset[ge.subset$degree == "mid", "speaker.p"] = c(0, 1, 0, 0, 0)
+head(ge.subset, n = 20)
+target.scalars = c("hi1", "low1")
 
-Overall model performance: $r^2$.
-M1 and M2 use literal listener values from exp8.
-M2 includes a generic "None" defined in terms of stars (1: 1.0, 2:0.0, 3:0.0, 4:0.0, 5:0.0).
-M3 uses the full set of literal listener alternatives from exp10, however r^2 values and tuning reflects comparisons to exp6 pragmatic listener judgments (not exp11).
-```{r overall_perf}
-performance.output$model = factor(performance.output$model, levels=c(
-  "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
-))
-# Populate extra model info
-performance.output$cor = as.numeric(performance.output$cor)
-performance.output$alphas = alphas
-performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
-grid.table(performance.output)
+# Run model
+m1 = ge.subset %>%
+  do(run.full(., alpha = 8, addMid = T))
+cor(m1$pred, m1$listener.p)
 
-qplot(data=performance.output, x=model, y=performance.output$cor,
-      geom="bar", stat="identity",
-      main = "Model performance", ylab="r^2", xlab="model") +
-  geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
-  scale_y_continuous(limits=c(0, 1))
+qplot(stars, listener.p, col=degree, 
+      data=m1,
+      ylab="Posterior p(rating | word)") + 
+  geom_line(aes(y = pred), lty = 4)
+
+m1 = m1[m1$degree %in% target.scalars, ]
+cor(m1$pred, m1$listener.p)
+
+combos = data.frame(c(0, 0, 1, 0, 0),
+                    c(0, 0.05, 0.9, 0.05, 0),
+                    c(0, 0.1, 0.8, 0.1, 0),
+                    c(0, 0.2, 0.6, 0.2, 0),
+                    c(0, 0.25, 0.5, 0.25, 0))
+colnames(combos) = LETTERS[1:length(colnames(combos))]
+cors = c()
+for (i in 1:ncol(combos)) {
+  print(i)
+  ge.subset = data.full[data.full$scale == "good_excellent", ]
+  ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
+  target.scalars = c("hi1", "hi2")
+  # Run model
+  m1 = ge.subset %>%
+    do(run.full(., alpha = 8, addMid = T))
+  m1 = m1[m1$degree %in% target.scalars, ]
+  cors[i] = cor(m1$pred, m1$listener.p)  
+}
+cors 
 ```
-
-## Individual model performance
-```{r individual_plots}
-m1.noFit.G = qplot(stars, listener.p, col=degree, 
-      data=m1.noFit,
-      main=paste("M1, no fit\nalpha: ", alphas[1]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m1.noFit.G
-
-m1.fit.G = qplot(stars, listener.p, col=degree, 
-      data=m1.fit,
-      main=paste("M1, fit\nalpha: ", alphas[2]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m1.fit.G
-
-m2.noFit.G = qplot(stars, listener.p, col=degree, 
-      data=m2.noFit,
-      main=paste("M2, no fit\nalpha: ", alphas[3]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m2.noFit.G
-
-m2.fit.G = qplot(stars, listener.p, col=degree, 
-      data=m2.fit,
-      main=paste("M2, fit\nalpha: ", alphas[4]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m2.fit.G
-
-m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.noFit.matched,
-      main=paste("M3, no fit\nalpha: ", alphas[5]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m3.matched.noFit.G
-cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
-
-m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.fit.matched,
-      main=paste("M3, fit\nalpha: ", alphas[6]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m3.matched.fit.G
-cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
-
-# Full model fitted - color scale
-m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-  geom_point(aes(colour = scale)) +
-  geom_smooth(method=lm) +
-  ggtitle("Model performance: M3 fit") +
-  labs(x = "human judgments", y="model prediction")
-m3.matched.fit.CorPlot
-
-# Full model fitted - color stars
-m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-  geom_point(aes(colour = stars)) +
-  geom_smooth(method=lm) +
-  ggtitle("Model performance: M3 fit") +
-  labs(x = "human judgments", y="model prediction")
-m3.matched.fit.CorPlot
-
-m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m4.noFit.matched,
-      main=paste("M4, no fit\nalpha: ", alphas[7]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m4.matched.noFit.G
-
-m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-      data=m4.fit.matched,
-      main=paste("M4, fit\nalpha: ", alphas[8]),
-      ylab="Posterior p(rating | word)") + 
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-m4.matched.fit.G
-```
-
-# Other exploration
-```{r}
-bad.predictions = m3.fit.matched$pred > 0 &
-                  m3.fit.matched$e6.listener.p == 0 &
-                  (m3.fit.matched$pred - m3.fit.matched$e6.listener.p > 0.05)
-```

### 2015-11-28 models/RSA+AmbiguousSemantics.Rmd
exploring scale entropy measures

@@
 setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
+library(tidyr)
 source("../analysis/useful_dplyr.R")
+library(dplyr)
 library(rjson)
@@
 library(jsonlite)
-library(tidyr)
+
 ```
@@
 
-d <- d1 %>% 
+d = d1 %>% 
   gather(base, alt, 
@@
 Conversely, scales such as `memorable_unforgettable` and `palatable_delicious` have a much longer tail of possible alternatives, with less cleary defined top competitors.
+
+```{r}
+
+pers = d[d$scale == "good_excellent", ]$n / sum(d[d$scale == "good_excellent", ]$n)
+H.ge = -sum(pers * log2(pers))
+pers = d[d$scale == "liked_loved", ]$n / sum(d[d$scale == "liked_loved", ]$n)
+H.ll = -sum(pers * log2(pers))
+pers = d[d$scale == "memorable_unforgettable", ]$n / sum(d[d$scale == "memorable_unforgettable", ]$n)
+H.mu = -sum(pers * log2(pers))
+pers = d[d$scale == "some_all", ]$n / sum(d[d$scale == "some_all", ]$n)
+H.sa = -sum(pers * log2(pers))
+pers = d[d$scale == "palatable_delicious", ]$n / sum(d[d$scale == "palatable_delicious", ]$n)
+H.pd = -sum(pers * log2(pers))
+
+H.ge
+H.ll
+H.mu
+H.sa
+H.pd
+
+```
 

### 2015-11-28 models/RSA+AmbiguousSemantics.Rmd
entropy measures for scales

@@
 
-H.ge
-H.ll
-H.mu
-H.sa
-H.pd
+scales.entropy = data.frame(c("good_excellent",
+                              "liked_loved",
+                              "memorable_unforgettable",
+                              "palatable_delicious",
+                              "some_all"),
+                            c(H.ge, H.ll, H.mu, H.pd, H.sa))
+colnames(scales.entropy) = c("scale", "Entropy")
 
+# Output to excel
+# write.csv(scales.entropy, "model_data/scales_entorpy.csv", row.names=FALSE)
 ```

### 2015-11-28 models/Model_Comparison.Rmd
added scale entropy data, not really using

@@
 run.full = function(d, alpha=1, useprior=F, usenone=F, addMid=F, normalize=F) {
+  # alpha = scales.entropy[scales.entropy$scale==d$scale[1], ]$Entropy
   if (addMid) {
@@
 priors = unif.priors
+
+scales.entropy = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/scales_entropy.csv")
 ```

### 2015-11-29 models/Model_additionalAlts.Rmd
exploring different subjective alts for liked_loved

@@
   group_by(scale)
+
+data.full$entropy = scales.entropy[data.full$scale, ]$Entropy
 ```
@@
 
-Focus on `good_excellent`:
+Focus on single scalar fn()
 ```{r}
@@
     m1 = ge.subset %>%
-      do(run.full(., alpha = 8, addMid = T, normalize=normalize))
+      do(run.full(., alpha = 1,
+                  addMid = T, normalize=normalize))
     if (target == "some_all") {
@@
 
-  i = which(cors == max(cors))
+  i = which(cors == max(cors))[1]
   # combos[i]
@@
   m1 = ge.subset %>%
-    do(run.full(., alpha = 8, addMid = T))
+    do(run.full(., alpha = 1, addMid = T))
 
@@
     geom_line(aes(y = pred), lty = 4)
-  return(combos[i])
+  return(c(combos[i], cors[i]))
 }
 
+combos = data.frame(c(0, 0, 1, 0, 0),
+                    c(0, 0.05, 1, .05, 0),
+                    c(0, 0.1, 1, .1, 0),
+                    c(0.05, 0.1, 1, .1, 0.05),
+                    c(0.1, 0.1, 1, .1, 0.1))  
+focus_alts("liked_loved", combos=combos)
+colnames(combos) = LETTERS[1:length(colnames(combos))]
 focus_alts("good_excellent", combos=NULL)
-focus_alts("liked_loved", combos=NULL)
+
 combos = data.frame(c(0, 1, 0, 0, 0),

### 2015-11-29 analysis/exp_data_clean.Rmd
created e10 data set with laplace smoothing (added one to each literal listener condition)

@@
 # write.csv(ms, "../models/L0_e10.csv", row.names=FALSE)
+```
+
+### Smoothing for e10
+```{r}
+NUM_ITEMS = 5
+ms.smoothing = d %>%
+  mutate(stars = as.numeric(as.character(stars))/20) %>%
+  group_by(scale, degree, stars) %>%
+  summarise(cil = ci.low(judgment), 
+            cih = ci.high(judgment), 
+            cnt.judgment = sum(judgment) + 1,
+            speaker.p2 = cnt.judgment / (n() + 1),
+            speaker.p = mean(judgment))
+ms.smoothing
+
+write.csv(ms, "../models/model_data/L0_e10_laplace.csv", row.names=FALSE)
 ```

### 2015-11-29 models/Model_Comparison.Rmd
alpha tuning with e6 or e11 toggle implemented

@@
     }
-    # Fit to e6 data
+    # Toggle fit to e6 data
     if (!is.null(compare.data)) {
+
+      # If we're using e11 data with multiple scalars
+      if ("hi1" %in% md$degree) {
         matched.items = which((md[, "scale"] != "some_all" &
@@
         stopifnot("listener.p" %in% colnames(compare.data))
+      }
       md$listener.p = compare.data$listener.p
@@
 performance.output = data.frame(model=rep(NA, 16),
-                                cor=rep(NA, 16),
+                                cor.e6=rep(NA, 16),
+                                cor.e11=rep(NA, 16),
                                 normalized=rep(NA, 16))
 alphas = rep(NA, 16)
-
+data.full.transfer = data.full[matched.items, ]
+data.full.transfer$degree =
+  ifelse(data.full.transfer$degree == "hi1", "hi", "low")
 # Model 1 - Entailment only models
@@
   do(run.partial(., alpha = alphas[1], useprior=T, usenone=F, normalize=T))
-# Store output
-performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5), T)
+# Store output and add e11
+m1.a = cbind(m1.a, data.full.transfer$listener.p)
+colnames(m1.a)[8] = "e11.listener.p"
+performance.output[1, ] = c("m1.a", round(cor(m1.a$listener.p, m1.a$pred), 5),
+                            round(cor(m1.a$e11.listener.p, m1.a$pred), 5), T)
 # Store plot
@@
 # Store output
-performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5), F)
+m1.b = cbind(m1.b, data.full.transfer$listener.p)
+colnames(m1.b)[8] = "e11.listener.p"
+performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5),
+                            round(cor(m1.b$e11.listener.p, m1.b$pred), 5), T)
 # Store plot
@@
 # alpha tune = T
-alphas[3] = tune.alpha(data.partial, normalize=T)
+alphas[3] = tune.alpha(data.partial, normalize=T, compare.data=data.full.transfer)
 m1.c = data.partial %>%
@@
 # Store output
-performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5), normalized=T)
+m1.c = cbind(m1.c, data.full.transfer$listener.p)
+colnames(m1.c)[8] = "e11.listener.p"
+performance.output[3, ] = c("m1.c", round(cor(m1.c$listener.p, m1.c$pred), 5),
+                            round(cor(m1.c$e11.listener.p, m1.c$pred), 5), T)
 # Store plot
@@
 # Store output
-performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5), normalized=F)
+m1.d = cbind(m1.d, data.full.transfer$listener.p)
+colnames(m1.d)[8] = "e11.listener.p"
+performance.output[4, ] = c("m1.d", round(cor(m1.d$listener.p, m1.d$pred), 5),
+                            round(cor(m1.d$e11.listener.p, m1.d$pred), 5), normalized=F)
 # Store plot
@@
 # Store output
-performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5), T)
+m2.a = cbind(m2.a, data.full.transfer$listener.p)
+colnames(m2.a)[8] = "e11.listener.p"
+performance.output[5, ] = c("m2.a", round(cor(m2.a$listener.p, m2.a$pred), 5),
+                            round(cor(m2.a$e11.listener.p, m2.a$pred), 5), T)
 # Store plot
@@
 # Store output
-performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5), F)
+m2.b = cbind(m2.b, data.full.transfer$listener.p)
+colnames(m2.b)[8] = "e11.listener.p"
+performance.output[6, ] = c("m2.b", round(cor(m2.b$listener.p, m2.b$pred), 5),
+                            round(cor(m2.b$e11.listener.p, m2.b$pred), 5), F)
 # Store plot
@@
 # alpha tune = T
-alphas[7] = tune.alpha(data.partial, normalize=T)
+# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
+alphas[7] = tune.alpha(data.partial, normalize=T, compare.data=NULL)
 m2.c = data.partial %>%
@@
 # Store output
-performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5), normalized=T)
+m2.c = cbind(m2.c, data.full.transfer$listener.p)
+colnames(m2.c)[8] = "e11.listener.p"
+performance.output[7, ] = c("m2.c", round(cor(m2.c$listener.p, m2.c$pred), 5),
+                            round(cor(m2.c$e11.listener.p, m2.c$pred), 5), T)
 # Store plot
@@
 # alpha tune = T
+# compare.data = Toggle this with data.full.transfer for e11 or NULL for e6
 alphas[8] = tune.alpha(data.partial, normalize=F)
@@
 # Store output
-performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5), normalized=F)
+m2.d = cbind(m2.d, data.full.transfer$listener.p)
+colnames(m2.d)[8] = "e11.listener.p"
+performance.output[8, ] = c("m2.d", round(cor(m2.d$listener.p, m2.d$pred), 5),
+                            round(cor(m2.d$e11.listener.p, m2.d$pred), 5), F)
 # Store plot
@@
 # Store output
-performance.output[9, ] = c("m3.a", round(cor(m3.a.matched$e6.listener.p, m3.a.matched$pred), 5), T)
+performance.output[9, ] = c("m3.a", round(cor(m3.a.matched$e6.listener.p, m3.a.matched$pred), 5),
+                            round(cor(m3.a.matched$listener.p, m3.a.matched$pred), 5), T)
 # Store plot
@@
 # Store output
-performance.output[10, ] = c("m3.b", round(cor(m3.b.matched$e6.listener.p, m3.b.matched$pred), 5), F)
+performance.output[10, ] = c("m3.b", round(cor(m3.b.matched$e6.listener.p, m3.b.matched$pred), 5),
+                             round(cor(m3.b.matched$listener.p, m3.b.matched$pred), 5), F)
 # Store plot
@@
 # alpha tune = T
+# compare.data = Toggle this with data.partial for e6 or NULL for e11
 alphas[11] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=T)
@@
 # Store output
-performance.output[11, ] = c("m3.c", round(cor(m3.c.matched$e6.listener.p, m3.c.matched$pred), 5), T)
+performance.output[11, ] = c("m3.c", round(cor(m3.c.matched$e6.listener.p, m3.c.matched$pred), 5),
+                             round(cor(m3.c.matched$listener.p, m3.c.matched$pred), 5), T)
 # Store plot
@@
       ylab="Posterior p(rating | word)") +
+      ylim(0, 1) +
   facet_wrap(~scale) + 
@@
 # alpha tune = T
+# compare.data = Toggle this with data.partial or NULL
 alphas[12] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
@@
 # Store output
-performance.output[12, ] = c("m3.d", round(cor(m3.d.matched$e6.listener.p, m3.d.matched$pred), 5), F)
+performance.output[12, ] = c("m3.d", round(cor(m3.d.matched$e6.listener.p, m3.d.matched$pred), 5),
+                             round(cor(m3.d.matched$listener.p, m3.d.matched$pred), 5), F)
 # Store plot
@@
 # Store output
-performance.output[13, ] = c("m4.a", round(cor(m4.a.matched$e6.listener.p, m4.a.matched$pred), 5), T)
+performance.output[13, ] = c("m4.a", round(cor(m4.a.matched$e6.listener.p, m4.a.matched$pred), 5), 
+                             round(cor(m4.a.matched$listener.p, m4.a.matched$pred), 5), T)
 # Store plot
@@
 # Store output
-performance.output[14, ] = c("m4.b", round(cor(m4.b.matched$e6.listener.p, m4.b.matched$pred), 5), F)
+performance.output[14, ] = c("m4.b", round(cor(m4.b.matched$e6.listener.p, m4.b.matched$pred), 5), 
+                             round(cor(m4.b.matched$listener.p, m4.b.matched$pred), 5), F)
 # Store plot
@@
 # alpha tune = T
+# compare.data = Toggle this with data.partial or NULL
 alphas[15] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=T)
@@
 colnames(m4.c.matched)[length(colnames(m4.c.matched))] = "e6.listener.p"
-# Store output
-performance.output[15, ] = c("m4.c", round(cor(m4.c.matched$e6.listener.p, m4.c.matched$pred), 5), T)
+# Store output (e11 and e6)
+performance.output[15, ] = c("m4.c", round(cor(m4.c.matched$e6.listener.p, m4.c.matched$pred), 5),
+                             round(cor(m4.c.matched$listener.p, m4.c.matched$pred), 5), T)
+
 # Store plot
-m4.c.plot = qplot(stars, e6.listener.p, col=degree, 
+m4.c.plot = qplot(stars, listener.p, col=degree, 
       data=m4.c.matched,
@@
 # alpha tune = T
+# compare.data = Toggle this with data.partial or NULL
 alphas[16] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=F)
@@
 # Store output
-performance.output[16, ] = c("m4.d", round(cor(m4.d.matched$e6.listener.p, m4.d.matched$pred), 5), F)
+performance.output[16, ] = c("m4.d", round(cor(m4.d.matched$e6.listener.p, m4.d.matched$pred), 5),
+                             round(cor(m4.d.matched$listener.p, m4.d.matched$pred), 5), F)
 # Store plot

### 2015-11-29 models/Model_Comparison.Rmd
starting write-up for model comparisons

@@
       data=m1.a,
-      main=paste("m1.a\nalpha: ", alphas[1], "\nNormalized = ", T),
+      main=paste("m1.a\nalpha: ", alphas[1],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[1, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
 performance.output[2, ] = c("m1.b", round(cor(m1.b$listener.p, m1.b$pred), 5),
-                            round(cor(m1.b$e11.listener.p, m1.b$pred), 5), T)
+                            round(cor(m1.b$e11.listener.p, m1.b$pred), 5), F)
 # Store plot
@@
       data=m1.b,
-      main=paste("m1.b\nalpha: ", alphas[2], "\nNormalized = ", F),
+      main=paste("m1.b\nalpha: ", alphas[2],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[2, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m1.c,
-      main=paste("m1.c\nalpha: ", alphas[3], "\nNormalized = ", T),
+      main=paste("m1.c\nalpha: ", alphas[3],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[3, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m1.d,
-      main=paste("m1.d\nalpha: ", alphas[4], "\nNormalized = ", F),
+      main=paste("m1.d\nalpha: ", alphas[4],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[4, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m2.a,
-      main=paste("m2.a\nalpha: ", alphas[5], "\nNormalized = ", T),
+      main=paste("m2.a\nalpha: ", alphas[5],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[5, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m2.b,
-      main=paste("m2.b\nalpha: ", alphas[6], "\nNormalized = ", F),
+      main=paste("m2.b\nalpha: ", alphas[6],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[6, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m2.c,
-      main=paste("m2.c\nalpha: ", alphas[7], "\nNormalized = ", T),
+      main=paste("m2.c\nalpha: ", alphas[7],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[7, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m2.d,
-      main=paste("m2.d\nalpha: ", alphas[8], "\nNormalized = ", F),
+      main=paste("m2.d\nalpha: ", alphas[8],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[8, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m3.a.matched,
-      main=paste("m3.a\nalpha: ", alphas[9], "\nNormalized = ", T),
+      main=paste("m3.a\nalpha: ", alphas[9],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[9, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m3.b.matched,
-      main=paste("m3.b\nalpha: ", alphas[10], "\nNormalized = ", F),
+      main=paste("m3.b\nalpha: ", alphas[10],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[10, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m3.c.matched,
-      main=paste("m3.c\nalpha: ", alphas[11], "\nNormalized = ", T),
+      main=paste("m3.c\nalpha: ", alphas[11],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[11, 2]),
       ylab="Posterior p(rating | word)") +
@@
       data=m3.d.matched,
-      main=paste("m3.d\nalpha: ", alphas[12], "\nNormalized = ", F),
+      main=paste("m3.d\nalpha: ", alphas[12],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[12, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m4.a.matched,
-      main=paste("m4.a\nalpha: ", alphas[13], "\nNormalized = ", T),
+      main=paste("m4.a\nalpha: ", alphas[13],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[13, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m4.b.matched,
-      main=paste("m4.b\nalpha: ", alphas[14], "\nNormalized = ", F),
+      main=paste("m4.b\nalpha: ", alphas[14],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[14, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m4.c.matched,
-      main=paste("m4.c\nalpha: ", alphas[15], "\nNormalized = ", T),
+      main=paste("m4.c\nalpha: ", alphas[15],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[15, 2]),
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
   facet_wrap(~scale) + 
@@
       data=m4.d.matched,
-      main=paste("m4.d\nalpha: ", alphas[16], "\nNormalized = ", F),
+      main=paste("m4.d\nalpha: ", alphas[16],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[16, 2]),
       ylab="Posterior p(rating | word)") +
+  ylim(0, 1) +
   facet_wrap(~scale) + 
   geom_line(aes(y = pred), lty = 4)
-
-# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
-# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
-# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
-# -- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^---- ^^^^^^^^^^--
-
-# Model 3 - Full, alpha tuning
-# ----------------------------
-# alphas[6] = tune.alpha(data.full, type = "full", compare.data=data.partial, addMid=F, normalize=F)
-# m3.fit = data.full %>%
-#   do(run.full(., alpha = alphas[6]))
-# m3.fit.matched = m3.fit[matched.items, ]
-# m3.fit.matched$degree = ifelse(m3.fit.matched$degree == "hi1", "hi", "low")
-# m3.fit.matched = cbind(m3.fit.matched, data.partial$listener.p)
-# # Check that everything lines up between partial and full
-# all(m3.fit.matched$scale == data.partial$scale & m3.fit.matched$degree == data.partial$degree)
-# colnames(m3.fit.matched)[length(colnames(m3.fit.matched))] = "e6.listener.p"
-# performance.output[6, ] = c("M3_fit", round(cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred), 5))
-# 
-# # Model 4 - Full, no alpha tuning
-# # -------------------------------
-# alphas[7] = 1
-# m4.noFit = data.full.extras %>%
-#   do(run.full(., alpha = alphas[7], addMid=T, normalize=T))
-# m4.noFit.matched = m4.noFit[matched.items.extras, ]
-# # Need to fix this to dealt with 'mid'
-# m4.noFit.matched$degree = ifelse(m4.noFit.matched$degree == "hi1", "hi", "low")
-# m4.noFit.matched = cbind(m4.noFit.matched, data.partial$listener.p)
-# # Check that everything lines up between partial and full
-# all(m4.noFit.matched$scale == data.partial$scale & m4.noFit.matched$degree == data.partial$degree)
-# colnames(m4.noFit.matched)[length(colnames(m4.noFit.matched))] = "e6.listener.p"
-# # store corr
-# performance.output[7, ] = c("M4_noFit", round(cor(m4.noFit.matched$e6.listener.p, m4.noFit.matched$pred), 5))
-# 
-# # Model 4 - Full, alpha tuning, added 'mid'
-# # ----------------------------
-# alphas[8] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T)
-# m4.fit = data.full.extras %>%
-#   do(run.full(., alpha = alphas[8], addMid=T))
-# m4.fit.matched = m4.fit[matched.items.extras, ]
-# m4.fit.matched$degree = ifelse(m4.fit.matched$degree == "hi1", "hi", "low")
-# m4.fit.matched = cbind(m4.fit.matched, data.partial$listener.p)
-# # Check that everything lines up between partial and full
-# all(m4.fit.matched$scale == data.partial$scale & m4.fit.matched$degree == data.partial$degree)
-# colnames(m4.fit.matched)[length(colnames(m4.fit.matched))] = "e6.listener.p"
-# # store corr
-# performance.output[8, ] = c("M4_fit", round(cor(m4.fit.matched$e6.listener.p, m4.fit.matched$pred), 5))
 ```
@@
 
-Overall model performance: $r^2$.
-M1 and M2 use literal listener values from exp8.
-M2 includes a generic "None" defined in terms of stars (1: 1.0, 2:0.0, 3:0.0, 4:0.0, 5:0.0).
-M3 uses the full set of literal listener alternatives from exp10, however r^2 values and tuning reflects comparisons to exp6 pragmatic listener judgments (not exp11).
+## Interpreting the output table:
+
+`m1:` Entailment only models (i.e. "some_all" scale only includes "some", "all")
+
+`m2:` Entailment + generic None models (i.e. "some_all" scale includes "some", "all", "none")
+
+`m3:` Full model with empirical alternatives (i.e. "some_all" scale includes "some", "all", "most", "none")
+
+`m4:` Entailment + empirical alternatives + additional fitted scalar (i.e. "some_all" scale includes "some", "all", "most", "none", "mid")
+
+`a:` Normalized literal listener values before running RSA, no alpha tuning
+
+`b:` No normalization for literal listener values before running RSA, no alpha tuning
+
+`c:` Normalized literal listener values before running RSA, alpha tuning
+
+`d:` No normalization for literal listener values before running RSA, alpha tuning
+
+Initial thoughts:
+
+We see fairly steady model improvement with the addition of salient alternatives.
+Let's focus on the normalized family of models (1a, 1c, ...
+, 4a, 4c) - I explain why this might be a good idea below, but I'm not totally convinced.
+Probably the most important comparisons to pay attention to is the jump in correlation values when we first introduce empirically derived alternatives (models m3).
+Comparing m2 models (entailment + generic None) and m3 models (empirically derived alternatives) we see jumps of +0.23 for r values with alpha tuning.
+See the plots below:
+```{r}
+m2.c.plot
+m3.c.plot
+```
+Importantly, we also see improvements with the addition of 'fitted' alternatives in m4 see the plots below:
+```{r}
+m3.c.plot
+m4.c.plot
+```
+
+Additional notes:
+
+1) In general model performance is greater (correlation) for e11 data.
+This may be due in part to less extreme literal listener evaluations in e11 (see RSA+AmbiguousSemantics for a more detailed analysis for literal listener experiment differences).
+Our best model performance occurs with e11 and the model is m4.c, correlation = `r round(performance.outpu[15, 3], 5)`.
+
+2) Non-normalized models seem to be more sensitive to alpha tuning as the number of alternatives increases (see m4.d and m3.d with alpha = 8).
+I'm inclined to stick with normalized model results because of this - we're interested in whether we see model improvement from the addition of salient alternatives - not from tuning hyperparameters.
+We tend to see more model improvement with alternatives when we're looking at normalized models (see `m3.c` vs `m4.c`).
+
+3) We may want to explore the the idea of unique alphas for a given scale (would need to change how we've written RSA), for example using scale entropy measures.
 ```{r overall_perf}
@@
 m4.d.plot
-# performance.output$model = factor(performance.output$model, levels=c(
-#   "M1_noFit", "M1_fit", "M2_noFit", "M2_fit", "M3_noFit", "M3_fit", "M4_noFit", "M4_fit"
-# ))
-# # Populate extra model info
-# performance.output$cor = as.numeric(performance.output$cor)
-# performance.output$alphas = alphas
-# performance.output$alts = c(rep("entailment only", 2), rep("entailment + None", 2), rep("full", 2), rep("full + extras", 2))
-# grid.table(performance.output)
-# 
-# qplot(data=performance.output, x=model, y=performance.output$cor,
-#       geom="bar", stat="identity",
-#       main = "Model performance", ylab="r^2", xlab="model") +
-#   geom_text(aes(label = round(cor, 3), y = cor + 0.02), size = 3) +
-#   scale_y_continuous(limits=c(0, 1))
-```
-
-## Individual model performance
-```{r individual_plots}
-# m1.noFit.G = qplot(stars, listener.p, col=degree, 
-#       data=m1.noFit,
-#       main=paste("M1, no fit\nalpha: ", alphas[1]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# # m1.noFit.G
-# 
-# m1.fit.G = qplot(stars, listener.p, col=degree, 
-#       data=m1.fit,
-#       main=paste("M1, fit\nalpha: ", alphas[2]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m1.fit.G
-# 
-# m2.noFit.G = qplot(stars, listener.p, col=degree, 
-#       data=m2.noFit,
-#       main=paste("M2, no fit\nalpha: ", alphas[3]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m2.noFit.G
-# 
-# m2.fit.G = qplot(stars, listener.p, col=degree, 
-#       data=m2.fit,
-#       main=paste("M2, fit\nalpha: ", alphas[4]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m2.fit.G
-# 
-# m3.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-#       data=m3.noFit.matched,
-#       main=paste("M3, no fit\nalpha: ", alphas[5]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m3.matched.noFit.G
-# cor(m3.noFit.matched$e6.listener.p, m3.noFit.matched$pred)
-# 
-# m3.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-#       data=m3.fit.matched,
-#       main=paste("M3, fit\nalpha: ", alphas[6]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m3.matched.fit.G
-# cor(m3.fit.matched$e6.listener.p, m3.fit.matched$pred)
-# 
-# # Full model fitted - color scale
-# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-#   geom_point(aes(colour = scale)) +
-#   geom_smooth(method=lm) +
-#   ggtitle("Model performance: M3 fit") +
-#   labs(x = "human judgments", y="model prediction")
-# m3.matched.fit.CorPlot
-# 
-# # Full model fitted - color stars
-# m3.matched.fit.CorPlot = ggplot(data=m3.fit.matched, aes(y=pred, x=e6.listener.p)) +
-#   geom_point(aes(colour = stars)) +
-#   geom_smooth(method=lm) +
-#   ggtitle("Model performance: M3 fit") +
-#   labs(x = "human judgments", y="model prediction")
-# m3.matched.fit.CorPlot
-# 
-# m4.matched.noFit.G = qplot(stars, e6.listener.p, col=degree, 
-#       data=m4.noFit.matched,
-#       main=paste("M4, no fit\nalpha: ", alphas[7]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m4.matched.noFit.G
-# 
-# m4.matched.fit.G = qplot(stars, e6.listener.p, col=degree, 
-#       data=m4.fit.matched,
-#       main=paste("M4, fit\nalpha: ", alphas[8]),
-#       ylab="Posterior p(rating | word)") + 
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = pred), lty = 4)
-# m4.matched.fit.G
 ```

### 2015-11-29 models/Model_Comparison.Rmd
plots with both e6 and e11 data for comparison - plot with combined prag listener judgments?

@@
                              round(cor(m3.c.matched$listener.p, m3.c.matched$pred), 5), T)
-# Store plot
+# Store plot 1
 m3.c.plot = qplot(stars, e6.listener.p, col=degree, 
@@
       ylab="Posterior p(rating | word)") +
+      ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# Store plot 2 - both e6 and e11 data
+m3.c.jointPlot = m3.c.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m3.c.jointPlot$study = ifelse(m3.c.jointPlot$study == "e6.listener.p", "e6", "e11")
+qplot(stars, listener.pred, col=degree, shape=study,
+      data=m3.c.jointPlot,
+      main=paste("m3.c\nalpha: ", alphas[11],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# Store plot 2 - both e6 and e11 data
+m3.d.jointPlot = m3.d.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m3.d.jointPlot$study = ifelse(m3.d.jointPlot$study == "e6.listener.p", "e6", "e11")
+qplot(stars, listener.pred, col=degree, shape=study,
+      data=m3.d.jointPlot,
+      main=paste("m3.d\nalpha: ", alphas[12],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
 # Store plot
-m4.c.plot = qplot(stars, listener.p, col=degree, 
+m4.c.plot = qplot(stars, e6.listener.p, col=degree, 
       data=m4.c.matched,
@@
       ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# Store plot 2 - both e6 and e11 data
+m4.c.jointPlot = m4.c.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m4.c.jointPlot$study = ifelse(m4.c.jointPlot$study == "e6.listener.p", "e6", "e11")
+qplot(stars, listener.pred, col=degree, shape=study,
+      data=m4.c.jointPlot,
+      main=paste("m4.c\nalpha: ", alphas[15],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
   geom_line(aes(y = pred), lty = 4)
+
+# Store plot 2 - both e6 and e11 data
+m4.d.jointPlot = m4.d.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m4.d.jointPlot$study = ifelse(m4.d.jointPlot$study == "e6.listener.p", "e6", "e11")
+qplot(stars, listener.pred, col=degree, shape=study,
+      data=m4.d.jointPlot,
+      main=paste("m4.d\nalpha: ", alphas[16],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
 ```
 
-# Plots
+# Discussion
 
@@
 
-`m2:` Entailment + generic None models (i.e. "some_all" scale includes "some", "all", "none")
+`m2:` Entailment + generic None models (i.e. "some_all" scale includes "none", "some", "all")
 
-`m3:` Full model with empirical alternatives (i.e. "some_all" scale includes "some", "all", "most", "none")
+`m3:` Full model with empirical alternatives (i.e. "some_all" scale includes "none", "some", "most", all")
 
-`m4:` Entailment + empirical alternatives + additional fitted scalar (i.e. "some_all" scale includes "some", "all", "most", "none", "mid")
+`m4:` Entailment + empirical alternatives + additional fitted scalar (i.e. "some_all" scale includes "none", "some", "mid", "most", all")
 
@@
 
-Initial thoughts:
+```{r}
+performance.output$cor.e6 = as.numeric(performance.output$cor.e6)
+performance.output$cor.e11 = as.numeric(performance.output$cor.e11)
+performance.output = performance.output %>%
+  mutate(avg.corr =
+           (cor.e6 + cor.e11) / 2)
+performance.output = cbind(performance.output, alphas)
+# reorder columns
+performance.output = performance.output[, c(1, 2, 3, 5, 4, 6)]
+grid.table(performance.output)
+```
 
-We see fairly steady model improvement with the addition of salient alternatives.
-Let's focus on the normalized family of models (1a, 1c, ...
-, 4a, 4c) - I explain why this might be a good idea below, but I'm not totally convinced.
-Probably the most important comparisons to pay attention to is the jump in correlation values when we first introduce empirically derived alternatives (models m3).
-Comparing m2 models (entailment + generic None) and m3 models (empirically derived alternatives) we see jumps of +0.23 for r values with alpha tuning.
-See the plots below:
+## Initial thoughts:
+
+### Overall
+
+Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives.
+The largest improvement in model fit occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
+Have a look at the `m2` vs `m3` correlation for models with pre-RSA normalization below (`c` models):
+```{r}
+# Tuned, normalized models r
+barchart.d = performance.output[c(3, 7, 11, 15), ] %>%
+  gather(study, cor, cor.e6, cor.e11)
+ggplot(barchart.d, aes(x=model, y=cor, fill=study)) + 
+  geom_bar(stat="identity", position="dodge") +
+  ylim(0, 1) + 
+  ggtitle("Model fit for e6 and e11\npragmatic listener judgments")
+  # geom_text(aes(x=model, y=as.numeric(cor) + 0.025, label=round(cor, 3)))
+```
+
+In particular, we first start to see a pretty
+
 ```{r}
@@
 ```
+
 Importantly, we also see improvements with the addition of 'fitted' alternatives in m4 see the plots below:
@@
 
-Additional notes:
+This improvement is particularly clear when we look at e11 data:
+```{r}
+qplot(stars, listener.p, col=degree, 
+      data=m3.c.matched,
+      main=paste("m4.c\nalpha: ", alphas[11],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[11, 3]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+qplot(stars, listener.p, col=degree, 
+      data=m4.c.matched,
+      main=paste("m4.c\nalpha: ", alphas[15],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[15, 3]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+```
+
+## Additional notes:
 
 1) In general model performance is greater (correlation) for e11 data.
-This may be due in part to less extreme literal listener evaluations in e11 (see RSA+AmbiguousSemantics for a more detailed analysis for literal listener experiment differences).
-Our best model performance occurs with e11 and the model is m4.c, correlation = `r round(performance.outpu[15, 3], 5)`.
+This may be due in part to less extreme literal listener evaluations in e11 (see `RSA+AmbiguousSemantics.Rmd` for a more detailed analysis for literal listener experiment differences).
+Our best model performance occurs with e11 and the model is m4.c, correlation = `r as.numeric(performance.output[15, 3])` (see plot below):
+```{r}
+qplot(stars, listener.p, col=degree, 
+      data=m4.c.matched,
+      main=paste("m4.c\nalpha: ", alphas[15],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[15, 3]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+```
 
@@
 3) We may want to explore the the idea of unique alphas for a given scale (would need to change how we've written RSA), for example using scale entropy measures.
+
+# All plots
 ```{r overall_perf}
-performance.output = cbind(performance.output, alphas)
-grid.table(performance.output)
-
 m1.a.plot

### 2015-11-30 models/Model_additionalAlts.Rmd
good_excellent and liked_loved performing better with strange distr - is this an indicator that we need more than one 'mid' extra scalar? Maybe this is a sign that we need multiple - could this be tied to scale family entropy?

@@
 ```{r}
-focus_alts = function(target, combos, normalize=F) {
+# focus_alts
+# ---------
+# target    --> specific scalar family we're interested in (i.e. "some_all")
+# combos    --> collection of possible 'mid' l0 distribution
+# normalize --> normaize pre RSA?
+# alpha     --> set alpha level
+focus_alts = function(target, combos, normalize=F, alpha=1) {
+  # Default normalish looking distr
   if (is.null(combos)) {
@@
   colnames(combos) = LETTERS[1:length(colnames(combos))]
+
+  # Find best distribution
   cors = c()
@@
     target.scalars = c("hi1", "hi2")
-    # Run model)
+
+    # Run model
     m1 = ge.subset %>%
-      do(run.full(., alpha = 1,
-                  addMid = T, normalize=normalize))
+      do(run.full(., alpha = alpha, addMid=T, normalize=normalize))
     if (target == "some_all") {
@@
   }
-  cors
 
+  # Get index of highest correlation
   i = which(cors == max(cors))[1]
-  # combos[i]
   ge.subset = data.full.extras[data.full.extras$scale == target, ]
@@
   m1 = ge.subset %>%
-    do(run.full(., alpha = 1, addMid = T))
+    do(run.full(., alpha = alpha, addMid=T, normalize=normalize))
 
-  qplot(stars, listener.p, col=degree, 
+  p = qplot(stars, listener.p, col=degree, 
         data=m1,
@@
     geom_line(aes(y = pred), lty = 4)
+
   return(c(combos[i], cors[i]))
 }
+```
 
+```{r}
+# liked_loved
 combos = data.frame(c(0, 0, 1, 0, 0),
@@
                     c(0, 0.1, 1, .1, 0),
-                    c(0.05, 0.1, 1, .1, 0.05),
+                    c(0, 0.1, 0.9, .1, 0),
+                    c(0, 0.2, 0.8, .2, 0),
+                    c(0, 0.25, 0.8, .25, 0),
+                    c(0.05, 0.1, 1, .1, 0.9),
                     c(0.1, 0.1, 1, .1, 0.1))  
-focus_alts("liked_loved", combos=combos)
-colnames(combos) = LETTERS[1:length(colnames(combos))]
-focus_alts("good_excellent", combos=NULL)
+focus_alts("liked_loved", combos=combos, alpha=4, normalize=T)
+focus_alts("liked_loved", combos=combos, alpha=8, normalize=F)
 
+# good_excellent
+combos = data.frame(c(0, 0, 1, 0, 0),
+                    c(0, 0.05, 0.9, 0.05, 0),
+                    c(0, 0.1, 0.8, 0.1, 0),
+                    c(0, 0.2, 0.6, 0.2, 0.9),
+                    c(0, 0.2, 0.6, 0.2, 1),
+                    c(0.05, 0.2, 0.6, 0.2, 0.05),
+                    c(0, 0.25, 0.5, 0.25, 0))  
+focus_alts("good_excellent", combos=combos, alpha = 4, normalize=T)
+focus_alts("good_excellent", combos=combos, alpha = 8, normalize=F)
+
+# some_all
 combos = data.frame(c(0, 1, 0, 0, 0),
-                    c(0.05, 0.9, 0.05, 0, 0),
+                    c(0.05, 2, 0.05, 0.05, 0.05),
                     c(0.1, 0.8, 0.1, 0, 0),
@@
                     c(0.25, 0.5, 0.25, 0, 0))
-focus_alts("some_all", combos=combos)
+focus_alts("some_all", combos=combos, alpha=4, normalize=T)
+focus_alts("some_all", combos=combos, alpha=8, normalize=F)
+
+# memorable_unforgettable
+combos = data.frame(rep(0.1, 5),
+                    c(0.05, 2, 0.05, 0.05, 0.05),
+                    c(0.05, 1, 0.05, 0.05, 0.05),
+                    c(0.05, 0.9, 0.05, 0.05, 0.05),
+                    c(0.05, 0.8, 0.05, 0.05, 0.05),
+                    c(0.05, 0.7, 0.05, 0.05, 0.05),
+                    c(0.05, 0.6, 0.05, 0.05, 0.05),
+                    c(0.05, 0.5, 0.05, 0.05, 0.05),
+                    c(0.1, 0.8, 0.1, 0.1, 0.1))
+focus_alts("memorable_unforgettable", combos=combos, alpha=4, normalize=T)
+focus_alts("memorable_unforgettable", combos=combos, alpha=8, normalize=F)
+
+# palatable_delicious
+combos = data.frame(rep(0.1, 5),
+                    c(0.05, 2, 0.05, 0.05, 0.05),
+                    c(0.05, 1, 0.05, 0.05, 0.05),
+                    c(0.05, 0.05, 0.05, 0.9, 0.1),
+                    c(0.05, 0.8, 0.05, 0.9, 0.05),
+                    c(0.05, 0.7, 0.05, 0.9, 0.05),
+                    c(0.05, 0.6, 0.05, 0.05, 0.05),
+                    c(0.05, 0.5, 0.05, 0.05, 0.05),
+                    c(0.1, 0.8, 0.1, 0.1, 0.1))
+focus_alts("palatable_delicious", combos=combos, alpha=4, normalize=T)
+focus_alts("palatable_delicious", combos=combos, alpha=8, normalize=F)
 ```

### 2015-11-30 models/RSA+AmbiguousSemantics.Rmd
prag listener judgements distr differences

@@
 library(jsonlite)
-
 ```
@@
 
+```
+
+### Pragmatic Listener studies - judgement distributional differences
+```{r}
+e6.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+e11.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+match_scales = which((e11.d[, "scale"] != "some_all" &
+        (e11.d[, "degree"] == "hi2" | e11.d[, "degree"] == "hi1")) |
+       (e11.d[, "scale"] == "some_all" &
+          (e11.d[, "degree"] == "hi1" | e11.d[, "degree"] == "low1")))
+e11.d.mod = e11.d[match_scales,]
+e11.d.mod$degree = ifelse(e11.d.mod$degree == "hi1", "hi", "low")
+e11.d.mod = e11.d.mod %>%
+  select(degree, scale, stars, listener.p) %>%
+  mutate(exp = "e11")
+e6.d = e6.d %>% mutate(exp = "e6")
+combined.d = rbind(e6.d, e11.d.mod)
+
+ggplot(combined.d, aes(x=stars, y=listener.p, fill=exp)) +
+  geom_bar(stat="identity", position="dodge") +
+  facet_wrap(~scale+degree) +
+  ggtitle("e6 vs e11 prag listener judgements")
 ```

### 2015-11-30 models/RSA+AmbiguousSemantics.Rmd
prag listener distributional differences update

--- 2015-11-28 models/RSA+AmbiguousSemantics.Rmd
@@
     toc: yes
-    toc_depth: 2
+    toc_depth: 3
 ---
@@
 
+### Pragmatic Listener studies - judgement distributional differences
+```{r}
+e6.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+e11.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+match_scales = which((e11.d[, "scale"] != "some_all" &
+        (e11.d[, "degree"] == "hi2" | e11.d[, "degree"] == "hi1")) |
+       (e11.d[, "scale"] == "some_all" &
+          (e11.d[, "degree"] == "hi1" | e11.d[, "degree"] == "low1")))
+e11.d.mod = e11.d[match_scales,]
+e11.d.mod$degree = ifelse(e11.d.mod$degree == "hi1", "hi", "low")
+e11.d.mod = e11.d.mod %>%
+  dplyr::select(degree, scale, stars, listener.p) %>%
+  mutate(exp = "e11")
+e6.d = e6.d %>% mutate(exp = "e6")
+combined.d = rbind(e6.d, e11.d.mod)
+
+ggplot(combined.d, aes(x=stars, y=listener.p, fill=exp)) +
+  geom_bar(stat="identity", position="dodge") +
+  facet_wrap(~scale+degree) +
+  ggtitle("e6 vs e11 prag listener judgements")
+```
+
 ### Description

### 2015-11-30 models/Model_additionalAlts.Rmd
basic functionlity and output for subjective 'addtional' scalars - do the funky results for liked_lovedpalatable_delicious (when we have something like 0.1, 0.1, 0.5, 0.1, 0.9) suggest that we need more than one other additional scalar?

@@
 date: "November 25, 2015"
-output: html_document
+output:
+  html_document:
+    highlight: pygments
+    theme: flatly
+    toc: yes
+    toc_depth: 3
 ---
@@
                     c(0, 0.1, 0.8, 0.1, 0),
-                    c(0, 0.2, 0.6, 0.2, 0.9),
+                    c(0, 0.2, 0.2, 0.2, 0.9),
                     c(0, 0.2, 0.6, 0.2, 1),
+                    c(0, 0.2, 0.6, 0.3, 0.2),
+                    c(0, 0.2, 0.6, 0.3, 0.3),
+                    c(0, 0.2, 0.6, 0.5, 0.4),
+                    c(0, 0.2, 0.6, 0.5, 0.5),
+                    c(0, 0.2, 0.6, 0.6, 0.4),
                     c(0.05, 0.2, 0.6, 0.2, 0.05),
                     c(0, 0.25, 0.5, 0.25, 0))  
-focus_alts("good_excellent", combos=combos, alpha = 4, normalize=T)
+focus_alts("good_excellent", combos=combos, alpha = 1, normalize=T)
 focus_alts("good_excellent", combos=combos, alpha = 8, normalize=F)
@@
                     c(0.05, 2, 0.05, 0.05, 0.05),
+                    c(0.2, 0.9, 0.2, 0.1, 0.1),
+                    c(0.2, 0.9, 0.2, 0.1, 0),
+                    c(0.1, 0.9, 0.1, 0, 0),
                     c(0.1, 0.8, 0.1, 0, 0),
@@
                     c(0.05, 0.05, 0.05, 0.9, 0.1),
-                    c(0.05, 0.8, 0.05, 0.9, 0.05),
-                    c(0.05, 0.7, 0.05, 0.9, 0.05),
+                    c(0.05, 0.05, 0.05, 0.9, 0.05),
+                    c(0.05, 0.7, 0.05, 0.5, 0.05),
                     c(0.05, 0.6, 0.05, 0.05, 0.05),
@@
 ```
-
-Focus on `some_all`:
-```{r}
-ge.subset = data.full[data.full$scale == "some_all", ]
-ge.subset[ge.subset$degree == "mid", "speaker.p"] = c(0, 1, 0, 0, 0)
-head(ge.subset, n = 20)
-target.scalars = c("hi1", "low1")
-
-# Run model
-m1 = ge.subset %>%
-  do(run.full(., alpha = 8, addMid = T))
-cor(m1$pred, m1$listener.p)
-
-qplot(stars, listener.p, col=degree, 
-      data=m1,
-      ylab="Posterior p(rating | word)") + 
-  geom_line(aes(y = pred), lty = 4)
-
-m1 = m1[m1$degree %in% target.scalars, ]
-cor(m1$pred, m1$listener.p)
-
-combos = data.frame(c(0, 0, 1, 0, 0),
-                    c(0, 0.05, 0.9, 0.05, 0),
-                    c(0, 0.1, 0.8, 0.1, 0),
-                    c(0, 0.2, 0.6, 0.2, 0),
-                    c(0, 0.25, 0.5, 0.25, 0))
-colnames(combos) = LETTERS[1:length(colnames(combos))]
-cors = c()
-for (i in 1:ncol(combos)) {
-  print(i)
-  ge.subset = data.full[data.full$scale == "good_excellent", ]
-  ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
-  target.scalars = c("hi1", "hi2")
-  # Run model
-  m1 = ge.subset %>%
-    do(run.full(., alpha = 8, addMid = T))
-  m1 = m1[m1$degree %in% target.scalars, ]
-  cors[i] = cor(m1$pred, m1$listener.p)  
-}
-cors 
-```

### 2015-11-30 models/Model_Comparison.Rmd
Model comparisons with reference to RSA+AmbiguousSemantics.Rmd and Model_additionalAlts.Rmd

--- 2015-11-29 models/Model_Comparison.Rmd
@@
                              round(cor(m3.c.matched$listener.p, m3.c.matched$pred), 5), T)
-# Store plot
-m3.c.plot = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.c.matched,
+
+# Store plot 2 - both e6 and e11 data
+m3.c.jointD = m3.c.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m3.c.jointD$study = ifelse(m3.c.jointD$study == "e6.listener.p", "e6", "e11")
+m3.c.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m3.c.jointD,
       main=paste("m3.c\nalpha: ", alphas[11],
                  "\nNormalized = ", T,
-                 "\nCorr = ", performance.output[11, 2]),
-      ylab="Posterior p(rating | word)") +
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
                              round(cor(m3.d.matched$listener.p, m3.d.matched$pred), 5), F)
-# Store plot
-m3.d.plot = qplot(stars, e6.listener.p, col=degree, 
-      data=m3.d.matched,
+
+# Store plot 2 - both e6 and e11 data
+m3.d.jointD = m3.d.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m3.d.jointD$study = ifelse(m3.d.jointD$study == "e6.listener.p", "e6", "e11")
+m3.d.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m3.d.jointD,
       main=paste("m3.d\nalpha: ", alphas[12],
-                 "\nNormalized = ", F,
-                 "\nCorr = ", performance.output[12, 2]),
-      ylab="Posterior p(rating | word)") + 
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
 
-# Store plot
-m4.c.plot = qplot(stars, listener.p, col=degree, 
-      data=m4.c.matched,
+# Store plot 2 - both e6 and e11 data
+m4.c.jointD = m4.c.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m4.c.jointD$study = ifelse(m4.c.jointD$study == "e6.listener.p", "e6", "e11")
+m4.c.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m4.c.jointD,
       main=paste("m4.c\nalpha: ", alphas[15],
                  "\nNormalized = ", T,
-                 "\nCorr = ", performance.output[15, 2]),
-      ylab="Posterior p(rating | word)") + 
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
                              round(cor(m4.d.matched$listener.p, m4.d.matched$pred), 5), F)
-# Store plot
-m4.d.plot = qplot(stars, e6.listener.p, col=degree, 
-      data=m4.d.matched,
+
+# Store plot 2 - both e6 and e11 data
+m4.d.jointD = m4.d.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m4.d.jointD$study = ifelse(m4.d.jointD$study == "e6.listener.p", "e6", "e11")
+m4.d.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m4.d.jointD,
       main=paste("m4.d\nalpha: ", alphas[16],
-                 "\nNormalized = ", F,
-                 "\nCorr = ", performance.output[16, 2]),
-      ylab="Posterior p(rating | word)") +
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
   ylim(0, 1) +
@@
 
-# Plots
+# Discussion
 
@@
 
-Initial thoughts:
+```{r}
+performance.output$cor.e6 = as.numeric(performance.output$cor.e6)
+performance.output$cor.e11 = as.numeric(performance.output$cor.e11)
+performance.output = performance.output %>%
+  mutate(avg.corr =
+           (cor.e6 + cor.e11) / 2)
+performance.output = cbind(performance.output, alphas)
+# reorder columns
+performance.output = performance.output[, c(1, 2, 3, 5, 4, 6)]
+grid.table(performance.output)
+```
 
-We see fairly steady model improvement with the addition of salient alternatives.
-Let's focus on the normalized family of models (1a, 1c, ...
-, 4a, 4c) - I explain why this might be a good idea below, but I'm not totally convinced.
-Probably the most important comparisons to pay attention to is the jump in correlation values when we first introduce empirically derived alternatives (models m3).
-Comparing m2 models (entailment + generic None) and m3 models (empirically derived alternatives) we see jumps of +0.23 for r values with alpha tuning.
-See the plots below:
+## Initial thoughts:
+
+### Overall
+
+Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives.
+The largest improvement in model fit occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
+Have a look at the `m2` vs `m3` correlation for models with pre-RSA normalization below (`c` models):
+```{r}
+# Tuned, normalized models r
+barchart.d = performance.output[c(3, 7, 11, 15), ] %>%
+  gather(study, cor, cor.e6, cor.e11)
+barchart.d$cor = as.numeric(barchart.d$cor)
+ggplot(barchart.d, aes(x=model, y=cor, fill=study)) + 
+  geom_bar(stat="identity", position="dodge") +
+  ylim(0, 1) + 
+  ggtitle("Model fit for e6 and e11\npragmatic listener judgments") +
+  geom_text(aes(x=model, y=as.numeric(cor) + 0.025, label=round(cor, 3), col=(study)))
+```
+
+Here's another look at the improvement in model fit between normalized `m2` and `m3`.
 ```{r}
 m2.c.plot
-m3.c.plot
+m3.c.jointPlot
 ```
+
 Importantly, we also see improvements with the addition of 'fitted' alternatives in m4 see the plots below:
 ```{r}
-m3.c.plot
-m4.c.plot
+m3.c.jointPlot
+m4.c.jointPlot
 ```
 
-Additional notes:
+This presents a little bit more of a challenge, however, as we'd like to jointly fit our alpha as well as our alternatives - is this worth delving into?
+Currently we're just fitting alpha and then finding alternatives.
 
-1) In general model performance is greater (correlation) for e11 data.
-This may be due in part to less extreme literal listener evaluations in e11 (see RSA+AmbiguousSemantics for a more detailed analysis for literal listener experiment differences).
-Our best model performance occurs with e11 and the model is m4.c, correlation = `r round(performance.outpu[15, 3], 5)`.
+## Additional notes:
 
-2) Non-normalized models seem to be more sensitive to alpha tuning as the number of alternatives increases (see m4.d and m3.d with alpha = 8).
-I'm inclined to stick with normalized model results because of this - we're interested in whether we see model improvement from the addition of salient alternatives - not from tuning hyperparameters.
-We tend to see more model improvement with alternatives when we're looking at normalized models (see `m3.c` vs `m4.c`).
+1) In general model performance is greater (correlation) for e11 data. This may be due in part to less extreme literal listener evaluations in e11 see:
 
-3) We may want to explore the the idea of unique alphas for a given scale (would need to change how we've written RSA), for example using scale entropy measures.
+https://cdn.rawgit.com/langcog/scalar_implicature/master/models/RSA%2BAmbiguousSemantics.html#pragmatic-listener-studies---judgement-distributional-differences
+
+Our best model performance occurs with e11 and the model is m4.c, correlation = `r as.numeric(performance.output[15, 3])` (see plot below):
+```{r}
+qplot(stars, listener.p, col=degree, 
+      data=m4.c.matched,
+      main=paste("m4.c\nalpha: ", alphas[15],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[15, 3]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+```
+
+Normalizing vs not normalizing before running RSA:
+
+Non-normalized models seem to be more sensitive to alpha tuning as the number of alternatives increases (see m4.d and m3.d with alpha = 8).
+I'm not sure if there is a theoretical consideration here that RSA may want to address?
+What does it mean to normalize literal listener values prior to computing the posterior?
+One repercussion is that during normalization we'll see larger impact from salient alternatives...
+In `Model_addtionalAlts.Rmd` I'm seeing that higher entropy scales `memorable_unforgettable`, `palatable_delicious` appear to be looking for more alternatives (correlation improves when I add wacky distributions such as [0, 0.1, 0.9, 0.1, 0.9] which suggests that we need possibly *two* more alternatives, not just one).
+This seems intuitive in the higher entropy setting...
+Can we interpret this kind of finding (at least intuitively) as the model telling us it wants *more* alternatives?
+See
+
+https://cdn.rawgit.com/langcog/scalar_implicature/master/models/Model_additionalAlts.html#match-items-between-studies-full-and-partial
+
+# All plots with e6 prag judgements
 ```{r overall_perf}
-performance.output = cbind(performance.output, alphas)
-grid.table(performance.output)
-
 m1.a.plot
@@
 m3.b.plot
-m3.c.plot
-m3.d.plot
+m3.c.jointPlot
+m3.d.jointPlot
 
@@
 m4.b.plot
-m4.c.plot
-m4.d.plot
+m4.c.jointPlot
+m4.d.jointPlot
 ```

### 2015-12-01 models/Model_additionalAlts.Rmd
prelim code for simplified gradient descent for alternative dist tuning

@@
 ```{r}
+
 # liked_loved
@@
 ```
+
+Fit params - weight update fn()
+```{r}
+# fit_distr()
+# -----------
+# target        --> specific scalar family we're interested in (i.e. "some_all")
+# numIters      --> 
+# eta           --> 
+# normalize     --> 
+fit_distr = function(target, numIters = 100, eta=0.01,  normalize=F, alpha=1, verbose=F) {
+  # Initialize to uniform
+  w = rep(0.1, 5)
+  # Focus on scalar 'target'
+  scalar.focused = data.full.extras[data.full.extras$scale == target, ]
+  # Initialize 'mid' alternative
+
+  match.scalars = which(scalar.focused$degree == "hi1" | scalar.focused$degree == "hi2")
+
+  # For numIters iterations...
+  for (i in 1:numIters) {
+    scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = w
+    m = scalar.focused %>%
+      do(run.full(., alpha = alpha, addMid=T, normalize=normalize))
+    w[1] = w[1] - eta * (sum(m[m$stars == 1, ]$listener.p - m[m$stars == 1, ]$pred))
+    w[2] = w[2] - eta * (sum(m[m$stars == 2, ]$listener.p - m[m$stars == 2, ]$pred))
+    w[3] = w[3] - eta * (sum(m[m$stars == 3, ]$listener.p - m[m$stars == 3, ]$pred))
+    w[4] = w[4] - eta * (sum(m[m$stars == 4, ]$listener.p - m[m$stars == 4, ]$pred))
+    w[5] = w[5] - eta * (sum(m[m$stars == 5, ]$listener.p - m[m$stars == 5, ]$pred))
+    w = ifelse(w <= 0, 0, w)
+    w = ifelse(w >= 1, 1, w)
+    if(verbose) {print(w)}
+  }
+  return(w)
+}
+normalize = function(w) { return (w / sum(w))}
+
+```
+
+```{r}
+targets = c("hi1", "hi2")
+fitted.w = fit_distr("good_excellent", numIters=100, alpha=4, eta=0.001, normalize=T)
+scalar.focused = data.full.extras[data.full.extras$scale == "good_excellent", ]
+scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = fitted.w
+m = scalar.focused %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=T))
+cor(m[m$degree %in% targets, ]$listener.p, m[m$degree %in% targets, ]$pred)
+normalize(fitted.w)
+
+fitted.w = fit_distr("liked_loved", numIters=100, alpha=4, eta=0.001, normalize=T)
+# fitted.w = fitted.w / sum(fitted.w)
+scalar.focused = data.full.extras[data.full.extras$scale == "good_excellent", ]
+scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = fitted.w
+m = scalar.focused %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=T))
+cor(m[m$degree %in% targets, ]$listener.p, m[m$degree %in% targets, ]$pred)
+normalize(fitted.w)
+
+targets = c("hi1", "low1")
+fitted.w = fit_distr("some_all", numIters=200, alpha=4, eta=0.001, normalize=T)
+# fitted.w = fitted.w / sum(fitted.w)
+scalar.focused = data.full.extras[data.full.extras$scale == "some_all", ]
+scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = fitted.w
+m = scalar.focused %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=T))
+cor(m[m$degree %in% targets, ]$listener.p, m[m$degree %in% targets, ]$pred)
+normalize(fitted.w)
+qplot(stars, listener.p, col=degree, 
+      data=m[m$degree %in% targets,],
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+targets = c("hi1", "hi2")
+fitted.w = fit_distr("palatable_delicious", numIters=200, alpha=4, eta=0.001, normalize=T)
+# fitted.w = fitted.w / sum(fitted.w)
+scalar.focused = data.full.extras[data.full.extras$scale == "palatable_delicious", ]
+scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = fitted.w
+m = scalar.focused %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=T))
+cor(m[m$degree %in% targets, ]$listener.p, m[m$degree %in% targets, ]$pred)
+normalize(fitted.w)
+
+qplot(stars, listener.p, col=degree, 
+      data=m[m$degree %in% targets,],
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+targets = c("hi1", "hi2")
+fitted.w = fit_distr("memorable_unforgettable", numIters=200, alpha=4, eta=0.01, normalize=T)
+# fitted.w = fitted.w / sum(fitted.w)
+scalar.focused = data.full.extras[data.full.extras$scale == "memorable_unforgettable", ]
+scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = fitted.w
+m = scalar.focused %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=T))
+cor(m[m$degree %in% targets, ]$listener.p, m[m$degree %in% targets, ]$pred)
+
+normalize(fitted.w)
+
+qplot(stars, listener.p, col=degree, 
+      data=m[m$degree %in% targets,],
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+```

### 2015-12-01 models/Model_additionalAlts.Rmd
updated params for fn call

@@
 # target        --> specific scalar family we're interested in (i.e. "some_all")
-# numIters      --> 
-# eta           --> 
-# normalize     --> 
-fit_distr = function(target, numIters = 100, eta=0.01,  normalize=F, alpha=1, verbose=F) {
+# numIters      --> number of iterations to run
+# eta           --> step size
+# alpha         --> alpha level for RSA?
+# normalize     --> normalize in RSA?
+fit_distr = function(target, numIters = 100, eta=0.01, normalize=T, alpha=1, verbose=F) {
   # Initialize to uniform
@@
   scalar.focused = data.full.extras[data.full.extras$scale == target, ]
-  # Initialize 'mid' alternative
-
-  match.scalars = which(scalar.focused$degree == "hi1" | scalar.focused$degree == "hi2")
 

### 2015-12-01 models/Model_additionalAlts.Rmd
modiefied gradient descent tracking and plotting

--- 2015-11-30 models/Model_additionalAlts.Rmd
@@
 
-Focus on single scalar fn()
+# Fit extra scalar literal listener distributions
+## modified gradient descent / MLE fn()
 ```{r}
-# focus_alts
-# ---------
+# normalize()
+# -----------
+# normalize a generic vector
+normalize = function(w) { return (w / sum(w))}
+
+# fit_distr()
+# -----------
 # target        --> specific scalar family we're interested in (i.e. "some_all")
-# combos    --> collection of possible 'mid' l0 distribution
-# normalize --> normaize pre RSA?
-# alpha     --> set alpha level
-focus_alts = function(target, combos, normalize=F, alpha=1) {
-  # Default normalish looking distr
-  if (is.null(combos)) {
-    combos = data.frame(c(0, 0, 1, 0, 0),
-                        c(0, 0.05, 0.9, 0.05, 0),
-                        c(0, 0.1, 0.8, 0.1, 0),
-                        c(0, 0.2, 0.6, 0.2, 0),
-                        c(0, 0.25, 0.5, 0.25, 0))  
-  }
-  colnames(combos) = LETTERS[1:length(colnames(combos))]
+# numIters      --> number of iterations to run
+# eta           --> step size
+# alpha         --> alpha level for RSA?
+# normalize     --> normalize in RSA?
+fit_distr = function(target, numIters = 100, eta=0.01, normalize=T,
+                     alpha=1, verbose=F, data.record=NULL) {
 
-  # Find best distribution
-  cors = c()
-  for (i in 1:ncol(combos)) {
-    ge.subset = data.full.extras[data.full.extras$scale == target, ]
-    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
-    target.scalars = c("hi1", "hi2")
+  if (verbose) { print(paste("Currently fitting", target, "...")) }
+  # Initialize to uniform
+  w = rep(0.1, 5)
+  # Focus on scalar 'target'
+  scalar.focused = data.full.extras[data.full.extras$scale == target, ]
 
-    # Run model
-    m1 = ge.subset %>%
+  # For numIters iterations...
+  for (i in 1:numIters) {
+    prev.w = w
+    scalar.focused[scalar.focused$degree == "mid", "speaker.p"] = w
+    m = scalar.focused %>%
       do(run.full(., alpha = alpha, addMid=T, normalize=normalize))
-    if (target == "some_all") {
-      target.scalars = c("hi1", "low1")
-      m1 = m1[m1$degree %in% target.scalars, ]  
-    } else {
-      m1 = m1[m1$degree %in% target.scalars, ]  
-    }
-    cors[i] = cor(m1$pred, m1$listener.p)  
+    w[1] = w[1] - eta * (sum(m[m$stars == 1, ]$listener.p - m[m$stars == 1, ]$pred))
+    w[2] = w[2] - eta * (sum(m[m$stars == 2, ]$listener.p - m[m$stars == 2, ]$pred))
+    w[3] = w[3] - eta * (sum(m[m$stars == 3, ]$listener.p - m[m$stars == 3, ]$pred))
+    w[4] = w[4] - eta * (sum(m[m$stars == 4, ]$listener.p - m[m$stars == 4, ]$pred))
+    w[5] = w[5] - eta * (sum(m[m$stars == 5, ]$listener.p - m[m$stars == 5, ]$pred))
+    w = ifelse(w <= 0, 0, w)
+    w = ifelse(w >= 1, 1, w)
+    w = normalize(w)
+
+    # Record convergence
+    if (!is.null(data.record)) {
+      data.record = rbind(data.record, w)
     }
 
-  # Get index of highest correlation
-  i = which(cors == max(cors))[1]
-  ge.subset = data.full.extras[data.full.extras$scale == target, ]
-    ge.subset[ge.subset$degree == "mid", "speaker.p"] = combos[, i]
-  m1 = ge.subset %>%
-    do(run.full(., alpha = alpha, addMid=T, normalize=normalize))
+    # Check if we've converged
+    if (sum(abs(prev.w - w)) < 0.00001) {
+      if(verbose) { print("Convergence") }
+      return(list(w, data.record))
+    }
 
-  p = qplot(stars, listener.p, col=degree, 
-        data=m1,
-        ylab="Posterior p(rating | word)") + 
-    geom_line(aes(y = pred), lty = 4)
+    if(verbose) {print(list(i, w))}
+  }
+  return(list(w, data.record))
+}
+```
 
-  return(c(combos[i], cors[i]))
+# Fit extra scalar literal listener distributions
+```{r}
+# Normalize in RSA?
+norm = T
+# Our scalars
+scalars = c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+fitted.distr = data.frame(matrix(rep(NA, 25), ncol=5))
+colnames(fitted.distr) = scalars
+
+# Fit each of our scalars / track fitting
+track.data = data.frame(matrix(ncol=6))
+for (i in 1:length(scalars)) {
+  # record fitting
+  data.record = data.frame(matrix(rep(NA, 5), ncol=5))
+  # output is optimal distr [[1]] and [[2]] record of fitting
+  out = fit_distr(scalars[i], numIters=20, eta=0.01,
+                  verbose=F, normalize=norm, alpha=4, data.record=data.record)
+
+  # get fitted scalar distr
+  fitted.distr[, i] = out[[1]]
+  # get tracking data
+  tracking = as.data.frame(out[[2]][-1,]) %>%
+    mutate(X6 = scalars[i])
+  track.data = rbind(track.data, tracking)
 }
@@
 ```{r}
-# liked_loved
-combos = data.frame(c(0, 0, 1, 0, 0),
-                    c(0, 0.05, 1, .05, 0),
-                    c(0, 0.1, 1, .1, 0),
-                    c(0, 0.1, 0.9, .1, 0),
-                    c(0, 0.2, 0.8, .2, 0),
-                    c(0, 0.25, 0.8, .25, 0),
-                    c(0.05, 0.1, 1, .1, 0.9),
-                    c(0.1, 0.1, 1, .1, 0.1))  
-focus_alts("liked_loved", combos=combos, alpha=4, normalize=T)
-focus_alts("liked_loved", combos=combos, alpha=8, normalize=F)
+# Format track data for display
+track.data = track.data[-1, ]
+track.data$step = rep(seq(1, 20), 5)
+track.data = track.data %>% 
+  gather(stars, value, X1:X5)
+```
 
-# good_excellent
-combos = data.frame(c(0, 0, 1, 0, 0),
-                    c(0, 0.05, 0.9, 0.05, 0),
-                    c(0, 0.1, 0.8, 0.1, 0),
-                    c(0, 0.2, 0.2, 0.2, 0.9),
-                    c(0, 0.2, 0.6, 0.2, 1),
-                    c(0, 0.2, 0.6, 0.3, 0.2),
-                    c(0, 0.2, 0.6, 0.3, 0.3),
-                    c(0, 0.2, 0.6, 0.5, 0.4),
-                    c(0, 0.2, 0.6, 0.5, 0.5),
-                    c(0, 0.2, 0.6, 0.6, 0.4),
-                    c(0.05, 0.2, 0.6, 0.2, 0.05),
-                    c(0, 0.25, 0.5, 0.25, 0))  
-focus_alts("good_excellent", combos=combos, alpha = 1, normalize=T)
-focus_alts("good_excellent", combos=combos, alpha = 8, normalize=F)
+## Run distribution fitting
+```{r}
+for (scale in scalars) {
+  data.full.extras[data.full.extras$scale == scale &
+                     data.full.extras$degree == "mid", ]$speaker.p =
+    normalize(fitted.distr[ , scale])
+}
+m = data.full.extras %>%
+  do(run.full(., alpha = 4, addMid=T, normalize=norm))
+cor(m[matched.items.extras, ]$listener.p, m[matched.items.extras, ]$pred)
+```
 
-# some_all
-combos = data.frame(c(0, 1, 0, 0, 0),
-                    c(0.05, 2, 0.05, 0.05, 0.05),
-                    c(0.2, 0.9, 0.2, 0.1, 0.1),
-                    c(0.2, 0.9, 0.2, 0.1, 0),
-                    c(0.1, 0.9, 0.1, 0, 0),
-                    c(0.1, 0.8, 0.1, 0, 0),
-                    c(0.2, 0.6, 0.2, 0, 0),
-                    c(0.25, 0.5, 0.25, 0, 0))
-focus_alts("some_all", combos=combos, alpha=4, normalize=T)
-focus_alts("some_all", combos=combos, alpha=8, normalize=F)
+## Plot distr
+```{r}
+# Normalize speaker.p for plotting
+for (scale in scalars) {
+  degrees = unique(data.full.extras$degree)
+  for (degree in degrees) {
+    data.full.extras[data.full.extras$scale == scale &
+                       data.full.extras$degree == degree, ]$speaker.p = 
+        normalize(data.full.extras[data.full.extras$scale == scale &
+                                     data.full.extras$degree == degree, ]$speaker.p)
+  }
+}
 
-# memorable_unforgettable
-combos = data.frame(rep(0.1, 5),
-                    c(0.05, 2, 0.05, 0.05, 0.05),
-                    c(0.05, 1, 0.05, 0.05, 0.05),
-                    c(0.05, 0.9, 0.05, 0.05, 0.05),
-                    c(0.05, 0.8, 0.05, 0.05, 0.05),
-                    c(0.05, 0.7, 0.05, 0.05, 0.05),
-                    c(0.05, 0.6, 0.05, 0.05, 0.05),
-                    c(0.05, 0.5, 0.05, 0.05, 0.05),
-                    c(0.1, 0.8, 0.1, 0.1, 0.1))
-focus_alts("memorable_unforgettable", combos=combos, alpha=4, normalize=T)
-focus_alts("memorable_unforgettable", combos=combos, alpha=8, normalize=F)
+# Differentiate tuned 'mid' scalar
+data.full.extras$type = ifelse(data.full.extras$degree == "mid", "red", "blue")
+qplot(x = stars, y = speaker.p, colour = type,
+      geom = "line", stat = "identity", position = "dodge", 
+      main = "Literal listener semantics\nEmpirical estimates and tuned extra 'mid'",
+      ylab = "P_{L0}(Word | Rating) - Normalized",
+      data = data.full.extras) + 
+  facet_wrap(~scale + degree)
 
-# palatable_delicious
-combos = data.frame(rep(0.1, 5),
-                    c(0.05, 2, 0.05, 0.05, 0.05),
-                    c(0.05, 1, 0.05, 0.05, 0.05),
-                    c(0.05, 0.05, 0.05, 0.9, 0.1),
-                    c(0.05, 0.05, 0.05, 0.9, 0.05),
-                    c(0.05, 0.7, 0.05, 0.5, 0.05),
-                    c(0.05, 0.6, 0.05, 0.05, 0.05),
-                    c(0.05, 0.5, 0.05, 0.05, 0.05),
-                    c(0.1, 0.8, 0.1, 0.1, 0.1))
-focus_alts("palatable_delicious", combos=combos, alpha=4, normalize=T)
-focus_alts("palatable_delicious", combos=combos, alpha=8, normalize=F)
+# Tracking of gradient descent tuning
+ggplot(data=track.data, aes(x=step, y=value, col=stars)) +
+  geom_line() +
+  facet_wrap(~X6)
 ```

### 2015-12-01 models/Model_additionalAlts.Rmd
slight modifications and correct output for fitted literal listener

@@
 # RSA functionality
-```{r}
+```{r RSA_function}
 # speaker informativity
@@
 # Run model functionality
-```{r}
+```{r run_functions}
 # run.partial()
@@
 ## Tune hyperparams
-```{r}
+```{r alpha_tuning}
 # tune.alhpa()
@@
 ### Data for full model - alternatives
-```{r}
+```{r full_model_data + alternatives, message=FALSE, warning=FALSE}
 speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10a.csv")
@@
 ## Match items between studies (full and partial)
-```{r}
+```{r match_items_between_studies}
 matched.items = which((data.full[, "scale"] != "some_all" &
@@
 ## modified gradient descent / MLE fn()
-```{r}
+```{r Fit extra scalars functions, warning=FALSE}
 # normalize()
@@
 # Fit extra scalar literal listener distributions
-```{r}
+```{r Run fit extra scalars}
+# Set parameters for tunin
 # Normalize in RSA?
 norm = T
+eta = 0.01
+alpha = 4
+numIters = 100
+
 # Our scalars
@@
   # output is optimal distr [[1]] and [[2]] record of fitting
-  out = fit_distr(scalars[i], numIters=20, eta=0.01,
-                  verbose=F, normalize=norm, alpha=4, data.record=data.record)
+  out = fit_distr(scalars[i], numIters=numIters, eta=eta,
+                  verbose=F, normalize=norm, alpha=alpha, data.record=data.record)
 
@@
 
-```{r}
+```{r format tracking data}
 # Format track data for display
 track.data = track.data[-1, ]
-track.data$step = rep(seq(1, 20), 5)
+track.data$step = rep(seq(1, numIters), 5)
 track.data = track.data %>% 
   gather(stars, value, X1:X5)
+track.data$stars = ifelse(track.data$stars == "X1", "1",
+                          ifelse(track.data$stars == "X2", "2",
+                                 ifelse(track.data$stars == "X3", "3",
+                                        ifelse(track.data$stars == "X4", "4", 5))))
+colnames(track.data)[1] = "scale"
 ```
@@
 ## Run distribution fitting
-```{r}
+```{r Run-data}
 for (scale in scalars) {
@@
 m = data.full.extras %>%
-  do(run.full(., alpha = 4, addMid=T, normalize=norm))
+  do(run.full(., alpha = alpha, addMid=T, normalize=norm))
 cor(m[matched.items.extras, ]$listener.p, m[matched.items.extras, ]$pred)
@@
 ## Plot distr
-```{r}
+```{r Plots}
 # Normalize speaker.p for plotting
@@
 # Differentiate tuned 'mid' scalar
-data.full.extras$type = ifelse(data.full.extras$degree == "mid", "red", "blue")
+plot.data = data.full.extras
+plot.data$type = ifelse(plot.data$degree == "mid", "red", "blue")
 qplot(x = stars, y = speaker.p, colour = type,
@@
       ylab = "P_{L0}(Word | Rating) - Normalized",
-      data = data.full.extras) + 
+      data = plot.data) + 
   facet_wrap(~scale + degree)
@@
   geom_line() +
-  facet_wrap(~X6)
+  facet_wrap(~scale) +
+  ylab("Normalized p(m | u)") +
+  xlab("Iterations") +
+  ggtitle("Fitted alternative distr fitting")
 ```
+
+## Output fitted literal listener to .csv
+```{r}
+data.out = data.full.extras %>%
+  select(degree, stars, speaker.p) %>%
+  mutate(cil = NA,
+         cih = NA,
+         cnt.judgment = NA)
+data.out = data.out[, c(1, 2, 3, 5, 6, 7, 4)]
+# write.csv(data.out,
+#           "~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10fittedAlts.csv")
+```

### 2015-12-01 models/Model_Comparison.Rmd
new discussion - acurrently running with fitted alternatives, but need to discuss with Mike

@@
 ```{r}
-speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10a.csv")
+# made up alts in 'L0_e10a.csv'
+# fitted alts in 'L0_e10fittedAlts.csv'
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10fittedAlts.csv")
 data.full.extras = left_join(speaker, listener) %>%
@@
 
-## Initial thoughts:
+# Interpretation
 
-### Overall
+## Overall results
 
-Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives.
-The largest improvement in model fit occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
-Have a look at the `m2` vs `m3` correlation for models with pre-RSA normalization below (`c` models):
+Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives: The largest improvement in model fit occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
+Have a look at the `m2` vs `m3` correlation for models with pre-RSA normalization below (`c` models)
 ```{r}
@@
 
-Here's another look at the improvement in model fit between normalized `m2` and `m3`.
+Here's a closer look at the improvement in fit between between normalized `m2` and `m3`.
 ```{r}
@@
 
-Importantly, we also see improvements with the addition of 'fitted' alternatives in m4 see the plots below:
+## Including alternatives
+
+Importantly, we also see improvements with the addition of 'fitted' alternatives in m4 see the plots below - especially in matching `weaker` scalar distriubtions (i.e. 'some' in 'some_all').
 ```{r}
-m3.c.jointPlot
 m4.c.jointPlot
@@
 
-This presents a little bit more of a challenge, however, as we'd like to jointly fit our alpha as well as our alternatives - is this worth delving into?
-Currently we're just fitting alpha and then finding alternatives.
+## Questions:
 
-## Additional notes:
+### 1) How do we want to deal with e6 vs e11 prag listener judgement differences?
+[e6 and e11 prag listener judgement differences](https://cdn.rawgit.com/langcog/scalar_implicature/master/models/RSA%2BAmbiguousSemantics.html#pragmatic-listener-studies---judgement-distributional-differences)
 
-1) In general model performance is greater (correlation) for e11 data. This may be due in part to less extreme literal listener evaluations in e11 see:
-
-https://cdn.rawgit.com/langcog/scalar_implicature/master/models/RSA%2BAmbiguousSemantics.html#pragmatic-listener-studies---judgement-distributional-differences
-
-Our best model performance occurs with e11 and the model is m4.c, correlation = `r as.numeric(performance.output[15, 3])` (see plot below):
-```{r}
-qplot(stars, listener.p, col=degree, 
-      data=m4.c.matched,
-      main=paste("m4.c\nalpha: ", alphas[15],
-                 "\nNormalized = ", T,
-                 "\nCorr = ", performance.output[15, 3]),
-      ylab="Posterior p(rating | word)") + 
-  ylim(0, 1) +
-  facet_wrap(~scale) + 
-  geom_line(aes(y = pred), lty = 4)
-```
-
-Normalizing vs not normalizing before running RSA:
+### 2) Normalizing vs not normalizing before running RSA:
 
@@
 One repercussion is that during normalization we'll see larger impact from salient alternatives...
-In `Model_addtionalAlts.Rmd` I'm seeing that higher entropy scales `memorable_unforgettable`, `palatable_delicious` appear to be looking for more alternatives (correlation improves when I add wacky distributions such as [0, 0.1, 0.9, 0.1, 0.9] which suggests that we need possibly *two* more alternatives, not just one).
-This seems intuitive in the higher entropy setting...
-Can we interpret this kind of finding (at least intuitively) as the model telling us it wants *more* alternatives?
-See
 
-https://cdn.rawgit.com/langcog/scalar_implicature/master/models/Model_additionalAlts.html#match-items-between-studies-full-and-partial
+### 3) Coming up with alternatives
 
-# All plots with e6 prag judgements
+I was trying to estimate what seemed liked 'sensible' alternatives and decided to try and 'fit' the distributions for alternatives using a pseudo gradient descent algorithm - 
+[fitting alternatives](https://cdn.rawgit.com/langcog/scalar_implicature/master/models/Model_additionalAlts.html#plot-distr)
+
+How can we interpret some of the more funky alternatives (i.e.
+`memorable_unforgettable`, `some_all`)?
+Does this scalar family 'want' more than one more alternative?
+That is, maybe the model is telling us that only one additional alternative is not enough...?
+Can we link this intuition back to entropy measures for the scales?
+```{r}
+# entropy measures 
+scales.entropy
+```
+
+# All plots
 ```{r overall_perf}

### 2015-12-01 models/Model_Comparison.Rmd
minor language tweak

@@
 
-Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives: The largest improvement in model fit occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
+Across e6 and e11 pragmatic listener judgements we see model fit improve as we add more alternatives: The largest improvement occurs when we first include the empirically derived salient alternatives (correlations jump +0.23).
 Have a look at the `m2` vs `m3` correlation for models with pre-RSA normalization below (`c` models)

### 2015-12-14 experiments/implicatures_e12.js
copied over e10 literal listener and e11 prag listener studies

@@ -1,0 +1,240 @@
+//############################## Helper functions ##############################
+// Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
+function showSlide(id) {
+	// Hide all slides
+	$(".slide").hide();
+	// Show just the slide we want to show
+	$("#"+id).show();
+}
+
+// Get random integers.
+// When called with no arguments, it returns either 0 or 1. When called with one argument, *a*, it returns a number in {*0, 1, ..., a-1*}. When called with two arguments, *a* and *b*, returns a random value in {*a*, *a + 1*, ... , *b*}.
+function random(a,b) {
+	if (typeof b == "undefined") {
+		a = a || 2;
+		return Math.floor(Math.random()*a);
+	} else {
+		return Math.floor(Math.random()*(b-a+1)) + a;
+	}
+}
+
+// Add a random selection function to all arrays (e.g., <code>[4,8,7].random()</code> could return 4, 8, or 7). This is useful for condition randomization.
+Array.prototype.random = function() {
+  return this[random(this.length)];
+}
+
+// shuffle function - from stackoverflow?
+// shuffle ordering of argument array -- are we missing a parenthesis?
+function shuffle (a) { 
+	var o = [];
+
+	for (var i=0; i < a.length; i++) {
+		o[i] = a[i];
+	}
+
+	for (var j, x, i = o.length;
+	 i;
+	 j = parseInt(Math.random() * i), x = o[--i], o[i] = o[j], o[j] = x);	
+	return o;
+}
+//############################## Helper functions ##############################	
+
+var sents = {
+    scale: {
+		training1: {
+		    //hi1:  "thought the food deserved a <b>very high</b> rating?",
+		    hi2:  "thought the food deserved a <b>high</b> rating?",
+		    low1:  "thought the food deserved a <b>low</b> rating?"
+		    //low2:  "thought the food deserved a <b>very low</b> rating?"
+		},
+		liked_loved: {		   
+		    hi1:  "<b>loved</b> the food?",
+		    hi2:  "<b>liked</b> the food?",
+		    low1:  "<b>disliked</b> the food?",
+		    low2:  "<b>hated</b> the food?",
+		},
+		good_excellent: {
+			hi1:  "thought the food was <b>excellent</b>?",
+		    hi2:  "thought the food was <b>good</b>?",
+		    low1:  "thought the food was <b>bad</b>?",
+		    low2:  "thought the food was <b>terrible</b>?"
+		},
[…]

### 2015-12-14 experiments/implicatures_e12.js
prelim code for mid/neutral scalar option - needs to be tested and populated with actual scalars?

@@ -1,3 +1,5 @@
+// Experiment 12 literal listener with 'neutral alternative'
+
 //############################## Helper functions ##############################
 // Shows slides. We're using jQuery here - the **$** is the jQuery selector function, which takes as input either a DOM element or a CSS selector string.
 function showSlide(id) {
@@ -50,44 +52,49 @@ var sents = {
 		liked_loved: {		   
 		    hi1:  "<b>loved</b> the food?",
 		    hi2:  "<b>liked</b> the food?",
+		    mid: "<b>mid</b the food",
 		    low1:  "<b>disliked</b> the food?",
 		    low2:  "<b>hated</b> the food?",
 		},
 		good_excellent: {
 			hi1:  "thought the food was <b>excellent</b>?",
 		    hi2:  "thought the food was <b>good</b>?",
+		    mid:  "thought the food was <b>mid</b>?",
 		    low1:  "thought the food was <b>bad</b>?",
 		    low2:  "thought the food was <b>terrible</b>?"
 		},
 		palatable_delicious: {
 			hi1:  "thought the food was <b>delicious</b>?",
 		    hi2:  "thought the food was <b>palatable</b>?",
+		    mid:  "thought the food was <b>mid</b>?",
 		    low1:  "thought the food was <b>gross</b>?",
 		    low2:  "thought the food was <b>disgusting</b>?"
 		},
 		memorable_unforgettable: {
 			hi1:  "thought the food was <b>unforgettable</b>?",
 		    hi2:  "thought the food was <b>memorable</b>?",
+		    mid:  "thought the food was <b>mid</b>?",
 		    low1:  "thought the food was <b>bland</b>?",
 		    low2:  "thought the food was <b>forgettable</b>?"
 		},
 		some_all: {
 			hi1: "enjoyed <b>all</b> of the food they ate?",
 			hi2: "enjoyed <b>most</b> of the food they ate?",
-			low1: "enjoyed <b>some</b> of the food they ate?",
+			mid: "enjoyed <b>some</b> of the food they ate?",
+			low1: "enjoyed <b>low1</b> of the food they ate?",
 			low2: "enjoyed <b>none</b> of the food they ate?"
 		}
     },
 };
 
 //Trial condition params initializations ------------------->
-var TOTAL_TRIALS = 102;
+var TOTAL_TRIALS = 152;
 var trials = [];
 for(var i = TOTAL_TRIALS; i > 0; --i) {
[…]

### 2015-12-15 models/midScalarInvestigation.Rmd
mid scalar suggestions - to sent to MF

---
title: "responeToFrankeTypicalUse"
author: "Ben Peloquin"
date: "December 14, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 3
---
```{r}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)
```

```{r multiplot(), echo=FALSE}
multiplot = function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

# "neutral" target scalars for e12/e13

We're trying to come up with scalars that will approximate the blue distributions here:
["https://htmlpreview.github.io/?https://raw.githubusercontent.com/langcog/scalar_implicature/master/models/Model_additionalAlts.html#plot-distr"]

## Currently proposing for e12 / e13:

I've populated e12/e13 with the first items (1) listed below. So we're including `okay` with good_excellent because that was the most frequent and "applicable" alternative.

"Somebody said they thought the food was \___."

good_excellent scale: 1) `okay`, 2) `average`, 3) `fine`

palatable_delicious scale: 1) `mediocre`, 2) `okay`

memorable_unforgettable scale: 1) `ordinary`, 2) `average`, 3) `unremarkable`

"Somebody said they \___ the food."

liked_loved scale: 1) `felt indifferent about`, 2) `appreciated`

(we might want to go with something like "felt okay about" or "felt fine about", but those weren't top competitors for liked_loved)

"Somebody said they enjoyed \___ of the food."

some_all scale: 1) `a little bit of`, 2) `bits of` 3) `parts of`

# Study e9 - Empirically derived alts (frequencies)
```{r}
d = fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T)
d = as.data.frame(d, stringsAsFactors = FALSE)

d = d %>% 
  gather(base, alt, 
         palatable, liked, good, loved, some, all, 
         delicious, excellent, memorable, unforgettable) %>%
  mutate(base = as.character(base)) %>%
  rowwise %>%
  mutate(scale = ifelse(base == "some" | base == "all", "some_all", 
                        ifelse(base == "palatable" | base == "delicious", "palatable_delicious",
                               ifelse(base == "liked" | base == "loved", "liked_loved",
                                      ifelse(base == "good" | base == "excellent", 
                                             "good_excellent", "memorable_unforgettable"))))) %>%
  group_by(scale, alt) %>%
  summarise(n = n())

# Plot findings of salient alternatives for each scale
# -------------------------------------------------------
scales = unique(d$scale)
ggplot(data=d[d$scale==scales[1],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[1])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[2],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[2])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[3],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[3])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[4],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[4])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(data=d[d$scale==scales[5],], aes(x=reorder(alt, -n), y=n)) +
  geom_bar(stat="identity") + ylim(0, 60) + labs(x = "alternative", y = "counts") +
  ggtitle(paste("Salient alternatives for ", scales[5])) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# multiplot(p1, p2, p3, p4, p5, cols=1)
```

# Emp alts for Some / All individually
```{r}
d = fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T)
d = as.data.frame(d, stringsAsFactors = FALSE)

d.some = d$some
d.some = as.data.frame(as.factor(d.some))
d.some = as.data.frame(table(d.some))
d.some = d.some[rev(order(d.some$Freq)), ]
d.some$prop = d.some$Freq / sum(d.some$Freq)
ggplot(d.some, aes(x=reorder(d.some, Freq), y=Freq)) +
  geom_bar(stat="identity", position="dodge") +
  xlab("alternatives") +
  ylab("frequency counts") +
  ggtitle("e9 - alternatives to 'some'")

d.all = d$all
d.all = as.data.frame(as.factor(d.all))
d.all = as.data.frame(table(d.all))
d.all = d.all[rev(order(d.all$Freq)), ]
d.all$prop = d.all$Freq / sum(d.all$Freq)
ggplot(d.all, aes(x=reorder(d.all, Freq), y=Freq)) +
  geom_bar(stat="identity", position="dodge") +
  xlab("alternatives") +
  ylab("frequency counts") +
  ggtitle("e9 - alternatives to 'all'")
```

### 2015-12-15 models/midScalarInvestigation.Rmd
updated output - language tweaks

@@
 ---
-title: "responeToFrankeTypicalUse"
+title: "responseToFrankeTypicalUse..."
 author: "Ben Peloquin"

### 2015-12-15 experiments/implicatures_e12.js
tweaks to randomziation- need to make sure this is running correctly

@@ -52,28 +52,28 @@ var sents = {
 		liked_loved: {		   
 		    hi1:  "<b>loved</b> the food?",
 		    hi2:  "<b>liked</b> the food?",
-		    mid: "<b>mid</b the food",
+		    mid: "<b>felt indifferent about</b the food",
 		    low1:  "<b>disliked</b> the food?",
 		    low2:  "<b>hated</b> the food?",
 		},
 		good_excellent: {
 			hi1:  "thought the food was <b>excellent</b>?",
 		    hi2:  "thought the food was <b>good</b>?",
-		    mid:  "thought the food was <b>mid</b>?",
+		    mid:  "thought the food was <b>okay</b>?",
 		    low1:  "thought the food was <b>bad</b>?",
 		    low2:  "thought the food was <b>terrible</b>?"
 		},
 		palatable_delicious: {
 			hi1:  "thought the food was <b>delicious</b>?",
 		    hi2:  "thought the food was <b>palatable</b>?",
-		    mid:  "thought the food was <b>mid</b>?",
+		    mid:  "thought the food was <b>mediocre</b>?",
 		    low1:  "thought the food was <b>gross</b>?",
 		    low2:  "thought the food was <b>disgusting</b>?"
 		},
 		memorable_unforgettable: {
 			hi1:  "thought the food was <b>unforgettable</b>?",
 		    hi2:  "thought the food was <b>memorable</b>?",
-		    mid:  "thought the food was <b>mid</b>?",
+		    mid:  "thought the food was <b>ordinary</b>?",
 		    low1:  "thought the food was <b>bland</b>?",
 		    low2:  "thought the food was <b>forgettable</b>?"
 		},
@@ -81,7 +81,7 @@ var sents = {
 			hi1: "enjoyed <b>all</b> of the food they ate?",
 			hi2: "enjoyed <b>most</b> of the food they ate?",
 			mid: "enjoyed <b>some</b> of the food they ate?",
-			low1: "enjoyed <b>low1</b> of the food they ate?",
+			low1: "enjoyed <b>a little</b> of the food they ate?",
 			low2: "enjoyed <b>none</b> of the food they ate?"
 		}
     },

### 2016-01-04 experiments/implicatures_e12.js
fixed off by one trial error

@@ -97,17 +97,16 @@ var sents = {
 var NUM_DEGREES = 5
 var NUM_SCALES = 5
 var NUM_STARS = 5
+var NUM_TRAINING_TRIALS = 2
 // 5 scales * 5 rating levels * 5 manipulation levels + 2 training trials
-var TOTAL_TRIALS = NUM_SCALES * NUM_STARS * NUM_DEGREES + 2;
+var TOTAL_TRIALS = NUM_SCALES * NUM_STARS * NUM_DEGREES + NUM_TRAINING_TRIALS;
 
 var scales = Object.keys(sents.scale);
 var scale_degrees = ["hi1", "hi2", "mid","low1", "low2"];
 var manipulation = ["20", "40", "60", "80", "100"];
 
 var trials = [];
-for(var i = TOTAL_TRIALS; i > 0; --i) {
-	trials.push(i);
-}
+for(var i = TOTAL_TRIALS - 1; i >= 0; --i) trials.push(i);
 
 // Show the instructions slide -- this is what we want subjects to see first.
 showSlide("instructions");
@@ -181,13 +180,14 @@ var experiment = {
 				    String(100 * ((TOTAL_TRIALS - trials.length)/TOTAL_TRIALS)) + "%");
 		    
 		    // Check for training runs
-		    if(trials.length > TOTAL_TRIALS - 2) {
+		    if(trials.length > TOTAL_TRIALS - NUM_TRAINING_TRIALS) {
 		    	// training #1: 'hi2' == "high" with 5 stars (expect 'Yes' resopnse)
 		    	if (trials.length == TOTAL_TRIALS) {
 			    	trials.shift();
 			    	current_scale = scales[0];
 			    	degree = "hi2";
 			    	manipulation_level = "100";
+
 			    } // training #2: 'low1' == "low" with 1 star (expect 'Yes' resopnse)
 			    else {
 			    	trials.shift();

### 2016-01-04 experiments/implicatures_e12.js
changed 'a little' to 'little'

@@ -86,7 +86,7 @@ var sents = {
 			hi1: "enjoyed <b>all</b> of the food they ate?",
 			hi2: "enjoyed <b>most</b> of the food they ate?",
 			mid: "enjoyed <b>some</b> of the food they ate?",
-			low1: "enjoyed <b>a little</b> of the food they ate?",
+			low1: "enjoyed <b>little</b> of the food they ate?",
 			low2: "enjoyed <b>none</b> of the food they ate?"
 		}
     },

### 2016-01-05 Paper/Paper.Rmd
Cogsci 2016 paper initial commit

---
title: "The importance of negative alternatives in pragmatic implicature"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract: 
    "Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly assume the presence of salient alternatives. For example, the standard quantity implicature arises the presence of a competiting and more informative alternatives. Using a Bayesian formulzation of this theory we assess the degree to which alternatives influence pragmatic enrichment of scalar items. Our findings suggest that the presence of a complete of set of possible alternatives."

keywords:
    "pragmatics; scalar implicature; bayesian modeling"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(ggplot2)
```

# Introduction

Implicature as a case study for pragmatics

RSA as a way of studying implicature [@frank2012]

Scalar implicature in particular, what are the alternatives? [@franke2014] [@degen2015]

Using the scalar diversity approach to get beyond the some/all implicature [@vantiel2013]

Outline of the rest of the paper

# Experiment 1a,b: Entailment scales

## Participants

## Procedure

## Results and Discussion

# Experiment 2: What are the alternatives?

## Participants

## Procedure

## Results and Discussion

# Experiment 3a,b: Adding Negative alternatives

## Participants

## Procedure

## Results and Discussion

# Model

## Details

## Model fitting and comparison

# General Discussion

# Acknowledgements

Thanks to NSF BCS #XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.

# References

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent

### 2016-01-05 Paper/Paper.tex
Cogsci 2016 paper initial commit

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{The importance of negative alternatives in pragmatic implicature}

\author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

\begin{document}

\maketitle

\begin{abstract}
Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly
assume the presence of salient alternatives. For example, the standard
quantity implicature arises the presence of a competiting and more
informative alternatives. Using a Bayesian formulzation of this theory
we assess the degree to which alternatives influence pragmatic
enrichment of scalar items. Our findings suggest that the presence of a
complete of set of possible alternatives.

\textbf{Keywords:}
pragmatics; scalar implicature; bayesian modeling
\end{abstract}

\section{Introduction}\label{introduction}

Implicature as a case study for pragmatics

RSA as a way of studying implicature ({\textbf{???}})

Scalar implicature in particular, what are the alternatives?
({\textbf{???}}) ({\textbf{???}})

Using the scalar diversity approach to get beyond the some/all
implicature ({\textbf{???}})

Outline of the rest of the paper

\section{Experiment 1a,b: Entailment
scales}\label{experiment-1ab-entailment-scales}

\subsection{Participants}\label{participants}

\subsection{Procedure}\label{procedure}

\subsection{Results and Discussion}\label{results-and-discussion}

\section{Experiment 2: What are the
alternatives?}\label{experiment-2-what-are-the-alternatives}

\subsection{Participants}\label{participants-1}

\subsection{Procedure}\label{procedure-1}

\subsection{Results and Discussion}\label{results-and-discussion-1}

\section{Experiment 3a,b: Adding Negative
alternatives}\label{experiment-3ab-adding-negative-alternatives}

\subsection{Participants}\label{participants-2}

\subsection{Procedure}\label{procedure-2}

\subsection{Results and Discussion}\label{results-and-discussion-2}

\section{Model}\label{model}

\subsection{Details}\label{details}

\subsection{Model fitting and
comparison}\label{model-fitting-and-comparison}

\section{General Discussion}\label{general-discussion}

\section{Acknowledgements}\label{acknowledgements}

Thanks to NSF BCS \#XYZ. Thanks to Michael Franke, Judith Degen, and
Noah Goodman.

\section{References}\label{references}

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

\end{document}

### 2016-01-07 Paper/Paper.Rmd
super rough start on populating exp descriptions

@@
 
-# Experiment 1a,b: Entailment scales
+# Experiments - Literal listener and Pragmatic Listener tasks
+
+We used a food review paradigm to approximate semantic and pragmatic judgments for scalar items.
+Within this framework, 'meaning' for a given scalar term is quantified as a distribution over stars.
+Previous work has  a quantitative measures of what would otherwise be ambiguous literal listener semantics.
+Second, this framework
+
+it allowed us to assses both semantic and pragmatic judgments of scalar items.
+Second, it provided an empirical measure of literal semantics for otherwise ambiguous scalar items (scalar diversity approach).
+
+Semantic judgments were assessed through a compatibility measure in what we've called a 'Literal Listener' task.
+Participants were presented a star-rating (betwen 1-5 stars) and asked "Do you think the person thought the person *loved* the food." We used a binary dependent measure "yes/no" to assess compatibility.
+To assess pragmatic judgments in our 'Pragmatic Listener' task, participants were presented a sentence such as "Someone said they *loved* the food" and were asked to select the number of stars the reviewer likely gave.
+In this case, the dependent measure was a star-rating from 1-5 stars.
+
+# Experimental 1a,b: Entailment scales
+
+Experiment 1a and 1b were conducted to assess semantic and pragmatic judgments for positive valenced scalar terms (such as 'good' and 'excellent').
+See Appendix 'X' for the complete list of scalar terms.
 
 ## Participants
+Using Amazon's Mechanical Turk, N workers were paid $0.20 to particpate in the Literal Listener task and N workers were paid $0.20 to participate in the Pragmatic Listener task.
+n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers.
+The final sample was N workers, all of whom  were naive to the purposeof the experiment.
 
-## Procedure
+## Procedure - Literal Listener
+On each trial participants were presented with a star-rating and asked a question with an embedded scalar term such as, "Do you think the person *____*ed the food".
+Participants were asked to judge the compatibility of the target scalar term with the stars by selecting 'yes/no'.
+Each participant saw the full set of scalar item / star-ratings pairs.
+Scalar item and star-rating combinations were randomized for each participant.
 
@@
 
+Building off van Tiel (2014) we wanted to
+
 ## Participants
+Using Amazon's Mechanical Turk, N workers were paid $0.20 to particpate.
+n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers.
+The final sample was N workers, all of whom  were naive to the purposeof the experiment.
 
 ## Procedure
+
+Participants were presented a target scalar term embedded in a sentence such as, "In a recent restaurant review someone said they thought they *----*ed the food." Participants were then presented, "If they'd felt differently about the food, what other words could they have used instead of *----*?" and asked to generate three alternatives.
 

### 2016-01-11 Paper/Paper.Rmd
initially populated first 6 paragraphs. Initial population of Experiment descriptions.

--- 2016-01-05 Paper/Paper.Rmd
@@
 ---
-title: "The importance of negative alternatives in pragmatic implicature"
+title: "The importance of full scale representations in scalar implicature"
 bibliography: library.bib
@@
 
-author-information: > 
-    \author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University
+author-information: 
+    \author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloqui@stanford.edu} \\ Department of Psychology \\ Stanford University
     \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
@@
 abstract:
-    "Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly assume the presence of salient alternatives.
-For example, the standard quantity implicature arises the presence of a competiting and more informative alternatives.
-Using a Bayesian formulzation of this theory we assess the degree to which alternatives influence pragmatic enrichment of scalar items.
-Our findings suggest that the presence of a complete of set of possible alternatives."
+
+    Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
+In the canonical "some, but not all" scalar implicature, listeners enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "She ate some of the cookies." A Gricean account of this phenomena assumes the presence of "salient alternatives" with varying degrees of informatitivy.
+"Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." While intuitive, empirical evidence for the presence of such alternatives is limited.
+Our current work explores the role different scale representations may play in scalar implicature.
+Using a Bayesian model of implicature generation we simulate various scale representations that might be available to a listener, comparing model predictions to human judgment.
+Results indicate that implicature generation likely requires "full" scale representations, including negative valenced alternatives, rather than the typical entailment only scales assumed in most research to date.
 
@@
 
-Implicature as a case study for pragmatics
+Humpty Dumpty Quote...
 
-RSA as a way of studying implicature [@frank2012]
+[Implicature as a case study for pragmatics]\newline
+\textbf{Succesful communication regularly requires listeners to make inferences that go beyond the semantic content of a speaker's utterance.} "Scalar implicatures" are a hallmark of such pragamtic enrichment.
+For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies." (citations) A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
+Continuing with the prior example, within this framework a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* to use "some" when "all" could have been used.
 
-Scalar implicature in particular, what are the alternatives? [@franke2014] [@degen2015]
+[Scalar implicature in particular, what are the alternatives?]\newline
+\textbf{The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice)}.
+Previous research indicates implicature generation is affected by the set of alternatives available, both in adults (Degen, Franke) and is possibly the source of difficulty in computing implicatures for children (Barner).
+Degen found ...
+Similarily, Franke demonstrated...
+(the importance of a strong negative valenced term such as "none" adopting a Bayesian model of implicature generation.
+Model performance improved significantly when "none" was included...) Despite these signals, little empirical evidence points directly to the impact of scale representaion in scalar implicature.
+The current work investigates the role different scale representaitons play in scalar implicature.
 
-Using the scalar diversity approach to get beyond the some/all implicature [@vantiel2013]
+[RSA as a way of studying implicature]\newline
+\textbf{Measuring the degree to which alternatives may be present during implicature generation is a difficult task}.
+Issues of introspection aside, simply querying a participant about the apparent saliency of particular alternatives is problematic because the alternatives are made salient in the query itself.
+To circumvent this issue, we adopted a computational model of implicature generation.
+Adopting a computational framework allowed us to simulate the effects of various scalar alternatives sets on implicature generation, comparing model predictions to human judgments.
 
-Outline of the rest of the paper
+[How RSA works]\newline
+\textbf{Rational Speech-act theory (RSA) is a Bayesian framework for modeling scalar implicature.} How it works...
+Previous work using RSA has accurately modeled human judgments in both ad-hoc (Frank & Goodman, 2012) and embedded implicature settings (Stuhmuller & Goodman ...)....
 
-# Experiment 1a,b: Entailment scales
+[Using the scalar diversity approach to get beyond the some/all implicature]\newline
+\textbf{Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably focusing on "some/all".} This lack "Scalar Diversity" (van Tiel, 2013) not only presents a problem in terms of generalization of findings, but within our current computational framework, presents a problem of data sparsity.
+We adopt a "Scalar Diversity" approach in our experimental design in order to incorporate multiple scalar items from a range of grammatical classes.
+In particular, we use a food review paradigm to quantify what would otherwise be ambiguous semantics as distirbutions over star-ratings.
+
+[Outline of the rest of the paper]\newline
+\textbf{In the following paper we present three experiments and three model simulations based on the experimental data.} We used a food review paradigm in which linguistic `meaning' for a given scalar item was quantified as a distribution over star-ratings.
+Quantifying both literal semantic content and pragmatic judgments in this way provided an important interface to RSA, especially for scalar items with ambigous literal semantics (items such as "memorable/unforgettable" or "palatable/delicious).
+In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
+Alternatives generated in Experiment 2 supplmented the original stimuli from Experiments 1a,b in Experiments 3a,b.
+Using the literal semantic data from Experiments 1a and 3a we modeled pragmatic enrichment using RSA and compared model predictions to human judgment data from Experiments 1b and 3b.
+Results indicated that model performance was significantly improved with the incorporation of negative valenced scalar items.
+Indeed, peak model performance occurs for simulations with the ``fullest" scale representations.
+This result suggests that more "fully specified" scale representations may be active for human participants while making pragmatic judgments.
+
+# Experiments - Literal listener and Pragmatic Listener tasks
+
+We used a food review paradigm to quantify literal semantics and assess pragmatic judgments for scalar items.
+Within this framework, 'meaning' for a given scalar term is quantified as a distribution over stars.
+Literal semantics for scalar items was assessed through a compatibility measure in Experiments 1a and 3a.
+Participants were presented a star-rating (betwen 1-5 stars) and asked "Do you think the person *loved* the food." We used a binary dependent measure "yes/no" to assess compatibility.
+To assess pragmatic judgments, participants were presented a sentence such as "Someone said they *loved* the food" and asked to select the number of stars they thought the reviewer likely gave.
+In this case, the dependent measure was a star-rating from 1-5 stars.
+
+# Experimental 1a,b: Entailment scales
+
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (study 1a) and assess pragamtic judgments (study 1b) for positive valenced scalar pairs (see appendix A for the complete list).
 
@@
 
+Particpants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+Thirty participants were recruited for Experiment 1a (Literal Listener task).
+Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+
+Fifty particpants were recruited for Experiment 1b (Pragmatic Listener task).
+Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+
 ## Procedure
+
+On each trial of the literal listener task (study 1a) participants were presented with a star-rating (between 1-5 stars) and asked to judge the compatibility of the star-rating with a target scalar term.
+Compatibiltiy was assessed through a binary "yes/no" response to a question of the form "Do you think that the person \___ed the food?" where a target scalar was presented in the "\___ed." Each participant was presented all scalar item and star-rating combinations with randomization.
+
+On each trial of the pragmatic listener task (study 1b), participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they \___ed the food" and were asked to generate a star-rating according to what they think the reviewer likely gave.
+Each participant was presented all scalar items with randomization.
 
@@
 
+In Experiment 2 we asked participants to generate plausible alternatives for the scalar items presented in Experiment 1.
+
 ## Participants
+Using Amazon's Mechanical Turk, N workers were paid $0.20 to particpate.
+n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers.
+The final sample was N workers, all of whom  were naive to the purposeof the experiment.
 
 ## Procedure
+Participants were presented a target scalar term embedded in a sentence such as, "In a recent restaurant review someone said they thought they *----*ed the food." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of *----*?" and asked to generate three alternatives.
 
@@
 
-# Experiment 3a,b: Adding Negative alternatives
+# Experiment 3a,b: Full scales - incorporating negative alternatives
+
+Experiment 3a,b was conducted to approximate literal listener semantic distributions (study a) and assess pragamtic judgments (study b) for both positive and negative valenced scalar items (see appendix b for the complete list of items used).
 
 ## Participants
+
+Particpants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+Thirty participants were recruited for Experiment 3a (Literal Listener task).
+Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+
+Fifty particpants were recruited for Experiment 3b (Pragmatic Listener task).
+Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
 
@@
 \noindent
+
+the role various scale representations might play in scalar implicature.
+In Experiment 1a,b we gather data for Entailment only scalar items such as "some/all," "good/excellent," etc.
+In Experiment 1a we quantify literal semantics for scalar items as compatibility distributions over star-ratings (Literal listener task).
+In Experiment 1b, we ask participants to make judgments about speaker intentions by generating star-ratings in response to reviews (Pragmatic listener task).
+In Experiment 2, we ask participants to generate plausible alternatives to the scalar items used in Experiments 1a,b.
+Experiments 3a,b are identical to 1a,b with the addition of scalar items from Experiment 2.
+In this we explore fuller scale descriptions, gathering both literal semantics and pragmatic judgments for fuller scale descriptions such as "none/some/most/all" or "horrible/bad/good/excellent."
+
+In three experiments we 
+Our "Scalar Diversity" approach involves a food review paradigm we employed throughout our three experiments.
+In both Literal Listener (1a, 3a) and Pragmatic Listener (1b, 3b) tasks, participants are shown one sentence prompts containing a target scalar term along with a star-rating.
+In individual trials, star-ratings were either pre-populated (in literal listener tasks) or used as the dependent variable (pragmatic listener tasks).
+This design allowed us to quantify literal semantics for individual scalar terms as compatibility distributions over star-ratings (literal listener tasks 1a and 3a).
+Similarily, we quantified pragmatic judgments by prompting participants with a target scalar term and asking them to generate a star-rating.

### 2016-01-11 Paper/Paper.tex
initially populated first 6 paragraphs. Initial population of Experiment descriptions.

@@
 
-\title{The importance of negative alternatives in pragmatic implicature}
+\title{The importance of full scale representations in scalar implicature}
 
-\author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
+\author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloqui@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
 Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
@@
 \begin{abstract}
-Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly
-assume the presence of salient alternatives. For example, the standard
-quantity implicature arises the presence of a competiting and more
-informative alternatives. Using a Bayesian formulzation of this theory
-we assess the degree to which alternatives influence pragmatic
-enrichment of scalar items. Our findings suggest that the presence of a
-complete of set of possible alternatives.
+Succesful communication regularly requires listeners to make pragmatic
+inferences - enrichments beyond the literal meaning of a speaker's
+utterance. In the canonical ``some, but not all'' scalar implicature,
+listeners enrich the meaning of ``some'' to ``some, but not all'' when
+interpreting a sentence such as ``She ate some of the cookies.'' A
+Gricean account of this phenomena assumes the presence of ``salient
+alternatives'' with varying degrees of informatitivy. ``Some,'' in the
+example above, is enriched to ``some, but not all'' in the presence of
+the stronger alternative ``all.'' While intuitive, empirical evidence
+for the presence of such alternatives is limited. Our current work
+explores the role different scale representations may play in scalar
+implicature. Using a Bayesian model of implicature generation we
+simulate various scale representations that might be available to a
+listener, comparing model predictions to human judgment. Results
+indicate that implicature generation likely requires ``full'' scale
+representations, including negative valenced alternatives, rather than
+the typical entailment only scales assumed in most research to date.
 
@@
 
-Implicature as a case study for pragmatics
+Humpty Dumpty Quote\ldots{}
 
-RSA as a way of studying implicature ({\textbf{???}})
+{[}Implicature as a case study for pragmatics{]}\newline
+\textbf{Succesful communication regularly requires listeners to make inferences that go beyond the semantic content of a speaker's utterance.}
+``Scalar implicatures'' are a hallmark of such pragamtic enrichment. For
+example, listeners routinely enrich the meaning of the scalar item
+``some'' to ``some, but not all'' in sentences like ``Bob ate some of
+the cookies.'' (citations) A Gricean account of this phenomena assumes
+listeners reason about the intended meaning of a speaker while
+incorporating knowledge about a) alternative scalar items a speaker
+could have used (such as ``all'') and b) the relative informativity of
+using such alternatives (Grice, 1975). Continuing with the prior
+example, within this framework a listener will infer that the speaker
+must have intended that Bob did not eat ``all'' the cookies because it
+would have been \emph{underinformative} to use ``some'' when ``all''
+could have been used.
 
-Scalar implicature in particular, what are the alternatives?
-({\textbf{???}}) ({\textbf{???}})
+{[}Scalar implicature in particular, what are the
+alternatives?{]}\newline
+\textbf{The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice)}.
+Previous research indicates implicature generation is affected by the
+set of alternatives available, both in adults (Degen, Franke) and is
+possibly the source of difficulty in computing implicatures for children
+(Barner). Degen found \ldots{} Similarily, Franke demonstrated\ldots{}
+(the importance of a strong negative valenced term such as ``none''
+adopting a Bayesian model of implicature generation. Model performance
+improved significantly when ``none'' was included\ldots{}) Despite these
+signals, little empirical evidence points directly to the impact of
+scale representaion in scalar implicature. The current work investigates
+the role different scale representaitons play in scalar implicature.
 
-Using the scalar diversity approach to get beyond the some/all
-implicature ({\textbf{???}})
+{[}RSA as a way of studying implicature{]}\newline
+\textbf{Measuring the degree to which alternatives may be present during implicature generation is a difficult task}.
+Issues of introspection aside, simply querying a participant about the
+apparent saliency of particular alternatives is problematic because the
+alternatives are made salient in the query itself. To circumvent this
+issue, we adopted a computational model of implicature generation.
+Adopting a computational framework allowed us to simulate the effects of
+various scalar alternatives sets on implicature generation, comparing
+model predictions to human judgments.
 
-Outline of the rest of the paper
+{[}How RSA works{]}\newline
+\textbf{Rational Speech-act theory (RSA) is a Bayesian framework for modeling scalar implicature.}
+How it works\ldots{} Previous work using RSA has accurately modeled
+human judgments in both ad-hoc (Frank \& Goodman, 2012) and embedded
+implicature settings (Stuhmuller \& Goodman \ldots{})\ldots{}.
 
-\section{Experiment 1a,b: Entailment
-scales}\label{experiment-1ab-entailment-scales}
+{[}Using the scalar diversity approach to get beyond the some/all
+implicature{]}\newline
+\textbf{Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably focusing on "some/all".}
+This lack ``Scalar Diversity'' (van Tiel, 2013) not only presents a
+problem in terms of generalization of findings, but within our current
+computational framework, presents a problem of data sparsity. We adopt a
+``Scalar Diversity'' approach in our experimental design in order to
+incorporate multiple scalar items from a range of grammatical classes.
+In particular, we use a food review paradigm to quantify what would
+otherwise be ambiguous semantics as distirbutions over star-ratings.
+
+{[}Outline of the rest of the paper{]}\newline
+\textbf{In the following paper we present three experiments and three model simulations based on the experimental data.}
+We used a food review paradigm in which linguistic `meaning' for a given
+scalar item was quantified as a distribution over star-ratings.
+Quantifying both literal semantic content and pragmatic judgments in
+this way provided an important interface to RSA, especially for scalar
+items with ambigous literal semantics (items such as
+``memorable/unforgettable'' or ``palatable/delicious). In addition to
+quantifying literal semantics and pragmatic judgments in Experiments
+1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
+based on van Tiel (2013, Experiment 2???), to generate a set of
+plausible alternatives to the scalar items used in Experiments 1a,b.
+Alternatives generated in Experiment 2 supplmented the original stimuli
+from Experiments 1a,b in Experiments 3a,b. Using the literal semantic
+data from Experiments 1a and 3a we modeled pragmatic enrichment using
+RSA and compared model predictions to human judgment data from
+Experiments 1b and 3b. Results indicated that model performance was
+significantly improved with the incorporation of negative valenced
+scalar items. Indeed, peak model performance occurs for simulations with
+the ``fullest'' scale representations. This result suggests that more
+``fully specified'' scale representations may be active for human
+participants while making pragmatic judgments.
+
+\section{Experiments - Literal listener and Pragmatic Listener
+tasks}\label{experiments---literal-listener-and-pragmatic-listener-tasks}
+
+We used a food review paradigm to quantify literal semantics and assess
+pragmatic judgments for scalar items. Within this framework, `meaning'
+for a given scalar term is quantified as a distribution over stars.
+Literal semantics for scalar items was assessed through a compatibility
+measure in Experiments 1a and 3a. Participants were presented a
+star-rating (betwen 1-5 stars) and asked ``Do you think the person
+\emph{loved} the food.'' We used a binary dependent measure ``yes/no''
+to assess compatibility. To assess pragmatic judgments, participants
+were presented a sentence such as ``Someone said they \emph{loved} the
+food'' and asked to select the number of stars they thought the reviewer
+likely gave. In this case, the dependent measure was a star-rating from
+1-5 stars.
+
+\section{Experimental 1a,b: Entailment
+scales}\label{experimental-1ab-entailment-scales}
+
+Experiment 1a and 1b were conducted to approximate literal listener
+semantic distributions (study 1a) and assess pragamtic judgments (study
+1b) for positive valenced scalar pairs (see appendix A for the complete
+list).
 
@@
 
+Particpants for both studies were recruited on Amazon Mechanical Turk
+and paid \$0.20 for their participation. Thirty participants were
+recruited for Experiment 1a (Literal Listener task). Data for N
+particpants was thrown out after particpants either failed to pass two
+training trials or were not native English speakers, leaving a total
+sample of N.
+
+Fifty particpants were recruited for Experiment 1b (Pragmatic Listener
+task). Data for N particpants was thrown out after particpants either
+failed to pass two training trials or were not native English speakers,
+leaving a total sample of N.
+
 \subsection{Procedure}\label{procedure}
+
+On each trial of the literal listener task (study 1a) participants were
+presented with a star-rating (between 1-5 stars) and asked to judge the
+compatibility of the star-rating with a target scalar term.
+Compatibiltiy was assessed through a binary ``yes/no'' response to a
+question of the form ``Do you think that the person \_\_\_ed the food?"
+where a target scalar was presented in the ``\_\_\_ed." Each participant
+was presented all scalar item and star-rating combinations with
+randomization.
+
+On each trial of the pragmatic listener task (study 1b), participants
+were presented with a one-sentence prompt containing a target scalar
+item such as ``Someone said they \_\_\_ed the food" and were asked to
+generate a star-rating according to what they think the reviewer likely
+gave. Each participant was presented all scalar items with
+randomization.
 
@@
 
+In Experiment 2 we asked participants to generate plausible alternatives
+for the scalar items presented in Experiment 1.
+
 \subsection{Participants}\label{participants-1}
+
+Using Amazon's Mechanical Turk, N workers were paid \$0.20 to
+particpate. n workers were dropped from the analysis because they either
+failed to pass training trials or were not native English speakers. The
+final sample was N workers, all of whom were naive to the purposeof the
+experiment.
 
@@
 
+Participants were presented a target scalar term embedded in a sentence
+such as, ``In a recent restaurant review someone said they thought they
+\emph{----}ed the food.'' Participants were then asked to generate
+plausible alternatives by responding to the question, ``If they'd felt
+differently about the food, what other words could they have used
+instead of \emph{----}?'' and asked to generate three alternatives.
+
 \subsection{Results and Discussion}\label{results-and-discussion-1}
 
-\section{Experiment 3a,b: Adding Negative
-alternatives}\label{experiment-3ab-adding-negative-alternatives}
+\section{Experiment 3a,b: Full scales - incorporating negative
+alternatives}\label{experiment-3ab-full-scales---incorporating-negative-alternatives}
+
+Experiment 3a,b was conducted to approximate literal listener semantic
+distributions (study a) and assess pragamtic judgments (study b) for
+both positive and negative valenced scalar items (see appendix b for the
+complete list of items used).
 
 \subsection{Participants}\label{participants-2}
+
+Particpants for both studies were recruited on Amazon Mechanical Turk
+and paid \$0.20 for their participation. Thirty participants were
+recruited for Experiment 3a (Literal Listener task). Data for N
+particpants was thrown out after particpants either failed to pass two
+training trials or were not native English speakers, leaving a total
+sample of N.
+
+Fifty particpants were recruited for Experiment 3b (Pragmatic Listener
+task). Data for N particpants was thrown out after particpants either
+failed to pass two training trials or were not native English speakers,
+leaving a total sample of N.
 
@@
 
+the role various scale representations might play in scalar implicature.
+In Experiment 1a,b we gather data for Entailment only scalar items such
+as ``some/all,'' ``good/excellent,'' etc. In Experiment 1a we quantify
+literal semantics for scalar items as compatibility distributions over
+star-ratings (Literal listener task). In Experiment 1b, we ask
+participants to make judgments about speaker intentions by generating
+star-ratings in response to reviews (Pragmatic listener task). In
+Experiment 2, we ask participants to generate plausible alternatives to
+the scalar items used in Experiments 1a,b. Experiments 3a,b are
+identical to 1a,b with the addition of scalar items from Experiment 2.
+In this we explore fuller scale descriptions, gathering both literal
+semantics and pragmatic judgments for fuller scale descriptions such as
+``none/some/most/all'' or ``horrible/bad/good/excellent.''
+
+In three experiments we Our ``Scalar Diversity'' approach involves a
+food review paradigm we employed throughout our three experiments. In
+both Literal Listener (1a, 3a) and Pragmatic Listener (1b, 3b) tasks,
+participants are shown one sentence prompts containing a target scalar
+term along with a star-rating. In individual trials, star-ratings were
+either pre-populated (in literal listener tasks) or used as the
+dependent variable (pragmatic listener tasks). This design allowed us to
+quantify literal semantics for individual scalar terms as compatibility
+distributions over star-ratings (literal listener tasks 1a and 3a).
+Similarily, we quantified pragmatic judgments by prompting participants
+with a target scalar term and asking them to generate a star-rating.
+
 \end{document}

### 2016-01-11 Paper/Paper.Rmd
title tweaks

@@
 ---
-title: "The importance of full scale representations in scalar implicature"
+title: "The importance of negative alternatives in scalar implicature"
 bibliography: library.bib

### 2016-01-12 models/Model_Comparison.Rmd
descending order for scale entropy measures
correlation plotting for langcog meeting on Tuesday 1.12.16

@@
           (data.full[, "degree"] == "hi1" | data.full[, "degree"] == "low1")))
+# Run if looking at MLE alts
+# --------------------------
 matched.items.extras = which((data.full.extras[, "scale"] != "some_all" &
@@
 # Save performance output
-performance.output = data.frame(model=rep(NA, 16),
-                                cor.e6=rep(NA, 16),
-                                cor.e11=rep(NA, 16),
-                                normalized=rep(NA, 16))
-alphas = rep(NA, 16)
+performance.output = data.frame(model=rep(NA, 20),
+                                cor.e6=rep(NA, 20),
+                                cor.e11=rep(NA, 20),
+                                normalized=rep(NA, 20))
+alphas = rep(NA, 20)
 data.full.transfer = data.full[matched.items, ]
@@
   geom_line(aes(y = pred), lty = 4)
+
+# Model 5 - Empirical alternatives + Empircal extras (e12)
+# -----------------------------------------
+
+# Run if looking at e12 data
+# --------------------------
+matched.items.extras = which((data.full.extras[, "scale"] != "some_all" &
+        (data.full.extras[, "degree"] == "hi2" | data.full.extras[, "degree"] == "hi1")) |
+       (data.full.extras[, "scale"] == "some_all" &
+          (data.full.extras[, "degree"] == "hi1" | data.full.extras[, "degree"] == "mid")))
+
+speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e12.csv")
+data.full.extras = left_join(speaker, listener) %>%
+  left_join(priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
+  group_by(scale)
+
+# 5.a)
+# Emp alts + extras
+# Normalized = T
+# alpha tuning = F
+alphas[17] = 1
+m5.a = data.full.extras %>%
+  do(run.full(., alpha = alphas[17], addMid=T, normalize=T))
+# Match with e6 w/ checks
+m5.a.matched = m5.a[matched.items.extras, ]
+m5.a.matched$degree = ifelse(m5.a.matched$degree == "hi1", "hi", "low")
+m5.a.matched = cbind(m5.a.matched, data.partial$listener.p)
+all(m5.a.matched$scale == data.partial$scale & m5.a.matched$degree == data.partial$degree)
+colnames(m5.a.matched)[length(colnames(m5.a.matched))] = "e6.listener.p"
+# Store output
+performance.output[17, ] = c("m5.a", round(cor(m5.a.matched$e6.listener.p, m5.a.matched$pred), 5), 
+                             round(cor(m5.a.matched$listener.p, m5.a.matched$pred), 5), T)
+# Store plot
+m5.a.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m5.a.matched,
+      main=paste("m5.a\nalpha: ", alphas[17],
+                 "\nNormalized = ", T,
+                 "\nCorr = ", performance.output[17, 2]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 5.b)
+# Emp alts + extras
+# Normalized = F
+# alpha tune = F
+alphas[18] = 1
+m5.b = data.full.extras %>%
+  do(run.full(., alpha = alphas[18], addMid=T, normalize=F))
+# Match with e6 w/ checks
+m5.b.matched = m5.b[matched.items.extras, ]
+m5.b.matched$degree = ifelse(m5.b.matched$degree == "hi1", "hi", "low")
+m5.b.matched = cbind(m5.b.matched, data.partial$listener.p)
+all(m5.b.matched$scale == data.partial$scale & m5.b.matched$degree == data.partial$degree)
+colnames(m5.b.matched)[length(colnames(m5.b.matched))] = "e6.listener.p"
+# Store output
+performance.output[18, ] = c("m5.b", round(cor(m5.b.matched$e6.listener.p, m5.b.matched$pred), 5), 
+                             round(cor(m5.b.matched$listener.p, m5.b.matched$pred), 5), F)
+# Store plot
+m5.b.plot = qplot(stars, e6.listener.p, col=degree, 
+      data=m5.b.matched,
+      main=paste("m5.b\nalpha: ", alphas[18],
+                 "\nNormalized = ", F,
+                 "\nCorr = ", performance.output[18, 2]),
+      ylab="Posterior p(rating | word)") + 
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 5.c)
+# Emp alts + extras
+# Normalized = T
+# alpha tune = T
+# compare.data = Toggle this with data.partial or NULL
+alphas[19] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=T)
+m5.c = data.full.extras %>%
+  do(run.full(., alpha = alphas[19], addMid=T, normalize=T))
+# Match with e6 w/ checks
+m5.c.matched = m5.c[matched.items.extras, ]
+m5.c.matched$degree = ifelse(m5.c.matched$degree == "hi1", "hi", "low")
+m5.c.matched = cbind(m5.c.matched, data.partial$listener.p)
+all(m5.c.matched$scale == data.partial$scale & m5.c.matched$degree == data.partial$degree)
+colnames(m5.c.matched)[length(colnames(m5.c.matched))] = "e6.listener.p"
+# Store output (e11 and e6)
+performance.output[19, ] = c("m5.c", round(cor(m5.c.matched$e6.listener.p, m5.c.matched$pred), 5),
+                             round(cor(m5.c.matched$listener.p, m5.c.matched$pred), 5), T)
+
+# Store plot 2 - both e6 and e11 data
+m5.c.jointD = m5.c.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m5.c.jointD$study = ifelse(m5.c.jointD$study == "e6.listener.p", "e6", "e11")
+m5.c.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m5.c.jointD,
+      main=paste("m5.c\nalpha: ", alphas[19],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+
+# 5.d)
+# Emp alts + extras
+# Normalized = F
+# alpha tune = T
+# compare.data = Toggle this with data.partial or NULL
+alphas[20] = tune.alpha(data.full.extras, type = "full", compare.data=data.partial, addMid=T, normalize=F)
+m5.d = data.full.extras %>%
+  do(run.full(., alpha = alphas[20], addMid=T, normalize=F))
+# Match with e6 w/ checks
+m5.d.matched = m5.d[matched.items.extras, ]
+m5.d.matched$degree = ifelse(m5.d.matched$degree == "hi1", "hi", "low")
+m5.d.matched = cbind(m5.d.matched, data.partial$listener.p)
+all(m5.d.matched$scale == data.partial$scale & m5.d.matched$degree == data.partial$degree)
+colnames(m5.d.matched)[length(colnames(m5.d.matched))] = "e6.listener.p"
+# Store output
+performance.output[20, ] = c("m5.d", round(cor(m5.d.matched$e6.listener.p, m5.d.matched$pred), 5),
+                             round(cor(m5.d.matched$listener.p, m5.d.matched$pred), 5), F)
+
+# Store plot 2 - both e6 and e11 data
+m5.d.jointD = m5.d.matched %>%
+  gather(study, listener.pred, listener.p, e6.listener.p)
+m5.d.jointD$study = ifelse(m5.d.jointD$study == "e6.listener.p", "e6", "e11")
+m5.d.jointPlot = qplot(stars, listener.pred, col=degree, shape=study,
+      data=m5.d.jointD,
+      main=paste("m5.d\nalpha: ", alphas[20],
+                 "\nNormalized = ", T,
+                 ylab="Posterior p(rating | word)")) +
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = pred), lty = 4)
+```
+
+## Looking at empirically derived 'mids'
+```{r}
+normalize = function(w) { return (w / sum(w))}
+
+scalars = c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+
+for (scale in scalars) {
+  degrees = unique(data.full.extras$degree)
+  for (degree in degrees) {
+    data.full.extras[data.full.extras$scale == scale &
+                       data.full.extras$degree == degree, ]$speaker.p = 
+        normalize(data.full.extras[data.full.extras$scale == scale &
+                                     data.full.extras$degree == degree, ]$speaker.p)
+  }
+}
+
+# Differentiate tuned 'mid' scalar
+plot.data = data.full.extras
+plot.data$type = ifelse((plot.data$degree == "mid" & plot.data$scale != "some_all") |
+                          (plot.data$degree == "low1" & plot.data$scale == "some_all"), "red", "blue")
+qplot(x = stars, y = speaker.p, colour = type,
+      geom = "line", stat = "identity", position = "dodge", 
+      main = "Literal listener semantics\nEmpirical estimates and tuned extra 'mid'",
+      ylab = "P_{L0}(Word | Rating) - Normalized",
+      data = plot.data) + 
+  facet_wrap(~scale + degree)
 ```
@@
 
+Output for LangCog Lab meeting 1/12/16
+```{r}
+# Relevant studies into long data
+plot.data <- subset(performance.output, model %in% c("m1.c", "m2.c", "m3.c"))
+plot.data <- plot.data %>%
+  gather(exp, cor, -c(normalized, model))
+ggplot(plot.data, aes(x=model, y=cor, fill=exp)) +
+  geom_bar(stat="identity", position="dodge") +
+  ylim(0.0, 1.0)
+```
+
 # Interpretation
@@
 # Tuned, normalized models r
-barchart.d = performance.output[c(3, 7, 11, 15), ] %>%
+barchart.d = performance.output[c(3, 7, 11), ] %>%
   gather(study, cor, cor.e6, cor.e11)
+barchart.d$model <- as.factor(barchart.d$model)
+levels(barchart.d$model) <- c("Entailment only",
+                              "Entailment + \ngeneric none",
+                              "Full model")
 barchart.d$cor = as.numeric(barchart.d$cor)
-ggplot(barchart.d, aes(x=model, y=cor, fill=study)) + 
+cor.chart <- ggplot(barchart.d, aes(x=model, y=cor, fill=study)) + 
   geom_bar(stat="identity", position="dodge") +
+  ylab("Correlation") +
+  xlab("Model") +
   ylim(0, 1) + 
-  ggtitle("Model fit for e6 and e11\npragmatic listener judgments") +
+  ggtitle("Model fit correlation coefficients") +
+  guides(colour=FALSE) +
   geom_text(aes(x=model, y=as.numeric(cor) + 0.025, label=round(cor, 3), col=(study)))
+
+png(filename="practiceChart.png", 
+    #type="cairo",
+    units="in", 
+    width=10, 
+    height=8, 
+    pointsize=12, 
+    res=96)
+cor.chart
+dev.off()
 ```
@@
 # entropy measures 
-scales.entropy
+scales.entropy[order(scales.entropy$Entropy, decreasing=T),]
 ```
@@
 m2.b.plot
+m2.d.plot
 m2.c.plot
-m2.d.plot
 

### 2016-01-18 models/RSA_alternativeCostFormulation.Rmd
re-written runRSA, better incorporation of costs and priors

---
title: "alternativeRSA"
author: "Ben Peloquin"
date: "January 13, 2016"
output: html_document
---

```{r}
rm(list = ls())
library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)
library(gridExtra)
```

Old RSA formulation
```{r}
# speaker informativity
# ---------------------
speaker.inf = function(d, alpha, cost = 0) {
  exp(alpha*(log(d) - cost))
}
# speaker likelihood
# ------------------
speaker.lhd = function(rating, degree, m, alpha) {
  numerator = speaker.inf(m[rating, degree], alpha)
  normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
  return(numerator / normalize)
}
# non-normalized posterior
# -----------------------
nn.post = function(rating, degree, m, alpha, useprior) {
  prior = priors[rating, "prior.p"]
  return(speaker.lhd(rating, degree, m, alpha) * prior)
}
# normalized posterior
# --------------------
norm.post = function(rating, degree, m, alpha, useprior) {
  nn = nn.post(rating, degree, m, alpha, useprior)
  normalize = sum(unlist(sapply(seq(1, 5),
                                function(i){nn.post(i, degree, m, alpha, useprior)})))
  return(nn / normalize)
}
```

New Prior incorporation
```{r}
speaker.inf3 = function(d, alpha, cost = 0) {
  exp(alpha*(log(d) - cost))
}
# speaker likelihood
# ------------------
speaker.lhd3 = function(currRating, currDegree, m, alpha, costs, allDegrees) {
  currCost <- subset(costs, degree == currDegree)$cost
  numerator = speaker.inf3(m[[currDegree]][currRating], alpha, currCost)
#   normalize = sum(unlist(sapply(seq(nrow(m)),
#                                 function(i) {
#                                   speaker.inf3(m[i, currDegree],
#                                                alpha,
#                                                subset(costs, degree == currDegree)$cost)})))
  # normalize over other words
  normalize <- sum(sapply(seq(allDegrees), FUN = 
                            function(i) {
                              speaker.inf(m[[allDegrees[i]]][currRating], alpha,
                                          subset(costs, degree == allDegrees[i])$cost)}
                          ))
  return(numerator / normalize)
  # return(numerator)
}
# old !!!!
# speaker.lhd = function(rating, degree, m, alpha) {
#   numerator = speaker.inf(m[rating, degree], alpha)
#   normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
#   return(numerator / normalize)
# }

# non-normalized posterior
# -----------------------
nn.post3 = function(currRating, currDegree, m, alpha, costs, priors, allDegrees) {
  # prior <- priors[rating, "prior.p"]
  # prior <- costs[degree]
  currPrior <- subset(priors, stars == currRating)$prior.p
  return(speaker.lhd3(currRating, currDegree, m, alpha, costs, allDegrees) * currPrior)
}
# normalized posterior
# --------------------
norm.post3 = function(currRating, currDegree, m, alpha, costs, priors, allDegrees) {
  nn <- nn.post3(currRating, currDegree, m, alpha, costs, priors, allDegrees)
  normalize <- sum(unlist(sapply(seq(1, 5),
                                function(i) {
                                  nn.post3(i, currDegree, m, alpha, costs, priors, allDegrees)}
                                )))
  return(nn / normalize)
}

normedVec <- function(vec) {
  vec / sum(vec)
}
```

New run fn()
```{r}
computePosteriors <- c(norm.post, norm.post3)
runFull2 <- function(data, calcFn = 1, alpha = 1) {
#############################################################################
## data       => contains scale | degree | stars | speaker.p | prior.p | cost
## calcFN     => without cost = 1, with cost = 2
## alpha      => set alpha level

  results <-
    data.frame(scale = c(),
               stars = c(),
               degree = c(),
               preds = c())

  scales <- unique(data$scale)
  for (s in scales) {
    force(
      mat <- subset(data, scale  == s) %>%
        select(stars, degree, speaker.p) %>%
        spread(degree, speaker.p) %>%
#         mutate(hi1 = hi1 / sum(hi1),
#                hi2 = hi2 / sum(hi2),
#                mid = mid / sum(mid),
#                low1 = low1 / sum(low1),
#                low2 = low2 / sum(low2)) %>%
        select(hi1, hi2, mid, low1, low2)
      )
    stars <- subset(data, scale == s)$stars
    degrees <- as.character(subset(data, scale == s)$degree)
    currCosts <- unique(subset(data, scale == s) %>% select(degree, cost))
    priors <- data %>% select(c(stars, prior.p)) %>% head(., n=5)

    results <- rbind(results,
                     data.frame(scale = s,
                                preds =
                                  as.numeric(mapply(computePosteriors[[calcFn]],
                                                    stars,
                                                    degrees,
                                                    MoreArgs =
                                                      list(m = mat,
                                                           alpha = alpha,
                                                           costs = currCosts,
                                                           priors = priors,
                                                           allDegrees = unique(degrees)))),
                                stars = stars,
                                degree = degrees,
                                stringsAsFactors = FALSE))
  }
  left_join(data, results)
}
```

Data
```{r}
# priors
# -------
unifPriors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empPriors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
salience <- c(0.22, 0.08, 0.05, 1, 1)
saliencePriors <- data.frame(stars=1:5, prior.p = (salience / sum(salience)))
salienceCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
                            cost = -1 * (salience / sum(salience)), stringsAsFactors = FALSE)
emptyCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
yelpPriors <- data.frame(stars=1:5,
                         prior.p =
                           c(0.090190981, 0.105689431, 0.162783722, 0.304569543, 0.336766323))

# speaker
speakerL12 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e12.csv")
speakerL10 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
speakerL08 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
# listener
listener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")

costs <- salienceCosts
priors <- unifPriors

data <- left_join(speakerL12, costs) %>%
  left_join(., priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, prior.p, cost) %>%
  group_by(scale)
```

Explore
```{r}
test <- runFull2(data, calcFn = 2, alpha = 20)

predDf <- test
getOverallCor <- function(predDf, listenerDf) {
  combinedDf <- data.frame(scale = c(), degree = c(), speaker.p = c(), prior.p = c(), cost = c(), preds = c())
  for (s in unique(predDf$scale)) {
    if (s == "some_all") {
      tempDf <- subset(predDf, scale == s & (degree == "hi1" | degree == "mid")) %>%
        mutate(degree = ifelse(degree == "hi1", "hi", "low"))  
    } else {
      tempDf <- subset(predDf, scale == s & (degree == "hi1" | degree == "hi2")) %>%
        mutate(degree = ifelse(degree == "hi1", "hi", "low"))  
    }
    combinedDf <- rbind(combinedDf, tempDf)
  }
  results <- merge(x = combinedDf,
                   y = listenerDf,
                   by = c("degree", "stars", "scale"),
                   all.x = TRUE) %>%
    mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))

  cor(results$preds, results$listener.p)
}
getOverallCor(test, listener)

tuneAlphas <- function(alphas = seq(1, 12), humanDf) {
  sapply(alphas, function(i) {
    predDf <- runFull2(data, calcFn = 2, alpha = i)
    getOverallCor(predDf, humanDf)
    })
}
tuneAlphas(humanDf = listener)
```

```{r}

normedVec(subset(test, scale == "good_excellent" & degree == "hi1")$preds)
#normedVec(subset(test, scale == "good_excellent" & degree == "mid")$preds)
sum(subset(test, scale == "good_excellent" & degree == "hi1")$preds)
dfPreds <- test
dfHuman <- listener
name <- "good_excellent"
getCorrs <- function(dfPreds, dfHuman, name) {
  predSubset <- subset(dfPreds, scale == name & (degree == "hi1" | degree == "hi2"))
  predSubset$degree = with(predSubset,
                           ifelse(degree == "hi1", "hi", "low"))
  humanSubset <- subset(dfHuman, scale == name)
  joinedDf <- merge(x = predSubset,
                    y = humanSubset,
                    by = c("degree", "stars", "scale"),
                    all.x = TRUE) %>%
    mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))
  cor(joinedDf$preds, joinedDf$listener.p)
}

getCorrs(test, listener, "good_excellent")
getCorrs(test, listener, "liked_loved")
getCorrs(test, listener, "memorable_unforgettable")
getCorrs(test, listener, "palatable_delicious")

######################################################################
----------------------------------------------------------------------
######################################################################

runModel <- function(model, mat, degree, alpha) {
  if (model == 1) unlist(mapply(seq(1,5),
                                FUN=function(x) norm.post(x, degree, mat, alpha, priors)))
}
mat <- data %>% 
  select(stars, degree, speaker.p) %>%
  spread(degree, speaker.p) %>%
  mutate(hi1 = hi1 / sum(hi1),
         hi2 = hi2 / sum(hi2),
         mid = mid / sum(mid),
         low1 = low1 / sum(low1),
         low2 = low2 / sum(low2)) %>%
  select(hi1, hi2, mid, low1, low2)

runModel(1, mat[1:5, ], 1, 6)
runModel(1, mat[1:5, ], 2, 6)

subset(listener, scale == "good_excellent")

```

New cost formulation
```{r}
speaker.inf2 = function(d, alpha, cost = 0) {
  exp(alpha*(log(d) - cost))
}
# speaker likelihood
# ------------------
speaker.lhd2 = function(rating, degree, m, alpha, costs) {
  numerator = speaker.inf2(m[rating, degree], alpha, costs[degree])
  normalize = sum(unlist(sapply(seq(nrow(m)),
                                function(i) {speaker.inf2(m[i, ], alpha, costs[degree])})))
  return(numerator / normalize)
  # return(numerator)
}
# non-normalized posterior
# -----------------------
nn.post2 = function(rating, degree, m, alpha, costs, useprior) {
  prior = priors[rating, "prior.p"]
  # prior <- 0.2
  return(speaker.lhd2(rating, degree, m, alpha, costs) * prior)
}
# normalized posterior
# --------------------
norm.post2 = function(rating, degree, m, alpha, costs, useprior) {
  nn = nn.post2(rating, degree, m, alpha, costs, useprior)
  normalize = sum(unlist(sapply(seq(1, 5),
                                function(i){nn.post2(rating, i, m, alpha, costs, useprior)})))
  return(nn / normalize)
}
```

```{r}
# good excellent
mat[1:5,]
salience <- c(1, 1, 0.05, 0.08, 0.22)
normed.salience <- -1 * (salience / sum(salience))

normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 1, mat[1:5,], 5, normed.salience))))
normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 2, mat[1:5,], 5, normed.salience))))

#################################
# good_excellent
# --------------
# low
good.exc.low <-
  listener[with(listener, which(scale == "good_excellent" & degree == "low")),]$listener.p %>%
  c(. , rep(0, 2))
# high
good.exc.high <-
  listener[with(listener, which(scale == "good_excellent" & degree == "hi")),]$listener.p %>%
  c(. , rep(0, 3))
# new formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 2, mat[1:5,], 7, normed.salience)))),
    good.exc.low[c(5, 4, 1, 2, 3)])
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 1, mat[1:5,], 7, normed.salience)))),
    good.exc.high[c(5, 4, 3, 1, 2)])
# old formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 2, mat[1:5,], 7)))),
    good.exc.low[c(5, 4, 1, 2, 3)])
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 1, mat[1:5,], 7)))),
    good.exc.high[c(5, 4, 3, 1, 2)])

#################################
# liked_loved
# low
liked.loved.low <-
  listener[with(listener, which(scale == "liked_loved" & degree == "low")),]$listener.p %>%
  c(. , rep(0, 2))
# high
liked.loved.high <-
  listener[with(listener, which(scale == "liked_loved" & degree == "hi")),]$listener.p %>%
  c(. , rep(0, 3))
# new formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 2, mat[6:10,], 7, normed.salience)))),
    liked.loved.low[c(5, 1, 2, 3, 4)])
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 1, mat[6:10,], 7, normed.salience)))),
    liked.loved.high[c(5, 4, 3, 1, 2)])
# old formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 2, mat[6:10,], 7)))),
    liked.loved.low[c(5, 1, 2, 3, 4)])
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 1, mat[6:10,], 7)))),
    liked.loved.high[c(5, 4, 3, 1, 2)])

#################################
# memorable_unforgettable
# low
mem.unf.low <-
  listener[with(listener, which(scale == "memorable_unforgettable" & degree == "low")),]$listener.p %>%
  c(. , rep(0, 3))
mem.unf.low <- mem.unf.low[c(5, 4, 3, 2, 1)]
# high
mem.unf.high <-
  listener[with(listener,
                which(scale == "memorable_unforgettable" & degree == "hi")),]$listener.p %>%
  c(. , rep(0, 1))
mem.unf.high <- mem.unf.high[c(1, 5, 2, 3, 4)]
# new formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 2, mat[11:15,], 7, normed.salience)))),
    mem.unf.low)
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post2(x, 1, mat[6:10,], 7, normed.salience)))),
    mem.unf.high)
# old formulations
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 2, mat[6:10,], 3)))),
    mem.unf.low)
cor(normalize(unlist(mapply(seq(1,5),
                        FUN=function(x) norm.post(x, 1, mat[6:10,], 7)))),
    mem.unf.high)
```

How to implement this using saliency rewards (negative costs)???
```{r}
run.newCosts = function(d, alpha=1, useprior=F, usenone=F, normalize=F) {
  mat <- data.full.extras %>% 
    select(stars, degree, speaker.p) %>%
    spread(degree, speaker.p) %>%
    select(hi1, hi2, mid, low1, low2)

  if (usenone) {
    mat$none = c(1, 0, 0, 0, 0)
  } 
  d$degree <- with(d, ifelse(degree == "hi1", 5,
                             ifelse(degree == "hi2", 4,
                                    ifelse(degree == "mid", 3, 
                                           ifelse(degree == "low1", 2, 3)))))
  d$pred = round(as.numeric(mapply(norm.post2, d$stars, d$degree, 
                                    MoreArgs = list(m = mat, 
                                                    alpha = alpha,
                                                    costs = normed.salience,
                                                    useprior = useprior))), 
                  digits=4)

  return(normalize(d))
}
run.newCosts(data.full.extras, alpha=7, useprior=TRUE, usenone=FALSE, normalize=normalize)
```

Old `run` function
```{r}
run.full = function(d, alpha=1, useprior=F, usenone=F, addMid=F, normalize=F) {
  # alpha = scales.entropy[scales.entropy$scale==d$scale[1], ]$Entropy
  if (addMid) {
    if (normalize) {
      mat = d %>%
        select(stars, degree, speaker.p) %>%
        spread(degree, speaker.p) %>%
        mutate(hi1 = hi1 / sum(hi1),
               hi2 = hi2 / sum(hi2),
               mid = mid / sum(mid),
               low1 = low1 / sum(low1),
               low2 = low2 / sum(low2)) %>%
        select(hi1, hi2, mid, low1, low2)    
    } else {
      mat = d %>%
        select(stars, degree, speaker.p) %>%
        spread(degree, speaker.p) %>%
        select(hi1, hi2, mid, low1, low2)    
    }
  } else {
    if (normalize) {
      mat = d %>%
        select(stars, degree, speaker.p) %>%
        spread(degree, speaker.p) %>%
        mutate(hi1 = hi1 / sum(hi1),
               hi2 = hi2 / sum(hi2),
               low1 = low1 / sum(low1),
               low2 = low2 / sum(low2)) %>%
        select(hi1, hi2, low1, low2)
    } else {
      mat = d %>%
        select(stars, degree, speaker.p) %>%
        spread(degree, speaker.p) %>%
        select(hi1, hi2, low1, low2)
    }
  }

  if (usenone) {
    mat$none = c(1, 0, 0, 0, 0)
  }

  d$pred = round(as.numeric(mapply(norm.post, d$stars, d$degree, 
                                    MoreArgs = list(m = mat, 
                                                    alpha = alpha, 
                                                    useprior = useprior))), 
                  digits=4)

  return(d)
}
```

```{r}
run.full(data.full.extras, useprior = TRUE, usenone = FALSE, addMid = TRUE, normalize = TRUE)
cor(data.full.extras$listener.p, data.full.extras$pred)
```

### 2016-01-18 models/midScalarInvestigation.Rmd
added salience numbers and CSV

@@
 
-d.all = d$all
 d.all = as.data.frame(as.factor(d.all))
@@
   ggtitle("e9 - alternatives to 'all'")
+
+d.good = d$good
+d.good = as.data.frame(as.factor(d.good))
+d.good = as.data.frame(table(d.good))
+d.good = d.good[rev(order(d.good$Freq)), ]
+d.good$prop = d.good$Freq / sum(d.good$Freq)
+ggplot(d.good, aes(x=reorder(d.good, Freq), y=Freq)) +
+  geom_bar(stat="identity", position="dodge") +
+  xlab("alternatives") +
+  ylab("frequency counts") +
+  ggtitle("e9 - alternatives to 'good'")
+# bad
+d.good[d.good$d.good == "bad", "prop"] / sum(d.good$prop)
+# terrrible
+d.good[d.good$d.good == "terrible", "prop"] / sum(d.good$prop)
+salience <- c(1, 1, 0.05, 0.08, 0.22)
+normed.salience <- salience / sum(salience)
+
+top.4 <- data.frame(c("excellent", "good", "okay", "bad", "terrible"),
+                    c(1, 1, 0.05, 0.22))
 ```
+
+```{r}
+d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T) %>% as.data.frame(., stingasFactors = FALSE)
+
+scales <- c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+degrees <- c("hi1", "hi2", "mid", "low1", "low2")
+
+# alternative counts
+altCounts <- data.frame(Var1 = c(), Freq = c(), percent = c())
+for (s in scales) {
+  scaleHeads <- strsplit(s, "_")[[1]]
+  s1 <- scaleHeads[1]
+  s2 <- scaleHeads[2]
+  combinedDf <- rbind(as.data.frame(table(d[, s1])), as.data.frame(table(d[, s2]))) %>%
+    aggregate(Freq ~ Var1 ,data = ., FUN = sum) %>%
+    mutate(scale = s,
+           percent = Freq / sum(Freq))
+  altCounts <- rbind(altCounts, combinedDf)
+}
+fullScales <- c("excellent", "good", "okay", "bad", "terrible",
+               "loved", "liked", "indifferent", "disliked", "hated",
+               "delicious", "palatable", "mediocre", "gross", "disgusting",
+               "unforgettable", "memorable", "ordinary", "bland", "forgettable",
+               "all", "most", "some", "little", "none")
+topAlts <- data.frame(good_excellent = c("okay", "bad", "terrible"),
+             liked_loved = c("indifferent", "disliked", "hated"),
+             palatable_delicious = c("mediocre", "gross", "disgusting"),
+             memorable_unforgettable = c("ordinary", "bland", "forgettable"),
+             some_all = c("most", "little", "none"))
+scales
+saliences <- data.frame(scale = unlist(sapply(scales, FUN=function(i){rep(i, 5)})),
+                        degree = unlist(sapply(degrees, FUN=function(i){rep(i, 5)})),
+                        salienceCost = rep(NA, 5^2))
+
+saliences <- data.frame(scale = c(rep(scales[1], 5),
+                                  rep(scales[2], 5),
+                                  rep(scales[3], 5),
+                                  rep(scales[4], 5),
+                                  rep(scales[5], 5)),
+                        degree = rep(degrees, 5),
+#                                   rep(degrees[2], 5),
+#                                   rep(degrees[3], 5),
+#                                   rep(degrees[4], 5),
+#                                   rep(degrees[5], 5)),
+                        salienceCost = rep(NA, 5^2),
+                        stringsAsFactors = FALSE)
+
+# subset(altCounts, scale == "good_excellent" & Var1 == "amazing")$percent
+# mapply(saliences$scale, saliences$degree, FUN = function(s, d) {
+#   subset(altCounts, scale == s & degree == d)$percent
+# })
+
+# Saliency
+
+# good_excellent
+saliences[saliences$scale == "good_excellent",]$salienceCost <- c(1, 1, 0.022, 0.189, 0.089)
+saliences[saliences$scale == "liked_loved",]$salienceCost <- c(1, 1, 0.0056, 0.25, 0.28)
+saliences[saliences$scale == "palatable_delicious",]$salienceCost <- c(1, 1, 0.011, 0.089, 0.133)
+saliences[saliences$scale == "memorable_unforgettable",]$salienceCost <- c(1, 1, 0.0389, 0.0722, 0.022)
+saliences[saliences$scale == "some_all",]$salienceCost <- c(1, 0.1278, 1, 0.09444, 0.2167)
+write.csv(saliences, file="saliences.csv")
+
+currScale = "some_all"
+subset(altCounts, scale == currScale & Var1 %in% topAlts[, currScale])
+```

### 2016-01-18 models/RSA_alternativeCostFormulation.Rmd
correct speaker.inf3 working. Also fixed normalization in speaker.lhd

@@
 speaker.inf3 = function(d, alpha, cost = 0) {
-  exp(alpha*(log(d) - cost))
+  exp(-1 * alpha * (-log(d) - cost))
+  # exp(alpha * (log(d) - cost))
 }
@@
   numerator = speaker.inf3(m[[currDegree]][currRating], alpha, currCost)
-#   normalize = sum(unlist(sapply(seq(nrow(m)),
-#                                 function(i) {
-#                                   speaker.inf3(m[i, currDegree],
-#                                                alpha,
-#                                                subset(costs, degree == currDegree)$cost)})))
   # normalize over other words
@@
 
-New run fn()
+Run RSA - five item scales
 ```{r}
 computePosteriors <- c(norm.post, norm.post3)
-runFull2 <- function(data, calcFn = 1, alpha = 1) {
-#############################################################################
-## data       => contains scale | degree | stars | speaker.p | prior.p | cost
-## calcFN     => without cost = 1, with cost = 2
-## alpha      => set alpha level
-
+# runFull() 
+# ---------
+# data       => contains scale | degree | stars | speaker.p | prior.p | cost
+# calcFN     => without cost = 1, with cost = 2
+# alpha      => set alpha level
+runFull <- function(data, calcFn = 1, alpha = 1, numAlts = 5) {
   results <-
@@
   for (s in scales) {
-    force(
+      if (numAlts == 5) {
         mat <- subset(data, scale  == s) %>%
@@
           select(hi1, hi2, mid, low1, low2)
-      )
+      } else if (numAlts == 4) {
+        mat <- subset(data, scale  == s) %>%
+          select(stars, degree, speaker.p) %>%
+          spread(degree, speaker.p) %>%
+          mutate(hi1 = hi1 / sum(hi1),
+                 hi2 = hi2 / sum(hi2),
+                 low1 = low1 / sum(low1),
+                 low2 = low2 / sum(low2)) %>%
+          select(hi1, hi2, low1, low2)
+      } else if (numAlts == 2) {
+        mat <- subset(data, scale  == s) %>%
+          select(stars, degree, speaker.p) %>%
+          spread(degree, speaker.p) %>%
+          mutate(hi1 = hi1 / sum(hi1),
+                 hi2 = hi2 / sum(hi2)) %>%
+          select(hi1, hi2)
+      }
     stars <- subset(data, scale == s)$stars
@@
 
-Data
+Data set-up
 ```{r}
-# priors
-# -------
+# All scales studied
+# ------------------
+scales <- c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+# Priors
+# ------
 unifPriors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
 empPriors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
-salience <- c(0.22, 0.08, 0.05, 1, 1)
-saliencePriors <- data.frame(stars=1:5, prior.p = (salience / sum(salience)))
-salienceCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
-                            cost = -1 * (salience / sum(salience)), stringsAsFactors = FALSE)
-emptyCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
-                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
 yelpPriors <- data.frame(stars=1:5,
@@
                            c(0.090190981, 0.105689431, 0.162783722, 0.304569543, 0.336766323))
+# Cost / rewards
+# --------------
+emptyCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
+                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
+salienceCosts <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences.csv")
+for (s in scales) {
+  salienceCosts[salienceCosts$scale == s, ]$cost <-
+    -1 * normedVec(salienceCosts[salienceCosts$scale == s, ]$cost)
+}
+# salience <- c(0.22, 0.08, 0.05, 1, 1)
+# saliencePriors <- data.frame(stars=1:5, prior.p = (salience / sum(salience)))
+# salienceCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
+#                             cost = -1 * (salience / sum(salience)), stringsAsFactors = FALSE)
 
-# speaker
+# Speaker
+# -------
 speakerL12 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e12.csv")
@@
 speakerL08 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
-# listener
+# Listener
+# --------
 listener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
@@
 priors <- unifPriors
-
 data <- left_join(speakerL12, costs) %>%
@@
   group_by(scale)
+
+# run fns()
+checkSaliences()
+tuneAlphas(modelData = data, humanDf = listener)
 ```
@@
 ```{r}
-test <- runFull2(data, calcFn = 2, alpha = 20)
+# matchModelHumandData()
+# -----------------------
+matchModelHumanData <- function(predDf, listenerDf, study) {
+  combinedDf <- data.frame(scale = c(),
+                           degree = c(),
+                           speaker.p = c(),
+                           prior.p = c(),
+                           cost = c(),
+                           preds = c())
 
-predDf <- test
-getOverallCor <- function(predDf, listenerDf) {
-  combinedDf <- data.frame(scale = c(), degree = c(), speaker.p = c(), prior.p = c(), cost = c(), preds = c())
   for (s in unique(predDf$scale)) {
@@
   }
+
   results <- merge(x = combinedDf,
@@
 
-  cor(results$preds, results$listener.p)
+  results
 }
-getOverallCor(test, listener)
+# mergedData <- matchModelHumanData(test, listener)
 
-tuneAlphas <- function(alphas = seq(1, 12), humanDf) {
+# Alpha Tuning - maximixize correlation
+# -------------------------------------
+tuneAlphas <- function(modelData, humanDf, alphas = seq(1, 12), numAlts = 5){
   sapply(alphas, function(i) {
-    predDf <- runFull2(data, calcFn = 2, alpha = i)
-    getOverallCor(predDf, humanDf)
+    predDf <- runFull(modelData, calcFn = 2, alpha = i, numAlts = numAlts)
+    mergedData <- matchModelHumanData(predDf, listener)
+    cor(mergedData$preds, mergedData$listener.p)
   })
 }
-tuneAlphas(humanDf = listener)
+tuneAlphas(modelData = data, humanDf = listener)
+
+checkSaliences <- function() {
+  predDf <- runFull(data, calcFn = 2, alpha = 1, numAlts = 5)
+  mergedData <- matchModelHumanData(predDf, listener)
+  cor(mergedData$preds, mergedData$listener.p)
+}
+checkSaliences()
+```
+
+Visualize
+```{r}
+mergedData <- matchModelHumanData(runFull(data, calcFn = 2, alpha = 7, numAlts = 5), listener)
+plotData <- mergedData
+qplot(stars, listener.p, col=degree,
+      data=plotData,
+      main=paste("title")) +
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = preds), lty = 4)
+
+correlationScatterPlot <-
+  ggplot(mergedData, aes(x = listener.p, y = preds, col=stars)) +
+  geom_point() + 
+  stat_smooth(method="lm")
+
 ```
@@
 ```{r}
-
 normedVec(subset(test, scale == "good_excellent" & degree == "hi1")$preds)

### 2016-01-19 Paper/Paper.Rmd
initial code for plotting / RSA

@@
     Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
-In the canonical "some, but not all" scalar implicature, listeners enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "She ate some of the cookies." A Gricean account of this phenomena assumes the presence of "salient alternatives" with varying degrees of informatitivy.
+In the frequently cited "some, but not all" scalar implicature, listeners enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "She ate some of the cookies." A Gricean account of this phenomena assumes the presence of "salient alternatives" with varying degrees of informatitivy.
 "Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." While intuitive, empirical evidence for the presence of such alternatives is limited.
 Our current work explores the role different scale representations may play in scalar implicature.
-Using a Bayesian model of implicature generation we simulate various scale representations that might be available to a listener, comparing model predictions to human judgment.
-Results indicate that implicature generation likely requires "full" scale representations, including negative valenced alternatives, rather than the typical entailment only scales assumed in most research to date.
+Using a Bayesian model of implicature generation we simulate various scale representations that might be available to a listener, comparing model predictions to human judgments.
+Results indicate that humans may rely on "fuller" scale representations, including negative and neutral valenced alternatives, rather than the typical entailment only scales assumed in most research to date.
 
@@
 library(ggplot2)
+library(knitr)
+library(rjson)
+library(dplyr)
+library(tidyr)
+library(gridExtra)
+library(jsonlite)
+```
+
+```{r helpers}
+normedVec <- function(vec) vec / sum(vec)
+```
+
+```{r RSA}
+
+```
+
+```{r, exp_data}
+scales <- c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+
+# Alternatives (Study e9)
+alternativesData <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/e9_alternativeCounts.csv", stringsAsFactors = FALSE)
+
+# Priors
+# ------
+unifPriors = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
+empPriors = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/emp_priors.csv")
+yelpPriors <- data.frame(stars=1:5,
+                         prior.p =
+                           c(0.090190981, 0.105689431, 0.162783722, 0.304569543, 0.336766323))
+# Cost / rewards
+# --------------
+emptyCosts5 <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
+                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
+emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
+                            cost = rep(0.0, 4), stringsAsFactors = FALSE)
+emptyCosts2 <- data.frame(degree = c("low", "hi"),
+                            cost = rep(0.0, 2), stringsAsFactors = FALSE)
+salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences5.csv")
+salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences4.csv")
+salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences2.csv")
+for (s in scales) {
+  salienceCosts5[salienceCosts5$scale == s, ]$cost <-
+    -1 * normedVec(salienceCosts5[salienceCosts5$scale == s, ]$cost)
+}
+
+# Speaker
+# -------
+speakerE8 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
+speakerE12 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e12.csv")
+speakerE10 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
+
+# Listener
+# --------
+listenerE6 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+listenerE11 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
+
+costs <- salienceCosts2
+priors <- unifPriors
+data <- left_join(speakerE8, costs) %>%
+  left_join(., priors) %>%
+  rowwise %>%
+  select(scale, degree, stars, speaker.p, prior.p, cost) %>%
+  group_by(scale)
 ```
@@
 \textbf{The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice)}.
-Previous research indicates implicature generation is affected by the set of alternatives available, both in adults (Degen, Franke) and is possibly the source of difficulty in computing implicatures for children (Barner).
+Recent studies indicate implicature generation is affected by the set of alternatives available to listeners, both in adults (Degen, Franke) and is possibly the source of difficulty in computing implicatures for children (Barner).
 Degen found ...
@@
 \textbf{Measuring the degree to which alternatives may be present during implicature generation is a difficult task}.
-Issues of introspection aside, simply querying a participant about the apparent saliency of particular alternatives is problematic because the alternatives are made salient in the query itself.
+Issues of introspection aside, simply querying a participant about the saliency of particular alternatives is problematic because the alternatives must be made salient during the actual query.
 To circumvent this issue, we adopted a computational model of implicature generation.
-Adopting a computational framework allowed us to simulate the effects of various scalar alternatives sets on implicature generation, comparing model predictions to human judgments.
+Adopting a computational framework allowed us to simulate the effects of various scalar alternative sets on implicature generation, comparing model predictions to human judgments.
 
@@
 [Using the scalar diversity approach to get beyond the some/all implicature]\newline
-\textbf{Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably focusing on "some/all".} This lack "Scalar Diversity" (van Tiel, 2013) not only presents a problem in terms of generalization of findings, but within our current computational framework, presents a problem of data sparsity.
+\textbf{Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably "some/all".} This lack "Scalar Diversity" (van Tiel, 2013) makes generalization across different scalar types problematic.
 We adopt a "Scalar Diversity" approach in our experimental design in order to incorporate multiple scalar items from a range of grammatical classes.
@@
 \textbf{In the following paper we present three experiments and three model simulations based on the experimental data.} We used a food review paradigm in which linguistic `meaning' for a given scalar item was quantified as a distribution over star-ratings.
-Quantifying both literal semantic content and pragmatic judgments in this way provided an important interface to RSA, especially for scalar items with ambigous literal semantics (items such as "memorable/unforgettable" or "palatable/delicious).
+Quantifying both literal semantic content and pragmatic judgments as distributions over stars, provided an important interface to RSA, especially for scalar items with ambigous literal semantics (items such as "memorable/unforgettable" or "palatable/delicious).
 In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
-Alternatives generated in Experiment 2 supplmented the original stimuli from Experiments 1a,b in Experiments 3a,b.
+This data served two purposes.
+First, since participants were asked to freely generate alternatives this data gives a measure of scalar "saliency" simply the as a proportion of items generated for a given scalar pair.
+Second, alternatives generated in Experiment 2 supplemented the original stimuli from Experiments 1a,b in Experiments 3a,b.
 Using the literal semantic data from Experiments 1a and 3a we modeled pragmatic enrichment using RSA and compared model predictions to human judgment data from Experiments 1b and 3b.
@@
 
+```{r}
+# Literal listener: Entailment (e8)
+ggplot(data = speakerE8, aes(x = stars, y = speaker.p, col=degree)) +
+  geom_line() +
+  facet_wrap(~scale) +
+  ylab("Percent yes") +
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih))
+  ggtitle("Literal listener compatibility judgments")
+```
+
+```{r}
+# Pragmatic listener: Entailment (e6)
+ggplot(data = listenerE6, aes(x = stars, y = listener.p, fill = scale)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~scale + degree) +
+  ylab("Percent making this star judgment") +
+  ggtitle("Pragamtic listener judgments")
+```
+
 # Experiment 2: What are the alternatives?
@@
 
+```{r}
+# Alternatives just good excellent
+plotData <- subset(alternativesData, scale == "good_excellent")
+removeRows <- which(plotData$alt == "good" | plotData$alt == "excellent")
+plotData <- plotData[-removeRows, ]
+ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
+  geom_bar(stat="identity") + ylim(0, 35) + labs(x = "alternative", y = "counts") +
+  ggtitle(paste("Salient alternatives for ", "Good, Excellent")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+```
+
 # Experiment 3a,b: Full scales - incorporating negative alternatives
 
-Experiment 3a,b was conducted to approximate literal listener semantic distributions (study a) and assess pragamtic judgments (study b) for both positive and negative valenced scalar items (see appendix b for the complete list of items used).
+Experiment 3a,b were conducted to approximate literal listener semantic distributions (study a) and assess pragamtic judgments (study b) for both positive and negative valenced scalar items (see appendix b for the complete list of items used).
 
@@
 
+```{r}
+# Literal listener: Negative alts (e10)
+ggplot(data = speakerE10, aes(x = stars, y = speaker.p, col=degree)) +
+  geom_line() +
+  facet_wrap(~scale) +
+  ylab("Percent yes") +
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih))
+  ggtitle("Literal listener compatibility judgments")
+```
+
+```{r}
+# Pragmatic listener: Negative alts (e11)
+ggplot(data = listenerE11, aes(x = stars, y = listener.p, fill = scale)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~scale + degree) +
+  ylab("Percent making this star judgment") +
+  ggtitle("Pragamtic listener judgments")
+```
+
 # Model
+Using literal semantics data from experiments 1a and 3a we can simulate the role alternatievs play in scalar implicature.
+In particular, we can vary the number of scalar items present during implicature generation.
+In the following analyses we focus on three sceneriors 1) Entailment only sclaes (good, excellent), 2) Negative Alternatives (horrible, bad, good, excellent) 3) Symmetric scale (horrible, bad, okay, good, excellent).
+
+## Entailment only
+
+## Negative alternatives
+
+## Symmetric scale
 

### 2016-01-19 Paper/Paper.Rmd
commented out literal listener e10 plot - need to fix. First model description write-up

@@
 ```{r}
-# Literal listener: Negative alts (e10)
-ggplot(data = speakerE10, aes(x = stars, y = speaker.p, col=degree)) +
-  geom_line() +
-  facet_wrap(~scale) +
-  ylab("Percent yes") +
-  geom_linerange(aes(ymin = speaker.p - cil, 
-                     ymax = speaker.p + cih))
-  ggtitle("Literal listener compatibility judgments")
+# Literal listener: Negative alts (e11)
+
+# FOR SOME REASON THIS ISN'T PLOTTING
+
+# ggplot(data = speakerE10, aes(x = stars, y = speaker.p, col = degree)) +
+#   geom_line() +
+#   facet_wrap(~scale) +
+#   ylab("Percent yes") +
+#   geom_linerange(aes(ymin = speaker.p - cil, 
+#                      ymax = speaker.p + cih))
+#   ggtitle("Literal listener compatibility judgments")
 ```
@@
 # Model
+Our model adopts a Bayesian framework to formalize the Gricean account of scalar implicature. 
+In particular, RSA adopts a "language understanding as social cognition" perspective which is captured in listener and speaker agents reasoning about one another.
+We focus on the problem of a listener inferring the meaning of a speaker's utterance.
+Let $u$ be an observed utterance by our speaker with an intended meaning $m$.
+We assume that the listener has access to a space of possible meanings $M$ and some model relating meanings $m \in M$ to $u$.
+
+Upon hearing an utterance $u$ the Listener agent evaluates all candidate word meanings, computing their posterior probabilities $p(m | u)$.
+This quantity is proportional to the product of the prior probability $p(m)$ of a particular meaning and the likelihood $p(u | m)$.
+
+$$p(m | u) = \frac{p(u | m)p(m)}{p(u)}$$
+$$= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}$$
+
+The prior $p(m)$ represents the listener's expectations about plausible meanings (star ratings), *independent* of the utterance $u$.
+To avoid biasing the data we assume priors over meanings are uniform, however future investigations may want to experiment with different priors, either through inferring them or empircal means.
+
+The likelihood $p(u | m)$ assumes that speakers choose words to maximize informatitivy in context.
+We quantified the informativeness of a word by its surprisal minus a cost.
+Cost, in this case is operationalized as a salience measure - more salient items should have a larger impact on implicature generation, than less salient alternatives.
+$$p(u | m) = \frac{e^{-\alpha(-log(p(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p(m|u)) - cost(u))}}$$
+
+The posterior $p(m | u)$ reflects the listener's degree of beleif that $m$ is the intended meaning of the speaker, given her utterance $u$.
+
 Using literal semantics data from experiments 1a and 3a we can simulate the role alternatievs play in scalar implicature.
@@
 ## Model fitting and comparison
+Figure XX shows plots model / human correlation for our three simulations. Alpha was tuned separately for each of these runs...
 
 # General Discussion
+By varying the type of scale representations available to our Bayesian model we tested the effects of scalar alternatives in scalar implicature.
+Model fit with human judgements was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
+In fact, we found that both neutral and negative valenced scalar items contribute to human-like implicature generation within our framework.
 
@@
 
-Thanks to NSF BCS #XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.
+Thanks to NSF BCS XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.
 

### 2016-01-19 models/RSA_alternativeCostFormulation.Rmd
fns() for model runs - entailment / neg alts / full

@@
   # normalize over other words
-  normalize <- sum(sapply(seq(allDegrees), FUN = 
+  normalize <- sum(unlist(sapply(seq(allDegrees), FUN = 
                             function(i) {
@@
                                           subset(costs, degree == allDegrees[i])$cost)}
-                          ))
+                          )))
   return(numerator / normalize)
@@
 # alpha      => set alpha level
-runFull <- function(data, calcFn = 1, alpha = 1, numAlts = 5) {
+runFull <- function(data, calcFn = 2, alpha = 1, numAlts = 5) {
   results <-
@@
           spread(degree, speaker.p) %>%
-#           mutate(hi1 = hi1 / sum(hi1),
-#                  hi2 = hi2 / sum(hi2),
-#                  mid = mid / sum(mid),
-#                  low1 = low1 / sum(low1),
-#                  low2 = low2 / sum(low2)) %>%
+          mutate(hi1 = hi1 / sum(hi1),
+                 hi2 = hi2 / sum(hi2),
+                 mid = mid / sum(mid),
+                 low1 = low1 / sum(low1),
+                 low2 = low2 / sum(low2)) %>%
           select(hi1, hi2, mid, low1, low2)
@@
           spread(degree, speaker.p) %>%
-          mutate(hi1 = hi1 / sum(hi1),
-                 hi2 = hi2 / sum(hi2)) %>%
-          select(hi1, hi2)
+          mutate(hi = hi / sum(hi),
+                 low = low / sum(low)) %>%
+          select(hi, low)
       }
@@
 # --------------
-emptyCosts <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
+emptyCosts5 <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
                             cost = rep(0.0, 5), stringsAsFactors = FALSE)
-salienceCosts <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences.csv")
+emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
+                            cost = rep(0.0, 4), stringsAsFactors = FALSE)
+emptyCosts2 <- data.frame(degree = c("low", "hi"),
+                            cost = rep(0.0, 2), stringsAsFactors = FALSE)
+salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences5.csv")
+salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences4.csv")
+salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences2.csv")
+normNegSalienceCosts <- function(saliences) {
   for (s in scales) {
-  salienceCosts[salienceCosts$scale == s, ]$cost <-
-    -1 * normedVec(salienceCosts[salienceCosts$scale == s, ]$cost)
+    saliences[saliences$scale == s, ]$cost <-
+      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
+  }
+  saliences
 }
@@
 
-costs <- salienceCosts
+costs <- salienceCosts2
 priors <- unifPriors
-data <- left_join(speakerL12, costs) %>%
+data <- left_join(speakerL08, costs) %>%
   left_join(., priors) %>%
@@
 checkSaliences()
-tuneAlphas(modelData = data, humanDf = listener)
+tuneAlphas(modelData = data, humanDf = listener, numAlts = 2)
 ```
 
-Explore
+Data exploration Fns()
 ```{r}
@@
 # -----------------------
-matchModelHumanData <- function(predDf, listenerDf, study) {
+# NEED TO FINISH WORKING HERE!!!!!!!!!!!!!!!!!!
+matchModelHumanData <- function(predDf, listenerDf, study = "e12") {
   combinedDf <- data.frame(scale = c(),
@@
   for (s in unique(predDf$scale)) {
+    if (study == "e12") {
       if (s == "some_all") {
@@
         }
+    } else if (study == "e10") {
+        if (s == "some_all") {
+          tempDf <- subset(predDf, scale == s & (degree == "hi1" | degree == "low1")) %>%
+            mutate(degree = ifelse(degree == "hi1", "hi", "low"))
+        } else {
+          tempDf <- subset(predDf, scale == s & (degree == "hi1" | degree == "hi2")) %>%
+            mutate(degree = ifelse(degree == "hi1", "hi", "low"))
+        }
+    } else { ## study e6
+      tempDf <- subset(predDf, scale == s)
+    }
+
     combinedDf <- rbind(combinedDf, tempDf)
@@
 }
-# mergedData <- matchModelHumanData(test, listener)
+# mergedData <- matchModelHumanData(data, listener, study = "e6")
 
@@
 # -------------------------------------
-tuneAlphas <- function(modelData, humanDf, alphas = seq(1, 12), numAlts = 5){
+tuneAlphas <- function(modelData, humanDf, alphas = seq(1, 12), numAlts = 5, study = "e12"){
   sapply(alphas, function(i) {
     predDf <- runFull(modelData, calcFn = 2, alpha = i, numAlts = numAlts)
-    mergedData <- matchModelHumanData(predDf, listener)
+    mergedData <- matchModelHumanData(predDf, listener, study = study)
     cor(mergedData$preds, mergedData$listener.p)
@@
 }
-tuneAlphas(modelData = data, humanDf = listener)
+# tuneAlphas(modelData = data, humanDf = listener, numAlts = 4)
 
-checkSaliences <- function() {
-  predDf <- runFull(data, calcFn = 2, alpha = 1, numAlts = 5)
-  mergedData <- matchModelHumanData(predDf, listener)
+checkSaliences <- function(d, study = "e12", alpha = 1, numAlts = 5) {
+  predDf <- runFull(d, calcFn = 2, alpha = alpha, numAlts = numAlts)
+  mergedData <- matchModelHumanData(predDf, listener, study = study)
   cor(mergedData$preds, mergedData$listener.p)
 }
-checkSaliences()
+# checkSaliences(data, study = "e6", alpha = 1, numAlts = 2)
 ```
@@
 plotData <- mergedData
+
+# predPlot()
+# ---------
+# plot preds over stars with human data
+predPlot <- function(d) {
   qplot(stars, listener.p, col=degree,
-      data=plotData,
+      data=d,
       main=paste("title")) +
@@
   geom_line(aes(y = preds), lty = 4)
-
-correlationScatterPlot <-
-  ggplot(mergedData, aes(x = listener.p, y = preds, col=stars)) +
+}
+# correlationScatterPlot()
+# -----------------------
+# plot correleation with low / hi
+correlationScatterPlot <- function(d) {
+  ggplot(d, aes(x = listener.p, y = preds, col=stars)) +
   geom_point() + 
   stat_smooth(method="lm")
+}
+```
 
+Entailment analysis
+```{r}
+
+```
+
+Negative alts analysis
+```{r}
+
+```
+
+Symmetric scale analysis
+```{r}
+# Set-up data
+
+completeModelRun <- function(speaker, listener, priors, costs, numAlts) {
+  results <- list() ## Will return this
+
+  newCosts <- normNegSalienceCosts(costs)
+  data <- left_join(speaker, newCosts) %>%
+    left_join(., priors) %>%
+    rowwise %>%
+    select(scale, degree, stars, speaker.p, prior.p, cost) %>%
+    group_by(scale)
+
+  studyNum <- ifelse(numAlts == 5, "e12", ifelse(numAlts == 4, "e10", "e6"))
+  # Tune alpha
+  bestAlpha <- which.max(tuneAlphas(data, listener, numAlts = numAlts, study = studyNum))
+  # Run model
+  modelData <- runFull(data, calcFn = 2, alpha = bestAlpha, numAlts = numAlts)
+  # Final data set for plotting / model fit
+
+  combinedDf <- matchModelHumanData(modelData, listener, study = studyNum)
+  fit <- cor(combinedDf$preds, combinedDf$listener.p)
+
+  # plots
+#   predPlot(combinedDf)
+#   correlationScatterPlot(combinedDf)
+
+  results[[1]] <- combinedDf
+  results[[2]] <- modelData
+  results[[3]] <- bestAlpha
+  results[[4]] <- fit
+  results[[5]] <- predPlot(combinedDf)
+  results[[6]] <- correlationScatterPlot(combinedDf)
+  results
+}
+```
+
+Entailment / Neg alts / Symmetric scale
+```{r}
+symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, salienceCosts5, numAlts = 5)
+symmetricScalerun[[4]]
+negAltsRun <-        completeModelRun(speakerL10, listener, unifPriors, salienceCosts4, numAlts = 4)
+negAltsRun[[4]]
+entailmentRun <-      completeModelRun(speakerL08, listener, unifPriors, salienceCosts2, numAlts = 2)
+entailmentRun[[4]]
+```
+
+Aggregate analysis
+```{r}
+cors <- data.frame(cors = c(symmetricScalerun[[4]], negAltsRun[[4]], entailmentRun[[4]]),
+                   m = c("full", "neg_alts", "entailment"))
+ggplot(cors, aes(x=reorder(m, cors), y = cors)) +
+  geom_bar(stat="identity", position="dodge") +
+  ylab("Correlation") +
+  xlab("Model") +
+  ylim(0, 1) + 
+  ggtitle("Model fit correlation coefficients") +
+  guides(colour=FALSE) +
+  geom_text(aes(x=m, y=as.numeric(cors) + 0.025, label=round(cors, 3)))
 ```

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
added model run data with write to csv

@@
 
-Run RSA - five item scales
+Run RSA
 ```{r}
@@
 listener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
+listener2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
 
@@
 # run fns()
-checkSaliences()
-tuneAlphas(modelData = data, humanDf = listener, numAlts = 2)
+# ---------
+# checkSaliences()
+# tuneAlphas(modelData = data, humanDf = listener, numAlts = 2)
 ```
@@
 # -----------------------
-# NEED TO FINISH WORKING HERE!!!!!!!!!!!!!!!!!!
 matchModelHumanData <- function(predDf, listenerDf, study = "e12") {
@@
 
-Entailment analysis
-```{r}
-
-```
-
-Negative alts analysis
-```{r}
-
-```
-
 Symmetric scale analysis
@@
 
-  # plots
-#   predPlot(combinedDf)
-#   correlationScatterPlot(combinedDf)
-
   results[[1]] <- combinedDf
@@
 entailmentRun[[4]]
+
+######WORKING HERE!!!!!!
+
+listener2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
+symmetricData <- symmetricScalerun[[1]]
+symmetricData$numAlts = 5
+negAltsData <- negAltsRun[[1]]
+negAltsData$numAlts = 4
+entailmentData <- entailmentRun[[1]]
+entailmentData$numAlts = 2
+
+# Aggregate data to write to .csv
+
+# combine with e11 prag listener nums
+aggregateData <- rbind(symmetricData, negAltsData, entailmentData)
+listener2 <- listener2[(listener2$scale == "some_all" & (listener2$degree == "low1" | listener2$degree == "hi1")) |
+                         (listener2$scale != "some_all" & (listener2$degree == "hi1" | listener2$degree == "hi2")), ]
+listener2$degree <- as.character(ifelse(listener2$degree == "hi1", "hi", "low"))
+names(listener2) <- c("degree", "scale", "stars", "listener.p2", "total")
+aggregateData <- left_join(aggregateData, listener2[, -5], by=c("degree", "stars", "scale")) %>%
+  mutate(listener.p2 = ifelse(is.na(listener.p2), 0, listener.p2))
+
+# record correlations for both studies
+modelRunData <- aggregateData
+symmetricE6cor <- cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p)
+symmetricE11cor <-cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p2)
+negAltsE6cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p)
+negAltsE11cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p2)
+entailmentE6cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p)
+entailmentE11cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p2)
+modelRunData$corE6 <- ifelse(modelRunData$numAlts == 5, symmetricE6cor,
+                             ifelse(modelRunData$numAlts == 4, negAltsE6cor, entailmentE6cor))
+modelRunData$corE11 <- ifelse(modelRunData$numAlts == 5, symmetricE11cor,
+                             ifelse(modelRunData$numAlts == 4, negAltsE11cor, entailmentE11cor))
+modelRunData$alphas <- ifelse(modelRunData$numAlts == 5, symmetricScalerun[[3]],
+                             ifelse(modelRunData$numAlts == 4, negAltsRun[[3]], entailmentRun[[3]]))
+
+# write.csv(modelRunData, "model_data/allModelRuns.csv")
 ```
-
-Aggregate analysis
-```{r}
-cors <- data.frame(cors = c(symmetricScalerun[[4]], negAltsRun[[4]], entailmentRun[[4]]),
-                   m = c("full", "neg_alts", "entailment"))
-ggplot(cors, aes(x=reorder(m, cors), y = cors)) +
-  geom_bar(stat="identity", position="dodge") +
-  ylab("Correlation") +
-  xlab("Model") +
-  ylim(0, 1) + 
-  ggtitle("Model fit correlation coefficients") +
-  guides(colour=FALSE) +
-  geom_text(aes(x=m, y=as.numeric(cors) + 0.025, label=round(cors, 3)))
-```
-
-```{r}
-normedVec(subset(test, scale == "good_excellent" & degree == "hi1")$preds)
-#normedVec(subset(test, scale == "good_excellent" & degree == "mid")$preds)
-sum(subset(test, scale == "good_excellent" & degree == "hi1")$preds)
-dfPreds <- test
-dfHuman <- listener
-name <- "good_excellent"
-getCorrs <- function(dfPreds, dfHuman, name) {
-  predSubset <- subset(dfPreds, scale == name & (degree == "hi1" | degree == "hi2"))
-  predSubset$degree = with(predSubset,
-                           ifelse(degree == "hi1", "hi", "low"))
-  humanSubset <- subset(dfHuman, scale == name)
-  joinedDf <- merge(x = predSubset,
-                    y = humanSubset,
-                    by = c("degree", "stars", "scale"),
-                    all.x = TRUE) %>%
-    mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))
-  cor(joinedDf$preds, joinedDf$listener.p)
-}
-
-getCorrs(test, listener, "good_excellent")
-getCorrs(test, listener, "liked_loved")
-getCorrs(test, listener, "memorable_unforgettable")
-getCorrs(test, listener, "palatable_delicious")
-
-######################################################################
-----------------------------------------------------------------------
-######################################################################
-
-runModel <- function(model, mat, degree, alpha) {
-  if (model == 1) unlist(mapply(seq(1,5),
-                                FUN=function(x) norm.post(x, degree, mat, alpha, priors)))
-}
-mat <- data %>% 
-  select(stars, degree, speaker.p) %>%
-  spread(degree, speaker.p) %>%
-  mutate(hi1 = hi1 / sum(hi1),
-         hi2 = hi2 / sum(hi2),
-         mid = mid / sum(mid),
-         low1 = low1 / sum(low1),
-         low2 = low2 / sum(low2)) %>%
-  select(hi1, hi2, mid, low1, low2)
-
-runModel(1, mat[1:5, ], 1, 6)
-runModel(1, mat[1:5, ], 2, 6)
-
-subset(listener, scale == "good_excellent")
-
-```
-
-New cost formulation
-```{r}
-speaker.inf2 = function(d, alpha, cost = 0) {
-  exp(alpha*(log(d) - cost))
-}
-# speaker likelihood
-# ------------------
-speaker.lhd2 = function(rating, degree, m, alpha, costs) {
-  numerator = speaker.inf2(m[rating, degree], alpha, costs[degree])
-  normalize = sum(unlist(sapply(seq(nrow(m)),
-                                function(i) {speaker.inf2(m[i, ], alpha, costs[degree])})))
-  return(numerator / normalize)
-  # return(numerator)
-}
-# non-normalized posterior
-# -----------------------
-nn.post2 = function(rating, degree, m, alpha, costs, useprior) {
-  prior = priors[rating, "prior.p"]
-  # prior <- 0.2
-  return(speaker.lhd2(rating, degree, m, alpha, costs) * prior)
-}
-# normalized posterior
-# --------------------
-norm.post2 = function(rating, degree, m, alpha, costs, useprior) {
-  nn = nn.post2(rating, degree, m, alpha, costs, useprior)
-  normalize = sum(unlist(sapply(seq(1, 5),
-                                function(i){nn.post2(rating, i, m, alpha, costs, useprior)})))
-  return(nn / normalize)
-}
-```
-
-```{r}
-# good excellent
-mat[1:5,]
-salience <- c(1, 1, 0.05, 0.08, 0.22)
-normed.salience <- -1 * (salience / sum(salience))
-
-normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 1, mat[1:5,], 5, normed.salience))))
-normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 2, mat[1:5,], 5, normed.salience))))
-
-#################################
-# good_excellent
-# --------------
-# low
-good.exc.low <-
-  listener[with(listener, which(scale == "good_excellent" & degree == "low")),]$listener.p %>%
-  c(. , rep(0, 2))
-# high
-good.exc.high <-
-  listener[with(listener, which(scale == "good_excellent" & degree == "hi")),]$listener.p %>%
-  c(. , rep(0, 3))
-# new formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 2, mat[1:5,], 7, normed.salience)))),
-    good.exc.low[c(5, 4, 1, 2, 3)])
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 1, mat[1:5,], 7, normed.salience)))),
-    good.exc.high[c(5, 4, 3, 1, 2)])
-# old formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 2, mat[1:5,], 7)))),
-    good.exc.low[c(5, 4, 1, 2, 3)])
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 1, mat[1:5,], 7)))),
-    good.exc.high[c(5, 4, 3, 1, 2)])
-
-#################################
-# liked_loved
-# low
-liked.loved.low <-
-  listener[with(listener, which(scale == "liked_loved" & degree == "low")),]$listener.p %>%
-  c(. , rep(0, 2))
-# high
-liked.loved.high <-
-  listener[with(listener, which(scale == "liked_loved" & degree == "hi")),]$listener.p %>%
-  c(. , rep(0, 3))
-# new formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 2, mat[6:10,], 7, normed.salience)))),
-    liked.loved.low[c(5, 1, 2, 3, 4)])
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 1, mat[6:10,], 7, normed.salience)))),
-    liked.loved.high[c(5, 4, 3, 1, 2)])
-# old formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 2, mat[6:10,], 7)))),
-    liked.loved.low[c(5, 1, 2, 3, 4)])
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 1, mat[6:10,], 7)))),
-    liked.loved.high[c(5, 4, 3, 1, 2)])
-
-#################################
-# memorable_unforgettable
-# low
-mem.unf.low <-
-  listener[with(listener, which(scale == "memorable_unforgettable" & degree == "low")),]$listener.p %>%
-  c(. , rep(0, 3))
-mem.unf.low <- mem.unf.low[c(5, 4, 3, 2, 1)]
-# high
-mem.unf.high <-
-  listener[with(listener,
-                which(scale == "memorable_unforgettable" & degree == "hi")),]$listener.p %>%
-  c(. , rep(0, 1))
-mem.unf.high <- mem.unf.high[c(1, 5, 2, 3, 4)]
-# new formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 2, mat[11:15,], 7, normed.salience)))),
-    mem.unf.low)
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post2(x, 1, mat[6:10,], 7, normed.salience)))),
-    mem.unf.high)
-# old formulations
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 2, mat[6:10,], 3)))),
-    mem.unf.low)
-cor(normalize(unlist(mapply(seq(1,5),
-                        FUN=function(x) norm.post(x, 1, mat[6:10,], 7)))),
-    mem.unf.high)
-```
-
-How to implement this using saliency rewards (negative costs)???
-```{r}
-run.newCosts = function(d, alpha=1, useprior=F, usenone=F, normalize=F) {
-  mat <- data.full.extras %>% 
-    select(stars, degree, speaker.p) %>%
-    spread(degree, speaker.p) %>%
-    select(hi1, hi2, mid, low1, low2)
-
-  if (usenone) {
-    mat$none = c(1, 0, 0, 0, 0)
-  } 
-  d$degree <- with(d, ifelse(degree == "hi1", 5,
-                             ifelse(degree == "hi2", 4,
-                                    ifelse(degree == "mid", 3, 
-                                           ifelse(degree == "low1", 2, 3)))))
-  d$pred = round(as.numeric(mapply(norm.post2, d$stars, d$degree, 
-                                    MoreArgs = list(m = mat, 
-                                                    alpha = alpha,
-                                                    costs = normed.salience,
-                                                    useprior = useprior))), 
-                  digits=4)
-
-  return(normalize(d))
-}
-run.newCosts(data.full.extras, alpha=7, useprior=TRUE, usenone=FALSE, normalize=normalize)
-```
-
-Old `run` function
-```{r}
-run.full = function(d, alpha=1, useprior=F, usenone=F, addMid=F, normalize=F) {
-  # alpha = scales.entropy[scales.entropy$scale==d$scale[1], ]$Entropy
-  if (addMid) {
-    if (normalize) {
-      mat = d %>%
-        select(stars, degree, speaker.p) %>%
-        spread(degree, speaker.p) %>%
-        mutate(hi1 = hi1 / sum(hi1),
-               hi2 = hi2 / sum(hi2),
-               mid = mid / sum(mid),
-               low1 = low1 / sum(low1),
-               low2 = low2 / sum(low2)) %>%
-        select(hi1, hi2, mid, low1, low2)    
-    } else {
-      mat = d %>%
-        select(stars, degree, speaker.p) %>%
-        spread(degree, speaker.p) %>%
-        select(hi1, hi2, mid, low1, low2)    
-    }
-  } else {
-    if (normalize) {
-      mat = d %>%
-        select(stars, degree, speaker.p) %>%
-        spread(degree, speaker.p) %>%
-        mutate(hi1 = hi1 / sum(hi1),
-               hi2 = hi2 / sum(hi2),
-               low1 = low1 / sum(low1),
-               low2 = low2 / sum(low2)) %>%
-        select(hi1, hi2, low1, low2)
-    } else {
-      mat = d %>%
-        select(stars, degree, speaker.p) %>%
-        spread(degree, speaker.p) %>%
-        select(hi1, hi2, low1, low2)
-    }
-  }
-
-  if (usenone) {
-    mat$none = c(1, 0, 0, 0, 0)
-  }
-
-  d$pred = round(as.numeric(mapply(norm.post, d$stars, d$degree, 
-                                    MoreArgs = list(m = mat, 
-                                                    alpha = alpha, 
-                                                    useprior = useprior))), 
-                  digits=4)
-
-  return(d)
-}
-```
-
-```{r}
-run.full(data.full.extras, useprior = TRUE, usenone = FALSE, addMid = TRUE, normalize = TRUE)
-cor(data.full.extras$listener.p, data.full.extras$pred)
-```

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
re-outputted full model runs data with modified saliency costs.

@@
 
-costs <- salienceCosts2
+costs <- salienceCosts5
 priors <- unifPriors
-data <- left_join(speakerL08, costs) %>%
+data <- left_join(speakerL12, costs) %>%
   left_join(., priors) %>%
@@
 
-# write.csv(modelRunData, "model_data/allModelRuns.csv")
+# write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
 ```

### 2016-01-20 models/midScalarInvestigation.Rmd
two approaches to saliences with output to csv.

@@
   summarise(n = n())
-
+# write.csv(d, "e9_alternativeCounts.csv")
 # Plot findings of salient alternatives for each scale
@@
 ```{r}
-d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame=T) %>% as.data.frame(., stingasFactors = FALSE)
+d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame = TRUE) %>%
+  as.data.frame(., stingasFactors = FALSE)
 
@@
                         degree = rep(degrees, 5),
-#                                   rep(degrees[2], 5),
-#                                   rep(degrees[3], 5),
-#                                   rep(degrees[4], 5),
-#                                   rep(degrees[5], 5)),
                         salienceCost = rep(NA, 5^2),
@@
 
-# subset(altCounts, scale == "good_excellent" & Var1 == "amazing")$percent
-# mapply(saliences$scale, saliences$degree, FUN = function(s, d) {
-#   subset(altCounts, scale == s & degree == d)$percent
-# })
-
-# Saliency
-
-# good_excellent
+# Manual coding salience costs
 saliences[saliences$scale == "good_excellent",]$salienceCost <- c(1, 1, 0.022, 0.189, 0.089)
@@
 saliences[saliences$scale == "some_all",]$salienceCost <- c(1, 0.1278, 1, 0.09444, 0.2167)
-write.csv(saliences, file="saliences.csv")
+# write.csv(saliences, file="saliences.csv")
+```
 
-currScale = "some_all"
-subset(altCounts, scale == currScale & Var1 %in% topAlts[, currScale])
+Saliences as counts for primary scalars and participant responses
+```{r}
+d <- fromJSON("../analysis/edited_alts.json", simplifyDataFrame = TRUE) %>%
+  as.data.frame(., stingasFactors = FALSE)
+scales <- c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+degrees <- c("hi1", "hi2", "mid", "low1", "low2")
+
+# Populate counts
+altCounts <- data.frame(Var1 = c(), Freq = c(), NewFreq = c(), percent = c())
+for (s in scales) {
+  scaleHeads <- strsplit(s, "_")[[1]]
+  s1 <- scaleHeads[1]
+  s2 <- scaleHeads[2]
+  combinedDf <- rbind(as.data.frame(table(d[, s1])), as.data.frame(table(d[, s2]))) %>%
+    aggregate(Freq ~ Var1 ,data = ., FUN = sum) %>%
+    mutate(scale = s,
+           NewFreq = ifelse((Var1 == s1 | Var1 == s2), Freq + 90, Freq))
+
+  altCounts <- rbind(altCounts, combinedDf)
+}
+#Adding 'palatable' to altCounts!!!
+altCounts <- rbind(altCounts, data.frame(Var1 = "palatable", Freq = 0, scale = "palatable_delicious", NewFreq = 90))
+
+# Populate saliences data for output
+saliences <- data.frame(scale = c(), degree = c(), count = c(), newCount = c())
+# good_excellent
+saliences <- rbind(saliences,
+      data.frame(scale = rep("good_excellent", 5), degree = degrees,
+                 count = c(subset(altCounts, scale == "good_excellent" & Var1 == "excellent")$Freq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "good")$Freq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "okay")$Freq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "bad")$Freq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "horrible")$Freq),
+                 newCount = c(subset(altCounts, scale == "good_excellent" & Var1 == "excellent")$NewFreq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "good")$NewFreq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "okay")$NewFreq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "bad")$NewFreq,
+                           subset(altCounts, scale == "good_excellent" & Var1 == "horrible")$NewFreq),
+                 stringsAsFactors = FALSE))
+# liked_loved
+saliences <- rbind(saliences,
+      data.frame(scale = rep("liked_loved", 5), degree = degrees,
+                 count = c(subset(altCounts, scale == "liked_loved" & Var1 == "loved")$Freq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "liked")$Freq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "indifferent")$Freq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "disliked")$Freq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "hated")$Freq),
+                 newCount = c(subset(altCounts, scale == "liked_loved" & Var1 == "loved")$NewFreq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "liked")$NewFreq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "indifferent")$NewFreq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "disliked")$NewFreq,
+                           subset(altCounts, scale == "liked_loved" & Var1 == "hated")$NewFreq),
+                 stringsAsFactors = FALSE))
+# memorable_unforgettable
+saliences <- rbind(saliences,
+      data.frame(scale = rep("memorable_unforgettable", 5), degree = degrees,
+                 count = c(subset(altCounts, scale == "memorable_unforgettable" & Var1 == "unforgettable")$Freq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "memorable")$Freq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "ordinary")$Freq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "bland")$Freq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "forgettable")$Freq),
+                 newCount = c(subset(altCounts, scale == "memorable_unforgettable" & Var1 == "unforgettable")$NewFreq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "memorable")$NewFreq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "ordinary")$NewFreq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "bland")$NewFreq,
+                           subset(altCounts, scale == "memorable_unforgettable" & Var1 == "forgettable")$NewFreq),
+                 stringsAsFactors = FALSE))
+
+# palatable_delicious
+saliences <- rbind(saliences,
+      data.frame(scale = rep("palatable_delicious", 5), degree = degrees,
+                 count = c(subset(altCounts, scale == "palatable_delicious" & Var1 == "delicious")$Freq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "palatable")$Freq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "mediocre")$Freq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "gross")$Freq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "disgusting")$Freq),
+                 newCount = c(subset(altCounts, scale == "palatable_delicious" & Var1 == "delicious")$NewFreq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "palatable")$NewFreq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "mediocre")$NewFreq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "gross")$NewFreq,
+                           subset(altCounts, scale == "palatable_delicious" & Var1 == "disgusting")$NewFreq),
+                 stringsAsFactors = FALSE))
+
+# some_all
+saliences <- rbind(saliences,
+      data.frame(scale = rep("some_all", 5), degree = degrees,
+                 count = c(subset(altCounts, scale == "some_all" & Var1 == "all")$Freq,
+                           subset(altCounts, scale == "some_all" & Var1 == "most")$Freq,
+                           subset(altCounts, scale == "some_all" & Var1 == "some")$Freq,
+                           subset(altCounts, scale == "some_all" & Var1 == "little")$Freq,
+                           subset(altCounts, scale == "some_all" & Var1 == "none")$Freq),
+                 newCount = c(subset(altCounts, scale == "some_all" & Var1 == "all")$NewFreq,
+                           subset(altCounts, scale == "some_all" & Var1 == "most")$NewFreq,
+                           subset(altCounts, scale == "some_all" & Var1 == "some")$NewFreq,
+                           subset(altCounts, scale == "some_all" & Var1 == "little")$NewFreq,
+                           subset(altCounts, scale == "some_all" & Var1 == "none")$NewFreq),
+                 stringsAsFactors = FALSE))
+
+# write.csv(saliences, "model_data/saliences5.csv")
 ```

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
improved cost formulation and norming as well as data files in models_data dir

@@
 }
-# old !!!!
-# speaker.lhd = function(rating, degree, m, alpha) {
-#   numerator = speaker.inf(m[rating, degree], alpha)
-#   normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
-#   return(numerator / normalize)
-# }
 
@@
                             cost = rep(0.0, 2), stringsAsFactors = FALSE)
-salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences5.csv")
-salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences4.csv")
-salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/saliences2.csv")
-normNegSalienceCosts <- function(saliences) {
-  for (s in scales) {
-    saliences[saliences$scale == s, ]$cost <-
-      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
-  }
-  saliences
-}
+salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
+salienceCosts4 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences4.csv")
+salienceCosts2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences2.csv")
+# normNegSalienceCosts <- function(saliences) {
+#   for (s in scales) {
+#     saliences[saliences$scale == s, ]$cost <-
+#       -1 * normedVec(saliences[saliences$scale == s, ]$cost)
+#   }
+#   saliences
+# }
 # salience <- c(0.22, 0.08, 0.05, 1, 1)
@@
 
-costs <- salienceCosts5
+############# NEW SALIENCES 1/20/16 #########
+salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
+NUM_ALTERNATIVES_E9 <- 180
+normNegSalienceCosts <- function(saliences) {
+  saliences$cost <- c(rep(NA, nrow(saliences)))
+  for (s in scales) {
+    saliences[saliences$scale == s, ]$cost <-
+      (-1 * saliences[saliences$scale == s, ]$newCount) / NUM_ALTERNATIVES_E9
+    saliences[saliences$scale == s, ]$cost <-
+      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
+  }
+  saliences[, c("scale", "degree", "cost")]
+}
+############# NEW SALIENCES 1/20/16 #########
+
+costs <- normNegSalienceCosts(salienceCosts5)
 priors <- unifPriors
@@
 ```{r}
-mergedData <- matchModelHumanData(runFull(data, calcFn = 2, alpha = 7, numAlts = 5), listener)
-plotData <- mergedData
+# mergedData <- matchModelHumanData(runFull(data, calcFn = 2, alpha = 7, numAlts = 5), listener)
+# plotData <- mergedData
 

### 2016-01-20 models/RSA_alternativeCostFormulation.Rmd
updated empty costs, re-outputed allModelRuns WITH salience costs

@@
 # --------------
-emptyCosts5 <- data.frame(degree = c("low2", "low1", "mid", "hi2", "hi1"),
-                            cost = rep(0.0, 5), stringsAsFactors = FALSE)
+emptyCosts5 <- data.frame(scale = c(rep("good_excellent", 5),
+                                    rep("liked_loved", 5),
+                                    rep("memorable_unforgettable", 5),
+                                    rep("palatable_delicious", 5),
+                                    rep("some_all", 5)),
+                          degree = rep(c("hi1", "hi2", "mid", "low1", "low2"), 5),
+                          newCount = rep(0.0, 25),
+                          stringsAsFactors = FALSE)
+emptyCosts4 <- data.frame(scale = c(rep("good_excellent", 4),
+                                    rep("liked_loved", 4),
+                                    rep("memorable_unforgettable", 4),
+                                    rep("palatable_delicious", 4),
+                                    rep("some_all", 4)),
+                          degree = rep(c("hi1", "hi2", "low1", "low2"), 5),
+                          newCount = rep(0.0, 20),
+                          stringsAsFactors = FALSE)
+emptyCosts2 <- data.frame(scale = c(rep("good_excellent", 2),
+                                    rep("liked_loved", 2),
+                                    rep("memorable_unforgettable", 2),
+                                    rep("palatable_delicious", 2),
+                                    rep("some_all", 2)),
+                          degree = rep(c("hi", "low"), 5),
+                          newCount = rep(0.0, 10),
+                          stringsAsFactors = FALSE)
+
+# degree = c("low2", "low1", "mid", "hi2", "hi1"),
+#                             newCount = rep(0.0, 5), stringsAsFactors = FALSE)
 emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
-                            cost = rep(0.0, 4), stringsAsFactors = FALSE)
+                            newCount = rep(0.0, 4), stringsAsFactors = FALSE)
 emptyCosts2 <- data.frame(degree = c("low", "hi"),
-                            cost = rep(0.0, 2), stringsAsFactors = FALSE)
+                            newCount = rep(0.0, 2), stringsAsFactors = FALSE)
 salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
@@
 normNegSalienceCosts <- function(saliences) {
-  saliences$cost <- c(rep(NA, nrow(saliences)))
+  # Add cost column
+  saliences$cost <- c(rep(0, nrow(saliences)))
+
+  # Check if we've passed emptyCost
+  if (all(saliences$newCount == 0)) return(saliences[, c("scale", "degree", "cost")])
+
   for (s in scales) {
@@
   results <- list() ## Will return this
+  newCosts <- normNegSalienceCosts(costs)
 
-  newCosts <- normNegSalienceCosts(costs)
   data <- left_join(speaker, newCosts) %>%
@@
 
-Entailment / Neg alts / Symmetric scale
+Run complte analyses and output to csv
 ```{r}
+# Run analyses
 symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, salienceCosts5, numAlts = 5)
@@
 entailmentRun[[4]]
-
-######WORKING HERE!!!!!!
 
@@
 
-# write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
+#write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
 ```

### 2016-01-20 Paper/Paper.Rmd
updated paper before meeting with mike Wed 01202016

--- 2016-01-11 Paper/Paper.Rmd
@@
 ---
-title: "The importance of negative alternatives in scalar implicature"
+title: "The importance of alternatives in scalar implicature"
 bibliography: library.bib
@@
     Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
-In the canonical "some, but not all" scalar implicature, listeners enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "She ate some of the cookies." A Gricean account of this phenomena assumes the presence of "salient alternatives" with varying degrees of informatitivy.
-"Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." While intuitive, empirical evidence for the presence of such alternatives is limited.
-Our current work explores the role different scale representations may play in scalar implicature.
-Using a Bayesian model of implicature generation we simulate various scale representations that might be available to a listener, comparing model predictions to human judgment.
-Results indicate that implicature generation likely requires "full" scale representations, including negative valenced alternatives, rather than the typical entailment only scales assumed in most research to date.
+For example, listeners routinely enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "Bob ate some of the cookies." A Gricean account of this phenomena assumes the presence of *salient alternatives* with varying degrees of informativity.
+"Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." Empirical evidence for the presence of such alternatives and accounts of their effect on implicature has been limited.
+Our current work explores the role different scale representations may play in scalar implicature using emperical measures of literal semantics and a Bayesian model of implicature generation.
+Comparisons with human judgments indicate that pragmatic inference may rely on fairly complete alternative sets rather than the typical entialment only scales assumed in most research to date.
 
@@
 library(ggplot2)
+library(knitr)
+library(rjson)
+library(dplyr)
+library(tidyr)
+library(gridExtra)
+library(jsonlite)
+library(png)
+library(grid)
+```
+
+```{r helpers}
+path <- "~/Desktop/Projects/scalar_implicature/models/"
+normedVec <- function(vec) vec / sum(vec)
+```
+
+```{r, data}
+# All scales studied
+# ------------------
+scales <- c("good_excellent",
+            "liked_loved",
+            "palatable_delicious",
+            "memorable_unforgettable",
+            "some_all")
+# Experiment E9: Alternatives
+# ---------------------------
+alternativesData <- read.csv(paste(path, "model_data/e9_alternativeCounts.csv", sep = ""),
+                             stringsAsFactors = FALSE)
+allModelRunData <- read.csv(paste(path, "model_data/allModelRuns.csv", sep = ""),
+                     stringsAsFactors = FALSE)
+
+# Experiments E8, E10, E12: Literal listener
+# ------------------------------------------
+speakerE12 <- read.csv(paste(path, "model_data/L0_e12.csv", sep  = ""), stringsAsFactors = FALSE)
+speakerE10 <- read.csv(paste(path, "model_data/L0_e10.csv", sep = ""), stringsAsFactors = FALSE)
+speakerE8 <- read.csv(paste(path, "model_data/L0_e8.csv", sep = ""), stringsAsFactors = FALSE)
+# Experiments E6, E11: Pragmatic listener
+# ---------------------------------------
+listenerE6 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
+listenerE11 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
 ```
@@
 
-[Implicature as a case study for pragmatics]\newline
-\textbf{Succesful communication regularly requires listeners to make inferences that go beyond the semantic content of a speaker's utterance.} "Scalar implicatures" are a hallmark of such pragamtic enrichment.
+Successful communication regularly requires listeners to make inferences that go beyond the literal semantic content of a speaker's utterance.
+"Scalar implicature" is a hallmark of such pragmatic enrichment.
 For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies." (citations) A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
-Continuing with the prior example, within this framework a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* to use "some" when "all" could have been used.
+Continuing with the cookie example, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* to use "some" when "all" could have been used.
 
-[Scalar implicature in particular, what are the alternatives?]\newline
-\textbf{The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice)}.
-Previous research indicates implicature generation is affected by the set of alternatives available, both in adults (Degen, Franke) and is possibly the source of difficulty in computing implicatures for children (Barner).
-Degen found ...
-Similarily, Franke demonstrated...
+The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice).
+Recent studies indicate implicature generation is affected by the set of alternatives (hereafter 'scale representations') available to listeners, both in adults (Degen, Franke) and is possibly a source of difficulty in computing implicatures for children (Barner).
+[Degen found ...
+Similarly, Franke demonstrated...
 (the importance of a strong negative valenced term such as "none" adopting a Bayesian model of implicature generation.
-Model performance improved significantly when "none" was included...) Despite these signals, little empirical evidence points directly to the impact of scale representaion in scalar implicature.
-The current work investigates the role different scale representaitons play in scalar implicature.
+Model performance improved significantly when "none" was included...)] Despite these signals, little empirical evidence points directly to the impact of scale representation in scalar implicature.
+The current work investigates the role different scale representations may play in scalar implicature.
 
-[RSA as a way of studying implicature]\newline
-\textbf{Measuring the degree to which alternatives may be present during implicature generation is a difficult task}.
-Issues of introspection aside, simply querying a participant about the apparent saliency of particular alternatives is problematic because the alternatives are made salient in the query itself.
-To circumvent this issue, we adopted a computational model of implicature generation.
-Adopting a computational framework allowed us to simulate the effects of various scalar alternatives sets on implicature generation, comparing model predictions to human judgments.
+While the notion of a set of alternatives is fairly intuitive in the context of scalar items (it's part of how their defined), measuring alternatives is not.
+Issues of introspection aside, simply querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the actual query.
+To avoid this issue we adopt a computational model, formalizing implicature generation as Bayesian inference.
+Using empirical measures we simulate the effects of different alternatives sets on model predictions.
+Model predictions are compared to human judgment data.
 
-[How RSA works]\newline
-\textbf{Rational Speech-act theory (RSA) is a Bayesian framework for modeling scalar implicature.} How it works...
-Previous work using RSA has accurately modeled human judgments in both ad-hoc (Frank & Goodman, 2012) and embedded implicature settings (Stuhmuller & Goodman ...)....
+Bayesian models of pragmatic enrichment have accurately predicted human judgments in ad-hoc (Frank & Goodman, 2012) and embedded (Stulhumuller & Goodman, 2014) implicature settings.
+Our current model follows both these studies and is based on Rational Speech-act theory (RSA).
+RSA frames language understanding as a special case of social cognition (Stulhumuller & Goodman, 2014), in which listeners and speakers reason about one-another.
+In the following set of experiments, we outline a literal semantics task (Experiments 1a, 3a and 4) as well as pragmatic judgment task (1b, 3b).
+Data from the literal semantics task are used to approximate information a Speaker might assume when reasoning about a Listener who interprets semantics literally (without pragmatic enrichment).
+Likewise, pragmatic judgments  are used to compare model posterior predictions and assess quality of fit.
 
-[Using the scalar diversity approach to get beyond the some/all implicature]\newline
-\textbf{Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably focusing on "some/all".} This lack "Scalar Diversity" (van Tiel, 2013) not only presents a problem in terms of generalization of findings, but within our current computational framework, presents a problem of data sparsity.
-We adopt a "Scalar Diversity" approach in our experimental design in order to incorporate multiple scalar items from a range of grammatical classes.
-In particular, we use a food review paradigm to quantify what would otherwise be ambiguous semantics as distirbutions over star-ratings.
+The heart of this investigation is concerned with populating our computational framework with empirical data.
+In particular we use experimental tools to measure otherwise ambigous literal semantics, to generate a set of plausible alternatives, and to obtain human pragmatic judgments for model comparison.
+Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably "some/all".
+This lack "Scalar Diversity" (van Tiel, 2013) makes generalization across different scalar families problematic.
+We adopt a "Scalar Diversity" approach in our experimental design in order to incorporate multiple scalar items from a range of grammatical classes (see Figure 5 for a complete set of scalar items used).
+In particular, we use a food review paradigm to quantify literal semantics and pragmatic judgments as distributions over star-ratings.
 
-[Outline of the rest of the paper]\newline
-\textbf{In the following paper we present three experiments and three model simulations based on the experimental data.} We used a food review paradigm in which linguistic `meaning' for a given scalar item was quantified as a distribution over star-ratings.
-Quantifying both literal semantic content and pragmatic judgments in this way provided an important interface to RSA, especially for scalar items with ambigous literal semantics (items such as "memorable/unforgettable" or "palatable/delicious).
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows a trial from Experiment 1a with the target scalar \`liked\'.
+Participants responses to the binary dependent variable are used to quantify literal semantics.
+The right panel shows a trial from Experiment 1b with the target scalar \`liked\'.
+Participants were asked to generate the star rating they think the speaker likely intended, given the target scalar (in this case 'liked')."}
+
+# Screen shots of literal listener and pragmatic listener conditions
+grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/exp1_stimuli.png"))
+```
+
+In the following paper we investigate the role of scale representation in scalar implicature.
+We use a food review paradigm in which 'meaning' for a given scalar item was quantified as a distribution over star-ratings.
+Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambigous literal semantics (e.g.
+items such as "liked/loved" or "memorable/unforgettable").
 In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
-Alternatives generated in Experiment 2 supplmented the original stimuli from Experiments 1a,b in Experiments 3a,b.
-Using the literal semantic data from Experiments 1a and 3a we modeled pragmatic enrichment using RSA and compared model predictions to human judgment data from Experiments 1b and 3b.
-Results indicated that model performance was significantly improved with the incorporation of negative valenced scalar items.
-Indeed, peak model performance occurs for simulations with the ``fullest" scale representations.
-This result suggests that more "fully specified" scale representations may be active for human participants while making pragmatic judgments.
+We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experimeng 2.
+Additionally, by looking at the relative frequencies of alternatives generated in Experiment 2 we were able to compute a saliency measure for each alternative.
+Using the literal semantic data from Experiments 1a, 3a and 4, we modeled pragmatic enrichment using RSA and compared model predictions to human judgments obtained in Experiments 1b and 3b.
+Model performance was significantly improved with the incorporation of alternatives.
+This result suggests that more ``fully specified" scale representations may be active for human participants while making pragmatic judgments for scalar items.
 
-# Experiments - Literal listener and Pragmatic Listener tasks
+# Experiment 1a,b: Entailment scales
 
-We used a food review paradigm to quantify literal semantics and assess pragmatic judgments for scalar items.
-Within this framework, 'meaning' for a given scalar term is quantified as a distribution over stars.
-Literal semantics for scalar items was assessed through a compatibility measure in Experiments 1a and 3a.
-Participants were presented a star-rating (betwen 1-5 stars) and asked "Do you think the person *loved* the food." We used a binary dependent measure "yes/no" to assess compatibility.
-To assess pragmatic judgments, participants were presented a sentence such as "Someone said they *loved* the food" and asked to select the number of stars they thought the reviewer likely gave.
-In this case, the dependent measure was a star-rating from 1-5 stars.
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (1a) and pragmatic judgments (1b) for entailment only scales (e.g. "liked/loved", "good/excellent", etc).
 
-# Experimental 1a,b: Entailment scales
+## Methods
 
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (study 1a) and assess pragamtic judgments (study 1b) for positive valenced scalar pairs (see appendix A for the complete list).
+### Participants
+Participants for both tasks were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+Thirty participants were recruited for Experiment 1a.
+Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Fifty participants were recruited for experiment 1b.
+Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
 
-## Participants
+### Design and procedure
+The left panel of Figure 1 shows a screen shot of a trial from Experiment 1a.
+Participants were presented with a target scalar item and a star-rating (between 1-5 stars) and asked to judge the compatibility of the scalar item and star-rating.
+Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person \___ed the food?" where a target scalar was presented in the "\___ed." Each participant was presented all scalar item and star-rating combinations with randomization.
 
-Particpants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
-Thirty participants were recruited for Experiment 1a (Literal Listener task).
-Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
-
-Fifty particpants were recruited for Experiment 1b (Pragmatic Listener task).
-Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
-
-## Procedure
-
-On each trial of the literal listener task (study 1a) participants were presented with a star-rating (between 1-5 stars) and asked to judge the compatibility of the star-rating with a target scalar term.
-Compatibiltiy was assessed through a binary "yes/no" response to a question of the form "Do you think that the person \___ed the food?" where a target scalar was presented in the "\___ed." Each participant was presented all scalar item and star-rating combinations with randomization.
-
-On each trial of the pragmatic listener task (study 1b), participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they \___ed the food" and were asked to generate a star-rating according to what they think the reviewer likely gave.
+The right panel of Figure 1 shows a screen shot of a trial from Experiment 1b.
+On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they \___ed the food." They were then asked to generate a star-rating according to what they think the reviewer likely gave.
 Each participant was presented all scalar items with randomization.
@@
 ## Results and Discussion
+
+The left panel of figure two shows literal semantics for each of the scalar terms "liked" and "loved" as distributions over star-ratings.
+
+Chi-squared test? Null results, not really important here anyway...
+```{r}
+# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
+#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
+# subset(speakerE8, degree == "low")$cnt.judgment
+# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
+#            subset(speakerE8, degree == "low")$cnt.judgment)
+```
+
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'.
+The y-axis is the percentage of \'yes\' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\\% of respondents beleived that \'liked\' was compatible with both 4 and 5 stars).
+Erro bars are 95\\% confidence intervals.
+The right panel plots pragmatic judgments for the scalar pair \'liked/loved\'.
+The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\\% of judgments when prompted with \'loved\' were 5-stars)."}
+
+plotData <- speakerE8 %>%
+  mutate(degree = ifelse(degree == "hi", "loved", "liked"))
+
+# Literal listener: Entailment (e8)
+e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
+  geom_line() +
+  ylab("Percent yes") +
+  geom_linerange(aes(ymin = speaker.p - cil, 
+                     ymax = speaker.p + cih)) +
+  ggtitle("Literal semantics")
+
+# Pragmatic listener: Entailment (e6)
+plotData <- listenerE6 %>%
+  mutate(degree = ifelse(degree == "hi", "loved", "liked"))
+e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
+                 aes(x = stars, y = listener.p, fill = degree)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~degree) +
+  ylab("Proportion of star-ratings chosen") +
+  ggtitle("Pragmatic judgments") +
+  theme(legend.position="none")
+
+gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
+```
 
@@
 
-## Participants
-Using Amazon's Mechanical Turk, N workers were paid $0.20 to particpate.
+## Methods
+
+### Participants
+
+Using Amazon's Mechanical Turk, N workers were paid $0.20 to participate.
 n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers.
-The final sample was N workers, all of whom  were naive to the purposeof the experiment.
+The final sample was N workers, all of whom  were naive to the purpose of the experiment.
 
-## Procedure
+### Design and procedure
 Participants were presented a target scalar term embedded in a sentence such as, "In a recent restaurant review someone said they thought they *----*ed the food." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of *----*?" and asked to generate three alternatives.
@@
 ## Results and Discussion
+Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g..
+"good/excellent", "memorable/unforgettable") were similarly long-tailed.
+In Experiments 3a,b we took the top two alternatives generated for each scalar item to enrich the entailment only scales from Experiments 1a,b.
+In experiment 4 we further enriched the scales from Experiments 3a,b with a neutral valence scalar chosen from the alternative sets.
 
-# Experiment 3a,b: Full scales - incorporating negative alternatives
+```{r exp2_altsPlot_likedLoved, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
 
-Experiment 3a,b was conducted to approximate literal listener semantic distributions (study a) and assess pragamtic judgments (study b) for both positive and negative valenced scalar items (see appendix b for the complete list of items used).
+# Subset alternatives for demo
+plotData <- subset(alternativesData, scale == "liked_loved")
+removeRows <- which(plotData$alt == "liked" | plotData$alt == "loved")
+plotData <- plotData[-removeRows, ]
+# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
+altsPlot <- ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
+  geom_bar(stat="identity") + ylim(0, 52) + labs(x = "alternative", y = "counts") +
+  ggtitle(paste("Salient alternatives for ", "liked/loved")) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+altsPlot
+```
+
+# Experiment 3a,b: Incorporating top alternatives
+
+Experiment 3a,b are identical to Experiments 1a,b except the set of target scalar was expanded to include the top two alternatives generated for each scalar family.
+The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.
 
@@
 
-Particpants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
 Thirty participants were recruited for Experiment 3a (Literal Listener task).
-Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
 
-Fifty particpants were recruited for Experiment 3b (Pragmatic Listener task).
-Data for N particpants was thrown out after particpants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Fifty participants were recruited for Experiment 3b (Pragmatic Listener task).
+Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
 
 ## Procedure
+The procedure of Experiments 3a,b follow the same form as Experiments 1a,b with the expanded set of target scalar items.
 
 ## Results and Discussion
+Distributional differences.
+
+# Experiment 4: Symmetric scales
+Experiment 4a is identical to Experiments 1a and 3a except the set of target scalar was expanded to include a neutral valence scalar item for each scalar family.
+The purple colored items in Table 1 denote additional scalar items added in Experiments 4.
+
+## Participants
+
+Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+Thirty participants were recruited for Experiment 4 (Literal Listener task).
+Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+
+## Procedure
+The procedure of Experiment 4 follow the same form as Experiments 1a and 3a with the addition of a neutrally valence scalar item.
+
+## Results and Discussion
+Distributional differences.
 
 # Model
+We adopt a Bayesian model of scalar implicature.
+In particular, RSA frames language understanding as a special case of social cognition (Stuhmuller & Goodman, 2014) in which listener and speaker agents reason about one another.
+We focus on the problem of a listener inferring the meaning of a speaker's utterance.
+Let $u$ be an observed utterance by our speaker with an intended meaning $m$.
+We assume that the listener has access to a space of possible meanings $M$ and some model relating meanings $m \in M$ to $u$.
 
-## Details
+Upon hearing an utterance $u$ the Listener agent evaluates all candidate word meanings, computing their posterior probabilities $p(m | u)$.
+This quantity is proportional to the product of the prior probability $p(m)$ of a particular meaning and the likelihood $p(u | m)$.
+
+$$p(m | u) = \frac{p(u | m)p(m)}{p(u)}$$
+$$= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}$$
+
+The prior $p(m)$ represents the listener's expectations about plausible meanings (star ratings), *independent* of the utterance $u$.
+To avoid biasing the data we assume priors over meanings are uniform, however future investigations may want to experiment with different priors, either by inferring them or using empirical measures
+
+The likelihood $p(u | m)$ assumes that speakers choose words to maximize informativity in context.
+We quantified the informativeness of a word by its surprisal minus a cost.
+Cost, in this case is operationalized as a salience measure - more salient items should have a larger impact on implicature generation than less salient alternatives.
+$$p(u | m) = \frac{e^{-\alpha(-log(p(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p(m|u)) - cost(u))}}$$
+
+The posterior $p(m | u)$ reflects the listener's degree of belief that $m$ is the intended meaning of the speaker, given her utterance $u$.
+
+Using literal semantics data from experiments 1a and 3a and 4, we can simulate the role alternatives play in scalar implicature.
+In particular, we can vary the number of scalar items present during implicature generation.
+In the following analyses we focus on three scenarios 1) Entailment only scales (good, excellent), 2) Negative Alternatives (horrible, bad, good, excellent) 3) Symmetric scale (horrible, bad, okay, good, excellent).
+Table 1 contains the set of scalar items used for each simulation.
 
@@
 
+### Results
+Table here
+
+Figure 4 plots model / human correlation for our three simulations. Alpha was tuned separately for each of these runs...
+```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
+Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.
+The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
+# Tuned model run data
+plotData <- allModelRunData %>%
+  mutate(study = ifelse(numAlts == 5, "Symmetric", 
+                        ifelse(numAlts == 4, "Neg_alts", "Entailment"))) %>%
+  gather(Experiment, cors, c(corE6, corE11)) %>%
+  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
+
+# Correlation bar chart
+corBarChart <- ggplot(plotData, aes(x=study, y=cors, fill = Experiment)) + 
+  geom_bar(stat="identity", position="dodge") +
+  ylab("Correlation") +
+  xlab("Model") +
+  ylim(0, 1) + 
+  ggtitle("Model fit correlation coefficients") +
+  guides(colour=FALSE) +
+  geom_text(aes(x = study, y=as.numeric(cors) + 0.025, label = round(cors, 2), col=(Experiment)))
+
+# Correlation scatter plot
+symmetricCorPlot <- ggplot(subset(plotData, study == "Symmetric"), aes(x = listener.p, y = preds)) + 
+  geom_point() +
+  xlab("Model predictions") +
+  ylab("Human judgments") +
+  stat_smooth(method = "lm") + 
+  ggtitle("Model fit\nSymmetric scale")
+
+corBarChart
+# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
+```
+
 # General Discussion
+By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature.
+Model fit with human judgement was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
+In fact, we found that both neutral and negative valence scalar items contribute to human-like implicature generation within our framework.
+
+```{r allScalesTable, fig.env = "figure", fig.pos = "h", fig.width=3.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "This table shows the stimuli used in Experiments 1a,b, 3a,b and 4.
+Colors denote the additions made in each experiment.
+For example, in Experiment 1a we measured literal semantics for \'liked/loved\'.
+In Experiment 3a,b we extended this group to \'textit{hated/disliked/liked/loved\'.
+In Experiment 4 we extended this grou to \'hated/disliked/felt indifferent about/liked/loved\'."}
+
+# Scale stimuli
+grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/alternativeSets.png"))
+```
 
@@
 This design allowed us to quantify literal semantics for individual scalar terms as compatibility distributions over star-ratings (literal listener tasks 1a and 3a).
-Similarily, we quantified pragmatic judgments by prompting participants with a target scalar term and asking them to generate a star-rating.
+Similarly, we quantified pragmatic judgments by prompting participants with a target scalar term and asking them to generate a star-rating.

### 2016-01-21 Paper/Paper.Rmd
updated draft. reordered/rewritten intro and modeling section

@@
 listenerE6 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
-listenerE11 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
+listenerE11 <- read.csv(paste(path, "model_data/L1_e11.csv", sep = ""), stringsAsFactors = FALSE)
 ```
 
+```{r}
+speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
+                      speakerE10 %>% mutate(expt = "3a"), 
+                      speakerE8 %>% mutate(expt = "1a"))
+# ggplot(speakers, 
+#        aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
+#   geom_line() + 
+#   facet_grid(.~ scale) + 
+#   theme_bw()
+```
+
+```{r}
+listeners <- bind_rows(listenerE6 %>% mutate(expt = "1b"), 
+                      listenerE11 %>% mutate(expt = "3b"))
+zeros <- expand.grid(degree = c("low","hi"), 
+            scale = unique(listeners$scale), 
+            stars = 1:5, 
+            expt = c("1b","3b"))
+
+zlisteners <- full_join(listeners, zeros) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))
+
+# ggplot(zlisteners, 
+#        aes(x = stars, y = listener.p, col = degree, lty = expt)) + 
+#   geom_line() + 
+#   facet_grid(. ~ scale) + 
+#   theme_bw()
+```
 # Introduction
@@
 "Scalar implicature" is a hallmark of such pragmatic enrichment.
-For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies." (citations) A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
-Continuing with the cookie example, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* to use "some" when "all" could have been used.
+For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies" (van Tiel, 2014).
+A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
+Under the Gricean account, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* for the speaker to use "some" when "all" could have been used.
 
-The presence of ``salient" alternatives is critical to standard accounts of scalar implicature (Grice).
-Recent studies indicate implicature generation is affected by the set of alternatives (hereafter 'scale representations') available to listeners, both in adults (Degen, Franke) and is possibly a source of difficulty in computing implicatures for children (Barner).
-[Degen found ...
-Similarly, Franke demonstrated...
-(the importance of a strong negative valenced term such as "none" adopting a Bayesian model of implicature generation.
-Model performance improved significantly when "none" was included...)] Despite these signals, little empirical evidence points directly to the impact of scale representation in scalar implicature.
-The current work investigates the role different scale representations may play in scalar implicature.
+The presence of ``salient" alternatives is critical to the standard Gricean account of scalar implicature (Grice, 1975).
+Recent experimental evidence appears to support this.
+Using a gumball paradigm, Degen & Tanenhaus (2014) demonstrated that the scalar item *some* was judged less appropriate (natural) for small sets of items when exact numbers were seen as viable alternatives.
+This finding points to the impact a particular alternative set can have on judgments regarding scalar appropriateness.
+Using a fundamentally differnt approach, Franke (2014) formalized the Gricean account of implicature using a Bayesian model, modeling graded typicality judgments and scalar implicature.
+Results supported 'none', 'one' and 'all' as the most serious (salient) alternatives to "some."
 
-While the notion of a set of alternatives is fairly intuitive in the context of scalar items (it's part of how their defined), measuring alternatives is not.
-Issues of introspection aside, simply querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the actual query.
-To avoid this issue we adopt a computational model, formalizing implicature generation as Bayesian inference.
-Using empirical measures we simulate the effects of different alternatives sets on model predictions.
-Model predictions are compared to human judgment data.
+Taken together, each of the previous studies signal the importance of scale representation (set of available alternatives) in scalar implicature.
+However, like many recent investigations which have focused only on a small subset of scalar items, both Degen & Tanehaus (2014) and Franke (2014) focus exclusively on the scalar family "some/all." This lack "Scalar Diversity" (van Tiel, 2014) makes generalization across different scalar families problematic.
+van Tiel (2014), found substantial variation in the rate of upper-bounded construals among over 40 different scalar pairs.
+This finding suggests that implicature may differ widely between different scales.
+We adopt a "Scalar Diversity" approach in our experimental design in order to extend our investigation beyond "some/all" scalar items.
+In the following set of studies we examine implicature for "some/all" and five additional scalar families from a range of grammatical classes (see Figure 5 for a complete set of scalar items used).
+The set of scalar items for this study were chosen from among the 40 used in van Tiel (2014).
+
+Consider a scalar item other than "some" -  in the context of a scalar item such as "good", the idea of set of lexical alternatives certainly xfeels intuitive ("bad", "excellent", etc.).
+But measuring the extent to which these alternatives are salient is not so clear.
+Nor is how to measure their impact on pragmatic intepretations of the scalar item "good." In an experimental setting, querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the query.
+In the spirit of Franke (2014) and Degen & Tanenhaus (2014), we pair a computational model of implicature with empirical measurments of linguistic material.
+This combination allows us to simulate the effect of various scale representations on implicature.
+In particular, we adopt a Bayesian model of implicature and a food-review paradigm to empirically quantify literal semantics and pragmatic judgments for our scalar stimuli.
 
@@
 RSA frames language understanding as a special case of social cognition (Stulhumuller & Goodman, 2014), in which listeners and speakers reason about one-another.
-In the following set of experiments, we outline a literal semantics task (Experiments 1a, 3a and 4) as well as pragmatic judgment task (1b, 3b).
-Data from the literal semantics task are used to approximate information a Speaker might assume when reasoning about a Listener who interprets semantics literally (without pragmatic enrichment).
-Likewise, pragmatic judgments  are used to compare model posterior predictions and assess quality of fit.
+In this framework, a listener uses Bayesiain inference to interpret the intended meaning $m$ of a speaker who has made an utterance $u$.
+We will make the model specifications explicit later in the paper.
 
-The heart of this investigation is concerned with populating our computational framework with empirical data.
-In particular we use experimental tools to measure otherwise ambigous literal semantics, to generate a set of plausible alternatives, and to obtain human pragmatic judgments for model comparison.
-Recent experimental investigations of scalar implicature have focused almost exclusively on a small subset of possible scales, most notably "some/all".
-This lack "Scalar Diversity" (van Tiel, 2013) makes generalization across different scalar families problematic.
-We adopt a "Scalar Diversity" approach in our experimental design in order to incorporate multiple scalar items from a range of grammatical classes (see Figure 5 for a complete set of scalar items used).
-In particular, we use a food review paradigm to quantify literal semantics and pragmatic judgments as distributions over star-ratings.
+In the following study we investigate the role of scale representation on scalar implicature.
+To do so we combine a computational framework with empirical measurements to simulate the type of scale representations that might be available to a listener.
+In the following sections we outline the specifics of the model and the particular components for which we need to to make empirical measurements.
+We then outline a series of experiments meant to a) quantify literal semantics for otherwise ambiguous scalar items, b) measure pragmatic judgments and c) generate a set of plausible alternatives for our set of scalar pairs taken from van Tiel (2014).
+In particular, we adopt a food review paradigm throughout our empirical data gathering, quantifying linguistic meaning (both literal semantics and pragmatic judgments) as distributions over star ratings.
+Finally, we simulate the impact of three different scale representations, "entailment", "mid" and "symmetric" on implicature generation, comparing model predictions with pragmatic judgments captured empirically.
+Results indicate that humans may employ more "fully specified" scale representatinos, relying on the presence of multiple alternatives during pragmatic enrichment.
+
+-----
+
+# Modeling implicature: Rational Speech-act theory
+We adopt a Bayesian model of scalar implicature known as Rational Speech-act theory (RSA).
+In particular, RSA frames language understanding as a special case of social cognition (Frank & Goodman, 2012; Stuhmuller & Goodman, 2014) in which listener and speaker agents reason about one another.
+We focus on the problem of a listener inferring the meaning of a speaker's utterance.
+Let $u$ be an observed utterance made by our speaker with an intended meaning $m$.
+We assume that the listener has access to a space of possible meanings $M$ and some model relating meanings $m \in M$ to $u$.
+
+Upon hearing an utterance $u$ the Listener agent evaluates all candidate word meanings, computing their posterior probabilities $p_{L1}(m | u)$.
+This quantity is proportional to the product of the prior probability $p(m)$ of a particular meaning and the likelihood $p(u | m)$.
+
+$$p_{L1}(m | u) = \frac{p(u | m)p(m)}{p(u)}$$
+$$= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}$$
+
+The **prior** $\mathbf{p(m)}$ represents the listener's expectations about plausible meanings (star ratings), *independent* of the utterance $u$.
+To avoid biasing the data we assume priors over meanings are uniform, however future investigations may want to experiment with different priors, either by inferring them or using empirical measures
+
+$\mathbf{p(u | m)}$ quantifies the **likelihood** that a speaker would make a particular utterance $u$ given an intended meaning $m$.
+Our model assumes that speakers choose words to maximize the utility of an utterance in context.
+Utility is operationalized as the informativity of a particular utterance (suprisal) minus a cost.
+In particular, the speaker chooses an utterance in order to maximize the utility of a listener who interprets her utterance literally $p_{L0}(m|u)$.
+$L_0$ denotes a literal listener interpretation.
+$$p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}$$
+
+The **posterior** $\mathbf{p_{L1}(m | u)}$ quantifies a listener's pragmatic enrichment of an utterance $u$ as degree of belief that $m$ is the intended meaning of the speaker, given an utterance $u$.
+$L_1$ denotes a pragmatic listener interpration.
+
+## Populating the model: Measuring literal semantics and pragmatic judgments
+In order to simulate the role of scale representation on implicature we pair a computational framework with empirical data.
+In particular we use experimental tools to populate three components of the model.
+First, to measure otherwise ambigous literal semantics $\mathbf{p_{L0}(m|u)}$ (our "Scalar Diversity"" approach).
+Second, to generate a set of plausible alternatives to the original scalar pairs taken from van Tiel (2014).
+Lastly, to obtain human pragmatic judgments for model comparison $\mathbf{p_{L1}(m|u)}$.
+
+Starting with the first component, consider the scalar items  "some" and "all." Both are convenient for modeling in a computational framework like the one we've proposed above.
+Their literal semantics $\mathbf{p_{L0}}$ are easily quantified over sets.
+
+$$\text{\textit{some of the A's are B's.}}$$
+$$[[some]] = \{<A, B> : |A \cap B| \geq 1 \}$$
+
+$$\text{\textit{all of the A's are B's.}}$$
+$$[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}$$
+
+The same cannot be said for items such as "good / excellent", "memorable / unforgettable" or "liked / loved."
+
+In the following set of studies we adopt a food-review paradigm to measure literal semantics and pragmatic judgments empirically.
+In order to capture graded typicality judgments as in Degen & Tanenhaus (2014) we use a compatiblity measure dependent variable, pairing scalar items with star-ratings in our literal listener task (Experiments 1a, 3a and 4).
+Data from these experiments is used to approximate the literal listener semantics for a given scalar item $u$ as a distribution over star-ratings $m \in \text{\{1 - 5 stars\}}$.
+Similarly, pragmatic judgment data from Experiments 1b and 3b serve as our primary points of comparison with model predictions $\mathbf{p_{L1}(m|u)}$, again quantifying judgments as distributions over star-ratings.
+In the following section we take the read through our experiments.
 
@@
 
-In the following paper we investigate the role of scale representation in scalar implicature.
-We use a food review paradigm in which 'meaning' for a given scalar item was quantified as a distribution over star-ratings.
-Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambigous literal semantics (e.g.
-items such as "liked/loved" or "memorable/unforgettable").
-In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
-We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experimeng 2.
-Additionally, by looking at the relative frequencies of alternatives generated in Experiment 2 we were able to compute a saliency measure for each alternative.
-Using the literal semantic data from Experiments 1a, 3a and 4, we modeled pragmatic enrichment using RSA and compared model predictions to human judgments obtained in Experiments 1b and 3b.
-Model performance was significantly improved with the incorporation of alternatives.
-This result suggests that more ``fully specified" scale representations may be active for human participants while making pragmatic judgments for scalar items.
-
 # Experiment 1a,b: Entailment scales
 
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (1a) and pragmatic judgments (1b) for entailment only scales (e.g. "liked/loved", "good/excellent", etc).
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (1a) and pragmatic judgments (1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
+Each pair consists of a "weaker" scalar term (e.g.
+"some") and a stronger scalar term (e.g.
+"all").
+We are calling these "entialment scales"", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.
 
@@
 
-# Model
-We adopt a Bayesian model of scalar implicature.
-In particular, RSA frames language understanding as a special case of social cognition (Stuhmuller & Goodman, 2014) in which listener and speaker agents reason about one another.
-We focus on the problem of a listener inferring the meaning of a speaker's utterance.
-Let $u$ be an observed utterance by our speaker with an intended meaning $m$.
-We assume that the listener has access to a space of possible meanings $M$ and some model relating meanings $m \in M$ to $u$.
-
-Upon hearing an utterance $u$ the Listener agent evaluates all candidate word meanings, computing their posterior probabilities $p(m | u)$.
-This quantity is proportional to the product of the prior probability $p(m)$ of a particular meaning and the likelihood $p(u | m)$.
-
-$$p(m | u) = \frac{p(u | m)p(m)}{p(u)}$$
-$$= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}$$
-
-The prior $p(m)$ represents the listener's expectations about plausible meanings (star ratings), *independent* of the utterance $u$.
-To avoid biasing the data we assume priors over meanings are uniform, however future investigations may want to experiment with different priors, either by inferring them or using empirical measures
-
-The likelihood $p(u | m)$ assumes that speakers choose words to maximize informativity in context.
-We quantified the informativeness of a word by its surprisal minus a cost.
-Cost, in this case is operationalized as a salience measure - more salient items should have a larger impact on implicature generation than less salient alternatives.
-$$p(u | m) = \frac{e^{-\alpha(-log(p(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p(m|u)) - cost(u))}}$$
-
-The posterior $p(m | u)$ reflects the listener's degree of belief that $m$ is the intended meaning of the speaker, given her utterance $u$.
-
-Using literal semantics data from experiments 1a and 3a and 4, we can simulate the role alternatives play in scalar implicature.
-In particular, we can vary the number of scalar items present during implicature generation.
-In the following analyses we focus on three scenarios 1) Entailment only scales (good, excellent), 2) Negative Alternatives (horrible, bad, good, excellent) 3) Symmetric scale (horrible, bad, okay, good, excellent).
-Table 1 contains the set of scalar items used for each simulation.
-
-## Model fitting and comparison
+# Temp section Model was here
 
@@
 
-the role various scale representations might play in scalar implicature.
-In Experiment 1a,b we gather data for Entailment only scalar items such as "some/all," "good/excellent," etc.
-In Experiment 1a we quantify literal semantics for scalar items as compatibility distributions over star-ratings (Literal listener task).
-In Experiment 1b, we ask participants to make judgments about speaker intentions by generating star-ratings in response to reviews (Pragmatic listener task).
-In Experiment 2, we ask participants to generate plausible alternatives to the scalar items used in Experiments 1a,b.
-Experiments 3a,b are identical to 1a,b with the addition of scalar items from Experiment 2.
-In this we explore fuller scale descriptions, gathering both literal semantics and pragmatic judgments for fuller scale descriptions such as "none/some/most/all" or "horrible/bad/good/excellent."
-
-In three experiments we 
-Our "Scalar Diversity" approach involves a food review paradigm we employed throughout our three experiments.
-In both Literal Listener (1a, 3a) and Pragmatic Listener (1b, 3b) tasks, participants are shown one sentence prompts containing a target scalar term along with a star-rating.
-In individual trials, star-ratings were either pre-populated (in literal listener tasks) or used as the dependent variable (pragmatic listener tasks).
-This design allowed us to quantify literal semantics for individual scalar terms as compatibility distributions over star-ratings (literal listener tasks 1a and 3a).
-Similarly, we quantified pragmatic judgments by prompting participants with a target scalar term and asking them to generate a star-rating.
+use a food review paradigm in which 'meaning' for a given scalar item was quantified as a distribution over star-ratings.
+Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambigous literal semantics (e.g.
+items such as "liked/loved" or "memorable/unforgettable").
+In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
+We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experimeng 2.
+Additionally, by looking at the relative frequencies of alternatives generated in Experiment 2 we were able to compute a saliency measure for each alternative.
+Using the literal semantic data from Experiments 1a, 3a and 4, we modeled pragmatic enrichment using RSA and compared model predictions to human judgments obtained in Experiments 1b and 3b.
+Model performance was significantly improved with the incorporation of alternatives.
+This result suggests that more ``fully specified" scale representations may be active for human participants while making pragmatic judgments for scalar items.

### 2016-01-21 Paper/Paper.tex
title tweaks
updated draft. reordered/rewritten intro and modeling section

--- 2016-01-05 Paper/Paper.tex
@@
 
-\title{The importance of negative alternatives in pragmatic implicature}
+\title{The importance of alternatives in scalar implicature}
 
-\author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloquin@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
+\author{{\large \bf Benjamin Peloquin} \\ \texttt{bpeloqui@stanford.edu} \\ Department of Psychology \\ Stanford University \And {\large \bf Michael C.
 Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}
@@
 \begin{abstract}
-Frameworks of pragmatic enrichment, starting with Grice 1975, implicitly
-assume the presence of salient alternatives. For example, the standard
-quantity implicature arises the presence of a competiting and more
-informative alternatives. Using a Bayesian formulzation of this theory
-we assess the degree to which alternatives influence pragmatic
-enrichment of scalar items. Our findings suggest that the presence of a
-complete of set of possible alternatives.
+Succesful communication regularly requires listeners to make pragmatic
+inferences - enrichments beyond the literal meaning of a speaker's
+utterance. For example, listeners routinely enrich the meaning of
+``some'' to ``some, but not all'' when interpreting a sentence such as
+``Bob ate some of the cookies.'' A Gricean account of this phenomena
+assumes the presence of \emph{salient alternatives} with varying degrees
+of informativity. ``Some,'' in the example above, is enriched to ``some,
+but not all'' in the presence of the stronger alternative ``all.''
+Empirical evidence for the presence of such alternatives and accounts of
+their effect on implicature has been limited. Our current work explores
+the role different scale representations may play in scalar implicature
+using emperical measures of literal semantics and a Bayesian model of
+implicature generation. Comparisons with human judgments indicate that
+pragmatic inference may rely on fairly complete alternative sets rather
+than the typical entialment only scales assumed in most research to
+date.
 
@@
 
-Implicature as a case study for pragmatics
+Humpty Dumpty Quote\ldots{}
 
-RSA as a way of studying implicature ({\textbf{???}})
+Successful communication regularly requires listeners to make inferences
+that go beyond the literal semantic content of a speaker's utterance.
+``Scalar implicature'' is a hallmark of such pragmatic enrichment. For
+example, listeners routinely enrich the meaning of the scalar item
+``some'' to ``some, but not all'' in sentences like ``Bob ate some of
+the cookies'' (van Tiel, 2014). A Gricean account of this phenomena
+assumes listeners reason about the intended meaning of a speaker while
+incorporating knowledge about a) alternative scalar items a speaker
+could have used (such as ``all'') and b) the relative informativity of
+using such alternatives (Grice, 1975). Under the Gricean account, a
+listener will infer that the speaker must have intended that Bob did not
+eat ``all'' the cookies because it would have been
+\emph{underinformative} for the speaker to use ``some'' when ``all''
+could have been used.
 
-Scalar implicature in particular, what are the alternatives?
-({\textbf{???}}) ({\textbf{???}})
+The presence of ``salient" alternatives is critical to the standard
+Gricean account of scalar implicature (Grice, 1975). Recent experimental
+evidence appears to support this. Using a gumball paradigm, Degen \&
+Tanenhaus (2014) demonstrated that the scalar item \emph{some} was
+judged less appropriate (natural) for small sets of items when exact
+numbers were seen as viable alternatives. This finding points to the
+impact a particular alternative set can have on judgments regarding
+scalar appropriateness. Using a fundamentally differnt approach, Franke
+(2014) formalized the Gricean account of implicature using a Bayesian
+model, modeling graded typicality judgments and scalar implicature.
+Results supported `none', `one' and `all' as the most serious (salient)
+alternatives to ``some.''
 
-Using the scalar diversity approach to get beyond the some/all
-implicature ({\textbf{???}})
+Taken together, each of the previous studies signal the importance of
+scale representation (set of available alternatives) in scalar
+implicature. However, like many recent investigations which have focused
+only on a small subset of scalar items, both Degen \& Tanehaus (2014)
+and Franke (2014) focus exclusively on the scalar family ``some/all.''
+This lack ``Scalar Diversity'' (van Tiel, 2014) makes generalization
+across different scalar families problematic. van Tiel (2014), found
+substantial variation in the rate of upper-bounded construals among over
+40 different scalar pairs. This finding suggests that implicature may
+differ widely between different scales. We adopt a ``Scalar Diversity''
+approach in our experimental design in order to extend our investigation
+beyond ``some/all'' scalar items. In the following set of studies we
+examine implicature for ``some/all'' and five additional scalar families
+from a range of grammatical classes (see Figure 5 for a complete set of
+scalar items used). The set of scalar items for this study were chosen
+from among the 40 used in van Tiel (2014).
 
-Outline of the rest of the paper
+Consider a scalar item other than ``some'' - in the context of a scalar
+item such as ``good'', the idea of set of lexical alternatives certainly
+xfeels intuitive (``bad'', ``excellent'', etc.). But measuring the
+extent to which these alternatives are salient is not so clear. Nor is
+how to measure their impact on pragmatic intepretations of the scalar
+item ``good.'' In an experimental setting, querying a participant about
+the saliency of a particular alternative is problematic because the
+alternative must be made salient during the query. In the spirit of
+Franke (2014) and Degen \& Tanenhaus (2014), we pair a computational
+model of implicature with empirical measurments of linguistic material.
+This combination allows us to simulate the effect of various scale
+representations on implicature. In particular, we adopt a Bayesian model
+of implicature and a food-review paradigm to empirically quantify
+literal semantics and pragmatic judgments for our scalar stimuli.
+
+Bayesian models of pragmatic enrichment have accurately predicted human
+judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhumuller
+\& Goodman, 2014) implicature settings. Our current model follows both
+these studies and is based on Rational Speech-act theory (RSA). RSA
+frames language understanding as a special case of social cognition
+(Stulhumuller \& Goodman, 2014), in which listeners and speakers reason
+about one-another. In this framework, a listener uses Bayesiain
+inference to interpret the intended meaning \(m\) of a speaker who has
+made an utterance \(u\). We will make the model specifications explicit
+later in the paper.
+
+In the following study we investigate the role of scale representation
+on scalar implicature. To do so we combine a computational framework
+with empirical measurements to simulate the type of scale
+representations that might be available to a listener. In the following
+sections we outline the specifics of the model and the particular
+components for which we need to to make empirical measurements. We then
+outline a series of experiments meant to a) quantify literal semantics
+for otherwise ambiguous scalar items, b) measure pragmatic judgments and
+c) generate a set of plausible alternatives for our set of scalar pairs
+taken from van Tiel (2014). In particular, we adopt a food review
+paradigm throughout our empirical data gathering, quantifying linguistic
+meaning (both literal semantics and pragmatic judgments) as
+distributions over star ratings. Finally, we simulate the impact of
+three different scale representations, ``entailment'', ``mid'' and
+``symmetric'' on implicature generation, comparing model predictions
+with pragmatic judgments captured empirically. Results indicate that
+humans may employ more ``fully specified'' scale representatinos,
+relying on the presence of multiple alternatives during pragmatic
+enrichment.
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+
+\section{Modeling implicature: Rational Speech-act
+theory}\label{modeling-implicature-rational-speech-act-theory}
+
+We adopt a Bayesian model of scalar implicature known as Rational
+Speech-act theory (RSA). In particular, RSA frames language
+understanding as a special case of social cognition (Frank \& Goodman,
+2012; Stuhmuller \& Goodman, 2014) in which listener and speaker agents
+reason about one another. We focus on the problem of a listener
+inferring the meaning of a speaker's utterance. Let \(u\) be an observed
+utterance made by our speaker with an intended meaning \(m\). We assume
+that the listener has access to a space of possible meanings \(M\) and
+some model relating meanings \(m \in M\) to \(u\).
+
+Upon hearing an utterance \(u\) the Listener agent evaluates all
+candidate word meanings, computing their posterior probabilities
+\(p_{L1}(m | u)\). This quantity is proportional to the product of the
+prior probability \(p(m)\) of a particular meaning and the likelihood
+\(p(u | m)\).
+
+\[p_{L1}(m | u) = \frac{p(u | m)p(m)}{p(u)}\]
+\[= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}\]
+
+The \textbf{prior} \(\mathbf{p(m)}\) represents the listener's
+expectations about plausible meanings (star ratings), \emph{independent}
+of the utterance \(u\). To avoid biasing the data we assume priors over
+meanings are uniform, however future investigations may want to
+experiment with different priors, either by inferring them or using
+empirical measures
+
+\(\mathbf{p(u | m)}\) quantifies the \textbf{likelihood} that a speaker
+would make a particular utterance \(u\) given an intended meaning \(m\).
+Our model assumes that speakers choose words to maximize the utility of
+an utterance in context. Utility is operationalized as the informativity
+of a particular utterance (suprisal) minus a cost. In particular, the
+speaker chooses an utterance in order to maximize the utility of a
+listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
+denotes a literal listener interpretation.
+\[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]
+
+The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
+listener's pragmatic enrichment of an utterance \(u\) as degree of
+belief that \(m\) is the intended meaning of the speaker, given an
+utterance \(u\). \(L_1\) denotes a pragmatic listener interpration.
+
+\subsection{Populating the model: Measuring literal semantics and
+pragmatic
+judgments}\label{populating-the-model-measuring-literal-semantics-and-pragmatic-judgments}
+
+In order to simulate the role of scale representation on implicature we
+pair a computational framework with empirical data. In particular we use
+experimental tools to populate three components of the model. First, to
+measure otherwise ambigous literal semantics \(\mathbf{p_{L0}(m|u)}\)
+(our ``Scalar Diversity''" approach). Second, to generate a set of
+plausible alternatives to the original scalar pairs taken from van Tiel
+(2014). Lastly, to obtain human pragmatic judgments for model comparison
+\(\mathbf{p_{L1}(m|u)}\).
+
+Starting with the first component, consider the scalar items ``some''
+and ``all.'' Both are convenient for modeling in a computational
+framework like the one we've proposed above. Their literal semantics
+\(\mathbf{p_{L0}}\) are easily quantified over sets.
+
+\[\text{\textit{some of the A's are B's.}}\]
+\[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]
+
+\[\text{\textit{all of the A's are B's.}}\]
+\[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]
+
+The same cannot be said for items such as ``good / excellent'',
+``memorable / unforgettable'' or ``liked / loved.''
+
+In the following set of studies we adopt a food-review paradigm to
+measure literal semantics and pragmatic judgments empirically. In order
+to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
+we use a compatiblity measure dependent variable, pairing scalar items
+with star-ratings in our literal listener task (Experiments 1a, 3a and
+4). Data from these experiments is used to approximate the literal
+listener semantics for a given scalar item \(u\) as a distribution over
+star-ratings \(m \in \text{\{1 - 5 stars\}}\). Similarly, pragmatic
+judgment data from Experiments 1b and 3b serve as our primary points of
+comparison with model predictions \(\mathbf{p_{L1}(m|u)}\), again
+quantifying judgments as distributions over star-ratings. In the
+following section we take the read through our experiments.
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/stimuli_exp1-1}
+
+}
+
+\caption[The left panel shows a trial from Experiment 1a with the target scalar `liked']{The left panel shows a trial from Experiment 1a with the target scalar `liked'.
+Participants responses to the binary dependent variable are used to quantify literal semantics.
+The right panel shows a trial from Experiment 1b with the target scalar `liked'.
+Participants were asked to generate the star rating they think the speaker likely intended, given the target scalar (in this case 'liked').}\label{fig:stimuli_exp1}
+\end{figure*}
+\end{CodeChunk}
 
@@
 
-\subsection{Participants}\label{participants}
+Experiment 1a and 1b were conducted to approximate literal listener
+semantic distributions (1a) and pragmatic judgments (1b) for five pairs
+of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
+Each pair consists of a ``weaker'' scalar term (e.g. ``some'') and a
+stronger scalar term (e.g. ``all''). We are calling these ``entialment
+scales''``, because they encode the assumption that a listener need only
+have a the stronger alternative present to generate an enriched
+interpretation of the weaker term.
 
-\subsection{Procedure}\label{procedure}
+\subsection{Methods}\label{methods}
+
+\subsubsection{Participants}\label{participants}
+
+Participants for both tasks were recruited on Amazon Mechanical Turk and
+paid \$0.20 for their participation. Thirty participants were recruited
+for Experiment 1a. Data for N participants was thrown out after
+participants either failed to pass two training trials or were not
+native English speakers, leaving a total sample of N. Fifty participants
+were recruited for experiment 1b. Data for N participants was thrown out
+after participants either failed to pass two training trials or were not
+native English speakers, leaving a total sample of N.
+
+\subsubsection{Design and procedure}\label{design-and-procedure}
+
+The left panel of Figure 1 shows a screen shot of a trial from
+Experiment 1a. Participants were presented with a target scalar item and
+a star-rating (between 1-5 stars) and asked to judge the compatibility
+of the scalar item and star-rating. Compatibility was assessed through a
+binary ``yes/no'' response to a question of the form ``Do you think that
+the person \_\_\_ed the food?" where a target scalar was presented in
+the ``\_\_\_ed." Each participant was presented all scalar item and
+star-rating combinations with randomization.
+
+The right panel of Figure 1 shows a screen shot of a trial from
+Experiment 1b. On each trial, participants were presented with a
+one-sentence prompt containing a target scalar item such as ``Someone
+said they \_\_\_ed the food." They were then asked to generate a
+star-rating according to what they think the reviewer likely gave. Each
+participant was presented all scalar items with randomization.
 
 \subsection{Results and Discussion}\label{results-and-discussion}
+
+The left panel of figure two shows literal semantics for each of the
+scalar terms ``liked'' and ``loved'' as distributions over star-ratings.
+
+Chi-squared test? Null results, not really important here anyway\ldots{}
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/exp1Plots-1}
+
+}
+
+\caption[The left panel plots literal semantic distributions for the scalar pair 'liked/loved']{The left panel plots literal semantic distributions for the scalar pair 'liked/loved'.
+The y-axis is the percentage of 'yes' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\% of respondents beleived that 'liked' was compatible with both 4 and 5 stars).
+Erro bars are 95\% confidence intervals.
+The right panel plots pragmatic judgments for the scalar pair 'liked/loved'.
+The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\% of judgments when prompted with 'loved' were 5-stars).}\label{fig:exp1Plots}
+\end{figure*}
+\end{CodeChunk}
 
@@
 
-\subsection{Participants}\label{participants-1}
+In Experiment 2 we asked participants to generate plausible alternatives
+for the scalar items presented in Experiment 1.
+
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Participants}\label{participants-1}
+
+Using Amazon's Mechanical Turk, N workers were paid \$0.20 to
+participate. n workers were dropped from the analysis because they
+either failed to pass training trials or were not native English
+speakers. The final sample was N workers, all of whom were naive to the
+purpose of the experiment.
+
+\subsubsection{Design and procedure}\label{design-and-procedure-1}
+
+Participants were presented a target scalar term embedded in a sentence
+such as, ``In a recent restaurant review someone said they thought they
+\emph{----}ed the food.'' Participants were then asked to generate
+plausible alternatives by responding to the question, ``If they'd felt
+differently about the food, what other words could they have used
+instead of \emph{----}?'' and asked to generate three alternatives.
+
+\subsection{Results and Discussion}\label{results-and-discussion-1}
+
+Figure 3 plots the combined counts of alternatives generated for the
+scalar items ``liked'' and ``loved.'' Alternative distributions for the
+other scalar pairs (e.g.. ``good/excellent'',
+``memorable/unforgettable'') were similarly long-tailed. In Experiments
+3a,b we took the top two alternatives generated for each scalar item to
+enrich the entailment only scales from Experiments 1a,b. In experiment 4
+we further enriched the scales from Experiments 3a,b with a neutral
+valence scalar chosen from the alternative sets.
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
+
+}
+
+\caption[Caption goes here]{Caption goes here}\label{fig:exp2_altsPlot_likedLoved}
+\end{figure*}
+\end{CodeChunk}
+
+\section{Experiment 3a,b: Incorporating top
+alternatives}\label{experiment-3ab-incorporating-top-alternatives}
+
+Experiment 3a,b are identical to Experiments 1a,b except the set of
+target scalar was expanded to include the top two alternatives generated
+for each scalar family. The orange colored items in table 1 denote
+additional scalar items added in Experiments 3a,b.
+
+\subsection{Participants}\label{participants-2}
+
+Participants for both studies were recruited on Amazon Mechanical Turk
+and paid \$0.20 for their participation. Thirty participants were
+recruited for Experiment 3a (Literal Listener task). Data for N
+participants was thrown out after participants either failed to pass two
+training trials or were not native English speakers, leaving a total
+sample of N.
+
+Fifty participants were recruited for Experiment 3b (Pragmatic Listener
+task). Data for N participants was thrown out after participants either
+failed to pass two training trials or were not native English speakers,
+leaving a total sample of N.
+
+\subsection{Procedure}\label{procedure}
+
+The procedure of Experiments 3a,b follow the same form as Experiments
+1a,b with the expanded set of target scalar items.
+
+\subsection{Results and Discussion}\label{results-and-discussion-2}
+
+Distributional differences.
+
+\section{Experiment 4: Symmetric
+scales}\label{experiment-4-symmetric-scales}
+
+Experiment 4a is identical to Experiments 1a and 3a except the set of
+target scalar was expanded to include a neutral valence scalar item for
+each scalar family. The purple colored items in Table 1 denote
+additional scalar items added in Experiments 4.
+
+\subsection{Participants}\label{participants-3}
+
+Participants for both studies were recruited on Amazon Mechanical Turk
+and paid \$0.20 for their participation. Thirty participants were
+recruited for Experiment 4 (Literal Listener task). Data for N
+participants was thrown out after participants either failed to pass two
+training trials or were not native English speakers, leaving a total
+sample of N.
 
@@
 
-\subsection{Results and Discussion}\label{results-and-discussion-1}
+The procedure of Experiment 4 follow the same form as Experiments 1a and
+3a with the addition of a neutrally valence scalar item.
 
-\section{Experiment 3a,b: Adding Negative
-alternatives}\label{experiment-3ab-adding-negative-alternatives}
+\subsection{Results and Discussion}\label{results-and-discussion-3}
 
-\subsection{Participants}\label{participants-2}
+Distributional differences.
 
-\subsection{Procedure}\label{procedure-2}
+\section{Temp section Model was here}\label{temp-section-model-was-here}
 
-\subsection{Results and Discussion}\label{results-and-discussion-2}
+\subsubsection{Results}\label{results}
 
-\section{Model}\label{model}
+Table here
 
-\subsection{Details}\label{details}
+Figure 4 plots model / human correlation for our three simulations.
+Alpha was tuned separately for each of these runs\ldots{}
 
-\subsection{Model fitting and
-comparison}\label{model-fitting-and-comparison}
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/performancePlots-1}
+
+}
+
+\caption[The left panel shows improved model fit as scale representations are enriched with more scalar items]{The left panel shows improved model fit as scale representations are enriched with more scalar items.
+Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.
+The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b.}\label{fig:performancePlots}
+\end{figure*}
+\end{CodeChunk}
 
@@
 
+By varying the type of scale representations available to our Bayesian
+model we investigated the effects of alternatives on scalar implicature.
+Model fit with human judgement was significantly improved by the
+inclusion of alternatives beyond the typical ``strong'' and ``weak''
+scalar items. In fact, we found that both neutral and negative valence
+scalar items contribute to human-like implicature generation within our
+framework.
+
+\textbackslash{}begin\{CodeChunk\}
+\textbackslash{}begin\{figure\}{[}h{]}
+
+\{\centering \includegraphics{figs/allScalesTable-1}
+
+\}
+
+\textbackslash{}caption{[}This table shows the stimuli used in
+Experiments 1a,b, 3a,b and 4{]}\{This table shows the stimuli used in
+Experiments 1a,b, 3a,b and 4. Colors denote the additions made in each
+experiment. For example, in Experiment 1a we measured literal semantics
+for `liked/loved'. In Experiment 3a,b we extended this group to
+`textit\{hated/disliked/liked/loved'. In Experiment 4 we extended this
+grou to `hated/disliked/felt indifferent
+about/liked/loved'.\}\label{fig:allScalesTable}
+\textbackslash{}end\{figure\} \textbackslash{}end\{CodeChunk\}
+
 \section{Acknowledgements}\label{acknowledgements}
 
-Thanks to NSF BCS \#XYZ. Thanks to Michael Franke, Judith Degen, and
-Noah Goodman.
+Thanks to NSF BCS XYZ. Thanks to Michael Franke, Judith Degen, and Noah
+Goodman.
 
@@
 
+use a food review paradigm in which `meaning' for a given scalar item
+was quantified as a distribution over star-ratings. Quantifying both
+literal semantic content and pragmatic judgments as distributions over
+stars provides an important interface to our model, especially for
+scalar items with ambigous literal semantics (e.g.~items such as
+``liked/loved'' or ``memorable/unforgettable''). In addition to
+quantifying literal semantics and pragmatic judgments in Experiments
+1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
+based on van Tiel (2013, Experiment 2???), to generate a set of
+plausible alternatives to the scalar items used in Experiments 1a,b. We
+extend the set of alternatives measured in Experiments 3a,b and 4 using
+data from Experimeng 2. Additionally, by looking at the relative
+frequencies of alternatives generated in Experiment 2 we were able to
+compute a saliency measure for each alternative. Using the literal
+semantic data from Experiments 1a, 3a and 4, we modeled pragmatic
+enrichment using RSA and compared model predictions to human judgments
+obtained in Experiments 1b and 3b. Model performance was significantly
+improved with the incorporation of alternatives. This result suggests
+that more ``fully specified" scale representations may be active for
+human participants while making pragmatic judgments for scalar items.
+
 \end{document}

### 2016-01-21 analysis/e12_analysis.Rmd
fixed compliance check

---
output: pdf_document
---

Experiment e12 - Pragmatic Listener experiment with alternatives
```{r}
rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")
library(ggplot2)
# commentary on weird RMarkdown bug
# https://github.com/hadley/xml2/issues/34
```

Data prep
---------
```{r}

# make sure to set directory path to 'production-results/e11/'
results_path = "production-results/e12/"
files <- dir(results_path, pattern = "*.json")
d.raw <- data.frame()

for (f in files) {
  jf <- paste(results_path,f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- data.frame(workerid = jd$WorkerId, 
                   scale = jd$answers$data$scale,
                   degree = jd$answers$data$degree,
                   stars = jd$answers$data$manipulation_level,
                   judgment = as.numeric(jd$answers$data$judgment),
                   language = jd$answers$data$language,
                   gender = jd$answers$data$gender,
                   age = jd$answers$data$age)
  d.raw <- bind_rows(d.raw, id)
}

# Number of participants
length(unique(d.raw$workerid))
```

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
# Make sure people answered training trials correctly
compliant <- d.raw %>% 
   filter(grepl("training", scale)) %>%
   group_by(workerid) %>%
   summarise(compliant = judgment[scale == "training1" & degree == "hi2"] == 1 & 
               judgment[scale == "training1" & degree == "low1"]== 1)

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1", 
         scale != "training2", 
         compliant == TRUE)

# remove training runs
d <- d.raw %>% filter(scale != "training1")
head(d)
length(unique(d$workerid))
```

Main analysis below
-------------------

Let's remove training runs
```{r}
#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
#d = d.raw %>% filter(scale != "training1")
```

Populate a new df
```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment),
            speaker.p = mean(judgment))
```

Write to csv
```{r}
# write.csv(ms, "models/model_data/L0_e12.csv", row.names=FALSE)
```

Plot our literal listener semantic (counts data)
```{r}
pdf("plots/e12_L0Counts.pdf", width=8, height = 5)
qplot(x = stars, y = cnt.judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = cnt.judgment - cil, 
                     ymax = cnt.judgment + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener counts")
dev.off()

pdf("plots/e12_L0Percent.pdf", width=8, height = 5)
qplot(x = stars, y = speaker.p, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = speaker.p - cil, 
                     ymax = speaker.p + cih)) + 
  facet_wrap(~scale) +
  ggtitle("Literal listener percent 'yes'")
dev.off()
```

```{r}

```

```{r}
# prop.calc = function(scalar, degree, stars, df) {
#   total = sum(df[(df$scale == scalar) & (df$degree == degree), "cnt.judgment"])
#   prop = df[(df$scale == scalar) & (df$degree == degree) & (df$stars = stars), "cnt.judgment"]
#   return(prop / total)
# }
# scales = rep("some_all", 5)
# stars = seq(1:5)
# degree = rep("hi1", 5)
# cnt.judgment = c(0, 0, 0, 2, 28)
# 
# df = data.frame(scales, stars, degree, cnt.judgment)
# prop.calc("some_all", "hi1", 1, df)
# 
# ms$judgment.prop = ms$judgment
# # write to csv for model
# #write.csv(ms, "models/e10.csv", row.names=FALSE)
```

### 2016-01-21 Paper/Paper.Rmd
Added final model fit plot

@@
 listenerE11 <- read.csv(paste(path, "model_data/L1_e11.csv", sep = ""), stringsAsFactors = FALSE)
-```
-
-```{r}
-speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
-                      speakerE10 %>% mutate(expt = "3a"), 
-                      speakerE8 %>% mutate(expt = "1a"))
-# ggplot(speakers, 
-#        aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
-#   geom_line() + 
-#   facet_grid(.~ scale) + 
-#   theme_bw()
 ```
@@
 
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions (1a) and pragmatic judgments (1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L0}(m|u)$ (Exerpiment 1a) and pragmatic judgments $p_{L1}(m|u)$ (Experiment 1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
 Each pair consists of a "weaker" scalar term (e.g.
@@
 We are calling these "entialment scales"", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.
+The grey colored items in Table 1 denote the original "entailment" items used in Experiments 1a,b.
 
@@
 Thirty participants were recruited for Experiment 1a.
-Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Data for two participants was thrown out during analysis because there were not native English speakers, leaving a total sample of 28 participants.
 Fifty participants were recruited for experiment 1b.
-Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Data for 7 participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 43 participants.
 
@@
 Participants were presented with a target scalar item and a star-rating (between 1-5 stars) and asked to judge the compatibility of the scalar item and star-rating.
-Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person \___ed the food?" where a target scalar was presented in the "\___ed." Each participant was presented all scalar item and star-rating combinations with randomization.
+Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the "\____." Each participant was presented all scalar item and star-rating combinations with randomization.
 
 The right panel of Figure 1 shows a screen shot of a trial from Experiment 1b.
-On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they \___ed the food." They were then asked to generate a star-rating according to what they think the reviewer likely gave.
+On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star-rating according to what they thought the reviewer likely gave.
 Each participant was presented all scalar items with randomization.
@@
 ## Results and Discussion
+Figure 2 plots literal listner $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
+Data from 1a is (...).
+We see clear variation between semantic judgments between scalar families in all the Experiments.
+For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved".
+We will address distributional similarity across the studies in later sections.
 
-The left panel of figure two shows literal semantics for each of the scalar terms "liked" and "loved" as distributions over star-ratings.
-
-Chi-squared test? Null results, not really important here anyway...
 ```{r}
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'.
 The y-axis is the percentage of \'yes\' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\\% of respondents beleived that \'liked\' was compatible with both 4 and 5 stars).
@@
 
-plotData <- speakerE8 %>%
-  mutate(degree = ifelse(degree == "hi", "loved", "liked"))
+speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
+                      speakerE10 %>% mutate(expt = "3a"), 
+                      speakerE8 %>% mutate(expt = "1a"))
 
-# Literal listener: Entailment (e8)
-e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
+ggplot(speakers, 
+       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
   geom_line() + 
-  ylab("Percent yes") +
-  geom_linerange(aes(ymin = speaker.p - cil, 
-                     ymax = speaker.p + cih)) +
-  ggtitle("Literal semantics")
+  facet_grid(.~ scale) + 
+  theme_bw()
 
-# Pragmatic listener: Entailment (e6)
-plotData <- listenerE6 %>%
-  mutate(degree = ifelse(degree == "hi", "loved", "liked"))
-e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
-                 aes(x = stars, y = listener.p, fill = degree)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  facet_wrap(~degree) +
-  ylab("Proportion of star-ratings chosen") +
-  ggtitle("Pragmatic judgments") +
-  theme(legend.position="none")
-
-gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
+####################################
+# OLD PLOTS -------------------------
+# plotData <- speakerE8 %>%
+#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
+# # Literal listener: Entailment (e8)
+# e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
+#   geom_line() +
+#   ylab("Percent yes") +
+#   geom_linerange(aes(ymin = speaker.p - cil, 
+#                      ymax = speaker.p + cih)) +
+#   ggtitle("Literal semantics")
+# 
+# # Pragmatic listener: Entailment (e6)
+# plotData <- listenerE6 %>%
+#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
+# e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
+#                  aes(x = stars, y = listener.p, fill = degree)) +
+#   geom_bar(stat = "identity", position = "dodge") +
+#   facet_wrap(~degree) +
+#   ylab("Proportion of star-ratings chosen") +
+#   ggtitle("Pragmatic judgments") +
+#   theme(legend.position="none")
+# gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
 ```
@@
 
-In Experiment 2 we asked participants to generate plausible alternatives for the scalar items presented in Experiment 1.
+In Experiment 1 we obtained literal semantic compatibility and pragmatic judgments for five pairs of scalar terms.
+We would like to extend the scale descriptions for each of these pairs to include other plausible alternatives.
+We chose to take an empirical approach rather than assign alternatives arbitrarily.
+We adopted a modified cloze task, inspired by Experiment 2 in van Tiel (2014) and asked participants to generate alternatives for us.
 
@@
 
-Using Amazon's Mechanical Turk, N workers were paid $0.20 to participate.
-n workers were dropped from the analysis because they either failed to pass training trials or were not native English speakers.
-The final sample was N workers, all of whom  were naive to the purpose of the experiment.
+Using Amazon's Mechanical Turk, 30 workers were paid $0.20 to participate. All participants were native English speakers and naive to the purpose of the experiment.
 
 ### Design and procedure
-Participants were presented a target scalar term embedded in a sentence such as, "In a recent restaurant review someone said they thought they *----*ed the food." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of *----*?" and asked to generate three alternatives.
+Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____" with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" and asked to generate three unique alternatives.
 
@@
 Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g..
-"good/excellent", "memorable/unforgettable") were similarly long-tailed.
-In Experiments 3a,b we took the top two alternatives generated for each scalar item to enrich the entailment only scales from Experiments 1a,b.
-In experiment 4 we further enriched the scales from Experiments 3a,b with a neutral valence scalar chosen from the alternative sets.
+"good/excellent", "memorable/unforgettable") were similarly long-tailed, however the size and content of the alternate sets were diverse.
+(SOMETHING MORE MORE FORMAL HERE???)
 
@@
 
-Experiment 3a,b are identical to Experiments 1a,b except the set of target scalar was expanded to include the top two alternatives generated for each scalar family.
+In Exerpiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales.
+In Exerpiment 2, we asked participants to generate plausible alternatives to these items.
+In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to inlclude the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2.
 The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.
@@
 Thirty participants were recruited for Experiment 3a (Literal Listener task).
-Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Data for six participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 24 participants.
 
 Fifty participants were recruited for Experiment 3b (Pragmatic Listener task).
-Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Data for five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
 
@@
 ## Results and Discussion
-Distributional differences.
+
+Run glmer() here:
+```{r}
+
+```
+To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject.
+Results indicate (...)
+
+Run elmer() here:
+```{r}
+
+```
+
+To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject.
+Results indicate.
+
+While conducting our analysis we realized that our literal semantic distributions for each scalar family was roughly split between two negative valenced items and two positively valenced items while more neutral alternatives appeared to be left out.
+(This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4 we explore the addition of a neutrally valenced scalar alternative for each scalar family.
 
 # Experiment 4: Symmetric scales
-Experiment 4a is identical to Experiments 1a and 3a except the set of target scalar was expanded to include a neutral valence scalar item for each scalar family.
+In Experiment 4, we continue to extend the alternative sets, each by one additional scalar item.
+While we simply took the top two alternatives generated in Experiment 2 for the additional alternatives in Experiments 3a,b, in this case we chose a subjectively "neutral" valenced scalar item from among the alternatives generated in Experiment 2.
+The idea was to simulate a "full" set of alternatievs with negative, neutral and positive valenced items.
 The purple colored items in Table 1 denote additional scalar items added in Experiments 4.
@@
 ## Participants
-
-Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
-Thirty participants were recruited for Experiment 4 (Literal Listener task).
-Data for N participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of N.
+Thirty participants were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
+There were no data exclusions due to training failures or native language requirements, leaving a total sample of thirty participants, all native English speakers, naive to the purpose of the experiment.
 
@@
 ## Results and Discussion
-Distributional differences.
+Distributions for neturally valenced scalar did appear fairly gaussian, occupying a literal semantic previously unoccupied by the other alternatives.
 
-# Temp section Model was here
+Run glmer() here:
+```{r}
 
-### Results
-Table here
+```
+To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject.
+Results indicate (...)
 
-Figure 4 plots model / human correlation for our three simulations. Alpha was tuned separately for each of these runs...
+Run elmer() here:
+```{r}
+
+```
+
+To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject.
+Results indicate.
+
+# Model Runs
+
+Using literal semantic data from Experiments 1a, 3a and 4 we conducted three simulations with our model.
+Each simulation used the specific literal semantic data to specify the scale representation avaiable to our model.
+The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014).
+These data were measured in Experiment 1a.
+The "mid" model used the extended the original set of alternatives with the top two alternatives generated in Experiment 2.
+These data were measured in Exerpiment 3a.
+The "full" model included the full set of alternatives, including a neutral valenced alternatives.
+These data were measured in Experiment 4.
+
 ```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
@@
 plotData <- allModelRunData %>%
-  mutate(study = ifelse(numAlts == 5, "Symmetric", 
-                        ifelse(numAlts == 4, "Neg_alts", "Entailment"))) %>%
+  mutate(study = ifelse(numAlts == 5, "Full", 
+                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
   gather(Experiment, cors, c(corE6, corE11)) %>%
@@
 # Correlation scatter plot
-symmetricCorPlot <- ggplot(subset(plotData, study == "Symmetric"), aes(x = listener.p, y = preds)) + 
+symmetricCorPlot <- ggplot(subset(plotData, study == "Top_two"), aes(x = listener.p, y = preds)) + 
   geom_point() +
@@
 
-corBarChart
+# corBarChart
+
+modifiedPlotData <- plotData %>%
+  gather(pragStudy, pragChoice, c(9,11))
+fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
+      data=subset(modifiedPlotData, study == "Full")) +
+  ylim(0, 1) +
+  facet_wrap(~scale) + 
+  geom_line(aes(y = preds), lty = 4)
+fullRepresentationFit
 # gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))

### 2016-01-21 Paper/Paper.tex
Added final model fit plot

@@
 Experiment 1a and 1b were conducted to approximate literal listener
-semantic distributions (1a) and pragmatic judgments (1b) for five pairs
-of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
-Each pair consists of a ``weaker'' scalar term (e.g. ``some'') and a
-stronger scalar term (e.g. ``all''). We are calling these ``entialment
+semantic distributions \(p_{L0}(m|u)\) (Exerpiment 1a) and pragmatic
+judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
+taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
+consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
+scalar term (e.g. ``all''). We are calling these ``entialment
 scales''``, because they encode the assumption that a listener need only
 have a the stronger alternative present to generate an enriched
-interpretation of the weaker term.
+interpretation of the weaker term. The grey colored items in Table 1
+denote the original''entailment" items used in Experiments 1a,b.
 
@@
 paid \$0.20 for their participation. Thirty participants were recruited
-for Experiment 1a. Data for N participants was thrown out after
-participants either failed to pass two training trials or were not
-native English speakers, leaving a total sample of N. Fifty participants
-were recruited for experiment 1b. Data for N participants was thrown out
-after participants either failed to pass two training trials or were not
-native English speakers, leaving a total sample of N.
+for Experiment 1a. Data for two participants was thrown out during
+analysis because there were not native English speakers, leaving a total
+sample of 28 participants. Fifty participants were recruited for
+experiment 1b. Data for 7 participants was thrown out after participants
+either failed to pass two training trials or were not native English
+speakers, leaving a total sample of 43 participants.
 
@@
 binary ``yes/no'' response to a question of the form ``Do you think that
-the person \_\_\_ed the food?" where a target scalar was presented in
-the ``\_\_\_ed." Each participant was presented all scalar item and
-star-rating combinations with randomization.
+the person thought the food was \_\_\_\_?" where a target scalar was
+presented in the ``\_\_\_\_." Each participant was presented all scalar
+item and star-rating combinations with randomization.
 
@@
 one-sentence prompt containing a target scalar item such as ``Someone
-said they \_\_\_ed the food." They were then asked to generate a
-star-rating according to what they think the reviewer likely gave. Each
-participant was presented all scalar items with randomization.
+said they thought the food was \_\_\_\_\_.'' Participants were then
+asked to generate a star-rating according to what they thought the
+reviewer likely gave. Each participant was presented all scalar items
+with randomization.
 
@@
 
-The left panel of figure two shows literal semantics for each of the
-scalar terms ``liked'' and ``loved'' as distributions over star-ratings.
-
-Chi-squared test? Null results, not really important here anyway\ldots{}
+Figure 2 plots literal listner \(p_{L0}(m|u)\) distributions obtained in
+Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
+variation between semantic judgments between scalar families in all the
+Experiments. For example, compatibility judgments for ``memorable'' and
+``forgettable'' are more similar than those for ``good / excellent'' or
+``liked / loved''. We will address distributional similarity across the
+studies in later sections.
 
@@
 
-In Experiment 2 we asked participants to generate plausible alternatives
-for the scalar items presented in Experiment 1.
+In Experiment 1 we obtained literal semantic compatibility and pragmatic
+judgments for five pairs of scalar terms. We would like to extend the
+scale descriptions for each of these pairs to include other plausible
+alternatives. We chose to take an empirical approach rather than assign
+alternatives arbitrarily. We adopted a modified cloze task, inspired by
+Experiment 2 in van Tiel (2014) and asked participants to generate
+alternatives for us.
 
@@
 
-Using Amazon's Mechanical Turk, N workers were paid \$0.20 to
-participate. n workers were dropped from the analysis because they
-either failed to pass training trials or were not native English
-speakers. The final sample was N workers, all of whom were naive to the
-purpose of the experiment.
+Using Amazon's Mechanical Turk, 30 workers were paid \$0.20 to
+participate. All participants were native English speakers and naive to
+the purpose of the experiment.
 
@@
 
-Participants were presented a target scalar term embedded in a sentence
-such as, ``In a recent restaurant review someone said they thought they
-\emph{----}ed the food.'' Participants were then asked to generate
-plausible alternatives by responding to the question, ``If they'd felt
-differently about the food, what other words could they have used
-instead of \emph{----}?'' and asked to generate three alternatives.
+Participants were presented a target scalar term from our original
+entailment set embedded in a sentence such as, ``In a recent restaurant
+review someone said they thought they the food was \_\_\_\_" with a
+target scalar presented in the ``\_\_\_\_." Participants were then asked
+to generate plausible alternatives by responding to the question, ``If
+they'd felt differently about the food, what other words could they have
+used instead of \_\_\_\_\_?'' and asked to generate three unique
+alternatives.
 
@@
 other scalar pairs (e.g.. ``good/excellent'',
-``memorable/unforgettable'') were similarly long-tailed. In Experiments
-3a,b we took the top two alternatives generated for each scalar item to
-enrich the entailment only scales from Experiments 1a,b. In experiment 4
-we further enriched the scales from Experiments 3a,b with a neutral
-valence scalar chosen from the alternative sets.
+``memorable/unforgettable'') were similarly long-tailed, however the
+size and content of the alternate sets were diverse. (SOMETHING MORE
+MORE FORMAL HERE???)
 
@@
 
-Experiment 3a,b are identical to Experiments 1a,b except the set of
-target scalar was expanded to include the top two alternatives generated
-for each scalar family. The orange colored items in table 1 denote
-additional scalar items added in Experiments 3a,b.
+In Exerpiment 1a,b we measured literal semantics and pragmatic judgments
+for Entailment scales. In Exerpiment 2, we asked participants to
+generate plausible alternatives to these items. In Experiments 3a,b we
+use the same experimental design for both literal semantics and
+pragmatic judgment tasks, however we now expand the set of scalar items
+to inlclude the original Entailment pairs from Experiments 1a,b with the
+top two alternatives generated for each scalar family by participants in
+Experiment 2. The orange colored items in table 1 denote additional
+scalar items added in Experiments 3a,b.
 
@@
 and paid \$0.20 for their participation. Thirty participants were
-recruited for Experiment 3a (Literal Listener task). Data for N
+recruited for Experiment 3a (Literal Listener task). Data for six
 participants was thrown out after participants either failed to pass two
 training trials or were not native English speakers, leaving a total
-sample of N.
+sample of 24 participants.
 
 Fifty participants were recruited for Experiment 3b (Pragmatic Listener
-task). Data for N participants was thrown out after participants either
-failed to pass two training trials or were not native English speakers,
-leaving a total sample of N.
+task). Data for five participants was thrown out after participants
+either failed to pass two training trials or were not native English
+speakers, leaving a total sample of 45 participants.
 
@@
 
-Distributional differences.
+Run glmer() here:
+
+To test whether literal listener compatibility judgments differed
+between Experiment 1a and 3a we ran a mixed effects model, regressing
+responses to the binary compatibility measure on scale, degree, and
+Experiment with random effects by subject. Results indicate (\ldots{})
+
+Run elmer() here:
+
+To test whether pragmatic judgments differed between Experiments 1b and
+3b we ran a mixed effects model, regressing star-rating selections on
+scale, scalar item and Exerpiment with random effects by subject.
+Results indicate.
+
+While conducting our analysis we realized that our literal semantic
+distributions for each scalar family was roughly split between two
+negative valenced items and two positively valenced items while more
+neutral alternatives appeared to be left out. (This pattern was true of
+all the scalar families, except for ``some ~all'' in which the top two
+alternatives were positive valenced ``most'' and negative valenced
+``none''.) In Experiment 4 we explore the addition of a neutrally
+valenced scalar alternative for each scalar family.
 
@@
 
-Experiment 4a is identical to Experiments 1a and 3a except the set of
-target scalar was expanded to include a neutral valence scalar item for
-each scalar family. The purple colored items in Table 1 denote
+In Experiment 4, we continue to extend the alternative sets, each by one
+additional scalar item. While we simply took the top two alternatives
+generated in Experiment 2 for the additional alternatives in Experiments
+3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
+item from among the alternatives generated in Experiment 2. The idea was
+to simulate a ``full'' set of alternatievs with negative, neutral and
+positive valenced items. The purple colored items in Table 1 denote
 additional scalar items added in Experiments 4.
@@
 
-Participants for both studies were recruited on Amazon Mechanical Turk
-and paid \$0.20 for their participation. Thirty participants were
-recruited for Experiment 4 (Literal Listener task). Data for N
-participants was thrown out after participants either failed to pass two
-training trials or were not native English speakers, leaving a total
-sample of N.
+Thirty participants were recruited on Amazon Mechanical Turk and paid
+\$0.20 for their participation. There were no data exclusions due to
+training failures or native language requirements, leaving a total
+sample of thirty participants, all native English speakers, naive to the
+purpose of the experiment.
 
@@
 
-Distributional differences.
+Distributions for neturally valenced scalar did appear fairly gaussian,
+occupying a literal semantic previously unoccupied by the other
+alternatives.
 
-\section{Temp section Model was here}\label{temp-section-model-was-here}
+Run glmer() here:
 
-\subsubsection{Results}\label{results}
+To test whether literal listener compatibility judgments differed
+between Experiment 1a and 3a we ran a mixed effects model, regressing
+responses to the binary compatibility measure on scale, degree, and
+Experiment with random effects by subject. Results indicate (\ldots{})
 
-Table here
+Run elmer() here:
 
-Figure 4 plots model / human correlation for our three simulations.
-Alpha was tuned separately for each of these runs\ldots{}
+To test whether pragmatic judgments differed between Experiments 1b and
+3b we ran a mixed effects model, regressing star-rating selections on
+scale, scalar item and Exerpiment with random effects by subject.
+Results indicate.
+
+\section{Model Runs}\label{model-runs}
+
+Using literal semantic data from Experiments 1a, 3a and 4 we conducted
+three simulations with our model. Each simulation used the specific
+literal semantic data to specify the scale representation avaiable to
+our model. The ``entailment'' model used only the original pair of
+scalar items pulled from van Tiel (2014). These data were measured in
+Experiment 1a. The ``mid'' model used the extended the original set of
+alternatives with the top two alternatives generated in Experiment 2.
+These data were measured in Exerpiment 3a. The ``full'' model included
+the full set of alternatives, including a neutral valenced alternatives.
+These data were measured in Experiment 4.
 

### 2016-01-21 Paper/Paper.Rmd
minor tweaks before sharing with mike 1.12

@@
 "Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." Empirical evidence for the presence of such alternatives and accounts of their effect on implicature has been limited.
-Our current work explores the role different scale representations may play in scalar implicature using emperical measures of literal semantics and a Bayesian model of implicature generation.
+Our current work explores the role different scale representations may play in scalar implicature using empirical measures of literal semantics and a Bayesian model of implicature generation.
 Comparisons with human judgments indicate that pragmatic inference may rely on fairly complete alternative sets rather than the typical entialment only scales assumed in most research to date.
@@
 "Scalar implicature" is a hallmark of such pragmatic enrichment.
-For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies" (van Tiel, 2014).
+For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies" (van Tiel, 2014; other...).
 A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
@@
 This finding points to the impact a particular alternative set can have on judgments regarding scalar appropriateness.
-Using a fundamentally differnt approach, Franke (2014) formalized the Gricean account of implicature using a Bayesian model, modeling graded typicality judgments and scalar implicature.
+Using a fundamentally different approach, Franke (2014) formalized the Gricean account of implicature using a Bayesian model, modeling graded typicality judgments and scalar implicature.
 Results supported 'none', 'one' and 'all' as the most serious (salient) alternatives to "some."
@@
 Taken together, each of the previous studies signal the importance of scale representation (set of available alternatives) in scalar implicature.
-However, like many recent investigations which have focused only on a small subset of scalar items, both Degen & Tanehaus (2014) and Franke (2014) focus exclusively on the scalar family "some/all." This lack "Scalar Diversity" (van Tiel, 2014) makes generalization across different scalar families problematic.
-van Tiel (2014), found substantial variation in the rate of upper-bounded construals among over 40 different scalar pairs.
+However, like many recent investigations which have focused only on a small subset of scalar items, both Degen & Tanenhaus (2014) and Franke (2014) focus exclusively on the scalar family "some/all." This lack "Scalar Diversity" (van Tiel, 2014) makes generalization across different scalar families problematic.
+van Tiel (2014), found substantial variation in the rate of upper-bounded construals aross more than 40 different scalar pairs.
 This finding suggests that implicature may differ widely between different scales.
@@
 
-Consider a scalar item other than "some" -  in the context of a scalar item such as "good", the idea of set of lexical alternatives certainly xfeels intuitive ("bad", "excellent", etc.).
+Consider a scalar item other than "some" -  in the context of the word "good", the idea of set of lexical alternatives seems intuitive ("bad", "excellent", etc.).
 But measuring the extent to which these alternatives are salient is not so clear.
-Nor is how to measure their impact on pragmatic intepretations of the scalar item "good." In an experimental setting, querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the query.
-In the spirit of Franke (2014) and Degen & Tanenhaus (2014), we pair a computational model of implicature with empirical measurments of linguistic material.
+Nor is how to measure their impact on pragmatic interpretations of the scalar item "good." In an experimental setting, querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the query.
+In the spirit of Franke (2014) and Degen & Tanenhaus (2014), we pair a computational model of implicature with empirical measurements of linguistic material.
 This combination allows us to simulate the effect of various scale representations on implicature.
@@
 
-Bayesian models of pragmatic enrichment have accurately predicted human judgments in ad-hoc (Frank & Goodman, 2012) and embedded (Stulhumuller & Goodman, 2014) implicature settings.
+Bayesian models of pragmatic enrichment have accurately predicted human judgments in ad-hoc (Frank & Goodman, 2012) and embedded (Stulhmuller & Goodman, 2014) implicature settings.
 Our current model follows both these studies and is based on Rational Speech-act theory (RSA).
-RSA frames language understanding as a special case of social cognition (Stulhumuller & Goodman, 2014), in which listeners and speakers reason about one-another.
-In this framework, a listener uses Bayesiain inference to interpret the intended meaning $m$ of a speaker who has made an utterance $u$.
+RSA frames language understanding as a special case of social cognition (Frank & Goodman, 2012; Stulhmuller & Goodman, 2014), in which listeners and speakers reason about one-another.
+In this framework, a listener uses Bayesian inference to interpret the intended meaning $m$ of a speaker who has made an utterance $u$.
 We will make the model specifications explicit later in the paper.
@@
 Finally, we simulate the impact of three different scale representations, "entailment", "mid" and "symmetric" on implicature generation, comparing model predictions with pragmatic judgments captured empirically.
-Results indicate that humans may employ more "fully specified" scale representatinos, relying on the presence of multiple alternatives during pragmatic enrichment.
+Results indicate that humans may employ more "fully specified" scale representations, relying on the presence of multiple alternatives during pragmatic enrichment.
 
@@
 Our model assumes that speakers choose words to maximize the utility of an utterance in context.
-Utility is operationalized as the informativity of a particular utterance (suprisal) minus a cost.
+Utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost.
 In particular, the speaker chooses an utterance in order to maximize the utility of a listener who interprets her utterance literally $p_{L0}(m|u)$.
-$L_0$ denotes a literal listener interpretation.
+$L_0$ denotes a literal listener interpretation of meaning $m$ given utterance $u$.
 $$p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}$$
 
-The **posterior** $\mathbf{p_{L1}(m | u)}$ quantifies a listener's pragmatic enrichment of an utterance $u$ as degree of belief that $m$ is the intended meaning of the speaker, given an utterance $u$.
-$L_1$ denotes a pragmatic listener interpration.
+The **posterior** $\mathbf{p_{L1}(m | u)}$ quantifies a listener's degree of belief that a speaker intended a meaning $m$ given an utterance $u$.
+The subscript $L_1$ denotes a pragmatic listener interpretation of meaning $m$ given utterance $u$.
 
-## Populating the model: Measuring literal semantics and pragmatic judgments
+## Simluating implicature: Measuring literal semantics and pragmatic judgments
 In order to simulate the role of scale representation on implicature we pair a computational framework with empirical data.
 In particular we use experimental tools to populate three components of the model.
-First, to measure otherwise ambigous literal semantics $\mathbf{p_{L0}(m|u)}$ (our "Scalar Diversity"" approach).
+First, to measure otherwise ambiguous literal semantics $\mathbf{p_{L0}(m|u)}$ (our "Scalar Diversity"" approach).
 Second, to generate a set of plausible alternatives to the original scalar pairs taken from van Tiel (2014).
@@
 
-$$\text{\textit{some of the A's are B's.}}$$
+$$\text{\text it{some of the A's are B's.}}$$
 $$[[some]] = \{<A, B> : |A \cap B| \geq 1 \}$$
 
-$$\text{\textit{all of the A's are B's.}}$$
+$$\text{\text it{all of the A's are B's.}}$$
 $$[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}$$
@@
 In the following set of studies we adopt a food-review paradigm to measure literal semantics and pragmatic judgments empirically.
-In order to capture graded typicality judgments as in Degen & Tanenhaus (2014) we use a compatiblity measure dependent variable, pairing scalar items with star-ratings in our literal listener task (Experiments 1a, 3a and 4).
+In order to capture graded typicality judgments as in Degen & Tanenhaus (2014) we use a compatibility measure dependent variable, pairing scalar items with star-ratings in our literal listener task (Experiments 1a, 3a and 4).
 Data from these experiments is used to approximate the literal listener semantics for a given scalar item $u$ as a distribution over star-ratings $m \in \text{\{1 - 5 stars\}}$.
 Similarly, pragmatic judgment data from Experiments 1b and 3b serve as our primary points of comparison with model predictions $\mathbf{p_{L1}(m|u)}$, again quantifying judgments as distributions over star-ratings.
-In the following section we take the read through our experiments.
+In the following section we take the reader through our experiments.
 
@@
 
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L0}(m|u)$ (Exerpiment 1a) and pragmatic judgments $p_{L1}(m|u)$ (Experiment 1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L0}(m|u)$ (Experiment 1a) and pragmatic judgments $p_{L1}(m|u)$ (Experiment 1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
 Each pair consists of a "weaker" scalar term (e.g.
@@
 "all").
-We are calling these "entialment scales"", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.
+We are calling these "entailment scales", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.
 The grey colored items in Table 1 denote the original "entailment" items used in Experiments 1a,b.
@@
 Thirty participants were recruited for Experiment 1a.
-Data for two participants was thrown out during analysis because there were not native English speakers, leaving a total sample of 28 participants.
-Fifty participants were recruited for experiment 1b.
+Data for two participants was thrown out during analysis because they were not native English speakers, leaving a total sample of 28 participants.
+Fifty participants were recruited for Experiment 1b.
 Data for 7 participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 43 participants.
@@
 ## Results and Discussion
-Figure 2 plots literal listner $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
+Figure 2 plots literal listener $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
 Data from 1a is (...).
-We see clear variation between semantic judgments between scalar families in all the Experiments.
+We see clear variation in semantic judgments between scalar families in all Experiments.
 For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved".
@@
 
-In Exerpiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales.
-In Exerpiment 2, we asked participants to generate plausible alternatives to these items.
-In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to inlclude the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2.
+In Experiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales.
+In Experiment 2, we asked participants to generate plausible alternatives to these items.
+In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to include the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2.
 The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.
@@
 
-To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject.
+To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject.
 Results indicate.
 
-While conducting our analysis we realized that our literal semantic distributions for each scalar family was roughly split between two negative valenced items and two positively valenced items while more neutral alternatives appeared to be left out.
-(This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4 we explore the addition of a neutrally valenced scalar alternative for each scalar family.
+While conducting our analysis we realized that our literal semantic distributions for each scalar family were roughly split between two negative valenced items and two positively valenced items while neutral alternatives appeared to be excluded.
+(This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4, we explore the addition of a neutrally valenced scalar alternative for each scalar family.
 
-# Experiment 4: Symmetric scales
+# Experiment 4: Full scales - adding a neutral alternative
 In Experiment 4, we continue to extend the alternative sets, each by one additional scalar item.
 While we simply took the top two alternatives generated in Experiment 2 for the additional alternatives in Experiments 3a,b, in this case we chose a subjectively "neutral" valenced scalar item from among the alternatives generated in Experiment 2.
-The idea was to simulate a "full" set of alternatievs with negative, neutral and positive valenced items.
+The idea was to simulate a "full" set of alternatives, with negative, neutral and positive valenced items for each scalar family.
 The purple colored items in Table 1 denote additional scalar items added in Experiments 4.
@@
 ## Results and Discussion
-Distributions for neturally valenced scalar did appear fairly gaussian, occupying a literal semantic previously unoccupied by the other alternatives.
+Distributions for neutrally valenced scalar did appear fairly Gaussian, occupying a literal semantic previously unoccupied by the other alternatives.
 
@@
 
-To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Exerpiment with random effects by subject.
+To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject.
 Results indicate.
@@
 Using literal semantic data from Experiments 1a, 3a and 4 we conducted three simulations with our model.
-Each simulation used the specific literal semantic data to specify the scale representation avaiable to our model.
+Each simulation used the specific literal semantic data to specify the scale representation available to our model.
 The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014).
 These data were measured in Experiment 1a.
-The "mid" model used the extended the original set of alternatives with the top two alternatives generated in Experiment 2.
-These data were measured in Exerpiment 3a.
-The "full" model included the full set of alternatives, including a neutral valenced alternatives.
+The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2.
+These data were measured in Experiment 3a.
+The "Full" model included the full set of alternatives, including a neutral valenced alternative.
 These data were measured in Experiment 4.
@@
 
+Ignore below this
+
 use a food review paradigm in which 'meaning' for a given scalar item was quantified as a distribution over star-ratings.
-Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambigous literal semantics (e.g.
+Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambiguous literal semantics (e.g.
 items such as "liked/loved" or "memorable/unforgettable").
 In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
-We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experimeng 2.
+We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experiment 2.
 Additionally, by looking at the relative frequencies of alternatives generated in Experiment 2 we were able to compute a saliency measure for each alternative.

### 2016-01-21 Paper/Paper.tex
minor tweaks before sharing with mike 1.12

@@
 the role different scale representations may play in scalar implicature
-using emperical measures of literal semantics and a Bayesian model of
+using empirical measures of literal semantics and a Bayesian model of
 implicature generation. Comparisons with human judgments indicate that
@@
 ``some'' to ``some, but not all'' in sentences like ``Bob ate some of
-the cookies'' (van Tiel, 2014). A Gricean account of this phenomena
-assumes listeners reason about the intended meaning of a speaker while
-incorporating knowledge about a) alternative scalar items a speaker
-could have used (such as ``all'') and b) the relative informativity of
-using such alternatives (Grice, 1975). Under the Gricean account, a
-listener will infer that the speaker must have intended that Bob did not
-eat ``all'' the cookies because it would have been
-\emph{underinformative} for the speaker to use ``some'' when ``all''
-could have been used.
+the cookies'' (van Tiel, 2014; other\ldots{}). A Gricean account of this
+phenomena assumes listeners reason about the intended meaning of a
+speaker while incorporating knowledge about a) alternative scalar items
+a speaker could have used (such as ``all'') and b) the relative
+informativity of using such alternatives (Grice, 1975). Under the
+Gricean account, a listener will infer that the speaker must have
+intended that Bob did not eat ``all'' the cookies because it would have
+been \emph{underinformative} for the speaker to use ``some'' when
+``all'' could have been used.
 
@@
 impact a particular alternative set can have on judgments regarding
-scalar appropriateness. Using a fundamentally differnt approach, Franke
+scalar appropriateness. Using a fundamentally different approach, Franke
 (2014) formalized the Gricean account of implicature using a Bayesian
@@
 implicature. However, like many recent investigations which have focused
-only on a small subset of scalar items, both Degen \& Tanehaus (2014)
+only on a small subset of scalar items, both Degen \& Tanenhaus (2014)
 and Franke (2014) focus exclusively on the scalar family ``some/all.''
@@
 across different scalar families problematic. van Tiel (2014), found
-substantial variation in the rate of upper-bounded construals among over
-40 different scalar pairs. This finding suggests that implicature may
-differ widely between different scales. We adopt a ``Scalar Diversity''
-approach in our experimental design in order to extend our investigation
-beyond ``some/all'' scalar items. In the following set of studies we
-examine implicature for ``some/all'' and five additional scalar families
-from a range of grammatical classes (see Figure 5 for a complete set of
-scalar items used). The set of scalar items for this study were chosen
-from among the 40 used in van Tiel (2014).
+substantial variation in the rate of upper-bounded construals aross more
+than 40 different scalar pairs. This finding suggests that implicature
+may differ widely between different scales. We adopt a ``Scalar
+Diversity'' approach in our experimental design in order to extend our
+investigation beyond ``some/all'' scalar items. In the following set of
+studies we examine implicature for ``some/all'' and five additional
+scalar families from a range of grammatical classes (see Figure 5 for a
+complete set of scalar items used). The set of scalar items for this
+study were chosen from among the 40 used in van Tiel (2014).
 
-Consider a scalar item other than ``some'' - in the context of a scalar
-item such as ``good'', the idea of set of lexical alternatives certainly
-xfeels intuitive (``bad'', ``excellent'', etc.). But measuring the
-extent to which these alternatives are salient is not so clear. Nor is
-how to measure their impact on pragmatic intepretations of the scalar
-item ``good.'' In an experimental setting, querying a participant about
-the saliency of a particular alternative is problematic because the
-alternative must be made salient during the query. In the spirit of
-Franke (2014) and Degen \& Tanenhaus (2014), we pair a computational
-model of implicature with empirical measurments of linguistic material.
-This combination allows us to simulate the effect of various scale
-representations on implicature. In particular, we adopt a Bayesian model
-of implicature and a food-review paradigm to empirically quantify
-literal semantics and pragmatic judgments for our scalar stimuli.
+Consider a scalar item other than ``some'' - in the context of the word
+``good'', the idea of set of lexical alternatives seems intuitive
+(``bad'', ``excellent'', etc.). But measuring the extent to which these
+alternatives are salient is not so clear. Nor is how to measure their
+impact on pragmatic interpretations of the scalar item ``good.'' In an
+experimental setting, querying a participant about the saliency of a
+particular alternative is problematic because the alternative must be
+made salient during the query. In the spirit of Franke (2014) and Degen
+\& Tanenhaus (2014), we pair a computational model of implicature with
+empirical measurements of linguistic material. This combination allows
+us to simulate the effect of various scale representations on
+implicature. In particular, we adopt a Bayesian model of implicature and
+a food-review paradigm to empirically quantify literal semantics and
+pragmatic judgments for our scalar stimuli.
 
 Bayesian models of pragmatic enrichment have accurately predicted human
-judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhumuller
+judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhmuller
 \& Goodman, 2014) implicature settings. Our current model follows both
@@
 frames language understanding as a special case of social cognition
-(Stulhumuller \& Goodman, 2014), in which listeners and speakers reason
-about one-another. In this framework, a listener uses Bayesiain
-inference to interpret the intended meaning \(m\) of a speaker who has
-made an utterance \(u\). We will make the model specifications explicit
-later in the paper.
+(Frank \& Goodman, 2012; Stulhmuller \& Goodman, 2014), in which
+listeners and speakers reason about one-another. In this framework, a
+listener uses Bayesian inference to interpret the intended meaning \(m\)
+of a speaker who has made an utterance \(u\). We will make the model
+specifications explicit later in the paper.
 
@@
 with pragmatic judgments captured empirically. Results indicate that
-humans may employ more ``fully specified'' scale representatinos,
+humans may employ more ``fully specified'' scale representations,
 relying on the presence of multiple alternatives during pragmatic
@@
 an utterance in context. Utility is operationalized as the informativity
-of a particular utterance (suprisal) minus a cost. In particular, the
+of a particular utterance (surprisal) minus a cost. In particular, the
 speaker chooses an utterance in order to maximize the utility of a
 listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
-denotes a literal listener interpretation.
+denotes a literal listener interpretation of meaning \(m\) given
+utterance \(u\).
 \[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]
@@
 The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
-listener's pragmatic enrichment of an utterance \(u\) as degree of
-belief that \(m\) is the intended meaning of the speaker, given an
-utterance \(u\). \(L_1\) denotes a pragmatic listener interpration.
+listener's degree of belief that a speaker intended a meaning \(m\)
+given an utterance \(u\). The subscript \(L_1\) denotes a pragmatic
+listener interpretation of meaning \(m\) given utterance \(u\).
 
-\subsection{Populating the model: Measuring literal semantics and
+\subsection{Simluating implicature: Measuring literal semantics and
 pragmatic
-judgments}\label{populating-the-model-measuring-literal-semantics-and-pragmatic-judgments}
+judgments}\label{simluating-implicature-measuring-literal-semantics-and-pragmatic-judgments}
 
@@
 experimental tools to populate three components of the model. First, to
-measure otherwise ambigous literal semantics \(\mathbf{p_{L0}(m|u)}\)
+measure otherwise ambiguous literal semantics \(\mathbf{p_{L0}(m|u)}\)
 (our ``Scalar Diversity''" approach). Second, to generate a set of
@@
 
-\[\text{\textit{some of the A's are B's.}}\]
+\[\text{\text it{some of the A's are B's.}}\]
 \[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]
 
-\[\text{\textit{all of the A's are B's.}}\]
+\[\text{\text it{all of the A's are B's.}}\]
 \[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]
@@
 to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
-we use a compatiblity measure dependent variable, pairing scalar items
+we use a compatibility measure dependent variable, pairing scalar items
 with star-ratings in our literal listener task (Experiments 1a, 3a and
@@
 quantifying judgments as distributions over star-ratings. In the
-following section we take the read through our experiments.
+following section we take the reader through our experiments.
 
@@
 Experiment 1a and 1b were conducted to approximate literal listener
-semantic distributions \(p_{L0}(m|u)\) (Exerpiment 1a) and pragmatic
+semantic distributions \(p_{L0}(m|u)\) (Experiment 1a) and pragmatic
 judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
@@
 consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
-scalar term (e.g. ``all''). We are calling these ``entialment
-scales''``, because they encode the assumption that a listener need only
-have a the stronger alternative present to generate an enriched
-interpretation of the weaker term. The grey colored items in Table 1
-denote the original''entailment" items used in Experiments 1a,b.
+scalar term (e.g. ``all''). We are calling these ``entailment scales'',
+because they encode the assumption that a listener need only have a the
+stronger alternative present to generate an enriched interpretation of
+the weaker term. The grey colored items in Table 1 denote the original
+``entailment'' items used in Experiments 1a,b.
 
@@
 for Experiment 1a. Data for two participants was thrown out during
-analysis because there were not native English speakers, leaving a total
+analysis because they were not native English speakers, leaving a total
 sample of 28 participants. Fifty participants were recruited for
-experiment 1b. Data for 7 participants was thrown out after participants
+Experiment 1b. Data for 7 participants was thrown out after participants
 either failed to pass two training trials or were not native English
@@
 
-Figure 2 plots literal listner \(p_{L0}(m|u)\) distributions obtained in
-Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
-variation between semantic judgments between scalar families in all the
+Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions obtained
+in Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
+variation in semantic judgments between scalar families in all
 Experiments. For example, compatibility judgments for ``memorable'' and
@@
 
-In Exerpiment 1a,b we measured literal semantics and pragmatic judgments
-for Entailment scales. In Exerpiment 2, we asked participants to
+In Experiment 1a,b we measured literal semantics and pragmatic judgments
+for Entailment scales. In Experiment 2, we asked participants to
 generate plausible alternatives to these items. In Experiments 3a,b we
@@
 pragmatic judgment tasks, however we now expand the set of scalar items
-to inlclude the original Entailment pairs from Experiments 1a,b with the
+to include the original Entailment pairs from Experiments 1a,b with the
 top two alternatives generated for each scalar family by participants in
@@
 3b we ran a mixed effects model, regressing star-rating selections on
-scale, scalar item and Exerpiment with random effects by subject.
+scale, scalar item and Experiment with random effects by subject.
 Results indicate.
@@
 While conducting our analysis we realized that our literal semantic
-distributions for each scalar family was roughly split between two
-negative valenced items and two positively valenced items while more
-neutral alternatives appeared to be left out. (This pattern was true of
-all the scalar families, except for ``some ~all'' in which the top two
+distributions for each scalar family were roughly split between two
+negative valenced items and two positively valenced items while neutral
+alternatives appeared to be excluded. (This pattern was true of all the
+scalar families, except for ``some ~all'' in which the top two
 alternatives were positive valenced ``most'' and negative valenced
-``none''.) In Experiment 4 we explore the addition of a neutrally
+``none''.) In Experiment 4, we explore the addition of a neutrally
 valenced scalar alternative for each scalar family.
 
-\section{Experiment 4: Symmetric
-scales}\label{experiment-4-symmetric-scales}
+\section{Experiment 4: Full scales - adding a neutral
+alternative}\label{experiment-4-full-scales---adding-a-neutral-alternative}
 
@@
 item from among the alternatives generated in Experiment 2. The idea was
-to simulate a ``full'' set of alternatievs with negative, neutral and
-positive valenced items. The purple colored items in Table 1 denote
-additional scalar items added in Experiments 4.
+to simulate a ``full'' set of alternatives, with negative, neutral and
+positive valenced items for each scalar family. The purple colored items
+in Table 1 denote additional scalar items added in Experiments 4.
 
@@
 
-Distributions for neturally valenced scalar did appear fairly gaussian,
+Distributions for neutrally valenced scalar did appear fairly Gaussian,
 occupying a literal semantic previously unoccupied by the other
@@
 three simulations with our model. Each simulation used the specific
-literal semantic data to specify the scale representation avaiable to
+literal semantic data to specify the scale representation available to
 our model. The ``entailment'' model used only the original pair of
 scalar items pulled from van Tiel (2014). These data were measured in
-Experiment 1a. The ``mid'' model used the extended the original set of
+Experiment 1a. The ``Top two'' model extended the original set of
 alternatives with the top two alternatives generated in Experiment 2.
-These data were measured in Exerpiment 3a. The ``full'' model included
-the full set of alternatives, including a neutral valenced alternatives.
+These data were measured in Experiment 3a. The ``Full'' model included
+the full set of alternatives, including a neutral valenced alternative.
 These data were measured in Experiment 4.
@@
 
+Ignore below this
+
 use a food review paradigm in which `meaning' for a given scalar item
@@
 stars provides an important interface to our model, especially for
-scalar items with ambigous literal semantics (e.g.~items such as
+scalar items with ambiguous literal semantics (e.g.~items such as
 ``liked/loved'' or ``memorable/unforgettable''). In addition to
@@
 extend the set of alternatives measured in Experiments 3a,b and 4 using
-data from Experimeng 2. Additionally, by looking at the relative
+data from Experiment 2. Additionally, by looking at the relative
 frequencies of alternatives generated in Experiment 2 we were able to

### 2016-01-23 Paper/Paper.Rmd
relative plots

@@
 knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=F, message=F, sanitize = T)
+                      echo=F, warning=F, cache=TRUE, message=F, sanitize = T)
 ```
@@
 ```{r helpers}
-path <- "~/Desktop/Projects/scalar_implicature/models/"
 normedVec <- function(vec) vec / sum(vec)
@@
 # ---------------------------
-alternativesData <- read.csv(paste(path, "model_data/e9_alternativeCounts.csv", sep = ""),
+alternativesData <- read.csv("../models/model_data/e9_alternativeCounts.csv",
                              stringsAsFactors = FALSE)
-allModelRunData <- read.csv(paste(path, "model_data/allModelRuns.csv", sep = ""),
+allModelRunData <- read.csv("../models/model_data/allModelRuns.csv",
                      stringsAsFactors = FALSE)
@@
 # ------------------------------------------
-speakerE12 <- read.csv(paste(path, "model_data/L0_e12.csv", sep  = ""), stringsAsFactors = FALSE)
-speakerE10 <- read.csv(paste(path, "model_data/L0_e10.csv", sep = ""), stringsAsFactors = FALSE)
-speakerE8 <- read.csv(paste(path, "model_data/L0_e8.csv", sep = ""), stringsAsFactors = FALSE)
+speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
+speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
+speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
 # Experiments E6, E11: Pragmatic listener
 # ---------------------------------------
-listenerE6 <- read.csv(paste(path, "model_data/L1_e6.csv", sep = ""), stringsAsFactors = FALSE)
-listenerE11 <- read.csv(paste(path, "model_data/L1_e11.csv", sep = ""), stringsAsFactors = FALSE)
+listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
+listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
 ```
@@
 # Screen shots of literal listener and pragmatic listener conditions
-grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/exp1_stimuli.png"))
+grid::grid.raster(png::readPNG("figs/exp1_stimuli.png"))
 ```
@@
 # Scale stimuli
-grid::grid.raster(png::readPNG("~/Desktop/Projects/scalar_implicature/Paper/figs/alternativeSets.png"))
+grid::grid.raster(png::readPNG("figs/alternativeSets.png"))
 ```

### 2016-01-24 Paper/Paper.Rmd
mcf pass 1

@@
 ---
-title: "The importance of alternatives in scalar implicature"
+title: "Determining the alternatives for scalar implicature"
 bibliography: library.bib
@@
 abstract: 
-
     Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
-For example, listeners routinely enrich the meaning of "some" to "some, but not all" when interpreting a sentence such as "Bob ate some of the cookies." A Gricean account of this phenomena assumes the presence of *salient alternatives* with varying degrees of informativity.
-"Some," in the example above, is enriched to "some, but not all" in the presence of the stronger alternative "all." Empirical evidence for the presence of such alternatives and accounts of their effect on implicature has been limited.
-Our current work explores the role different scale representations may play in scalar implicature using empirical measures of literal semantics and a Bayesian model of implicature generation.
-Comparisons with human judgments indicate that pragmatic inference may rely on fairly complete alternative sets rather than the typical entialment only scales assumed in most research to date.
+For example, when interpreting a sentence such as "Bob ate some of the cookies," listeners routinely infer that Bob did not eat all of them.
+A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
+We use a computational model of pragmatic inference to test out hypotheses about how well different sets of alternatives allow us to predict scalar implicature performance across a range of different scales.
+Our findings suggest that human comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.
 
@@
 library(grid)
+library(langcog)
 ```
@@
 #   theme_bw()
+# Humpty Dumpty Quote...
 ```
@@
 
-Humpty Dumpty Quote...
+Successful communication requires listeners to make pragmatic inferences that go beyond the literal semantic content of speakers' utterances.
+For example, listeners  commonly enrich the meaning of the scalar item "some" to "some but not all" in sentences like "Bob ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
+These inferences, called _scalar implicatures_, have been an important test case for understnading pragmatic inferences more generally.
+A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives [@grice1975].
+According to this account, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* for the speaker to use "some" when "all" could have been used.
 
-Successful communication regularly requires listeners to make inferences that go beyond the literal semantic content of a speaker's utterance.
-"Scalar implicature" is a hallmark of such pragmatic enrichment.
-For example, listeners routinely enrich the meaning of the scalar item "some" to "some, but not all" in sentences like "Bob ate some of the cookies" (van Tiel, 2014; other...).
-A Gricean account of this phenomena assumes listeners reason about the intended meaning of a speaker while incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives (Grice, 1975).
-Under the Gricean account, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* for the speaker to use "some" when "all" could have been used.
+But what are the alternatives that should be considered in this computation more generally?
+Under classic accounts of implicature, listeners consider only those words whose meaning would entail the word that is actually sent [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000].
+For example, because "all" entails "some," and hence is a "stronger" meaning, "all" should be considered as an alternative to "some" in implicatures.
+Similar scales exist for non-quantifier scales, e.g.
+"love" entails "like" (and hence "I liked the movie" implicates that I didn't love it).
 
-The presence of ``salient" alternatives is critical to the standard Gricean account of scalar implicature (Grice, 1975).
-Recent experimental evidence appears to support this.
-Using a gumball paradigm, Degen & Tanenhaus (2014) demonstrated that the scalar item *some* was judged less appropriate (natural) for small sets of items when exact numbers were seen as viable alternatives.
-This finding points to the impact a particular alternative set can have on judgments regarding scalar appropriateness.
-Using a fundamentally different approach, Franke (2014) formalized the Gricean account of implicature using a Bayesian model, modeling graded typicality judgments and scalar implicature.
-Results supported 'none', 'one' and 'all' as the most serious (salient) alternatives to "some."
+Recent empirical evidence has called into question whether entailment scales are all that is necessary for understanding scalar implicature.
+For example, @degen2015  demonstrated that the scalar item "some" was judged less appropriate when exact numbers were seen as viable alternatives.
+And in a different paradigm, @vantiel2014 found converging evidence that "some" was judged to be atypical for small quantities.
+These data provide indirect evidence about a broader set of alternatives: since "some" is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words "one" and "two") reduced the felicity of "some" via a pragmatic inference.
 
-Taken together, each of the previous studies signal the importance of scale representation (set of available alternatives) in scalar implicature.
-However, like many recent investigations which have focused only on a small subset of scalar items, both Degen & Tanenhaus (2014) and Franke (2014) focus exclusively on the scalar family "some/all." This lack "Scalar Diversity" (van Tiel, 2014) makes generalization across different scalar families problematic.
-van Tiel (2014), found substantial variation in the rate of upper-bounded construals aross more than 40 different scalar pairs.
-This finding suggests that implicature may differ widely between different scales.
-We adopt a "Scalar Diversity" approach in our experimental design in order to extend our investigation beyond "some/all" scalar items.
-In the following set of studies we examine implicature for "some/all" and five additional scalar families from a range of grammatical classes (see Figure 5 for a complete set of scalar items used).
-The set of scalar items for this study were chosen from among the 40 used in van Tiel (2014).
+By formalizing pragmatic reasoning, computational models can help provide more direct evidence about the role that alternatives play.
+The "rational speech act" model (RSA) is one recent framework for understanding inferences about meaning in context [@frank2012;@goodman2013].
+RSA models frame language understanding as a special case of social cognition, in which listeners and speakers reason recursively about one another's goals.
+In the case of scalar implicature, a listener makes a probabilistic inference about what the speaker's most likely communicative goal was, given that she picked the quantifier "some" rather than the stronger quantifier "all." In turn, the speaker reasons about what message would best convey her intended meaning to the listener, given that he is reasoning in this way.
+This recursion is grounded in a "literal" listener who reasons only according to the basic truth-functional semantics of the language.
 
-Consider a scalar item other than "some" -  in the context of the word "good", the idea of set of lexical alternatives seems intuitive ("bad", "excellent", etc.).
-But measuring the extent to which these alternatives are salient is not so clear.
-Nor is how to measure their impact on pragmatic interpretations of the scalar item "good." In an experimental setting, querying a participant about the saliency of a particular alternative is problematic because the alternative must be made salient during the query.
-In the spirit of Franke (2014) and Degen & Tanenhaus (2014), we pair a computational model of implicature with empirical measurements of linguistic material.
-This combination allows us to simulate the effect of various scale representations on implicature.
-In particular, we adopt a Bayesian model of implicature and a food-review paradigm to empirically quantify literal semantics and pragmatic judgments for our scalar stimuli.
+@franke2014 used an RSA-style model to assess what alternatives a speaker would need to consider in order to produce the typicality/felicity ratings reported by @degen2015 and @vantiel2014.
+In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions.
+Surprisingly, along with weighting "one" highly (a conclusion that was suppored by the empirical work),the best-fitting model assigned substantial weight to "none" as an alternative.
+This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g.
+"one" entails "some" even if it is not classically considered to be part of the scale scale).
 
-Bayesian models of pragmatic enrichment have accurately predicted human judgments in ad-hoc (Frank & Goodman, 2012) and embedded (Stulhmuller & Goodman, 2014) implicature settings.
-Our current model follows both these studies and is based on Rational Speech-act theory (RSA).
-RSA frames language understanding as a special case of social cognition (Frank & Goodman, 2012; Stulhmuller & Goodman, 2014), in which listeners and speakers reason about one-another.
-In this framework, a listener uses Bayesian inference to interpret the intended meaning $m$ of a speaker who has made an utterance $u$.
-We will make the model specifications explicit later in the paper.
+In our current work, we pick up where these previous studies left off,  considering the set of alternatives for implicature using the RSA model.
+To gain empirical traction on this issue, however, we broaden the set of scales we consider.
+Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g.
+"liked/loved," or "palatable/delicious.").
+Making use of some of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
 
-In the following study we investigate the role of scale representation on scalar implicature.
-To do so we combine a computational framework with empirical measurements to simulate the type of scale representations that might be available to a listener.
-In the following sections we outline the specifics of the model and the particular components for which we need to to make empirical measurements.
-We then outline a series of experiments meant to a) quantify literal semantics for otherwise ambiguous scalar items, b) measure pragmatic judgments and c) generate a set of plausible alternatives for our set of scalar pairs taken from van Tiel (2014).
-In particular, we adopt a food review paradigm throughout our empirical data gathering, quantifying linguistic meaning (both literal semantics and pragmatic judgments) as distributions over star ratings.
-Finally, we simulate the impact of three different scale representations, "entailment", "mid" and "symmetric" on implicature generation, comparing model predictions with pragmatic judgments captured empirically.
-Results indicate that humans may employ more "fully specified" scale representations, relying on the presence of multiple alternatives during pragmatic enrichment.
+We begin by presenting the computational framework we use throughout the paper.
+We next describe a series of experiments deisgned to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items.
+These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements.
+To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgements, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgements with high accuracy.
 
------
+# Modeling Implicature Using RSA
 
-# Modeling implicature: Rational Speech-act theory
-We adopt a Bayesian model of scalar implicature known as Rational Speech-act theory (RSA).
-In particular, RSA frames language understanding as a special case of social cognition (Frank & Goodman, 2012; Stuhmuller & Goodman, 2014) in which listener and speaker agents reason about one another.
-We focus on the problem of a listener inferring the meaning of a speaker's utterance.
-Let $u$ be an observed utterance made by our speaker with an intended meaning $m$.
-We assume that the listener has access to a space of possible meanings $M$ and some model relating meanings $m \in M$ to $u$.
+We begin by giving a brief presentation of the basic RSA model.
+This model simulates the judgements of a pragmatic listener who wants to infer a speaker's intended meaning $m$ from her utterance $u$.
+For simplicity, we present a version of this model in which there is only full recursion: that is, the pragmatic listener reasons about a pragmatic speaker, who in turn reasons about a "literal listener." We assume throughout that this computation takes place in a signaling game [@lewis1969] with a fixed set of possible meanings $m \in M$ and a fixed possible set of utterances $u \in U$, with both known to both participants.
+Our goal in this study is to determine what utterances fall in $U$.
 
-Upon hearing an utterance $u$ the Listener agent evaluates all candidate word meanings, computing their posterior probabilities $p_{L1}(m | u)$.
-This quantity is proportional to the product of the prior probability $p(m)$ of a particular meaning and the likelihood $p(u | m)$.
+In the standard RSA model, the pragmatic listener (denoted $L_1$), makes a Bayesian inference:
 
-$$p_{L1}(m | u) = \frac{p(u | m)p(m)}{p(u)}$$
-$$= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}$$
+$$p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)$$
 
-The **prior** $\mathbf{p(m)}$ represents the listener's expectations about plausible meanings (star ratings), *independent* of the utterance $u$.
-To avoid biasing the data we assume priors over meanings are uniform, however future investigations may want to experiment with different priors, either by inferring them or using empirical measures
+\noindent In other words, the probability of a particular meaning given an utterance is proportional to the speaker's proability of using that particular utterance to express that meaning, weighted by a prior over meanings.
+This prior represents the listener's _a priori_ expectations about plausible meanings, independent of the utterance.
+Because our experiments take place in a context in which listeners should have very little expectation about which meanings speakers want to convey, for simplicity we assume a uniform prior $p(m) \propto 1$.
 
-$\mathbf{p(u | m)}$ quantifies the **likelihood** that a speaker would make a particular utterance $u$ given an intended meaning $m$.
-Our model assumes that speakers choose words to maximize the utility of an utterance in context.
-Utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost.
-In particular, the speaker chooses an utterance in order to maximize the utility of a listener who interprets her utterance literally $p_{L0}(m|u)$.
-$L_0$ denotes a literal listener interpretation of meaning $m$ given utterance $u$.
-$$p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}$$
+The pragmatic speaker in turn considers the probability that a literal listener would interpret her utterance correctly:
 
-The **posterior** $\mathbf{p_{L1}(m | u)}$ quantifies a listener's degree of belief that a speaker intended a meaning $m$ given an utterance $u$.
-The subscript $L_1$ denotes a pragmatic listener interpretation of meaning $m$ given utterance $u$.
+$$ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)$$
 
-## Simluating implicature: Measuring literal semantics and pragmatic judgments
-In order to simulate the role of scale representation on implicature we pair a computational framework with empirical data.
-In particular we use experimental tools to populate three components of the model.
-First, to measure otherwise ambiguous literal semantics $\mathbf{p_{L0}(m|u)}$ (our "Scalar Diversity"" approach).
-Second, to generate a set of plausible alternatives to the original scalar pairs taken from van Tiel (2014).
-Lastly, to obtain human pragmatic judgments for model comparison $\mathbf{p_{L1}(m|u)}$.
+\noindent where $L_0$ refers to a listener who only considers the truth-functional semantics of the utterance (that is, which meanings the utterance can refer to).
 
-Starting with the first component, consider the scalar items  "some" and "all." Both are convenient for modeling in a computational framework like the one we've proposed above.
-Their literal semantics $\mathbf{p_{L0}}$ are easily quantified over sets.
+This model of the pragmatic speaker is consistent with a speaker who choses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:
 
-$$\text{\text it{some of the A's are B's.}}$$
-$$[[some]] = \{<A, B> : |A \cap B| \geq 1 \}$$
+$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},$$
 
-$$\text{\text it{all of the A's are B's.}}$$
-$$[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}$$
+\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ for the literal listener (the information content of the utterance), and ($\alpha$ is a parameter in a standard choice rule.
+If $\alpha=0$, speakers choose randomly and as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative.
+In our simulations below, we treat $\alpha$ as a free parameter and fit it to the data.
 
-The same cannot be said for items such as "good / excellent", "memorable / unforgettable" or "liked / loved."
+To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an onine restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
+We then use experiments to measure three components of the model.
+First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiments 1a, 3a, and 4).
+Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2).
+Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances.
 
-In the following set of studies we adopt a food-review paradigm to measure literal semantics and pragmatic judgments empirically.
-In order to capture graded typicality judgments as in Degen & Tanenhaus (2014) we use a compatibility measure dependent variable, pairing scalar items with star-ratings in our literal listener task (Experiments 1a, 3a and 4).
-Data from these experiments is used to approximate the literal listener semantics for a given scalar item $u$ as a distribution over star-ratings $m \in \text{\{1 - 5 stars\}}$.
-Similarly, pragmatic judgment data from Experiments 1b and 3b serve as our primary points of comparison with model predictions $\mathbf{p_{L1}(m|u)}$, again quantifying judgments as distributions over star-ratings.
-In the following section we take the reader through our experiments.
+# Experiment 1: Entailment scales
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows a trial from Experiment 1a with the target scalar \`liked\'.
-Participants responses to the binary dependent variable are used to quantify literal semantics.
-The right panel shows a trial from Experiment 1b with the target scalar \`liked\'.
-Participants were asked to generate the star rating they think the speaker likely intended, given the target scalar (in this case 'liked')."}
+```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1a,b, 3a,b and 4."}
+
+# Scale stimuli
+grid::grid.raster(png::readPNG("figs/alternativeSets.png"))
+```
+
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1a (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar \`liked.\'"}
 
@@
 
-# Experiment 1a,b: Entailment scales
-
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L0}(m|u)$ (Experiment 1a) and pragmatic judgments $p_{L1}(m|u)$ (Experiment 1b) for five pairs of scalar items taken from van Tiel (2014) (see figure 5 for stimuli).
-Each pair consists of a "weaker" scalar term (e.g.
-"some") and a stronger scalar term (e.g.
+Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ (Experiment 1a) and pragmatic judgments $p_{L_1}(m \mid u)$ (Experiment 1b) for five pairs of scalar items taken from @vantiel2014.
+Scales and alternative utterances are shown in Figure \ref{fig:allScalesTable}.
+Each pair of scalar items consists of a "weaker" term (e.g.
+"some") and a stronger term (e.g.
 "all").
-We are calling these "entailment scales", because they encode the assumption that a listener need only have a the stronger alternative present to generate an enriched interpretation of the weaker term.
-The grey colored items in Table 1 denote the original "entailment" items used in Experiments 1a,b.
+We begin with these classic members of the Horn scale [@horn1972] as a test of the hypothesis that these alternatives are all that is necessary to predict the strength of listeners' pragmatic inferences.
 
@@
 ### Participants
-Participants for both tasks were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
-Thirty participants were recruited for Experiment 1a.
-Data for two participants was thrown out during analysis because they were not native English speakers, leaving a total sample of 28 participants.
-Fifty participants were recruited for Experiment 1b.
-Data for 7 participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 43 participants.
+
+We recruited 30 participants from Amazon Mechanical Turk (AMT) for Experiment 1a; two participants were excluded because they reported having a native language other than English for a final sample of 28 participants.
+We recruited 50 for Experiment 1b, also from AMT, and data for 7 participants were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
 
 ### Design and procedure
-The left panel of Figure 1 shows a screen shot of a trial from Experiment 1a.
-Participants were presented with a target scalar item and a star-rating (between 1-5 stars) and asked to judge the compatibility of the scalar item and star-rating.
-Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the "\____." Each participant was presented all scalar item and star-rating combinations with randomization.
 
-The right panel of Figure 1 shows a screen shot of a trial from Experiment 1b.
-On each trial, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star-rating according to what they thought the reviewer likely gave.
-Each participant was presented all scalar items with randomization.
+Figure \ref{fig:stimuli_exp1} shows the experimental setup for both experiments.
+In Experiment 1a, the literal listener task, participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating.
+Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
+Each participant saw all scalar item and star rating combinations, in a random oder.
+
+In Experiment 1b, the pragmatic listener experiment, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
+Each participant was presented with all scalar items in a random order.
 
 ## Results and Discussion
-Figure 2 plots literal listener $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
-Data from 1a is (...).
-We see clear variation in semantic judgments between scalar families in all Experiments.
-For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved".
-We will address distributional similarity across the studies in later sections.
 
-```{r}
-# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
-#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
-# subset(speakerE8, degree == "low")$cnt.judgment
-# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
-#            subset(speakerE8, degree == "low")$cnt.judgment)
-```
-
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel plots literal semantic distributions for the scalar pair \'liked/loved\'.
-The y-axis is the percentage of \'yes\' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\\% of respondents beleived that \'liked\' was compatible with both 4 and 5 stars).
-Erro bars are 95\\% confidence intervals.
-The right panel plots pragmatic judgments for the scalar pair \'liked/loved\'.
-The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\\% of judgments when prompted with \'loved\' were 5-stars)."}
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4.
+Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).
+Each panel shows one scalar pair."}
 
@@
   facet_grid(.~ scale) + 
-  theme_bw()
+  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
+                               title = "Scalar Item"), 
+         linetype = guide_legend(direction = "horizontal", nrow = 1, 
+                                 title = "Experiment")) + 
+  xlab("Star Rating") +
+  ylab("Proportion Judgments") + 
+  scale_colour_solarized() + 
+  theme_bw() + 
+  theme(legend.position = "bottom",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"))
 
@@
 # gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
+```
+
+Figure 2 plots literal listener $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
+Data from 1a is (...).
+We see clear variation in semantic judgments between scalar families in all Experiments.
+For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved".
+We will address distributional similarity across the studies in later sections.
+
+```{r}
+# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
+#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
+# subset(speakerE8, degree == "low")$cnt.judgment
+# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
+#            subset(speakerE8, degree == "low")$cnt.judgment)
 ```
@@
 
-# Model Runs
+# Model Results
 
@@
 
-```{r allScalesTable, fig.env = "figure", fig.pos = "h", fig.width=3.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=1, fig.cap = "This table shows the stimuli used in Experiments 1a,b, 3a,b and 4.
-Colors denote the additions made in each experiment.
-For example, in Experiment 1a we measured literal semantics for \'liked/loved\'.
-In Experiment 3a,b we extended this group to \'textit{hated/disliked/liked/loved\'.
-In Experiment 4 we extended this grou to \'hated/disliked/felt indifferent about/liked/loved\'."}
-
-# Scale stimuli
-grid::grid.raster(png::readPNG("figs/alternativeSets.png"))
-```
-
 # Acknowledgements
@@
 
-```{r}
-# References will be generated automatically by Pandoc and included here.
-# The following code is some latex to format the bibliography. Do not remove it.
-```
-
 \setlength{\parindent}{-0.1in} 
@@
 \noindent
-
-Ignore below this
-
-use a food review paradigm in which 'meaning' for a given scalar item was quantified as a distribution over star-ratings.
-Quantifying both literal semantic content and pragmatic judgments as distributions over stars provides an important interface to our model, especially for scalar items with ambiguous literal semantics (e.g.
-items such as "liked/loved" or "memorable/unforgettable").
-In addition to quantifying literal semantics and pragmatic judgments in Experiments 1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task, based on van Tiel (2013, Experiment 2???), to generate a set of plausible alternatives to the scalar items used in Experiments 1a,b.
-We extend the set of alternatives measured in Experiments 3a,b and 4 using data from Experiment 2.
-Additionally, by looking at the relative frequencies of alternatives generated in Experiment 2 we were able to compute a saliency measure for each alternative.
-Using the literal semantic data from Experiments 1a, 3a and 4, we modeled pragmatic enrichment using RSA and compared model predictions to human judgments obtained in Experiments 1b and 3b.
-Model performance was significantly improved with the incorporation of alternatives.
-This result suggests that more ``fully specified" scale representations may be active for human participants while making pragmatic judgments for scalar items.

### 2016-01-24 Paper/Paper.tex
relative plots
mcf pass 1

@@
 \usepackage{float}
+\usepackage{caption}
 
@@
 
-\title{The importance of alternatives in scalar implicature}
+\title{Determining the alternatives for scalar implicature}
 
@@
 inferences - enrichments beyond the literal meaning of a speaker's
-utterance. For example, listeners routinely enrich the meaning of
-``some'' to ``some, but not all'' when interpreting a sentence such as
-``Bob ate some of the cookies.'' A Gricean account of this phenomena
-assumes the presence of \emph{salient alternatives} with varying degrees
-of informativity. ``Some,'' in the example above, is enriched to ``some,
-but not all'' in the presence of the stronger alternative ``all.''
-Empirical evidence for the presence of such alternatives and accounts of
-their effect on implicature has been limited. Our current work explores
-the role different scale representations may play in scalar implicature
-using empirical measures of literal semantics and a Bayesian model of
-implicature generation. Comparisons with human judgments indicate that
-pragmatic inference may rely on fairly complete alternative sets rather
-than the typical entialment only scales assumed in most research to
-date.
+utterance. For example, when interpreting a sentence such as ``Bob ate
+some of the cookies,'' listeners routinely infer that Bob did not eat
+all of them. A Gricean account of this phenomena assumes the presence of
+alternatives (like ``all of the cookies'') with varying degrees of
+informativity, but it remains an open question precisely what these
+alternatives are. We use a computational model of pragmatic inference to
+test out hypotheses about how well different sets of alternatives allow
+us to predict scalar implicature performance across a range of different
+scales. Our findings suggest that human comprehenders likely consider a
+much broader set of alternatives beyond those entailed by the initial
+description.
 
@@
 
-Humpty Dumpty Quote\ldots{}
+Successful communication requires listeners to make pragmatic inferences
+that go beyond the literal semantic content of speakers' utterances. For
+example, listeners commonly enrich the meaning of the scalar item
+``some'' to ``some but not all'' in sentences like ``Bob ate some of the
+cookies'' (Grice, 1975; Horn, 1984; Levinson, 2000). These inferences,
+called \emph{scalar implicatures}, have been an important test case for
+understnading pragmatic inferences more generally. A Gricean account of
+this phenomena assumes listeners reason about the meaning the speaker
+intended by incorporating knowledge about a) alternative scalar items a
+speaker could have used (such as ``all'') and b) the relative
+informativity of using such alternatives (Grice, 1975). According to
+this account, a listener will infer that the speaker must have intended
+that Bob did not eat ``all'' the cookies because it would have been
+\emph{underinformative} for the speaker to use ``some'' when ``all''
+could have been used.
 
-Successful communication regularly requires listeners to make inferences
-that go beyond the literal semantic content of a speaker's utterance.
-``Scalar implicature'' is a hallmark of such pragmatic enrichment. For
-example, listeners routinely enrich the meaning of the scalar item
-``some'' to ``some, but not all'' in sentences like ``Bob ate some of
-the cookies'' (van Tiel, 2014; other\ldots{}). A Gricean account of this
-phenomena assumes listeners reason about the intended meaning of a
-speaker while incorporating knowledge about a) alternative scalar items
-a speaker could have used (such as ``all'') and b) the relative
-informativity of using such alternatives (Grice, 1975). Under the
-Gricean account, a listener will infer that the speaker must have
-intended that Bob did not eat ``all'' the cookies because it would have
-been \emph{underinformative} for the speaker to use ``some'' when
-``all'' could have been used.
+But what are the alternatives that should be considered in this
+computation more generally? Under classic accounts of implicature,
+listeners consider only those words whose meaning would entail the word
+that is actually sent (Horn, 1972), and these alternatives enter into
+conventionalized or semi-conventionalized scales (Levinson, 2000). For
+example, because ``all'' entails ``some,'' and hence is a ``stronger''
+meaning, ``all'' should be considered as an alternative to ``some'' in
+implicatures. Similar scales exist for non-quantifier scales, e.g.
+``love'' entails ``like'' (and hence ``I liked the movie'' implicates
+that I didn't love it).
 
-The presence of ``salient" alternatives is critical to the standard
-Gricean account of scalar implicature (Grice, 1975). Recent experimental
-evidence appears to support this. Using a gumball paradigm, Degen \&
-Tanenhaus (2014) demonstrated that the scalar item \emph{some} was
-judged less appropriate (natural) for small sets of items when exact
-numbers were seen as viable alternatives. This finding points to the
-impact a particular alternative set can have on judgments regarding
-scalar appropriateness. Using a fundamentally different approach, Franke
-(2014) formalized the Gricean account of implicature using a Bayesian
-model, modeling graded typicality judgments and scalar implicature.
-Results supported `none', `one' and `all' as the most serious (salient)
-alternatives to ``some.''
+Recent empirical evidence has called into question whether entailment
+scales are all that is necessary for understanding scalar implicature.
+For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
+``some'' was judged less appropriate when exact numbers were seen as
+viable alternatives. And in a different paradigm, Tiel (2014) found
+converging evidence that ``some'' was judged to be atypical for small
+quantities. These data provide indirect evidence about a broader set of
+alternatives: since ``some'' is logically true of sets with one or two
+members, these authors argued that the presence of salient alternatives
+(the words ``one'' and ``two'') reduced the felicity of ``some'' via a
+pragmatic inference.
 
-Taken together, each of the previous studies signal the importance of
-scale representation (set of available alternatives) in scalar
-implicature. However, like many recent investigations which have focused
-only on a small subset of scalar items, both Degen \& Tanenhaus (2014)
-and Franke (2014) focus exclusively on the scalar family ``some/all.''
-This lack ``Scalar Diversity'' (van Tiel, 2014) makes generalization
-across different scalar families problematic. van Tiel (2014), found
-substantial variation in the rate of upper-bounded construals aross more
-than 40 different scalar pairs. This finding suggests that implicature
-may differ widely between different scales. We adopt a ``Scalar
-Diversity'' approach in our experimental design in order to extend our
-investigation beyond ``some/all'' scalar items. In the following set of
-studies we examine implicature for ``some/all'' and five additional
-scalar families from a range of grammatical classes (see Figure 5 for a
-complete set of scalar items used). The set of scalar items for this
-study were chosen from among the 40 used in van Tiel (2014).
+By formalizing pragmatic reasoning, computational models can help
+provide more direct evidence about the role that alternatives play. The
+``rational speech act'' model (RSA) is one recent framework for
+understanding inferences about meaning in context (Frank \& Goodman,
+2012; N. D. Goodman \& Stuhlm{ü}ller, 2013). RSA models frame language
+understanding as a special case of social cognition, in which listeners
+and speakers reason recursively about one another's goals. In the case
+of scalar implicature, a listener makes a probabilistic inference about
+what the speaker's most likely communicative goal was, given that she
+picked the quantifier ``some'' rather than the stronger quantifier
+``all.'' In turn, the speaker reasons about what message would best
+convey her intended meaning to the listener, given that he is reasoning
+in this way. This recursion is grounded in a ``literal'' listener who
+reasons only according to the basic truth-functional semantics of the
+language.
 
-Consider a scalar item other than ``some'' - in the context of the word
-``good'', the idea of set of lexical alternatives seems intuitive
-(``bad'', ``excellent'', etc.). But measuring the extent to which these
-alternatives are salient is not so clear. Nor is how to measure their
-impact on pragmatic interpretations of the scalar item ``good.'' In an
-experimental setting, querying a participant about the saliency of a
-particular alternative is problematic because the alternative must be
-made salient during the query. In the spirit of Franke (2014) and Degen
-\& Tanenhaus (2014), we pair a computational model of implicature with
-empirical measurements of linguistic material. This combination allows
-us to simulate the effect of various scale representations on
-implicature. In particular, we adopt a Bayesian model of implicature and
-a food-review paradigm to empirically quantify literal semantics and
-pragmatic judgments for our scalar stimuli.
+Franke (2014) used an RSA-style model to assess what alternatives a
+speaker would need to consider in order to produce the
+typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
+Tiel (2014). In order to do this, Franke (2014)'s model assigned weights
+to a set of alternative numerical expressions. Surprisingly, along with
+weighting ``one'' highly (a conclusion that was suppored by the
+empirical work),the best-fitting model assigned substantial weight to
+``none'' as an alternative. This finding was especially surprising
+considering the emphasis of standard theories on scalar items that stand
+in entailment relationships with one another (e.g. ``one'' entails
+``some'' even if it is not classically considered to be part of the
+scale scale).
 
-Bayesian models of pragmatic enrichment have accurately predicted human
-judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhmuller
-\& Goodman, 2014) implicature settings. Our current model follows both
-these studies and is based on Rational Speech-act theory (RSA). RSA
-frames language understanding as a special case of social cognition
-(Frank \& Goodman, 2012; Stulhmuller \& Goodman, 2014), in which
-listeners and speakers reason about one-another. In this framework, a
-listener uses Bayesian inference to interpret the intended meaning \(m\)
-of a speaker who has made an utterance \(u\). We will make the model
-specifications explicit later in the paper.
+In our current work, we pick up where these previous studies left off,
+considering the set of alternatives for implicature using the RSA model.
+To gain empirical traction on this issue, however, we broaden the set of
+scales we consider. Our inspiration for this move comes from work by Van
+Tiel, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
+phenomenon that they dubbed ``scalar diversity,'' namely the substantial
+difference in the strength of scalar implicature across a variety of
+scalar pairs (e.g. ``liked/loved,'' or ``palatable/delicious.''). Making
+use of some of this diversity allows us to investigate the ways that
+different alternative sets give rise to implicatures of different
+strengths across scales.
 
-In the following study we investigate the role of scale representation
-on scalar implicature. To do so we combine a computational framework
-with empirical measurements to simulate the type of scale
-representations that might be available to a listener. In the following
-sections we outline the specifics of the model and the particular
-components for which we need to to make empirical measurements. We then
-outline a series of experiments meant to a) quantify literal semantics
-for otherwise ambiguous scalar items, b) measure pragmatic judgments and
-c) generate a set of plausible alternatives for our set of scalar pairs
-taken from van Tiel (2014). In particular, we adopt a food review
-paradigm throughout our empirical data gathering, quantifying linguistic
-meaning (both literal semantics and pragmatic judgments) as
-distributions over star ratings. Finally, we simulate the impact of
-three different scale representations, ``entailment'', ``mid'' and
-``symmetric'' on implicature generation, comparing model predictions
-with pragmatic judgments captured empirically. Results indicate that
-humans may employ more ``fully specified'' scale representations,
-relying on the presence of multiple alternatives during pragmatic
-enrichment.
+We begin by presenting the computational framework we use throughout the
+paper. We next describe a series of experiments deisgned to measure both
+the literal semantics of a set of scalar items and comprehenders'
+pragmatic judgments for these same items. These experiments allow us to
+compare the effects of different alternative sets on our ability to
+model listeners' pragmatic judgements. To preview our results: we find
+that standard entailment alternatives do not allow us to fit
+participants' judgements, but that expanding the range of alternatives
+empirically (by asking participants to generate alternative messages)
+allows us to model listener judgements with high accuracy.
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
+\section{Modeling Implicature Using
+RSA}\label{modeling-implicature-using-rsa}
 
-\section{Modeling implicature: Rational Speech-act
-theory}\label{modeling-implicature-rational-speech-act-theory}
+We begin by giving a brief presentation of the basic RSA model. This
+model simulates the judgements of a pragmatic listener who wants to
+infer a speaker's intended meaning \(m\) from her utterance \(u\). For
+simplicity, we present a version of this model in which there is only
+full recursion: that is, the pragmatic listener reasons about a
+pragmatic speaker, who in turn reasons about a ``literal listener.'' We
+assume throughout that this computation takes place in a signaling game
+(Lewis, 1969) with a fixed set of possible meanings \(m \in M\) and a
+fixed possible set of utterances \(u \in U\), with both known to both
+participants. Our goal in this study is to determine what utterances
+fall in \(U\).
 
-We adopt a Bayesian model of scalar implicature known as Rational
-Speech-act theory (RSA). In particular, RSA frames language
-understanding as a special case of social cognition (Frank \& Goodman,
-2012; Stuhmuller \& Goodman, 2014) in which listener and speaker agents
-reason about one another. We focus on the problem of a listener
-inferring the meaning of a speaker's utterance. Let \(u\) be an observed
-utterance made by our speaker with an intended meaning \(m\). We assume
-that the listener has access to a space of possible meanings \(M\) and
-some model relating meanings \(m \in M\) to \(u\).
+In the standard RSA model, the pragmatic listener (denoted \(L_1\)),
+makes a Bayesian inference:
 
-Upon hearing an utterance \(u\) the Listener agent evaluates all
-candidate word meanings, computing their posterior probabilities
-\(p_{L1}(m | u)\). This quantity is proportional to the product of the
-prior probability \(p(m)\) of a particular meaning and the likelihood
-\(p(u | m)\).
+\[p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)\]
 
-\[p_{L1}(m | u) = \frac{p(u | m)p(m)}{p(u)}\]
-\[= \frac{p(u | m)p(m)}{\sum_{m \in M}p(u | m)}\]
+\noindent In other words, the probability of a particular meaning given
+an utterance is proportional to the speaker's proability of using that
+particular utterance to express that meaning, weighted by a prior over
+meanings. This prior represents the listener's \emph{a priori}
+expectations about plausible meanings, independent of the utterance.
+Because our experiments take place in a context in which listeners
+should have very little expectation about which meanings speakers want
+to convey, for simplicity we assume a uniform prior \(p(m) \propto 1\).
 
-The \textbf{prior} \(\mathbf{p(m)}\) represents the listener's
-expectations about plausible meanings (star ratings), \emph{independent}
-of the utterance \(u\). To avoid biasing the data we assume priors over
-meanings are uniform, however future investigations may want to
-experiment with different priors, either by inferring them or using
-empirical measures
+The pragmatic speaker in turn considers the probability that a literal
+listener would interpret her utterance correctly:
 
-\(\mathbf{p(u | m)}\) quantifies the \textbf{likelihood} that a speaker
-would make a particular utterance \(u\) given an intended meaning \(m\).
-Our model assumes that speakers choose words to maximize the utility of
-an utterance in context. Utility is operationalized as the informativity
-of a particular utterance (surprisal) minus a cost. In particular, the
-speaker chooses an utterance in order to maximize the utility of a
-listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
-denotes a literal listener interpretation of meaning \(m\) given
-utterance \(u\).
-\[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]
+\[ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)\]
 
-The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
-listener's degree of belief that a speaker intended a meaning \(m\)
-given an utterance \(u\). The subscript \(L_1\) denotes a pragmatic
-listener interpretation of meaning \(m\) given utterance \(u\).
+\noindent where \(L_0\) refers to a listener who only considers the
+truth-functional semantics of the utterance (that is, which meanings the
+utterance can refer to).
 
-\subsection{Simluating implicature: Measuring literal semantics and
-pragmatic
-judgments}\label{simluating-implicature-measuring-literal-semantics-and-pragmatic-judgments}
+This model of the pragmatic speaker is consistent with a speaker who
+choses words to maximize the utility of an utterance in context (Frank
+\& Goodman, 2012), where utility is operationalized as the informativity
+of a particular utterance (surprisal) minus a cost:
 
-In order to simulate the role of scale representation on implicature we
-pair a computational framework with empirical data. In particular we use
-experimental tools to populate three components of the model. First, to
-measure otherwise ambiguous literal semantics \(\mathbf{p_{L0}(m|u)}\)
-(our ``Scalar Diversity''" approach). Second, to generate a set of
-plausible alternatives to the original scalar pairs taken from van Tiel
-(2014). Lastly, to obtain human pragmatic judgments for model comparison
-\(\mathbf{p_{L1}(m|u)}\).
+\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},\]
 
-Starting with the first component, consider the scalar items ``some''
-and ``all.'' Both are convenient for modeling in a computational
-framework like the one we've proposed above. Their literal semantics
-\(\mathbf{p_{L0}}\) are easily quantified over sets.
+\noindent where \(C(u)\) is the cost of a particular utterance,
+\(-log(p_{L_0})\) represents the \emph{surprisal} for the literal
+listener (the information content of the utterance), and (\(\alpha\) is
+a parameter in a standard choice rule. If \(\alpha=0\), speakers choose
+randomly and as \(\alpha \rightarrow \infty\), they greedily choose the
+highest probability alternative. In our simulations below, we treat
+\(\alpha\) as a free parameter and fit it to the data.
 
-\[\text{\text it{some of the A's are B's.}}\]
-\[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]
+To instantiate our signaling game with a tractable message set \(M\), in
+our studies we adopt a food-review paradigm: we assume that speakers and
+listeners are trying to communicate the number of stars in an onine
+restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
+experiments to measure three components of the model. First, to measure
+literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
+participants to judge whether a message is applicable to a particular
+meaning (Experiments 1a, 3a, and 4). Second, to generate a set of
+plausible alternative messages in \(U\), we elicit alternatives directly
+(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
+ask participants to interpret a speaker's utterances.
 
-\[\text{\text it{all of the A's are B's.}}\]
-\[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]
-
-The same cannot be said for items such as ``good / excellent'',
-``memorable / unforgettable'' or ``liked / loved.''
-
-In the following set of studies we adopt a food-review paradigm to
-measure literal semantics and pragmatic judgments empirically. In order
-to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
-we use a compatibility measure dependent variable, pairing scalar items
-with star-ratings in our literal listener task (Experiments 1a, 3a and
-4). Data from these experiments is used to approximate the literal
-listener semantics for a given scalar item \(u\) as a distribution over
-star-ratings \(m \in \text{\{1 - 5 stars\}}\). Similarly, pragmatic
-judgment data from Experiments 1b and 3b serve as our primary points of
-comparison with model predictions \(\mathbf{p_{L1}(m|u)}\), again
-quantifying judgments as distributions over star-ratings. In the
-following section we take the reader through our experiments.
+\section{Experiment 1a,b: Entailment
+scales}\label{experiment-1ab-entailment-scales}
 
 \begin{CodeChunk}
-\begin{figure*}[t]
+\begin{figure}[t]
+\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1a,b, 3a,b and 4]{Stimuli for Experiments 1a,b, 3a,b and 4.}\label{fig:allScalesTable}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
 
@@
 
-\caption[The left panel shows a trial from Experiment 1a with the target scalar `liked']{The left panel shows a trial from Experiment 1a with the target scalar `liked'.
-Participants responses to the binary dependent variable are used to quantify literal semantics.
-The right panel shows a trial from Experiment 1b with the target scalar `liked'.
-Participants were asked to generate the star rating they think the speaker likely intended, given the target scalar (in this case 'liked').}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 
-\section{Experiment 1a,b: Entailment
-scales}\label{experiment-1ab-entailment-scales}
-
 Experiment 1a and 1b were conducted to approximate literal listener
-semantic distributions \(p_{L0}(m|u)\) (Experiment 1a) and pragmatic
-judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
-taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
-consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
-scalar term (e.g. ``all''). We are calling these ``entailment scales'',
-because they encode the assumption that a listener need only have a the
-stronger alternative present to generate an enriched interpretation of
-the weaker term. The grey colored items in Table 1 denote the original
-``entailment'' items used in Experiments 1a,b.
+semantic distributions \(p_{L_0}(m \mid u)\) (Experiment 1a) and
+pragmatic judgments \(p_{L_1}(m \mid u)\) (Experiment 1b) for five pairs
+of scalar items taken from Tiel (2014). Scales and alternative
+utterances are shown in Figure \ref{fig:allScalesTable}. Each pair of
+scalar items consists of a ``weaker'' term (e.g. ``some'') and a
+stronger term (e.g. ``all''). We begin with these classic members of the
+Horn scale (Horn, 1972) as a test of the hypothesis that these
+alternatives are all that is necessary to predict the strength of
+listeners' pragmatic inferences.
 
@@
 
-Participants for both tasks were recruited on Amazon Mechanical Turk and
-paid \$0.20 for their participation. Thirty participants were recruited
-for Experiment 1a. Data for two participants was thrown out during
-analysis because they were not native English speakers, leaving a total
-sample of 28 participants. Fifty participants were recruited for
-Experiment 1b. Data for 7 participants was thrown out after participants
-either failed to pass two training trials or were not native English
-speakers, leaving a total sample of 43 participants.
+We recruited 30 participants from Amazon Mechanical Turk (AMT) for
+Experiment 1a; two participants were excluded because they reported
+having a native language other than English for a final sample of 28
+participants. We recruited 50 for Experiment 1b, also from AMT, and data
+for 7 participants were excluded after participants either failed to
+pass two training trials or reported a non-English native language,
+leaving a total sample of 43 participants.
 
@@
 
-The left panel of Figure 1 shows a screen shot of a trial from
-Experiment 1a. Participants were presented with a target scalar item and
-a star-rating (between 1-5 stars) and asked to judge the compatibility
-of the scalar item and star-rating. Compatibility was assessed through a
-binary ``yes/no'' response to a question of the form ``Do you think that
-the person thought the food was \_\_\_\_?" where a target scalar was
-presented in the ``\_\_\_\_." Each participant was presented all scalar
-item and star-rating combinations with randomization.
+Figure \ref{fig:stimuli_exp1} shows the experimental setup for both
+experiments. In Experiment 1a, the literal listener task, participants
+were presented with a target scalar item and a star rating (1--5 stars)
+and asked to judge the compatibility of the scalar item and star-rating.
+Compatibility was assessed through a binary ``yes/no'' response to a
+question of the form ``Do you think that the person thought the food was
+\_\_\_\_?" where a target scalar was presented in the blank. Each
+participant saw all scalar item and star rating combinations, in a
+random oder.
 
-The right panel of Figure 1 shows a screen shot of a trial from
-Experiment 1b. On each trial, participants were presented with a
-one-sentence prompt containing a target scalar item such as ``Someone
-said they thought the food was \_\_\_\_\_.'' Participants were then
-asked to generate a star-rating according to what they thought the
-reviewer likely gave. Each participant was presented all scalar items
-with randomization.
+In Experiment 1b, the pragmatic listener experiment, participants were
+presented with a one-sentence prompt containing a target scalar item
+such as ``Someone said they thought the food was \_\_\_\_\_.''
+Participants were then asked to generate a star rating representing the
+rating they thought the reviewer likely gave. Each participant was
+presented with all scalar items in a random order.
 
 \subsection{Results and Discussion}\label{results-and-discussion}
+
+\begin{CodeChunk}
+\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
+
+{\centering \includegraphics{figs/exp1Plots-1}
+
+}
+
+\caption[Literal listener judgements from Experiments 1a, 3a, and 4]{Literal listener judgements from Experiments 1a, 3a, and 4.
+Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).
+Each panel shows one scalar pair.}\label{fig:exp1Plots}
+\end{figure*}
+\end{CodeChunk}
 
@@
 studies in later sections.
-
-\begin{CodeChunk}
-\begin{figure*}[t]
-
-{\centering \includegraphics{figs/exp1Plots-1}
-
-}
-
-\caption[The left panel plots literal semantic distributions for the scalar pair 'liked/loved']{The left panel plots literal semantic distributions for the scalar pair 'liked/loved'.
-The y-axis is the percentage of 'yes' responses for a scalar term that is compatibible with the number of stars on the x-axis (ie 100\% of respondents beleived that 'liked' was compatible with both 4 and 5 stars).
-Erro bars are 95\% confidence intervals.
-The right panel plots pragmatic judgments for the scalar pair 'liked/loved'.
-The y-axis is the proportion of selection of the star-rating on the x-axis (ie over 80\% of judgments when prompted with 'loved' were 5-stars).}\label{fig:exp1Plots}
-\end{figure*}
-\end{CodeChunk}
 
@@
 \begin{CodeChunk}
-\begin{figure*}[t]
+\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
 
@@
 
-\textbackslash{}begin\{CodeChunk\}
-\textbackslash{}begin\{figure\}{[}h{]}
-
-\{\centering \includegraphics{figs/allScalesTable-1}
-
-\}
-
-\textbackslash{}caption{[}This table shows the stimuli used in
-Experiments 1a,b, 3a,b and 4{]}\{This table shows the stimuli used in
-Experiments 1a,b, 3a,b and 4. Colors denote the additions made in each
-experiment. For example, in Experiment 1a we measured literal semantics
-for `liked/loved'. In Experiment 3a,b we extended this group to
-`textit\{hated/disliked/liked/loved'. In Experiment 4 we extended this
-grou to `hated/disliked/felt indifferent
-about/liked/loved'.\}\label{fig:allScalesTable}
-\textbackslash{}end\{figure\} \textbackslash{}end\{CodeChunk\}
-
 \section{Acknowledgements}\label{acknowledgements}
@@
 
-Ignore below this
+Degen, J., \& Tanenhaus, M. K. (2015). Processing scalar implicature: A
+constraint-based approach. \emph{Cognitive Science}, \emph{39}(4),
+667--710.
 
-use a food review paradigm in which `meaning' for a given scalar item
-was quantified as a distribution over star-ratings. Quantifying both
-literal semantic content and pragmatic judgments as distributions over
-stars provides an important interface to our model, especially for
-scalar items with ambiguous literal semantics (e.g.~items such as
-``liked/loved'' or ``memorable/unforgettable''). In addition to
-quantifying literal semantics and pragmatic judgments in Experiments
-1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
-based on van Tiel (2013, Experiment 2???), to generate a set of
-plausible alternatives to the scalar items used in Experiments 1a,b. We
-extend the set of alternatives measured in Experiments 3a,b and 4 using
-data from Experiment 2. Additionally, by looking at the relative
-frequencies of alternatives generated in Experiment 2 we were able to
-compute a saliency measure for each alternative. Using the literal
-semantic data from Experiments 1a, 3a and 4, we modeled pragmatic
-enrichment using RSA and compared model predictions to human judgments
-obtained in Experiments 1b and 3b. Model performance was significantly
-improved with the incorporation of alternatives. This result suggests
-that more ``fully specified" scale representations may be active for
-human participants while making pragmatic judgments for scalar items.
+Frank, M., \& Goodman, N. (2012). Predicting pragmatic reasoning in
+language games. \emph{Science}, \emph{336}(6084), 998.
+
+Franke, M. (2014). Typical use of quantifiers: A probabilistic speaker
+model. In \emph{Proceedings of the 36th annual conference of the
+cognitive science society} (pp. 487--492).
+
+Goodman, N. D., \& Stuhlm{ü}ller, A. (2013). Knowledge and implicature:
+Modeling language understanding as social cognition. \emph{Topics in
+Cognitive Science}, \emph{5}(1), 173--184.
+
+Grice, H. P. (1975). Logic and conversation. In P. Cole \& J. Morgan
+(Eds.), \emph{Syntax and semantics} (Vol. 3). New York: Academic Press.
+
+Horn, L. R. (1972). \emph{On the semantic properties of logical
+operators.} (PhD thesis). University of California, Los Angeles.
+
+Horn, L. R. (1984). Toward a new taxonomy for pragmatic inference:
+Q-based and R-based implicature. \emph{Meaning, Form, and Use in
+Context}, \emph{42}.
+
+Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of
+generalized conversational implicature}. MIT Press.
+
+Lewis, D. (1969). \emph{Convention: A philosophical study}. John Wiley
+\& Sons.
+
+Tiel, B. van. (2014). Quantity matters: Implicatures, typicality, and
+truth.
+
+Van Tiel, B., Van Miltenburg, E., Zevakhina, N., \& Geurts, B. (2014).
+Scalar diversity. \emph{Journal of Semantics}, ffu017.
 

### 2016-01-24 Paper/Paper.Rmd
reorg into 1 2 3

@@
 We begin by presenting the computational framework we use throughout the paper.
-We next describe a series of experiments deisgned to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items.
+We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items.
 These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements.
@@
 We then use experiments to measure three components of the model.
-First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiments 1a, 3a, and 4).
+First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiment 1).
 Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2).
-Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances.
+Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances (Experiment 3).
 
-# Experiment 1: Entailment scales
+# Experiment 1: Literal listener task
 
-```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1a,b, 3a,b and 4."}
+```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1, 2, and 3"}
 
@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1a (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar \`liked.\'"}
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \`liked.\'"}
 
@@
 
-Experiment 1a and 1b were conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ (Experiment 1a) and pragmatic judgments $p_{L_1}(m \mid u)$ (Experiment 1b) for five pairs of scalar items taken from @vantiel2014.
-Scales and alternative utterances are shown in Figure \ref{fig:allScalesTable}.
-Each pair of scalar items consists of a "weaker" term (e.g.
-"some") and a stronger term (e.g.
-"all").
-We begin with these classic members of the Horn scale [@horn1972] as a test of the hypothesis that these alternatives are all that is necessary to predict the strength of listeners' pragmatic inferences.
+Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
+We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives.
+The two-alternative entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
+The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
 
@@
 
-We recruited 30 participants from Amazon Mechanical Turk (AMT) for Experiment 1a; two participants were excluded because they reported having a native language other than English for a final sample of 28 participants.
-We recruited 50 for Experiment 1b, also from AMT, and data for 7 participants were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
+In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
+In the two-alternative condition, two participants were excluded because they reported having a native language other than English for a final sample of 28 participants.
+In the four-alternative condition,  six participants were excluded for either failing to pass two training trials a non-English native language, leaving a total sample of 24 participants.
+In the five-alternative condition, there were no data exclusions due to training failures or native language requirements, leaving a total sample of 30 participants.
 
@@
 
-Figure \ref{fig:stimuli_exp1} shows the experimental setup for both experiments.
-In Experiment 1a, the literal listener task, participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating.
+Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
+Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating.
 Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
-Each participant saw all scalar item and star rating combinations, in a random oder.
+Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.
 
-In Experiment 1b, the pragmatic listener experiment, participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
-Each participant was presented with all scalar items in a random order.
+The two-alternatives condition included only the scalar pairs from @vantiel2014.
+The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
+The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2.
 
@@
         legend.key.size = unit(.1, "in"))
-
-####################################
-# OLD PLOTS -------------------------
-# plotData <- speakerE8 %>%
-#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
-# # Literal listener: Entailment (e8)
-# e6Plot <- ggplot(data = subset(plotData, scale == "liked_loved"), aes(x = stars, y = speaker.p, col=degree)) +
-#   geom_line() +
-#   ylab("Percent yes") +
-#   geom_linerange(aes(ymin = speaker.p - cil, 
-#                      ymax = speaker.p + cih)) +
-#   ggtitle("Literal semantics")
-# 
-# # Pragmatic listener: Entailment (e6)
-# plotData <- listenerE6 %>%
-#   mutate(degree = ifelse(degree == "hi", "loved", "liked"))
-# e8Plot <- ggplot(data = subset(plotData, scale == "liked_loved"),
-#                  aes(x = stars, y = listener.p, fill = degree)) +
-#   geom_bar(stat = "identity", position = "dodge") +
-#   facet_wrap(~degree) +
-#   ylab("Proportion of star-ratings chosen") +
-#   ggtitle("Pragmatic judgments") +
-#   theme(legend.position="none")
-# gridExtra::grid.arrange(e6Plot, e8Plot, ncol = 2, widths = c(2.5,3))
 ```
 
-Figure 2 plots literal listener $p_{L0}(m|u)$ distributions obtained in Experiments 1a, 3a and 4.
-Data from 1a is (...).
-We see clear variation in semantic judgments between scalar families in all Experiments.
-For example, compatibility judgments for "memorable" and "forgettable" are more similar than those for "good / excellent" or "liked / loved".
-We will address distributional similarity across the studies in later sections.
+Figure 2 plots literal listener $p_{L0}(m|u)$ distributions for the three conditions.
+Several trends are visible.
+First, in each scale, the alternatives spanned the star scale, such that there were alternatives that were highly compatible with both the lowest and highest numbers of stars.
+Second, there was clear variability between scalar families.
+For example, compatibility judgments for the top items in the "memorable / unforgettable" scale were more similar than those for "good / excellent" or "liked / loved." Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
 
-```{r}
-# chisq.test(subset(speakerE8, degree == "hi" & scale == "memorable_unforgettable")$speaker.p,
-#            subset(speakerE8, degree == "low" & scale == "memorable_unforgettable")$speaker.p)
-# subset(speakerE8, degree == "low")$cnt.judgment
-# chisq.test(subset(speakerE8, degree == "hi")$cnt.judgment,
-#            subset(speakerE8, degree == "low")$cnt.judgment)
-```
+# Experiment 2: Alternative Elicitation
 
-# Experiment 2: What are the alternatives?
-
-In Experiment 1 we obtained literal semantic compatibility and pragmatic judgments for five pairs of scalar terms.
-We would like to extend the scale descriptions for each of these pairs to include other plausible alternatives.
-We chose to take an empirical approach rather than assign alternatives arbitrarily.
-We adopted a modified cloze task, inspired by Experiment 2 in van Tiel (2014) and asked participants to generate alternatives for us.
+To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 2 of @vantiel2014.
 
@@
 
-Using Amazon's Mechanical Turk, 30 workers were paid $0.20 to participate. All participants were native English speakers and naive to the purpose of the experiment.
+We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
 
 ### Design and procedure
-Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____" with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" and asked to generate three unique alternatives.
+
+Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.
 
 ## Results and Discussion
-Figure 3 plots the combined counts of alternatives generated for the scalar items "liked" and "loved." Alternative distributions for the other scalar pairs (e.g..
-"good/excellent", "memorable/unforgettable") were similarly long-tailed, however the size and content of the alternate sets were diverse.
-(SOMETHING MORE MORE FORMAL HERE???)
 
-```{r exp2_altsPlot_likedLoved, fig.env = "figure*", fig.pos = "t", fig.width=7, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
 
 # Subset alternatives for demo
-plotData <- subset(alternativesData, scale == "liked_loved")
-removeRows <- which(plotData$alt == "liked" | plotData$alt == "loved")
-plotData <- plotData[-removeRows, ]
+plotData <- alternativesData %>%
+  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
+  mutate(prop = n / sum(n))
+
 # plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
-altsPlot <- ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
-  geom_bar(stat="identity") + ylim(0, 52) + labs(x = "alternative", y = "counts") +
-  ggtitle(paste("Salient alternatives for ", "liked/loved")) +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
-
-altsPlot
+ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
+  geom_bar(stat="identity") + 
+  ylim(0, 52) + 
+  labs(x = "alternative", y = "counts") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
+  ylab("Proportion of responses")
 ```
 
-# Experiment 3a,b: Incorporating top alternatives
+Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items "liked" and "loved" (combined).
+Alternative distributions for the other scalar pairs (e.g..
+"good/excellent", "memorable/unforgettable") were similarly long-tailed.
 
-In Experiment 1a,b we measured literal semantics and pragmatic judgments for Entailment scales.
-In Experiment 2, we asked participants to generate plausible alternatives to these items.
-In Experiments 3a,b we use the same experimental design for both literal semantics and pragmatic judgment tasks, however we now expand the set of scalar items to include the original Entailment pairs from Experiments 1a,b with the top two alternatives generated for each scalar family by participants in Experiment 2.
-The orange colored items in table 1 denote additional scalar items added in Experiments 3a,b.
+# Experiment 3: Pragmatic Listener
+
+In Experiment 3, we asked participants to make pragmatic listener judgements.
+
+CONDITIONS
 
@@
 
-Participants for both studies were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
-Thirty participants were recruited for Experiment 3a (Literal Listener task).
-Data for six participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 24 participants.
-
-Fifty participants were recruited for Experiment 3b (Pragmatic Listener task).
-Data for five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
+We recruited 150 participants from AMT, 50 for each condition.
+Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
+In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
 
 ## Procedure
-The procedure of Experiments 3a,b follow the same form as Experiments 1a,b with the expanded set of target scalar items.
+
+Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
+Each participant was presented with all scalar items in a random order.
+The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
 
@@
 
-Run glmer() here:
-```{r}
-
-```
-To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject.
-Results indicate (...)
-
-Run elmer() here:
-```{r}
-
-```
-
-To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject.
-Results indicate.
-
-While conducting our analysis we realized that our literal semantic distributions for each scalar family were roughly split between two negative valenced items and two positively valenced items while neutral alternatives appeared to be excluded.
-(This pattern was true of all the scalar families, except for "some \ all" in which the top two alternatives were positive valenced "most" and negative valenced "none".) In Experiment 4, we explore the addition of a neutrally valenced scalar alternative for each scalar family.
-
-# Experiment 4: Full scales - adding a neutral alternative
-In Experiment 4, we continue to extend the alternative sets, each by one additional scalar item.
-While we simply took the top two alternatives generated in Experiment 2 for the additional alternatives in Experiments 3a,b, in this case we chose a subjectively "neutral" valenced scalar item from among the alternatives generated in Experiment 2.
-The idea was to simulate a "full" set of alternatives, with negative, neutral and positive valenced items for each scalar family.
-The purple colored items in Table 1 denote additional scalar items added in Experiments 4.
-
-## Participants
-Thirty participants were recruited on Amazon Mechanical Turk and paid $0.20 for their participation.
-There were no data exclusions due to training failures or native language requirements, leaving a total sample of thirty participants, all native English speakers, naive to the purpose of the experiment.
-
-## Procedure
-The procedure of Experiment 4 follow the same form as Experiments 1a and 3a with the addition of a neutrally valence scalar item.
-
-## Results and Discussion
-Distributions for neutrally valenced scalar did appear fairly Gaussian, occupying a literal semantic previously unoccupied by the other alternatives.
-
-Run glmer() here:
-```{r}
-
-```
-To test whether literal listener compatibility judgments differed between Experiment 1a and 3a we ran a mixed effects model, regressing responses to the binary compatibility measure on scale, degree, and Experiment with random effects by subject.
-Results indicate (...)
-
-Run elmer() here:
-```{r}
-
-```
-
-To test whether pragmatic judgments differed between Experiments 1b and 3b we ran a mixed effects model, regressing star-rating selections on scale, scalar item and Experiment with random effects by subject.
-Results indicate.
-
 # Model Results
 
-Using literal semantic data from Experiments 1a, 3a and 4 we conducted three simulations with our model.
+Using literal semantic data from Experiment 1 we conducted three simulations with our model.
 Each simulation used the specific literal semantic data to specify the scale representation available to our model.
@@
 # General Discussion
+
 By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature.

### 2016-01-24 Paper/Paper.tex
reorg into 1 2 3

@@
 We begin by presenting the computational framework we use throughout the
-paper. We next describe a series of experiments deisgned to measure both
+paper. We next describe a series of experiments designed to measure both
 the literal semantics of a set of scalar items and comprehenders'
@@
 participants to judge whether a message is applicable to a particular
-meaning (Experiments 1a, 3a, and 4). Second, to generate a set of
-plausible alternative messages in \(U\), we elicit alternatives directly
+meaning (Experiment 1). Second, to generate a set of plausible
+alternative messages in \(U\), we elicit alternatives directly
 (Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
-ask participants to interpret a speaker's utterances.
+ask participants to interpret a speaker's utterances (Experiment 3).
 
-\section{Experiment 1a,b: Entailment
-scales}\label{experiment-1ab-entailment-scales}
+\section{Experiment 1: Literal listener
+task}\label{experiment-1-literal-listener-task}
 
@@
 \begin{figure}[t]
-\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1a,b, 3a,b and 4]{Stimuli for Experiments 1a,b, 3a,b and 4.}\label{fig:allScalesTable}
+\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1, 2, and 3]{Stimuli for Experiments 1, 2, and 3}\label{fig:allScalesTable}
 \end{figure}
@@
 
-\caption[(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1a (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 1b (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 
-Experiment 1a and 1b were conducted to approximate literal listener
-semantic distributions \(p_{L_0}(m \mid u)\) (Experiment 1a) and
-pragmatic judgments \(p_{L_1}(m \mid u)\) (Experiment 1b) for five pairs
-of scalar items taken from Tiel (2014). Scales and alternative
-utterances are shown in Figure \ref{fig:allScalesTable}. Each pair of
-scalar items consists of a ``weaker'' term (e.g. ``some'') and a
-stronger term (e.g. ``all''). We begin with these classic members of the
-Horn scale (Horn, 1972) as a test of the hypothesis that these
-alternatives are all that is necessary to predict the strength of
-listeners' pragmatic inferences.
+Experiment 1 was conducted to approximate literal listener semantic
+distributions \(p_{L_0}(m \mid u)\) for five pairs of scalar items taken
+from Tiel (2014). We include three conditions in Experiment 1,
+corresponding to the sets of alternatives within a scale that
+participants were presented with: two alternatives (``entailment''),
+four alternatives, and five alternatives. The two-alternative entailment
+condition makes a test of the hypothesis that the two members of the
+classic Horn scale (Horn, 1972) are the only alternatives necessary to
+predict the strength of listeners' pragmatic inference. The four- and
+five-alternative conditions then add successively more alternatives to
+test whether including a larger number of alternatives will increase
+model
+fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
 
@@
 
-We recruited 30 participants from Amazon Mechanical Turk (AMT) for
-Experiment 1a; two participants were excluded because they reported
-having a native language other than English for a final sample of 28
-participants. We recruited 50 for Experiment 1b, also from AMT, and data
-for 7 participants were excluded after participants either failed to
-pass two training trials or reported a non-English native language,
-leaving a total sample of 43 participants.
+In each condition we recruited 30 participants from Amazon Mechanical
+Turk (AMT). In the two-alternative condition, two participants were
+excluded because they reported having a native language other than
+English for a final sample of 28 participants. In the four-alternative
+condition, six participants were excluded for either failing to pass two
+training trials a non-English native language, leaving a total sample of
+24 participants. In the five-alternative condition, there were no data
+exclusions due to training failures or native language requirements,
+leaving a total sample of 30 participants.
 
@@
 
-Figure \ref{fig:stimuli_exp1} shows the experimental setup for both
-experiments. In Experiment 1a, the literal listener task, participants
-were presented with a target scalar item and a star rating (1--5 stars)
-and asked to judge the compatibility of the scalar item and star-rating.
-Compatibility was assessed through a binary ``yes/no'' response to a
-question of the form ``Do you think that the person thought the food was
-\_\_\_\_?" where a target scalar was presented in the blank. Each
-participant saw all scalar item and star rating combinations, in a
-random oder.
+Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
+Participants were presented with a target scalar item and a star rating
+(1--5 stars) and asked to judge the compatibility of the scalar item and
+star-rating. Compatibility was assessed through a binary ``yes/no''
+response to a question of the form ``Do you think that the person
+thought the food was \_\_\_\_?" where a target scalar was presented in
+the blank. Each participant saw all scalar item and star rating
+combinations for their particular condition (see Figure
+\ref{fig:allScalesTable}), in a random oder.
 
-In Experiment 1b, the pragmatic listener experiment, participants were
-presented with a one-sentence prompt containing a target scalar item
-such as ``Someone said they thought the food was \_\_\_\_\_.''
-Participants were then asked to generate a star rating representing the
-rating they thought the reviewer likely gave. Each participant was
-presented with all scalar items in a random order.
+The two-alternatives condition included only the scalar pairs from Tiel
+(2014). The four-alternatives condition included the two scalar items
+plus the top two alternatives generated for each scalar family by
+participants in Experiment 2. The five-alternatives condition included
+the four previous items plus one more ``neutral'' item chosen from those
+alternatives generated in Experiment 2.
 
@@
 
-Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions obtained
-in Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
-variation in semantic judgments between scalar families in all
-Experiments. For example, compatibility judgments for ``memorable'' and
-``forgettable'' are more similar than those for ``good / excellent'' or
-``liked / loved''. We will address distributional similarity across the
-studies in later sections.
+Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions for the
+three conditions. Several trends are visible. First, in each scale, the
+alternatives spanned the star scale, such that there were alternatives
+that were highly compatible with both the lowest and highest numbers of
+stars. Second, there was clear variability between scalar families. For
+example, compatibility judgments for the top items in the ``memorable /
+unforgettable'' scale were more similar than those for ``good /
+excellent'' or ``liked / loved.'' Finally, there was substantial
+consistency in ratings for items that were repeated across experiments,
+suggesting that this paradigm elicited stable judgments from
+participants.
 
-\section{Experiment 2: What are the
-alternatives?}\label{experiment-2-what-are-the-alternatives}
+\section{Experiment 2: Alternative
+Elicitation}\label{experiment-2-alternative-elicitation}
 
-In Experiment 1 we obtained literal semantic compatibility and pragmatic
-judgments for five pairs of scalar terms. We would like to extend the
-scale descriptions for each of these pairs to include other plausible
-alternatives. We chose to take an empirical approach rather than assign
-alternatives arbitrarily. We adopted a modified cloze task, inspired by
-Experiment 2 in van Tiel (2014) and asked participants to generate
-alternatives for us.
+To elicit empirical alternatives for the scales we used in Experiment 1,
+we adopted a modified cloze task inspired by Experiment 2 of Tiel
+(2014).
 
@@
 
-Using Amazon's Mechanical Turk, 30 workers were paid \$0.20 to
-participate. All participants were native English speakers and naive to
-the purpose of the experiment.
+We recruited 30 workers on AMT. All participants were native English
+speakers and naive to the purpose of the experiment.
 
@@
 entailment set embedded in a sentence such as, ``In a recent restaurant
-review someone said they thought they the food was \_\_\_\_" with a
+review someone said they thought they the food was \_\_\_\_," with a
 target scalar presented in the ``\_\_\_\_." Participants were then asked
@@
 they'd felt differently about the food, what other words could they have
-used instead of \_\_\_\_\_?'' and asked to generate three unique
-alternatives.
+used instead of \_\_\_\_\_?'' They were prompted to generate three
+unique alternatives.
 
@@
 
-Figure 3 plots the combined counts of alternatives generated for the
-scalar items ``liked'' and ``loved.'' Alternative distributions for the
-other scalar pairs (e.g.. ``good/excellent'',
-``memorable/unforgettable'') were similarly long-tailed, however the
-size and content of the alternate sets were diverse. (SOMETHING MORE
-MORE FORMAL HERE???)
-
 \begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
+\captionsetup{width=0.8\textwidth}\begin{figure}[t]
 
@@
 \caption[Caption goes here]{Caption goes here}\label{fig:exp2_altsPlot_likedLoved}
-\end{figure*}
+\end{figure}
 \end{CodeChunk}
 
-\section{Experiment 3a,b: Incorporating top
-alternatives}\label{experiment-3ab-incorporating-top-alternatives}
+Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar
+items ``liked'' and ``loved'' (combined). Alternative distributions for
+the other scalar pairs (e.g.. ``good/excellent'',
+``memorable/unforgettable'') were similarly long-tailed.
 
-In Experiment 1a,b we measured literal semantics and pragmatic judgments
-for Entailment scales. In Experiment 2, we asked participants to
-generate plausible alternatives to these items. In Experiments 3a,b we
-use the same experimental design for both literal semantics and
-pragmatic judgment tasks, however we now expand the set of scalar items
-to include the original Entailment pairs from Experiments 1a,b with the
-top two alternatives generated for each scalar family by participants in
-Experiment 2. The orange colored items in table 1 denote additional
-scalar items added in Experiments 3a,b.
+\section{Experiment 3: Pragmatic
+Listener}\label{experiment-3-pragmatic-listener}
+
+In Experiment 3, we asked participants to make pragmatic listener
+judgements.
+
+CONDITIONS
 
@@
 
-Participants for both studies were recruited on Amazon Mechanical Turk
-and paid \$0.20 for their participation. Thirty participants were
-recruited for Experiment 3a (Literal Listener task). Data for six
-participants was thrown out after participants either failed to pass two
-training trials or were not native English speakers, leaving a total
-sample of 24 participants.
-
-Fifty participants were recruited for Experiment 3b (Pragmatic Listener
-task). Data for five participants was thrown out after participants
-either failed to pass two training trials or were not native English
-speakers, leaving a total sample of 45 participants.
+We recruited 150 participants from AMT, 50 for each condition. Data for
+7 participants in the two-alternative condition were excluded after
+participants either failed to pass two training trials or reported a
+non-English native language, leaving a total sample of 43 participants.
+In the four-alternative condition, data from five participants was
+thrown out after participants either failed to pass two training trials
+or were not native English speakers, leaving a total sample of 45
+participants.
 
@@
 
-The procedure of Experiments 3a,b follow the same form as Experiments
-1a,b with the expanded set of target scalar items.
+Participants were presented with a one-sentence prompt containing a
+target scalar item such as ``Someone said they thought the food was
+\_\_\_\_\_.'' Participants were then asked to generate a star rating
+representing the rating they thought the reviewer likely gave. Each
+participant was presented with all scalar items in a random order. The
+experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
 
@@
 
-Run glmer() here:
+\section{Model Results}\label{model-results}
 
-To test whether literal listener compatibility judgments differed
-between Experiment 1a and 3a we ran a mixed effects model, regressing
-responses to the binary compatibility measure on scale, degree, and
-Experiment with random effects by subject. Results indicate (\ldots{})
-
-Run elmer() here:
-
-To test whether pragmatic judgments differed between Experiments 1b and
-3b we ran a mixed effects model, regressing star-rating selections on
-scale, scalar item and Experiment with random effects by subject.
-Results indicate.
-
-While conducting our analysis we realized that our literal semantic
-distributions for each scalar family were roughly split between two
-negative valenced items and two positively valenced items while neutral
-alternatives appeared to be excluded. (This pattern was true of all the
-scalar families, except for ``some ~all'' in which the top two
-alternatives were positive valenced ``most'' and negative valenced
-``none''.) In Experiment 4, we explore the addition of a neutrally
-valenced scalar alternative for each scalar family.
-
-\section{Experiment 4: Full scales - adding a neutral
-alternative}\label{experiment-4-full-scales---adding-a-neutral-alternative}
-
-In Experiment 4, we continue to extend the alternative sets, each by one
-additional scalar item. While we simply took the top two alternatives
-generated in Experiment 2 for the additional alternatives in Experiments
-3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
-item from among the alternatives generated in Experiment 2. The idea was
-to simulate a ``full'' set of alternatives, with negative, neutral and
-positive valenced items for each scalar family. The purple colored items
-in Table 1 denote additional scalar items added in Experiments 4.
-
-\subsection{Participants}\label{participants-3}
-
-Thirty participants were recruited on Amazon Mechanical Turk and paid
-\$0.20 for their participation. There were no data exclusions due to
-training failures or native language requirements, leaving a total
-sample of thirty participants, all native English speakers, naive to the
-purpose of the experiment.
-
-\subsection{Procedure}\label{procedure-1}
-
-The procedure of Experiment 4 follow the same form as Experiments 1a and
-3a with the addition of a neutrally valence scalar item.
-
-\subsection{Results and Discussion}\label{results-and-discussion-3}
-
-Distributions for neutrally valenced scalar did appear fairly Gaussian,
-occupying a literal semantic previously unoccupied by the other
-alternatives.
-
-Run glmer() here:
-
-To test whether literal listener compatibility judgments differed
-between Experiment 1a and 3a we ran a mixed effects model, regressing
-responses to the binary compatibility measure on scale, degree, and
-Experiment with random effects by subject. Results indicate (\ldots{})
-
-Run elmer() here:
-
-To test whether pragmatic judgments differed between Experiments 1b and
-3b we ran a mixed effects model, regressing star-rating selections on
-scale, scalar item and Experiment with random effects by subject.
-Results indicate.
-
-\section{Model Runs}\label{model-runs}
-
-Using literal semantic data from Experiments 1a, 3a and 4 we conducted
-three simulations with our model. Each simulation used the specific
-literal semantic data to specify the scale representation available to
-our model. The ``entailment'' model used only the original pair of
-scalar items pulled from van Tiel (2014). These data were measured in
+Using literal semantic data from Experiment 1 we conducted three
+simulations with our model. Each simulation used the specific literal
+semantic data to specify the scale representation available to our
+model. The ``entailment'' model used only the original pair of scalar
+items pulled from van Tiel (2014). These data were measured in
 Experiment 1a. The ``Top two'' model extended the original set of

### 2016-01-24 Paper/Paper.Rmd
minor spelling tweaks, commented out library(langcog) - not compatibile with R version 3.2.3 - only impacts solorazied ggplot coloring

@@
 library(grid)
-library(langcog)
+# library(langcog)
 ```
@@
 For example, listeners  commonly enrich the meaning of the scalar item "some" to "some but not all" in sentences like "Bob ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
-These inferences, called _scalar implicatures_, have been an important test case for understnading pragmatic inferences more generally.
+These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
 A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives [@grice1975].
@@
 In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions.
-Surprisingly, along with weighting "one" highly (a conclusion that was suppored by the empirical work),the best-fitting model assigned substantial weight to "none" as an alternative.
+Surprisingly, along with weighting "one" highly (a conclusion that was suppored by the empirical work), the best-fitting model assigned substantial weight to "none" as an alternative.
 This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g.
-"one" entails "some" even if it is not classically considered to be part of the scale scale).
+"one" entails "some" even if it is not classically considered to be part of the scale).
 
@@
 
-This model of the pragmatic speaker is consistent with a speaker who choses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:
+This model of the pragmatic speaker is consistent with a speaker who chooses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:
 
@@
 The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2.
+See Figure 1 for the complete list of alternatives used in each condition.
 
@@
   ylab("Proportion Judgments") + 
-  scale_colour_solarized() + 
+  # scale_colour_solarized() + 
   theme_bw() + 
@@
 
-To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 2 of @vantiel2014.
+To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 3 of @vantiel2014.
 
@@
 
-Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the "\____." Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.
+Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
+Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.
 

### 2016-01-24 Paper/Paper.tex
minor spelling tweaks, commented out library(langcog) - not compatibile with R version 3.2.3 - only impacts solorazied ggplot coloring

@@
 \usepackage{float}
-\usepackage{caption}
 
@@
 called \emph{scalar implicatures}, have been an important test case for
-understnading pragmatic inferences more generally. A Gricean account of
+understanding pragmatic inferences more generally. A Gricean account of
 this phenomena assumes listeners reason about the meaning the speaker
@@
 weighting ``one'' highly (a conclusion that was suppored by the
-empirical work),the best-fitting model assigned substantial weight to
+empirical work), the best-fitting model assigned substantial weight to
 ``none'' as an alternative. This finding was especially surprising
@@
 ``some'' even if it is not classically considered to be part of the
-scale scale).
+scale).
 
@@
 This model of the pragmatic speaker is consistent with a speaker who
-choses words to maximize the utility of an utterance in context (Frank
+chooses words to maximize the utility of an utterance in context (Frank
 \& Goodman, 2012), where utility is operationalized as the informativity
@@
 \begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
+\begin{figure*}[t]
 
@@
 the four previous items plus one more ``neutral'' item chosen from those
-alternatives generated in Experiment 2.
+alternatives generated in Experiment 2. See Figure 1 for the complete
+list of alternatives used in each condition.
 
@@
 To elicit empirical alternatives for the scales we used in Experiment 1,
-we adopted a modified cloze task inspired by Experiment 2 of Tiel
+we adopted a modified cloze task inspired by Experiment 3 of Tiel
 (2014).
@@
 review someone said they thought they the food was \_\_\_\_," with a
-target scalar presented in the ``\_\_\_\_." Participants were then asked
-to generate plausible alternatives by responding to the question, ``If
+target scalar presented in the blank. Participants were then asked to
+generate plausible alternatives by responding to the question, ``If
 they'd felt differently about the food, what other words could they have
@@
 \begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure}[t]
+\begin{figure}[t]
 

### 2016-01-25 models/RSA_alternativeCostFormulation.Rmd
fixed correct speaker.lhd3 call (to speaker.inf3) and handling 0 in denom case for Exp8 literal listener with compliance

@@
 speaker.inf3 = function(d, alpha, cost = 0) {
+  if (d == 0) return(0)
   exp(-1 * alpha * (-log(d) - cost))
@@
                             function(i) {
-                              speaker.inf(m[[allDegrees[i]]][currRating], alpha,
+                              speaker.inf3(m[[allDegrees[i]]][currRating], alpha,
                                           subset(costs, degree == allDegrees[i])$cost)}
                           )))
+  if (normalize == 0) return(0)
   return(numerator / normalize)
@@
 #                             newCount = rep(0.0, 5), stringsAsFactors = FALSE)
-emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
-                            newCount = rep(0.0, 4), stringsAsFactors = FALSE)
-emptyCosts2 <- data.frame(degree = c("low", "hi"),
-                            newCount = rep(0.0, 2), stringsAsFactors = FALSE)
+# emptyCosts4 <- data.frame(degree = c("low2", "low1","hi2", "hi1"),
+#                             newCount = rep(0.0, 4), stringsAsFactors = FALSE)
+# emptyCosts2 <- data.frame(degree = c("low", "hi"),
+#                             newCount = rep(0.0, 2), stringsAsFactors = FALSE)
 salienceCosts5 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/saliences5.csv")
@@
 speakerL08 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
+speakerL08 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8Compliance.csv")
 # Listener
@@
 
-Run complte analyses and output to csv
+Run complete analyses and output to csv
 ```{r}
 # Run analyses
-symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, salienceCosts5, numAlts = 5)
+symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, emptyCosts5, numAlts = 5)
 symmetricScalerun[[4]]
-negAltsRun <- completeModelRun(speakerL10, listener, unifPriors, salienceCosts4, numAlts = 4)
+negAltsRun <- completeModelRun(speakerL10, listener, unifPriors, emptyCosts4, numAlts = 4)
 negAltsRun[[4]]
-entailmentRun <- completeModelRun(speakerL08, listener, unifPriors, salienceCosts2, numAlts = 2)
+entailmentRun <- completeModelRun(speakerL08, listener, unifPriors, emptyCosts2, numAlts = 2)
 entailmentRun[[4]]
@@
 
-#write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
+# write.csv(modelRunData, "~/Desktop/Projects/scalar_implicature/models/model_data/allModelRuns.csv")
 ```

### 2016-01-26 analysis/BetweenExpDifferences.Rmd
initial between experiment tests for literal listener data

---
title: "BetweenExpDifferences"
author: "Ben Peloquin"
date: "January 25, 2016"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---

```{r}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/analysis")
library(rjson)
library(jsonlite)
library(tidyr)
library(dplyr)
library(lme4)
library(lmerTest)
```

# Literal Listener Data

## Get all L0 listener data
```{r}

# readLiteralListenerData()
# filesPath :: path to directory with .json files ("../production-results/e8/")
readLiteralListenerData <- function(filesPath) {
  files <- dir(filesPath, pattern = "*.json")
  dRaw <- data.frame()

  for (f in files) {
    jf <- paste(filesPath, f, sep="")
    jd <- fromJSON(paste(readLines(jf), collapse=""))
    id <- data.frame(workerid = jd$WorkerId,
                     scale = jd$answers$data$scale,
                     degree = jd$answers$data$degree,
                     stars = jd$answers$data$manipulation_level,
                     judgment = as.numeric(jd$answers$data$judgment),
                     language = jd$answers$data$language)
    dRaw <- bind_rows(dRaw, id)
  }
  dRaw
}

e8 <- readLiteralListenerData("../production-results/e8/")
e10 <- readLiteralListenerData("../production-results/e10/")
e12 <- readLiteralListenerData("../production-results/e12/")
```

## Data cleaning and combine
```{r}
# workerid as factor
e8$workerid <- as.factor(e8$workerid)
e8$exp <- "e8"
e10$workerid <- as.factor(e10$workerid)
e10$exp <- "e10"
e12$workerid <- as.factor(e12$workerid)
e12$exp <- "e12"

# compliance checks here

```

## Predictor factoring
```{r}
allL0Listener <- rbind(e8, e10, e12)
allL0Listener$exp <- as.factor(allL0Listener$exp)
allL0Listener$judgment <- as.numeric(allL0Listener$judgment)
levels(allL0Listener$stars) <- c("5", "1", "2", "3", "4")
str(allL0Listener)
```

## glmer()
```{r}
# glmer WITHOUT experiment and with random effect for subjects
glm1 <- glmer(judgment ~ scale + degree + stars + (1 | workerid), data = allL0Listener)
# glmer WITH experiment and with random effect for subjects
glm2 <- glmer(judgment ~ exp + scale + degree + stars + (1 | workerid), data = allL0Listener)
```

## Visulaziations
```{r}
ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
  geom_point(alpha = 0.5) +
  geom_jitter(width = 0.1, height = 0.1) +
  facet_wrap(~scale + exp)
```

## Model Comaprisons
```{r}
summary(glm2)
anova(glm1, glm2)
```
Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. However, it does look like there might be a significant difference

Inidivual words
```{r}
if (scale == "some_all") {
  if (exp == "10") {
    if (degree == "hi1") {
      d$word <- "most"
    } else if (degree == "low1") {
      d$word <- "some"
    } else 
  }
}

if (scale == "some_all") {
  switch(degree, "hi2" = "all", "hi1" = "most", "low1" = "some")
}
a <- data.frame(scale = rep("some_all", 4), degree = c("hi2", "hi1", "low1", "low2"), stringsAsFactors = FALSE)

for (d in a$degree) {
  print(d)
  a$word <- switch(d, "hi2" = "all", "hi1" = "most", "low1" = "some", "low2" = "none")  
}

a
```

### 2016-01-26 analysis/BetweenExpDifferences.Rmd
included specific scalr words, improved compliance checks

@@
 
-## Data cleaning and combine
+## Data org / cleaning
 ```{r}
@@
 # compliance checks here
+getCompliantWorkerIds <- function(df, exp) {
+  if (exp == "e8") {
+    compliant <- df %>% 
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training1", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = judgment[scale == "training1" & degree == "hi"] == 1 & 
+                  judgment[scale == "training1" & degree == "low"] == 0)
+  } else {
+    compliant <- df %>% 
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
+              (judgment[scale == "training1" & degree == "low1"] == 1))
+  }
+  # return compliant ids
+  compliant
+}
 
+# Append compliance booleans
+e8CompliantIds <- getCompliantWorkerIds(e8, "e8")
+e8 <- left_join(e8, e8CompliantIds)
+e10CompliantIds <- getCompliantWorkerIds(e10, "e10")
+e10 <- left_join(e10, e10CompliantIds)
+e12CompliantIds <- getCompliantWorkerIds(e12, "e12")
+e12 <- left_join(e12, e12CompliantIds)
 ```
 
-## Predictor factoring
+# Populate literal listener combined data
 ```{r}
-allL0Listener <- rbind(e8, e10, e12)
-allL0Listener$exp <- as.factor(allL0Listener$exp)
-allL0Listener$judgment <- as.numeric(allL0Listener$judgment)
-levels(allL0Listener$stars) <- c("5", "1", "2", "3", "4")
+# filter out compliance and training
+allL0Listener <- rbind(e8, e10, e12) %>%
+  subset(scale != "training1" & scale != "training2") %>%
+  filter(compliant == TRUE)
+
+allL0Listener$exp <- as.factor(allL0Listener$exp) ## exp. is factor
+allL0Listener$judgment <- as.numeric(allL0Listener$judgment) ## judgment is numeric
+levels(allL0Listener$stars) <- c("5", "1", "2", "3", "4") ## re-arrange stars
 str(allL0Listener)
+```
+
+## Add inidivual words
+```{r}
+lookupScalar <- function(degree, scale, exp) {
+  # some_all
+  if (scale == "some_all") {
+    if (exp == "e12") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "mid") return("some")
+      if (degree == "low1") return("little")
+      if (degree == "low2") return("none")
+    } else if (exp == "e10") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "low1") return("some")
+      if (degree == "low2") return("none")
+    } else { ## must be exp 8
+      if (degree == "hi") return("all")
+      if (degree == "low") return("some")
+    }
+  # liked_loved
+  } else if (scale == "liked_loved") {
+    if (degree == "hi1" | degree == "hi") return("loved")
+    if (degree == "hi2" | degree == "low") return("liked")
+    if (degree == "mid") return("indifferent")
+    if (degree == "low1") return("disliked")
+    if (degree == "low2") return("hated")
+  # good_excellent
+  } else if (scale == "good_excellent") {
+    if (degree == "hi1" | degree == "hi") return("excellent")
+    if (degree == "hi2" | degree == "low") return("good")
+    if (degree == "mid") return("okay")
+    if (degree == "low1") return("bad")
+    if (degree == "low2") return("horrible")
+  # paltable_delicious
+  } else if (scale == "palatable_delicious") {
+    if (degree == "hi1" | degree == "hi") return("delicious")
+    if (degree == "hi2" | degree == "low") return("palatable")
+    if (degree == "mid") return("mediocre")
+    if (degree == "low1") return("gross")
+    if (degree == "low2") return("disgusting")
+  # memorable_unforgettable
+  } else if (scale == "memorable_unforgettable") {
+    if (degree == "hi1" | degree == "hi") return("unforgettable")
+    if (degree == "hi2" | degree == "low") return("memorable")
+    if (degree == "mid") return("ordinary")
+    if (degree == "low1") return("bland")
+    if (degree == "low2") return("forgettable")
+  }
+  NA
+}
+
+allL0Listener$word <- as.factor(with(allL0Listener, mapply(lookupScalar, degree, scale, exp)))
 ```
@@
 ```{r}
+# fix contrasts so we're comparing most disparate experimetns (e8 and e12)
+contrasts(allL0Listener$exp) <- cbind("e10" = c(1, 0, 0), "e8" = c(0, 0, 1))
+
 # glmer WITHOUT experiment and with random effect for subjects
-glm1 <- glmer(judgment ~ scale + degree + stars + (1 | workerid), data = allL0Listener)
+glm1 <- glmer(judgment ~ scale + word + stars + (1 | workerid), data = allL0Listener)
 # glmer WITH experiment and with random effect for subjects
-glm2 <- glmer(judgment ~ exp + scale + degree + stars + (1 | workerid), data = allL0Listener)
+glm2 <- glmer(judgment ~ exp + word + scale +  stars + (1 | workerid), data = allL0Listener)
 ```
 
-## Visulaziations
+## Visulaziations?
 ```{r}
-ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
-  geom_point(alpha = 0.5) +
-  geom_jitter(width = 0.1, height = 0.1) +
-  facet_wrap(~scale + exp)
+# ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
+#   geom_point(alpha = 0.5) +
+#   geom_jitter(width = 0.1, height = 0.1) +
+#   facet_wrap(~scale + exp)
 ```
@@
 Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. However, it does look like there might be a significant difference
-
-Inidivual words
-```{r}
-if (scale == "some_all") {
-  if (exp == "10") {
-    if (degree == "hi1") {
-      d$word <- "most"
-    } else if (degree == "low1") {
-      d$word <- "some"
-    } else 
-  }
-}
-
-if (scale == "some_all") {
-  switch(degree, "hi2" = "all", "hi1" = "most", "low1" = "some")
-}
-a <- data.frame(scale = rep("some_all", 4), degree = c("hi2", "hi1", "low1", "low2"), stringsAsFactors = FALSE)
-
-for (d in a$degree) {
-  print(d)
-  a$word <- switch(d, "hi2" = "all", "hi1" = "most", "low1" = "some", "low2" = "none")  
-}
-
-a
-```

### 2016-01-26 analysis/BetweenExpDifferences.Rmd
starting pragmatic listener data gathering

@@
 ```{r}
-
 # readLiteralListenerData()
+# -------------------------
 # filesPath :: path to directory with .json files ("../production-results/e8/")
@@
 Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. However, it does look like there might be a significant difference
+
+# Pragmatic listener data
+```{r}
+# readPragmaticListenerData()
+# -------------------------
+# filesPath :: path to directory with .json files ("../production-results/e8/")
+readPragmaticListenerData <- function(filesPath) {
+  files <- dir(filesPath, pattern = "*.json")
+  dRaw <- data.frame()
+
+  if (grepl("e6", filesPath)) {
+    for (f in files) {
+      jf <- paste(filesPath, f, sep="")
+      jd <- fromJSON(paste(readLines(jf), collapse=""))
+      id <- data.frame(workerid = jd$WorkerId, 
+                       scale = jd$answer$scale,
+                       degree = jd$answer$degree,
+                       stars = as.numeric(jd$answer$judgment),
+                       language = jd$answer$language)
+      dRaw <- bind_rows(dRaw, id)
+    }
+  } else if (grepl("e11", filesPath)) {
+    for (f in files) {
+    jf <- paste(filesPath, f, sep="")
+    jd <- fromJSON(paste(readLines(jf), collapse=""))
+    id <- data.frame(workerid = jd$WorkerId, 
+                     scale = jd$answer$data$scale,
+                     degree = jd$answer$data$degree,
+                     stars = as.numeric(jd$answer$data$judgment),
+                     language = jd$answer$data$language)
+    dRaw <- bind_rows(dRaw, id)
+    }
+  } else stop("Must enter 'e6' or 'e11' for exp")
+
+  dRaw
+}
+e6 <- readPragmaticListenerData("../production-results/e6/")
+e11 <- readPragmaticListenerData("../production-results/e11/")
+```

### 2016-01-26 analysis/BetweenExpDifferences.Rmd
ME models for both literal listener l0 and pragmatic listener l1

--- 2016-01-26 analysis/BetweenExpDifferences.Rmd
@@
 
-# Literal Listener Data
-
-## Get all L0 listener data
+# Functionality
+## read in literal listener data fn()
 ```{r}
-
 # readLiteralListenerData()
+# -------------------------
 # filesPath :: path to directory with .json files ("../production-results/e8/")
@@
 }
+```
 
+## read in Pragmatic listener data
+```{r}
+# readPragmaticListenerData()
+# -------------------------
+# filesPath :: path to directory with .json files ("../production-results/e8/")
+readPragmaticListenerData <- function(filesPath) {
+  files <- dir(filesPath, pattern = "*.json")
+  dRaw <- data.frame()
+
+  if (grepl("e6", filesPath)) {
+    for (f in files) {
+      jf <- paste(filesPath, f, sep="")
+      jd <- fromJSON(paste(readLines(jf), collapse=""))
+      id <- data.frame(workerid = jd$WorkerId, 
+                       scale = jd$answer$scale,
+                       degree = jd$answer$degree,
+                       stars = as.numeric(jd$answer$judgment),
+                       language = jd$answer$language)
+      dRaw <- bind_rows(dRaw, id)
+    }
+  } else if (grepl("e11", filesPath)) {
+    for (f in files) {
+    jf <- paste(filesPath, f, sep="")
+    jd <- fromJSON(paste(readLines(jf), collapse=""))
+    id <- data.frame(workerid = jd$WorkerId, 
+                     scale = jd$answer$data$scale,
+                     degree = jd$answer$data$degree,
+                     stars = as.numeric(jd$answer$data$judgment),
+                     language = jd$answer$data$language)
+    dRaw <- bind_rows(dRaw, id)
+    }
+  } else stop("Must enter 'e6' or 'e11' for exp")
+
+  dRaw
+}
+```
+
+## get compliant worker ids
+```{r}
+# getCompliantWorkerIds()
+# -----------------------
+# df  :: data frame for exp
+# exp :: experiment id 
+getCompliantWorkerIds <- function(df, exp) {
+  if (exp == "e8") {
+    compliant <- df %>% 
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training1", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = judgment[scale == "training1" & degree == "hi"] == 1 & 
+                  judgment[scale == "training1" & degree == "low"] == 0)
+  } else if (exp == "e10" | exp == "e12") {
+    compliant <- df %>% 
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
+              (judgment[scale == "training1" & degree == "low1"] == 1))
+  } else if (exp == "e6") {
+    compliant <- df %>%
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training1", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = stars[scale == "training1" & degree == "hi"] >= 4 &
+                  stars[scale == "training1" & degree == "low"] <= 2)
+  } else if (exp == "e11") {
+    compliant <- df %>%
+      filter(tolower(language) == "english") %>%
+      filter(grepl("training1", scale)) %>%
+      group_by(workerid) %>%
+      summarise(compliant = stars[scale == "training1" & degree == "hi2"] >= 4 &
+                  stars[scale == "training1" & degree == "low1"] <= 2)
+  } else stop("Entered a bad experiment id (e6, e8, e10, e11, e12")
+  # return compliant ids
+  compliant
+}
+```
+
+## get individual scalar items
+```{r}
+# lookupScalar()
+# --------------
+# degree :: scale degree ("hi", "low", "hi2" "h1", etc)
+# scale  :: "some_all", "good_excellent"...
+# exp    :: exp ide (e12, e8)
+lookupScalar <- function(degree, scale, exp) {
+  # some_all
+  if (scale == "some_all") {
+    if (exp == "e12") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "mid") return("some")
+      if (degree == "low1") return("little")
+      if (degree == "low2") return("none")
+    } else if (exp == "e10") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "low1") return("some")
+      if (degree == "low2") return("none")
+    } else { ## must be exp 8
+      if (degree == "hi") return("all")
+      if (degree == "low") return("some")
+    }
+  # liked_loved
+  } else if (scale == "liked_loved") {
+    if (degree == "hi1" | degree == "hi") return("loved")
+    if (degree == "hi2" | degree == "low") return("liked")
+    if (degree == "mid") return("indifferent")
+    if (degree == "low1") return("disliked")
+    if (degree == "low2") return("hated")
+  # good_excellent
+  } else if (scale == "good_excellent") {
+    if (degree == "hi1" | degree == "hi") return("excellent")
+    if (degree == "hi2" | degree == "low") return("good")
+    if (degree == "mid") return("okay")
+    if (degree == "low1") return("bad")
+    if (degree == "low2") return("horrible")
+  # paltable_delicious
+  } else if (scale == "palatable_delicious") {
+    if (degree == "hi1" | degree == "hi") return("delicious")
+    if (degree == "hi2" | degree == "low") return("palatable")
+    if (degree == "mid") return("mediocre")
+    if (degree == "low1") return("gross")
+    if (degree == "low2") return("disgusting")
+  # memorable_unforgettable
+  } else if (scale == "memorable_unforgettable") {
+    if (degree == "hi1" | degree == "hi") return("unforgettable")
+    if (degree == "hi2" | degree == "low") return("memorable")
+    if (degree == "mid") return("ordinary")
+    if (degree == "low1") return("bland")
+    if (degree == "low2") return("forgettable")
+  }
+  NA
+}
+```
+
+# Literal Listener Data
+
+## Get all L0 listener data
+```{r echo = FALSE, message = FALSE, warning = FALSE}
 e8 <- readLiteralListenerData("../production-results/e8/")
@@
 
-## Data cleaning and combine
+## Data org / cleaning / compliance checks
 ```{r}
@@
 
-# compliance checks here
-
+# Append compliance booleans
+e8CompliantIds <- getCompliantWorkerIds(e8, "e8")
+e8 <- left_join(e8, e8CompliantIds)
+e10CompliantIds <- getCompliantWorkerIds(e10, "e10")
+e10 <- left_join(e10, e10CompliantIds)
+e12CompliantIds <- getCompliantWorkerIds(e12, "e12")
+e12 <- left_join(e12, e12CompliantIds)
 ```
 
-## Predictor factoring
+## Populate literal listener combined data
 ```{r}
-allL0Listener <- rbind(e8, e10, e12)
+# filter out compliance and training
+allL0Listener <- rbind(e8, e10, e12) %>%
+  subset(scale != "training1" & scale != "training2") %>%
+  filter(compliant == TRUE)
+## exp :: factor
 allL0Listener$exp <- as.factor(allL0Listener$exp)
+## judgment :: numeric
 allL0Listener$judgment <- as.numeric(allL0Listener$judgment) 
-levels(allL0Listener$stars) <- c("5", "1", "2", "3", "4")
+allL0Listener$stars <- as.numeric(as.character(allL0Listener$stars)) / 20
 str(allL0Listener)
+```
+
+### Add inidivual words
+```{r}
+allL0Listener$word <- as.factor(with(allL0Listener, mapply(lookupScalar, degree, scale, exp)))
 ```
@@
 ```{r}
+# fix contrasts so we're comparing most disparate experimetns (e8 and e12)
+contrasts(allL0Listener$exp) <- cbind("e10" = c(1, 0, 0), "e8" = c(0, 0, 1))
+
 # glmer WITHOUT experiment and with random effect for subjects
-glm1 <- glmer(judgment ~ scale + degree + stars + (1 | workerid), data = allL0Listener)
+glm1 <- glmer(judgment ~ scale + stars + (1 | word) + (1 | workerid), data = allL0Listener)
 # glmer WITH experiment and with random effect for subjects
-glm2 <- glmer(judgment ~ exp + scale + degree + stars + (1 | workerid), data = allL0Listener)
+glm2 <- glmer(judgment ~ exp + scale +  stars + (1 | word) +  (1 | workerid), data = allL0Listener)
 ```
 
-## Visulaziations
+## Visulaziations?
 ```{r}
-ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
-  geom_point(alpha = 0.5) +
-  geom_jitter(width = 0.1, height = 0.1) +
-  facet_wrap(~scale + exp)
+# ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
+#   geom_point(alpha = 0.5) +
+#   geom_jitter(width = 0.1, height = 0.1) +
+#   facet_wrap(~scale + exp)
 ```
@@
 ```
-Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. However, it does look like there might be a significant difference
+Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. Also, exp is not a significant predictor in the ME model.
 
-Inidivual words
+# Pragmatic listener data
+
+## Get all L1 listener data
+```{r echo = FALSE, message = FALSE, warning = FALSE}
+e6 <- readPragmaticListenerData("../production-results/e6/")
+e11 <- readPragmaticListenerData("../production-results/e11/")
+```
+
+## Data org / cleaning / compliance checks
 ```{r}
-if (scale == "some_all") {
-  if (exp == "10") {
-    if (degree == "hi1") {
-      d$word <- "most"
-    } else if (degree == "low1") {
-      d$word <- "some"
-    } else 
-  }
-}
+# workerid as factor
+e6$workerid <- as.factor(e6$workerid)
+e6$exp <- "e6"
+e11$workerid <- as.factor(e11$workerid)
+e11$exp <- "e11"
 
-if (scale == "some_all") {
-  switch(degree, "hi2" = "all", "hi1" = "most", "low1" = "some")
-}
-a <- data.frame(scale = rep("some_all", 4), degree = c("hi2", "hi1", "low1", "low2"), stringsAsFactors = FALSE)
+# Append compliance booleans
+e6CompliantIds <- getCompliantWorkerIds(e6, "e6")
+e6 <- left_join(e6, e6CompliantIds)
+e11CompliantIds <- getCompliantWorkerIds(e11, "e11")
+e11 <- left_join(e11, e11CompliantIds)
+```
 
-for (d in a$degree) {
-  print(d)
-  a$word <- switch(d, "hi2" = "all", "hi1" = "most", "low1" = "some", "low2" = "none")  
-}
+## Populate pragmatic listener combined data
+```{r}
+# filter out compliance and training
+allL1Listener <- rbind(e6, e11) %>%
+  subset(scale != "training1" & scale != "training2") %>%
+  filter(compliant == TRUE)
+## exp :: factor
+allL1Listener$exp <- as.factor(allL1Listener$exp)
+str(allL1Listener)
+```
 
-a
+### Add inidivual words
+```{r}
+allL1Listener$word <- as.factor(with(allL1Listener, mapply(lookupScalar, degree, scale, exp)))
 ```
+
+## glmer()
+```{r}
+# glmer WITHOUT experiment and with random effect for subjects
+glm1 <- lmer(stars ~ scale + (1 | word) + (1 | workerid), data = allL1Listener)
+# glmer WITH experiment and with random effect for subjects
+glm2 <- lmer(stars ~ exp + scale + (1 | word) +  (1 | workerid), data = allL1Listener)
+```
+
+## Model Comaprisons
+```{r}
+summary(glm2)
+anova(glm1, glm2)
+```
+Looks like we dont' see a significant improvement in model fit when we include the fixed effect for experiment. Also, exp is not a significant predictor in the ME model.

### 2016-01-27 Paper/Paper.Rmd
changed literal semantics plot. have first version of pragmatic lisetner plot (only showing top scalar items

@@
 ```{r helpers}
+# lookupScalar()
+# --------------
+# degree :: scale degree ("hi", "low", "hi2" "h1", etc)
+# scale  :: "some_all", "good_excellent"...
+# exp    :: exp ide (e12, e8)
+lookupScalar <- function(degree, scale, exp) {
+  if (scale == "some_all") {
+    if (exp == "e12") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "mid") return("some")
+      if (degree == "low1") return("little")
+      if (degree == "low2") return("none")
+    } else if (exp == "e10" | exp == "e11") {
+      if (degree == "hi1") return("all")
+      if (degree == "hi2") return("most")
+      if (degree == "low1") return("some")
+      if (degree == "low2") return("none")
+    } else { ## must be exp 8
+      if (degree == "hi") return("all")
+      if (degree == "low") return("some")
+    }
+  # liked_loved
+  } else if (scale == "liked_loved") {
+    if (degree == "hi1" | degree == "hi") return("loved")
+    if (degree == "hi2" | degree == "low") return("liked")
+    if (degree == "mid") return("indifferent")
+    if (degree == "low1") return("disliked")
+    if (degree == "low2") return("hated")
+  # good_excellent
+  } else if (scale == "good_excellent") {
+    if (degree == "hi1" | degree == "hi") return("excellent")
+    if (degree == "hi2" | degree == "low") return("good")
+    if (degree == "mid") return("okay")
+    if (degree == "low1") return("bad")
+    if (degree == "low2") return("horrible")
+  # paltable_delicious
+  } else if (scale == "palatable_delicious") {
+    if (degree == "hi1" | degree == "hi") return("delicious")
+    if (degree == "hi2" | degree == "low") return("palatable")
+    if (degree == "mid") return("mediocre")
+    if (degree == "low1") return("gross")
+    if (degree == "low2") return("disgusting")
+  # memorable_unforgettable
+  } else if (scale == "memorable_unforgettable") {
+    if (degree == "hi1" | degree == "hi") return("unforgettable")
+    if (degree == "hi2" | degree == "low") return("memorable")
+    if (degree == "mid") return("ordinary")
+    if (degree == "low1") return("bland")
+    if (degree == "low2") return("forgettable")
+  }
+  NA
+}
+
 normedVec <- function(vec) vec / sum(vec)
@@
 speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
-speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
+# speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
+speakerE8 <- read.csv("../models/model_data/L0_e8Compliance.csv", stringsAsFactors = FALSE)
 # Experiments E6, E11: Pragmatic listener
@@
 
-```{r}
-listeners <- bind_rows(listenerE6 %>% mutate(expt = "1b"), 
-                      listenerE11 %>% mutate(expt = "3b"))
-zeros <- expand.grid(degree = c("low","hi"), 
-            scale = unique(listeners$scale), 
-            stars = 1:5, 
-            expt = c("1b","3b"))
-
-zlisteners <- full_join(listeners, zeros) %>%
-  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))
-
-# ggplot(zlisteners, 
-#        aes(x = stars, y = listener.p, col = degree, lty = expt)) + 
-#   geom_line() + 
-#   facet_grid(. ~ scale) + 
-#   theme_bw()
 # Humpty Dumpty Quote...
-```
 # Introduction
@@
 Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
-Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating.
+Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star rating.
 Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4.
 Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
 
-speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
-                      speakerE10 %>% mutate(expt = "3a"), 
-                      speakerE8 %>% mutate(expt = "1a"))
+speakers <- bind_rows(speakerE12 %>% mutate(expt = "e12"), 
+                      speakerE10 %>% mutate(expt = "e10"), 
+                      speakerE8 %>% mutate(expt = "e8"))
+speakers$scale <- as.factor(speakers$scale)
 
+speakers$word <- as.factor(with(speakers, mapply(lookupScalar, degree, scale, expt)))
+speakers$wordPlots <- factor(speakers$word, levels=c("excellent", "good", "okay", "bad", "horrible",
+                           "loved", "liked", "indifferent", "disliked", "hated",
+                           "unforgettable", "memorable", "ordinary", "bland", "forgettable",
+                           "delicious", "palatable", "mediocre", "gross", "disgusting",
+                           "all", "most", "some", "little", "none"))
+
+# change col = word and facet_grid(.~scale)
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
+       aes(x = stars, y = speaker.p, col = scale, lty = expt)) + 
   geom_line() + 
-  facet_grid(.~ scale) + 
+  # facet_grid(.~ scale) + 
+  facet_wrap(~wordPlots) +
   guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
@@
                                  title = "Experiment")) + 
-  xlab("Star Rating") +
-  ylab("Proportion Judgments") + 
+  xlab("star rating") +
+  ylab("Proportion compatible") + 
+  ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
   # scale_colour_solarized() + 
   theme_bw() +
-  theme(legend.position = "bottom",
+  theme(strip.text.x = element_text(size = 8),
+        legend.position = "bottom",
         legend.margin = unit(.02,"in"),
         legend.key = element_blank(), 
-        legend.key.size = unit(.1, "in"))
+        legend.key.size = unit(.1, "in"),
+        axis.text.x = element_text(size = 8),
+        axis.text.y = element_text(size = 6))
 ```
@@
   ylim(0, 52) + 
-  labs(x = "alternative", y = "counts") +
-  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
-  ylab("Proportion of responses")
+  labs(x = "Alternatives", y = "Counts") +
+  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
+  theme_bw() +
+  theme(strip.text.x = element_text(size = 8),
+        legend.position = "bottom",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
+        axis.text.y = element_text(size = 10))
 ```
@@
 These data were measured in Experiment 4.
+
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items.
+Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
+Each panel shows one scalar pair."}
+# Get zero's in data frame
+baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
+                     scale = c(rep("good_excellent", 6 * 5),
+                               rep("liked_loved", 6 * 5),
+                               rep("memorable_unforgettable", 6 * 5),
+                               rep("palatable_delicious", 6 * 5),
+                               rep("some_all", 6 * 5)),
+                     stars = rep(1:5, 30),
+                     combine = rep(TRUE, 150))
+listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
+                      listenerE11 %>% mutate(expt = "e11"))
+listeners <- left_join(baseDf, listeners) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
+         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
+listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
+listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
+                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
+                               TRUE, ifelse(scale != "some_all" & (
+                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
+                                 TRUE, FALSE)))
+listeners$scalarType <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
+
+# Plot pragmatic listener data here
+ggplot(subset(listeners, plotThis == TRUE),
+       aes(x = stars, y = listener.p, col = scalarType, lty = expt)) + 
+  geom_line() + 
+  facet_grid(.~ scale) + 
+  ggtitle("Pragmatic listener judgments") +
+  ylab("Proportion of stars selected") +
+  xlab("Star rating") +
+  theme_bw() +
+  theme(strip.text.x = element_text(size = 6),
+        legend.position = "bottom",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
+        legend.title = element_text(size = 10),
+        legend.text = element_text(size = 8))
+```
 

### 2016-01-27 Paper/Paper.tex
changed literal semantics plot. have first version of pragmatic lisetner plot (only showing top scalar items

@@
 \end{abstract}
+
+\section{Humpty Dumpty Quote\ldots{}}\label{humpty-dumpty-quote}
 
@@
 (1--5 stars) and asked to judge the compatibility of the scalar item and
-star-rating. Compatibility was assessed through a binary ``yes/no''
+star rating. Compatibility was assessed through a binary ``yes/no''
 response to a question of the form ``Do you think that the person
@@
 
+{\centering \includegraphics{figs/exp2Plots-1}
+
+}
+
+\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items.
+Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
+Each panel shows one scalar pair.}\label{fig:exp2Plots}
+\end{figure*}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
 {\centering \includegraphics{figs/performancePlots-1}

### 2016-01-27 Paper/Paper.Rmd
got xtable working, should modify? more than one table?

@@
 library(grid)
+library(xtable)
 # library(langcog)
@@
 
-```{r performancePlots, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
+```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
 Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.
@@
   mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
+
+tableCors <- plotData  %>%
+  select(cors, study, Experiment) %>%
+  unique() %>%
+  mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
+  spread(Experiment, cors)
+
+names(tableCors) <- c("r", "model", "Experiment")
+tableCors <- tableCors[c(1, 3, 2),]
+tab <- xtable(tableCors)
+print(tab, type="latex")
 
@@
   geom_line(aes(y = preds), lty = 4)
-fullRepresentationFit
+# fullRepresentationFit
 # gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))

### 2016-01-27 Paper/Paper.tex
got xtable working, should modify? more than one table?

@@
 
-\begin{CodeChunk}
-\begin{figure*}[t]
+\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Tue Jan
+26 20:47:20 2016
 
-{\centering \includegraphics{figs/performancePlots-1}
-
-}
-
-\caption[The left panel shows improved model fit as scale representations are enriched with more scalar items]{The left panel shows improved model fit as scale representations are enriched with more scalar items.
-Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.
-The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b.}\label{fig:performancePlots}
-\end{figure*}
-\end{CodeChunk}
+\begin{table}[ht]
+\centering
+\begin{tabular}{rlrr}
+  \hline
+ & r & model & Experiment \\ 
+  \hline
+1 & Entailment & 0.54 & 0.57 \\ 
+  3 & Top\_two & 0.84 & 0.90 \\ 
+  2 & Full & 0.86 & 0.90 \\ 
+   \hline
+\end{tabular}
+\end{table}
 

### 2016-01-27 analysis/BetweenExpDifferences.Rmd
outputting raw literal listener and pramatic listener combined data sets

@@
 
+### Save literalListenerData
+```{r}
+# write.csv(allL0Listener, "/Users/benpeloquin/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
+```
+
 ## glmer()
@@
 ```{r}
-# ggplot(allL0Listener, aes(x=stars, y=judgment, col=degree)) + 
-#   geom_point(alpha = 0.5) +
-#   geom_jitter(width = 0.1, height = 0.1) +
-#   facet_wrap(~scale + exp)
 ```
@@
 
+### Save literalListenerData
+```{r}
+# write.csv(allL1Listener, "/Users/benpeloquin/Desktop/Projects/scalar_implicature/models/model_data/RawPragmaticListenerCombined.csv")
+```
+
 ## glmer()

### 2016-01-27 Paper/Paper.Rmd
new opening sentence and convered scalar items to italics from quotes

@@
 
-# Experiments E8, E10, E12: Literal listener
-# ------------------------------------------
+# Non-summarized data
+# -------------------
+allLiteralListener <- read.csv("../models/model_data/RawLiteralListenerCombined.csv", 
+                               stringsAsFactors = FALSE)
+allPragmaticListener <- read.csv("../models/model_data/RawPragmaticListenerCombined.csv", 
+                               stringsAsFactors = FALSE)
+
+# Model run data
+# --------------
+# Speakers ::
 speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
@@
 speakerE8 <- read.csv("../models/model_data/L0_e8Compliance.csv", stringsAsFactors = FALSE)
-# Experiments E6, E11: Pragmatic listener
-# ---------------------------------------
+# Listeners ::
 listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
 listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
+
+# \begin{center}
+# \textit{``When I choose a word," Humpty Dumpty said, in a rather scornful tone, ``it means just what I choose it to mean - neither more nor less"- Lewis Caroll, Through the Looking-Glass}
+# \end{center}
 ```
 
-# Humpty Dumpty Quote...
 # Introduction
 
-Successful communication requires listeners to make pragmatic inferences that go beyond the literal semantic content of speakers' utterances.
-For example, listeners  commonly enrich the meaning of the scalar item "some" to "some but not all" in sentences like "Bob ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
+How much of what we mean comes from the words that go unsaid?
+As listeners, the ability to enrich meaning in context is an indispensible component of succesful communication.
+For example, listeners  commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
-A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as "all") and b) the relative informativity of using such alternatives [@grice1975].
-According to this account, a listener will infer that the speaker must have intended that Bob did not eat "all" the cookies because it would have been *underinformative* for the speaker to use "some" when "all" could have been used.
+A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
+According to this account, a listener will infer that the speaker must have intended that Alice did not eat *all* the cookies because it would have been *underinformative* for the speaker to use *some* when *all* could have been used.
 
-But what are the alternatives that should be considered in this computation more generally?
+But how much of the meaning of *some* comes from the alternatives that weren't chosen?
+Put differently, what are the alternatives that should be considered in this computation more generally?
 Under classic accounts of implicature, listeners consider only those words whose meaning would entail the word that is actually sent [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000].
-For example, because "all" entails "some," and hence is a "stronger" meaning, "all" should be considered as an alternative to "some" in implicatures.
+For example, because *all* entails *some*, and hence is a "stronger" meaning, *all* should be considered as an alternative to *some* in implicatures.
 Similar scales exist for non-quantifier scales, e.g.
-"love" entails "like" (and hence "I liked the movie" implicates that I didn't love it).
+*loved* entails *liked* (and hence "I liked the movie" implicates that I didn't love it).
 
 Recent empirical evidence has called into question whether entailment scales are all that is necessary for understanding scalar implicature.
-For example, @degen2015  demonstrated that the scalar item "some" was judged less appropriate when exact numbers were seen as viable alternatives.
-And in a different paradigm, @vantiel2014 found converging evidence that "some" was judged to be atypical for small quantities.
-These data provide indirect evidence about a broader set of alternatives: since "some" is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words "one" and "two") reduced the felicity of "some" via a pragmatic inference.
+For example, @degen2015  demonstrated that the scalar item *some* was judged less appropriate when exact numbers were seen as viable alternatives.
+And in a different paradigm, @vantiel2014 found converging evidence that *some* was judged to be atypical for small quantities.
+These data provide indirect evidence about a broader set of alternatives: since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*) reduced the felicity of *some* via a pragmatic inference.
 
@@
 RSA models frame language understanding as a special case of social cognition, in which listeners and speakers reason recursively about one another's goals.
-In the case of scalar implicature, a listener makes a probabilistic inference about what the speaker's most likely communicative goal was, given that she picked the quantifier "some" rather than the stronger quantifier "all." In turn, the speaker reasons about what message would best convey her intended meaning to the listener, given that he is reasoning in this way.
+In the case of scalar implicature, a listener makes a probabilistic inference about what the speaker's most likely communicative goal was, given that she picked the quantifier *some* rather than the stronger quantifier *all*.
+In turn, the speaker reasons about what message would best convey her intended meaning to the listener, given that he is reasoning in this way.
 This recursion is grounded in a "literal" listener who reasons only according to the basic truth-functional semantics of the language.
@@
 In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions.
-Surprisingly, along with weighting "one" highly (a conclusion that was suppored by the empirical work), the best-fitting model assigned substantial weight to "none" as an alternative.
+Surprisingly, along with weighting *one* highly (a conclusion that was suppored by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative.
 This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g.
-"one" entails "some" even if it is not classically considered to be part of the scale).
+*one* entails *some* even if it is not classically considered to be part of the scale).
 
@@
 Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g.
-"liked/loved," or "palatable/delicious.").
+*liked/loved,* or *palatable/delicious.*).
 Making use of some of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
@@
 Second, there was clear variability between scalar families.
-For example, compatibility judgments for the top items in the "memorable / unforgettable" scale were more similar than those for "good / excellent" or "liked / loved." Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
+For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved.* Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
 
@@
 ## Results and Discussion
-
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
-
-# Subset alternatives for demo
-plotData <- alternativesData %>%
-  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
-  mutate(prop = n / sum(n))
-
-# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
-ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
-  geom_bar(stat="identity") + 
-  ylim(0, 52) + 
-  labs(x = "Alternatives", y = "Counts") +
-  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
-  theme_bw() +
-  theme(strip.text.x = element_text(size = 8),
-        legend.position = "bottom",
-        legend.margin = unit(.02,"in"),
-        legend.key = element_blank(), 
-        legend.key.size = unit(.1, "in"),
-        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
-        axis.text.y = element_text(size = 10))
-```
-
-Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items "liked" and "loved" (combined).
-Alternative distributions for the other scalar pairs (e.g..
-"good/excellent", "memorable/unforgettable") were similarly long-tailed.
-
-# Experiment 3: Pragmatic Listener
-
-In Experiment 3, we asked participants to make pragmatic listener judgements.
-
-CONDITIONS
-
-## Participants
-
-We recruited 150 participants from AMT, 50 for each condition.
-Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
-In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
-
-## Procedure
-
-Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
-Each participant was presented with all scalar items in a random order.
-The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
-
-## Results and Discussion
-
-# Model Results
-
-Using literal semantic data from Experiment 1 we conducted three simulations with our model.
-Each simulation used the specific literal semantic data to specify the scale representation available to our model.
-The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014).
-These data were measured in Experiment 1a.
-The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2.
-These data were measured in Experiment 3a.
-The "Full" model included the full set of alternatives, including a neutral valenced alternative.
-These data were measured in Experiment 4.
 
@@
 ```
+
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
+
+# Subset alternatives for demo
+plotData <- alternativesData %>%
+  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
+  mutate(prop = n / sum(n))
+
+# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
+ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
+  geom_bar(stat="identity") + 
+  ylim(0, 52) + 
+  labs(x = "Alternatives", y = "Counts") +
+  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
+  theme_bw() +
+  theme(strip.text.x = element_text(size = 8),
+        legend.position = "bottom",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
+        axis.text.y = element_text(size = 10))
+```
+
+Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items *liked* and *loved* (combined).
+Alternative distributions for the other scalar pairs (e.g..
+*good/excellent*, *memorable/unforgettable*) were similarly long-tailed.
+
+# Experiment 3: Pragmatic Listener
+
+Experiment 3 was conducted to measure pragmatic judgments $p_{L_1}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
+We include two conditions in Experiment 3.
+In the two-alternative entailment condition, participants made judgments for items included in the entailment scales.
+In the four-alternative condition, participants made pragmatic judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2.
+Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
+\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+
+## Participants
+
+We recruited 100 participants from AMT, 50 for each condition.
+Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
+In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
+
+## Procedure
+
+Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
+Each participant was presented with all scalar items in a random order.
+The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
+
+## Results and Discussion
+
+# Model Results
+
+Using literal semantic data from Experiment 1 we conducted three simulations with our model.
+Each simulation used the specific literal semantic data to specify the scale representation available to our model.
+The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014).
+These data were measured in Experiment 1a.
+The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2.
+These data were measured in Experiment 3a.
+The "Full" model included the full set of alternatives, including a neutral valenced alternative.
+These data were measured in Experiment 4.
 

### 2016-01-27 Paper/Paper.tex
new opening sentence and convered scalar items to italics from quotes

@@
 
-\section{Humpty Dumpty Quote\ldots{}}\label{humpty-dumpty-quote}
-
 \section{Introduction}\label{introduction}
 
-Successful communication requires listeners to make pragmatic inferences
-that go beyond the literal semantic content of speakers' utterances. For
-example, listeners commonly enrich the meaning of the scalar item
-``some'' to ``some but not all'' in sentences like ``Bob ate some of the
-cookies'' (Grice, 1975; Horn, 1984; Levinson, 2000). These inferences,
-called \emph{scalar implicatures}, have been an important test case for
-understanding pragmatic inferences more generally. A Gricean account of
-this phenomena assumes listeners reason about the meaning the speaker
-intended by incorporating knowledge about a) alternative scalar items a
-speaker could have used (such as ``all'') and b) the relative
-informativity of using such alternatives (Grice, 1975). According to
-this account, a listener will infer that the speaker must have intended
-that Bob did not eat ``all'' the cookies because it would have been
-\emph{underinformative} for the speaker to use ``some'' when ``all''
-could have been used.
+How much of what we mean comes from the words that go unsaid? As
+listeners, the ability to enrich meaning in context is an indispensible
+component of succesful communication. For example, listeners commonly
+enrich the meaning of the scalar item \emph{some} to \emph{some but not
+all} in sentences like ``Alice ate some of the cookies'' (Grice, 1975;
+Horn, 1984; Levinson, 2000). These inferences, called \emph{scalar
+implicatures}, have been an important test case for understanding
+pragmatic inferences more generally. A Gricean account of this phenomena
+assumes listeners reason about the meaning the speaker intended by
+incorporating knowledge about a) alternative scalar items a speaker
+could have used (such as \emph{all}) and b) the relative informativity
+of using such alternatives (Grice, 1975). According to this account, a
+listener will infer that the speaker must have intended that Alice did
+not eat \emph{all} the cookies because it would have been
+\emph{underinformative} for the speaker to use \emph{some} when
+\emph{all} could have been used.
 
-But what are the alternatives that should be considered in this
-computation more generally? Under classic accounts of implicature,
-listeners consider only those words whose meaning would entail the word
-that is actually sent (Horn, 1972), and these alternatives enter into
-conventionalized or semi-conventionalized scales (Levinson, 2000). For
-example, because ``all'' entails ``some,'' and hence is a ``stronger''
-meaning, ``all'' should be considered as an alternative to ``some'' in
-implicatures. Similar scales exist for non-quantifier scales, e.g.
-``love'' entails ``like'' (and hence ``I liked the movie'' implicates
-that I didn't love it).
+But how much of the meaning of \emph{some} comes from the alternatives
+that weren't chosen? Put differently, what are the alternatives that
+should be considered in this computation more generally? Under classic
+accounts of implicature, listeners consider only those words whose
+meaning would entail the word that is actually sent (Horn, 1972), and
+these alternatives enter into conventionalized or semi-conventionalized
+scales (Levinson, 2000). For example, because \emph{all} entails
+\emph{some}, and hence is a ``stronger'' meaning, \emph{all} should be
+considered as an alternative to \emph{some} in implicatures. Similar
+scales exist for non-quantifier scales, e.g. \emph{loved} entails
+\emph{liked} (and hence ``I liked the movie'' implicates that I didn't
+love it).
 
@@
 For example, Degen \& Tanenhaus (2015) demonstrated that the scalar item
-``some'' was judged less appropriate when exact numbers were seen as
+\emph{some} was judged less appropriate when exact numbers were seen as
 viable alternatives. And in a different paradigm, Tiel (2014) found
-converging evidence that ``some'' was judged to be atypical for small
+converging evidence that \emph{some} was judged to be atypical for small
 quantities. These data provide indirect evidence about a broader set of
-alternatives: since ``some'' is logically true of sets with one or two
-members, these authors argued that the presence of salient alternatives
-(the words ``one'' and ``two'') reduced the felicity of ``some'' via a
-pragmatic inference.
+alternatives: since \emph{some} is logically true of sets with one or
+two members, these authors argued that the presence of salient
+alternatives (the words \emph{one} and \emph{two}) reduced the felicity
+of \emph{some} via a pragmatic inference.
 
@@
 what the speaker's most likely communicative goal was, given that she
-picked the quantifier ``some'' rather than the stronger quantifier
-``all.'' In turn, the speaker reasons about what message would best
+picked the quantifier \emph{some} rather than the stronger quantifier
+\emph{all}. In turn, the speaker reasons about what message would best
 convey her intended meaning to the listener, given that he is reasoning
@@
 to a set of alternative numerical expressions. Surprisingly, along with
-weighting ``one'' highly (a conclusion that was suppored by the
+weighting \emph{one} highly (a conclusion that was suppored by the
 empirical work), the best-fitting model assigned substantial weight to
-``none'' as an alternative. This finding was especially surprising
+\emph{none} as an alternative. This finding was especially surprising
 considering the emphasis of standard theories on scalar items that stand
-in entailment relationships with one another (e.g. ``one'' entails
-``some'' even if it is not classically considered to be part of the
+in entailment relationships with one another (e.g. \emph{one} entails
+\emph{some} even if it is not classically considered to be part of the
 scale).
@@
 difference in the strength of scalar implicature across a variety of
-scalar pairs (e.g. ``liked/loved,'' or ``palatable/delicious.''). Making
-use of some of this diversity allows us to investigate the ways that
-different alternative sets give rise to implicatures of different
+scalar pairs (e.g. \emph{liked/loved,} or \emph{palatable/delicious.}).
+Making use of some of this diversity allows us to investigate the ways
+that different alternative sets give rise to implicatures of different
 strengths across scales.
@@
 stars. Second, there was clear variability between scalar families. For
-example, compatibility judgments for the top items in the ``memorable /
-unforgettable'' scale were more similar than those for ``good /
-excellent'' or ``liked / loved.'' Finally, there was substantial
-consistency in ratings for items that were repeated across experiments,
-suggesting that this paradigm elicited stable judgments from
-participants.
+example, compatibility judgments for the top items in the
+\emph{memorable / unforgettable} scale were more similar than those for
+\emph{good / excellent} or \emph{liked / loved.} Finally, there was
+substantial consistency in ratings for items that were repeated across
+experiments, suggesting that this paradigm elicited stable judgments
+from participants.
 
@@
 \begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/exp2Plots-1}
+
+}
+
+\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items.
+Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
+Each panel shows one scalar pair.}\label{fig:exp2Plots}
+\end{figure*}
+\end{CodeChunk}
+
+\begin{CodeChunk}
 \begin{figure}[t]
@@
 Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar
-items ``liked'' and ``loved'' (combined). Alternative distributions for
-the other scalar pairs (e.g.. ``good/excellent'',
-``memorable/unforgettable'') were similarly long-tailed.
+items \emph{liked} and \emph{loved} (combined). Alternative
+distributions for the other scalar pairs (e.g.. \emph{good/excellent},
+\emph{memorable/unforgettable}) were similarly long-tailed.
 
@@
 
-In Experiment 3, we asked participants to make pragmatic listener
-judgements.
-
-CONDITIONS
+Experiment 3 was conducted to measure pragmatic judgments
+\(p_{L_1}(m \mid u)\) for five pairs of scalar items taken from Tiel
+(2014). We include two conditions in Experiment 3. In the
+two-alternative entailment condition, participants made judgments for
+items included in the entailment scales. In the four-alternative
+condition, participants made pragmatic judgments for the entialment
+items and also the top two alternatives elicited for each scale in
+Experiment 2. Running two pragmatic judgment conditions allowed us to
+rule out the potential effects of having a larger set of alternatives
+during the pragmatic judgment elicitation and also provided two sets of
+human judgments to compare with model predictions.
+\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 
-We recruited 150 participants from AMT, 50 for each condition. Data for
+We recruited 100 participants from AMT, 50 for each condition. Data for
 7 participants in the two-alternative condition were excluded after
@@
 These data were measured in Experiment 4.
-
-\begin{CodeChunk}
-\begin{figure*}[t]
-
-{\centering \includegraphics{figs/exp2Plots-1}
-
-}
-
-\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items.
-Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
-Each panel shows one scalar pair.}\label{fig:exp2Plots}
-\end{figure*}
-\end{CodeChunk}
 

### 2016-01-27 Paper/Paper.tex
tweaked intro

@@
 How much of what we mean comes from the words that go unsaid? As
-listeners, the ability to enrich meaning in context is an indispensible
-component of succesful communication. For example, listeners commonly
-enrich the meaning of the scalar item \emph{some} to \emph{some but not
-all} in sentences like ``Alice ate some of the cookies'' (Grice, 1975;
-Horn, 1984; Levinson, 2000). These inferences, called \emph{scalar
-implicatures}, have been an important test case for understanding
-pragmatic inferences more generally. A Gricean account of this phenomena
-assumes listeners reason about the meaning the speaker intended by
-incorporating knowledge about a) alternative scalar items a speaker
-could have used (such as \emph{all}) and b) the relative informativity
-of using such alternatives (Grice, 1975). According to this account, a
-listener will infer that the speaker must have intended that Alice did
-not eat \emph{all} the cookies because it would have been
+listeners, the ability to enrich a speaker's meaning in context is an
+indispensable component of successful communication. For example,
+listeners commonly enrich the meaning of the scalar item \emph{some} to
+\emph{some but not all} in sentences like ``Alice ate some of the
+cookies'' (Grice, 1975; Horn, 1984; Levinson, 2000). These inferences,
+called \emph{scalar implicatures}, have been an important test case for
+understanding pragmatic inferences more generally. A Gricean account of
+this phenomena assumes listeners reason about the meaning the speaker
+intended by incorporating knowledge about a) alternative scalar items a
+speaker could have used (such as \emph{all}) and b) the relative
+informativity of using such alternatives (Grice, 1975). According to
+this account, a listener will infer that the speaker must have intended
+that Alice did not eat \emph{all} the cookies because it would have been
 \emph{underinformative} for the speaker to use \emph{some} when

### 2016-01-27 Paper/Paper.Rmd
tweaked intro
reporting ME models, lot's a little tweaks

@@
     Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
-For example, when interpreting a sentence such as "Bob ate some of the cookies," listeners routinely infer that Bob did not eat all of them.
+For example, when interpreting a sentence such as "Alice ate some of the cookies," listeners routinely infer that Alice did not eat all of them.
 A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
-We use a computational model of pragmatic inference to test out hypotheses about how well different sets of alternatives allow us to predict scalar implicature performance across a range of different scales.
+We use a computational model of pragmatic inference to test hypotheses about how well different sets of alternatives allow us to predict scalar implicature performance across a range of different scales.
 Our findings suggest that human comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.
@@
 ```{r, libraries}
+library(dplyr)
 library(ggplot2)
-library(knitr)
-library(rjson)
-library(dplyr)
-library(tidyr)
+library(grid)
 library(gridExtra)
 library(jsonlite)
+library(lme4)
+library(lmerTest)
+library(knitr)
 library(png)
-library(grid)
+library(rjson)
+library(tidyr)
 library(xtable)
@@
 # -------------------
-allLiteralListener <- read.csv("../models/model_data/RawLiteralListenerCombined.csv", 
-                               stringsAsFactors = FALSE)
-allPragmaticListener <- read.csv("../models/model_data/RawPragmaticListenerCombined.csv", 
-                               stringsAsFactors = FALSE)
+allLiteralListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
+allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models//model_data/RawPragmaticListenerCombined.csv")
 
@@
 How much of what we mean comes from the words that go unsaid?
-As listeners, the ability to enrich meaning in context is an indispensible component of succesful communication.
+As listeners, our ability to make precise inferences about a speaker's intended meaning in context is an indispensable component of successful communication.
 For example, listeners  commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
@@
 A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
-According to this account, a listener will infer that the speaker must have intended that Alice did not eat *all* the cookies because it would have been *underinformative* for the speaker to use *some* when *all* could have been used.
+According to this account, a listener will infer that the speaker must have intended that Alice did not eat *all* the cookies because it would have been underinformative for the speaker to use *some* when *all* could have been used.
 
-But how much of the meaning of *some* comes from the alternatives that weren't chosen?
-Put differently, what are the alternatives that should be considered in this computation more generally?
+But what are the alternatives that should be considered in this computation more generally?
 Under classic accounts of implicature, listeners consider only those words whose meaning would entail the word that is actually sent [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000].
@@
 
-\noindent In other words, the probability of a particular meaning given an utterance is proportional to the speaker's proability of using that particular utterance to express that meaning, weighted by a prior over meanings.
+\noindent In other words, the probability of a particular meaning given an utterance is proportional to the speaker's probability of using that particular utterance to express that meaning, weighted by a prior over meanings.
 This prior represents the listener's _a priori_ expectations about plausible meanings, independent of the utterance.
@@
 
-$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},$$
+$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$
 
@@
 
-To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an onine restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
+To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an online restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
 We then use experiments to measure three components of the model.
@@
 ### Participants
+```{r}
+exp1a <- subset(allLiteralListener, exp == "e8")
+exp1b <- subset(allLiteralListener, exp == "e10")
+exp1c <- subset(allLiteralListener, exp == "e12")
+```
 
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two-alternative condition, two participants were excluded because they reported having a native language other than English for a final sample of 28 participants.
-In the four-alternative condition,  six participants were excluded for either failing to pass two training trials a non-English native language, leaving a total sample of 24 participants.
-In the five-alternative condition, there were no data exclusions due to training failures or native language requirements, leaving a total sample of 30 participants.
+In the two-alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.
+In the four-alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+In the five-alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
 
@@
 Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
-Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.
+Each participant saw all scalar item and star rating combinations for their particular condition, in a random order.
 
@@
 The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2.
-See Figure 1 for the complete list of alternatives used in each condition.
+See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each condition.
 
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a,b,c.
 Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).
-Each panel shows one scalar pair."}
+Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items)."}
 
@@
 speakers$word <- as.factor(with(speakers, mapply(lookupScalar, degree, scale, expt)))
-speakers$wordPlots <- factor(speakers$word, levels=c("excellent", "good", "okay", "bad", "horrible",
-                           "loved", "liked", "indifferent", "disliked", "hated",
-                           "unforgettable", "memorable", "ordinary", "bland", "forgettable",
-                           "delicious", "palatable", "mediocre", "gross", "disgusting",
-                           "all", "most", "some", "little", "none"))
+speakers$wordPlots <- factor(speakers$word, levels=c("horrible", "bad", "okay", "good", "excellent",
+  "hated", "disliked", "indifferent", "liked", "loved",
+  "forgettable", "bland", "ordinary", "memorable", "unforgettable",
+  "disgusting", "gross", "mediocre", "palatable", "delicious",
+  "none", "little", "some", "most", "all"))
 
+# for plotting
+speakers$study <- ifelse(speakers$expt == "e8", "1a",
+                                 ifelse(speakers$expt == "e10", "1b", "1c"))
 # change col = word and facet_grid(.~scale)
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = scale, lty = expt)) + 
+       aes(x = stars, y = speaker.p, col = scale, lty = study)) + 
   geom_line() + 
@@
   xlab("star rating") +
-  ylab("Proportion compatible") + 
-  ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
+  ylab("proportion compatible ('yes' responses)") + 
+  # ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
   # scale_colour_solarized() + 
   theme_bw() +
-  theme(strip.text.x = element_text(size = 8),
+  theme(strip.text.x = element_text(size = 6),
         legend.position = "bottom",
@@
         legend.key.size = unit(.1, "in"),
-        axis.text.x = element_text(size = 8),
+        legend.title = element_text(size = 10),
+        axis.text.x = element_text(size = 7),
         axis.text.y = element_text(size = 6))
@@
 
-Figure 2 plots literal listener $p_{L0}(m|u)$ distributions for the three conditions.
+Figure \ref{fig:exp2Plots} plots literal listener $p_{L0}(m|u)$ scalar item distributions for the three conditions.
+Each row plots a unique scalar family with items ordered horizontally by valence.
 Several trends are visible.
@@
 For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved.* Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
+```{r literalListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
+# fix contrasts so we're comparing most disparate experimetns (e8 and e12)
+contrasts(allLiteralListener$exp) <- cbind("e10" = c(1, 0, 0), "e8" = c(0, 0, 1))
+
+# glmer WITHOUT experiment and with random effect for subjects
+glm1 <- glmer(judgment ~ scale + stars + (1 | word) + (1 | workerid),
+              family=  "binomial", data = allLiteralListener)
+# glmer WITH experiment and with random effect for subjects
+glm2 <- glmer(judgment ~ exp + scale +  stars + (1 | word) +  (1 | workerid),
+              family = "binomial", data = allLiteralListener)
+sumGlm2 <- summary(glm2)
+anovaResults <- anova(glm1, glm2)
+```
+To test whether there were between experiment differences in acceptability judgments, we ran a mixed effects model, regressing acceptability judgements on scale, number of stars and experiment type, with by subject and by word random effects.
+Results indicate no significant differences between Experiment 1a and 1c $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment type variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
-Each panel shows one scalar pair."}
+Each panel shows one scalar pair.
+We are only showing scalar items used for model comparison (items used in Experiments 1a / 3a) for simplicity,"}
 # Get zero's in data frame
@@
   facet_grid(.~ scale) + 
-  ggtitle("Pragmatic listener judgments") +
-  ylab("Proportion of stars selected") +
-  xlab("Star rating") +
+  # ggtitle("Pragmatic listener judgments") +
+  ylab("proportion of selection") +
+  xlab("star rating") +
   theme_bw() +
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Caption goes here"}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale.
+Participants were shown a target scalar (either liked or loved) and asked to give three alternatives."}
 
@@
 
-Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar items *liked* and *loved* (combined).
+Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
 Alternative distributions for the other scalar pairs (e.g..
@@
 
+```{r, allPragStudySubsets, echo = FALSE, messgae = FALSE, warning = FALSE}
+exp3a <- subset(allPragmaticListener, exp == "e6")
+exp3b <- subset(allPragmaticListener, exp == "e11")
+```
+
 We recruited 100 participants from AMT, 50 for each condition.
-Data for 7 participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of 43 participants.
-In the four-alternative condition, data from five participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of 45 participants.
+Data for `r 50 - length(unique(exp3a$workerid))` participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.
 
@@
 Each participant was presented with all scalar items in a random order.
-The experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
+The experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
 
 ## Results and Discussion
+```{r pragmaticListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
+# glmer WITHOUT experiment and with random effect for subjects
+glm1 <- lmer(stars ~ scale + (1 | word) + (1 | workerid), data = allPragmaticListener)
+# glmer WITH experiment and with random effect for subjects
+glm2 <- lmer(stars ~ exp + scale + (1 | word) +  (1 | workerid), data = allPragmaticListener)
+sumGlm2 <- summary(glm2)
+anovaResults <- anova(glm1, glm2)
+```
+
+Figure \ref{fig:exp2Plots} plots pragmatic listener judgments distributions for "weak" / "strong" scalar pairs (ie *good*/*excellent*).
+We only include the original entailment pairs in this figure for simplicity.
+Several trends are visible.
+First, in each scale participants generated implicatures and were less likely to assign high star-ratings to weaker scalar terms, despite literal semantic compatibility.
+Second, the "size" of the difference between judgments between "strong" and "weak" scalar items varied by scale, confirming results found by Tiel (2014).
+
+To test whether there were between experiment differences in pragmatic judgments, we ran a mixed effects model, regressing pragmatic judgements on scale and experiment with subject and word level random effects.
+Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 2)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 
-```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
+```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
 Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.

### 2016-01-27 Paper/Paper.tex
reporting ME models, lot's a little tweaks

--- 2016-01-27 Paper/Paper.tex
@@
 inferences - enrichments beyond the literal meaning of a speaker's
-utterance. For example, when interpreting a sentence such as ``Bob ate
-some of the cookies,'' listeners routinely infer that Bob did not eat
+utterance. For example, when interpreting a sentence such as ``Alice ate
+some of the cookies,'' listeners routinely infer that Alice did not eat
 all of them. A Gricean account of this phenomena assumes the presence of
@@
 alternatives are. We use a computational model of pragmatic inference to
-test out hypotheses about how well different sets of alternatives allow
-us to predict scalar implicature performance across a range of different
+test hypotheses about how well different sets of alternatives allow us
+to predict scalar implicature performance across a range of different
 scales. Our findings suggest that human comprehenders likely consider a
@@
 How much of what we mean comes from the words that go unsaid? As
-listeners, the ability to enrich meaning in context is an indispensible
-component of succesful communication. For example, listeners commonly
-enrich the meaning of the scalar item \emph{some} to \emph{some but not
-all} in sentences like ``Alice ate some of the cookies'' (Grice, 1975;
-Horn, 1984; Levinson, 2000). These inferences, called \emph{scalar
-implicatures}, have been an important test case for understanding
-pragmatic inferences more generally. A Gricean account of this phenomena
-assumes listeners reason about the meaning the speaker intended by
-incorporating knowledge about a) alternative scalar items a speaker
-could have used (such as \emph{all}) and b) the relative informativity
-of using such alternatives (Grice, 1975). According to this account, a
-listener will infer that the speaker must have intended that Alice did
-not eat \emph{all} the cookies because it would have been
-\emph{underinformative} for the speaker to use \emph{some} when
-\emph{all} could have been used.
+listeners, our ability to make precise inferences about a speaker's
+intended meaning in context is an indispensable component of successful
+communication. For example, listeners commonly enrich the meaning of the
+scalar item \emph{some} to \emph{some but not all} in sentences like
+``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
+2000). These inferences, called \emph{scalar implicatures}, have been an
+important test case for understanding pragmatic inferences more
+generally. A Gricean account of this phenomena assumes listeners reason
+about the meaning the speaker intended by incorporating knowledge about
+a) alternative scalar items a speaker could have used (such as
+\emph{all}) and b) the relative informativity of using such alternatives
+(Grice, 1975). According to this account, a listener will infer that the
+speaker must have intended that Alice did not eat \emph{all} the cookies
+because it would have been underinformative for the speaker to use
+\emph{some} when \emph{all} could have been used.
 
-But how much of the meaning of \emph{some} comes from the alternatives
-that weren't chosen? Put differently, what are the alternatives that
-should be considered in this computation more generally? Under classic
-accounts of implicature, listeners consider only those words whose
-meaning would entail the word that is actually sent (Horn, 1972), and
-these alternatives enter into conventionalized or semi-conventionalized
-scales (Levinson, 2000). For example, because \emph{all} entails
-\emph{some}, and hence is a ``stronger'' meaning, \emph{all} should be
-considered as an alternative to \emph{some} in implicatures. Similar
-scales exist for non-quantifier scales, e.g. \emph{loved} entails
-\emph{liked} (and hence ``I liked the movie'' implicates that I didn't
-love it).
+But what are the alternatives that should be considered in this
+computation more generally? Under classic accounts of implicature,
+listeners consider only those words whose meaning would entail the word
+that is actually sent (Horn, 1972), and these alternatives enter into
+conventionalized or semi-conventionalized scales (Levinson, 2000). For
+example, because \emph{all} entails \emph{some}, and hence is a
+``stronger'' meaning, \emph{all} should be considered as an alternative
+to \emph{some} in implicatures. Similar scales exist for non-quantifier
+scales, e.g. \emph{loved} entails \emph{liked} (and hence ``I liked the
+movie'' implicates that I didn't love it).
 
@@
 \noindent In other words, the probability of a particular meaning given
-an utterance is proportional to the speaker's proability of using that
+an utterance is proportional to the speaker's probability of using that
 particular utterance to express that meaning, weighted by a prior over
@@
 
-\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))},\]
+\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]
 
@@
 our studies we adopt a food-review paradigm: we assume that speakers and
-listeners are trying to communicate the number of stars in an onine
+listeners are trying to communicate the number of stars in an online
 restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
@@
 In each condition we recruited 30 participants from Amazon Mechanical
-Turk (AMT). In the two-alternative condition, two participants were
-excluded because they reported having a native language other than
-English for a final sample of 28 participants. In the four-alternative
-condition, six participants were excluded for either failing to pass two
-training trials a non-English native language, leaving a total sample of
-24 participants. In the five-alternative condition, there were no data
-exclusions due to training failures or native language requirements,
-leaving a total sample of 30 participants.
+Turk (AMT). In the two-alternative condition, 16 participants were
+excluded
+\footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c}
+for either failing to pass two training trails or were not native
+English speakers, leaving a total sample of 14 participants. In the
+four-alternative condition, 7 participants were excluded for either
+failing to pass two training trials or were not native English speakers,
+leaving a total sample of 23 participants. In the five-alternative
+condition, 3 participants were excluded for either failing to pass two
+training trials or were not native English speakers, leaving a total
+sample of 27.
 
@@
 
-Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions for the
-three conditions. Several trends are visible. First, in each scale, the
-alternatives spanned the star scale, such that there were alternatives
-that were highly compatible with both the lowest and highest numbers of
-stars. Second, there was clear variability between scalar families. For
-example, compatibility judgments for the top items in the
-\emph{memorable / unforgettable} scale were more similar than those for
-\emph{good / excellent} or \emph{liked / loved.} Finally, there was
-substantial consistency in ratings for items that were repeated across
-experiments, suggesting that this paradigm elicited stable judgments
-from participants.
+Figure \ref{fig:exp2Plots} plots literal listener \(p_{L0}(m|u)\) scalar
+item distributions for the three conditions. Each row plots a unique
+scalar family with items ordered horizontally by valence. Several trends
+are visible. First, in each scale, the alternatives spanned the star
+scale, such that there were alternatives that were highly compatible
+with both the lowest and highest numbers of stars. Second, there was
+clear variability between scalar families. For example, compatibility
+judgments for the top items in the \emph{memorable / unforgettable}
+scale were more similar than those for \emph{good / excellent} or
+\emph{liked / loved.} Finally, there was substantial consistency in
+ratings for items that were repeated across experiments, suggesting that
+this paradigm elicited stable judgments from participants.
+
+To test whether there were between experiment differences in
+acceptability judgments, we ran a mixed effects model, regressing
+acceptability judgements on scale, number of stars and experiment type,
+with by subject and by word random effects. Results indicate no
+significant differences between Experiment 1a and 1c \(b =\)-0.05,
+\(Z =\) -0.53, \(p =\) 0.59 or between 1b and 1c \(b =\) -0.04, \(Z =\)
+-0.52 \(p =\) 0.6 and the addition of our experiment predictor did not
+significantly improve model fit when compared to a model without the
+experiment type variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\)
+0.81.
 
@@
 Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
-Each panel shows one scalar pair.}\label{fig:exp2Plots}
+Each panel shows one scalar pair.
+We are only showing scalar items used for model comparison (items used in Experiments 1a / 3a) for simplicity,}\label{fig:exp2Plots}
 \end{figure*}
@@
 
-\caption[Caption goes here]{Caption goes here}\label{fig:exp2_altsPlot_likedLoved}
+\caption[Combined counts for participant generated alternatives for 'liked  loved' scale]{Combined counts for participant generated alternatives for 'liked  loved' scale.
+Participants were shown a target scalar (either liked or loved) and asked to give three alternatives.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 
-Figure \ref{fig:exp2_altsPlot} an example alternative set for the scalar
-items \emph{liked} and \emph{loved} (combined). Alternative
+Figure \ref{fig:exp2_altsPlot_likedLoved} an example alternative set for
+the scalar items \emph{liked} and \emph{loved} (combined). Alternative
 distributions for the other scalar pairs (e.g.. \emph{good/excellent},
@@
 We recruited 100 participants from AMT, 50 for each condition. Data for
-7 participants in the two-alternative condition were excluded after
+9 participants in the two-alternative condition were excluded after
 participants either failed to pass two training trials or reported a
-non-English native language, leaving a total sample of 43 participants.
-In the four-alternative condition, data from five participants was
-thrown out after participants either failed to pass two training trials
-or were not native English speakers, leaving a total sample of 45
-participants.
+non-English native language, leaving a total sample of 41 participants.
+In the four-alternative condition, data from 7 participants was thrown
+out after participants either failed to pass two training trials or were
+not native English speakers, leaving a total sample of 43 participants.
 
@@
 participant was presented with all scalar items in a random order. The
-experimental setup is shown in Figure \ref{fig:expt1_stimuli}, right.
+experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
 
 \subsection{Results and Discussion}\label{results-and-discussion-2}
+
+To test whether there were between experiment differences in pragmatic
+judgments, we ran a mixed effects model, regressing pragmatic judgements
+on scale and experiment with subject and word level random effects.
+Results indicate there were no significant differences between
+Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150.4 \() =\) 1.04,
+\(p =\) 0.3 and the addition of our experiment predictor did not
+significantly improve model fit when compared to a model without the
+experiment variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\)
+0.29.
 
@@
 
-\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Tue Jan
-26 20:47:20 2016
+\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Wed Jan
+27 09:40:50 2016
 

### 2016-01-27 Paper/Paper.Rmd
fixed xtable plotting

@@
 
-names(tableCors) <- c("r", "model", "Experiment")
+names(tableCors) <- c("Model", "Exp. 3a", "Exp 3b")
 tableCors <- tableCors[c(1, 3, 2),]
-tab <- xtable(tableCors)
-print(tab, type="latex")
+tab <- xtable(tableCors, caption = "Model fit measured by correlation coefficients")
+print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE)
 

### 2016-01-27 Paper/Paper.tex
fixed xtable plotting

@@
 the blank. Each participant saw all scalar item and star rating
-combinations for their particular condition (see Figure
-\ref{fig:allScalesTable}), in a random oder.
+combinations for their particular condition, in a random order.
 
@@
 the four previous items plus one more ``neutral'' item chosen from those
-alternatives generated in Experiment 2. See Figure 1 for the complete
-list of alternatives used in each condition.
+alternatives generated in Experiment 2. See Figure
+\ref{fig:allScalesTable} for the complete list of alternatives used in
+each condition.
 
@@
 
-\caption[Literal listener judgements from Experiments 1a, 3a, and 4]{Literal listener judgements from Experiments 1a, 3a, and 4.
+\caption[Literal listener judgements from Experiments 1a,b,c]{Literal listener judgements from Experiments 1a,b,c.
 Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).
-Each panel shows one scalar pair.}\label{fig:exp1Plots}
+Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).}\label{fig:exp1Plots}
 \end{figure*}
@@
 
-Figure \ref{fig:exp2_altsPlot_likedLoved} an example alternative set for
-the scalar items \emph{liked} and \emph{loved} (combined). Alternative
-distributions for the other scalar pairs (e.g.. \emph{good/excellent},
-\emph{memorable/unforgettable}) were similarly long-tailed.
+Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative
+set for the scalar items \emph{liked} and \emph{loved} (combined).
+Alternative distributions for the other scalar pairs (e.g..
+\emph{good/excellent}, \emph{memorable/unforgettable}) were similarly
+long-tailed.
 
@@
 
+Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
+distributions for ``weak'' / ``strong'' scalar pairs (ie
+\emph{good}/\emph{excellent}). We only include the original entailment
+pairs in this figure for simplicity. Several trends are visible. First,
+in each scale participants generated implicatures and were less likely
+to assign high star-ratings to weaker scalar terms, despite literal
+semantic compatibility. Second, the ``size'' of the difference between
+judgments between ``strong'' and ``weak'' scalar items varied by scale,
+confirming results found by Tiel (2014).
+
 To test whether there were between experiment differences in pragmatic
@@
 
-\% latex table generated in R 3.2.3 by xtable 1.8-0 package \% Wed Jan
-27 09:40:50 2016
-
 \begin{table}[ht]
 \centering
-\begin{tabular}{rlrr}
+\begin{tabular}{lrr}
   \hline
- & r & model & Experiment \\ 
+Model & Exp. 3a & Exp 3b \\ 
   \hline
-1 & Entailment & 0.54 & 0.57 \\ 
-  3 & Top\_two & 0.84 & 0.90 \\ 
-  2 & Full & 0.86 & 0.90 \\ 
+Entailment & 0.54 & 0.57 \\ 
+  Top\_two & 0.84 & 0.90 \\ 
+  Full & 0.86 & 0.90 \\ 
    \hline
 \end{tabular}
+\caption{Model fit measured by correlation coefficients} 
 \end{table}

### 2016-01-27 Paper/Paper.Rmd
minor tweaks before meeting with MF 1.27.16

@@
 
-$$ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)$$
+$$ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$
 
@@
 
-$$p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$
+$$p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$
 
@@
 In the two-alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.
 In the four-alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
@@
 Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
-Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \_____?" They were prompted to generate three unique alternatives.
+Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
 
@@
 We include two conditions in Experiment 3.
-In the two-alternative entailment condition, participants made judgments for items included in the entailment scales.
-In the four-alternative condition, participants made pragmatic judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2.
+In the two-alternative condition, participants made judgments for items included in the entailment scales.
+In the four-alternative condition, participants made judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2.
 Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
@@
 We recruited 100 participants from AMT, 50 for each condition.
-Data for `r 50 - length(unique(exp3a$workerid))` participants in the two-alternative condition were excluded after participants either failed to pass two training trials or reported a non-English native language, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
-In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was thrown out after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.
+Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.
 
@@
 To test whether there were between experiment differences in pragmatic judgments, we ran a mixed effects model, regressing pragmatic judgements on scale and experiment with subject and word level random effects.
-Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 2)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 
-Using literal semantic data from Experiment 1 we conducted three simulations with our model.
+Using literal semantic data from Experiments 1a,b,c we conducted three simulations with our model.
 Each simulation used the specific literal semantic data to specify the scale representation available to our model.

### 2016-01-27 Paper/Paper.tex
minor tweaks before meeting with MF 1.27.16

@@
 
-\[ p_{S_1} (u \mid m) \propto p_{L_0} (m \mid u)\]
+\[ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]
 
@@
 
-\[p(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]
+\[p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]
 
@@
 \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,1c}
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c}
 for either failing to pass two training trails or were not native
@@
 they'd felt differently about the food, what other words could they have
-used instead of \_\_\_\_\_?'' They were prompted to generate three
-unique alternatives.
+used instead of \_\_\_\_?" They were prompted to generate three unique
+alternatives.
 
@@
 (2014). We include two conditions in Experiment 3. In the
-two-alternative entailment condition, participants made judgments for
-items included in the entailment scales. In the four-alternative
-condition, participants made pragmatic judgments for the entialment
-items and also the top two alternatives elicited for each scale in
-Experiment 2. Running two pragmatic judgment conditions allowed us to
-rule out the potential effects of having a larger set of alternatives
-during the pragmatic judgment elicitation and also provided two sets of
-human judgments to compare with model predictions.
+two-alternative condition, participants made judgments for items
+included in the entailment scales. In the four-alternative condition,
+participants made judgments for the entialment items and also the top
+two alternatives elicited for each scale in Experiment 2. Running two
+pragmatic judgment conditions allowed us to rule out the potential
+effects of having a larger set of alternatives during the pragmatic
+judgment elicitation and also provided two sets of human judgments to
+compare with model predictions.
 \footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
@@
 We recruited 100 participants from AMT, 50 for each condition. Data for
-9 participants in the two-alternative condition were excluded after
-participants either failed to pass two training trials or reported a
-non-English native language, leaving a total sample of 41 participants.
-In the four-alternative condition, data from 7 participants was thrown
-out after participants either failed to pass two training trials or were
-not native English speakers, leaving a total sample of 43 participants.
+9 participants was excluded after participants either failed to pass two
+training trials or were non-native English speakers, leaving a total
+sample of 41 participants. In the four-alternative condition, data from
+7 participants was excluded after participants either failed to pass two
+training trials or were not native English speakers, leaving a total
+sample of 43 participants.
 
@@
 Results indicate there were no significant differences between
-Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150.4 \() =\) 1.04,
-\(p =\) 0.3 and the addition of our experiment predictor did not
-significantly improve model fit when compared to a model without the
-experiment variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\)
-0.29.
+Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\)
+0.3 and the addition of our experiment predictor did not significantly
+improve model fit when compared to a model without the experiment
+variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
 
@@
 
-Using literal semantic data from Experiment 1 we conducted three
+Using literal semantic data from Experiments 1a,b,c we conducted three
 simulations with our model. Each simulation used the specific literal

### 2016-01-29 models/RSA_alternativeCostFormulation.Rmd
added generic None (all prob mass under one star runs

@@
           select(hi1, hi2, low1, low2)
+      } else if (numAlts == 3) {
+        mat <- subset(data, scale  == s) %>%
+          select(stars, degree, speaker.p) %>%
+          spread(degree, speaker.p) %>%
+          mutate(hi = hi / sum(hi),
+                 low = low / sum(low),
+                 none = none / sum(none)) %>%
+          select(hi, low, none)
       } else if (numAlts == 2) {
@@
 # --------------
+# for five alts
 emptyCosts5 <- data.frame(scale = c(rep("good_excellent", 5),
@@
                           stringsAsFactors = FALSE)
+# for four alts
 emptyCosts4 <- data.frame(scale = c(rep("good_excellent", 4),
@@
                           stringsAsFactors = FALSE)
+# Used with generic none run
+emptyCosts3 <- data.frame(scale = c(rep("good_excellent", 3),
+                                    rep("liked_loved", 3),
+                                    rep("memorable_unforgettable", 3),
+                                    rep("palatable_delicious", 3),
+                                    rep("some_all", 3)),
+                          degree = rep(c("hi", "low", "none"), 5),
+                          newCount = rep(0.0, 15),
+                          stringsAsFactors = FALSE)
+# for two-alts
 emptyCosts2 <- data.frame(scale = c(rep("good_excellent", 2),
@@
 speakerL10 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e10.csv")
+speakerGenericNone <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8_genericNone.csv")
 speakerL08 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L0_e8.csv")
@@
     saliences[saliences$scale == s, ]$cost <-
-      (-1 * saliences[saliences$scale == s, ]$newCount) / NUM_ALTERNATIVES_E9
-    saliences[saliences$scale == s, ]$cost <-
-      -1 * normedVec(saliences[saliences$scale == s, ]$cost)
+      saliences[saliences$scale == s, ]$newCount / NUM_ALTERNATIVES_E9
+
+    saliences[saliences$scale == s, ]$cost <- 1 / log(saliences[saliences$scale == s, ]$cost)
   }
@@
 
-costs <- normNegSalienceCosts(salienceCosts5)
-priors <- unifPriors
-data <- left_join(speakerL12, costs) %>%
-  left_join(., priors) %>%
-  rowwise %>%
-  select(scale, degree, stars, speaker.p, prior.p, cost) %>%
-  group_by(scale)
+# costs <- normNegSalienceCosts(salienceCosts5)
+# priors <- unifPriors
+# data <- left_join(speakerL12, costs) %>%
+#   left_join(., priors) %>%
+#   rowwise %>%
+#   select(scale, degree, stars, speaker.p, prior.p, cost) %>%
+#   group_by(scale)
 
@@
         }
+    } else if (study == "genericNone") {
+      tempDf <- subset(predDf, scale == s & degree != "none")
     } else { ## study e6
@@
     predDf <- runFull(modelData, calcFn = 2, alpha = i, numAlts = numAlts)
+    # Watch for generic none run
+    if (study == "genericNone") {
+      mergedData <- matchModelHumanData(subset(predDf, degree != "none"), listener, study = study)
+    } else {
       mergedData <- matchModelHumanData(predDf, listener, study = study)
+    }
     cor(mergedData$preds, mergedData$listener.p)
@@
 
-Symmetric scale analysis
+Run full model analysis
 ```{r}
-# Set-up data
-
+# completeModelRun()
+# ------------------
 completeModelRun <- function(speaker, listener, priors, costs, numAlts) {
@@
 
-  studyNum <- ifelse(numAlts == 5, "e12", ifelse(numAlts == 4, "e10", "e6"))
+  studyNum <- ifelse(numAlts == 5, "e12",
+                     ifelse(numAlts == 4, "e10",
+                            ifelse(numAlts == 3, "genericNone", "e6")))
   # Tune alpha
@@
 # Run analyses
-symmetricScalerun <- completeModelRun(speakerL12, listener, unifPriors, emptyCosts5, numAlts = 5)
-symmetricScalerun[[4]]
-negAltsRun <- completeModelRun(speakerL10, listener, unifPriors, emptyCosts4, numAlts = 4)
-negAltsRun[[4]]
-entailmentRun <- completeModelRun(speakerL08, listener, unifPriors, emptyCosts2, numAlts = 2)
-entailmentRun[[4]]
+fiveAlts <- completeModelRun(speakerL12, listener, unifPriors, emptyCosts5, numAlts = 5)
+fiveAlts[[4]]
+fourAlts <- completeModelRun(speakerL10, listener, unifPriors, emptyCosts4, numAlts = 4)
+fourAlts[[4]]
+twoAltsGenericNone <- completeModelRun(speakerGenericNone, listener, unifPriors, emptyCosts3, numAlts = 3)
+twoAltsGenericNone[[4]]
+twoAlts <- completeModelRun(speakerL08, listener, unifPriors, emptyCosts2, numAlts = 2)
+twoAlts[[4]]
 
 listener2 <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
-symmetricData <- symmetricScalerun[[1]]
-symmetricData$numAlts = 5
-negAltsData <- negAltsRun[[1]]
-negAltsData$numAlts = 4
-entailmentData <- entailmentRun[[1]]
-entailmentData$numAlts = 2
+fiveAltsData <- fiveAlts[[1]]
+fiveAltsData$numAlts = 5
+fourAltsData <- fourAlts[[1]]
+fourAltsData$numAlts = 4
+twoAltsGenericNoneData <- twoAltsGenericNone[[1]]
+twoAltsGenericNoneData$numAlts = 3
+twoAltsData <- twoAlts[[1]]
+twoAltsData$numAlts = 2
 
@@
 # combine with e11 prag listener nums
-aggregateData <- rbind(symmetricData, negAltsData, entailmentData)
+aggregateData <- rbind(fiveAltsData, fourAltsData, twoAltsGenericNoneData, twoAltsData)
 listener2 <- listener2[(listener2$scale == "some_all" & (listener2$degree == "low1" | listener2$degree == "hi1")) |
@@
 modelRunData <- aggregateData
-symmetricE6cor <- cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p)
-symmetricE11cor <-cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p2)
-negAltsE6cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p)
-negAltsE11cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p2)
-entailmentE6cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p)
-entailmentE11cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p2)
-modelRunData$corE6 <- ifelse(modelRunData$numAlts == 5, symmetricE6cor,
-                             ifelse(modelRunData$numAlts == 4, negAltsE6cor, entailmentE6cor))
-modelRunData$corE11 <- ifelse(modelRunData$numAlts == 5, symmetricE11cor,
-                             ifelse(modelRunData$numAlts == 4, negAltsE11cor, entailmentE11cor))
-modelRunData$alphas <- ifelse(modelRunData$numAlts == 5, symmetricScalerun[[3]],
-                             ifelse(modelRunData$numAlts == 4, negAltsRun[[3]], entailmentRun[[3]]))
+fiveAltsE6cor <- cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p)
+fiveAltsE11cor <-cor(subset(modelRunData, numAlts == 5)$preds, subset(modelRunData, numAlts == 5)$listener.p2)
+fourAltsE6cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p)
+fourAltsE11cor <- cor(subset(modelRunData, numAlts == 4)$preds, subset(modelRunData, numAlts == 4)$listener.p2)
+twoAltsGenericNoneE6cor <-
+  cor(subset(modelRunData, numAlts == 3)$preds, subset(modelRunData, numAlts == 3)$listener.p)
+twoAltsGenericNoneE11cor <-
+  cor(subset(modelRunData, numAlts == 3)$preds, subset(modelRunData, numAlts == 3)$listener.p2)
+twoAltsE6cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p)
+twoAltsE11cor <- cor(subset(modelRunData, numAlts == 2)$preds, subset(modelRunData, numAlts == 2)$listener.p2)
+
+modelRunData$corE6 <- ifelse(modelRunData$numAlts == 5, fiveAltsE6cor,
+                             ifelse(modelRunData$numAlts == 4, fourAltsE6cor,
+                                    ifelse(modelRunData$numAlts == 3, twoAltsGenericNoneE6cor, twoAltsE6cor)))
+modelRunData$corE11 <- ifelse(modelRunData$numAlts == 5, fiveAltsE11cor,
+                             ifelse(modelRunData$numAlts == 4, fourAltsE11cor,
+                                    ifelse(modelRunData$numAlts == 3, twoAltsGenericNoneE11cor, twoAltsE11cor)))
+modelRunData$alphas <- ifelse(modelRunData$numAlts == 5, fiveAlts[[3]],
+                             ifelse(modelRunData$numAlts == 4, fourAlts[[3]],
+                                    ifelse(modelRunData$numAlts == 3, twoAltsGenericNone[[3]], twoAlts[[3]])))
 

### 2016-01-29 Paper/Paper.Rmd
fixed plotting for literal listener and cut out part of model results (now it's in the general discussion)

@@
 speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
-# speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
+# speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE) ## for nonCompliance data
+# speakerGenericNone <- read.csv("../models/model_data/L0_e8_genericNone.csv", stringsAsFactors = FALSE) ## for genericNone data
 speakerE8 <- read.csv("../models/model_data/L0_e8Compliance.csv", stringsAsFactors = FALSE)
+
 # Listeners ::
@@
 listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
-
-# \begin{center}
-# \textit{``When I choose a word," Humpty Dumpty said, in a rather scornful tone, ``it means just what I choose it to mean - neither more nor less"- Lewis Caroll, Through the Looking-Glass}
-# \end{center}
 ```
@@
 The two-alternative entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiments 1b,c tests whether the total set of alternatives queried during literal semantic elicitation effects compatibility judgments.
+(If it does we should see differences in compatibility judgments between experiments.) We address this possibiliy in the results section.
 
@@
                                  ifelse(speakers$expt == "e10", "1b", "1c"))
-# change col = word and facet_grid(.~scale)
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = scale, lty = study)) + 
+       aes(x = stars, y = speaker.p, col = study, lty = study)) + 
   geom_line() + 
@@
 ```
-To test whether there were between experiment differences in acceptability judgments, we ran a mixed effects model, regressing acceptability judgements on scale, number of stars and experiment type, with by subject and by word random effects.
-Results indicate no significant differences between Experiment 1a and 1c $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment type variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+To test our secondary hypothesis, that the different sets of scalar items queried might result in differences in compatibility judgments between experiments, we ran a mixed effects model.
+We regressed compatibility judgments on scale, number of stars and experiment (1a,b,c), with subject and word level random effects, which was the maximal structure that converged.
+Results indicate no significant differences between Experiment 1a and 1c $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items.
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
                                  TRUE, FALSE)))
-listeners$scalarType <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
+listeners$`Scalar type` <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
+listeners$Experiment <- with(listeners, ifelse(expt == "e6", "3a", "3b"))
 
@@
 ggplot(subset(listeners, plotThis == TRUE),
-       aes(x = stars, y = listener.p, col = scalarType, lty = expt)) + 
+       aes(x = stars, y = listener.p, col = `Scalar type`, lty = Experiment)) + 
   geom_line() + 
@@
   # ggtitle("Pragmatic listener judgments") +
-  ylab("proportion of selection") +
+  ylab("percentage selecting") +
   xlab("star rating") +
@@
         legend.title = element_text(size = 10),
-        legend.text = element_text(size = 8))
+        legend.text = element_text(size = 8),
+        axis.title.x = element_text(size = 8.5),
+        axis.title.y = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10))
 ```
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale.
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale.
 Participants were shown a target scalar (either liked or loved) and asked to give three alternatives."}
@@
   ylim(0, 52) + 
-  labs(x = "Alternatives", y = "Counts") +
-  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
+  labs(x = "alternatives", y = "counts") +
   theme_bw() +
@@
         axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
-        axis.text.y = element_text(size = 10))
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 10),
+        axis.title.y = element_text(size = 10))
 ```
@@
 Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
-\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 3b tests whether the total set of alternatives queried in Experiments 3a,b effects pragmatic judgments.
+(If it does we should see differences in pragmatic judgments between experiments.) We address this possibiliy in the results section.
 
@@
 
-To test whether there were between experiment differences in pragmatic judgments, we ran a mixed effects model, regressing pragmatic judgements on scale and experiment with subject and word level random effects.
+To test our secondary hypothesis, that the different sets of scalar items queried might result in differences in pragmatic judgments between experiments, we ran a mixed effects model.
+We regressed pragmatic judgements on scale and experiment (3a,b) with subject and word level random effects, which was the maximal structure that converged.
 Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
@@
 Each simulation used the specific literal semantic data to specify the scale representation available to our model.
-The "entailment" model used only the original pair of scalar items pulled from van Tiel (2014).
-These data were measured in Experiment 1a.
-The "Top two" model extended the original set of alternatives with the top two alternatives generated in Experiment 2.
-These data were measured in Experiment 3a.
-The "Full" model included the full set of alternatives, including a neutral valenced alternative.
-These data were measured in Experiment 4.
 
@@
 plotData <- allModelRunData %>%
-  mutate(study = ifelse(numAlts == 5, "Full", 
-                        ifelse(numAlts == 4, "Top_two", "Entailment"))) %>%
+  mutate(study = ifelse(numAlts == 5, "Five alts", 
+                        ifelse(numAlts == 4, "Four alts",
+                               ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
   gather(Experiment, cors, c(corE6, corE11)) %>%
@@
 tableCors <- plotData  %>%
-  select(cors, study, Experiment) %>%
+  select(cors, study, Experiment, alphas) %>%
   unique() %>%
@@
 
-names(tableCors) <- c("Model", "Exp. 3a", "Exp 3b")
-tableCors <- tableCors[c(1, 3, 2),]
-tab <- xtable(tableCors, caption = "Model fit measured by correlation coefficients")
-print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE)
+# Plot model performance table
+names(tableCors) <- c("Model", "$\\alpha$", "Exp. 3a", "Exp. 3b")
+tableCors <- tableCors[c(3, 4, 2, 1),]
+tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in our two Pragmatic listener experiments (3a,b)")
+print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
+      sanitize.colnames.function = identity)
 
 # Correlation bar chart
-corBarChart <- ggplot(plotData, aes(x=study, y=cors, fill = Experiment)) + 
-  geom_bar(stat="identity", position="dodge") +
-  ylab("Correlation") +
-  xlab("Model") +
-  ylim(0, 1) + 
-  ggtitle("Model fit correlation coefficients") +
-  guides(colour=FALSE) +
-  geom_text(aes(x = study, y=as.numeric(cors) + 0.025, label = round(cors, 2), col=(Experiment)))
+# corBarChart <- ggplot(plotData, aes(x=study, y=cors, fill = Experiment)) + 
+#   geom_bar(stat="identity", position="dodge") +
+#   ylab("Correlation") +
+#   xlab("Model") +
+#   ylim(0, 1) + 
+#   ggtitle("Model fit correlation coefficients") +
+#   guides(colour=FALSE) +
+#   geom_text(aes(x = study, y=as.numeric(cors) + 0.025, label = round(cors, 2), col=(Experiment)))
 
-# Correlation scatter plot
-symmetricCorPlot <- ggplot(subset(plotData, study == "Top_two"), aes(x = listener.p, y = preds)) + 
-  geom_point() +
-  xlab("Model predictions") +
-  ylab("Human judgments") +
-  stat_smooth(method = "lm") + 
-  ggtitle("Model fit\nSymmetric scale")
-
-# corBarChart
-
-modifiedPlotData <- plotData %>%
-  gather(pragStudy, pragChoice, c(9,11))
-fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
-      data=subset(modifiedPlotData, study == "Full")) +
-  ylim(0, 1) +
-  facet_wrap(~scale) + 
-  geom_line(aes(y = preds), lty = 4)
+# modifiedPlotData <- plotData %>%
+#   gather(pragStudy, pragChoice, c(9,11))
+# fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
+#       data=subset(modifiedPlotData, study == "Full")) +
+#   ylim(0, 1) +
+#   facet_wrap(~scale) + 
+#   geom_line(aes(y = preds), lty = 4)
 # fullRepresentationFit
 # gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
+```
+
+```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Model fit: model predictions are plotted on the x-axis.
+Human judgments from Exerpiment 3b are plotted on the y-axis.
+Coloration denotes star rating for which judgment was made."}
+# Correlation scatter plot
+fiveAltsScatter <- ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
+  geom_point() +
+  xlab("model predictions") +
+  ylab("human judgments (Exp. 3b)") +
+  stat_smooth(method = "lm") +
+  theme(strip.text.x = element_text(size = 8),
+#         legend.position = "bottom",
+#         legend.margin = unit(.02,"in"),
+#         legend.key = element_blank(), 
+#         legend.key.size = unit(.1, "in"),
+        axis.title.x = element_text(size = 8.5),
+        axis.title.y = element_text(size = 8.5))
+  # ggtitle("Model fit\nFive alternatives")
+fiveAltsScatter
 ```
@@
 By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature.
-Model fit with human judgement was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
-In fact, we found that both neutral and negative valence scalar items contribute to human-like implicature generation within our framework.
+Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
+The "Two alternative" model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature.
+Model performance with this limited alternative set was poor when compared to human judgments from Experiment 3a,b (row 1, Table \ref{xtable}).
+Building off findings in Franke (2014), in which the best-fitting model assigned substantial weight to *none* as an alternative, we included a "generic" negative alternative that was only compatible with 1-star.
+Model fit for this modified "Two alternative with generic negative" alternative set did improve, however overall correlation was still low (row 2, Table \ref{xtable}).
+Model fit jumped substantially by adding the top-two alternatives for each scale (row 3, Table \ref{xtable}).
+Finally, our "Five alternative" model included a neutral alternative along with the original entailment pair and top two (row 4, Table \ref{xtable}).
+
+While model improvement seemed to be related to the number of alternatives present, we did not see substantial differences between our four- and five-alternative models.
+One possibility is that alternatives are differentially salient in context.
+Our current framework makes the simplifying assumption that all alternatives are equally salient.
+However, it may well be the case that while both *all* and *most* are *present* during pragmatic enrichment of *some*, *all* is more salient and therefore should carry greater weight in our model.
+Findings from Experiment 2, in which participants generated plausible alternatives, supports this intuition, as some alternatives appeared more often than others.
+This distinction between binary *presence* and graded *salience* is an important one that deserves further investigation.
+
+It is also likely that the precise set of alternatives present during implicature are domain dependent.
+Our current empirical paradigm elicited literal semantics, pragmatic judgments and plausible alternatives all within the restricted domain of food reviews.
+Participant data may have differed greatly if we had instead asked them to respond in a movie review paradigm, which would have been acceptable for a number of our stimuli (ie *memorable*/*unforgettable*, *liked*/*loved*, etc.).
+
+Considering the possibility that alternative sets may be domain specific even for scalar items may provide a way forward in uniting generalized and particularized implicatures.
+Findings from our investigation indicate that human literal semantic and pragmatic judgments are often graded and diverse, much like the set of plausible alternatives that give rise to pragmatic inferences.
 

### 2016-01-29 Paper/Paper.tex
fixed plotting for literal listener and cut out part of model results (now it's in the general discussion)

@@
 fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+A secondary goal of Experiments 1b,c tests whether the total set of
+alternatives queried during literal semantic elicitation effects
+compatibility judgments. (If it does we should see differences in
+compatibility judgments between experiments.) We address this possibiliy
+in the results section.
 
@@
 
-To test whether there were between experiment differences in
-acceptability judgments, we ran a mixed effects model, regressing
-acceptability judgements on scale, number of stars and experiment type,
-with by subject and by word random effects. Results indicate no
-significant differences between Experiment 1a and 1c \(b =\)-0.05,
-\(Z =\) -0.53, \(p =\) 0.59 or between 1b and 1c \(b =\) -0.04, \(Z =\)
--0.52 \(p =\) 0.6 and the addition of our experiment predictor did not
-significantly improve model fit when compared to a model without the
-experiment type variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\)
-0.81.
+To test our secondary hypothesis, that the different sets of scalar
+items queried might result in differences in compatibility judgments
+between experiments, we ran a mixed effects model. We regressed
+compatibility judgments on scale, number of stars and experiment
+(1a,b,c), with subject and word level random effects, which was the
+maximal structure that converged. Results indicate no significant
+differences between Experiment 1a and 1c \(b =\)-0.05, \(Z =\) -0.53,
+\(p =\) 0.59 or between 1b and 1c \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
+0.6 and the addition of our experiment predictor did not significantly
+improve model fit when compared to a model without the experiment
+variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\) 0.81.
 
@@
 \footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+A secondary goal of Experiment 3b tests whether the total set of
+alternatives queried in Experiments 3a,b effects pragmatic judgments.
+(If it does we should see differences in pragmatic judgments between
+experiments.) We address this possibiliy in the results section.
 
@@
 
-To test whether there were between experiment differences in pragmatic
-judgments, we ran a mixed effects model, regressing pragmatic judgements
-on scale and experiment with subject and word level random effects.
-Results indicate there were no significant differences between
-Experiment 3a and 3b for \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\)
-0.3 and the addition of our experiment predictor did not significantly
-improve model fit when compared to a model without the experiment
-variable using ANOVA \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
+To test our secondary hypothesis, that the different sets of scalar
+items queried might result in differences in pragmatic judgments between
+experiments, we ran a mixed effects model. We regressed pragmatic
+judgements on scale and experiment (3a,b) with subject and word level
+random effects, which was the maximal structure that converged. Results
+indicate there were no significant differences between Experiment 3a and
+3b for \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3 and the
+addition of our experiment predictor did not significantly improve model
+fit when compared to a model without the experiment variable using ANOVA
+\(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
 
@@
 semantic data to specify the scale representation available to our
-model. The ``entailment'' model used only the original pair of scalar
-items pulled from van Tiel (2014). These data were measured in
-Experiment 1a. The ``Top two'' model extended the original set of
-alternatives with the top two alternatives generated in Experiment 2.
-These data were measured in Experiment 3a. The ``Full'' model included
-the full set of alternatives, including a neutral valenced alternative.
-These data were measured in Experiment 4.
+model.
 
@@
 \centering
-\begin{tabular}{lrr}
+\begin{tabular}{lrrr}
   \hline
-Model & Exp. 3a & Exp 3b \\ 
+Model & $\alpha$ & Exp. 3a & Exp. 3b \\ 
   \hline
-Entailment & 0.54 & 0.57 \\ 
-  Top\_two & 0.84 & 0.90 \\ 
-  Full & 0.86 & 0.90 \\ 
+Two alts &   9 & 0.54 & 0.57 \\ 
+  Two alts + generic negative  &   6 & 0.62 & 0.66 \\ 
+  Four alts &   4 & 0.84 & 0.90 \\ 
+  Five alts &   4 & 0.86 & 0.90 \\ 
    \hline
 \end{tabular}
-\caption{Model fit measured by correlation coefficients} 
+\caption{Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in our two Pragmatic listener experiments (3a,b)} 
 \end{table}
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/fiveAltsScatter-1}
+
+}
+
+\caption[Model fit]{Model fit: model predictions are plotted on the x-axis.
+Human judgments from Exerpiment 3b are plotted on the y-axis.
+Coloration denotes star rating for which judgment was made.}\label{fig:fiveAltsScatter}
+\end{figure*}
+\end{CodeChunk}
 
@@
 model we investigated the effects of alternatives on scalar implicature.
-Model fit with human judgement was significantly improved by the
+Model fit with human judgments was significantly improved by the
 inclusion of alternatives beyond the typical ``strong'' and ``weak''
-scalar items. In fact, we found that both neutral and negative valence
-scalar items contribute to human-like implicature generation within our
-framework.
+scalar items. The ``Two alternative'' model contained only entailment
+items, which, under classic accounts, should be sufficient to generate
+implicature. Model performance with this limited alternative set was
+poor when compared to human judgments from Experiment 3a,b (row 1, Table
+\ref{xtable}). Building off findings in Franke (2014), in which the
+best-fitting model assigned substantial weight to \emph{none} as an
+alternative, we included a ``generic'' negative alternative that was
+only compatible with 1-star. Model fit for this modified ``Two
+alternative with generic negative'' alternative set did improve, however
+overall correlation was still low (row 2, Table \ref{xtable}). Model fit
+jumped substantially by adding the top-two alternatives for each scale
+(row 3, Table \ref{xtable}). Finally, our ``Five alternative'' model
+included a neutral alternative along with the original entailment pair
+and top two (row 4, Table \ref{xtable}).
+
+While model improvement seemed to be related to the number of
+alternatives present, we did not see substantial differences between our
+four- and five-alternative models. One possibility is that alternatives
+are differentially salient in context. Our current framework makes the
+simplifying assumption that all alternatives are equally salient.
+However, it may well be the case that while both \emph{all} and
+\emph{most} are \emph{present} during pragmatic enrichment of
+\emph{some}, \emph{all} is more salient and therefore should carry
+greater weight in our model. Findings from Experiment 2, in which
+participants generated plausible alternatives, supports this intuition,
+as some alternatives appeared more often than others. This distinction
+between binary \emph{presence} and graded \emph{salience} is an
+important one that deserves further investigation.
+
+It is also likely that the precise set of alternatives present during
+implicature are domain dependent. Our current empirical paradigm
+elicited literal semantics, pragmatic judgments and plausible
+alternatives all within the restricted domain of food reviews.
+Participant data may have differed greatly if we had instead asked them
+to respond in a movie review paradigm, which would have been acceptable
+for a number of our stimuli (ie \emph{memorable}/\emph{unforgettable},
+\emph{liked}/\emph{loved}, etc.).
+
+Considering the possibility that alternative sets may be domain specific
+even for scalar items may provide a way forward in uniting generalized
+and particularized implicatures. Findings from our investigation
+indicate that human literal semantic and pragmatic judgments are often
+graded and diverse, much like the set of plausible alternatives that
+give rise to pragmatic inferences.
 

### 2016-01-29 Paper/Paper.Rmd
minor edits, spelling, naming, before sending to MF

@@
 abstract: 
-    Succesful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
+    Successful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
 For example, when interpreting a sentence such as "Alice ate some of the cookies," listeners routinely infer that Alice did not eat all of them.
@@
 In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions.
-Surprisingly, along with weighting *one* highly (a conclusion that was suppored by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative.
+Surprisingly, along with weighting *one* highly (a conclusion that was supported by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative.
 This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g.
@@
 We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items.
-These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgements.
-To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgements, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgements with high accuracy.
+These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgments.
+To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgments, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgments with high accuracy.
 
@@
 We begin by giving a brief presentation of the basic RSA model.
-This model simulates the judgements of a pragmatic listener who wants to infer a speaker's intended meaning $m$ from her utterance $u$.
+This model simulates the judgments of a pragmatic listener who wants to infer a speaker's intended meaning $m$ from her utterance $u$.
 For simplicity, we present a version of this model in which there is only full recursion: that is, the pragmatic listener reasons about a pragmatic speaker, who in turn reasons about a "literal listener." We assume throughout that this computation takes place in a signaling game [@lewis1969] with a fixed set of possible meanings $m \in M$ and a fixed possible set of utterances $u \in U$, with both known to both participants.
@@
 
-This model of the pragmatic speaker is consistent with a speaker who chooses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:
+This model of the pragmatic speaker (denoted $S_1$) is consistent with a speaker who chooses words to maximize the utility of an utterance in context [@frank2012], where utility is operationalized as the informativity of a particular utterance (surprisal) minus a cost:
 
@@
 
-\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ for the literal listener (the information content of the utterance), and ($\alpha$ is a parameter in a standard choice rule.
+\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ for the literal listener (the information content of the utterance), and $\alpha$ is a parameter in a standard choice rule.
 If $\alpha=0$, speakers choose randomly and as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative.
@@
 We then use experiments to measure three components of the model.
-First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is applicable to a particular meaning (Experiment 1).
+First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 1).
 Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2).
@@
 Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
-We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives.
-The two-alternative entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four- and five-alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiments 1b,c tests whether the total set of alternatives queried during literal semantic elicitation effects compatibility judgments.
-(If it does we should see differences in compatibility judgments between experiments.) We address this possibiliy in the results section.
+We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
+The two-alternatives entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
+The four- and five-alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiments 1a,b,c tests whether the set of alternatives queried during literal semantic elicitation impacts compatibility judgments.
+(If it does we should see differences in compatibility judgments for shared items between experiments.) We address this possibility in the results section.
 
@@
 Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star rating.
-Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
+Compatibility was assessed through a binary "yes/no" response to a question of the form, "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank.
 Each participant saw all scalar item and star rating combinations for their particular condition, in a random order.
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a,b,c.
-Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items)."}
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c.
+Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Rows are grouped by scale and items within rows are ordered by valence.
+Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items."}
 
@@
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = study, lty = study)) + 
+       aes(x = stars, y = speaker.p, col = study)) + 
   geom_line() + 
@@
 Figure \ref{fig:exp2Plots} plots literal listener $p_{L0}(m|u)$ scalar item distributions for the three conditions.
-Each row plots a unique scalar family with items ordered horizontally by valence.
+Each row shows a unique scalar family with items ordered horizontally by valence.
 Several trends are visible.
@@
 We regressed compatibility judgments on scale, number of stars and experiment (1a,b,c), with subject and word level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between Experiment 1a and 1c $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 
-Participants were presented a target scalar term from our original entailment set embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
+Participants were presented a target scalar item from our original entailment set (see Figure \ref{fig:allScalesTable}) embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale.
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale from Experiment 2.
 Participants were shown a target scalar (either liked or loved) and asked to give three alternatives."}
@@
 We include two conditions in Experiment 3.
-In the two-alternative condition, participants made judgments for items included in the entailment scales.
-In the four-alternative condition, participants made judgments for the entialment items and also the top two alternatives elicited for each scale in Experiment 2.
-Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
-\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 3b tests whether the total set of alternatives queried in Experiments 3a,b effects pragmatic judgments.
-(If it does we should see differences in pragmatic judgments between experiments.) We address this possibiliy in the results section.
+In the two-alternatives condition, participants made judgments for items included in the entailment scales.
+In the four-alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2.
+Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}.
+A secondary goal of Experiment 3b tests whether the set of alternatives queried in Experiments 3a,b impacts pragmatic judgments.
+(If it does we should see differences in pragmatic judgments between experiments.) We address this possibility in the results section.
 
@@
 
-Figure \ref{fig:exp2Plots} plots pragmatic listener judgments distributions for "weak" / "strong" scalar pairs (ie *good*/*excellent*).
+Figure \ref{fig:exp2Plots} plots pragmatic listener judgments distributions for "weak" / "strong" scalar pairs (e.g.
+*good*/*excellent*).
 We only include the original entailment pairs in this figure for simplicity.
@@
 First, in each scale participants generated implicatures and were less likely to assign high star-ratings to weaker scalar terms, despite literal semantic compatibility.
-Second, the "size" of the difference between judgments between "strong" and "weak" scalar items varied by scale, confirming results found by Tiel (2014).
+Second, the "size" of the difference between judgments between "strong" and "weak" scalar items varied by scale, consistent with results from Tiel (2014).
 
 To test our secondary hypothesis, that the different sets of scalar items queried might result in differences in pragmatic judgments between experiments, we ran a mixed effects model.
-We regressed pragmatic judgements on scale and experiment (3a,b) with subject and word level random effects, which was the maximal structure that converged.
-Results indicate there were no significant differences between Experiment 3a and 3b for $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+We regressed pragmatic judgments on scale and experiment (3a,b) with subject and word level random effects, which was the maximal structure that converged.
+Results indicate there were no significant differences between Experiment 3a and 3b, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
-The "Two alternative" model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature.
+The two-alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature.
 Model performance with this limited alternative set was poor when compared to human judgments from Experiment 3a,b (row 1, Table \ref{xtable}).
 Building off findings in Franke (2014), in which the best-fitting model assigned substantial weight to *none* as an alternative, we included a "generic" negative alternative that was only compatible with 1-star.
-Model fit for this modified "Two alternative with generic negative" alternative set did improve, however overall correlation was still low (row 2, Table \ref{xtable}).
+Model fit for this modified entailment alternative set did improve, however overall correlation was still low (row 2, Table \ref{xtable}).
 Model fit jumped substantially by adding the top-two alternatives for each scale (row 3, Table \ref{xtable}).
-Finally, our "Five alternative" model included a neutral alternative along with the original entailment pair and top two (row 4, Table \ref{xtable}).
+Finally, our five-alternatives model included a neutral alternative along with the original entailment pair and top two (row 4, Table \ref{xtable}).
 
@@
 However, it may well be the case that while both *all* and *most* are *present* during pragmatic enrichment of *some*, *all* is more salient and therefore should carry greater weight in our model.
-Findings from Experiment 2, in which participants generated plausible alternatives, supports this intuition, as some alternatives appeared more often than others.
+Findings from Experiment 2, in which participants generated plausible alternatives, support this intuition, as some alternatives appeared more often than others.
 This distinction between binary *presence* and graded *salience* is an important one that deserves further investigation.
@@
 It is also likely that the precise set of alternatives present during implicature are domain dependent.
-Our current empirical paradigm elicited literal semantics, pragmatic judgments and plausible alternatives all within the restricted domain of food reviews.
-Participant data may have differed greatly if we had instead asked them to respond in a movie review paradigm, which would have been acceptable for a number of our stimuli (ie *memorable*/*unforgettable*, *liked*/*loved*, etc.).
+Our current empirical paradigm elicited literal semantics, pragmatic judgments and plausible alternatives all within the restricted domain of restaurant reviews.
+Participant data may have differed greatly if we had instead asked them to respond in a movie review paradigm, which would have been acceptable for a number of our stimuli (e.g.
+*memorable*/*unforgettable*, *liked*/*loved*, etc.).
 
@@
 
-Thanks to NSF BCS XYZ. Thanks to Michael Franke, Judith Degen, and Noah Goodman.
+Thanks to NSF BCS. Thanks to Michael Franke, Judith Degen, and Noah Goodman.
 

### 2016-01-29 Paper/Paper.tex
minor edits, spelling, naming, before sending to MF

@@
 \begin{abstract}
-Succesful communication regularly requires listeners to make pragmatic
+Successful communication regularly requires listeners to make pragmatic
 inferences - enrichments beyond the literal meaning of a speaker's
@@
 to a set of alternative numerical expressions. Surprisingly, along with
-weighting \emph{one} highly (a conclusion that was suppored by the
+weighting \emph{one} highly (a conclusion that was supported by the
 empirical work), the best-fitting model assigned substantial weight to
@@
 compare the effects of different alternative sets on our ability to
-model listeners' pragmatic judgements. To preview our results: we find
+model listeners' pragmatic judgments. To preview our results: we find
 that standard entailment alternatives do not allow us to fit
-participants' judgements, but that expanding the range of alternatives
+participants' judgments, but that expanding the range of alternatives
 empirically (by asking participants to generate alternative messages)
-allows us to model listener judgements with high accuracy.
+allows us to model listener judgments with high accuracy.
 
@@
 We begin by giving a brief presentation of the basic RSA model. This
-model simulates the judgements of a pragmatic listener who wants to
-infer a speaker's intended meaning \(m\) from her utterance \(u\). For
+model simulates the judgments of a pragmatic listener who wants to infer
+a speaker's intended meaning \(m\) from her utterance \(u\). For
 simplicity, we present a version of this model in which there is only
@@
 
-This model of the pragmatic speaker is consistent with a speaker who
-chooses words to maximize the utility of an utterance in context (Frank
-\& Goodman, 2012), where utility is operationalized as the informativity
-of a particular utterance (surprisal) minus a cost:
+This model of the pragmatic speaker (denoted \(S_1\)) is consistent with
+a speaker who chooses words to maximize the utility of an utterance in
+context (Frank \& Goodman, 2012), where utility is operationalized as
+the informativity of a particular utterance (surprisal) minus a cost:
 
@@
 \(-log(p_{L_0})\) represents the \emph{surprisal} for the literal
-listener (the information content of the utterance), and (\(\alpha\) is
-a parameter in a standard choice rule. If \(\alpha=0\), speakers choose
+listener (the information content of the utterance), and \(\alpha\) is a
+parameter in a standard choice rule. If \(\alpha=0\), speakers choose
 randomly and as \(\alpha \rightarrow \infty\), they greedily choose the
@@
 literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
-participants to judge whether a message is applicable to a particular
+participants to judge whether a message is compatible with a particular
 meaning (Experiment 1). Second, to generate a set of plausible
@@
 corresponding to the sets of alternatives within a scale that
-participants were presented with: two alternatives (``entailment''),
-four alternatives, and five alternatives. The two-alternative entailment
-condition makes a test of the hypothesis that the two members of the
-classic Horn scale (Horn, 1972) are the only alternatives necessary to
-predict the strength of listeners' pragmatic inference. The four- and
-five-alternative conditions then add successively more alternatives to
-test whether including a larger number of alternatives will increase
-model
+participants were presented with: two-alternatives (``entailment''),
+four-alternatives, and five-alternatives. The two-alternatives
+entailment condition makes a test of the hypothesis that the two members
+of the classic Horn scale (Horn, 1972) are the only alternatives
+necessary to predict the strength of listeners' pragmatic inference. The
+four- and five-alternatives conditions then add successively more
+alternatives to test whether including a larger number of alternatives
+will increase model
 fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
-A secondary goal of Experiments 1b,c tests whether the total set of
-alternatives queried during literal semantic elicitation effects
+A secondary goal of Experiments 1a,b,c tests whether the set of
+alternatives queried during literal semantic elicitation impacts
 compatibility judgments. (If it does we should see differences in
-compatibility judgments between experiments.) We address this possibiliy
-in the results section.
+compatibility judgments for shared items between experiments.) We
+address this possibility in the results section.
 
@@
 star rating. Compatibility was assessed through a binary ``yes/no''
-response to a question of the form ``Do you think that the person
+response to a question of the form, ``Do you think that the person
 thought the food was \_\_\_\_?" where a target scalar was presented in
@@
 
-\caption[Literal listener judgements from Experiments 1a,b,c]{Literal listener judgements from Experiments 1a,b,c.
-Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).}\label{fig:exp1Plots}
+\caption[Literal listener judgments from Experiments 1a,b,c]{Literal listener judgments from Experiments 1a,b,c.
+Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Rows are grouped by scale and items within rows are ordered by valence.
+Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items.}\label{fig:exp1Plots}
 \end{figure*}
@@
 Figure \ref{fig:exp2Plots} plots literal listener \(p_{L0}(m|u)\) scalar
-item distributions for the three conditions. Each row plots a unique
+item distributions for the three conditions. Each row shows a unique
 scalar family with items ordered horizontally by valence. Several trends
@@
 maximal structure that converged. Results indicate no significant
-differences between Experiment 1a and 1c \(b =\)-0.05, \(Z =\) -0.53,
-\(p =\) 0.59 or between 1b and 1c \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
+differences between Experiment 1a and 1c, \(b =\)-0.05, \(Z =\) -0.53,
+\(p =\) 0.59 or between 1b and 1c, \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
 0.6 and the addition of our experiment predictor did not significantly
@@
 
-Participants were presented a target scalar term from our original
-entailment set embedded in a sentence such as, ``In a recent restaurant
-review someone said they thought they the food was \_\_\_\_," with a
-target scalar presented in the blank. Participants were then asked to
-generate plausible alternatives by responding to the question, ``If
-they'd felt differently about the food, what other words could they have
-used instead of \_\_\_\_?" They were prompted to generate three unique
-alternatives.
+Participants were presented a target scalar item from our original
+entailment set (see Figure \ref{fig:allScalesTable}) embedded in a
+sentence such as, ``In a recent restaurant review someone said they
+thought they the food was \_\_\_\_," with a target scalar presented in
+the blank. Participants were then asked to generate plausible
+alternatives by responding to the question, ``If they'd felt differently
+about the food, what other words could they have used instead of
+\_\_\_\_?" They were prompted to generate three unique alternatives.
 
@@
 
-\caption[Combined counts for participant generated alternatives for 'liked  loved' scale]{Combined counts for participant generated alternatives for 'liked  loved' scale.
+\caption[Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2]{Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2.
 Participants were shown a target scalar (either liked or loved) and asked to give three alternatives.}\label{fig:exp2_altsPlot_likedLoved}
@@
 (2014). We include two conditions in Experiment 3. In the
-two-alternative condition, participants made judgments for items
-included in the entailment scales. In the four-alternative condition,
-participants made judgments for the entialment items and also the top
+two-alternatives condition, participants made judgments for items
+included in the entailment scales. In the four-alternatives condition,
+participants made judgments for the entailment items and also the top
 two alternatives elicited for each scale in Experiment 2. Running two
@@
 judgment elicitation and also provided two sets of human judgments to
-compare with model predictions.
-\footnote{Note that alternatives in the four-alternative condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
-A secondary goal of Experiment 3b tests whether the total set of
-alternatives queried in Experiments 3a,b effects pragmatic judgments.
-(If it does we should see differences in pragmatic judgments between
-experiments.) We address this possibiliy in the results section.
+compare with model
+predictions\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}.
+A secondary goal of Experiment 3b tests whether the set of alternatives
+queried in Experiments 3a,b impacts pragmatic judgments. (If it does we
+should see differences in pragmatic judgments between experiments.) We
+address this possibility in the results section.
 
@@
 Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
-distributions for ``weak'' / ``strong'' scalar pairs (ie
+distributions for ``weak'' / ``strong'' scalar pairs (e.g.
 \emph{good}/\emph{excellent}). We only include the original entailment
@@
 judgments between ``strong'' and ``weak'' scalar items varied by scale,
-confirming results found by Tiel (2014).
+consistent with results from Tiel (2014).
 
@@
 experiments, we ran a mixed effects model. We regressed pragmatic
-judgements on scale and experiment (3a,b) with subject and word level
+judgments on scale and experiment (3a,b) with subject and word level
 random effects, which was the maximal structure that converged. Results
 indicate there were no significant differences between Experiment 3a and
-3b for \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3 and the
-addition of our experiment predictor did not significantly improve model
-fit when compared to a model without the experiment variable using ANOVA
+3b, \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3 and the addition
+of our experiment predictor did not significantly improve model fit when
+compared to a model without the experiment variable using ANOVA
 \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
@@
 inclusion of alternatives beyond the typical ``strong'' and ``weak''
-scalar items. The ``Two alternative'' model contained only entailment
+scalar items. The two-alternatives model contained only entailment
 items, which, under classic accounts, should be sufficient to generate
@@
 alternative, we included a ``generic'' negative alternative that was
-only compatible with 1-star. Model fit for this modified ``Two
-alternative with generic negative'' alternative set did improve, however
-overall correlation was still low (row 2, Table \ref{xtable}). Model fit
-jumped substantially by adding the top-two alternatives for each scale
-(row 3, Table \ref{xtable}). Finally, our ``Five alternative'' model
-included a neutral alternative along with the original entailment pair
-and top two (row 4, Table \ref{xtable}).
+only compatible with 1-star. Model fit for this modified entailment
+alternative set did improve, however overall correlation was still low
+(row 2, Table \ref{xtable}). Model fit jumped substantially by adding
+the top-two alternatives for each scale (row 3, Table \ref{xtable}).
+Finally, our five-alternatives model included a neutral alternative
+along with the original entailment pair and top two (row 4, Table
+\ref{xtable}).
 
@@
 greater weight in our model. Findings from Experiment 2, in which
-participants generated plausible alternatives, supports this intuition,
+participants generated plausible alternatives, support this intuition,
 as some alternatives appeared more often than others. This distinction
@@
 elicited literal semantics, pragmatic judgments and plausible
-alternatives all within the restricted domain of food reviews.
+alternatives all within the restricted domain of restaurant reviews.
 Participant data may have differed greatly if we had instead asked them
 to respond in a movie review paradigm, which would have been acceptable
-for a number of our stimuli (ie \emph{memorable}/\emph{unforgettable},
+for a number of our stimuli (e.g. \emph{memorable}/\emph{unforgettable},
 \emph{liked}/\emph{loved}, etc.).
@@
 
-Thanks to NSF BCS XYZ. Thanks to Michael Franke, Judith Degen, and Noah
+Thanks to NSF BCS. Thanks to Michael Franke, Judith Degen, and Noah
 Goodman.

### 2016-01-29 Paper/Paper.Rmd
changed axis title on speakers plot

@@
 allLiteralListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
-allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models//model_data/RawPragmaticListenerCombined.csv")
+allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawPragmaticListenerCombined.csv")
 
@@
   guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
-                               title = "Scalar Item"), 
-         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                title = "Experiment")) + 

### 2016-01-31 Paper/Paper.Rmd
editing pass + gd revisions

@@
 A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
-We use a computational model of pragmatic inference to test hypotheses about how well different sets of alternatives allow us to predict scalar implicature performance across a range of different scales.
-Our findings suggest that human comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.
+We collect empirical measurements of speaker and listener judgments and use these as inputs to a computational model of pragmatic inference.
+This approach allows us to test hypotheses about how well different sets of alternatives predict implicature performance across a range of different scales.
+Our findings suggest that comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.
 
@@
 knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
-                      echo=F, warning=F, cache=TRUE, message=F, sanitize = T)
+                      echo=F, warning=F, cache=F, message=F, sanitize = T)
 ```
@@
 # -------------------
-allLiteralListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawLiteralListenerCombined.csv")
-allPragmaticListener <- read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/RawPragmaticListenerCombined.csv")
+allLiteralListener <- read.csv("../models/model_data/RawLiteralListenerCombined.csv")
+allPragmaticListener <- read.csv("../models/model_data/RawPragmaticListenerCombined.csv")
 
@@
 How much of what we mean comes from the words that go unsaid?
-As listeners, our ability to make precise inferences about a speaker's intended meaning in context is an indispensable component of successful communication.
+As listeners, our ability to make precise inferences about a speaker's intended meaning in context is  indispensable to successful communication.
 For example, listeners commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
-A Gricean account of this phenomena assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
-According to this account, a listener will infer that the speaker must have intended that Alice did not eat *all* the cookies because it would have been underinformative for the speaker to use *some* when *all* could have been used.
+A Gricean account of this phenomenon assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
+According to this account, a listener will infer that the speaker must have intended that Alice did not eat all the cookies because otherwise it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
 
-But what are the alternatives that should be considered in this computation more generally?
-Under classic accounts of implicature, listeners consider only those words whose meaning would entail the word that is actually sent [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000].
+But what are the alternatives that should be considered in the implicature computation more generally?
+Under classic accounts, listeners consider only those words whose meanings entail the actual message [@horn1972], and these alternatives enter into conventionalized or semi-conventionalized scales [@levinson2000].
 For example, because *all* entails *some*, and hence is a "stronger" meaning, *all* should be considered as an alternative to *some* in implicatures.
@@
 And in a different paradigm, @vantiel2014 found converging evidence that *some* was judged to be atypical for small quantities.
-These data provide indirect evidence about a broader set of alternatives: since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*) reduced the felicity of *some* via a pragmatic inference.
+These data provide indirect evidence about a broader set of alternatives: since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*, for example) reduced the felicity of *some* via a pragmatic inference.
 
@@
 
-$$p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)$$
+$$p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}$$
 
@@
 
-$$p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}$$
+$$p_{S_1}(u \mid m) \propto e^{-\alpha\[-log(p_{L_0}(m \mid u)) - C(u)\]}$$
 
-\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ for the literal listener (the information content of the utterance), and $\alpha$ is a parameter in a standard choice rule.
+\noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ of the message for the literal listener (the information content of the utterance), and $\alpha$ is a parameter in a standard choice rule.
 If $\alpha=0$, speakers choose randomly and as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative.
@@
 
-To instantiate our signaling game with a tractable message set $M$, in our studies we adopt a food-review paradigm: we assume that speakers and listeners are trying to communicate the number of stars in an online restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
+To instantiate our signaling game with a tractable message set $M$, in our studies we adopt the world of restaurant reviews as our communication game.
+We assume that speakers and listeners are trying to communicate the number of stars in an online restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
 We then use experiments to measure three components of the model.
@@
 Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
-We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
-The two-alternatives entailment condition makes a test of the hypothesis that the two  members of the classic Horn scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four- and five-alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiments 1a,b,c tests whether the set of alternatives queried during literal semantic elicitation impacts compatibility judgments.
-(If it does we should see differences in compatibility judgments for shared items between experiments.) We address this possibility in the results section.
+We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives.
+The two alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
+The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 1 is to test whether the set of alternatives queried during literal semantic elicitation impacts compatibility judgments.
+(If it does we should see differences in compatibility judgments for shared items between experiments.)
 
@@
 
+Conditions were run sequentially.
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two-alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded \footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c} for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.
-In the four-alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
-In the five-alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
+In the two alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternative condition was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
 
@@
 
-The two-alternatives condition included only the scalar pairs from @vantiel2014.
-The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
-The five-alternatives condition included the four previous items plus one more "neutral" item chosen from those alternatives generated in Experiment 2.
+The two alternatives condition included only the scalar pairs from @vantiel2014.
+The four alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
+The five alternatives condition included the four previous items plus one more neutral item chosen from those alternatives generated in Experiment 2.
 See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each condition.
@@
 # for plotting
-speakers$study <- ifelse(speakers$expt == "e8", "1a",
-                                 ifelse(speakers$expt == "e10", "1b", "1c"))
+speakers$condition <- ifelse(speakers$expt == "e8", "two alts",
+                                 ifelse(speakers$expt == "e10", 
+                                        "four alts", "five alts"))
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = study)) + 
+       aes(x = stars, y = speaker.p, col = condition)) + 
   geom_line() + 
@@
   guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
-                               title = "Experiment")) + 
+                               title = "Condition")) + 
   xlab("star rating") +
@@
 Second, there was clear variability between scalar families.
-For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved.* Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
+For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved*.
+Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
+
 ```{r literalListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
@@
 ```
-To test our secondary hypothesis, that the different sets of scalar items queried might result in differences in compatibility judgments between experiments, we ran a mixed effects model.
-We regressed compatibility judgments on scale, number of stars and experiment (1a,b,c), with subject and word level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+To test our secondary hypothesis, that the different sets of scalar items might result in differences in compatibility judgments between experiments, we ran a mixed effects model.
+We regressed compatibility judgments on scale, number of stars and condition, with subject and word level random effects, which was the maximal structure that converged.
+Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items.
-Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
-Each panel shows one scalar pair.
-We are only showing scalar items used for model comparison (items used in Experiments 1a / 3a) for simplicity,"}
-# Get zero's in data frame
-baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
-                     scale = c(rep("good_excellent", 6 * 5),
-                               rep("liked_loved", 6 * 5),
-                               rep("memorable_unforgettable", 6 * 5),
-                               rep("palatable_delicious", 6 * 5),
-                               rep("some_all", 6 * 5)),
-                     stars = rep(1:5, 30),
-                     combine = rep(TRUE, 150))
-listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
-                      listenerE11 %>% mutate(expt = "e11"))
-listeners <- left_join(baseDf, listeners) %>%
-  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
-         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
-listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
-listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
-                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
-                               TRUE, ifelse(scale != "some_all" & (
-                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
-                                 TRUE, FALSE)))
-listeners$`Scalar type` <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
-listeners$Experiment <- with(listeners, ifelse(expt == "e6", "3a", "3b"))
-
-# Plot pragmatic listener data here
-ggplot(subset(listeners, plotThis == TRUE),
-       aes(x = stars, y = listener.p, col = `Scalar type`, lty = Experiment)) + 
-  geom_line() + 
-  facet_grid(.~ scale) + 
-  # ggtitle("Pragmatic listener judgments") +
-  ylab("percentage selecting") +
-  xlab("star rating") +
-  theme_bw() +
-  theme(strip.text.x = element_text(size = 6),
-        legend.position = "bottom",
-        legend.margin = unit(.02,"in"),
-        legend.key = element_blank(), 
-        legend.key.size = unit(.1, "in"),
-        legend.title = element_text(size = 10),
-        legend.text = element_text(size = 8),
-        axis.title.x = element_text(size = 8.5),
-        axis.title.y = element_text(size = 10),
-        axis.text.x = element_text(size = 10),
-        axis.text.y = element_text(size = 10))
-```
-
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant generated alternatives for 'liked \ loved' scale from Experiment 2.
-Participants were shown a target scalar (either liked or loved) and asked to give three alternatives."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the "liked \ loved" scale in Experiment 2."}
 
@@
 
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for scalar items.
+Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Line type denotes condition, and colors indicate the particular scalar items.
+Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity."}
+# Get zero's in data frame
+baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
+                     scale = c(rep("good_excellent", 6 * 5),
+                               rep("liked_loved", 6 * 5),
+                               rep("memorable_unforgettable", 6 * 5),
+                               rep("palatable_delicious", 6 * 5),
+                               rep("some_all", 6 * 5)),
+                     stars = rep(1:5, 30),
+                     combine = rep(TRUE, 150))
+listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
+                      listenerE11 %>% mutate(expt = "e11"))
+listeners <- left_join(baseDf, listeners) %>%
+  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
+         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
+listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
+listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
+                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
+                               TRUE, ifelse(scale != "some_all" & (
+                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
+                                 TRUE, FALSE)))
+listeners$`Scalar type` <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))
+listeners$Condition <- with(listeners, ifelse(expt == "e6", "two alts", "four alts"))
+
+# Plot pragmatic listener data here
+ggplot(subset(listeners, plotThis == TRUE),
+       aes(x = stars, y = listener.p, col = `Scalar type`, lty = Condition)) + 
+  geom_line() + 
+  facet_grid(.~ scale) + 
+  # ggtitle("Pragmatic listener judgments") +
+  ylab("percentage selecting") +
+  xlab("star rating") +
+  theme_bw() +
+  theme(strip.text.x = element_text(size = 6),
+        legend.position = "bottom",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
+        legend.title = element_text(size = 10),
+        legend.text = element_text(size = 8),
+        axis.title.x = element_text(size = 8.5),
+        axis.title.y = element_text(size = 10),
+        axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10))
+```
+
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
@@
 
-Experiment 3 was conducted to measure pragmatic judgments $p_{L_1}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
-We include two conditions in Experiment 3.
-In the two-alternatives condition, participants made judgments for items included in the entailment scales.
-In the four-alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2.
-Running two pragmatic judgment conditions allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}.
-A secondary goal of Experiment 3b tests whether the set of alternatives queried in Experiments 3a,b impacts pragmatic judgments.
-(If it does we should see differences in pragmatic judgments between experiments.) We address this possibility in the results section.
+Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation \ref{eq:rsa}.
+As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
+In the two alternatives condition, participants made judgments for items included in the entailment scales.
+In the four alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2.
+Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 We recruited 100 participants from AMT, 50 for each condition.
-Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
-In the four-alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp3b$workerid))` participants.
+Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+In the four alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
 
@@
 *good*/*excellent*).
-We only include the original entailment pairs in this figure for simplicity.
+We include only the original entailment pairs in this figure for simplicity.
 Several trends are visible.
-First, in each scale participants generated implicatures and were less likely to assign high star-ratings to weaker scalar terms, despite literal semantic compatibility.
-Second, the "size" of the difference between judgments between "strong" and "weak" scalar items varied by scale, consistent with results from Tiel (2014).
+First, in each scale participants generated implicatures.
+They were substantially  less likely to assign high star ratings to weaker scalar terms, despite the literal semantic compatibility of those terms with those states shown in Experiment 1.
+Second, the size of the difference between strong and weak scalar items varied considerably across scales, consistent with previous work [@vantiel2014].
 
-To test our secondary hypothesis, that the different sets of scalar items queried might result in differences in pragmatic judgments between experiments, we ran a mixed effects model.
-We regressed pragmatic judgments on scale and experiment (3a,b) with subject and word level random effects, which was the maximal structure that converged.
-Results indicate there were no significant differences between Experiment 3a and 3b, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of our experiment predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+To test our secondary hypothesis, that the different sets of scalar items in the two conditions might result in differences in pragmatic judgments for the same items, we fit a mixed effects model.
+We regressed pragmatic judgments on scale and condition with subject- and word-level random effects, which was the maximal structure that converged.
+There were no significant differences between conditions, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
-# Model Results
+# Model Comparison
 
-Using literal semantic data from Experiments 1a,b,c we conducted three simulations with our model.
-Each simulation used the specific literal semantic data to specify the scale representation available to our model.
+Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model.
+Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Table \ref{fig:allScalesTable): 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
+
+Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table \ref{fig:xtable}).
+The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
+The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
+An example fit for the five-alternative model is shown in Figure \ref{fig:fiveAltsScatter}.
 
@@
 
-```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Model fit: model predictions are plotted on the x-axis.
-Human judgments from Exerpiment 3b are plotted on the y-axis.
-Coloration denotes star rating for which judgment was made."}
+```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3, four alternatives condition, are plotted against model predictions.
+Colors show the star rating for individual judgments."}
 # Correlation scatter plot
-fiveAltsScatter <- ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
+ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
   geom_point() +
@@
   stat_smooth(method = "lm") +
+  theme_bw() + 
   theme(strip.text.x = element_text(size = 8),
@@
   # ggtitle("Model fit\nFive alternatives")
-fiveAltsScatter
+
 ```
@@
 
-By varying the type of scale representations available to our Bayesian model we investigated the effects of alternatives on scalar implicature.
-Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the typical "strong" and "weak" scalar items.
-The two-alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature.
-Model performance with this limited alternative set was poor when compared to human judgments from Experiment 3a,b (row 1, Table \ref{xtable}).
-Building off findings in Franke (2014), in which the best-fitting model assigned substantial weight to *none* as an alternative, we included a "generic" negative alternative that was only compatible with 1-star.
-Model fit for this modified entailment alternative set did improve, however overall correlation was still low (row 2, Table \ref{xtable}).
-Model fit jumped substantially by adding the top-two alternatives for each scale (row 3, Table \ref{xtable}).
-Finally, our five-alternatives model included a neutral alternative along with the original entailment pair and top two (row 4, Table \ref{xtable}).
+Pragmatic inference requires reasoning about alternatives.
+The fundamental pragmatic computation is counterfactual: "if she had meant X, she would have said Y, but she didn't." Yet the nature of these alternatives has been controversial.
+For a few well-studied scales, a small set of logically-determined alternatives has been claimed to be all that is necessary [@horn1972].
+For other, contextually-determined inferences, the issue of alternatives has been considered relatively intractable in terms of formal inquiry [@sperber1995].
 
-While model improvement seemed to be related to the number of alternatives present, we did not see substantial differences between our four- and five-alternative models.
-One possibility is that alternatives are differentially salient in context.
-Our current framework makes the simplifying assumption that all alternatives are equally salient.
-However, it may well be the case that while both *all* and *most* are *present* during pragmatic enrichment of *some*, *all* is more salient and therefore should carry greater weight in our model.
-Findings from Experiment 2, in which participants generated plausible alternatives, support this intuition, as some alternatives appeared more often than others.
-This distinction between binary *presence* and graded *salience* is an important one that deserves further investigation.
+In our current work, we used the rational speech act framework to investigate the set of alternatives that best allowed the model to predict pragmatic judgments across a series of different scales.
+We found that the best predictions came when a range of scale-dependent negative and neutral alternatives were added to the implicature computation, suggesting the importance of considering non-entailment alternatives.
+This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2015].
 
-It is also likely that the precise set of alternatives present during implicature are domain dependent.
-Our current empirical paradigm elicited literal semantics, pragmatic judgments and plausible alternatives all within the restricted domain of restaurant reviews.
-Participant data may have differed greatly if we had instead asked them to respond in a movie review paradigm, which would have been acceptable for a number of our stimuli (e.g.
-*memorable*/*unforgettable*, *liked*/*loved*, etc.).
+While improvements in model fit were substantial as we moved from two to four alternatives, we saw only a minor increase in fit from the move to five alternatives.
+One possible explanation is that alternatives are differentially salient in context, and moving to larger sets would consider weighting the alternatives differentially [as @franke2014 did].
+Preliminary simulations using weightings derived from Experiment 2 provide some support for this idea but would require further empirical work for confirmation.
 
-Considering the possibility that alternative sets may be domain specific even for scalar items may provide a way forward in uniting generalized and particularized implicatures.
-Findings from our investigation indicate that human literal semantic and pragmatic judgments are often graded and diverse, much like the set of plausible alternatives that give rise to pragmatic inferences.
+The precise set of alternatives present during implicature is likely to be domain dependent.
+Our current empirical paradigm elicited literal semantics, pragmatic judgments, and plausible alternatives all within the restricted domain of restaurant reviews.
+Our measurements might have differed substantially if we had instead grounded our ratings in a different context.
+Future investigations should probe the context-specificity of the weight and availability of particular alternative sets.
+
+More broadly, considering the context- and domain-specificity of alternative sets may provide a way to unite what @grice1975 called "generalized" (cross-context) and "particularized" (context-dependent) implicatures.
+Rather than being grounded in a firm distinction, we may find that these categories are simply a reflection of the effects of context on a constantly-shifting set of pragmatic alternatives.
 
@@
 
-Thanks to NSF BCS. Thanks to Michael Franke, Judith Degen, and Noah Goodman.
+Thanks to NSF BCS #1456077 for support, and thanks to Michael Franke, Judith Degen, and Noah Goodman for valuable discussion.
 

### 2016-01-31 Paper/Paper.Rmd
minor
pushing MF changes

@@
 
-$$ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$
+$$p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$
 
@@
 
-$$p_{S_1}(u \mid m) \propto e^{-\alpha\[-log(p_{L_0}(m \mid u)) - C(u)\]}$$
+$$p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}$$
 
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the "liked \ loved" scale in Experiment 2."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the 'liked \ loved' scale in Experiment 2."}
 
@@
 
-# Model Comparison
+# Model
 

### 2016-01-31 Paper/Paper.tex
pushing MF changes

@@
 informativity, but it remains an open question precisely what these
-alternatives are. We use a computational model of pragmatic inference to
-test hypotheses about how well different sets of alternatives allow us
-to predict scalar implicature performance across a range of different
-scales. Our findings suggest that human comprehenders likely consider a
-much broader set of alternatives beyond those entailed by the initial
-description.
+alternatives are. We collect empirical measurements of speaker and
+listener judgments and use these as inputs to a computational model of
+pragmatic inference. This approach allows us to test hypotheses about
+how well different sets of alternatives predict implicature performance
+across a range of different scales. Our findings suggest that
+comprehenders likely consider a much broader set of alternatives beyond
+those entailed by the initial description.
 
@@
 listeners, our ability to make precise inferences about a speaker's
-intended meaning in context is an indispensable component of successful
+intended meaning in context is indispensable to successful
 communication. For example, listeners commonly enrich the meaning of the
@@
 important test case for understanding pragmatic inferences more
-generally. A Gricean account of this phenomena assumes listeners reason
+generally. A Gricean account of this phenomenon assumes listeners reason
 about the meaning the speaker intended by incorporating knowledge about
@@
 (Grice, 1975). According to this account, a listener will infer that the
-speaker must have intended that Alice did not eat \emph{all} the cookies
-because it would have been underinformative for the speaker to use
-\emph{some} when \emph{all} could have been used.
+speaker must have intended that Alice did not eat all the cookies
+because otherwise it would have been underinformative to use the
+descriptor \emph{some} when the alternative \emph{all} could have been
+used just as easily.
 
-But what are the alternatives that should be considered in this
-computation more generally? Under classic accounts of implicature,
-listeners consider only those words whose meaning would entail the word
-that is actually sent (Horn, 1972), and these alternatives enter into
-conventionalized or semi-conventionalized scales (Levinson, 2000). For
-example, because \emph{all} entails \emph{some}, and hence is a
-``stronger'' meaning, \emph{all} should be considered as an alternative
-to \emph{some} in implicatures. Similar scales exist for non-quantifier
-scales, e.g. \emph{loved} entails \emph{liked} (and hence ``I liked the
-movie'' implicates that I didn't love it).
+But what are the alternatives that should be considered in the
+implicature computation more generally? Under classic accounts,
+listeners consider only those words whose meanings entail the actual
+message (Horn, 1972), and these alternatives enter into conventionalized
+or semi-conventionalized scales (Levinson, 2000). For example, because
+\emph{all} entails \emph{some}, and hence is a ``stronger'' meaning,
+\emph{all} should be considered as an alternative to \emph{some} in
+implicatures. Similar scales exist for non-quantifier scales, e.g.
+\emph{loved} entails \emph{liked} (and hence ``I liked the movie''
+implicates that I didn't love it).
 
@@
 two members, these authors argued that the presence of salient
-alternatives (the words \emph{one} and \emph{two}) reduced the felicity
-of \emph{some} via a pragmatic inference.
+alternatives (the words \emph{one} and \emph{two}, for example) reduced
+the felicity of \emph{some} via a pragmatic inference.
 
@@
 
-\[p_{L1}(m \mid u) \propto p_{S_1} (u \mid m) p(m)\]
+\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}\]
 
@@
 
-\[ p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]
+\[p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]
 
@@
 
-\[p_{S_1}(u \mid m) \propto e^{-\alpha(-log(p_{L_0}(m \mid u)) - C(u))}\]
+\[p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}\]
 
 \noindent where \(C(u)\) is the cost of a particular utterance,
-\(-log(p_{L_0})\) represents the \emph{surprisal} for the literal
-listener (the information content of the utterance), and \(\alpha\) is a
-parameter in a standard choice rule. If \(\alpha=0\), speakers choose
-randomly and as \(\alpha \rightarrow \infty\), they greedily choose the
-highest probability alternative. In our simulations below, we treat
-\(\alpha\) as a free parameter and fit it to the data.
+\(-log(p_{L_0})\) represents the \emph{surprisal} of the message for the
+literal listener (the information content of the utterance), and
+\(\alpha\) is a parameter in a standard choice rule. If \(\alpha=0\),
+speakers choose randomly and as \(\alpha \rightarrow \infty\), they
+greedily choose the highest probability alternative. In our simulations
+below, we treat \(\alpha\) as a free parameter and fit it to the data.
 
 To instantiate our signaling game with a tractable message set \(M\), in
-our studies we adopt a food-review paradigm: we assume that speakers and
-listeners are trying to communicate the number of stars in an online
-restaurant review (where \(m \in \{1, 2, 3, 4, 5\}\)). We then use
-experiments to measure three components of the model. First, to measure
-literal semantics \({p_{L_0} (m \mid u)}\) (we ask experiment
-participants to judge whether a message is compatible with a particular
-meaning (Experiment 1). Second, to generate a set of plausible
-alternative messages in \(U\), we elicit alternatives directly
-(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
-ask participants to interpret a speaker's utterances (Experiment 3).
+our studies we adopt the world of restaurant reviews as our
+communication game. We assume that speakers and listeners are trying to
+communicate the number of stars in an online restaurant review (where
+\(m \in \{1, 2, 3, 4, 5\}\)). We then use experiments to measure three
+components of the model. First, to measure literal semantics
+\({p_{L_0} (m \mid u)}\) (we ask experiment participants to judge
+whether a message is compatible with a particular meaning (Experiment
+1). Second, to generate a set of plausible alternative messages in
+\(U\), we elicit alternatives directly (Experiment 2). Lastly, to obtain
+human \(L_1\) pragmatic judgments, we ask participants to interpret a
+speaker's utterances (Experiment 3).
 
@@
 corresponding to the sets of alternatives within a scale that
-participants were presented with: two-alternatives (``entailment''),
-four-alternatives, and five-alternatives. The two-alternatives
-entailment condition makes a test of the hypothesis that the two members
-of the classic Horn scale (Horn, 1972) are the only alternatives
-necessary to predict the strength of listeners' pragmatic inference. The
-four- and five-alternatives conditions then add successively more
-alternatives to test whether including a larger number of alternatives
-will increase model
-fit.\footnote{Note that alternatives in the four- and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
-A secondary goal of Experiments 1a,b,c tests whether the set of
+participants were presented with: two alternatives (``entailment''),
+four alternatives, and five alternatives. The two alternatives condition
+makes a test of the hypothesis that the two members of the classic Horn
+(entailment) scale (Horn, 1972) are the only alternatives necessary to
+predict the strength of listeners' pragmatic inference. The four and
+five alternatives conditions then add successively more alternatives to
+test whether including a larger number of alternatives will increase
+model
+fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+A secondary goal of Experiment 1 is to test whether the set of
 alternatives queried during literal semantic elicitation impacts
 compatibility judgments. (If it does we should see differences in
-compatibility judgments for shared items between experiments.) We
-address this possibility in the results section.
+compatibility judgments for shared items between experiments.)
 
@@
 
-In each condition we recruited 30 participants from Amazon Mechanical
-Turk (AMT). In the two-alternative condition, 16 participants were
-excluded
-\footnote{The majority of respondent data excluded from Experiment 1a was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in Experiments 1b,c}
-for either failing to pass two training trails or were not native
-English speakers, leaving a total sample of 14 participants. In the
-four-alternative condition, 7 participants were excluded for either
-failing to pass two training trials or were not native English speakers,
-leaving a total sample of 23 participants. In the five-alternative
-condition, 3 participants were excluded for either failing to pass two
-training trials or were not native English speakers, leaving a total
-sample of 27.
+Conditions were run sequentially. In each condition we recruited 30
+participants from Amazon Mechanical Turk (AMT). In the two alternative
+condition, 16 participants were excluded for either failing to pass two
+training trails or were not native English speakers, leaving a total
+sample of 14
+participants.\footnote{The majority of respondent data excluded from the two alternative condition was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
+In the four alternative condition, 7 participants were excluded for
+either failing to pass two training trials or were not native English
+speakers, leaving a total sample of 23 participants. In the five
+alternative condition, 3 participants were excluded for either failing
+to pass two training trials or were not native English speakers, leaving
+a total sample of 27.
 
@@
 
-The two-alternatives condition included only the scalar pairs from Tiel
-(2014). The four-alternatives condition included the two scalar items
+The two alternatives condition included only the scalar pairs from Tiel
+(2014). The four alternatives condition included the two scalar items
 plus the top two alternatives generated for each scalar family by
-participants in Experiment 2. The five-alternatives condition included
-the four previous items plus one more ``neutral'' item chosen from those
+participants in Experiment 2. The five alternatives condition included
+the four previous items plus one more neutral item chosen from those
 alternatives generated in Experiment 2. See Figure
@@
 scale were more similar than those for \emph{good / excellent} or
-\emph{liked / loved.} Finally, there was substantial consistency in
+\emph{liked / loved}. Finally, there was substantial consistency in
 ratings for items that were repeated across experiments, suggesting that
@@
 To test our secondary hypothesis, that the different sets of scalar
-items queried might result in differences in compatibility judgments
-between experiments, we ran a mixed effects model. We regressed
-compatibility judgments on scale, number of stars and experiment
-(1a,b,c), with subject and word level random effects, which was the
-maximal structure that converged. Results indicate no significant
-differences between Experiment 1a and 1c, \(b =\)-0.05, \(Z =\) -0.53,
-\(p =\) 0.59 or between 1b and 1c, \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
-0.6 and the addition of our experiment predictor did not significantly
-improve model fit when compared to a model without the experiment
-variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\) 0.81.
+items might result in differences in compatibility judgments between
+experiments, we ran a mixed effects model. We regressed compatibility
+judgments on scale, number of stars and condition, with subject and word
+level random effects, which was the maximal structure that converged.
+Results indicate no significant differences between Experiment 1a and
+1c, \(b =\)-0.05, \(Z =\) -0.53, \(p =\) 0.59 or between 1b and 1c,
+\(b =\) -0.04, \(Z =\) -0.52 \(p =\) 0.6 and the addition of condition
+as a predictor did not significantly improve model fit when compared to
+a model without the experiment variable using ANOVA \(\chi^2(\) 2
+\() =\) 0.43, \(p =\) 0.81.
 
@@
 \begin{CodeChunk}
+\begin{figure}[t]
+
+{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
+
+}
+
+\caption[Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2]{Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
 \begin{figure*}[t]
@@
 
-\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items.
+\caption[Pragmatic listener judgements for scalar items]{Pragmatic listener judgements for scalar items.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale.
-Each panel shows one scalar pair.
-We are only showing scalar items used for model comparison (items used in Experiments 1a / 3a) for simplicity,}\label{fig:exp2Plots}
+Line type denotes condition, and colors indicate the particular scalar items.
+Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity.}\label{fig:exp2Plots}
 \end{figure*}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\begin{figure}[t]
-
-{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
-
-}
-
-\caption[Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2]{Combined counts for participant generated alternatives for 'liked  loved' scale from Experiment 2.
-Participants were shown a target scalar (either liked or loved) and asked to give three alternatives.}\label{fig:exp2_altsPlot_likedLoved}
-\end{figure}
 \end{CodeChunk}
@@
 
-Experiment 3 was conducted to measure pragmatic judgments
-\(p_{L_1}(m \mid u)\) for five pairs of scalar items taken from Tiel
-(2014). We include two conditions in Experiment 3. In the
-two-alternatives condition, participants made judgments for items
-included in the entailment scales. In the four-alternatives condition,
-participants made judgments for the entailment items and also the top
-two alternatives elicited for each scale in Experiment 2. Running two
-pragmatic judgment conditions allowed us to rule out the potential
-effects of having a larger set of alternatives during the pragmatic
-judgment elicitation and also provided two sets of human judgments to
-compare with model
-predictions\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}.
-A secondary goal of Experiment 3b tests whether the set of alternatives
-queried in Experiments 3a,b impacts pragmatic judgments. (If it does we
-should see differences in pragmatic judgments between experiments.) We
-address this possibility in the results section.
+Experiment 3 was conducted to measure pragmatic
+judgments---\(p_{L_1}(m \mid u)\) in Equation \ref{eq:rsa}. As in
+Experiment 1, we include several conditions to test inferences in the
+presence of different alternative sets. In the two alternatives
+condition, participants made judgments for items included in the
+entailment scales. In the four alternatives condition, participants made
+judgments for the entailment items and also the top two alternatives
+elicited for each scale in Experiment 2. Including two conditions with
+differing alternatives allowed us to rule out the potential effects of
+having a larger set of alternatives during the pragmatic judgment
+elicitation and also provided two sets of human judgments to compare
+with model
+predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 We recruited 100 participants from AMT, 50 for each condition. Data for
-9 participants was excluded after participants either failed to pass two
-training trials or were non-native English speakers, leaving a total
-sample of 41 participants. In the four-alternative condition, data from
-7 participants was excluded after participants either failed to pass two
-training trials or were not native English speakers, leaving a total
-sample of 43 participants.
+9 participants was excluded from the two alternatives condition after
+participants either failed to pass two training trials or were
+non-native English speakers, leaving a total sample of 41 participants.
+In the four alternative condition, data from 7 participants was excluded
+after participants either failed to pass two training trials or were not
+native English speakers, leaving 43 participants.
 
@@
 distributions for ``weak'' / ``strong'' scalar pairs (e.g.
-\emph{good}/\emph{excellent}). We only include the original entailment
+\emph{good}/\emph{excellent}). We include only the original entailment
 pairs in this figure for simplicity. Several trends are visible. First,
-in each scale participants generated implicatures and were less likely
-to assign high star-ratings to weaker scalar terms, despite literal
-semantic compatibility. Second, the ``size'' of the difference between
-judgments between ``strong'' and ``weak'' scalar items varied by scale,
-consistent with results from Tiel (2014).
+in each scale participants generated implicatures. They were
+substantially less likely to assign high star ratings to weaker scalar
+terms, despite the literal semantic compatibility of those terms with
+those states shown in Experiment 1. Second, the size of the difference
+between strong and weak scalar items varied considerably across scales,
+consistent with previous work (Tiel, 2014).
 
 To test our secondary hypothesis, that the different sets of scalar
-items queried might result in differences in pragmatic judgments between
-experiments, we ran a mixed effects model. We regressed pragmatic
-judgments on scale and experiment (3a,b) with subject and word level
-random effects, which was the maximal structure that converged. Results
-indicate there were no significant differences between Experiment 3a and
-3b, \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3 and the addition
-of our experiment predictor did not significantly improve model fit when
-compared to a model without the experiment variable using ANOVA
-\(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
+items in the two conditions might result in differences in pragmatic
+judgments for the same items, we fit a mixed effects model. We regressed
+pragmatic judgments on scale and condition with subject- and word-level
+random effects, which was the maximal structure that converged. There
+were no significant differences between conditions, \(b =\) 0.05, \(t(\)
+150 \() =\) 1.04, \(p =\) 0.3 and the addition of the condition
+predictor did not significantly improve model fit when compared to a
+model without that variable \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
 
-\section{Model Results}\label{model-results}
+\section{Model}\label{model}
 
-Using literal semantic data from Experiments 1a,b,c we conducted three
-simulations with our model. Each simulation used the specific literal
-semantic data to specify the scale representation available to our
-model.
+Using literal listener data from Experiment 1, we conducted a set of
+simulations with the RSA model. Each simulation kept the model constant,
+fitting the choice parameter \(\alpha\) as a free parameter, but used a
+set of alternatives to specify the scale over which predictions were
+computed. We considered four different alternative sets, with empirical
+measurements corresponding to those shown in Table
+\textbackslash{}ref\{fig:allScalesTable): 1) the two alternatives in the
+classic entailment scales, 2) those two alternatives with the addition
+of a generic negative alternative, 3) the expanded set of four
+alternatives tested in Experiment 1, and 4) the expanded set of five
+alternatives tested in Experiment 1.
+
+Model fit with human judgments was significantly improved by the
+inclusion of alternatives beyond the entailment items (Table
+\ref{fig:xtable}). The two alternatives model contained only entailment
+items, which, under classic accounts, should be sufficient to generate
+implicature, but fit to data was quite poor with these items. The
+addition of a generic negative element produced some gains in
+performance, but much higher performance was found when we included four
+and five alternatives, with the alternatives derived empirically for the
+specific scale we used. An example fit for the five-alternative model is
+shown in Figure \ref{fig:fiveAltsScatter}.
 
@@
 
-\caption[Model fit]{Model fit: model predictions are plotted on the x-axis.
-Human judgments from Exerpiment 3b are plotted on the y-axis.
-Coloration denotes star rating for which judgment was made.}\label{fig:fiveAltsScatter}
+\caption[Judgments from Experiment 3, four alternatives condition, are plotted against model predictions]{Judgments from Experiment 3, four alternatives condition, are plotted against model predictions.
+Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
 \end{figure*}
@@
 
-By varying the type of scale representations available to our Bayesian
-model we investigated the effects of alternatives on scalar implicature.
-Model fit with human judgments was significantly improved by the
-inclusion of alternatives beyond the typical ``strong'' and ``weak''
-scalar items. The two-alternatives model contained only entailment
-items, which, under classic accounts, should be sufficient to generate
-implicature. Model performance with this limited alternative set was
-poor when compared to human judgments from Experiment 3a,b (row 1, Table
-\ref{xtable}). Building off findings in Franke (2014), in which the
-best-fitting model assigned substantial weight to \emph{none} as an
-alternative, we included a ``generic'' negative alternative that was
-only compatible with 1-star. Model fit for this modified entailment
-alternative set did improve, however overall correlation was still low
-(row 2, Table \ref{xtable}). Model fit jumped substantially by adding
-the top-two alternatives for each scale (row 3, Table \ref{xtable}).
-Finally, our five-alternatives model included a neutral alternative
-along with the original entailment pair and top two (row 4, Table
-\ref{xtable}).
+Pragmatic inference requires reasoning about alternatives. The
+fundamental pragmatic computation is counterfactual: ``if she had meant
+X, she would have said Y, but she didn't.'' Yet the nature of these
+alternatives has been controversial. For a few well-studied scales, a
+small set of logically-determined alternatives has been claimed to be
+all that is necessary (Horn, 1972). For other, contextually-determined
+inferences, the issue of alternatives has been considered relatively
+intractable in terms of formal inquiry (Sperber \& Wilson, 1995).
 
-While model improvement seemed to be related to the number of
-alternatives present, we did not see substantial differences between our
-four- and five-alternative models. One possibility is that alternatives
-are differentially salient in context. Our current framework makes the
-simplifying assumption that all alternatives are equally salient.
-However, it may well be the case that while both \emph{all} and
-\emph{most} are \emph{present} during pragmatic enrichment of
-\emph{some}, \emph{all} is more salient and therefore should carry
-greater weight in our model. Findings from Experiment 2, in which
-participants generated plausible alternatives, support this intuition,
-as some alternatives appeared more often than others. This distinction
-between binary \emph{presence} and graded \emph{salience} is an
-important one that deserves further investigation.
+In our current work, we used the rational speech act framework to
+investigate the set of alternatives that best allowed the model to
+predict pragmatic judgments across a series of different scales. We
+found that the best predictions came when a range of scale-dependent
+negative and neutral alternatives were added to the implicature
+computation, suggesting the importance of considering non-entailment
+alternatives. This work builds on previous investigations, reinforcing
+the claim that negative alternatives are critical for understanding
+implicature (Franke, 2014), and replicates and extends findings that
+different lexical scales produce strikingly different patterns of
+inference ({\textbf{???}}).
 
-It is also likely that the precise set of alternatives present during
-implicature are domain dependent. Our current empirical paradigm
-elicited literal semantics, pragmatic judgments and plausible
-alternatives all within the restricted domain of restaurant reviews.
-Participant data may have differed greatly if we had instead asked them
-to respond in a movie review paradigm, which would have been acceptable
-for a number of our stimuli (e.g. \emph{memorable}/\emph{unforgettable},
-\emph{liked}/\emph{loved}, etc.).
+While improvements in model fit were substantial as we moved from two to
+four alternatives, we saw only a minor increase in fit from the move to
+five alternatives. One possible explanation is that alternatives are
+differentially salient in context, and moving to larger sets would
+consider weighting the alternatives differentially (as Franke, 2014
+did). Preliminary simulations using weightings derived from Experiment 2
+provide some support for this idea but would require further empirical
+work for confirmation.
 
-Considering the possibility that alternative sets may be domain specific
-even for scalar items may provide a way forward in uniting generalized
-and particularized implicatures. Findings from our investigation
-indicate that human literal semantic and pragmatic judgments are often
-graded and diverse, much like the set of plausible alternatives that
-give rise to pragmatic inferences.
+The precise set of alternatives present during implicature is likely to
+be domain dependent. Our current empirical paradigm elicited literal
+semantics, pragmatic judgments, and plausible alternatives all within
+the restricted domain of restaurant reviews. Our measurements might have
+differed substantially if we had instead grounded our ratings in a
+different context. Future investigations should probe the
+context-specificity of the weight and availability of particular
+alternative sets.
+
+More broadly, considering the context- and domain-specificity of
+alternative sets may provide a way to unite what Grice (1975) called
+``generalized'' (cross-context) and ``particularized''
+(context-dependent) implicatures. Rather than being grounded in a firm
+distinction, we may find that these categories are simply a reflection
+of the effects of context on a constantly-shifting set of pragmatic
+alternatives.
 
@@
 
-Thanks to NSF BCS. Thanks to Michael Franke, Judith Degen, and Noah
-Goodman.
+Thanks to NSF BCS \#1456077 for support, and thanks to Michael Franke,
+Judith Degen, and Noah Goodman for valuable discussion.
 
@@
 
+Sperber, D., \& Wilson, D. (1995). \emph{Relevance: Communication and
+cognition} (2nd ed.). Oxford, UK: Blackwell.
+
 Tiel, B. van. (2014). Quantity matters: Implicatures, typicality, and

### 2016-01-31 Paper/Paper.Rmd
fixed equation reference (used \tag{1} in 7383 .. 7383)
fixed van tiel reference, removed table 1 reference and replaced with hardcoded 'Table 1'

@@
 
-$$p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}$$
+$$p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \tag{1}$$
 
@@
 
-Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation \ref{eq:rsa}.
+Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation $(1)$.
 As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
@@
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Table \ref{fig:allScalesTable): 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
 
-Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table \ref{fig:xtable}).
+Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table 1).
 The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
@@
 We found that the best predictions came when a range of scale-dependent negative and neutral alternatives were added to the implicature computation, suggesting the importance of considering non-entailment alternatives.
-This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2015].
+This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2014].
 

### 2016-01-31 Paper/Paper.tex
fixed equation reference (used \tag{1} in 7383 .. 7383)
fixed van tiel reference, removed table 1 reference and replaced with hardcoded 'Table 1'

@@
 
-\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \label{eq:rsa}\]
+\[p_{L_1}(m \mid u) \propto p_{S_1} (u \mid m) p(m) \tag{1}\]
 
@@
 Experiment 3 was conducted to measure pragmatic
-judgments---\(p_{L_1}(m \mid u)\) in Equation \ref{eq:rsa}. As in
-Experiment 1, we include several conditions to test inferences in the
-presence of different alternative sets. In the two alternatives
-condition, participants made judgments for items included in the
-entailment scales. In the four alternatives condition, participants made
-judgments for the entailment items and also the top two alternatives
-elicited for each scale in Experiment 2. Including two conditions with
-differing alternatives allowed us to rule out the potential effects of
-having a larger set of alternatives during the pragmatic judgment
-elicitation and also provided two sets of human judgments to compare
-with model
+judgments---\(p_{L_1}(m \mid u)\) in Equation \((1)\). As in Experiment
+1, we include several conditions to test inferences in the presence of
+different alternative sets. In the two alternatives condition,
+participants made judgments for items included in the entailment scales.
+In the four alternatives condition, participants made judgments for the
+entailment items and also the top two alternatives elicited for each
+scale in Experiment 2. Including two conditions with differing
+alternatives allowed us to rule out the potential effects of having a
+larger set of alternatives during the pragmatic judgment elicitation and
+also provided two sets of human judgments to compare with model
 predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
@@
 computed. We considered four different alternative sets, with empirical
-measurements corresponding to those shown in Table
-\textbackslash{}ref\{fig:allScalesTable): 1) the two alternatives in the
-classic entailment scales, 2) those two alternatives with the addition
-of a generic negative alternative, 3) the expanded set of four
-alternatives tested in Experiment 1, and 4) the expanded set of five
-alternatives tested in Experiment 1.
+measurements corresponding to those shown in Figure
+\ref{fig:allScalesTable}: 1) the two alternatives in the classic
+entailment scales, 2) those two alternatives with the addition of a
+generic negative alternative, 3) the expanded set of four alternatives
+tested in Experiment 1, and 4) the expanded set of five alternatives
+tested in Experiment 1.
 
 Model fit with human judgments was significantly improved by the
-inclusion of alternatives beyond the entailment items (Table
-\ref{fig:xtable}). The two alternatives model contained only entailment
-items, which, under classic accounts, should be sufficient to generate
-implicature, but fit to data was quite poor with these items. The
-addition of a generic negative element produced some gains in
-performance, but much higher performance was found when we included four
-and five alternatives, with the alternatives derived empirically for the
-specific scale we used. An example fit for the five-alternative model is
-shown in Figure \ref{fig:fiveAltsScatter}.
+inclusion of alternatives beyond the entailment items (Table 1). The two
+alternatives model contained only entailment items, which, under classic
+accounts, should be sufficient to generate implicature, but fit to data
+was quite poor with these items. The addition of a generic negative
+element produced some gains in performance, but much higher performance
+was found when we included four and five alternatives, with the
+alternatives derived empirically for the specific scale we used. An
+example fit for the five-alternative model is shown in Figure
+\ref{fig:fiveAltsScatter}.
 
@@
 different lexical scales produce strikingly different patterns of
-inference ({\textbf{???}}).
+inference (Tiel, 2014).
 

### 2016-01-31 Paper/Paper.Rmd
first eyoon edits, need to fix stuhmuller umlaute

@@
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
-A Gricean account of this phenomenon assumes listeners reason about the meaning the speaker intended by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
-According to this account, a listener will infer that the speaker must have intended that Alice did not eat all the cookies because otherwise it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
+A Gricean account of this phenomenon assumes listeners reason about a speaker's intended meaning by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
+According to this account, a listener will infer that the speaker must have intended that Alice did not eat all the cookies because it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
 
@@
 
-@franke2014 used an RSA-style model to assess what alternatives a speaker would need to consider in order to produce the typicality/felicity ratings reported by @degen2015 and @vantiel2014.
+@franke2014 used an RSA-style model to assess what alternatives a speaker would need to consider in order to produce the typicality/felicity ratings reported by @degen2015 and @vantiel2014 for the scale *some*/*all*.
 In order to do this, @franke2014's model assigned weights to a set of alternative numerical expressions.
-Surprisingly, along with weighting *one* highly (a conclusion that was supported by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative.
+Surprisingly, along with weighting *one* highly (a conclusion that was supported by the empirical work), the best-fitting model assigned substantial weight to *none* as an alternative to *some*.
 This finding was especially surprising considering the emphasis of standard theories on scalar items that stand in entailment relationships with one another (e.g.

### 2016-01-31 Paper/Paper.tex
first eyoon edits, need to fix stuhmuller umlaute

@@
 generally. A Gricean account of this phenomenon assumes listeners reason
-about the meaning the speaker intended by incorporating knowledge about
-a) alternative scalar items a speaker could have used (such as
-\emph{all}) and b) the relative informativity of using such alternatives
-(Grice, 1975). According to this account, a listener will infer that the
-speaker must have intended that Alice did not eat all the cookies
-because otherwise it would have been underinformative to use the
-descriptor \emph{some} when the alternative \emph{all} could have been
-used just as easily.
+about a speaker's intended meaning by incorporating knowledge about a)
+alternative scalar items a speaker could have used (such as \emph{all})
+and b) the relative informativity of using such alternatives (Grice,
+1975). According to this account, a listener will infer that the speaker
+must have intended that Alice did not eat all the cookies because it
+would have been underinformative to use the descriptor \emph{some} when
+the alternative \emph{all} could have been used just as easily.
 
@@
 understanding inferences about meaning in context (Frank \& Goodman,
-2012; N. D. Goodman \& Stuhlm{ü}ller, 2013). RSA models frame language
+2012; N. D. Goodman \& Stuhlmuller, 2013). RSA models frame language
 understanding as a special case of social cognition, in which listeners
@@
 typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
-Tiel (2014). In order to do this, Franke (2014)'s model assigned weights
-to a set of alternative numerical expressions. Surprisingly, along with
-weighting \emph{one} highly (a conclusion that was supported by the
-empirical work), the best-fitting model assigned substantial weight to
-\emph{none} as an alternative. This finding was especially surprising
-considering the emphasis of standard theories on scalar items that stand
-in entailment relationships with one another (e.g. \emph{one} entails
-\emph{some} even if it is not classically considered to be part of the
-scale).
+Tiel (2014) for the scale \emph{some}/\emph{all}. In order to do this,
+Franke (2014)'s model assigned weights to a set of alternative numerical
+expressions. Surprisingly, along with weighting \emph{one} highly (a
+conclusion that was supported by the empirical work), the best-fitting
+model assigned substantial weight to \emph{none} as an alternative to
+\emph{some}. This finding was especially surprising considering the
+emphasis of standard theories on scalar items that stand in entailment
+relationships with one another (e.g. \emph{one} entails \emph{some} even
+if it is not classically considered to be part of the scale).
 
@@
 
-Goodman, N. D., \& Stuhlm{ü}ller, A. (2013). Knowledge and implicature:
+Goodman, N. D., \& Stuhlmuller, A. (2013). Knowledge and implicature:
 Modeling language understanding as social cognition. \emph{Topics in

### 2016-01-31 Paper/Paper.Rmd
changes to Exp1 results and descr. Changes to Exp 2 results. Added model names in allScalesTable fig1

@@
 Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g.
-*liked/loved,* or *palatable/delicious.*).
+*liked*/*loved,* or *palatable*/*delicious.*).
 Making use of some of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
@@
 We then use experiments to measure three components of the model.
-First, to measure literal semantics ${p_{L_0} (m \mid u)}$ (we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 1).
+First, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 1).
 Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2).
@@
 Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
-We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two alternatives ("entailment"), four alternatives, and five alternatives.
-The two alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 1 is to test whether the set of alternatives queried during literal semantic elicitation impacts compatibility judgments.
-(If it does we should see differences in compatibility judgments for shared items between experiments.)
+We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
+The two-alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
+The four and five-alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 1 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
+If it does we should see differences in these judgments for shared items between experiments.
 
@@
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two alternative condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternative condition was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
-In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
+In the two-alternatives condition (Experiment 1a), `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition (Experiment 1b),  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+In the five alternative condition (Experiment 1c), `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
 
@@
 
-The two alternatives condition included only the scalar pairs from @vantiel2014.
-The four alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
-The five alternatives condition included the four previous items plus one more neutral item chosen from those alternatives generated in Experiment 2.
-See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each condition.
+The two-alternatives condition included only the scalar pairs from @vantiel2014.
+The four-alternatives condition included the two scalar items plus the top two-alternatives generated for each scalar family by participants in Experiment 2.
+The five-alternatives condition included the four previous items plus one more neutral item chosen from those alternatives generated in Experiment 2.
+See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each model.
 
@@
 Several trends are visible.
-First, in each scale, the alternatives spanned the star scale, such that there were alternatives that were highly compatible with both the lowest and highest numbers of stars.
-Second, there was clear variability between scalar families.
-For example, compatibility judgments for the top items in the *memorable / unforgettable* scale were more similar than those for *good / excellent* or *liked / loved*.
-Finally, there was substantial consistency in ratings for items that were repeated across experiments, suggesting that this paradigm elicited stable judgments from participants.
-
+First, in each scale, the alternatives spanned the star scale, such that there were scalar items that were highly compatible with both the lowest and highest numbers of stars.
+Second, participant compatibility judgments match intuitive literal semantics.
+That is, both weaker (e.g.
+*some* or *good*) and stronger (e.g.
+*all* or *excellent*) entailment items were seen as compatible with five-star ratings.
+This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
+We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual scalar items are consistent in Experiments 1a,b,c).
 ```{r literalListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
@@
 ```
-To test our secondary hypothesis, that the different sets of scalar items might result in differences in compatibility judgments between experiments, we ran a mixed effects model.
-We regressed compatibility judgments on scale, number of stars and condition, with subject and word level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the experiment variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+To examine this last issue of consistency across experiments (our secondary hypothesis) we ran a mixed effects model regressing compatibility judgments on scale, number of stars and experimental condition, with subject and word level random effects, which was the maximal structure that converged.
+Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the experiment condition variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+These findings suggest that literal semantic intuitions are not effected by the set of alternatives queried in our paradigm.
+This finding is important because literal semantic data generated in these three conditions are used to simulate the effects of different alternative sets on implicature generation in our model.
 
@@
 
-To elicit empirical alternatives for the scales we used in Experiment 1, we adopted a modified cloze task inspired by Experiment 3 of @vantiel2014.
+To examine the effect different alternative sets have on implicature, we needed a way of selecting plausible alternatives.
+We addressed this issue by adopting a modified cloze task to elicit empirical alternatives for the entailment items we used in Experiment 1a and 3a.
+This design was inspired by Experiment 3 of @vantiel2014.
 
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the 'liked \ loved' scale in Experiment 2."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the `liked \ loved' scale in Experiment 2."}
 
@@
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity."}
+Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity."}
 # Get zero's in data frame
@@
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
-Alternative distributions for the other scalar pairs (e.g..
-*good/excellent*, *memorable/unforgettable*) were similarly long-tailed.
+We expanded our alternative set from only entailment items (Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by including the top two alternatives elicited for each scale in Experiment 2.
+For example, the top two alternatives for the *liked*/*loved* scale were *hated* and *disliked* and were included in four-alternatives model runs.
+Similarly, neutral items (e.g.
+*okay* in the *good*/*excellent* scalar family) were chosen from among the set of alternatives elicited in Experiment 2.
+Alternative set distributions for the other scalar families (e.g.
+*good*/*excellent*, *memorable*/*unforgettable*) were similarly long-tailed.
+See Figure \ref{fig:allScalesTable} for the complete list of alternatives we used from Experiment 2.
 
@@
 As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
-In the two alternatives condition, participants made judgments for items included in the entailment scales.
-In the four alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 2.
-Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+In the two-alternatives condition, participants made judgments for items included in the entailment scales.
+In the four-alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
+Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 We recruited 100 participants from AMT, 50 for each condition.
-Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two-alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
 In the four alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
@@
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
 
 Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table 1).
-The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
+The two-alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
 The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
@@
 
-```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3, four alternatives condition, are plotted against model predictions.
+```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions.
 Colors show the star rating for individual judgments."}

### 2016-01-31 Paper/Paper.Rmd
added condition descriptors to Exp 3 description. Changed topic sentence in Exp 3 results

@@
 As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
-In the two-alternatives condition, participants made judgments for items included in the entailment scales.
-In the four-alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
+In the two-alternatives condition (Experiment 3a), participants made judgments for items included in the entailment scales.
+In the four-alternatives condition (Experiment 3b), participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
 Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
@@
 We recruited 100 participants from AMT, 50 for each condition.
-Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two-alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
-In the four alternative condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
+Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+In the four alternatives condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
 
@@
 
-To test our secondary hypothesis, that the different sets of scalar items in the two conditions might result in differences in pragmatic judgments for the same items, we fit a mixed effects model.
-We regressed pragmatic judgments on scale and condition with subject- and word-level random effects, which was the maximal structure that converged.
-There were no significant differences between conditions, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+To rule out the potential effects of having a larger set of alternatives  during  the  pragmatic  judgment  elicitation, we fit a mixed effects model.
+We regressed pragmatic judgments on scale and experimental condition with subject- and word-level random effects, which was the maximal structure that converged.
+There were no significant differences between conditions 3a and 3b, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 
@@
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives tested in Experiment 1, and 4) the expanded set of five alternatives tested in Experiment 1.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative \footnote{literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline "none" style semantics in which the scalar item is only compatible with 1 star}, 3) the expanded set of four alternatives tested in Experiment 1b, and 4) the expanded set of five alternatives tested in Experiment 1c.
 
@@
 While improvements in model fit were substantial as we moved from two to four alternatives, we saw only a minor increase in fit from the move to five alternatives.
-One possible explanation is that alternatives are differentially salient in context, and moving to larger sets would consider weighting the alternatives differentially [as @franke2014 did].
+One possible explanation is that alternatives are differentially salient in context, and in moving to larger sets we should consider weighting the alternatives differentially [as @franke2014 did].
 Preliminary simulations using weightings derived from Experiment 2 provide some support for this idea but would require further empirical work for confirmation.

### 2016-01-31 Paper/Paper.Rmd
shrunk literal listener plots to heigh=4

@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c.
 Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.

### 2016-02-01 Paper/Paper.Rmd
bp pass sunday afternoon

@@
 Similar scales exist for non-quantifier scales, e.g.
-*loved* entails *liked* (and hence "I liked the movie" implicates that I didn't love it).
+*loved* entails *liked* (and hence "I liked the movie" implicates I didn't love it).
 
@@
 
-$$p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)$$
+$$p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u) \tag{2}$$
 
@@
 
-$$p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}$$
+$$p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]} \tag{3}$$
 
@@
 The two-alternatives condition included only the scalar pairs from @vantiel2014.
-The four-alternatives condition included the two scalar items plus the top two-alternatives generated for each scalar family by participants in Experiment 2.
-The five-alternatives condition included the four previous items plus one more neutral item chosen from those alternatives generated in Experiment 2.
-See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each model.
+The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
+The five-alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 2.
+See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each condition.
 
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiments 1a,b,c.
-Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiment 1.
+Proportion of participants indicating compatibility (answering `yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
-Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items."}
+Colors indicate the specific condition (1a,b,c) with conditions including different numbers of items."}
 
@@
 ```
-To examine this last issue of consistency across experiments (our secondary hypothesis) we ran a mixed effects model regressing compatibility judgments on scale, number of stars and experimental condition, with subject and word level random effects, which was the maximal structure that converged.
+To examine this last issue of consistency across experiments (our secondary hypothesis) we fit a mixed effects model, regressing compatibility judgment on scale, number of stars and experimental condition, with subject- and word-level random effects, which was the maximal structure that converged.
 Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the experiment condition variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
@@
 
-To examine the effect different alternative sets have on implicature, we needed a way of selecting plausible alternatives.
-We addressed this issue by adopting a modified cloze task to elicit empirical alternatives for the entailment items we used in Experiment 1a and 3a.
+To examine the effect different alternative sets have on implicature, we needed a way of expanding alternative sets beyond entailment pairs.
+We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
 This design was inspired by Experiment 3 of @vantiel2014.
@@
         legend.position = "bottom",
-        legend.margin = unit(.02,"in"),
+        # legend.margin = unit(.02,"in"),
         legend.key = element_blank(), 
-        legend.key.size = unit(.1, "in"),
-        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
+        # legend.key.size = unit(.1, "in"),
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, size = 6),
         axis.text.y = element_text(size = 10),
@@
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity."}
+Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity in reporting."}
 # Get zero's in data frame
@@
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
-We expanded our alternative set from only entailment items (Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by including the top two alternatives elicited for each scale in Experiment 2.
-For example, the top two alternatives for the *liked*/*loved* scale were *hated* and *disliked* and were included in four-alternatives model runs.
+We expanded our alternative set from only entailment items (items used in Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by including the top two alternatives elicited for each scale in Experiment 2.
+For example, the top two alternatives for the *liked*/*loved* scale were *hated* and *disliked* and were included in four-alternatives model.
 Similarly, neutral items (e.g.
-*okay* in the *good*/*excellent* scalar family) were chosen from among the set of alternatives elicited in Experiment 2.
-Alternative set distributions for the other scalar families (e.g.
-*good*/*excellent*, *memorable*/*unforgettable*) were similarly long-tailed.
+*okay* in the *good*/*excellent* scale) were chosen from among the set of alternatives elicited in Experiment 2.
 See Figure \ref{fig:allScalesTable} for the complete list of alternatives we used from Experiment 2.
@@
 In the four-alternatives condition (Experiment 3b), participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
-Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 *good*/*excellent*).
-We include only the original entailment pairs in this figure for simplicity.
 Several trends are visible.
@@
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative \footnote{literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline "none" style semantics in which the scalar item is only compatible with 1 star}, 3) the expanded set of four alternatives tested in Experiment 1b, and 4) the expanded set of five alternatives tested in Experiment 1c.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative\footnote{Literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline ``none" style semantics in which the scalar item is only compatible with 1 star.}, 3) the expanded set of four alternatives tested in Experiment 1b, and 4) the expanded set of five alternatives tested in Experiment 1c.
 

### 2016-02-01 Paper/Paper.tex
bp pass sunday afternoon

@@
 \emph{loved} entails \emph{liked} (and hence ``I liked the movie''
-implicates that I didn't love it).
+implicates I didn't love it).
 
@@
 difference in the strength of scalar implicature across a variety of
-scalar pairs (e.g. \emph{liked/loved,} or \emph{palatable/delicious.}).
-Making use of some of this diversity allows us to investigate the ways
-that different alternative sets give rise to implicatures of different
-strengths across scales.
+scalar pairs (e.g. \emph{liked}/\emph{loved,} or
+\emph{palatable}/\emph{delicious.}). Making use of some of this
+diversity allows us to investigate the ways that different alternative
+sets give rise to implicatures of different strengths across scales.
 
@@
 
-\[p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u)\]
+\[p_{S_1}(u \mid m) \propto p_{L_0} (m \mid u) \tag{2}\]
 
@@
 
-\[p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]}\]
+\[p_{S_1}(u \mid m) \propto e^{-\alpha[-log(p_{L_0}(m \mid u)) - C(u)]} \tag{3}\]
 
@@
 components of the model. First, to measure literal semantics
-\({p_{L_0} (m \mid u)}\) (we ask experiment participants to judge
-whether a message is compatible with a particular meaning (Experiment
-1). Second, to generate a set of plausible alternative messages in
-\(U\), we elicit alternatives directly (Experiment 2). Lastly, to obtain
-human \(L_1\) pragmatic judgments, we ask participants to interpret a
+\({p_{L_0} (m \mid u)}\) we ask experiment participants to judge whether
+a message is compatible with a particular meaning (Experiment 1).
+Second, to generate a set of plausible alternative messages in \(U\), we
+elicit alternatives directly (Experiment 2). Lastly, to obtain human
+\(L_1\) pragmatic judgments, we ask participants to interpret a
 speaker's utterances (Experiment 3).
@@
 corresponding to the sets of alternatives within a scale that
-participants were presented with: two alternatives (``entailment''),
-four alternatives, and five alternatives. The two alternatives condition
+participants were presented with: two-alternatives (``entailment''),
+four-alternatives, and five-alternatives. The two-alternatives condition
 makes a test of the hypothesis that the two members of the classic Horn
@@
 predict the strength of listeners' pragmatic inference. The four and
-five alternatives conditions then add successively more alternatives to
+five-alternatives conditions then add successively more alternatives to
 test whether including a larger number of alternatives will increase
 model
-fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
 A secondary goal of Experiment 1 is to test whether the set of
-alternatives queried during literal semantic elicitation impacts
-compatibility judgments. (If it does we should see differences in
-compatibility judgments for shared items between experiments.)
+alternatives queried during literal semantic elicitation impacts literal
+semantic judgments. If it does we should see differences in these
+judgments for shared items between experiments.
 
@@
 Conditions were run sequentially. In each condition we recruited 30
-participants from Amazon Mechanical Turk (AMT). In the two alternative
-condition, 16 participants were excluded for either failing to pass two
-training trails or were not native English speakers, leaving a total
-sample of 14
-participants.\footnote{The majority of respondent data excluded from the two alternative condition was caused by failure to pass training trials.
+participants from Amazon Mechanical Turk (AMT). In the two-alternatives
+condition (Experiment 1a), 16 participants were excluded for either
+failing to pass two training trails or were not native English speakers,
+leaving a total sample of 14
+participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
-In the four alternative condition, 7 participants were excluded for
-either failing to pass two training trials or were not native English
-speakers, leaving a total sample of 23 participants. In the five
-alternative condition, 3 participants were excluded for either failing
-to pass two training trials or were not native English speakers, leaving
-a total sample of 27.
+In the four alternative condition (Experiment 1b), 7 participants were
+excluded for either failing to pass two training trials or were not
+native English speakers, leaving a total sample of 23 participants. In
+the five alternative condition (Experiment 1c), 3 participants were
+excluded for either failing to pass two training trials or were not
+native English speakers, leaving a total sample of 27.
 
@@
 
-The two alternatives condition included only the scalar pairs from Tiel
-(2014). The four alternatives condition included the two scalar items
-plus the top two alternatives generated for each scalar family by
-participants in Experiment 2. The five alternatives condition included
+The two-alternatives condition included only the scalar pairs from Tiel
+(2014). The four-alternatives condition included the two scalar items
+plus the top two-alternatives generated for each scalar family by
+participants in Experiment 2. The five-alternatives condition included
 the four previous items plus one more neutral item chosen from those
@@
 \ref{fig:allScalesTable} for the complete list of alternatives used in
-each condition.
+each model.
 
@@
 are visible. First, in each scale, the alternatives spanned the star
-scale, such that there were alternatives that were highly compatible
-with both the lowest and highest numbers of stars. Second, there was
-clear variability between scalar families. For example, compatibility
-judgments for the top items in the \emph{memorable / unforgettable}
-scale were more similar than those for \emph{good / excellent} or
-\emph{liked / loved}. Finally, there was substantial consistency in
-ratings for items that were repeated across experiments, suggesting that
-this paradigm elicited stable judgments from participants.
+scale, such that there were scalar items that were highly compatible
+with both the lowest and highest numbers of stars. Second, participant
+compatibility judgments match intuitive literal semantics. That is, both
+weaker (e.g. \emph{some} or \emph{good}) and stronger (e.g. \emph{all}
+or \emph{excellent}) entailment items were seen as compatible with
+five-star ratings. This means participants' compatibility judgements
+reflect literal semantic intuitions, not enriched pragmatic judgments.
+We see clear variability between scalar families (literal semantic
+distributions for \emph{memorable} are considerably different from
+\emph{palatable}), but also substantial consistency across conditions
+(compatibility judgments for individual scalar items are consistent in
+Experiments 1a,b,c).
 
-To test our secondary hypothesis, that the different sets of scalar
-items might result in differences in compatibility judgments between
-experiments, we ran a mixed effects model. We regressed compatibility
-judgments on scale, number of stars and condition, with subject and word
-level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between Experiment 1a and
-1c, \(b =\)-0.05, \(Z =\) -0.53, \(p =\) 0.59 or between 1b and 1c,
-\(b =\) -0.04, \(Z =\) -0.52 \(p =\) 0.6 and the addition of condition
-as a predictor did not significantly improve model fit when compared to
-a model without the experiment variable using ANOVA \(\chi^2(\) 2
-\() =\) 0.43, \(p =\) 0.81.
+To examine this last issue of consistency across experiments (our
+secondary hypothesis) we ran a mixed effects model regressing
+compatibility judgments on scale, number of stars and experimental
+condition, with subject and word level random effects, which was the
+maximal structure that converged. Results indicate no significant
+differences between Experiment 1a and 1c, \(b =\)-0.05, \(Z =\) -0.53,
+\(p =\) 0.59 or between 1b and 1c, \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
+0.6 and the addition of condition as a predictor did not significantly
+improve model fit when compared to a model without the experiment
+condition variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\) 0.81.
+These findings suggest that literal semantic intuitions are not effected
+by the set of alternatives queried in our paradigm. This finding is
+important because literal semantic data generated in these three
+conditions are used to simulate the effects of different alternative
+sets on implicature generation in our model.
 
@@
 
-To elicit empirical alternatives for the scales we used in Experiment 1,
-we adopted a modified cloze task inspired by Experiment 3 of Tiel
-(2014).
+To examine the effect different alternative sets have on implicature, we
+needed a way of selecting plausible alternatives. We addressed this
+issue by adopting a modified cloze task to elicit empirical alternatives
+for the entailment items we used in Experiment 1a and 3a. This design
+was inspired by Experiment 3 of Tiel (2014).
 
@@
 
-\caption[Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2]{Combined counts for participant-generated alternatives for the 'liked  loved' scale in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
+\caption[Combined counts for participant-generated alternatives for the `liked  loved' scale in Experiment 2]{Combined counts for participant-generated alternatives for the `liked  loved' scale in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity.}\label{fig:exp2Plots}
+Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity.}\label{fig:exp2Plots}
 \end{figure*}
@@
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative
-set for the scalar items \emph{liked} and \emph{loved} (combined).
-Alternative distributions for the other scalar pairs (e.g..
-\emph{good/excellent}, \emph{memorable/unforgettable}) were similarly
-long-tailed.
+set for the scalar items \emph{liked} and \emph{loved} (combined). We
+expanded our alternative set from only entailment items (Experiments 1a,
+3a) to four alternatives (Experiments 1b, 3b) by including the top two
+alternatives elicited for each scale in Experiment 2. For example, the
+top two alternatives for the \emph{liked}/\emph{loved} scale were
+\emph{hated} and \emph{disliked} and were included in four-alternatives
+model runs. Similarly, neutral items (e.g. \emph{okay} in the
+\emph{good}/\emph{excellent} scalar family) were chosen from among the
+set of alternatives elicited in Experiment 2. Alternative set
+distributions for the other scalar families (e.g.
+\emph{good}/\emph{excellent}, \emph{memorable}/\emph{unforgettable})
+were similarly long-tailed. See Figure \ref{fig:allScalesTable} for the
+complete list of alternatives we used from Experiment 2.
 
@@
 1, we include several conditions to test inferences in the presence of
-different alternative sets. In the two alternatives condition,
-participants made judgments for items included in the entailment scales.
-In the four alternatives condition, participants made judgments for the
-entailment items and also the top two alternatives elicited for each
-scale in Experiment 2. Including two conditions with differing
-alternatives allowed us to rule out the potential effects of having a
-larger set of alternatives during the pragmatic judgment elicitation and
-also provided two sets of human judgments to compare with model
-predictions.\footnote{Note that alternatives in the four alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+different alternative sets. In the two-alternatives condition
+(Experiment 3a), participants made judgments for items included in the
+entailment scales. In the four-alternatives condition (Experiment 3b),
+participants made judgments for the entailment items and also the top
+two-alternatives elicited for each scale in Experiment 2. Including two
+conditions with differing alternatives allowed us to rule out the
+potential effects of having a larger set of alternatives during the
+pragmatic judgment elicitation and also provided two sets of human
+judgments to compare with model
+predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 non-native English speakers, leaving a total sample of 41 participants.
-In the four alternative condition, data from 7 participants was excluded
-after participants either failed to pass two training trials or were not
-native English speakers, leaving 43 participants.
+In the four alternatives condition, data from 7 participants was
+excluded after participants either failed to pass two training trials or
+were not native English speakers, leaving 43 participants.
 
@@
 
-To test our secondary hypothesis, that the different sets of scalar
-items in the two conditions might result in differences in pragmatic
-judgments for the same items, we fit a mixed effects model. We regressed
-pragmatic judgments on scale and condition with subject- and word-level
-random effects, which was the maximal structure that converged. There
-were no significant differences between conditions, \(b =\) 0.05, \(t(\)
-150 \() =\) 1.04, \(p =\) 0.3 and the addition of the condition
-predictor did not significantly improve model fit when compared to a
-model without that variable \(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
+To rule out the potential effects of having a larger set of alternatives
+during the pragmatic judgment elicitation, we fit a mixed effects model.
+We regressed pragmatic judgments on scale and experimental condition
+with subject- and word-level random effects, which was the maximal
+structure that converged. There were no significant differences between
+conditions 3a and 3b, \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3
+and the addition of the condition predictor did not significantly
+improve model fit when compared to a model without that variable
+\(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
 
@@
 measurements corresponding to those shown in Figure
-\ref{fig:allScalesTable}: 1) the two alternatives in the classic
+\ref{fig:allScalesTable}: 1) the two-alternatives in the classic
 entailment scales, 2) those two alternatives with the addition of a
-generic negative alternative, 3) the expanded set of four alternatives
-tested in Experiment 1, and 4) the expanded set of five alternatives
-tested in Experiment 1.
+generic negative alternative
+\footnote{literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline "none" style semantics in which the scalar item is only compatible with 1 star},
+3) the expanded set of four alternatives tested in Experiment 1b, and 4)
+the expanded set of five alternatives tested in Experiment 1c.
 
 Model fit with human judgments was significantly improved by the
-inclusion of alternatives beyond the entailment items (Table 1). The two
-alternatives model contained only entailment items, which, under classic
-accounts, should be sufficient to generate implicature, but fit to data
-was quite poor with these items. The addition of a generic negative
-element produced some gains in performance, but much higher performance
-was found when we included four and five alternatives, with the
-alternatives derived empirically for the specific scale we used. An
+inclusion of alternatives beyond the entailment items (Table 1). The
+two-alternatives model contained only entailment items, which, under
+classic accounts, should be sufficient to generate implicature, but fit
+to data was quite poor with these items. The addition of a generic
+negative element produced some gains in performance, but much higher
+performance was found when we included four and five alternatives, with
+the alternatives derived empirically for the specific scale we used. An
 example fit for the five-alternative model is shown in Figure
@@
 
-\caption[Judgments from Experiment 3, four alternatives condition, are plotted against model predictions]{Judgments from Experiment 3, four alternatives condition, are plotted against model predictions.
+\caption[Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions]{Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions.
 Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
@@
 five alternatives. One possible explanation is that alternatives are
-differentially salient in context, and moving to larger sets would
-consider weighting the alternatives differentially (as Franke, 2014
-did). Preliminary simulations using weightings derived from Experiment 2
-provide some support for this idea but would require further empirical
-work for confirmation.
+differentially salient in context, and in moving to larger sets we
+should consider weighting the alternatives differentially (as Franke,
+2014 did). Preliminary simulations using weightings derived from
+Experiment 2 provide some support for this idea but would require
+further empirical work for confirmation.
 

### 2016-02-01 Paper/Paper.Rmd
minor pass monday morning

@@
 
-Experiment 1 was conducted to approximate literal listener semantic distributions $p_{L_0}(m \mid u)$ for five pairs of scalar items taken from @vantiel2014.
+Experiment 1 was conducted to approximate literal listener semantics - $p_{L_0}(m \mid u)$ in Equation (2), for five pairs of scalar items taken from @vantiel2014.
 We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
@@
 
-Figure \ref{fig:exp2Plots} plots literal listener $p_{L0}(m|u)$ scalar item distributions for the three conditions.
+Figure \ref{fig:exp1Plots} plots literal listener $p_{L0}(m|u)$ scalar item distributions for the three conditions.
 Each row shows a unique scalar family with items ordered horizontally by valence.
@@
 Similarly, neutral items (e.g.
-*okay* in the *good*/*excellent* scale) were chosen from among the set of alternatives elicited in Experiment 2.
+*okay* in the *good*/*excellent* scale) were chosen from among the set of alternatives elicited in Experiment 2 and added to the five-alternatives model.
 See Figure \ref{fig:allScalesTable} for the complete list of alternatives we used from Experiment 2.
@@
 
-Participants were presented with a one-sentence prompt containing a target scalar item such as "Someone said they thought the food was \_____." Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
+Participants were presented with a one-sentence prompt such as "Someone said they thought the food was \_____." with a target scalar item in the blank.
+Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
 Each participant was presented with all scalar items in a random order.
@@
 
-Figure \ref{fig:exp2Plots} plots pragmatic listener judgments distributions for "weak" / "strong" scalar pairs (e.g.
+Figure \ref{fig:exp2Plots} plots pragmatic listener judgment distributions for "weak" / "strong" scalar pairs (e.g.
 *good*/*excellent*).
@@
 
-```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions.
+```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3b are plotted against five-alternatives model predictions.
 Colors show the star rating for individual judgments."}

### 2016-02-01 Paper/Paper.tex
minor pass monday morning

@@
 
-Experiment 1 was conducted to approximate literal listener semantic
-distributions \(p_{L_0}(m \mid u)\) for five pairs of scalar items taken
-from Tiel (2014). We include three conditions in Experiment 1,
+Experiment 1 was conducted to approximate literal listener semantics -
+\(p_{L_0}(m \mid u)\) in Equation (2), for five pairs of scalar items
+taken from Tiel (2014). We include three conditions in Experiment 1,
 corresponding to the sets of alternatives within a scale that
@@
 (2014). The four-alternatives condition included the two scalar items
-plus the top two-alternatives generated for each scalar family by
+plus the top two alternatives generated for each scalar family by
 participants in Experiment 2. The five-alternatives condition included
-the four previous items plus one more neutral item chosen from those
+the four previous items plus one more neutral item chosen from
 alternatives generated in Experiment 2. See Figure
 \ref{fig:allScalesTable} for the complete list of alternatives used in
-each model.
+each condition.
 
@@
 
-\caption[Literal listener judgments from Experiments 1a,b,c]{Literal listener judgments from Experiments 1a,b,c.
-Proportion of participants indicating compatibility (answering 'yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+\caption[Literal listener judgments from Experiment 1]{Literal listener judgments from Experiment 1.
+Proportion of participants indicating compatibility (answering `yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
-Colors indicate the specific experiment (1a,b,c) with experiments including different numbers of items.}\label{fig:exp1Plots}
+Colors indicate the specific condition (1a,b,c) with conditions including different numbers of items.}\label{fig:exp1Plots}
 \end{figure*}
@@
 
-Figure \ref{fig:exp2Plots} plots literal listener \(p_{L0}(m|u)\) scalar
+Figure \ref{fig:exp1Plots} plots literal listener \(p_{L0}(m|u)\) scalar
 item distributions for the three conditions. Each row shows a unique
@@
 To examine this last issue of consistency across experiments (our
-secondary hypothesis) we ran a mixed effects model regressing
-compatibility judgments on scale, number of stars and experimental
-condition, with subject and word level random effects, which was the
+secondary hypothesis) we fit a mixed effects model, regressing
+compatibility judgment on scale, number of stars and experimental
+condition, with subject- and word-level random effects, which was the
 maximal structure that converged. Results indicate no significant
@@
 To examine the effect different alternative sets have on implicature, we
-needed a way of selecting plausible alternatives. We addressed this
-issue by adopting a modified cloze task to elicit empirical alternatives
-for the entailment items we used in Experiment 1a and 3a. This design
-was inspired by Experiment 3 of Tiel (2014).
+needed a way of expanding alternative sets beyond entailment pairs. We
+addressed this issue by adopting a modified cloze task to elicit
+alternatives empirically. This design was inspired by Experiment 3 of
+Tiel (2014).
 
@@
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity.}\label{fig:exp2Plots}
+Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity in reporting.}\label{fig:exp2Plots}
 \end{figure*}
@@
 set for the scalar items \emph{liked} and \emph{loved} (combined). We
-expanded our alternative set from only entailment items (Experiments 1a,
-3a) to four alternatives (Experiments 1b, 3b) by including the top two
-alternatives elicited for each scale in Experiment 2. For example, the
-top two alternatives for the \emph{liked}/\emph{loved} scale were
-\emph{hated} and \emph{disliked} and were included in four-alternatives
-model runs. Similarly, neutral items (e.g. \emph{okay} in the
-\emph{good}/\emph{excellent} scalar family) were chosen from among the
-set of alternatives elicited in Experiment 2. Alternative set
-distributions for the other scalar families (e.g.
-\emph{good}/\emph{excellent}, \emph{memorable}/\emph{unforgettable})
-were similarly long-tailed. See Figure \ref{fig:allScalesTable} for the
+expanded our alternative set from only entailment items (items used in
+Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by
+including the top two alternatives elicited for each scale in Experiment
+2. For example, the top two alternatives for the
+\emph{liked}/\emph{loved} scale were \emph{hated} and \emph{disliked}
+and were included in four-alternatives model. Similarly, neutral items
+(e.g. \emph{okay} in the \emph{good}/\emph{excellent} scale) were chosen
+from among the set of alternatives elicited in Experiment 2 and added to
+the five-alternatives model. See Figure \ref{fig:allScalesTable} for the
 complete list of alternatives we used from Experiment 2.
@@
 judgments to compare with model
-predictions.\footnote{Note that alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
 
@@
 
-Participants were presented with a one-sentence prompt containing a
-target scalar item such as ``Someone said they thought the food was
-\_\_\_\_\_.'' Participants were then asked to generate a star rating
+Participants were presented with a one-sentence prompt such as ``Someone
+said they thought the food was \_\_\_\_\_.'' with a target scalar item
+in the blank. Participants were then asked to generate a star rating
 representing the rating they thought the reviewer likely gave. Each
@@
 
-Figure \ref{fig:exp2Plots} plots pragmatic listener judgments
+Figure \ref{fig:exp2Plots} plots pragmatic listener judgment
 distributions for ``weak'' / ``strong'' scalar pairs (e.g.
-\emph{good}/\emph{excellent}). We include only the original entailment
-pairs in this figure for simplicity. Several trends are visible. First,
-in each scale participants generated implicatures. They were
-substantially less likely to assign high star ratings to weaker scalar
-terms, despite the literal semantic compatibility of those terms with
-those states shown in Experiment 1. Second, the size of the difference
-between strong and weak scalar items varied considerably across scales,
-consistent with previous work (Tiel, 2014).
+\emph{good}/\emph{excellent}). Several trends are visible. First, in
+each scale participants generated implicatures. They were substantially
+less likely to assign high star ratings to weaker scalar terms, despite
+the literal semantic compatibility of those terms with those states
+shown in Experiment 1. Second, the size of the difference between strong
+and weak scalar items varied considerably across scales, consistent with
+previous work (Tiel, 2014).
 
@@
 entailment scales, 2) those two alternatives with the addition of a
-generic negative alternative
-\footnote{literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline "none" style semantics in which the scalar item is only compatible with 1 star},
+generic negative
+alternative\footnote{Literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline ``none" style semantics in which the scalar item is only compatible with 1 star.},
 3) the expanded set of four alternatives tested in Experiment 1b, and 4)
@@
 
-\caption[Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions]{Judgments from Experiment 3, four-alternatives condition, are plotted against model predictions.
+\caption[Judgments from Experiment 3b are plotted against five-alternatives model predictions]{Judgments from Experiment 3b are plotted against five-alternatives model predictions.
 Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}

### 2016-02-01 Paper/Paper.Rmd
tweaks in meeting

@@
 A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
-We collect empirical measurements of speaker and listener judgments and use these as inputs to a computational model of pragmatic inference.
-This approach allows us to test hypotheses about how well different sets of alternatives predict implicature performance across a range of different scales.
-Our findings suggest that comprehenders likely consider a much broader set of alternatives beyond those entailed by the initial description.
+To address this question, we collect empirical measurements of speaker and listener judgments about varying sets of alternatives across a range of scales and use these as inputs to a computational model of pragmatic inference.
+This approach allows us to test hypotheses about how well different sets of alternatives predict implicature performance.
+Our findings suggest that comprehenders likely consider a broader set of alternatives beyond those logically entailed by the initial message.
 
@@
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
-A Gricean account of this phenomenon assumes listeners reason about a speaker's intended meaning by incorporating knowledge about a) alternative scalar items a speaker could have used (such as *all*) and b) the relative informativity of using such alternatives [@grice1975].
+A Gricean account of this phenomenon assumes listeners reason about a speaker's intended meaning by incorporating knowledge about A) alternative scalar items a speaker could have used (such as *all*) and B) the relative informativity of using such alternatives [@grice1975].
 According to this account, a listener will infer that the speaker must have intended that Alice did not eat all the cookies because it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
@@
 Similar scales exist for non-quantifier scales, e.g.
-*loved* entails *liked* (and hence "I liked the movie" implicates I didn't love it).
+*loved* entails *liked* (and hence "I liked the movie" implicates that I didn't love it).
 
@@
 And in a different paradigm, @vantiel2014 found converging evidence that *some* was judged to be atypical for small quantities.
-These data provide indirect evidence about a broader set of alternatives: since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*, for example) reduced the felicity of *some* via a pragmatic inference.
+These data provide indirect evidence about a broader set of alternatives.
+Since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*, for example) reduced the felicity of *some* via a pragmatic inference.
 
@@
 To gain empirical traction on this issue, however, we broaden the set of scales we consider.
-Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g.
-*liked*/*loved,* or *palatable*/*delicious.*).
-Making use of some of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
+Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g., *liked* / *loved,* *palatable* / *delicious*).
+Making use of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
 
@@
 These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgments.
-To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgments, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to model listener judgments with high accuracy.
+To preview our results: we find that standard entailment alternatives do not allow us to fit participants' judgments, but that expanding the range of alternatives empirically (by asking participants to generate alternative messages) allows us to predict listeners' pragmatic judgments with high accuracy.
 
@@
 This model simulates the judgments of a pragmatic listener who wants to infer a speaker's intended meaning $m$ from her utterance $u$.
-For simplicity, we present a version of this model in which there is only full recursion: that is, the pragmatic listener reasons about a pragmatic speaker, who in turn reasons about a "literal listener." We assume throughout that this computation takes place in a signaling game [@lewis1969] with a fixed set of possible meanings $m \in M$ and a fixed possible set of utterances $u \in U$, with both known to both participants.
-Our goal in this study is to determine what utterances fall in $U$.
+For simplicity, we present a version of this model in which there is only one full recursion: The pragmatic listener reasons about a pragmatic speaker, who in turn reasons about a "literal listener." We assume throughout that this computation takes place in a signaling game [@lewis1969] with a fixed set of possible meanings $m \in M$ and a fixed possible set of utterances $u \in U$, with both known to both participants.
+Our goal in this study is to determine which utterances fall in $U$.
 
@@
 This prior represents the listener's _a priori_ expectations about plausible meanings, independent of the utterance.
-Because our experiments take place in a context in which listeners should have very little expectation about which meanings speakers want to convey, for simplicity we assume a uniform prior $p(m) \propto 1$.
+Because our experiments take place in a context in which listeners should have very little expectation about which meanings speakers want to convey, for simplicity we assume a uniform prior where $p(m) \propto 1$.
 
@@
 \noindent where $C(u)$ is the cost of a particular utterance, $-log(p_{L_0})$ represents the _surprisal_ of the message for the literal listener (the information content of the utterance), and $\alpha$ is a parameter in a standard choice rule.
-If $\alpha=0$, speakers choose randomly and as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative.
+If $\alpha=0$, speakers choose randomly; as $\alpha \rightarrow \infty$, they greedily choose the highest probability alternative.
 In our simulations below, we treat $\alpha$ as a free parameter and fit it to the data.
@@
 To instantiate our signaling game with a tractable message set $M$, in our studies we adopt the world of restaurant reviews as our communication game.
-We assume that speakers and listeners are trying to communicate the number of stars in an online restaurant review (where $m \in \{1, 2, 3, 4, 5\}$).
+We assume that speakers and listeners are trying to communicate the number of stars in an online restaurant review (where $m \in \{1...5\}$).
 We then use experiments to measure three components of the model.
@@
 
-```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Stimuli for Experiments 1, 2, and 3"}
+```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Alternative sets for Experiments 1, 2, and 3."}
 
@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \`liked.\' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \`liked.\'"}
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \"liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \"liked.\""}
 
@@
 
-Experiment 1 was conducted to approximate literal listener semantics - $p_{L_0}(m \mid u)$ in Equation (2), for five pairs of scalar items taken from @vantiel2014.
+Experiment 1 was conducted to approximate literal listener semantics---$p_{L_0}(m \mid u)$ in Equation (2)---for five pairs of scalar items taken from @vantiel2014.
 We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
@@
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two-alternatives condition (Experiment 1a), `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition (Experiment 1b),  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
-In the five alternative condition (Experiment 1c), `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or were not native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
+In the two-alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
 
@@
 
-The two-alternatives condition included only the scalar pairs from @vantiel2014.
+The two-alternatives condition included only the two terms in the pairs from van Tiel (2014).
 The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
@@
   # scale_colour_solarized() + 
+  scale_colour_manual(values=c("#dc322f","#268bd2","#859900")) + 
   theme_bw() +
@@
 
-Figure \ref{fig:exp1Plots} plots literal listener $p_{L0}(m|u)$ scalar item distributions for the three conditions.
+Figure \ref{fig:exp1Plots} plots the estimated literal listener semantics for the three conditions.
 Each row shows a unique scalar family with items ordered horizontally by valence.
@@
 This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
-We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual scalar items are consistent in Experiments 1a,b,c).
+We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual scalar items are consistent across conditions).
+
 ```{r literalListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
@@
 ```
-To examine this last issue of consistency across experiments (our secondary hypothesis) we fit a mixed effects model, regressing compatibility judgment on scale, number of stars and experimental condition, with subject- and word-level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between Experiment 1a and 1c, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between 1b and 1c, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the experiment condition variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+
+To examine this last issue of consistency across conditions (our secondary hypothesis) we fit a mixed effects model, regressing compatibility judgment on scale, number of stars and experimental condition, with subject- and word-level random effects, which was the maximal structure that converged.
+Results indicate no significant differences between two- and five-alternative conditions, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between four- and five-alternative conditions, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the condition variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
 These findings suggest that literal semantic intuitions are not effected by the set of alternatives queried in our paradigm.
@@
 ggplot(subset(listeners, plotThis == TRUE),
-       aes(x = stars, y = listener.p, col = `Scalar type`, lty = Condition)) + 
+       aes(x = stars, y = listener.p, lty = `Scalar type`, col = Condition)) + 
   geom_line() + 
@@
   theme_bw() +
+  scale_colour_manual(values=c("#268bd2","#859900")) + 
   theme(strip.text.x = element_text(size = 6),
@@
 
-Experiment 3 was conducted to measure pragmatic judgments---$p_{L_1}(m \mid u)$ in Equation $(1)$.
+Experiment 3 was conducted to measure pragmatic judgments.
 As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
-In the two-alternatives condition (Experiment 3a), participants made judgments for items included in the entailment scales.
-In the four-alternatives condition (Experiment 3b), participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
+In the two-alternatives condition, participants made judgments for items included in the entailment scales.
+In the four-alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
 Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}

### 2016-02-01 Paper/Paper.tex
tweaks in meeting

@@
 informativity, but it remains an open question precisely what these
-alternatives are. We collect empirical measurements of speaker and
-listener judgments and use these as inputs to a computational model of
-pragmatic inference. This approach allows us to test hypotheses about
-how well different sets of alternatives predict implicature performance
-across a range of different scales. Our findings suggest that
-comprehenders likely consider a much broader set of alternatives beyond
-those entailed by the initial description.
+alternatives are. To address this question, we collect empirical
+measurements of speaker and listener judgments about varying sets of
+alternatives across a range of scales and use these as inputs to a
+computational model of pragmatic inference. This approach allows us to
+test hypotheses about how well different sets of alternatives predict
+implicature performance. Our findings suggest that comprehenders likely
+consider a broader set of alternatives beyond those logically entailed
+by the initial message.
 
@@
 generally. A Gricean account of this phenomenon assumes listeners reason
-about a speaker's intended meaning by incorporating knowledge about a)
+about a speaker's intended meaning by incorporating knowledge about A)
 alternative scalar items a speaker could have used (such as \emph{all})
-and b) the relative informativity of using such alternatives (Grice,
+and B) the relative informativity of using such alternatives (Grice,
 1975). According to this account, a listener will infer that the speaker
@@
 \emph{loved} entails \emph{liked} (and hence ``I liked the movie''
-implicates I didn't love it).
+implicates that I didn't love it).
 
@@
 \emph{some} was judged less appropriate when exact numbers were seen as
-viable alternatives. And in a different paradigm, Tiel (2014) found
-converging evidence that \emph{some} was judged to be atypical for small
-quantities. These data provide indirect evidence about a broader set of
-alternatives: since \emph{some} is logically true of sets with one or
-two members, these authors argued that the presence of salient
+viable alternatives. And in a different paradigm, {van Tiel} (2014)
+found converging evidence that \emph{some} was judged to be atypical for
+small quantities. These data provide indirect evidence about a broader
+set of alternatives. Since \emph{some} is logically true of sets with
+one or two members, these authors argued that the presence of salient
 alternatives (the words \emph{one} and \emph{two}, for example) reduced
@@
 understanding inferences about meaning in context (Frank \& Goodman,
-2012; N. D. Goodman \& Stuhlmuller, 2013). RSA models frame language
+2012; Goodman \& Stuhlmuller, 2013). RSA models frame language
 understanding as a special case of social cognition, in which listeners
@@
 typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
-Tiel (2014) for the scale \emph{some}/\emph{all}. In order to do this,
-Franke (2014)'s model assigned weights to a set of alternative numerical
-expressions. Surprisingly, along with weighting \emph{one} highly (a
-conclusion that was supported by the empirical work), the best-fitting
-model assigned substantial weight to \emph{none} as an alternative to
-\emph{some}. This finding was especially surprising considering the
-emphasis of standard theories on scalar items that stand in entailment
-relationships with one another (e.g. \emph{one} entails \emph{some} even
-if it is not classically considered to be part of the scale).
+{van Tiel} (2014) for the scale \emph{some}/\emph{all}. In order to do
+this, Franke (2014)'s model assigned weights to a set of alternative
+numerical expressions. Surprisingly, along with weighting \emph{one}
+highly (a conclusion that was supported by the empirical work), the
+best-fitting model assigned substantial weight to \emph{none} as an
+alternative to \emph{some}. This finding was especially surprising
+considering the emphasis of standard theories on scalar items that stand
+in entailment relationships with one another (e.g. \emph{one} entails
+\emph{some} even if it is not classically considered to be part of the
+scale).
 
@@
 To gain empirical traction on this issue, however, we broaden the set of
-scales we consider. Our inspiration for this move comes from work by Van
-Tiel, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
+scales we consider. Our inspiration for this move comes from work by
+{van Tiel}, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
 phenomenon that they dubbed ``scalar diversity,'' namely the substantial
 difference in the strength of scalar implicature across a variety of
-scalar pairs (e.g. \emph{liked}/\emph{loved,} or
-\emph{palatable}/\emph{delicious.}). Making use of some of this
-diversity allows us to investigate the ways that different alternative
-sets give rise to implicatures of different strengths across scales.
+scalar pairs (e.g., \emph{liked} / \emph{loved,} \emph{palatable} /
+\emph{delicious}). Making use of this diversity allows us to investigate
+the ways that different alternative sets give rise to implicatures of
+different strengths across scales.
 
@@
 empirically (by asking participants to generate alternative messages)
-allows us to model listener judgments with high accuracy.
+allows us to predict listeners' pragmatic judgments with high accuracy.
 
@@
 simplicity, we present a version of this model in which there is only
-full recursion: that is, the pragmatic listener reasons about a
-pragmatic speaker, who in turn reasons about a ``literal listener.'' We
-assume throughout that this computation takes place in a signaling game
-(Lewis, 1969) with a fixed set of possible meanings \(m \in M\) and a
-fixed possible set of utterances \(u \in U\), with both known to both
-participants. Our goal in this study is to determine what utterances
+one full recursion: The pragmatic listener reasons about a pragmatic
+speaker, who in turn reasons about a ``literal listener.'' We assume
+throughout that this computation takes place in a signaling game (Lewis,
+1969) with a fixed set of possible meanings \(m \in M\) and a fixed
+possible set of utterances \(u \in U\), with both known to both
+participants. Our goal in this study is to determine which utterances
 fall in \(U\).
@@
 should have very little expectation about which meanings speakers want
-to convey, for simplicity we assume a uniform prior \(p(m) \propto 1\).
+to convey, for simplicity we assume a uniform prior where
+\(p(m) \propto 1\).
 
@@
 \(\alpha\) is a parameter in a standard choice rule. If \(\alpha=0\),
-speakers choose randomly and as \(\alpha \rightarrow \infty\), they
+speakers choose randomly; as \(\alpha \rightarrow \infty\), they
 greedily choose the highest probability alternative. In our simulations
@@
 communicate the number of stars in an online restaurant review (where
-\(m \in \{1, 2, 3, 4, 5\}\)). We then use experiments to measure three
+\(m \in \{1...5\}\)). We then use experiments to measure three
 components of the model. First, to measure literal semantics
@@
 \begin{figure}[t]
-\includegraphics{figs/allScalesTable-1} \caption[Stimuli for Experiments 1, 2, and 3]{Stimuli for Experiments 1, 2, and 3}\label{fig:allScalesTable}
+\includegraphics{figs/allScalesTable-1} \caption[Alternative sets for Experiments 1, 2, and 3]{Alternative sets for Experiments 1, 2, and 3.}\label{fig:allScalesTable}
 \end{figure}
@@
 
-\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar `liked.' (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar `liked.'}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar "liked."}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 
-Experiment 1 was conducted to approximate literal listener semantics -
-\(p_{L_0}(m \mid u)\) in Equation (2), for five pairs of scalar items
-taken from Tiel (2014). We include three conditions in Experiment 1,
-corresponding to the sets of alternatives within a scale that
-participants were presented with: two-alternatives (``entailment''),
-four-alternatives, and five-alternatives. The two-alternatives condition
-makes a test of the hypothesis that the two members of the classic Horn
-(entailment) scale (Horn, 1972) are the only alternatives necessary to
-predict the strength of listeners' pragmatic inference. The four and
-five-alternatives conditions then add successively more alternatives to
-test whether including a larger number of alternatives will increase
-model
+Experiment 1 was conducted to approximate literal listener
+semantics---\(p_{L_0}(m \mid u)\) in Equation (2)---for five pairs of
+scalar items taken from {van Tiel} (2014). We include three conditions
+in Experiment 1, corresponding to the sets of alternatives within a
+scale that participants were presented with: two-alternatives
+(``entailment''), four-alternatives, and five-alternatives. The
+two-alternatives condition makes a test of the hypothesis that the two
+members of the classic Horn (entailment) scale (Horn, 1972) are the only
+alternatives necessary to predict the strength of listeners' pragmatic
+inference. The four and five-alternatives conditions then add
+successively more alternatives to test whether including a larger number
+of alternatives will increase model
 fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
@@
 condition (Experiment 1a), 16 participants were excluded for either
-failing to pass two training trails or were not native English speakers,
-leaving a total sample of 14
+failing to pass two training trails or because they were not native
+English speakers, leaving a total sample of 14
 participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
@@
 In the four alternative condition (Experiment 1b), 7 participants were
-excluded for either failing to pass two training trials or were not
+excluded for either failing to pass two training trials or not being
 native English speakers, leaving a total sample of 23 participants. In
 the five alternative condition (Experiment 1c), 3 participants were
-excluded for either failing to pass two training trials or were not
+excluded for either failing to pass two training trials or not being
 native English speakers, leaving a total sample of 27.
@@
 
-The two-alternatives condition included only the scalar pairs from Tiel
-(2014). The four-alternatives condition included the two scalar items
-plus the top two alternatives generated for each scalar family by
-participants in Experiment 2. The five-alternatives condition included
-the four previous items plus one more neutral item chosen from
+The two-alternatives condition included only the two terms in the pairs
+from van Tiel (2014). The four-alternatives condition included the two
+scalar items plus the top two alternatives generated for each scalar
+family by participants in Experiment 2. The five-alternatives condition
+included the four previous items plus one more neutral item chosen from
 alternatives generated in Experiment 2. See Figure
@@
 
-Figure \ref{fig:exp1Plots} plots literal listener \(p_{L0}(m|u)\) scalar
-item distributions for the three conditions. Each row shows a unique
-scalar family with items ordered horizontally by valence. Several trends
-are visible. First, in each scale, the alternatives spanned the star
-scale, such that there were scalar items that were highly compatible
-with both the lowest and highest numbers of stars. Second, participant
+Figure \ref{fig:exp1Plots} plots the estimated literal listener
+semantics for the three conditions. Each row shows a unique scalar
+family with items ordered horizontally by valence. Several trends are
+visible. First, in each scale, the alternatives spanned the star scale,
+such that there were scalar items that were highly compatible with both
+the lowest and highest numbers of stars. Second, participant
 compatibility judgments match intuitive literal semantics. That is, both
@@
 alternatives empirically. This design was inspired by Experiment 3 of
-Tiel (2014).
+{van Tiel} (2014).
 
@@
 \begin{CodeChunk}
-\begin{figure}[t]
+\captionsetup{width=0.8\textwidth}\begin{figure}[t]
 
@@
 and weak scalar items varied considerably across scales, consistent with
-previous work (Tiel, 2014).
+previous work ({van Tiel}, 2014).
 
@@
 
+\captionsetup{width=0.8\textwidth}
+
 \begin{table}[ht]
@@
 different lexical scales produce strikingly different patterns of
-inference (Tiel, 2014).
+inference ({van Tiel}, 2014).
 
@@
 
-Frank, M., \& Goodman, N. (2012). Predicting pragmatic reasoning in
+Frank, M., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in
 language games. \emph{Science}, \emph{336}(6084), 998.
@@
 
-Tiel, B. van. (2014). Quantity matters: Implicatures, typicality, and
-truth.
+{van Tiel}, B. J. M. (2014). Quantity matters: Implicatures, typicality,
+and truth.
 
-Van Tiel, B., Van Miltenburg, E., Zevakhina, N., \& Geurts, B. (2014).
-Scalar diversity. \emph{Journal of Semantics}, ffu017.
+{van Tiel}, B. J. M., Van Miltenburg, E., Zevakhina, N., \& Geurts, B.
+(2014). Scalar diversity. \emph{Journal of Semantics}, ffu017.
 

### 2016-02-01 Paper/Paper.Rmd
experiment renumbering'

@@
 ```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiment 1.
-Proportion of participants indicating compatibility (answering `yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Proportion of participants indicating compatibility (answering \"yes\") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
@@
 To examine this last issue of consistency across conditions (our secondary hypothesis) we fit a mixed effects model, regressing compatibility judgment on scale, number of stars and experimental condition, with subject- and word-level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between two- and five-alternative conditions, $b =$`r round(sumGlm2$coefficients[3], 2)`, $Z =$ `r round(sumGlm2$coefficients[19], 2)`, $p =$ `r round(sumGlm2$coefficients[27], 2)` or between four- and five-alternative conditions, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $Z =$ `r round(sumGlm2$coefficients[18], 2)` $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of condition as a predictor did not significantly improve model fit when compared to a model without the condition variable using ANOVA $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+Results indicate no significant differences between two- and five-alternative conditions ($\beta=`r round(sumGlm2$coefficients[3], 2)`$, $z = `r round(sumGlm2$coefficients[19], 2)`$, $p = `r round(sumGlm2$coefficients[27], 2)`$) or between four- and five-alternative conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $z = `r round(sumGlm2$coefficients[18], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
+The addition of condition as a predictor did not significantly improve model fit when compared to a model without the condition variable using ANOVA ($\chi^2(`r anovaResults$"Chi Df"[2]`) = `r round(anovaResults$Chisq[2], 2)`$, $p = `r round(anovaResults$"Pr(>Chisq)"[2], 2)`$).
 These findings suggest that literal semantic intuitions are not effected by the set of alternatives queried in our paradigm.
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', set.cap.width=T, fig.height=2, num.cols.cap=2, fig.cap = "Combined counts for participant-generated alternatives for the `liked \ loved' scale in Experiment 2."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 2."}
 
@@
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
-We expanded our alternative set from only entailment items (items used in Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by including the top two alternatives elicited for each scale in Experiment 2.
-For example, the top two alternatives for the *liked*/*loved* scale were *hated* and *disliked* and were included in four-alternatives model.
-Similarly, neutral items (e.g.
-*okay* in the *good*/*excellent* scale) were chosen from among the set of alternatives elicited in Experiment 2 and added to the five-alternatives model.
-See Figure \ref{fig:allScalesTable} for the complete list of alternatives we used from Experiment 2.
+Figure \ref{fig:allScalesTable} shows the complete list of alternative sets derived from Experiment 2.
 
@@
 ## Results and Discussion
+
 ```{r pragmaticListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
@@
 
-```{r xtable, results = "asis", fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "The left panel shows improved model fit as scale representations are enriched with more scalar items.
-Correlations are coputed using pragmatic judgment data from Experiments 1b and 3b.
-The right panel plots model predictions using full symmetric scales versus human judgments from Experiment 3b."}
+```{r xtable, results = "asis"}
+
 # Tuned model run data
@@
 
-```{r fiveAltsScatter, fig.env = "figure*", fig.pos = "t", fig.width=4.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "Judgments from Experiment 3b are plotted against five-alternatives model predictions.
+```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
 Colors show the star rating for individual judgments."}
@@
   geom_point() +
-  xlab("model predictions") +
-  ylab("human judgments (Exp. 3b)") +
+  xlab("Model predictions") +
+  ylab("Human judgments") +
   stat_smooth(method = "lm") +
@@
   theme(strip.text.x = element_text(size = 8),
-#         legend.position = "bottom",
-#         legend.margin = unit(.02,"in"),
-#         legend.key = element_blank(), 
-#         legend.key.size = unit(.1, "in"),
+        legend.position = "right",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
         axis.title.x = element_text(size = 8.5),

### 2016-02-01 Paper/Paper.tex
experiment renumbering'

@@
 participants from Amazon Mechanical Turk (AMT). In the two-alternatives
-condition (Experiment 1a), 16 participants were excluded for either
-failing to pass two training trails or because they were not native
-English speakers, leaving a total sample of 14
+condition, 16 participants were excluded for either failing to pass two
+training trails or because they were not native English speakers,
+leaving a total sample of 14
 participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
-In the four alternative condition (Experiment 1b), 7 participants were
-excluded for either failing to pass two training trials or not being
-native English speakers, leaving a total sample of 23 participants. In
-the five alternative condition (Experiment 1c), 3 participants were
-excluded for either failing to pass two training trials or not being
-native English speakers, leaving a total sample of 27.
+In the four alternative condition, 7 participants were excluded for
+either failing to pass two training trials or not being native English
+speakers, leaving a total sample of 23 participants. In the five
+alternative condition, 3 participants were excluded for either failing
+to pass two training trials or not being native English speakers,
+leaving a total sample of 27.
 
@@
 \caption[Literal listener judgments from Experiment 1]{Literal listener judgments from Experiment 1.
-Proportion of participants indicating compatibility (answering `yes') is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Proportion of participants indicating compatibility (answering "yes") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
@@
 \emph{palatable}), but also substantial consistency across conditions
-(compatibility judgments for individual scalar items are consistent in
-Experiments 1a,b,c).
+(compatibility judgments for individual scalar items are consistent
+across conditions).
 
-To examine this last issue of consistency across experiments (our
+To examine this last issue of consistency across conditions (our
 secondary hypothesis) we fit a mixed effects model, regressing
@@
 maximal structure that converged. Results indicate no significant
-differences between Experiment 1a and 1c, \(b =\)-0.05, \(Z =\) -0.53,
-\(p =\) 0.59 or between 1b and 1c, \(b =\) -0.04, \(Z =\) -0.52 \(p =\)
-0.6 and the addition of condition as a predictor did not significantly
-improve model fit when compared to a model without the experiment
-condition variable using ANOVA \(\chi^2(\) 2 \() =\) 0.43, \(p =\) 0.81.
+differences between two- and five-alternative conditions
+(\(\beta=-0.05\), \(z = -0.53\), \(p = 0.59\)) or between four- and
+five-alternative conditions (\(\beta = -0.04\), \(z = -0.52\),
+\(p = 0.6\)). The addition of condition as a predictor did not
+significantly improve model fit when compared to a model without the
+condition variable using ANOVA (\(\chi^2(2) = 0.43\), \(p = 0.81\)).
 These findings suggest that literal semantic intuitions are not effected
@@
 
-\caption[Combined counts for participant-generated alternatives for the `liked  loved' scale in Experiment 2]{Combined counts for participant-generated alternatives for the `liked  loved' scale in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
+\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
+loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 
-Experiment 3 was conducted to measure pragmatic
-judgments---\(p_{L_1}(m \mid u)\) in Equation \((1)\). As in Experiment
-1, we include several conditions to test inferences in the presence of
-different alternative sets. In the two-alternatives condition
-(Experiment 3a), participants made judgments for items included in the
-entailment scales. In the four-alternatives condition (Experiment 3b),
-participants made judgments for the entailment items and also the top
-two-alternatives elicited for each scale in Experiment 2. Including two
-conditions with differing alternatives allowed us to rule out the
-potential effects of having a larger set of alternatives during the
-pragmatic judgment elicitation and also provided two sets of human
-judgments to compare with model
+Experiment 3 was conducted to measure pragmatic judgments. As in
+Experiment 1, we include several conditions to test inferences in the
+presence of different alternative sets. In the two-alternatives
+condition, participants made judgments for items included in the
+entailment scales. In the four-alternatives condition, participants made
+judgments for the entailment items and also the top two-alternatives
+elicited for each scale in Experiment 2. Including two conditions with
+differing alternatives allowed us to rule out the potential effects of
+having a larger set of alternatives during the pragmatic judgment
+elicitation and also provided two sets of human judgments to compare
+with model
 predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
@@
 
-\captionsetup{width=0.8\textwidth}
-
 \begin{table}[ht]
@@
 \begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
-
-{\centering \includegraphics{figs/fiveAltsScatter-1}
-
-}
-
-\caption[Judgments from Experiment 3b are plotted against five-alternatives model predictions]{Judgments from Experiment 3b are plotted against five-alternatives model predictions.
+\begin{figure}[t]
+\includegraphics{figs/fiveAltsScatter-1} \caption[Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1]{Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
 Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
-\end{figure*}
+\end{figure}
 \end{CodeChunk}

### 2016-02-01 Paper/Paper.Rmd
reorg finished

@@
 As listeners, our ability to make precise inferences about a speaker's intended meaning in context is  indispensable to successful communication.
-For example, listeners commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@horn1984;@levinson2000].
+For example, listeners commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@levinson2000].
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
@@
 We then use experiments to measure three components of the model.
-First, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 1).
-Second, to generate a set of plausible alternative messages in $U$, we elicit alternatives directly (Experiment 2).
+First, to generate a set of plausible alternative messages in $U$, we ask paticipants to generate alternatives for particular scalar items (Experiment 1).
+Next, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 2).
 Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances (Experiment 3).
-
-# Experiment 1: Literal listener task
 
@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 1 (literal listener) with the target scalar \"liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \"liked.\""}
+# Experiment 1: Alternative Elicitation
+
+To examine the effect different alternative sets have on implicature, we needed a way of expanding alternative sets beyond entailment pairs.
+We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
+This design was inspired by Experiment 3 of @vantiel2014.
+
+## Methods
+
+### Participants
+
+We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
+
+### Design and procedure
+
+Participants were presented with a target scalar item from five scales, selected from @vantiel2014b (see Figure \ref{fig:allScalesTable}).
+These were embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
+Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
+
+## Results and Discussion
+
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 2."}
+
+# Subset alternatives for demo
+plotData <- alternativesData %>%
+  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
+  mutate(prop = n / sum(n))
+
+# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
+ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
+  geom_bar(stat="identity") + 
+  ylim(0, 52) +
+  labs(x = "alternatives", y = "counts") +
+  theme_bw() +
+  theme(strip.text.x = element_text(size = 8),
+        legend.position = "bottom",
+        # legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        # legend.key.size = unit(.1, "in"),
+        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, size = 6),
+        axis.text.y = element_text(size = 10),
+        axis.title.x = element_text(size = 10),
+        axis.title.y = element_text(size = 10))
+```
+
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \"liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \"liked.\""}
 
@@
 
-Experiment 1 was conducted to approximate literal listener semantics---$p_{L_0}(m \mid u)$ in Equation (2)---for five pairs of scalar items taken from @vantiel2014.
-We include three conditions in Experiment 1, corresponding to the sets of alternatives within a scale that participants were presented with: two-alternatives ("entailment"), four-alternatives, and five-alternatives.
-The two-alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four and five-alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 1 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
+Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
+Figure \ref{fig:allScalesTable} shows the complete list of alternative sets derived from Experiment 1.
+
+# Experiment 2: Literal listener task
+
+Experiment 2 was conducted to approximate literal listener semantics---$p_{L_0}(m \mid u)$ in Equation (2)---for the same five pairs of scalar items used in Experiment 1.
+We included three conditions: two alternatives ("entailment"), four alternatives, and five alternatives.
+The two alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
+The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
 If it does we should see differences in these judgments for shared items between experiments.
@@
 The two-alternatives condition included only the two terms in the pairs from van Tiel (2014).
-The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 2.
-The five-alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 2.
-See Figure \ref{fig:allScalesTable} for the complete list of alternatives used in each condition.
+The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 1.
+The five-alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1.
 
@@
 
-```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiment 1.
+```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiment 2.
 Proportion of participants indicating compatibility (answering \"yes\") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
 
-# Experiment 2: Alternative Elicitation
+# Experiment 3: Pragmatic Listener
 
-To examine the effect different alternative sets have on implicature, we needed a way of expanding alternative sets beyond entailment pairs.
-We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
-This design was inspired by Experiment 3 of @vantiel2014.
+Experiment 3 was conducted to measure pragmatic judgments.
+As in Experiment 2, we include several conditions to test inferences in the presence of different alternative sets.
+In the two alternatives condition, participants made judgments for items included in the entailment scales.
+In the four alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
+Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
 
-## Methods
+## Participants
 
-### Participants
+```{r, allPragStudySubsets, echo = FALSE, messgae = FALSE, warning = FALSE}
+exp3a <- subset(allPragmaticListener, exp == "e6")
+exp3b <- subset(allPragmaticListener, exp == "e11")
+```
 
-We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
+We recruited 100 participants from AMT, 50 for each condition.
+Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
+In the four alternatives condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
 
-### Design and procedure
+## Procedure
 
-Participants were presented a target scalar item from our original entailment set (see Figure \ref{fig:allScalesTable}) embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
-Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
+Participants were presented with a one-sentence prompt such as "Someone said they thought the food was \_____." with a target scalar item in the blank.
+Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
+Each participant was presented with all scalar items in a random order.
+The experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
 
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 2."}
-
-# Subset alternatives for demo
-plotData <- alternativesData %>%
-  filter(scale == "liked_loved", alt != "liked", alt != "loved") %>%
-  mutate(prop = n / sum(n))
-
-# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
-ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
-  geom_bar(stat="identity") + 
-  ylim(0, 52) +
-  labs(x = "alternatives", y = "counts") +
-  theme_bw() +
-  theme(strip.text.x = element_text(size = 8),
-        legend.position = "bottom",
-        # legend.margin = unit(.02,"in"),
-        legend.key = element_blank(), 
-        # legend.key.size = unit(.1, "in"),
-        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, size = 6),
-        axis.text.y = element_text(size = 10),
-        axis.title.x = element_text(size = 10),
-        axis.title.y = element_text(size = 10))
-```
-
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for scalar items.
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements in Experiment 3.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity in reporting."}
+Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity in reporting."}
 # Get zero's in data frame
@@
 
-Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
-Figure \ref{fig:allScalesTable} shows the complete list of alternative sets derived from Experiment 2.
-
-# Experiment 3: Pragmatic Listener
-
-Experiment 3 was conducted to measure pragmatic judgments.
-As in Experiment 1, we include several conditions to test inferences in the presence of different alternative sets.
-In the two-alternatives condition, participants made judgments for items included in the entailment scales.
-In the four-alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
-Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
-
-## Participants
-
-```{r, allPragStudySubsets, echo = FALSE, messgae = FALSE, warning = FALSE}
-exp3a <- subset(allPragmaticListener, exp == "e6")
-exp3b <- subset(allPragmaticListener, exp == "e11")
-```
-
-We recruited 100 participants from AMT, 50 for each condition.
-Data for `r 50 - length(unique(exp3a$workerid))` participants was excluded from the two alternatives condition after participants either failed to pass two training trials or were non-native English speakers, leaving a total sample of `r length(unique(exp3a$workerid))` participants.
-In the four alternatives condition, data from `r 50 - length(unique(exp3b$workerid))` participants was excluded after participants either failed to pass two training trials or were not native English speakers, leaving `r length(unique(exp3b$workerid))` participants.
-
-## Procedure
-
-Participants were presented with a one-sentence prompt such as "Someone said they thought the food was \_____." with a target scalar item in the blank.
-Participants were then asked to generate a star rating representing the rating they thought the reviewer likely gave.
-Each participant was presented with all scalar items in a random order.
-The experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
-
-## Results and Discussion
-
 ```{r pragmaticListener_ME_models, echo = FALSE, warning = FALSE, message = FALSE}
@@
 First, in each scale participants generated implicatures.
-They were substantially  less likely to assign high star ratings to weaker scalar terms, despite the literal semantic compatibility of those terms with those states shown in Experiment 1.
-Second, the size of the difference between strong and weak scalar items varied considerably across scales, consistent with previous work [@vantiel2014].
+They were substantially  less likely to assign high star ratings to weaker scalar terms, despite the literal semantic compatibility of those terms with those states shown in Experiment 2.
+Second, the size of the difference between strong and weak scalar items varied considerably across scales, consistent with previous work [@vantiel2014b].
 
@@
 We regressed pragmatic judgments on scale and experimental condition with subject- and word-level random effects, which was the maximal structure that converged.
-There were no significant differences between conditions 3a and 3b, $b =$ `r round(sumGlm2$coefficients[2], 2)`, $t($ `r round(sumGlm2$coefficients[14], 0)` $) =$ `r round(sumGlm2$coefficients[20], 2)`, $p =$ `r round(sumGlm2$coefficients[26], 2)` and the addition of the condition predictor did not significantly improve model fit when compared to a model without that variable $\chi^2($ `r anovaResults$"Chi Df"[2]` $) =$ `r round(anovaResults$Chisq[2], 2)`, $p =$ `r round(anovaResults$"Pr(>Chisq)"[2], 2)`.
+There were no significant differences between the two alternatives and four alternatives conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $t(`r round(sumGlm2$coefficients[14], 0)`) = `r round(sumGlm2$coefficients[20], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
+The addition of the condition predictor did not significantly improve model fit when compared to a model without that variable ($\chi^2(`r anovaResults$"Chi Df"[2]`) = `r round(anovaResults$Chisq[2], 2)`$, $p = `r round(anovaResults$"Pr(>Chisq)"[2], 2)`$).
 
@@
 
-Using literal listener data from Experiment 1, we conducted a set of simulations with the RSA model.
+Using literal listener data from Experiment 2, we conducted a set of simulations with the RSA model.
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative\footnote{Literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline ``none" style semantics in which the scalar item is only compatible with 1 star.}, 3) the expanded set of four alternatives tested in Experiment 1b, and 4) the expanded set of five alternatives tested in Experiment 1c.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives, and 4) the expanded set of five alternatives.
+Literal semantics for the generic negative alternative serve as a baseline ``none"-style semantics in which the scalar item is only compatible with 1 star.
 
@@
 # Plot model performance table
-names(tableCors) <- c("Model", "$\\alpha$", "Exp. 3a", "Exp. 3b")
+names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
 tableCors <- tableCors[c(3, 4, 2, 1),]
-tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in our two Pragmatic listener experiments (3a,b)")
+tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
 print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
@@
 We found that the best predictions came when a range of scale-dependent negative and neutral alternatives were added to the implicature computation, suggesting the importance of considering non-entailment alternatives.
-This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2014].
+This work builds on previous investigations, reinforcing the claim that negative alternatives are critical for understanding implicature [@franke2014], and replicates and extends findings that different lexical scales produce strikingly different patterns of inference [@vantiel2014b].
 
@@
 One possible explanation is that alternatives are differentially salient in context, and in moving to larger sets we should consider weighting the alternatives differentially [as @franke2014 did].
-Preliminary simulations using weightings derived from Experiment 2 provide some support for this idea but would require further empirical work for confirmation.
+Preliminary simulations using weightings derived from Experiment 1 provide some support for this idea but would require further empirical work for confirmation.
 

### 2016-02-01 Paper/Paper.tex
reorg finished

@@
 scalar item \emph{some} to \emph{some but not all} in sentences like
-``Alice ate some of the cookies'' (Grice, 1975; Horn, 1984; Levinson,
-2000). These inferences, called \emph{scalar implicatures}, have been an
-important test case for understanding pragmatic inferences more
-generally. A Gricean account of this phenomenon assumes listeners reason
-about a speaker's intended meaning by incorporating knowledge about A)
+``Alice ate some of the cookies'' (Grice, 1975; Levinson, 2000). These
+inferences, called \emph{scalar implicatures}, have been an important
+test case for understanding pragmatic inferences more generally. A
+Gricean account of this phenomenon assumes listeners reason about a
+speaker's intended meaning by incorporating knowledge about A)
 alternative scalar items a speaker could have used (such as \emph{all})
@@
 \(m \in \{1...5\}\)). We then use experiments to measure three
-components of the model. First, to measure literal semantics
-\({p_{L_0} (m \mid u)}\) we ask experiment participants to judge whether
-a message is compatible with a particular meaning (Experiment 1).
-Second, to generate a set of plausible alternative messages in \(U\), we
-elicit alternatives directly (Experiment 2). Lastly, to obtain human
-\(L_1\) pragmatic judgments, we ask participants to interpret a
-speaker's utterances (Experiment 3).
-
-\section{Experiment 1: Literal listener
-task}\label{experiment-1-literal-listener-task}
+components of the model. First, to generate a set of plausible
+alternative messages in \(U\), we ask paticipants to generate
+alternatives for particular scalar items (Experiment 1). Next, to
+measure literal semantics \({p_{L_0} (m \mid u)}\) we ask experiment
+participants to judge whether a message is compatible with a particular
+meaning (Experiment 2). Lastly, to obtain human \(L_1\) pragmatic
+judgments, we ask participants to interpret a speaker's utterances
+(Experiment 3).
 
@@
 \includegraphics{figs/allScalesTable-1} \caption[Alternative sets for Experiments 1, 2, and 3]{Alternative sets for Experiments 1, 2, and 3.}\label{fig:allScalesTable}
+\end{figure}
+\end{CodeChunk}
+
+\section{Experiment 1: Alternative
+Elicitation}\label{experiment-1-alternative-elicitation}
+
+To examine the effect different alternative sets have on implicature, we
+needed a way of expanding alternative sets beyond entailment pairs. We
+addressed this issue by adopting a modified cloze task to elicit
+alternatives empirically. This design was inspired by Experiment 3 of
+{van Tiel} (2014).
+
+\subsection{Methods}\label{methods}
+
+\subsubsection{Participants}\label{participants}
+
+We recruited 30 workers on AMT. All participants were native English
+speakers and naive to the purpose of the experiment.
+
+\subsubsection{Design and procedure}\label{design-and-procedure}
+
+Participants were presented with a target scalar item from five scales,
+selected from {van Tiel} et al. (2014) (see Figure
+\ref{fig:allScalesTable}). These were embedded in a sentence such as,
+``In a recent restaurant review someone said they thought they the food
+was \_\_\_\_," with a target scalar presented in the blank. Participants
+were then asked to generate plausible alternatives by responding to the
+question, ``If they'd felt differently about the food, what other words
+could they have used instead of \_\_\_\_?" They were prompted to
+generate three unique alternatives.
+
+\subsection{Results and Discussion}\label{results-and-discussion}
+
+\begin{CodeChunk}
+\begin{figure}[t]
+
+{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
+
+}
+
+\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
+loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 
-\caption[(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked]{(Left) A trial from Experiment 1 (literal listener) with the target scalar "liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar "liked."}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar "liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar "liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar "liked."}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 
-Experiment 1 was conducted to approximate literal listener
-semantics---\(p_{L_0}(m \mid u)\) in Equation (2)---for five pairs of
-scalar items taken from {van Tiel} (2014). We include three conditions
-in Experiment 1, corresponding to the sets of alternatives within a
-scale that participants were presented with: two-alternatives
-(``entailment''), four-alternatives, and five-alternatives. The
-two-alternatives condition makes a test of the hypothesis that the two
-members of the classic Horn (entailment) scale (Horn, 1972) are the only
-alternatives necessary to predict the strength of listeners' pragmatic
-inference. The four and five-alternatives conditions then add
-successively more alternatives to test whether including a larger number
-of alternatives will increase model
-fit.\footnote{Note that alternatives in the four and five-alternatives conditions were chosen on the basis of Experiment 2, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
-A secondary goal of Experiment 1 is to test whether the set of
+Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative
+set for the scalar items \emph{liked} and \emph{loved} (combined).
+Figure \ref{fig:allScalesTable} shows the complete list of alternative
+sets derived from Experiment 1.
+
+\section{Experiment 2: Literal listener
+task}\label{experiment-2-literal-listener-task}
+
+Experiment 2 was conducted to approximate literal listener
+semantics---\(p_{L_0}(m \mid u)\) in Equation (2)---for the same five
+pairs of scalar items used in Experiment 1. We included three
+conditions: two alternatives (``entailment''), four alternatives, and
+five alternatives. The two alternatives condition makes a test of the
+hypothesis that the two members of the classic Horn (entailment) scale
+(Horn, 1972) are the only alternatives necessary to predict the strength
+of listeners' pragmatic inference. The four and five alternatives
+conditions then add successively more alternatives to test whether
+including a larger number of alternatives will increase model
+fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+A secondary goal of Experiment 2 is to test whether the set of
 alternatives queried during literal semantic elicitation impacts literal
@@
 
-\subsection{Methods}\label{methods}
+\subsection{Methods}\label{methods-1}
 
-\subsubsection{Participants}\label{participants}
+\subsubsection{Participants}\label{participants-1}
 
@@
 
-\subsubsection{Design and procedure}\label{design-and-procedure}
+\subsubsection{Design and procedure}\label{design-and-procedure-1}
 
@@
 scalar items plus the top two alternatives generated for each scalar
-family by participants in Experiment 2. The five-alternatives condition
+family by participants in Experiment 1. The five-alternatives condition
 included the four previous items plus one more neutral item chosen from
-alternatives generated in Experiment 2. See Figure
-\ref{fig:allScalesTable} for the complete list of alternatives used in
-each condition.
+alternatives generated in Experiment 1.
 
-\subsection{Results and Discussion}\label{results-and-discussion}
+\subsection{Results and Discussion}\label{results-and-discussion-1}
 
@@
 
-\caption[Literal listener judgments from Experiment 1]{Literal listener judgments from Experiment 1.
+\caption[Literal listener judgments from Experiment 2]{Literal listener judgments from Experiment 2.
 Proportion of participants indicating compatibility (answering "yes") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
 
-\section{Experiment 2: Alternative
-Elicitation}\label{experiment-2-alternative-elicitation}
-
-To examine the effect different alternative sets have on implicature, we
-needed a way of expanding alternative sets beyond entailment pairs. We
-addressed this issue by adopting a modified cloze task to elicit
-alternatives empirically. This design was inspired by Experiment 3 of
-{van Tiel} (2014).
-
-\subsection{Methods}\label{methods-1}
-
-\subsubsection{Participants}\label{participants-1}
-
-We recruited 30 workers on AMT. All participants were native English
-speakers and naive to the purpose of the experiment.
-
-\subsubsection{Design and procedure}\label{design-and-procedure-1}
-
-Participants were presented a target scalar item from our original
-entailment set (see Figure \ref{fig:allScalesTable}) embedded in a
-sentence such as, ``In a recent restaurant review someone said they
-thought they the food was \_\_\_\_," with a target scalar presented in
-the blank. Participants were then asked to generate plausible
-alternatives by responding to the question, ``If they'd felt differently
-about the food, what other words could they have used instead of
-\_\_\_\_?" They were prompted to generate three unique alternatives.
-
-\subsection{Results and Discussion}\label{results-and-discussion-1}
-
-\begin{CodeChunk}
-\begin{figure}[t]
-
-{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
-
-}
-
-\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
-loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
-\end{figure}
-\end{CodeChunk}
-
-\begin{CodeChunk}
-\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
-
-{\centering \includegraphics{figs/exp2Plots-1}
-
-}
-
-\caption[Pragmatic listener judgements for scalar items]{Pragmatic listener judgements for scalar items.
-Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two-alternatives condition) shown here for simplicity in reporting.}\label{fig:exp2Plots}
-\end{figure*}
-\end{CodeChunk}
-
-Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative
-set for the scalar items \emph{liked} and \emph{loved} (combined). We
-expanded our alternative set from only entailment items (items used in
-Experiments 1a, 3a) to four alternatives (Experiments 1b, 3b) by
-including the top two alternatives elicited for each scale in Experiment
-2. For example, the top two alternatives for the
-\emph{liked}/\emph{loved} scale were \emph{hated} and \emph{disliked}
-and were included in four-alternatives model. Similarly, neutral items
-(e.g. \emph{okay} in the \emph{good}/\emph{excellent} scale) were chosen
-from among the set of alternatives elicited in Experiment 2 and added to
-the five-alternatives model. See Figure \ref{fig:allScalesTable} for the
-complete list of alternatives we used from Experiment 2.
-
 \section{Experiment 3: Pragmatic
@@
 Experiment 3 was conducted to measure pragmatic judgments. As in
-Experiment 1, we include several conditions to test inferences in the
-presence of different alternative sets. In the two-alternatives
+Experiment 2, we include several conditions to test inferences in the
+presence of different alternative sets. In the two alternatives
 condition, participants made judgments for items included in the
-entailment scales. In the four-alternatives condition, participants made
+entailment scales. In the four alternatives condition, participants made
 judgments for the entailment items and also the top two-alternatives
@@
 elicitation and also provided two sets of human judgments to compare
-with model
-predictions.\footnote{Alternatives in the four-alternatives condition were chosen on the basis of Experiment 2, which was run chronologically after the two-alternatives condition; both pragmatic listener experiments are grouped together for simplicity in reporting.}
+with model predictions.
 
@@
 
+\begin{CodeChunk}
+\captionsetup{width=0.8\textwidth}\begin{figure*}[t]
+
+{\centering \includegraphics{figs/exp2Plots-1}
+
+}
+
+\caption[Pragmatic listener judgements in Experiment 3]{Pragmatic listener judgements in Experiment 3.
+Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Line type denotes condition, and colors indicate the particular scalar items.
+Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity in reporting.}\label{fig:exp2Plots}
+\end{figure*}
+\end{CodeChunk}
+
 Figure \ref{fig:exp2Plots} plots pragmatic listener judgment
@@
 the literal semantic compatibility of those terms with those states
-shown in Experiment 1. Second, the size of the difference between strong
+shown in Experiment 2. Second, the size of the difference between strong
 and weak scalar items varied considerably across scales, consistent with
-previous work ({van Tiel}, 2014).
+previous work ({van Tiel} et al., 2014).
 
@@
 structure that converged. There were no significant differences between
-conditions 3a and 3b, \(b =\) 0.05, \(t(\) 150 \() =\) 1.04, \(p =\) 0.3
-and the addition of the condition predictor did not significantly
-improve model fit when compared to a model without that variable
-\(\chi^2(\) 1 \() =\) 1.13, \(p =\) 0.29.
+the two alternatives and four alternatives conditions (\(\beta = 0.05\),
+\(t(150) = 1.04\), \(p = 0.3\)). The addition of the condition predictor
+did not significantly improve model fit when compared to a model without
+that variable (\(\chi^2(1) = 1.13\), \(p = 0.29\)).
 
@@
 
-Using literal listener data from Experiment 1, we conducted a set of
+Using literal listener data from Experiment 2, we conducted a set of
 simulations with the RSA model. Each simulation kept the model constant,
@@
 entailment scales, 2) those two alternatives with the addition of a
-generic negative
-alternative\footnote{Literal semantics for the generic negative alternative were not generated empirically, but serve as a baseline ``none" style semantics in which the scalar item is only compatible with 1 star.},
-3) the expanded set of four alternatives tested in Experiment 1b, and 4)
-the expanded set of five alternatives tested in Experiment 1c.
+generic negative alternative, 3) the expanded set of four alternatives,
+and 4) the expanded set of five alternatives. Literal semantics for the
+generic negative alternative serve as a baseline ``none``-style
+semantics in which the scalar item is only compatible with 1 star.
 
@@
   \hline
-Model & $\alpha$ & Exp. 3a & Exp. 3b \\ 
+Model & $\alpha$ & Two alts & Four alts \\ 
   \hline
@@
 \end{tabular}
-\caption{Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in our two Pragmatic listener experiments (3a,b)} 
+\caption{Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.} 
 \end{table}
@@
 different lexical scales produce strikingly different patterns of
-inference ({van Tiel}, 2014).
+inference ({van Tiel} et al., 2014).
 
@@
 2014 did). Preliminary simulations using weightings derived from
-Experiment 2 provide some support for this idea but would require
+Experiment 1 provide some support for this idea but would require
 further empirical work for confirmation.
@@
 
-Horn, L. R. (1984). Toward a new taxonomy for pragmatic inference:
-Q-based and R-based implicature. \emph{Meaning, Form, and Use in
-Context}, \emph{42}.
-
 Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of

### 2016-02-02 Paper/Paper.Rmd
BP minor pass after switching Exp 1 and exp 2

@@
 We then use experiments to measure three components of the model.
-First, to generate a set of plausible alternative messages in $U$, we ask paticipants to generate alternatives for particular scalar items (Experiment 1).
+First, to generate a set of plausible alternative messages in $U$, we ask participants to generate alternatives for particular scalar items (Experiment 1).
 Next, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 2).
@@
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two-alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trails or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
+In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
@@
 In the two alternatives condition, participants made judgments for items included in the entailment scales.
-In the four alternatives condition, participants made judgments for the entailment items and also the top two-alternatives elicited for each scale in Experiment 2.
+In the four alternatives condition, participants made judgments for the entailment items and also the top two alternatives elicited for each scale in Experiment 1.
 Including two conditions with differing alternatives allowed us to rule out the potential effects of having a larger set of alternatives during the pragmatic judgment elicitation and also provided two sets of human judgments to compare with model predictions.
@@
 Each simulation kept the model constant, fitting the choice parameter $\alpha$ as a free parameter, but used a set of alternatives to specify the scale over which predictions were computed.
-We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two-alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives, and 4) the expanded set of five alternatives.
+We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives, and 4) the expanded set of five alternatives.
 Literal semantics for the generic negative alternative serve as a baseline ``none"-style semantics in which the scalar item is only compatible with 1 star.
@@
 The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
-An example fit for the five-alternative model is shown in Figure \ref{fig:fiveAltsScatter}.
+An example fit for the five-alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
 

### 2016-02-02 Paper/Paper.tex
BP minor pass after switching Exp 1 and exp 2

@@
 components of the model. First, to generate a set of plausible
-alternative messages in \(U\), we ask paticipants to generate
+alternative messages in \(U\), we ask participants to generate
 alternatives for particular scalar items (Experiment 1). Next, to
@@
 Conditions were run sequentially. In each condition we recruited 30
-participants from Amazon Mechanical Turk (AMT). In the two-alternatives
+participants from Amazon Mechanical Turk (AMT). In the two alternatives
 condition, 16 participants were excluded for either failing to pass two
-training trails or because they were not native English speakers,
+training trials or because they were not native English speakers,
 leaving a total sample of 14
@@
 entailment scales. In the four alternatives condition, participants made
-judgments for the entailment items and also the top two-alternatives
-elicited for each scale in Experiment 2. Including two conditions with
+judgments for the entailment items and also the top two alternatives
+elicited for each scale in Experiment 1. Including two conditions with
 differing alternatives allowed us to rule out the potential effects of
@@
 measurements corresponding to those shown in Figure
-\ref{fig:allScalesTable}: 1) the two-alternatives in the classic
+\ref{fig:allScalesTable}: 1) the two alternatives in the classic
 entailment scales, 2) those two alternatives with the addition of a
@@
 the alternatives derived empirically for the specific scale we used. An
-example fit for the five-alternative model is shown in Figure
+example fit for the five-alternatives model is shown in Figure
 \ref{fig:fiveAltsScatter}.

### 2016-02-02 Paper/Paper.Rmd
implemented Kyle's suggestions

@@
 To address this question, we collect empirical measurements of speaker and listener judgments about varying sets of alternatives across a range of scales and use these as inputs to a computational model of pragmatic inference.
-This approach allows us to test hypotheses about how well different sets of alternatives predict implicature performance.
+This approach allows us to test hypotheses about how well different sets of alternatives predict pragmatic judgments by people.
 Our findings suggest that comprehenders likely consider a broader set of alternatives beyond those logically entailed by the initial message.
@@
 And in a different paradigm, @vantiel2014 found converging evidence that *some* was judged to be atypical for small quantities.
-These data provide indirect evidence about a broader set of alternatives.
+These data provide indirect evidence that people may actually consider a broader set of alternatives when computing scalar implicatures.
 Since *some* is logically true of sets with one or two members, these authors argued that the presence of salient alternatives (the words *one* and *two*, for example) reduced the felicity of *some* via a pragmatic inference.
@@
 
-We begin by presenting the computational framework we use throughout the paper.
-We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items and comprehenders' pragmatic judgments for these same items.
+In our current work, we use a computational framework to investigate the set of alternatives that best allow the model to predict human pragmatic judgments.
+We begin by presenting the computational framework (RSA) we use throughout the paper.
+We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items (used to simulate different alternative sets available to listeners) and comprehenders' pragmatic judgments for these same items (used for model comparison).
 These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgments.
@@
 First, to generate a set of plausible alternative messages in $U$, we ask participants to generate alternatives for particular scalar items (Experiment 1).
-Next, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask experiment participants to judge whether a message is compatible with a particular meaning (Experiment 2).
+Next, to measure literal semantics ${p_{L_0} (m \mid u)}$ we ask participants to judge whether a message is compatible with a particular meaning (Experiment 2).
 Lastly, to obtain human $L_1$ pragmatic judgments, we ask participants to interpret a speaker's utterances (Experiment 3).
 
-```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Alternative sets for Experiments 1, 2, and 3."}
+```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Alternative sets used in Experiments 2 and 3.
+Green coloring denotes classic entailment items used in conditions 2a and 3a.
+Blue coloring denotes top-two alternatives added to entailment scales (from Experiment 1) in conditions 2b and 3b.
+Red coloring denotes ``neutral\" items aded in condition 2c."}
 
@@
 ```
-
-# Experiment 1: Alternative Elicitation
-
-To examine the effect different alternative sets have on implicature, we needed a way of expanding alternative sets beyond entailment pairs.
-We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
-This design was inspired by Experiment 3 of @vantiel2014.
-
-## Methods
-
-### Participants
-
-We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
-
-### Design and procedure
-
-Participants were presented with a target scalar item from five scales, selected from @vantiel2014b (see Figure \ref{fig:allScalesTable}).
-These were embedded in a sentence such as, "In a recent restaurant review someone said they thought they the food was \____," with a target scalar presented in the blank.
-Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
-
-## Results and Discussion
 
@@
 
+# Experiment 1: Alternative Elicitation
+
+To examine the effect different alternative sets have on implicature, we needed a way of expanding alternative sets beyond entailment pairs.
+We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
+This design was inspired by Experiment 3 of @vantiel2014.
+
+## Methods
+
+### Participants
+
+We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
+
+### Design and procedure
+
+Participants were presented with a target scalar item from five scales, selected from @vantiel2014b (see Figure \ref{fig:allScalesTable}).
+These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the the food was \____," with a target scalar presented in the blank.
+Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
+
+## Results and Discussion
+
 ```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \"liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \"liked.\""}
@@
 
-Experiment 2 was conducted to approximate literal listener semantics---$p_{L_0}(m \mid u)$ in Equation (2)---for the same five pairs of scalar items used in Experiment 1.
+Experiment 2 was conducted to approximate literal listener semantics---$p_{L_0}(m \mid u)$ in Equation (3)---for the same five pairs of scalar items used in Experiment 1.
 We included three conditions: two alternatives ("entailment"), four alternatives, and five alternatives.
@@
 
-Figure \ref{fig:exp1Plots} plots the estimated literal listener semantics for the three conditions.
+Figure \ref{fig:exp1Plots} plots estimated literal listener semantics for the three conditions.
 Each row shows a unique scalar family with items ordered horizontally by valence.
 Several trends are visible.
-First, in each scale, the alternatives spanned the star scale, such that there were scalar items that were highly compatible with both the lowest and highest numbers of stars.
+First, in each scale, the alternatives spanned the star scale - there were scalar items that were highly compatible with both the lowest and highest numbers of stars.
 Second, participant compatibility judgments match intuitive literal semantics.
@@
 This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
-We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual scalar items are consistent across conditions).
+We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual items are consistent across conditions).
 
@@
 The addition of condition as a predictor did not significantly improve model fit when compared to a model without the condition variable using ANOVA ($\chi^2(`r anovaResults$"Chi Df"[2]`) = `r round(anovaResults$Chisq[2], 2)`$, $p = `r round(anovaResults$"Pr(>Chisq)"[2], 2)`$).
-These findings suggest that literal semantic intuitions are not effected by the set of alternatives queried in our paradigm.
+These findings suggest that literal semantic intuitions are not affected by the set of alternatives queried in our paradigm.
 This finding is important because literal semantic data generated in these three conditions are used to simulate the effects of different alternative sets on implicature generation in our model.
@@
 
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements in Experiment 3.
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.15, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements in Experiment 3.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
 They were substantially  less likely to assign high star ratings to weaker scalar terms, despite the literal semantic compatibility of those terms with those states shown in Experiment 2.
-Second, the size of the difference between strong and weak scalar items varied considerably across scales, consistent with previous work [@vantiel2014b].
+Second, the difference between strong and weak scalar items varied considerably across scales, consistent with previous work [@vantiel2014b].
 
@@
 
-```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
-Colors show the star rating for individual judgments."}
-# Correlation scatter plot
-ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
-  geom_point() +
-  xlab("Model predictions") +
-  ylab("Human judgments") +
-  stat_smooth(method = "lm") +
-  theme_bw() + 
-  theme(strip.text.x = element_text(size = 8),
-        legend.position = "right",
-        legend.margin = unit(.02,"in"),
-        legend.key = element_blank(), 
-        legend.key.size = unit(.1, "in"),
-        axis.title.x = element_text(size = 8.5),
-        axis.title.y = element_text(size = 8.5)) 
-  # ggtitle("Model fit\nFive alternatives")
-
-```
-
 # General Discussion
@@
 The precise set of alternatives present during implicature is likely to be domain dependent.
-Our current empirical paradigm elicited literal semantics, pragmatic judgments, and plausible alternatives all within the restricted domain of restaurant reviews.
+Our empirical paradigm elicited literal semantics, pragmatic judgments, and plausible alternatives all within the restricted domain of restaurant reviews.
 Our measurements might have differed substantially if we had instead grounded our ratings in a different context.
@@
 Rather than being grounded in a firm distinction, we may find that these categories are simply a reflection of the effects of context on a constantly-shifting set of pragmatic alternatives.
+
+```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.25, fig.cap = "Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
+Colors show the star rating for individual judgments."}
+# Correlation scatter plot
+ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
+  geom_point() +
+  xlab("model predictions") +
+  ylab("human judgments") +
+  stat_smooth(method = "lm") +
+  theme_bw() + 
+  theme(strip.text.x = element_text(size = 8),
+        legend.position = "right",
+        legend.margin = unit(.02,"in"),
+        legend.key = element_blank(), 
+        legend.key.size = unit(.1, "in"),
+        axis.title.x = element_text(size = 8.5),
+        axis.title.y = element_text(size = 8.5)) 
+  # ggtitle("Model fit\nFive alternatives")
+```
 

### 2016-02-02 Paper/Paper.tex
implemented Kyle's suggestions

@@
 test hypotheses about how well different sets of alternatives predict
-implicature performance. Our findings suggest that comprehenders likely
-consider a broader set of alternatives beyond those logically entailed
-by the initial message.
+pragmatic judgments by people. Our findings suggest that comprehenders
+likely consider a broader set of alternatives beyond those logically
+entailed by the initial message.
 
@@
 found converging evidence that \emph{some} was judged to be atypical for
-small quantities. These data provide indirect evidence about a broader
-set of alternatives. Since \emph{some} is logically true of sets with
-one or two members, these authors argued that the presence of salient
+small quantities. These data provide indirect evidence that people may
+actually consider a broader set of alternatives when computing scalar
+implicatures. Since \emph{some} is logically true of sets with one or
+two members, these authors argued that the presence of salient
 alternatives (the words \emph{one} and \emph{two}, for example) reduced
@@
 
-We begin by presenting the computational framework we use throughout the
-paper. We next describe a series of experiments designed to measure both
-the literal semantics of a set of scalar items and comprehenders'
-pragmatic judgments for these same items. These experiments allow us to
-compare the effects of different alternative sets on our ability to
-model listeners' pragmatic judgments. To preview our results: we find
-that standard entailment alternatives do not allow us to fit
-participants' judgments, but that expanding the range of alternatives
-empirically (by asking participants to generate alternative messages)
-allows us to predict listeners' pragmatic judgments with high accuracy.
+In our current work, we use a computational framework to investigate the
+set of alternatives that best allow the model to predict human pragmatic
+judgments. We begin by presenting the computational framework (RSA) we
+use throughout the paper. We next describe a series of experiments
+designed to measure both the literal semantics of a set of scalar items
+(used to simulate different alternative sets available to listeners) and
+comprehenders' pragmatic judgments for these same items (used for model
+comparison). These experiments allow us to compare the effects of
+different alternative sets on our ability to model listeners' pragmatic
+judgments. To preview our results: we find that standard entailment
+alternatives do not allow us to fit participants' judgments, but that
+expanding the range of alternatives empirically (by asking participants
+to generate alternative messages) allows us to predict listeners'
+pragmatic judgments with high accuracy.
 
@@
 alternatives for particular scalar items (Experiment 1). Next, to
-measure literal semantics \({p_{L_0} (m \mid u)}\) we ask experiment
-participants to judge whether a message is compatible with a particular
-meaning (Experiment 2). Lastly, to obtain human \(L_1\) pragmatic
-judgments, we ask participants to interpret a speaker's utterances
-(Experiment 3).
+measure literal semantics \({p_{L_0} (m \mid u)}\) we ask participants
+to judge whether a message is compatible with a particular meaning
+(Experiment 2). Lastly, to obtain human \(L_1\) pragmatic judgments, we
+ask participants to interpret a speaker's utterances (Experiment 3).
 
@@
 \begin{figure}[t]
-\includegraphics{figs/allScalesTable-1} \caption[Alternative sets for Experiments 1, 2, and 3]{Alternative sets for Experiments 1, 2, and 3.}\label{fig:allScalesTable}
+\includegraphics{figs/allScalesTable-1} \caption[Alternative sets used in Experiments 2 and 3]{Alternative sets used in Experiments 2 and 3.
+Green coloring denotes classic entailment items used in conditions 2a and 3a.
+Blue coloring denotes top-two alternatives added to entailment scales (from Experiment 1) in conditions 2b and 3b.
+Red coloring denotes ``neutral" items aded in condition 2c.}\label{fig:allScalesTable}
+\end{figure}
+\end{CodeChunk}
+
+\begin{CodeChunk}
+\begin{figure}[t]
+
+{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
+
+}
+
+\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
+loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 \ref{fig:allScalesTable}). These were embedded in a sentence such as,
-``In a recent restaurant review someone said they thought they the food
+``In a recent restaurant review someone said they thought the the food
 was \_\_\_\_," with a target scalar presented in the blank. Participants
@@
 \subsection{Results and Discussion}\label{results-and-discussion}
-
-\begin{CodeChunk}
-\begin{figure}[t]
-
-{\centering \includegraphics{figs/exp2_altsPlot_likedLoved-1}
-
-}
-
-\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
-loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
-\end{figure}
-\end{CodeChunk}
 
@@
 Experiment 2 was conducted to approximate literal listener
-semantics---\(p_{L_0}(m \mid u)\) in Equation (2)---for the same five
+semantics---\(p_{L_0}(m \mid u)\) in Equation (3)---for the same five
 pairs of scalar items used in Experiment 1. We included three
@@
 
-Figure \ref{fig:exp1Plots} plots the estimated literal listener
-semantics for the three conditions. Each row shows a unique scalar
-family with items ordered horizontally by valence. Several trends are
-visible. First, in each scale, the alternatives spanned the star scale,
-such that there were scalar items that were highly compatible with both
-the lowest and highest numbers of stars. Second, participant
-compatibility judgments match intuitive literal semantics. That is, both
-weaker (e.g. \emph{some} or \emph{good}) and stronger (e.g. \emph{all}
-or \emph{excellent}) entailment items were seen as compatible with
+Figure \ref{fig:exp1Plots} plots estimated literal listener semantics
+for the three conditions. Each row shows a unique scalar family with
+items ordered horizontally by valence. Several trends are visible.
+First, in each scale, the alternatives spanned the star scale - there
+were scalar items that were highly compatible with both the lowest and
+highest numbers of stars. Second, participant compatibility judgments
+match intuitive literal semantics. That is, both weaker (e.g.
+\emph{some} or \emph{good}) and stronger (e.g. \emph{all} or
+\emph{excellent}) entailment items were seen as compatible with
 five-star ratings. This means participants' compatibility judgements
@@
 \emph{palatable}), but also substantial consistency across conditions
-(compatibility judgments for individual scalar items are consistent
-across conditions).
+(compatibility judgments for individual items are consistent across
+conditions).
 
@@
 condition variable using ANOVA (\(\chi^2(2) = 0.43\), \(p = 0.81\)).
-These findings suggest that literal semantic intuitions are not effected
+These findings suggest that literal semantic intuitions are not affected
 by the set of alternatives queried in our paradigm. This finding is
@@
 the literal semantic compatibility of those terms with those states
-shown in Experiment 2. Second, the size of the difference between strong
-and weak scalar items varied considerably across scales, consistent with
-previous work ({van Tiel} et al., 2014).
+shown in Experiment 2. Second, the difference between strong and weak
+scalar items varied considerably across scales, consistent with previous
+work ({van Tiel} et al., 2014).
 
@@
 
-\begin{CodeChunk}
-\begin{figure}[t]
-\includegraphics{figs/fiveAltsScatter-1} \caption[Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1]{Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
-Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
-\end{figure}
-\end{CodeChunk}
-
 \section{General Discussion}\label{general-discussion}
@@
 The precise set of alternatives present during implicature is likely to
-be domain dependent. Our current empirical paradigm elicited literal
-semantics, pragmatic judgments, and plausible alternatives all within
-the restricted domain of restaurant reviews. Our measurements might have
+be domain dependent. Our empirical paradigm elicited literal semantics,
+pragmatic judgments, and plausible alternatives all within the
+restricted domain of restaurant reviews. Our measurements might have
 differed substantially if we had instead grounded our ratings in a
@@
 alternatives.
+
+\begin{CodeChunk}
+\begin{figure}[t]
+\includegraphics{figs/fiveAltsScatter-1} \caption[Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1]{Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
+Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}
+\end{figure}
+\end{CodeChunk}
 

### 2016-02-02 Paper/Paper.Rmd
second to last pass fixed x- alts labeling and some wording

@@
 We begin by presenting the computational framework (RSA) we use throughout the paper.
-We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items (used to simulate different alternative sets available to listeners) and comprehenders' pragmatic judgments for these same items (used for model comparison).
+We next describe a series of experiments designed to measure both the literal semantics of a set of scalar items (used as input to the model) and comprehenders' pragmatic judgments for these same items (used for model comparison).
 These experiments allow us to compare the effects of different alternative sets on our ability to model listeners' pragmatic judgments.
@@
 
-```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Alternative sets used in Experiments 2 and 3.
-Green coloring denotes classic entailment items used in conditions 2a and 3a.
-Blue coloring denotes top-two alternatives added to entailment scales (from Experiment 1) in conditions 2b and 3b.
-Red coloring denotes ``neutral\" items aded in condition 2c."}
+```{r allScalesTable, fig.pos = "t", fig.width=3.5, fig.height=2.5, fig.cap = "Alternative sets used in Experiments 2 and 3 (generated in Experiment 1).
+Green coloring denotes classic entailment items pulled from van Tiel et al.
+(2014), used in the two alternative condition.
+Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
+Red coloring denotes ``neutral\" items aded in the five alternatives condition."}
 
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 2."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 1."}
 
@@
 We addressed this issue by adopting a modified cloze task to elicit alternatives empirically.
-This design was inspired by Experiment 3 of @vantiel2014.
+This design was inspired by Experiment 3 of @vantiel2014b.
 
@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \"liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \"liked.\""}
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \``liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \``liked.\""}
 
@@
 The two alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
+The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
 If it does we should see differences in these judgments for shared items between experiments.
@@
 In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
-In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
+In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
-In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))`.
+In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))` participants.
 
@@
 
-The two-alternatives condition included only the two terms in the pairs from van Tiel (2014).
-The four-alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 1.
-The five-alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1.
+The two alternatives condition included only the two terms in the pairs from @vantiel2014b.
+The four alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 1.
+The five alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1.
 
@@
 ```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=4, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgments from Experiment 2.
-Proportion of participants indicating compatibility (answering \"yes\") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Proportion of participants indicating compatibility (answering \``yes\") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
-Colors indicate the specific condition (1a,b,c) with conditions including different numbers of items."}
+Colors indicate the specific condition with conditions including different numbers of items."}
 
@@
 This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
-We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions (compatibility judgments for individual items are consistent across conditions).
+We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions.
 
@@
 To examine this last issue of consistency across conditions (our secondary hypothesis) we fit a mixed effects model, regressing compatibility judgment on scale, number of stars and experimental condition, with subject- and word-level random effects, which was the maximal structure that converged.
-Results indicate no significant differences between two- and five-alternative conditions ($\beta=`r round(sumGlm2$coefficients[3], 2)`$, $z = `r round(sumGlm2$coefficients[19], 2)`$, $p = `r round(sumGlm2$coefficients[27], 2)`$) or between four- and five-alternative conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $z = `r round(sumGlm2$coefficients[18], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
+Results indicate no significant differences between two and five alternative conditions ($\beta=`r round(sumGlm2$coefficients[3], 2)`$, $z = `r round(sumGlm2$coefficients[19], 2)`$, $p = `r round(sumGlm2$coefficients[27], 2)`$) or between four and five alternative conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $z = `r round(sumGlm2$coefficients[18], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
 The addition of condition as a predictor did not significantly improve model fit when compared to a model without the condition variable using ANOVA ($\chi^2(`r anovaResults$"Chi Df"[2]`) = `r round(anovaResults$Chisq[2], 2)`$, $p = `r round(anovaResults$"Pr(>Chisq)"[2], 2)`$).
 These findings suggest that literal semantic intuitions are not affected by the set of alternatives queried in our paradigm.
-This finding is important because literal semantic data generated in these three conditions are used to simulate the effects of different alternative sets on implicature generation in our model.
+This finding is important because literal semantic data generated in these three conditions are used as input to our model to simulate the effects of different alternative sets on implicature generation.
 
@@
 Model fit with human judgments was significantly improved by the inclusion of alternatives beyond the entailment items (Table 1).
-The two-alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
+The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
 The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
-An example fit for the five-alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
+An example fit for the five alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
 
@@
 
-```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.25, fig.cap = "Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
+```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.25, fig.cap = "Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2.
 Colors show the star rating for individual judgments."}

### 2016-02-02 Paper/Paper.tex
second to last pass fixed x- alts labeling and some wording

@@
 designed to measure both the literal semantics of a set of scalar items
-(used to simulate different alternative sets available to listeners) and
-comprehenders' pragmatic judgments for these same items (used for model
-comparison). These experiments allow us to compare the effects of
-different alternative sets on our ability to model listeners' pragmatic
-judgments. To preview our results: we find that standard entailment
-alternatives do not allow us to fit participants' judgments, but that
-expanding the range of alternatives empirically (by asking participants
-to generate alternative messages) allows us to predict listeners'
-pragmatic judgments with high accuracy.
+(used as input to the model) and comprehenders' pragmatic judgments for
+these same items (used for model comparison). These experiments allow us
+to compare the effects of different alternative sets on our ability to
+model listeners' pragmatic judgments. To preview our results: we find
+that standard entailment alternatives do not allow us to fit
+participants' judgments, but that expanding the range of alternatives
+empirically (by asking participants to generate alternative messages)
+allows us to predict listeners' pragmatic judgments with high accuracy.
 
@@
 \begin{figure}[t]
-\includegraphics{figs/allScalesTable-1} \caption[Alternative sets used in Experiments 2 and 3]{Alternative sets used in Experiments 2 and 3.
-Green coloring denotes classic entailment items used in conditions 2a and 3a.
-Blue coloring denotes top-two alternatives added to entailment scales (from Experiment 1) in conditions 2b and 3b.
-Red coloring denotes ``neutral" items aded in condition 2c.}\label{fig:allScalesTable}
+\includegraphics{figs/allScalesTable-1} \caption[Alternative sets used in Experiments 2 and 3 (generated in Experiment 1)]{Alternative sets used in Experiments 2 and 3 (generated in Experiment 1).
+Green coloring denotes classic entailment items pulled from van Tiel et al.
+(2014), used in the two alternative condition.
+Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
+Red coloring denotes ``neutral" items aded in the five alternatives condition.}\label{fig:allScalesTable}
 \end{figure}
@@
 \caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
-loved in Experiment 2.}\label{fig:exp2_altsPlot_likedLoved}
+loved in Experiment 1.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 alternatives empirically. This design was inspired by Experiment 3 of
-{van Tiel} (2014).
+{van Tiel} et al. (2014).
 
@@
 
-\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar "liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar "liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar "liked."}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar ``liked."}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 including a larger number of alternatives will increase model
-fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two-alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
 A secondary goal of Experiment 2 is to test whether the set of
@@
 leaving a total sample of 14
-participants.\footnote{The majority of respondent data excluded from the two-alternatives condition was caused by failure to pass training trials.
+participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
@@
 to pass two training trials or not being native English speakers,
-leaving a total sample of 27.
+leaving a total sample of 27 participants.
 
@@
 
-The two-alternatives condition included only the two terms in the pairs
-from van Tiel (2014). The four-alternatives condition included the two
-scalar items plus the top two alternatives generated for each scalar
-family by participants in Experiment 1. The five-alternatives condition
-included the four previous items plus one more neutral item chosen from
-alternatives generated in Experiment 1.
+The two alternatives condition included only the two terms in the pairs
+from {van Tiel} et al. (2014). The four alternatives condition included
+the two scalar items plus the top two alternatives generated for each
+scalar family by participants in Experiment 1. The five alternatives
+condition included the four previous items plus one more neutral item
+chosen from alternatives generated in Experiment 1.
 
@@
 \caption[Literal listener judgments from Experiment 2]{Literal listener judgments from Experiment 2.
-Proportion of participants indicating compatibility (answering "yes") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
+Proportion of participants indicating compatibility (answering ``yes") is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Rows are grouped by scale and items within rows are ordered by valence.
-Colors indicate the specific condition (1a,b,c) with conditions including different numbers of items.}\label{fig:exp1Plots}
+Colors indicate the specific condition with conditions including different numbers of items.}\label{fig:exp1Plots}
 \end{figure*}
@@
 distributions for \emph{memorable} are considerably different from
-\emph{palatable}), but also substantial consistency across conditions
-(compatibility judgments for individual items are consistent across
-conditions).
+\emph{palatable}), but also substantial consistency across conditions.
 
@@
 maximal structure that converged. Results indicate no significant
-differences between two- and five-alternative conditions
-(\(\beta=-0.05\), \(z = -0.53\), \(p = 0.59\)) or between four- and
-five-alternative conditions (\(\beta = -0.04\), \(z = -0.52\),
-\(p = 0.6\)). The addition of condition as a predictor did not
-significantly improve model fit when compared to a model without the
-condition variable using ANOVA (\(\chi^2(2) = 0.43\), \(p = 0.81\)).
-These findings suggest that literal semantic intuitions are not affected
-by the set of alternatives queried in our paradigm. This finding is
-important because literal semantic data generated in these three
-conditions are used to simulate the effects of different alternative
-sets on implicature generation in our model.
+differences between two and five alternative conditions
+(\(\beta=-0.05\), \(z = -0.53\), \(p = 0.59\)) or between four and five
+alternative conditions (\(\beta = -0.04\), \(z = -0.52\), \(p = 0.6\)).
+The addition of condition as a predictor did not significantly improve
+model fit when compared to a model without the condition variable using
+ANOVA (\(\chi^2(2) = 0.43\), \(p = 0.81\)). These findings suggest that
+literal semantic intuitions are not affected by the set of alternatives
+queried in our paradigm. This finding is important because literal
+semantic data generated in these three conditions are used as input to
+our model to simulate the effects of different alternative sets on
+implicature generation.
 
@@
 Model fit with human judgments was significantly improved by the
-inclusion of alternatives beyond the entailment items (Table 1). The
-two-alternatives model contained only entailment items, which, under
-classic accounts, should be sufficient to generate implicature, but fit
-to data was quite poor with these items. The addition of a generic
-negative element produced some gains in performance, but much higher
-performance was found when we included four and five alternatives, with
-the alternatives derived empirically for the specific scale we used. An
-example fit for the five-alternatives model is shown in Figure
+inclusion of alternatives beyond the entailment items (Table 1). The two
+alternatives model contained only entailment items, which, under classic
+accounts, should be sufficient to generate implicature, but fit to data
+was quite poor with these items. The addition of a generic negative
+element produced some gains in performance, but much higher performance
+was found when we included four and five alternatives, with the
+alternatives derived empirically for the specific scale we used. An
+example fit for the five alternatives model is shown in Figure
 \ref{fig:fiveAltsScatter}.
@@
 \begin{figure}[t]
-\includegraphics{figs/fiveAltsScatter-1} \caption[Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1]{Judgments from the four-alternatives condition of Experiment 3 are plotted against model predictions using the five-alternatives data from Experiment 1.
+\includegraphics{figs/fiveAltsScatter-1} \caption[Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2]{Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2.
 Colors show the star rating for individual judgments.}\label{fig:fiveAltsScatter}

### 2016-02-02 Paper/Paper.Rmd
incorporated some of Mika's comments

@@
 abstract: 
-    Successful communication regularly requires listeners to make pragmatic inferences - enrichments beyond the literal meaning of a speaker's utterance.
+    Successful communication regularly requires listeners to make pragmatic inferences --- enrichments beyond the literal meaning of a speaker's utterance.
 For example, when interpreting a sentence such as "Alice ate some of the cookies," listeners routinely infer that Alice did not eat all of them.
@@
 In our current work, we pick up where these previous studies left off,  considering the set of alternatives for implicature using the RSA model.
-To gain empirical traction on this issue, however, we broaden the set of scales we consider.
+To gain empirical traction on this issue, we broaden the set of scales we consider.
 Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g., *liked* / *loved,* *palatable* / *delicious*).
@@
 
-We recruited 30 workers on AMT. All participants were native English speakers and naive to the purpose of the experiment.
+We recruited 30 workers on Amazon Mechanical Turk (AMT). All participants were native English speakers and naive to the purpose of the experiment.
 
@@
 
-Participants were presented with a target scalar item from five scales, selected from @vantiel2014b (see Figure \ref{fig:allScalesTable}).
+Participants were presented with a target scalar item from five scales, selected from @vantiel2014b.
 These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the the food was \____," with a target scalar presented in the blank.
@@
 Conditions were run sequentially.
-In each condition we recruited 30 participants from Amazon Mechanical Turk (AMT).
+In each condition we recruited 30 participants from AMT.
 In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
@@
 Several trends are visible.
-First, in each scale, the alternatives spanned the star scale - there were scalar items that were highly compatible with both the lowest and highest numbers of stars.
+First, in each scale, the alternatives spanned the star scale --- there were scalar items that were highly compatible with both the lowest and highest numbers of stars.
 Second, participant compatibility judgments match intuitive literal semantics.
@@
 This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
-We see clear variability between scalar families (literal semantic distributions for *memorable* are considerably different from *palatable*), but also substantial consistency across conditions.
+We see clear variability between scalar families (literal semantic judgments for *memorable* are considerably different from *palatable*), but also substantial consistency for individual scalar items across conditions (*good* in the two alternative condition is similar to *good* in the four and five alternative condition).
 
@@
 The two alternatives model contained only entailment items, which, under classic accounts, should be sufficient to generate implicature, but fit to data was quite poor with these items.
-The addition of a generic negative element produced some gains in performance, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
+The addition of a generic negative element produced some gains, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
 An example fit for the five alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
@@
 # Correlation scatter plot
-ggplot(subset(plotData, study == "Five alts"), aes(x = listener.p2, y = preds, col=stars)) + 
+ggplot(subset(plotData, study == "Five alts"),
+       aes(x = listener.p2, y = preds, col=stars)) + 
   geom_point() +

### 2016-02-02 Paper/Paper.tex
incorporated some of Mika's comments

@@
 Successful communication regularly requires listeners to make pragmatic
-inferences - enrichments beyond the literal meaning of a speaker's
+inferences --- enrichments beyond the literal meaning of a speaker's
 utterance. For example, when interpreting a sentence such as ``Alice ate
@@
 considering the set of alternatives for implicature using the RSA model.
-To gain empirical traction on this issue, however, we broaden the set of
-scales we consider. Our inspiration for this move comes from work by
-{van Tiel}, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
+To gain empirical traction on this issue, we broaden the set of scales
+we consider. Our inspiration for this move comes from work by {van
+Tiel}, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
 phenomenon that they dubbed ``scalar diversity,'' namely the substantial
@@
 
-We recruited 30 workers on AMT. All participants were native English
-speakers and naive to the purpose of the experiment.
+We recruited 30 workers on Amazon Mechanical Turk (AMT). All
+participants were native English speakers and naive to the purpose of
+the experiment.
 
@@
 Participants were presented with a target scalar item from five scales,
-selected from {van Tiel} et al. (2014) (see Figure
-\ref{fig:allScalesTable}). These were embedded in a sentence such as,
-``In a recent restaurant review someone said they thought the the food
-was \_\_\_\_," with a target scalar presented in the blank. Participants
-were then asked to generate plausible alternatives by responding to the
-question, ``If they'd felt differently about the food, what other words
-could they have used instead of \_\_\_\_?" They were prompted to
-generate three unique alternatives.
+selected from {van Tiel} et al. (2014). These were embedded in a
+sentence such as, ``In a recent restaurant review someone said they
+thought the the food was \_\_\_\_," with a target scalar presented in
+the blank. Participants were then asked to generate plausible
+alternatives by responding to the question, ``If they'd felt differently
+about the food, what other words could they have used instead of
+\_\_\_\_?" They were prompted to generate three unique alternatives.
 
@@
 Conditions were run sequentially. In each condition we recruited 30
-participants from Amazon Mechanical Turk (AMT). In the two alternatives
-condition, 16 participants were excluded for either failing to pass two
-training trials or because they were not native English speakers,
-leaving a total sample of 14
+participants from AMT. In the two alternatives condition, 16
+participants were excluded for either failing to pass two training
+trials or because they were not native English speakers, leaving a total
+sample of 14
 participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
@@
 items ordered horizontally by valence. Several trends are visible.
-First, in each scale, the alternatives spanned the star scale - there
+First, in each scale, the alternatives spanned the star scale --- there
 were scalar items that were highly compatible with both the lowest and
@@
 We see clear variability between scalar families (literal semantic
-distributions for \emph{memorable} are considerably different from
-\emph{palatable}), but also substantial consistency across conditions.
+judgments for \emph{memorable} are considerably different from
+\emph{palatable}), but also substantial consistency for individual
+scalar items across conditions (\emph{good} in the two alternative
+condition is similar to \emph{good} in the four and five alternative
+condition).
 
@@
 was quite poor with these items. The addition of a generic negative
-element produced some gains in performance, but much higher performance
-was found when we included four and five alternatives, with the
-alternatives derived empirically for the specific scale we used. An
-example fit for the five alternatives model is shown in Figure
-\ref{fig:fiveAltsScatter}.
+element produced some gains, but much higher performance was found when
+we included four and five alternatives, with the alternatives derived
+empirically for the specific scale we used. An example fit for the five
+alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
 

### 2016-02-02 Paper/Paper.Rmd
last pass???

@@
 Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
-Red coloring denotes ``neutral\" items aded in the five alternatives condition."}
+Red coloring denotes ``neutral\" items added in the five alternatives condition."}
 
@@
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
+Each participant was presented with all scalar items in a random order.
 
@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \``liked.\"(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \``liked.\""}
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \``liked.\" (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \``liked.\""}
 
@@
 The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
-If it does we should see differences in these judgments for shared items between experiments.
+If it does we should see differences in these judgments for shared items between conditions
 
@@
 In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternative condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
-In the five alternative condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))` participants.
+We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternatives condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+In the five alternatives condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))` participants.
 
@@
 
-The two alternatives condition included only the two terms in the pairs from @vantiel2014b.
-The four alternatives condition included the two scalar items plus the top two alternatives generated for each scalar family by participants in Experiment 1.
+The two alternatives condition only included entailment pairs taken from @vantiel2014b.
+The four alternatives condition included entailment pairs plus the top two alternatives generated for each scalar family by participants in Experiment 1.
 The five alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1.
@@
 *all* or *excellent*) entailment items were seen as compatible with five-star ratings.
-This means participants' compatibility judgements reflect literal semantic intuitions, not enriched pragmatic judgments.
-We see clear variability between scalar families (literal semantic judgments for *memorable* are considerably different from *palatable*), but also substantial consistency for individual scalar items across conditions (*good* in the two alternative condition is similar to *good* in the four and five alternative condition).
+This means participants' compatibility judgments reflect literal semantic intuitions, not enriched pragmatic judgments.
+We see clear variability between scalar families (literal semantic judgments for *memorable* are considerably different from *palatable*), but also substantial consistency for individual scalar items across conditions (*good* in the two alternatives condition is similar to *good* in the four and five alternative conditions).
 
@@
 
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.15, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements in Experiment 3.
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.15, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity in reporting."}
+Each panel shows one scalar pair, with only entailment items shown here for simplicity in reporting."}
 # Get zero's in data frame
@@
 We regressed pragmatic judgments on scale and experimental condition with subject- and word-level random effects, which was the maximal structure that converged.
-There were no significant differences between the two alternatives and four alternatives conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $t(`r round(sumGlm2$coefficients[14], 0)`) = `r round(sumGlm2$coefficients[20], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
+There were no significant differences between the two alternative and four alternative conditions ($\beta = `r round(sumGlm2$coefficients[2], 2)`$, $t(`r round(sumGlm2$coefficients[14], 0)`) = `r round(sumGlm2$coefficients[20], 2)`$, $p = `r round(sumGlm2$coefficients[26], 2)`$).
 The addition of the condition predictor did not significantly improve model fit when compared to a model without that variable ($\chi^2(`r anovaResults$"Chi Df"[2]`) = `r round(anovaResults$Chisq[2], 2)`$, $p = `r round(anovaResults$"Pr(>Chisq)"[2], 2)`$).

### 2016-02-02 Paper/Paper.tex
last pass???

@@
 Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
-Red coloring denotes ``neutral" items aded in the five alternatives condition.}\label{fig:allScalesTable}
+Red coloring denotes ``neutral" items added in the five alternatives condition.}\label{fig:allScalesTable}
 \end{figure}
@@
 \_\_\_\_?" They were prompted to generate three unique alternatives.
+Each participant was presented with all scalar itmes in a random order.
 
@@
 
-\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked."(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar ``liked."}\label{fig:stimuli_exp1}
+\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked." (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar ``liked."}\label{fig:stimuli_exp1}
 \end{figure*}
@@
 semantic judgments. If it does we should see differences in these
-judgments for shared items between experiments.
+judgments for shared items between conditions
 
@@
 We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
-In the four alternative condition, 7 participants were excluded for
+In the four alternatives condition, 7 participants were excluded for
 either failing to pass two training trials or not being native English
 speakers, leaving a total sample of 23 participants. In the five
-alternative condition, 3 participants were excluded for either failing
+alternatives condition, 3 participants were excluded for either failing
 to pass two training trials or not being native English speakers,
@@
 
-The two alternatives condition included only the two terms in the pairs
-from {van Tiel} et al. (2014). The four alternatives condition included
-the two scalar items plus the top two alternatives generated for each
-scalar family by participants in Experiment 1. The five alternatives
-condition included the four previous items plus one more neutral item
-chosen from alternatives generated in Experiment 1.
+The two alternatives condition only included entailment pairs taken from
+{van Tiel} et al. (2014). The four alternatives condition included
+entailment pairs plus the top two alternatives generated for each scalar
+family by participants in Experiment 1. The five alternatives condition
+included the four previous items plus one more neutral item chosen from
+alternatives generated in Experiment 1.
 
@@
 \emph{palatable}), but also substantial consistency for individual
-scalar items across conditions (\emph{good} in the two alternative
+scalar items across conditions (\emph{good} in the two alternatives
 condition is similar to \emph{good} in the four and five alternative
-condition).
+conditions).
 

### 2016-02-02 Paper/Paper.Rmd
last pass

@@
 
-In our current work, we pick up where these previous studies left off,  considering the set of alternatives for implicature using the RSA model.
+We pick up where these previous studies left off,  considering the set of alternatives for implicature using the RSA model.
 To gain empirical traction on this issue, we broaden the set of scales we consider.
-Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g., *liked* / *loved,* *palatable* / *delicious*).
+Our inspiration for this move comes from work by @vantiel2014b, who examined a phenomenon that they dubbed "scalar diversity," namely the substantial difference in the strength of scalar implicature across a variety of scalar pairs (e.g., *liked* / *loved*, *palatable* / *delicious*).
 Making use of this diversity allows us to investigate the ways that different alternative sets give rise to implicatures of different strengths across scales.
 
-In our current work, we use a computational framework to investigate the set of alternatives that best allow the model to predict human pragmatic judgments.
+In our current work, we use a computational framework to investigate the set of alternatives that best allow the model to predict human pragmatic judgments across a series of different scales.
 We begin by presenting the computational framework (RSA) we use throughout the paper.
@@
 Green coloring denotes classic entailment items pulled from van Tiel et al.
-(2014), used in the two alternative condition.
-Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
+(2014), used in the two alternatives condition.
+Blue coloring denotes top-two alternatives added to entailment scales in the four alternatives condition.
 Red coloring denotes ``neutral\" items added in the five alternatives condition."}
@@
 
-Participants were presented with a target scalar item from five scales, selected from @vantiel2014b.
+On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b.
 These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the the food was \____," with a target scalar presented in the blank.
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
-Each participant was presented with all scalar items in a random order.
 
@@
 The two alternatives condition makes a test of the hypothesis that the two members of the classic Horn (entailment) scale [@horn1972] are the only alternatives necessary to predict the strength of listeners' pragmatic inference.
-The four and five alternatives conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
+The four and five alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternative conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
 If it does we should see differences in these judgments for shared items between conditions
@@
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items shown here for simplicity in reporting."}
+Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting."}
 # Get zero's in data frame
@@
 We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives, and 4) the expanded set of five alternatives.
-Literal semantics for the generic negative alternative serve as a baseline ``none"-style semantics in which the scalar item is only compatible with 1 star.
+Literal semantics for the generic negative alternative served as a baseline ``none"-style semantics in which the scalar item was only compatible with 1 star.
 

### 2016-02-02 Paper/Paper.tex
last pass

@@
 
-In our current work, we pick up where these previous studies left off,
-considering the set of alternatives for implicature using the RSA model.
-To gain empirical traction on this issue, we broaden the set of scales
-we consider. Our inspiration for this move comes from work by {van
-Tiel}, Van Miltenburg, Zevakhina, \& Geurts (2014), who examined a
-phenomenon that they dubbed ``scalar diversity,'' namely the substantial
-difference in the strength of scalar implicature across a variety of
-scalar pairs (e.g., \emph{liked} / \emph{loved,} \emph{palatable} /
-\emph{delicious}). Making use of this diversity allows us to investigate
-the ways that different alternative sets give rise to implicatures of
-different strengths across scales.
+We pick up where these previous studies left off, considering the set of
+alternatives for implicature using the RSA model. To gain empirical
+traction on this issue, we broaden the set of scales we consider. Our
+inspiration for this move comes from work by {van Tiel}, Van Miltenburg,
+Zevakhina, \& Geurts (2014), who examined a phenomenon that they dubbed
+``scalar diversity,'' namely the substantial difference in the strength
+of scalar implicature across a variety of scalar pairs (e.g.,
+\emph{liked} / \emph{loved}, \emph{palatable} / \emph{delicious}).
+Making use of this diversity allows us to investigate the ways that
+different alternative sets give rise to implicatures of different
+strengths across scales.
 
@@
 set of alternatives that best allow the model to predict human pragmatic
-judgments. We begin by presenting the computational framework (RSA) we
-use throughout the paper. We next describe a series of experiments
-designed to measure both the literal semantics of a set of scalar items
-(used as input to the model) and comprehenders' pragmatic judgments for
-these same items (used for model comparison). These experiments allow us
-to compare the effects of different alternative sets on our ability to
-model listeners' pragmatic judgments. To preview our results: we find
-that standard entailment alternatives do not allow us to fit
-participants' judgments, but that expanding the range of alternatives
-empirically (by asking participants to generate alternative messages)
-allows us to predict listeners' pragmatic judgments with high accuracy.
+judgments across a series of different scales. We begin by presenting
+the computational framework (RSA) we use throughout the paper. We next
+describe a series of experiments designed to measure both the literal
+semantics of a set of scalar items (used as input to the model) and
+comprehenders' pragmatic judgments for these same items (used for model
+comparison). These experiments allow us to compare the effects of
+different alternative sets on our ability to model listeners' pragmatic
+judgments. To preview our results: we find that standard entailment
+alternatives do not allow us to fit participants' judgments, but that
+expanding the range of alternatives empirically (by asking participants
+to generate alternative messages) allows us to predict listeners'
+pragmatic judgments with high accuracy.
 
@@
 Green coloring denotes classic entailment items pulled from van Tiel et al.
-(2014), used in the two alternative condition.
-Blue coloring denotes top-two alternatives added to entailment scales in the four alternative condition.
+(2014), used in the two alternatives condition.
+Blue coloring denotes top-two alternatives added to entailment scales in the four alternatives condition.
 Red coloring denotes ``neutral" items added in the five alternatives condition.}\label{fig:allScalesTable}
@@
 
-Participants were presented with a target scalar item from five scales,
-selected from {van Tiel} et al. (2014). These were embedded in a
-sentence such as, ``In a recent restaurant review someone said they
-thought the the food was \_\_\_\_," with a target scalar presented in
-the blank. Participants were then asked to generate plausible
-alternatives by responding to the question, ``If they'd felt differently
-about the food, what other words could they have used instead of
-\_\_\_\_?" They were prompted to generate three unique alternatives.
-Each participant was presented with all scalar itmes in a random order.
+On each trial participants were presented with a target scalar item from
+five scales, selected from the entailment items used in {van Tiel} et
+al. (2014). These were embedded in a sentence such as, ``In a recent
+restaurant review someone said they thought the the food was \_\_\_\_,"
+with a target scalar presented in the blank. Participants were then
+asked to generate plausible alternatives by responding to the question,
+``If they'd felt differently about the food, what other words could they
+have used instead of \_\_\_\_?" They were prompted to generate three
+unique alternatives.
 
@@
 (Horn, 1972) are the only alternatives necessary to predict the strength
-of listeners' pragmatic inference. The four and five alternatives
+of listeners' pragmatic inference. The four and five alternative
 conditions then add successively more alternatives to test whether
 including a larger number of alternatives will increase model
-fit.\footnote{Note that alternatives in the four and five alternatives conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
+fit.\footnote{Note that alternatives in the four and five alternative conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.}
 A secondary goal of Experiment 2 is to test whether the set of
@@
 \emph{excellent}) entailment items were seen as compatible with
-five-star ratings. This means participants' compatibility judgements
+five-star ratings. This means participants' compatibility judgments
 reflect literal semantic intuitions, not enriched pragmatic judgments.
@@
 
-\caption[Pragmatic listener judgements in Experiment 3]{Pragmatic listener judgements in Experiment 3.
+\caption[Pragmatic listener judgments from Experiment 3]{Pragmatic listener judgments from Experiment 3.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
 Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only entailment items (two alternatives condition) shown here for simplicity in reporting.}\label{fig:exp2Plots}
+Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting.}\label{fig:exp2Plots}
 \end{figure*}
@@
 structure that converged. There were no significant differences between
-the two alternatives and four alternatives conditions (\(\beta = 0.05\),
+the two alternative and four alternative conditions (\(\beta = 0.05\),
 \(t(150) = 1.04\), \(p = 0.3\)). The addition of the condition predictor
@@
 and 4) the expanded set of five alternatives. Literal semantics for the
-generic negative alternative serve as a baseline ``none``-style
-semantics in which the scalar item is only compatible with 1 star.
+generic negative alternative served as a baseline ``none``-style
+semantics in which the scalar item was only compatible with 1 star.
 

### 2016-02-02 Paper/Paper.Rmd
Final read

@@
 On each trial participants were presented with a target scalar item from five scales, selected from the entailment items used in @vantiel2014b.
-These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the the food was \____," with a target scalar presented in the blank.
+These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank.
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.

### 2016-02-02 Paper/Paper.tex
Final read

@@
 al. (2014). These were embedded in a sentence such as, ``In a recent
-restaurant review someone said they thought the the food was \_\_\_\_,"
-with a target scalar presented in the blank. Participants were then
-asked to generate plausible alternatives by responding to the question,
-``If they'd felt differently about the food, what other words could they
-have used instead of \_\_\_\_?" They were prompted to generate three
-unique alternatives.
+restaurant review someone said they thought the food was \_\_\_\_," with
+a target scalar presented in the blank. Participants were then asked to
+generate plausible alternatives by responding to the question, ``If
+they'd felt differently about the food, what other words could they have
+used instead of \_\_\_\_?" They were prompted to generate three unique
+alternatives.
 

### 2016-03-17 analysis/BetweenExpDifferences.Rmd
added section - comparing non-compliant vs compliant literal listener data.

@@
 
+### Save non-compliant
+```{r}
+allL0ListenerNC <- rbind(e8, e10, e12) %>%
+  subset(scale != "training1" & scale != "training2")
+allL0ListenerNC$exp <- as.factor(allL0ListenerNC$exp)
+## judgment :: numeric
+allL0ListenerNC$judgment <- as.numeric(allL0ListenerNC$judgment) 
+allL0ListenerNC$stars <- as.numeric(as.character(allL0ListenerNC$stars)) / 20
+
+ne8 <- allL0ListenerNC %>%
+  filter(exp == "e8") %>%
+  group_by(workerid) %>%
+  summarise(n = 1) %>%
+  nrow()
+ne10 <- allL0ListenerNC %>%
+  filter(exp == "e10") %>%
+  group_by(workerid) %>%
+  summarise(n = 1) %>%
+  nrow()
+ne12 <- allL0ListenerNC %>%
+  filter(exp == "e12") %>%
+  group_by(workerid) %>%
+  summarise(n = 1) %>%
+  nrow()
+
+literalD_NC <- allL0ListenerNC %>%
+  group_by(exp, scale, degree, stars) %>%
+  summarise(cnt.judgment = sum(judgment))
+literalD_NC$speaker.p <- with(literalD_NC,
+                           ifelse(exp == "e8", cnt.judgment / ne8,
+                                  ifelse(exp == "e10",
+                                         cnt.judgment / ne10, cnt.judgment / ne12)))
+literalD_NC$exp <- as.character(literalD_NC$exp)
+literalD_NC$words <- mapply(lookupScalar, literalD_NC$degree, literalD_NC$scale, literalD_NC$exp)
+drop <- c("cnt.judgment", "degree")
+literalD_NC <- literalD_NC[, !(names(literalD_NC) %in% drop)]
+
+# normalize for comparison
+for (e in unique(literalD_NC$exp)) {
+  for (word in unique(literalD_NC$words)) {
+    literalD_NC[literalD_NC$words == word & literalD_NC$exp == e, "speaker.p"] <-
+      rrrsa::rsa.normVec(subset(literalD_NC, words == word & exp == e)$speaker.p)
+  }
+}
+
+subset(literalD_NC, words == "excellent" & exp == "e12")
+subset(peloquinFrank_4Alts, words == "excellent")
+rrrsa::rsa.normVec(subset(speakerL12, scale == "good_excellent" & degree == "hi1")$speaker.p)
+
+```
+
 ## glmer()

### 2016-04-26 Paper/Paper.Rmd
commit before making cog sci edits

@@
 }
-
+#####
+##### normedVec()
+##### normalize vector
+#####
 normedVec <- function(vec) vec / sum(vec)

### 2016-04-26 Paper/Paper.Rmd
new results table and commented out old one

@@
 ```{r, libraries}
+library(rrrsa)
 library(dplyr)
@@
 ```{r xtable, results = "asis"}
+check_words <- c("good", "excellent", "liked", "loved", "memorable", "unforgettable", "palatable", "delicious", "some", "all")
 
-# Tuned model run data
-plotData <- allModelRunData %>%
-  mutate(study = ifelse(numAlts == 5, "Five alts", 
-                        ifelse(numAlts == 4, "Four alts",
-                               ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
-  gather(Experiment, cors, c(corE6, corE11)) %>%
-  mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
+exps <- c("e6", "e11")
+res_table <- data.frame()
+compare_indices2 <- which(peloquinFrank_2Alts$words %in% check_words)
+for (exp in exps) {
+  two_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_2Alts,
+            semanticsVarName = "speaker.p",
+            quantityVarName = "stars",
+            itemVarName = "words",
+            groupName = "scale",
+            compareIndices = compare_indices2,
+            compareDataName = exp,
+            alphas = seq(0, 10, by = 0.1))
+  res_table <- rbind(res_table, exp = two_alt_alphas[1, ])
+}
 
-tableCors <- plotData  %>%
-  select(cors, study, Experiment, alphas) %>%
-  unique() %>%
-  mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
-  spread(Experiment, cors)
+compare_indices3 <- which(peloquinFrank_3Alts$words %in% check_words)
+for (exp in exps) {
+  three_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_3Alts,
+              semanticsVarName = "speaker.p",
+              quantityVarName = "stars",
+              itemVarName = "words",
+              groupName = "scale",
+              compareIndices = compare_indices3,
+              compareDataName = exp,
+              alphas = seq(0, 20, by = 0.1))
+  res_table <- rbind(res_table, exp = three_alt_alphas[1, ])
+}
+compare_indices4 <- which(peloquinFrank_4Alts$words %in% check_words)
+for (exp in exps) {
+  four_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_4Alts,
+              semanticsVarName = "speaker.p",
+              quantityVarName = "stars",
+              itemVarName = "words",
+              groupName = "scale",
+              compareIndices = compare_indices4,
+              compareDataName = exp,
+              alphas = seq(0, 10, by = 0.1))
+  res_table <- rbind(res_table, exp = four_alt_alphas[1, ])
+}
+compare_indices5 <- which(peloquinFrank_5Alts$words %in% check_words)
+for (exp in exps) {
+  five_alt_alphas <- rsa.tuneDepthAlpha(data = peloquinFrank_5Alts,
+              semanticsVarName = "speaker.p",
+              quantityVarName = "stars",
+              itemVarName = "words",
+              groupName = "scale",
+              compareIndices = compare_indices5,
+              compareDataName = exp,
+              alphas = seq(0, 10, by = 0.1))
+  res_table <- rbind(res_table, exp = five_alt_alphas[1, ])
+}
+res_table$row_num <- seq(1, nrow(res_table))
+res_table <- res_table %>% 
+  mutate(exp = ifelse(row_num %% 2 == 0, "Human judgments 4-alts", "Human judgments 2-alts"),
+         model = ifelse(row_num < 3, "2-alts",
+                           ifelse(row_num < 5, "3-alts",
+                                  ifelse(row_num < 7, "4-alts", "5-alts"))),
+         result = paste0("", round(cor, 2), " (alpha = ", alpha, ")")) %>%
+  select(model, result, exp) %>%
+  spread(exp, result)
 
-# Plot model performance table
-names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
-tableCors <- tableCors[c(3, 4, 2, 1),]
-tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
+tab <- xtable(res_table[4:1, ], caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
 print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
       sanitize.colnames.function = identity)
+
+# two_alt_alphas[1,]
+# three_alt_alphas[1,]
+# four_alt_alphas[1,]
+# five_alt_alphas[1,]
+# 
+# # Tuned model run data
+# plotData <- allModelRunData %>%
+#   mutate(study = ifelse(numAlts == 5, "Five alts", 
+#                         ifelse(numAlts == 4, "Four alts",
+#                                ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
+#   gather(Experiment, cors, c(corE6, corE11)) %>%
+#   mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
+# 
+# tableCors <- plotData  %>%
+#   select(cors, study, Experiment, alphas) %>%
+#   unique() %>%
+#   mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
+#   spread(Experiment, cors)
+#   
+# # Plot model performance table
+# names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
+# tableCors <- tableCors[c(3, 4, 2, 1),]
+# tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
+# print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
+#       sanitize.colnames.function = identity)
 

### 2016-04-26 Paper/Paper.Rmd
new correlation plot (last plot)

@@
 Colors show the star rating for individual judgments."}
-# Correlation scatter plot
-ggplot(subset(plotData, study == "Five alts"),
-       aes(x = listener.p2, y = preds, col=stars)) + 
+best_alpha <- 4.5
+best_run <- plyr::ddply(.data = peloquinFrank_5Alts, .variables =c("scale"), .fun = rsa.runDf,
+                        semanticsVarName = "speaker.p",
+                        quantityVarName = "stars",
+                        itemVarName = "words",
+                        alpha = best_alpha) %>%
+  filter(words %in% check_words)
+
+## Correlation scatter plot
+ggplot(best_run, aes(x = preds, y = e11, col = stars)) +
   geom_point() +
@@
         axis.title.y = element_text(size = 8.5)) 
-  # ggtitle("Model fit\nFive alternatives")
 ```

### 2016-04-26 Paper/Paper.Rmd
fixed problems with example literal and pragmatic listener .png - it was the quotes

@@
 
-```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar \``liked.\" (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar \``liked.\""}
-
-# Screen shots of literal listener and pragmatic listener conditions
-grid::grid.raster(png::readPNG("figs/exp1_stimuli.png"))
-```
-
 Figure \ref{fig:exp2_altsPlot_likedLoved} shows an example alternative set for the scalar items *liked* and *loved* (combined).
@@
 ## Methods
+
+```{r stimuli_exp1, fig.env = "figure*", fig.pos = "t", fig.width=6, fig.height=4, fig.align='center', set.cap.width=TRUE, num.cols.cap=2, fig.cap = "(Left) A trial from Experiment 2 (literal listener) with the target scalar 'liked'.
+(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar 'liked'."}
+
+# Screen shots of literal listener and pragmatic listener conditions
+grid::grid.raster(png::readPNG("figs/exp1_stimuli.png"))
+```
 
@@
 res_table <- res_table %>% 
-  mutate(exp = ifelse(row_num %% 2 == 0, "Human judgments 4-alts", "Human judgments 2-alts"),
+  mutate(exp = ifelse(row_num %% 2 == 0, "Empirical 4-alts", "Empirical 2-alts"),
          model = ifelse(row_num < 3, "2-alts",

### 2016-04-26 Paper/Paper.Rmd
minor edits from Jason suggestions

@@
 As listeners, our ability to make precise inferences about a speaker's intended meaning in context is  indispensable to successful communication.
-For example, listeners commonly enrich the meaning of the scalar item *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@levinson2000].
+For example, listeners commonly enrich the meaning of the word *some* to *some but not all* in sentences like "Alice ate some of the cookies" [@grice1975;@levinson2000].
 These inferences, called _scalar implicatures_, have been an important test case for understanding pragmatic inferences more generally.
 A Gricean account of this phenomenon assumes listeners reason about a speaker's intended meaning by incorporating knowledge about A) alternative scalar items a speaker could have used (such as *all*) and B) the relative informativity of using such alternatives [@grice1975].
-According to this account, a listener will infer that the speaker must have intended that Alice did not eat all the cookies because it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
+According to this account, a listener will infer that the speaker intended to convey that Alice did not eat all the cookies because it would have been underinformative to use the descriptor *some* when the alternative *all* could have been used just as easily.
 
@@
 
-```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked vs. loved in Experiment 1."}
+```{r exp2_altsPlot_likedLoved, fig.pos = "t", fig.align='center', fig.height=2, fig.cap = "Combined counts for participant-generated alternatives for liked and loved in Experiment 1."}
 
@@
 We considered four different alternative sets, with empirical measurements corresponding to those shown in Figure \ref{fig:allScalesTable}: 1) the two alternatives in the classic entailment scales, 2) those two alternatives with the addition of a generic negative alternative, 3) the expanded set of four alternatives, and 4) the expanded set of five alternatives.
-Literal semantics for the generic negative alternative served as a baseline ``none"-style semantics in which the scalar item was only compatible with 1 star.
+Literal semantics for the generic negative alternative served as a baseline ``none" semantics in which the scalar item was only compatible with 1 star.
 
@@
       sanitize.colnames.function = identity)
-
-# two_alt_alphas[1,]
-# three_alt_alphas[1,]
-# four_alt_alphas[1,]
-# five_alt_alphas[1,]
-# 
-# # Tuned model run data
-# plotData <- allModelRunData %>%
-#   mutate(study = ifelse(numAlts == 5, "Five alts", 
-#                         ifelse(numAlts == 4, "Four alts",
-#                                ifelse(numAlts == 3, "Two alts + generic negative ", "Two alts")))) %>%
-#   gather(Experiment, cors, c(corE6, corE11)) %>%
-#   mutate(Experiment = ifelse(Experiment == "corE6", "1b", "3b"))
-# 
-# tableCors <- plotData  %>%
-#   select(cors, study, Experiment, alphas) %>%
-#   unique() %>%
-#   mutate(Experiment = ifelse(Experiment == "1b", "Pragmatic_Listener_exp1", "Pragmatic_Listener_exp2")) %>%
-#   spread(Experiment, cors)
-#   
-# # Plot model performance table
-# names(tableCors) <- c("Model", "$\\alpha$", "Two alts", "Four alts")
-# tableCors <- tableCors[c(3, 4, 2, 1),]
-# tab <- xtable(tableCors, caption = "Model performance with fitted alpha levels. Model fit assessed through correlation with human judgments in the two conditions of Experiment 3.")
-# print(tab, type="latex", floating = TRUE, include.rownames = FALSE, comment = FALSE,
-#       sanitize.colnames.function = identity)
-
-# Correlation bar chart
-# corBarChart <- ggplot(plotData, aes(x=study, y=cors, fill = Experiment)) + 
-#   geom_bar(stat="identity", position="dodge") +
-#   ylab("Correlation") +
-#   xlab("Model") +
-#   ylim(0, 1) + 
-#   ggtitle("Model fit correlation coefficients") +
-#   guides(colour=FALSE) +
-#   geom_text(aes(x = study, y=as.numeric(cors) + 0.025, label = round(cors, 2), col=(Experiment)))
-
-# modifiedPlotData <- plotData %>%
-#   gather(pragStudy, pragChoice, c(9,11))
-# fullRepresentationFit <- qplot(stars, pragChoice, col=degree, shape = pragStudy,
-#       data=subset(modifiedPlotData, study == "Full")) +
-#   ylim(0, 1) +
-#   facet_wrap(~scale) + 
-#   geom_line(aes(y = preds), lty = 4)
-# fullRepresentationFit
-# gridExtra::grid.arrange(corBarChart, symmetricCorPlot, ncol = 2, widths = c(2.5,3))
 ```

### 2016-04-28 Paper/Paper.Rmd
adding information about trials per participant for three exps

@@
 These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank.
-Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" They were prompted to generate three unique alternatives.
+Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order.
+In total each participant saw ten target scalar items (each entailment pair from the five scales selected from @vantiel2014b ).
 
@@
 The four and five alternative conditions then add successively more alternatives to test whether including a larger number of alternatives will increase model fit.\footnote{Note that alternatives in the four and five alternative conditions were chosen on the basis of Experiment 1, which was run chronologically after the two alternative condition; all literal listener experiments are grouped together for simplicity in reporting.} A secondary goal of Experiment 2 is to test whether the set of alternatives queried during literal semantic elicitation impacts literal semantic judgments.
-If it does we should see differences in these judgments for shared items between conditions
+If it does we should see differences in these judgments for shared items between conditions.
 
@@
 In the two alternatives condition, `r 30 - length(unique(exp1a$workerid))` participants were excluded for either failing to pass two training trials or because they were not native English speakers, leaving a total sample of `r length(unique(exp1a$workerid))` participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.} In the four alternatives condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
+We believe the task may have been too difficult for most respondents who may have been confused by the question wording.
+Training trials in later conditions included clearer language.} In the four alternatives condition,  `r 30 - length(unique(exp1b$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1b$workerid))` participants.
 In the five alternatives condition, `r 30 - length(unique(exp1c$workerid))` participants were excluded for either failing to pass two training trials or not being native English speakers, leaving a total sample of `r length(unique(exp1c$workerid))` participants.
@@
 
-The two alternatives condition only included entailment pairs taken from @vantiel2014b.
-The four alternatives condition included entailment pairs plus the top two alternatives generated for each scalar family by participants in Experiment 1.
-The five alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1.
+The two alternatives condition only included entailment pairs taken from @vantiel2014b for a total of 5 trails for each participant.
+The four alternatives condition included entailment pairs plus the top two alternatives generated for each scalar family by participants in Experiment 1 (100 trials per participant).
+The five alternatives condition included the four previous items plus one more neutral item chosen from alternatives generated in Experiment 1 (125 trials per participant).
 
@@
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = condition)) + 
+       aes(x = stars, y = speaker.p, col = condition, lty = condition)) + 
   geom_line() + 
@@
 Each participant was presented with all scalar items in a random order.
+Participants in the two alternatives condition gave total of 10 pragmatic judgments.
+Participants in the four alternatives condition gave a total of 20 pragmatic judgments.
 The experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
@@
                                   ifelse(row_num < 7, "4-alts", "5-alts"))),
-         result = paste0("", round(cor, 2), " (alpha = ", alpha, ")")) %>%
+         result = paste0("r = ", round(cor, 2), " (alpha = ", alpha, ")")) %>%
   select(model, result, exp) %>%
@@
 Colors show the star rating for individual judgments."}
-best_alpha <- 4.5
+
+check_words <- c("good", "excellent", "liked", "loved", "memorable", "unforgettable", "palatable", "delicious", "some", "all")
+check_indices <- which(peloquinFrank_5Alts$words %in% check_words)
+best_alpha <- rrrsa::rsa.tuneDepthAlpha(peloquinFrank_5Alts, semanticsVarName = "speaker.p",
+                          quantityVarName = "stars", groupName = "scale", itemVarName = "words",
+                          alphas = seq(1, 5, by = 0.1),  compareDataName = "e11",
+                          compareIndices =check_indices)[1, 'alpha']
+
 best_run <- plyr::ddply(.data = peloquinFrank_5Alts, .variables =c("scale"), .fun = rsa.runDf,

### 2016-04-30 Paper/Paper.Rmd
cogsci edits before sharing with MF

@@
 For example, when interpreting a sentence such as "Alice ate some of the cookies," listeners routinely infer that Alice did not eat all of them.
-A Gricean account of this phenomena assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
+A Gricean account of this phenomenon assumes the presence of alternatives (like "all of the cookies") with varying degrees of informativity, but it remains an open question precisely what these alternatives are.
 To address this question, we collect empirical measurements of speaker and listener judgments about varying sets of alternatives across a range of scales and use these as inputs to a computational model of pragmatic inference.
@@
 Similar scales exist for non-quantifier scales, e.g.
-*loved* entails *liked* (and hence "I liked the movie" implicates that I didn't love it).
+*loved* entails *liked* (hence "I liked the movie" implicates that I didn't love it).
 
@@
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order.
-In total each participant saw ten target scalar items (each entailment pair from the five scales selected from @vantiel2014b ).
+In total each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).
 
@@
 
-The two alternatives condition only included entailment pairs taken from @vantiel2014b for a total of 5 trails for each participant.
+The two alternatives condition only included entailment pairs taken from @vantiel2014b for a total of 50 trials for each participant.
 The four alternatives condition included entailment pairs plus the top two alternatives generated for each scalar family by participants in Experiment 1 (100 trials per participant).
@@
 # for plotting
-speakers$condition <- ifelse(speakers$expt == "e8", "two alts",
+speakers$Condition <- ifelse(speakers$expt == "e8", "two alts",
                                  ifelse(speakers$expt == "e10", 
@@
 ggplot(speakers, 
-       aes(x = stars, y = speaker.p, col = condition, lty = condition)) + 
+       aes(x = stars, y = speaker.p, col = Condition, lty = Condition)) + 
   geom_line() + 
@@
 Figure \ref{fig:exp2Plots} plots pragmatic listener judgment distributions for "weak" / "strong" scalar pairs (e.g.
-*good*/*excellent*).
+*good* / *excellent*).
 Several trends are visible.
@@
 The addition of a generic negative element produced some gains, but much higher performance was found when we included four and five alternatives, with the alternatives derived empirically for the specific scale we used.
-An example fit for the five alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
+Figure \ref{fig:fiveAltsScatter} plots model fit for the five alternatives model.
 

### 2016-05-10 Paper/Paper.Rmd
edits to fig 5 spacing

@@
 Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order.
-In total each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).
+In total, each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).
 
@@
 
-```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2.15, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3.
+```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3.
 Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
@@
         legend.position = "bottom",
+        legend.box = "horizontal",
         legend.margin = unit(.02,"in"),
@@
 
-```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2.25, fig.cap = "Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2.
+```{r fiveAltsScatter, fig.pos = "t", fig.width=3.5, fig.height=2, fig.cap = "Judgments for entailment items from the four alternatives condition of Experiment 3 are plotted against model predictions using the five alternatives data from Experiment 2.
 Colors show the star rating for individual judgments."}

### 2016-05-10 Paper/Paper.Rmd
made MF edits - down to six pages

@@
 Each participant was presented with all scalar items in a random order.
-Participants in the two alternatives condition gave total of 10 pragmatic judgments.
+Participants in the two alternatives condition gave a total of 10 pragmatic judgments.
 Participants in the four alternatives condition gave a total of 20 pragmatic judgments.
@@
 ```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3.
-Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting."}
+Verticle axis shows proportion of participants generating a star rating.
+Horizontal axis shows number of stars on which the utterance was judged.
+Line type denotes condition and colors indicate the particular scalar items.
+Each panel shows one entailment scalar pair."}
 # Get zero's in data frame

### 2016-05-12 Paper/Paper.Rmd
more edits from converting to word
final edits before final cogsci submission

@@
 These were embedded in a sentence such as, "In a recent restaurant review someone said they thought the food was \____," with a target scalar presented in the blank.
-Participants were then asked to generate plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order.
+Participants were then asked to generate three plausible alternatives by responding to the question, "If they'd felt differently about the food, what other words could they have used instead of \____?" Participants saw each scalar item in random order.
 In total, each participant saw ten target scalar items (each entailment pair from the five scales selected from van Tiel et al., 2014).
@@
 
-# Experiment 2: Literal listener task
+# Experiment 2: Literal Listener Task
 
@@
 
-# Experiment 3: Pragmatic Listener
+# Experiment 3: Pragmatic Listener Task
 
@@
 
-## Participants
+## Methods
+
+### Participants
 
@@
 
-## Procedure
+### Design and Procedure
 
@@
 ```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=2, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgments from Experiment 3.
-Verticle axis shows proportion of participants generating a star rating.
+Vertical axis shows proportion of participants generating a star rating.
 Horizontal axis shows number of stars on which the utterance was judged.
@@
 
-# Model
+# Model Simulations
 

### 2016-10-02 Paper/Paper.tex
sanitize

@@
 some of the cookies,'' listeners routinely infer that Alice did not eat
-all of them. A Gricean account of this phenomena assumes the presence of
-alternatives (like ``all of the cookies'') with varying degrees of
+all of them. A Gricean account of this phenomenon assumes the presence
+of alternatives (like ``all of the cookies'') with varying degrees of
 informativity, but it remains an open question precisely what these
@@
 communication. For example, listeners commonly enrich the meaning of the
-scalar item \emph{some} to \emph{some but not all} in sentences like
-``Alice ate some of the cookies'' (Grice, 1975; Levinson, 2000). These
+word \emph{some} to \emph{some but not all} in sentences like ``Alice
+ate some of the cookies'' (Grice, 1975; Levinson, 2000). These
 inferences, called \emph{scalar implicatures}, have been an important
@@
 1975). According to this account, a listener will infer that the speaker
-must have intended that Alice did not eat all the cookies because it
+intended to convey that Alice did not eat all the cookies because it
 would have been underinformative to use the descriptor \emph{some} when
@@
 implicatures. Similar scales exist for non-quantifier scales, e.g.
-\emph{loved} entails \emph{liked} (and hence ``I liked the movie''
+\emph{loved} entails \emph{liked} (hence ``I liked the movie''
 implicates that I didn't love it).
@@
 \emph{some} was judged less appropriate when exact numbers were seen as
-viable alternatives. And in a different paradigm, {van Tiel} (2014)
-found converging evidence that \emph{some} was judged to be atypical for
-small quantities. These data provide indirect evidence that people may
+viable alternatives. And in a different paradigm, van Tiel (2014) found
+converging evidence that \emph{some} was judged to be atypical for small
+quantities. These data provide indirect evidence that people may
 actually consider a broader set of alternatives when computing scalar
@@
 typicality/felicity ratings reported by Degen \& Tanenhaus (2015) and
-{van Tiel} (2014) for the scale \emph{some}/\emph{all}. In order to do
+van Tiel (2014) for the scale \emph{some}/\emph{all}. In order to do
 this, Franke (2014)'s model assigned weights to a set of alternative
@@
 traction on this issue, we broaden the set of scales we consider. Our
-inspiration for this move comes from work by {van Tiel}, Van Miltenburg,
+inspiration for this move comes from work by van Tiel, Van Miltenburg,
 Zevakhina, \& Geurts (2014), who examined a phenomenon that they dubbed
@@
 
-\caption[Combined counts for participant-generated alternatives for liked vs]{Combined counts for participant-generated alternatives for liked vs.
-loved in Experiment 1.}\label{fig:exp2_altsPlot_likedLoved}
+\caption[Combined counts for participant-generated alternatives for liked and loved in Experiment 1]{Combined counts for participant-generated alternatives for liked and loved in Experiment 1.}\label{fig:exp2_altsPlot_likedLoved}
 \end{figure}
@@
 alternatives empirically. This design was inspired by Experiment 3 of
-{van Tiel} et al. (2014).
+van Tiel et al. (2014).
 
@@
 On each trial participants were presented with a target scalar item from
-five scales, selected from the entailment items used in {van Tiel} et
-al. (2014). These were embedded in a sentence such as, ``In a recent
+five scales, selected from the entailment items used in van Tiel et al.
+(2014). These were embedded in a sentence such as, ``In a recent
 restaurant review someone said they thought the food was \_\_\_\_," with
 a target scalar presented in the blank. Participants were then asked to
-generate plausible alternatives by responding to the question, ``If
-they'd felt differently about the food, what other words could they have
-used instead of \_\_\_\_?" They were prompted to generate three unique
-alternatives.
+generate three plausible alternatives by responding to the question,
+``If they'd felt differently about the food, what other words could they
+have used instead of \_\_\_\_?" Participants saw each scalar item in
+random order. In total, each participant saw ten target scalar items
+(each entailment pair from the five scales selected from van Tiel et
+al., 2014).
 
 \subsection{Results and Discussion}\label{results-and-discussion}
-
-\begin{CodeChunk}
-\begin{figure*}[t]
-
-{\centering \includegraphics{figs/stimuli_exp1-1}
-
-}
-
-\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked]{(Left) A trial from Experiment 2 (literal listener) with the target scalar ``liked." (Right) A trial from Experiment 3 (pragmatic listener) with the target scalar ``liked."}\label{fig:stimuli_exp1}
-\end{figure*}
-\end{CodeChunk}
 
@@
 
-\section{Experiment 2: Literal listener
-task}\label{experiment-2-literal-listener-task}
+\section{Experiment 2: Literal Listener
+Task}\label{experiment-2-literal-listener-task}
 
@@
 semantic judgments. If it does we should see differences in these
-judgments for shared items between conditions
+judgments for shared items between conditions.
 
 \subsection{Methods}\label{methods-1}
+
+\begin{CodeChunk}
+\begin{figure*}[t]
+
+{\centering \includegraphics{figs/stimuli_exp1-1}
+
+}
+
+\caption[(Left) A trial from Experiment 2 (literal listener) with the target scalar 'liked']{(Left) A trial from Experiment 2 (literal listener) with the target scalar 'liked'.
+(Right) A trial from Experiment 3 (pragmatic listener) with the target scalar 'liked'.}\label{fig:stimuli_exp1}
+\end{figure*}
+\end{CodeChunk}
 
@@
 participants.\footnote{The majority of respondent data excluded from the two alternatives condition was caused by failure to pass training trials.
-We believe the task may have been too difficult for most respondents and made adjustments to the training trials in later conditions.}
+We believe the task may have been too difficult for most respondents who may have been confused by the question wording.
+Training trials in later conditions included clearer language.}
 In the four alternatives condition, 7 participants were excluded for
@@
 The two alternatives condition only included entailment pairs taken from
-{van Tiel} et al. (2014). The four alternatives condition included
-entailment pairs plus the top two alternatives generated for each scalar
-family by participants in Experiment 1. The five alternatives condition
-included the four previous items plus one more neutral item chosen from
-alternatives generated in Experiment 1.
+van Tiel et al. (2014) for a total of 50 trials for each participant.
+The four alternatives condition included entailment pairs plus the top
+two alternatives generated for each scalar family by participants in
+Experiment 1 (100 trials per participant). The five alternatives
+condition included the four previous items plus one more neutral item
+chosen from alternatives generated in Experiment 1 (125 trials per
+participant).
 
@@
 
-\section{Experiment 3: Pragmatic
-Listener}\label{experiment-3-pragmatic-listener}
+\section{Experiment 3: Pragmatic Listener
+Task}\label{experiment-3-pragmatic-listener-task}
 
@@
 
-\subsection{Participants}\label{participants-2}
+\subsection{Methods}\label{methods-2}
+
+\subsubsection{Participants}\label{participants-2}
 
@@
 
-\subsection{Procedure}\label{procedure}
+\subsubsection{Design and Procedure}\label{design-and-procedure-2}
 
@@
 representing the rating they thought the reviewer likely gave. Each
-participant was presented with all scalar items in a random order. The
-experimental setup is shown in Figure \ref{fig:stimuli_exp1}, right.
+participant was presented with all scalar items in a random order.
+Participants in the two alternatives condition gave a total of 10
+pragmatic judgments. Participants in the four alternatives condition
+gave a total of 20 pragmatic judgments. The experimental setup is shown
+in Figure \ref{fig:stimuli_exp1}, right.
 
@@
 \caption[Pragmatic listener judgments from Experiment 3]{Pragmatic listener judgments from Experiment 3.
-Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged.
-Line type denotes condition, and colors indicate the particular scalar items.
-Each panel shows one scalar pair, with only standard entailment pairs shown here for simplicity in reporting.}\label{fig:exp2Plots}
+Vertical axis shows proportion of participants generating a star rating.
+Horizontal axis shows number of stars on which the utterance was judged.
+Line type denotes condition and colors indicate the particular scalar items.
+Each panel shows one entailment scalar pair.}\label{fig:exp2Plots}
 \end{figure*}
@@
 Figure \ref{fig:exp2Plots} plots pragmatic listener judgment
-distributions for ``weak'' / ``strong'' scalar pairs (e.g.
-\emph{good}/\emph{excellent}). Several trends are visible. First, in
-each scale participants generated implicatures. They were substantially
-less likely to assign high star ratings to weaker scalar terms, despite
-the literal semantic compatibility of those terms with those states
-shown in Experiment 2. Second, the difference between strong and weak
-scalar items varied considerably across scales, consistent with previous
-work ({van Tiel} et al., 2014).
+distributions for ``weak'' / ``strong'' scalar pairs (e.g. \emph{good} /
+\emph{excellent}). Several trends are visible. First, in each scale
+participants generated implicatures. They were substantially less likely
+to assign high star ratings to weaker scalar terms, despite the literal
+semantic compatibility of those terms with those states shown in
+Experiment 2. Second, the difference between strong and weak scalar
+items varied considerably across scales, consistent with previous work
+(van Tiel et al., 2014).
 
@@
 
-\section{Model}\label{model}
+\section{Model Simulations}\label{model-simulations}
 
@@
 and 4) the expanded set of five alternatives. Literal semantics for the
-generic negative alternative served as a baseline ``none``-style
-semantics in which the scalar item was only compatible with 1 star.
+generic negative alternative served as a baseline ``none" semantics in
+which the scalar item was only compatible with 1 star.
 
@@
 we included four and five alternatives, with the alternatives derived
-empirically for the specific scale we used. An example fit for the five
-alternatives model is shown in Figure \ref{fig:fiveAltsScatter}.
+empirically for the specific scale we used. Figure
+\ref{fig:fiveAltsScatter} plots model fit for the five alternatives
+model.
 
@@
 \centering
-\begin{tabular}{lrrr}
+\begin{tabular}{lll}
   \hline
-Model & $\alpha$ & Two alts & Four alts \\ 
+model & Empirical 2-alts & Empirical 4-alts \\ 
   \hline
-Two alts &   9 & 0.54 & 0.57 \\ 
-  Two alts + generic negative  &   6 & 0.62 & 0.66 \\ 
-  Four alts &   4 & 0.84 & 0.90 \\ 
-  Five alts &   4 & 0.86 & 0.90 \\ 
+5-alts & r = 0.88 (alpha = 4.4) & r = 0.91 (alpha = 4.5) \\ 
+  4-alts & r = 0.85 (alpha = 4.4) & r = 0.89 (alpha = 4.7) \\ 
+  3-alts & r = 0.68 (alpha = 6.8) & r = 0.71 (alpha = 6.7) \\ 
+  2-alts & r = 0.54 (alpha = 8.9) & r = 0.56 (alpha = 9.4) \\ 
    \hline
@@
 different lexical scales produce strikingly different patterns of
-inference ({van Tiel} et al., 2014).
+inference (van Tiel et al., 2014).
 
@@
 
+\hypertarget{refs}{}
+\hypertarget{ref-degen2015}{}
 Degen, J., \& Tanenhaus, M. K. (2015). Processing scalar implicature: A
@@
 
+\hypertarget{ref-frank2012}{}
 Frank, M., \& Goodman, N. D. (2012). Predicting pragmatic reasoning in
@@
 
+\hypertarget{ref-franke2014}{}
 Franke, M. (2014). Typical use of quantifiers: A probabilistic speaker
@@
 
+\hypertarget{ref-goodman2013}{}
 Goodman, N. D., \& Stuhlmuller, A. (2013). Knowledge and implicature:
@@
 
+\hypertarget{ref-grice1975}{}
 Grice, H. P. (1975). Logic and conversation. In P. Cole \& J. Morgan
@@
 
+\hypertarget{ref-horn1972}{}
 Horn, L. R. (1972). \emph{On the semantic properties of logical
@@
 
+\hypertarget{ref-levinson2000}{}
 Levinson, S. C. (2000). \emph{Presumptive meanings: The theory of
@@
 
+\hypertarget{ref-lewis1969}{}
 Lewis, D. (1969). \emph{Convention: A philosophical study}. John Wiley
@@
 
+\hypertarget{ref-sperber1995}{}
 Sperber, D., \& Wilson, D. (1995). \emph{Relevance: Communication and
@@
 
-{van Tiel}, B. J. M. (2014). Quantity matters: Implicatures, typicality,
+\hypertarget{ref-vantiel2014}{}
+van Tiel, B. J. M. (2014). Quantity matters: Implicatures, typicality,
 and truth.
 
-{van Tiel}, B. J. M., Van Miltenburg, E., Zevakhina, N., \& Geurts, B.
+\hypertarget{ref-vantiel2014b}{}
+van Tiel, B. J. M., Van Miltenburg, E., Zevakhina, N., \& Geurts, B.
 (2014). Scalar diversity. \emph{Journal of Semantics}, ffu017.

### 2016-10-02 models/RSA_alternativeCostFormulation.Rmd
sanitize

@@
   numerator = speaker.inf(m[rating, degree], alpha)
-  normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
-  return(numerator / normalize)
+  return(ifelse(numerator < 0, 0, numerator))
+#   normalize = sum(sapply(m[rating, ], function(i) {speaker.inf(i, alpha)}))
+#   return(numerator / normalize)
 }
@@
                           )))
+  # return(ifelse(numerator < 0, 0, numerator))
   if (normalize == 0) return(0)
